### 2014-08-15 ising/Fibonacci/about.tex
start writing about fibonacci

\title{Error Correction in a Phenomenological Fibonacci Anyon Quantum Code}

\author{Simon Burton, Courtney Brell, Steven Flammia}
%\date{\today}

\documentclass[12pt]{article}
%\documentclass[11pt, twocolumn]{article}

%\usepackage{epsf}
\usepackage{amsmath}
\usepackage{color}
\usepackage{natbib}
%\usepackage{cite}

\RequirePackage{amsmath}
\RequirePackage{amssymb}
\RequirePackage{amsthm}
%\RequirePackage{algorithmic}
%\RequirePackage{algorithm}
%\RequirePackage{theorem}
%\RequirePackage{eucal}
\RequirePackage{color}
\RequirePackage{url}
\RequirePackage{mdwlist}

\RequirePackage[all]{xy}
\CompileMatrices
\RequirePackage{hyperref}
\RequirePackage{graphicx}
\RequirePackage[dvips]{geometry}

\begin{document}

\maketitle

\def\Complex {C}
\def\tensor{\otimes}
\def\Tensor{\bigotimes}
\def\bra #1{\langle #1|}
\def\ket #1{|#1\rangle}
\def\braket #1#2{\langle #1|#2 \rangle}

%\def\Set{\widetilde{\text{Set}}}
%\def\Top{\widetilde{\text{Top}}}
%\def\Vec{\widetilde{\text{Vec}}}
%\def\Chain{\widetilde{\text{Chain}}}

%\def\ker{\text{ker}}
%\def\coker{\text{coker}}
%\def\im{\text{im}}

%\def\H{\mathcal{H}}
%\def\H{H}
%\def\S{S}
\def\mathZ{\mathbb{Z}}
\def\mathR{\mathbb{R}}

%\def\nin{\not\in}

% ----------------------------------------------------------------------------
%

\section{Braid group}

Braid group on $n$ strands is the group $B_n$ generated by $n-1$ generators
$\sigma_1, \sigma_2, ... \sigma_{n-1}$ with the following relations:
    $$ \sigma_i \sigma_j = \sigma_j \sigma_i \ \text{when}\ |i-j| > 2, $$
    $$ \sigma_i \sigma_{i+1} \sigma_i =  \sigma_{i+1} \sigma_i \sigma_{i+1}.$$

\section{Fibonacci Anyons}

So we have a representation of the braid group.

\section{Curve Diagrams}

Given a topological space $X$ we define the {\it mapping class group} of $X$ as
the set of homeomorphisms $f:X\to X$ modulo isotopy

    % $$ MCG(X) := \{ f : X \to X \text{s.t.} f \text{is homeomorphism} \} / \sim_{\text{iso}} $$
    $$ MCG(X) := \{ f : X \to X \} / \sim_{\text{iso}}.$$

In particular we are interested in the $n$-punctured disc:

    $$ D_n := \mathZ^2 - n.$$

topologically this is a sphere with $n+1$ holes in it.

It is a theorem that the group $MCG(D_n)$ is isomorphic to $B_n.$
(See \cite{Kassel10}, chapter 1.)

Curve diagrams, see \cite{Dehornoy02}.

We verify the braid relations directly.

%
%\begin{center}
%%\includegraphics[width=0.5\textwidth]{mypicture.png}
%\includegraphics{fig00.eps}
%\end{center}

% ----------------------------------------------------------------------------

\bibliography{refs}{}
\bibliographystyle{abbrv}

\end{document}

### 2014-08-15 ising/Fibonacci/render.py
start writing about fibonacci

@@ -1,0 +1,54 @@
+#!/usr/bin/env python
+
+import sys
+
+from pyx import canvas, path, deco, trafo, style, text, color
+
+text.set(mode="latex") 
+text.set(docopt="12pt")
+#text.preamble(r"\usepackage{amsmath}")
+#text.preamble(r"\
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+def arrow(x0, y0, x1, y1, extra=[]):
+    c.stroke(path.line(x0, y0, x1, y1),
+        extra+[deco.earrow(size=0.1)])
+
+#c.stroke(
+#    path.curve(0, 0, 0, 4, 2, 4, 3, 3),
+#    [style.linewidth.THICK, style.linestyle.dashed, color.rgb.blue,
+#    deco.earrow([deco.stroked([color.rgb.red, style.linejoin.round]),
+#                       deco.filled([color.rgb.green])], size=1)])
+
+def line(x0, y0, x1, y1, extra=[]):
+    c.stroke(path.line(x0, y0, x1, y1), extra)
+
+def varrow(x, y0, y1, extra=[], label=None):
+    arrow(x, y0, x, y1, extra)
+    if label:
+        c.text(x-0.1, (y0+y1)/2., label, [text.halign.boxright])
+
+
+def harrow(x0, x1, y, extra=[], label=None):
+    arrow(x0, y, x1, y, extra)
+    if label:
+        c.text((x0+x1)/2., y+0.1, label,
+            [text.valign.bottom, text.halign.boxcenter])
+
+
+
+# -------------------------------------------------
+
+c = canvas.canvas()
+
+harrow(0, 1, 0)
+
+c.writeEPSfile("fig00.eps")
+
+# -------------------------------------------------
+
+
+
+

### 2014-08-18 ising/Fibonacci/qip2014/poster.py

@@ -1,0 +1,760 @@
+#!/usr/bin/env python
+
+import sys
+import math
+from random import *
+from math import log10
+
+from pyx import canvas, path, deco, trafo, style, text, color, unit, epsfile, deformer
+
+
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow = (rgb.red,
+    rgbfromhexstring("#008000"),
+    rgb.blue, rgb(0.75, 0.75, 0))
+
+blue = rgb(0., 0., 0.8)
+lred = rgb(1., 0.4, 0.4)
+
+
+text.set(mode="latex") 
+#text.set(docopt="10pt")
+text.preamble(r'\usepackage{amsfonts}')
+text.preamble(r"\def\I{\mathbb{I}}")
+
+
+c = canvas.canvas()
+# [trafo.scale(10.)])
+
+# Dimensions of A0 in cm
+SCALE = 4.
+#w = 118.9 / SCALE
+#h = 84.1 / SCALE
+
+# portrait
+w = 84.1 / SCALE
+h = 118.9 / SCALE
+
+dr = 0.5 # line height..
+
+dw = w/3 # column separation
+m = 0.5 # margin width
+
+
+def cross(x, y, r=0.1):
+    c.stroke(path.line(x-r, y, x+r, y))
+    c.stroke(path.line(x, y-r, x, y+r))
+
+cross(0.1, 0.1)
+cross(w-0.1, 0.1)
+cross(0.1, h-0.1)
+cross(w-0.1, h-0.1)
+
+
+y = h-2*dr
+
+c.text(w/2, y,
+    r"{\huge Error Correction in a Fibonacci Fusion Code}",
+    [text.halign.boxcenter, text.valign.top, text.size(1)])
+
+y -= 2*dr
+c.text(w/2, y,
+    r"{\large Simon Burton$^1$, Courtney G. Brell$^{1,2}$, Steven T. Flammia$^1$}",
+    [text.halign.boxcenter, text.valign.top])
+
+#c.text(w/2, y,
+#    r"{\large Simon Burton{\tiny(1)}, Courtney G. Brell\(1,2\), Steven T. Flammia{(1)}}",
+#    [text.halign.boxcenter, text.valign.top])
+
+y -= dr
+c.text(w/2, y,
+    r"{\it $^1$ Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}",
[…]

### 2014-08-19 ising/Fibonacci/about.tex

@@
 
-\documentclass[12pt]{article}
+\documentclass[12pt,a4paper]{article}
 %\documentclass[11pt, twocolumn]{article}
+
+\usepackage[paper=a4paper,dvips,top=1.5cm,left=1.5cm,right=1.5cm,
+    foot=1cm,bottom=1.5cm]{geometry}
 
@@
 
+%\def\heading #1{\noindent\underline{\Large\bf #1}}
+\def\heading #1{\vskip 20pt \noindent\underline{\bf #1}\vskip 5pt}
+
 % ----------------------------------------------------------------------------
@@
 
-\section{Braid group}
+\heading{Braid group}
 
@@
 
-\section{Fibonacci Anyons}
+% ----------------------------------------------------------------------------
 
-So we have a representation of the braid group.
+\heading{Fibonacci Anyons}
 
-\section{Curve Diagrams}
+So we have a (linear) representation of the braid group:
 
-Given a topological space $X$ we define the {\it mapping class group} of $X$ as
-the set of homeomorphisms $f:X\to X$ modulo isotopy
+    $$ \kappa : B_n \to GL(F_n).$$
 
-    % $$ MCG(X) := \{ f : X \to X \text{s.t.} f \text{is homeomorphism} \} / \sim_{\text{iso}} $$
-    $$ MCG(X) := \{ f : X \to X \} / \sim_{\text{iso}}.$$
+Where $F_n$ is the Hilbert state space of $n$ Fibonacci anyons with
+trivial total charge.
 
-In particular we are interested in the $n$-punctured disc:
+% ----------------------------------------------------------------------------
 
-    $$ D_n := \mathZ^2 - n.$$
+\heading{Snake Diagrams}
 
-topologically this is a sphere with $n+1$ holes in it.
+%Given a topological space $X$ we define the {\it mapping class group} of $X$ as
+%the set of homeomorphisms $f:X\to X$ modulo isotopy
+%
+%    % $$ MCG(X) := \{ f : X \to X \text{s.t.} f \text{is homeomorphism} \} / \sim_{\text{iso}} $$
+%    $$ MCG(X) := \{ f : X \to X \} / \sim_{\text{iso}}.$$
+
+Given a topological manifold $M$ we define the {\it mapping class group} of $M$ as
+the set of homeomorphisms $f:M\to M$ modulo isotopy
+
+    $$ MCG(M) := \{ f : M \to M \} / \sim_{\text{iso}}.$$
+
+If $M$ has boundary $\partial M$ we require the homeomorphisms to
+be the identity on $\partial M$.
+
+In particular we are interested in
+ the $n$-punctured disc.
+This is a disc $D = \{ x\in \mathR^2 s.t. |x|\leq 1 \} $
+with $n$ points removed:
+
+    $$ D_n := D - Q_n,$$
+
+where $Q_n$ is some finite subset of the interior of $D$.
+
+%topologically this is a sphere with $n+1$ holes in it.
 
@@
 
-Curve diagrams, see \cite{Dehornoy02}.
+We fix $Q_n$ to be the points $\{(0, i/(n+1)) for i=1,...n\}$
+then we define the line $L = \{(0, x) s.t. |x|\leq 1\}.$
+Given a representative $f$ of an element of $MCG(D_n)$
+we define the
+snake diagram as the
+image of $L$ under $f$.
 
-We verify the braid relations directly.
+It is a theorem (see \cite{Dehornoy02}) that such snake diagrams
+correspond uniquely to elements of the mapping class group, and
+hence to the braid group $B_n$.
 
-%
-%\begin{center}
-%%\includegraphics[width=0.5\textwidth]{mypicture.png}
-%\includegraphics{fig00.eps}
-%\end{center}
+Here we verify the braid relations directly:
+
+\begin{center}
+%\includegraphics[width=0.5\textwidth]{mypicture.png}
+\includegraphics[width=0.5\textwidth]{curve-braid.eps}
+\end{center}
+
+% ----------------------------------------------------------------------------
+
+\heading{Pair-of-pants decompositions}
+
+We measure charge in regions bounded by curves, ie. elements of
+the first homology group $H_1(D_n).$
 

### 2014-08-19 ising/Fibonacci/qip2014/poster.py

@@ -746,7 +746,10 @@ instance that exceeds this bound is considered
 [text.parbox(dw-2*m),])
 
 y -= 18*dr
-c.insert(epsfile.epsfile(x, y, "qip/fibonacci.eps", width=(dw-2*m)))
+try:
+    c.insert(epsfile.epsfile(x, y, "qip/fibonacci.eps", width=(dw-2*m)))
+except IOError, e:
+    print e
 
 
 # -------------------------------------------------------------------

### 2014-08-22 ising/Fibonacci/about.tex

@@
 
-\heading{Snake Diagrams}
+\heading{Curve Diagrams}
 
@@
 we define the
-snake diagram as the
+curve diagram as the
 image of $L$ under $f$.
 
-It is a theorem (see \cite{Dehornoy02}) that such snake diagrams
+It is a theorem (see \cite{Dehornoy02}) that such curve diagrams
 correspond uniquely to elements of the mapping class group, and
@@
 
-We measure charge in regions bounded by curves, ie. elements of
-the first homology group $H_1(D_n).$
+%We measure charge in regions bounded by curves, ie. elements of
+%the first homology group $H_1(D_n).$
 

### 2014-08-24 ising/Fibonacci/about.tex
whack whack

@@
-\title{Error Correction in a Phenomenological Fibonacci Anyon Quantum Code}
+%\title{Error Correction in a Phenomenological Fibonacci Anyon Quantum Code}
+\title{Random Fibonacci Anyons Simulable via Covariant Action of Mapping Class Group}
 
@@
 %\def\heading #1{\noindent\underline{\Large\bf #1}}
-\def\heading #1{\vskip 20pt \noindent\underline{\bf #1}\vskip 5pt}
+\def\heading #1{\vskip 20pt \noindent\underline{\large \bf #1}\vskip 5pt}
+
+\def\important #1{\underline{\bf #1}}
 
@@
 
+The disc $D = \{ x\in \mathR^2\ s.t.\ |x|\leq 1 \} $,
+has boundary $\partial D = \{ x\in \mathR^2\ s.t.\ |x|=1 \} $.
+
+Given a finite set $ Q_n \subset D-\partial D$,
+we denote $D_n$ as the pair $(D, Q_n).$
+%Topologically, this definition does not depend on
+%anything but the cardinality of $Q_n.$
+
+We define the mapping class group of $D_n$,
+$MCG(D_n),$ as the set of homeomorphisms $D\to D$ that
+restrict to a permutation on $Q_n,$ modulo isotopy that
+fixes $Q_n.$
+Such an equivelance class
+of homeomorphisms will be denoted as $\phi:D_n\to D_n.$
+
+We can think of $D_n$ as the unit disc with $n$ holes,
+and the mapping class group as the set of homeomorphisms on
+this space, modulo isotopy.
+
+The line $L = \{ x\in \mathR\ s.t.\ |x|\leq 1 \} $,
+and a finite set $R_n\subset L$,
+$L_n = (L, R_n).$
+
+We define a curve diagram as an embedding $f : L\to D$ that
+restricts to an injection $R_n\to Q_n,$ modulo
+isotopy.
+This will be denoted as $f : L_n\to D_n.$
+We can generalize this to $f : L_m\to D_n$ with $m\leq n$
+to mean a map $L\to D$ that restricts to an injection $R_m\to Q_n,$
+modulo isotopy.
+
+%\important{Definition:} A curve diagram is...
+
+% ----------------------------------------------------------------------------
+
+\heading{Group action}
+
+The mapping class group $MCG(D_n)$ acts on curve diagrams $f : L_n\to D_n$
+via post-composition.
+
+\important{Definition:} by a {\it local action} on a curve
+diagram $f:L_n\to D_n$ we mean an element of $MCG(D_n)$
+that can be represented by a half-twist that acts
+on a small neighbourhood of $f([i, i+1]).$
+We denote such an element by $b(i, f).$
+
+\important{Definition:} by a {\it sequence of local moves} on a curve
+diagram $f:L_n\to D_n$ we mean a
+sequence of curve diagrams $f_k: L_n\to D_n$ and local actions:
+
+        $$ b(i_1, f_1), b(i_2, f_2), ... b(i_N, f_N) $$
+
+such that $f_1=f,$ and
+
+        $$ f_{k+1} = b(i_k, f_k) f_k,\ \  \text{} 1\leq k<N.$$
+
+% ----------------------------------------------------------------------------
+
+\heading{Local factorization of $MCG(D_n)$}
+
+\important{Theorem:}
+Given curve diagrams $f:L_n\to D_n$ and $g:L_2\to D_n$
+find $\phi\in MCG(D_n)$ as a product of
+a sequence of local moves such that % DIAGRAM
+$g = \phi f i.$
+
+\important{Proof:}
+
+1) decompose $f$ along (finitely many) intersections
+with $g.$
+
+% DIAGRAM
+
+2) on each component $k$:
+
+% DIAGRAM
+
+let $h_k = g_k + f_k.$
+This is a simple closed curve in $D$...
+
+% ----------------------------------------------------------------------------
+
 %Given a topological space $X$ we define the {\it mapping class group} of $X$ as
@@
 
-Given a topological manifold $M$ we define the {\it mapping class group} of $M$ as
-the set of homeomorphisms $f:M\to M$ modulo isotopy
+%Given a topological manifold $M$ we define the {\it mapping class group} of $M$ as
+%the set of homeomorphisms $f:M\to M$ modulo isotopy
+%
+%    $$ MCG(M) := \{ f : M \to M \} / \sim_{\text{iso}}.$$
+%
+%If $M$ has boundary $\partial M$ we require the homeomorphisms to
+%be the identity on $\partial M$.
+%
+%In particular we are interested in
+% the $n$-punctured disc.
+%This is a disc $D = \{ x\in \mathR^2 s.t. |x|\leq 1 \} $
+%with $n$ points removed:
+%
+%    $$ D_n := D - Q_n,$$
+%
+%where $Q_n$ is some finite subset of the interior of $D$.
+%
+%%topologically this is a sphere with $n+1$ holes in it.
+%
+%It is a theorem that the group $MCG(D_n)$ is isomorphic to $B_n.$
+%(See \cite{Kassel10}, chapter 1.)
+%
+%We fix $Q_n$ to be the points $\{(0, i/(n+1)) for i=1,...n\}$
+%then we define the line $L = \{(0, x) s.t. |x|\leq 1\}.$
+%Given a representative $f$ of an element of $MCG(D_n)$
+%we define the
+%curve diagram as the
+%image of $L$ under $f$.
+%
+%It is a theorem (see \cite{Dehornoy02}) that such curve diagrams
+%correspond uniquely to elements of the mapping class group, and
+%hence to the braid group $B_n$.
 
-    $$ MCG(M) := \{ f : M \to M \} / \sim_{\text{iso}}.$$
-
-If $M$ has boundary $\partial M$ we require the homeomorphisms to
-be the identity on $\partial M$.
-
-In particular we are interested in
- the $n$-punctured disc.
-This is a disc $D = \{ x\in \mathR^2 s.t. |x|\leq 1 \} $
-with $n$ points removed:
-
-    $$ D_n := D - Q_n,$$
-
-where $Q_n$ is some finite subset of the interior of $D$.
-
-%topologically this is a sphere with $n+1$ holes in it.
-
-It is a theorem that the group $MCG(D_n)$ is isomorphic to $B_n.$
-(See \cite{Kassel10}, chapter 1.)
-
-We fix $Q_n$ to be the points $\{(0, i/(n+1)) for i=1,...n\}$
-then we define the line $L = \{(0, x) s.t. |x|\leq 1\}.$
-Given a representative $f$ of an element of $MCG(D_n)$
-we define the
-curve diagram as the
-image of $L$ under $f$.
-
-It is a theorem (see \cite{Dehornoy02}) that such curve diagrams
-correspond uniquely to elements of the mapping class group, and
-hence to the braid group $B_n$.
+\heading{Braid group representation}
 
@@
 
+\cite{Dehornoy02}
+
 % ----------------------------------------------------------------------------
 
-\heading{Pair-of-pants decompositions}
+%\heading{Pair-of-pants decompositions}
 
@@
 %the first homology group $H_1(D_n).$
+
+%http://arxiv.org/pdf/1002.2816.pdf
+%http://www.math.ucsb.edu/~zhenghwa/data/course/lecture_notes/Chap2.pdf
+%http://physics.stackexchange.com/questions/93183/about-the-atiyah-segal-axioms-on-topological-quantum-field-theory
+%http://mathoverflow.net/questions/359/a-reading-list-for-topological-quantum-field-theory
+%http://projecteuclid.org/download/pdf_1/euclid.cmp/1104178138
+%http://arxiv.org/pdf/math/9912085v1.pdf
 

### 2014-08-25 ising/Fibonacci/about.tex

@@
 
-%\important{Definition:} A curve diagram is...
+DIAGRAM
 
@@
 
-        $$ b(i_1, f_1), b(i_2, f_2), ... b(i_N, f_N) $$
+        $$ b(i_1, f_1),\ b(i_2, f_2),\ ...\ b(i_N, f_N) $$
 
@@
 
-\important{Theorem:}
+\important{Problem:}
 Given curve diagrams $f:L_n\to D_n$ and $g:L_2\to D_n$
@@
 
-\important{Proof:}
+\important{Solution:}
 
@@
 let $h_k = g_k + f_k.$
-This is a simple closed curve in $D$...
+This is a simple closed curve in $D$ which splits $D$
+into two regions, the inside (simply connected) and the
+outside.
+We find six cases, which we can distinguish between
+using the winding number and whether the end points
+of $f$ are inside or outside:
+
+% DIAGRAM
+
+% ----------------------------------------------------------------------------
+
+\heading{Combinatorial formulation}
+
+We discretize the prolem for software implementation...
+
+% ----------------------------------------------------------------------------
+
+\heading{Numerical results}
 

### 2014-08-25 ising/Fibonacci/about.tex

@@
 
-\usepackage[paper=a4paper,dvips,top=1.5cm,left=1.5cm,right=1.5cm,
-    foot=1cm,bottom=1.5cm]{geometry}
+%\usepackage[paper=a4paper,dvips,top=1.5cm,left=1.5cm,right=1.5cm,foot=1cm,bottom=1.5cm]{geometry}
+\usepackage[paper=a4paper,dvips,top=3.0cm,left=1.5cm,right=1.5cm,foot=1cm,bottom=1.5cm]{geometry}
 
@@
 $L_n = (L, R_n).$
+By a slight abuse of notation, we enumerate the points in $R_n$ 
+in a monotonically increasing order,
+and understand such notation as $[i, i+1]$ to mean the closed interval in $L$
+with (consecutive) endpoints $i, i+1 \in R_n.$
 
 We define a curve diagram as an embedding $f : L\to D$ that
-restricts to an injection $R_n\to Q_n,$ modulo
+restricts to a bijection $R_n\to Q_n,$ modulo
 isotopy.
@@
 
-DIAGRAM
+\begin{center}
+\includegraphics[width=0.5\textwidth]{curve-diagram.eps}
+\end{center}
 
@@
 
-\important{Definition:} by a {\it local action} on a curve
-diagram $f:L_n\to D_n$ we mean an element of $MCG(D_n)$
+\important{Definition:} by a {\it half-twist} on a curve
+diagram $f:L_n\to D_n$ at $i$ we mean an element of $MCG(D_n)$
 that can be represented by a half-twist that acts
 on a small neighbourhood of $f([i, i+1]).$
-We denote such an element by $b(i, f).$
+We denote a clockwise half-twist by $b(i, f):$
 
-\important{Definition:} by a {\it sequence of local moves} on a curve
+\begin{center}
+\includegraphics[width=0.2\textwidth]{halftwist-1.eps}
+\includegraphics[width=0.15\textwidth]{halftwist-2.eps}
+\end{center}
+
+See \cite{Kassel10} for more details on half-twists.
+
+\important{Definition:} by a {\it sequence of half-twists} on a curve
 diagram $f:L_n\to D_n$ we mean a
-sequence of curve diagrams $f_k: L_n\to D_n$ and local actions:
+sequence of curve diagrams $f_k: L_n\to D_n$, and a sequence of half-twists:
 
@@
 
-\heading{Local factorization of $MCG(D_n)$}
+\heading{Half-twist factorization of $MCG(D_n)$}
 
@@
 find $\phi\in MCG(D_n)$ as a product of
-a sequence of local moves such that % DIAGRAM
-$g = \phi f i.$
+a sequence of half-twists such that % DIAGRAM
+$g = \phi f i,$ where $i$ is an inclusion of $L_2$ into $L_n:$
+
+\begin{center}
+\includegraphics{halftwist-factor.eps}
+\end{center}
+
+\important{Examples:}
+
+In this example we use an inverse half-twist about the segment $[a, a+1]:$
+
+\begin{center}
+\includegraphics[width=0.6\textwidth]{example-problem-1.eps}
+\end{center}
 
@@
 
+\heading{Combinatorial Formulation}
+
+% ----------------------------------------------------------------------------
+
+\heading{Numerical Simulations}
+
+% ----------------------------------------------------------------------------
+
 \bibliography{refs}{}

### 2014-08-25 ising/Fibonacci/render.py

@@ -43,9 +43,20 @@ def harrow(x0, x1, y, extra=[], label=None):
 
 c = canvas.canvas()
 
-harrow(0, 1, 0)
+c.text(0.0, 1.8, "$L_2$", [])
+c.text(1.8, 1.8, "$D_n$", [])
+harrow(0.6, 1.8, 2.0, label="$g$")
 
-c.writeEPSfile("fig00.eps")
+c.text(0.9, 0.0, "$L_n$", [])
+
+arrow(0.2, 1.7, 1.0, 0.5)
+#c.text(0.2, 0.8, "$\subset$", [])
+c.text(0.2, 0.8, "$i$", [])
+
+arrow(1.2, 0.5, 1.9, 1.7)
+c.text(1.6, 0.8, "$\phi f$", [])
+
+c.writeEPSfile("halftwist-factor.eps")
 
 # -------------------------------------------------
 

### 2014-08-25 ising/Fibonacci/mkim.py

@@ -1,0 +1,190 @@
+#!/usr/bin/env python
+
+import sys
+import os
+import Image
+import numpy
+
+
+def write(c):
+    sys.stdout.write(c)
+    sys.stdout.flush()
+
+
+def flatten(im):
+
+    a = numpy.array(im)
+    shape = a.shape
+    m, n, _ = shape
+    
+    for i in range(m):
+      for j in range(n):
+    
+        v = a[i, j]
+    
+        vs = v.sum()
+        va = vs / 3
+        vd = ((v-va)**2/3.).sum()**0.5
+    
+        if va > 200:
+    
+            a[i, j] = [255, 255, 255]
+            #write('.')
+    
+        elif va>50 and vd>20:
+            a[i, j] = [0, 0, 0] # switch colour to black
+    
+        elif 1:
+    
+            continue
+    
+        elif va < 50:
+    
+            a[i, j] = [0, 0, 0]
+    
+        elif vd > 20.:
+    
+            a[i, j] = [255, 0, 0]
+    
+        else:
+            a[i, j] = [0, 0, 0]
+    
+            #print "%.1f"%va,
+            #print "%.0f"%vd,
+    
+            #vm = 1.*max(v)
+            #r = 255. / vm
+            #a[i, j] = r*v
+    
+      write('.')
+    write('\n')
+
+    im = Image.fromarray(a)
+
+    return im
+
+
+def pick(im):
+
+    a = numpy.array(im)
+    shape = a.shape
+    m, n, _ = shape
+    
+    for i in range(m):
+      for j in range(n):
+    
+        v = a[i, j]
+    
+        vs = v.sum()
+        va = vs / 3
+        vd = ((v-va)**2/3.).sum()**0.5
+    
+        if va > 200:
+            a[i, j] = [255, 255, 255]
+    
+        elif va>50 and vd>20:
+            a[i, j] = [0, 0, 0] # switch colour to black
+    
+        else:
+            a[i, j] = [255, 255, 255]
+    
+      write('.')
+    write('\n')
+
+    im = Image.fromarray(a)
+
+    return im
+
+
+def null(im):
+    return None
+
+
+def eps_setcolor(name, r, g, b):
+    s = open(name).read()
+    s = s.replace('0 setgray', '%.2f %.2f %.2f setrgbcolor' % (r, g, b))
+    open(name, 'w').write(s)
+
+
+def eps_split(name):
+
[…]

### 2014-08-26 ising/Fibonacci/about.tex
whack whack

@@
 
+Every surface that is not a sphere, torus, disc or annulus, admits
+a pair-of-pants decomposition, see \cite{Ivanov01}, Theorem 2.4.A.
+
 So we have a (linear) representation of the braid group:
@@
 The mapping class group $MCG(D_n)$ acts on curve diagrams $f : L_n\to D_n$
-via post-composition.
+via post-composition (left multiplication). See \cite{Dehornoy02}, chapter 6.
+
+%\heading{Braid group representation}
+
+In particular, we can single out specific ``braid'' elements of $MCG(D_n)$.
+These act on the image of a pair-of-pants embedding: $g:D_2\to D_n.$
+
+DIAGRAM
+
+Here we verify the braid relations directly:
+
+\begin{center}
+%\includegraphics[width=0.5\textwidth]{mypicture.png}
+\includegraphics[width=0.5\textwidth]{curve-braid.eps}
+\end{center}
+
+% ----------------------------------------------------------------------------
+
+\heading{Half-twists}
 
@@
 
-See \cite{Kassel10} for more details on half-twists.
+Each half-twist corresponds to a braid action of two neighbouring
+holes on $f$.
+See \cite{Kassel10}, Section 1.6.2, for more details on half-twists.
 
@@
 find $\phi\in MCG(D_n)$ as a product of
-a sequence of half-twists such that % DIAGRAM
+a sequence of half-twists such that
 $g = \phi f i,$ where $i$ is an inclusion of $L_2$ into $L_n:$
@@
 \end{center}
+
+The idea is that we would like to apply half-twists to a curve diagram
+until the two holes indicated by $g$ become neighbours.
 
@@
 
-% DIAGRAM
+\begin{center}
+\includegraphics[width=0.3\textwidth]{snake-decompose.eps}
+\end{center}
 
@@
 
-% DIAGRAM
+\begin{center}
+\includegraphics[width=0.3\textwidth]{snake-component.eps}
+\end{center}
 
@@
 outside.
-We find six cases, which we can distinguish between
+We find three basic cases (there are more including reflections
+and rotations of these), which we can distinguish between
 using the winding number and whether the end points
-of $f$ are inside or outside:
+of $f$ are on the inside or outside of $h_k$:
 
-% DIAGRAM
+\begin{center}
+\includegraphics[width=0.5\textwidth]{snake-cases.eps}
+\end{center}
 
@@
 
-\heading{Combinatorial formulation}
+\heading{Disjoint sum of two curve diagrams}
 
-We discretize the prolem for software implementation...
+Given two disjoint curve diagrams $f:L_m\to D_n$ and $f':L_{m'}\to D_n$
+we define their sum  $f+f':L_{m+m'}\to D_n$ ...
+
+% ----------------------------------------------------------------------------
+
+\heading{Planar diagrams}
+
+We aim discretize the problem for software implementation.
+Our first task is to characterize what happens to a curve
+if we ``forget'' any braiding inside a disc.
+We define the following set of ``planar diagrams'' as:
+
+    $$ T = \{ f(L)\cap E / \sim \ \text{s.t.}\ f:L\to D \}$$
+
+where $f:L\to D$ is a curve (not an isotopy class)
+whose image $f(L)$ intersects a disc $E\subset D$ in a finite number of components
+and the equivalence relation $\sim$ consists of isotopies that fix $\partial E.$
+
+This object has a simple combinatorial description 
+as a string consisting of
+the four labels {\bf ( ) H T} such that 
+the parentheses are balanced. The two labels H and T specify the
+head and tail endpoints of $f$, and each appears at most once in the string.
+
+For example, the following diagram is represented by
+the string {\bf(())H}:
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{planar.eps}
+\end{center}
+
+See \cite{Abramsky08} Proposition 1.6, for a similar treatment.
+
+% ----------------------------------------------------------------------------
+
+\heading{Tiling}
+
+Now we consider a tiling of the disc into subdiscs that are disjoint on
+their interiors.
+
+% ----------------------------------------------------------------------------
+
+\heading{Simulation and noise model}
 
@@
 \heading{Numerical results}
+
+\begin{center}
+\includegraphics[width=0.5\textwidth]{threshold-graph.eps}
+\end{center}
 
@@
 
-\heading{Braid group representation}
-
-Here we verify the braid relations directly:
-
-\begin{center}
-%\includegraphics[width=0.5\textwidth]{mypicture.png}
-\includegraphics[width=0.5\textwidth]{curve-braid.eps}
-\end{center}
-
-\cite{Dehornoy02}
-
 % ----------------------------------------------------------------------------
@@
 
-% ----------------------------------------------------------------------------
-
-\heading{Combinatorial Formulation}
-
-% ----------------------------------------------------------------------------
-
-\heading{Numerical Simulations}
+%% ----------------------------------------------------------------------------
+%
+%\heading{Combinatorial Formulation}
+%
+%% ----------------------------------------------------------------------------
+%
+%\heading{Numerical Simulations}
 

### 2014-08-26 ising/Fibonacci/mkim.py

@@ -11,7 +11,7 @@ def write(c):
     sys.stdout.flush()
 
 
-def flatten(im):
+def flat(im):
 
     a = numpy.array(im)
     shape = a.shape
@@ -86,7 +86,7 @@ def pick(im):
             a[i, j] = [0, 0, 0] # switch colour to black
     
         else:
-            a[i, j] = [255, 255, 255]
+            a[i, j] = [255, 255, 255] # whiteout
     
       write('.')
     write('\n')
@@ -155,6 +155,24 @@ if funcname == 'cat':
     args = sys.argv[2:]
     eps_cat(*args)
 
+elif funcname == 'trace':
+
+    name = sys.argv[2]
+    stem = '.'.join(name.split('.')[:-1])
+    
+    name_png = "%s.png" % (stem,)
+    name_pnm = "%s.pnm" % (stem,)
+    name_eps = "%s.eps" % (stem,)
+    
+    cmd = 'pngtopnm %s > %s' % (name_png, name_pnm)
+    print cmd
+    os.system(cmd)
+    
+    cmd = 'potrace -e -q -c %s' % (name_pnm)
+    print cmd
+    os.system(cmd)
+    
+    r, g, b = 1., 0.5, 0.5
 
 else:
     func = eval(funcname)
@@ -163,8 +181,8 @@ else:
     stem = '.'.join(name.split('.')[:-1])
     
     im = None
-    #im = Image.open(name)
-    #im = func(im)
+    im = Image.open(name)
+    im = func(im)
     
     name_png = "%s-%s.png" % (stem, funcname)
     name_pnm = "%s-%s.pnm" % (stem, funcname)
@@ -183,6 +201,8 @@ else:
     os.system(cmd)
     
     r, g, b = 1., 0.5, 0.5
+
+
 
 
 

### 2014-08-29 ising/Fibonacci/about.tex

@@
 
-\heading{Fibonacci Anyons}
+\heading{Anyons}
 
-Every surface that is not a sphere, torus, disc or annulus, admits
-a pair-of-pants decomposition, see \cite{Ivanov01}, Theorem 2.4.A.
+We measure charge contained within a disc. % region, circle
+Commuting measurements are either disjoint discs or
+one wholly contained within the other:
+
+DIAGRAM
+
+So (proof?) we get a basis for the Hilbert space from
+a pair-of-pants (POP) decomposition:
+
+DIAGRAM
+
+Every surface that is not a sphere, torus, disc or annulus, has
+a POP decomposition, see \cite{Ivanov01}, Theorem 2.4.A.
+
+We say that a POP decomposition of $D_n$
+{\it admits} a curve $f:L_n\to D_n$
+if the curve performs a depth first traversal of $Q_n.$
+This means that if the curve visits the trunk of a POP
+then it visits all the legs of the POP before leaving the POP.
+
+Conversely, given a curve $f:L_n\to D_n$
+and a binary rooted tree $t$,
+we can recover a unique POP that admits $f$.
+(proof: use small neighbourhoods of the curve)
+
+DIAGRAM
+
+\important{F-moves:} given a nested POP and admissable $f$,
+the f-move is the change of basis as follows:
+
+DIAGRAM
+
+\important{R-moves:} we examine the action of $MCG(D_n)$
+on our state space. Given a single POP and curve $f:L_2\to D_n$,
+the half-twist acts on $\psi$ as $R\psi$.
+
+DIAGRAM
+
+This together with f-moves gives all the half-twists on
+the curve $f$.
 
@@
 
-Where $F_n$ is the Hilbert state space of $n$ Fibonacci anyons with
-trivial total charge.
+Where $F_n$ is the Hilbert state space of $n$ Fibonacci anyons.
+%with trivial total charge.
+
+See \cite{Pfeifer12, Pfeifer14}
 
@@
 if we ``forget'' any braiding inside a disc.
-We define the following set of ``planar diagrams'' as:
+We adapt the Abramsky combinatorial formalism 
+of the Temperly-Lieb algebra to our needs (\cite{Abramsky08}, Proposition 1.6).
+The following set of ``planar diagrams'' as is defined as:
 
@@
 whose image $f(L)$ intersects a disc $E\subset D$ in a finite number of components
-and the equivalence relation $\sim$ consists of isotopies that fix $\partial E.$
+and the equivalence relation $\sim$ consists of 
+isotopies that fix $\partial E.$ % Local (relative?) isotopies
 
@@
 as a string consisting of
-the four labels {\bf ( ) H T} such that 
-the parentheses are balanced. The two labels H and T specify the
-head and tail endpoints of $f$, and each appears at most once in the string.
+the four labels {\bf (, ), H, T} such that 
+the parentheses are balanced. The two labels {\bf H} and {\bf T} specify the
+head and tail endpoints of $f$, each of which appears at most once in the string.
 
@@
 
-See \cite{Abramsky08} Proposition 1.6, for a similar treatment.
-
 % ----------------------------------------------------------------------------
@@
 
-Now we consider a tiling of the disc into subdiscs that are disjoint on
-their interiors.
+%Now we consider a tiling of the disc into subdiscs that are disjoint on
+%their interiors.
+We consider now a cellulation of a disc.
+Concretely, we choose a regular $l$ by $l$ square tiling of a square region.
+
+DIAGRAM
+
+The holes $Q_n$ will always be contained within the interior of the
+tiles.
+
+\important{Definition:} the discrete curve space $C_n^(l)$ consists of
+curves $L_n\to D_n$ modulo isotopy that fixes the boundary of
+every tile.
 

### 2014-08-31 ising/Fibonacci/about.tex

@@
     $$ \sigma_i \sigma_{i+1} \sigma_i =  \sigma_{i+1} \sigma_i \sigma_{i+1}.$$
-
-% ----------------------------------------------------------------------------
-
-\heading{Anyons}
-
-We measure charge contained within a disc. % region, circle
-Commuting measurements are either disjoint discs or
-one wholly contained within the other:
-
-DIAGRAM
-
-So (proof?) we get a basis for the Hilbert space from
-a pair-of-pants (POP) decomposition:
-
-DIAGRAM
-
-Every surface that is not a sphere, torus, disc or annulus, has
-a POP decomposition, see \cite{Ivanov01}, Theorem 2.4.A.
-
-We say that a POP decomposition of $D_n$
-{\it admits} a curve $f:L_n\to D_n$
-if the curve performs a depth first traversal of $Q_n.$
-This means that if the curve visits the trunk of a POP
-then it visits all the legs of the POP before leaving the POP.
-
-Conversely, given a curve $f:L_n\to D_n$
-and a binary rooted tree $t$,
-we can recover a unique POP that admits $f$.
-(proof: use small neighbourhoods of the curve)
-
-DIAGRAM
-
-\important{F-moves:} given a nested POP and admissable $f$,
-the f-move is the change of basis as follows:
-
-DIAGRAM
-
-\important{R-moves:} we examine the action of $MCG(D_n)$
-on our state space. Given a single POP and curve $f:L_2\to D_n$,
-the half-twist acts on $\psi$ as $R\psi$.
-
-DIAGRAM
-
-This together with f-moves gives all the half-twists on
-the curve $f$.
-
-So we have a (linear) representation of the braid group:
-
-    $$ \kappa : B_n \to GL(F_n).$$
-
-Where $F_n$ is the Hilbert state space of $n$ Fibonacci anyons.
-%with trivial total charge.
-
-See \cite{Pfeifer12, Pfeifer14}
 
@@
 
+% ----------------------------------------------------------------------------
+
+\heading{Anyons}
+
+We measure charge contained within a disc. % region, circle
+Commuting measurements are either disjoint discs or
+one wholly contained within the other.
+So (proof?) we get a basis for the Hilbert space from
+a pair-of-pants (POP) decomposition:
+
+\begin{center}
+\includegraphics[width=0.2\textwidth]{POP-1.eps}
+\end{center}
+
+The feet of the POP form the $n$ holes $Q_n$ in the disc $D$.
+\footnote{Every surface that is not a sphere, torus, disc or annulus, has
+a POP decomposition, see \cite{Ivanov01}, Theorem 2.4.A.}
+
+We say that a POP decomposition of $D_n$
+{\it admits} a curve $f:L_n\to D_n$
+if (there is a curve in the isotopy class of)
+the curve performs a depth first traversal of the POP.
+This means that if the curve visits the trunk of a POP
+then it visits all the legs of the POP before leaving that POP.
+
+\begin{center}
+\includegraphics[width=0.2\textwidth]{POP-2.eps}
+\end{center}
+
+Conversely, given a curve $f:L_n\to D_n$
+and a binary rooted tree $t$,
+we can recover a unique POP that admits $f$.
+(proof: use small neighbourhoods of the curve)
+
+\begin{center}
+\includegraphics[width=0.2\textwidth]{POP-3.eps}
+\end{center}
+
+\important{F-moves:} given a nested POP and admissable $f$,
+the F-move is the change of basis as follows:
+
+\begin{center}
+\includegraphics[width=0.3\textwidth]{POP-4.eps}
+\end{center}
+
+\important{R-moves:} we examine the action of $MCG(D_n)$
+on our state space. Given a single POP and curve $f:L_2\to D_n$,
+the half-twist on $f$ acts on $\psi$ as $R\psi$.
+
+DIAGRAM?
+
+This together with f-moves gives all the half-twists on
+the curve $f$.
+
+So we have a (linear) representation of the braid group:
+
+    $$ \kappa : B_n \to GL(F_n).$$
+
+Where $F_n$ is the Hilbert state space of $n$ Fibonacci anyons.
+%with trivial total charge.
+
+See \cite{Pfeifer12, Pfeifer14}
+
+% ----------------------------------------------------------------------------
+
+\heading{Half-twist factorization of $MCG(D_n)$}
+
 \important{Definition:} by a {\it sequence of half-twists} on a curve
@@
         $$ f_{k+1} = b(i_k, f_k) f_k,\ \  \text{} 1\leq k<N.$$
-
-% ----------------------------------------------------------------------------
-
-\heading{Half-twist factorization of $MCG(D_n)$}
 

### 2014-08-31 ising/Fibonacci/about.tex

@@
-%\title{Error Correction in a Phenomenological Fibonacci Anyon Quantum Code}
-\title{Random Fibonacci Anyons Simulable via Covariant Action of Mapping Class Group}
-
-\author{Simon Burton, Courtney Brell, Steven Flammia}
-%\date{\today}
-
 \documentclass[12pt,a4paper]{article}
@@
 
+\title{Random Fibonacci Anyons Simulable via Covariant Action of Mapping Class Group}
+
+\author{Simon Burton, Courtney G. Brell, Steven T. Flammia}
+
+%\date{\today}
+
+%\author{Simon Burton}
+%\affiliation{Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}
+%
+%\author{Courtney G. Brell}
+%\affiliation{Institut f\"ur Theoretische Physik, Leibniz Universit\"at Hannover, Appelstra\ss e 2, 30167 Hannover, Germany}
+%\affiliation{Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}
+%
+%\author{Steven T. Flammia}
+%\affiliation{Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}
+
 \maketitle
+
+%{\it $^1$ Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}
+%{\it $^2$ Institut f\"ur Theoretische Physik, Leibniz Universit\"at Hannover, Appelstra\ss e 2, 30167 Hannover, Germany}
 
@@
 \def\important #1{\underline{\bf #1}}
-
-% ----------------------------------------------------------------------------
-%
-
-\heading{Braid group}
-
-Braid group on $n$ strands is the group $B_n$ generated by $n-1$ generators
-$\sigma_1, \sigma_2, ... \sigma_{n-1}$ with the following relations:
-    $$ \sigma_i \sigma_j = \sigma_j \sigma_i \ \text{when}\ |i-j| > 2, $$
-    $$ \sigma_i \sigma_{i+1} \sigma_i =  \sigma_{i+1} \sigma_i \sigma_{i+1}.$$
 
@@
 
-We define a curve diagram as an embedding $f : L\to D$ that
+We define a {\it curve diagram} as an embedding $f : L\to D$ that
 restricts to a bijection $R_n\to Q_n,$ modulo
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{curve-diagram.eps}
+\includegraphics[width=0.4\textwidth]{curve-diagram.eps}
 \end{center}
@@
 The mapping class group $MCG(D_n)$ acts on curve diagrams $f : L_n\to D_n$
-via post-composition (left multiplication). See \cite{Dehornoy02}, chapter 6.
+via post-composition (left multiplication).
+This action is transitive and XXX so we can identify an element of
+$MCG(D_n)$ by its action on any curve $f:L_n\to D_n.$
+See \cite{Dehornoy02}, chapter 6.
 
@@
 
-In particular, we can single out specific ``braid'' elements of $MCG(D_n)$.
+We single out specific ``braid'' elements of $MCG(D_n)$.
 These act on the image of a pair-of-pants embedding: $g:D_2\to D_n.$
@@
 DIAGRAM
+
+The {\it braid group} on $n$ strands is the group $B_n$ generated by $n-1$ generators
+$\sigma_1, \sigma_2, ... \sigma_{n-1}$ with the following relations:
+    $$ \sigma_i \sigma_j = \sigma_j \sigma_i \ \text{when}\ |i-j| > 2, $$
+    $$ \sigma_i \sigma_{i+1} \sigma_i =  \sigma_{i+1} \sigma_i \sigma_{i+1}.$$
 
@@
 \end{center}
-
-% ----------------------------------------------------------------------------
-
-\heading{Half-twists}
 
@@
 holes on $f$.
-See \cite{Kassel10}, Section 1.6.2, for more details on half-twists.
+\footnote{See \cite{Kassel10}, Section 1.6.2, for more details on half-twists.}
 
@@
 We measure charge contained within a disc. % region, circle
+Measurement outcomes belong to a set of charges $\Lambda.$
 Commuting measurements are either disjoint discs or
 one wholly contained within the other.
-So (proof?) we get a basis for the Hilbert space from
+So (proof?) we get a basis for the Hilbert space of our system from
 a pair-of-pants (POP) decomposition:
@@
 
-The feet of the POP form the $n$ holes $Q_n$ in the disc $D$.
+The feet of the POP decomposition form the $n$ holes $Q_n$ in the disc $D$.
 \footnote{Every surface that is not a sphere, torus, disc or annulus, has
@@
 we can recover a unique POP that admits $f$.
-(proof: use small neighbourhoods of the curve)
+The above POP would be represented by the following tree:
 
@@
 \end{center}
+
+(proof: use small neighbourhoods of the curve)
 
@@
 Our first task is to characterize what happens to a curve
-if we ``forget'' any braiding inside a disc.
-We adapt the Abramsky combinatorial formalism 
-of the Temperly-Lieb algebra to our needs (\cite{Abramsky08}, Proposition 1.6).
-The following set of ``planar diagrams'' as is defined as:
+if we ``forget'' any braiding inside a sub-disc.
+We adapt the Abramsky combinatorial description 
+of the Temperly-Lieb algebra to our needs
+(see \cite{Abramsky08}, section 6.) %Proposition 1.6).
 
-    $$ T = \{ f(L)\cap E / \sim \ \text{s.t.}\ f:L\to D \}$$
+The set of {\it planar diagrams} is defined as:
 
-where $f:L\to D$ is a curve (not an isotopy class)
-whose image $f(L)$ intersects a disc $E\subset D$ in a finite number of components
+    $$ P = \{ f(L)\cap E / \sim \ \text{s.t.}\ f:L\to D \}$$
+
+where $f:L\to D$ is a continuous function 
+whose image $f(L)$ intersects a disc $E\subset D$ in a finite number of components,
 and the equivalence relation $\sim$ consists of 
@@
 the four labels {\bf (, ), H, T} such that 
-the parentheses are balanced. The two labels {\bf H} and {\bf T} specify the
+the parentheses are balanced.
+To construct the string, begin at a point on $\partial E$, and proceed
+clockwise. Visiting a strand for the first time produces a {\bf ( } label,
+and visiting a strand for the second time produces a {\bf ) } label.
+The two labels {\bf H} and {\bf T} specify the
 head and tail endpoints of $f$, each of which appears at most once in the string.
 
-For example, the following diagram is represented by
+For example, the following planar diagram can be represented by
 the string {\bf(())H}:
@@
 %their interiors.
-We consider now a cellulation of a disc.
+We now consider a cellulation of a disc.
 Concretely, we choose a regular $l$ by $l$ square tiling of a square region.
@@
 
-\important{Definition:} the discrete curve space $C_n^(l)$ consists of
+\important{Definition:} the discrete curve space $C_n^{(l)}$ consists of
 curves $L_n\to D_n$ modulo isotopy that fixes the boundary of

### 2014-08-31 ising/Fibonacci/mkim.py

@@ -76,8 +76,12 @@ def pick(im):
         v = a[i, j]
     
         vs = v.sum()
-        va = vs / 3
-        vd = ((v-va)**2/3.).sum()**0.5
+        va = vs / 3.
+        #vd = ((v-va)**2/3.).sum()**0.5
+        vd = ((v[0]-va)**2+(v[1]-va)**2+(v[2]-va)**2 ) / 3.
+        vd = vd**0.5
+
+        #write("%.0f,%.0f "%(va,vd))
     
         if va > 200:
             a[i, j] = [255, 255, 255]
@@ -86,6 +90,7 @@ def pick(im):
             a[i, j] = [0, 0, 0] # switch colour to black
     
         else:
+            #print "%.1f:%s"%(vd, v-va),
             a[i, j] = [255, 255, 255] # whiteout
     
       write('.')

### 2014-09-01 ising/Fibonacci/about.tex

@@
 
+%\begin{abstract}
+%
+%\end{abstract}
+
 \maketitle
@@
 
-\heading{Curve Diagrams}
+\heading{Abstract}
+
+Technical contribution: 
+(1) discretization of curve diagrams,
+(2) classification theorem
+(3) simulation
+
+% ----------------------------------------------------------------------------
+
+\heading{Introduction}
+
+Fibonacci hard
+
+Below bond-percolation threshold we expect to see clusters
+of charges of size $O(log(n))$ with variance $O(log(log(n))$. CITATION
+
+% ----------------------------------------------------------------------------
+
+\heading{Curve diagrams}
 
@@
 \begin{center}
-\includegraphics[width=0.2\textwidth]{POP-3.eps}
+\includegraphics[width=0.14\textwidth]{POP-3.eps}
 \end{center}
@@
 
+XXX F-moves can be nested
+
 \important{R-moves:} we examine the action of $MCG(D_n)$
@@
 This together with f-moves gives all the half-twists on
-the curve $f$.
+the curve $f$. Therefore, we may work solely with curve
+diagrams, forgetting the underlying POP (tree) structure.
 
-So we have a (linear) representation of the braid group:
+We have a (linear) representation of the braid group:
 
@@
 
+XXX
+
 % ----------------------------------------------------------------------------
@@
 isotopies that fix $\partial E.$ % Local (relative?) isotopies
+Each component of $f(L)\cap E$ we call a {\it strand.}
 
-This object has a simple combinatorial description 
-as a string consisting of
+Elements of $P$ have a simple combinatorial description 
+as a finite sequence (a word) consisting of
 the four labels {\bf (, ), H, T} such that 
 the parentheses are balanced.
-To construct the string, begin at a point on $\partial E$, and proceed
-clockwise. Visiting a strand for the first time produces a {\bf ( } label,
+To construct such a word, begin at a point on $\partial E$, and proceeding
+clockwise: visiting a strand for the first time produces a {\bf ( } label,
 and visiting a strand for the second time produces a {\bf ) } label.
 The two labels {\bf H} and {\bf T} specify the
-head and tail endpoints of $f$, each of which appears at most once in the string.
+head and tail endpoints of $f$, each of which appears at most once in the word.
 
 For example, the following planar diagram can be represented by
-the string {\bf(())H}:
+the word {\bf(())H}:
 
@@
 
+Combinatorialy, we store an element of $C_n^{(l)}$ by patching
+together words for planar diagrams in a compatible way: 
+neighbouring tiles must agree on the strands that they share.
+
 % ----------------------------------------------------------------------------
@@
 \heading{Simulation and noise model}
+
+Poisson process, pair creation $t_{\mathrm{sim}}$
+
+Extraction of syndrome, PICTURE
+
+Clustering of charges, CITE BravyiHaah
+
+Multi-round
 
@@
 \end{center}
+
+Threshold appears at $t_{\mathrm{sim}}\simeq 0.125$
+
+% ----------------------------------------------------------------------------
+
+\heading{Conclusion}
+
+% ----------------------------------------------------------------------------
+
+\important{Acknowledgements}
 
@@
 
-%We measure charge in regions bounded by curves, ie. elements of
+%In an abelian theory we measure charge in regions bounded by curves, ie. elements of
 %the first homology group $H_1(D_n).$
@@
 
-%% ----------------------------------------------------------------------------
-%
-%\heading{Combinatorial Formulation}
-%
-%% ----------------------------------------------------------------------------
-%
-%\heading{Numerical Simulations}
-
 % ----------------------------------------------------------------------------

### 2014-09-02 about.tex
tweaks

--- 2014-09-01 ising/Fibonacci/about.tex
@@
 Below bond-percolation threshold we expect to see clusters
-of charges of size $O(log(n))$ with variance $O(log(log(n))$. CITATION
+of charges of size $O(log(n))$ with variance $O(1)$ \cite{Bazant00}.
 
@@
 
+XXX $\partial L\to \partial D$ XXX
+
+Given two disjoint curve diagrams $f:L_m\to D_n$ and $f':L_{m'}\to D_n$
+we define their sum  $f+f':L_{m+m'}\to D_n$ ...
+
 % ----------------------------------------------------------------------------
@@
 See \cite{Dehornoy02}, chapter 6.
+XXX $\partial L\to \partial D$ XXX
 
@@
 
-\heading{Disjoint sum of two curve diagrams}
-
-Given two disjoint curve diagrams $f:L_m\to D_n$ and $f':L_{m'}\to D_n$
-we define their sum  $f+f':L_{m+m'}\to D_n$ ...
-
-% ----------------------------------------------------------------------------
-
 \heading{Planar diagrams}
 
-We aim discretize the problem for software implementation.
+We aim to discretize the problem for software implementation.
 Our first task is to characterize what happens to a curve
@@
 Concretely, we choose a regular $l$ by $l$ square tiling of a square region.
-
-DIAGRAM
-
 The holes $Q_n$ will always be contained within the interior of the
@@
 
+\begin{center}
+\includegraphics[width=0.4\textwidth]{discrete-curve.eps}
+\end{center}
+
 % ----------------------------------------------------------------------------
@@
 
-Extraction of syndrome, PICTURE
+PICTURE
 
-Clustering of charges, CITE BravyiHaah
+Extraction of syndrome
+
+PICTURE
 
 Multi-round
+Clustering of charges, \cite{Brell13} \cite{Bravyi13}
+
+Fail on big braid
 
@@
 
-Threshold appears at $t_{\mathrm{sim}}\simeq 0.125$
+Threshold appears at $t_{\mathrm{sim}}\simeq 0.124 \pm 0.004$
+
+Plot of computational power...
 
@@
 
-\heading{Conclusion}
+\heading{Conclusion/Discussion}
 
@@
 \important{Acknowledgements}
+
+Yo to my bro's and homies
 

### 2014-09-02 about.tex
diagrams

@@
-\documentclass[12pt,a4paper]{article}
+\documentclass[11pt,a4paper]{article}
 %\documentclass[11pt, twocolumn]{article}
@@
 Technical contribution: 
-(1) discretization of curve diagrams,
-(2) classification theorem
+(1) classification theorem
+(2) discretization of curve diagrams
 (3) simulation
@@
 
+the dimensionality of the state space
+of anyons grows as $d^n$.
+For fibonacci anyons $d\simeq 1.6$ and
+it is known that braiding generates a dense
+set of unitaries on the state space, so we
+only expect to be able to simulate for small $n.$
+
 Below bond-percolation threshold we expect to see clusters
 of charges of size $O(log(n))$ with variance $O(1)$ \cite{Bazant00}.
+
+DIAGRAM
 
@@
 \begin{center}
-\includegraphics[width=0.4\textwidth]{discrete-curve.eps}
+\includegraphics[width=0.3\textwidth]{discrete-curve.eps}
 \end{center}
@@
 
-Poisson process, pair creation $t_{\mathrm{sim}}$
+\begin{center}
+(i)
+\includegraphics[width=0.26\textwidth]{pair-create.eps}
+\hskip 10pt
+(ii)
+\includegraphics[width=0.26\textwidth]{syndrome-1.eps}
+\hskip 10pt
+(iii)
+\includegraphics[width=0.26\textwidth]{syndrome-2.eps}
+\end{center}
 
-PICTURE
+We Maintain a collection of disjoint curves.
 
-Extraction of syndrome
+(i) Poisson process, pair creation $t_{\mathrm{sim}}$.
 
-PICTURE
+(ii) join fusion trees (curves)
+that participate in the same site (tile).
+(iii) measure charge on each site and leave result on
+one of the strands.
+These charge measurements give the initial syndrome for the
+error correction procedure.
 
-Multi-round
-Clustering of charges, \cite{Brell13} \cite{Bravyi13}
+Multi-round, clustering of charges, \cite{Brell13} \cite{Bravyi13}
 
+Torus:
 Fail on big braid

### 2014-11-05 fibonacci.tex
new version

%\documentclass[12pt,a4]{revtex4}
%\documentclass[12pt]{article}
%\documentclass[11pt, twocolumn]{article}
\documentclass[12pt,notitlepage,aps,pra,longbibliography,nofootinbib,tightenlines,superscriptaddress]{revtex4}

%\usepackage{epsf}
\usepackage{amsmath}
\usepackage{color}

%\documentclass[12pt,a4]{revtex4}
%\documentclass[12pt]{article}
%\documentclass[11pt, twocolumn]{article}

%\usepackage{epsf}
\usepackage{amsmath}
\usepackage{color}
\usepackage{natbib}
\usepackage{wrapfig}
%\usepackage{cite}

\RequirePackage{amsmath}
\RequirePackage{amssymb}
\RequirePackage{amsthm}
%\RequirePackage{algorithmic}
%\RequirePackage{algorithm}
%\RequirePackage{theorem}
%\RequirePackage{eucal}
\RequirePackage{color}
\RequirePackage{url}
\RequirePackage{mdwlist}

\RequirePackage[all]{xy}
\CompileMatrices
\RequirePackage{hyperref}
\RequirePackage{graphicx}
%\RequirePackage[dvips]{geometry}

\def\Xcite#1{}

\def\heading #1{\vskip 20pt \noindent\underline{\large \bf #1}\vskip 5pt}

\def\important #1{\underline{\bf #1}}

\begin{document}

\title{Error Correction in a Fibonacci Anyon Code}

%\author{Simon Burton, Courtney G. Brell, Steven T. Flammia}
%\affiliation{Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}

\author{Simon Burton}
\affiliation{Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}
\author{Courtney G.\ Brell}
\affiliation{Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}
\affiliation{Institut f\"ur Theoretische Physik, Leibniz Universit\"at Hannover, Appelstra\ss e 2, 30167 Hannover, Germany}
\author{Steven T.\ Flammia}
\affiliation{Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}

%\begin{abstract}
%We consider two dimensional
%systems that support Fibonacci
%anyon excitations.
%These are phenomenological models in that
%we ignore microscopic structure such as
%any underlying spin model.
%In our system the vacuum state of a torus
%is two-fold degenerate and we use this as a
%one qubit code.
%The error model consists of iid pair-creation
%processes for some varying amount of time.
%Error correction proceeds by first measuring
%a syndrome: this is the total charge in each
%tile of some tiling of the surface.
%The (classical) error correction algorithm
%performs repeated hierarchical clustering (fusing) of anyons,
%until there are no more charges remaining.
%This fails (destroys the encoded state)
%exactly when a topologically non-trivial operation occurs.
%Note that the error correction algorithm runs in polynomial time,
%but the simulation of the anyon system naively takes exponential
%time (and memory.) Here we find that a divide and conquer approach,
%as well as heuristics to minimise braid operations, allow
%simulation of systems to a reasonably large size (128x128 tiles),
%and we observe an error correction threshold of around $12.5\%$.
%\end{abstract}

\maketitle

%\heading{Introduction}

\important{Introduction.}
Topologically ordered systems in two dimensions are of great interest  
for quantum information processing and storage. These systems can be  
realized as ground states of local Hamiltonians and have natural  
robustness to local Hamiltonian perturbations~\cite{Bravyi2010,  
Bravyi2011a, Michalakis2013}. Furthermore, these systems typically  
have anyonic excitations~\cite{Wilczek1990, Kitaev2006} that may be  
used to realize fault-tolerant quantum computation by braiding of  
these particles~\cite{Kitaev2003, Nayak2008}. Different topologically  
ordered systems have different anyonic excitations, but only anyon  
models with sufficient complexity can be used to perform universal  
quantum computation in this way.

The Fibonacci anyon model is one of the simplest abstract anyon models  
to describe, having only one non-trivial particle type. Nonetheless,  
it allows for universal quantum computation by braiding~\cite{Freedman2002} and so  
is of great theoretical interest. Furthermore, the Fibonacci anyons  
are experimentally motivated as the expected excitations of the  
$\nu=\frac{12}{5}$ fractional quantum Hall states~\cite{Slingerland2001}, and can  
also be realized in several spin models~\cite{Levin2005, Palumbo2013, Kapit2013}.

Any scheme using anyon braiding to perform quantum computation will  
periodically require some form of active error correction to remove  
spurious thermal excitations. Left unchecked, the computation will  
quickly be spoiled at finite temperature. Such error-correction  
schemes have been well-developed for the simple class of abelian anyon  
models~\cite{Dennis2002,Duclos-Cianci2010a,Bravyi2011}, where only trivial computation can be performed by  
braiding.
Recently, the first error-correction schemes for non-abelian  
anyon models were proposed and demonstrated~\cite{Wootton2013, Brell2013}.
These schemes  
were developed for particular anyon models that cannot be used for  
universal quantum computation by braiding of anyons alone. This lack  
of computational power was in fact a motivating feature of the study  
of these models, as the anyon dynamics can be efficiently simulated on  
a classical computer.
By contrast, the fact that the Fibonacci anyons  
can realize universal quantum computation makes the direct  
simulation of these anyons on a classical computer decidedly  
inefficient.

%In this work we focus on demonstrating one of the main claims
%of topological quantum computing:
%that the effects of local noise
%can be overcome using error correction techniques.
In this work we use monte-carlo simulations of a 
phenomenological model.
This ignores any microscopic structure such as
an underlying lattice of spins.
The two dimensional manifold of our model has the global 
geometry of a torus which supports a two-fold degenerate
vacuum state.
This space is the codespace.
The noise model consists of iid pair-creation
events for some varying amount of time.
Error correction proceeds by first measuring
a syndrome: this is the total charge in each
tile of some tiling of the surface.
The (classical) error correction algorithm
performs repeated hierarchical clustering (fusing) of anyons,
until there are no more charges remaining.
This fails, destroying the encoded state,
exactly when a topologically non-trivial operation occurs.
Note that the error correction algorithm runs in polynomial time,
but the simulation of the anyon system naively takes exponential
time and memory.
Here we find that a divide and conquer approach,
as well as heuristics to minimise braid operations, allow
simulation of systems to a reasonably large size (128x128 tiles),
and we observe an error correction threshold of around $12.5\%$.

\important{Simulation.}
Unlike Ising anyon systems \cite{Brell2013},
Fibonacci anyon dynamics are known to be sufficient
for quantum computing \cite{Freedman2002}.
In particular, the dimension of the Hilbert
space associated with $n$ anyons
grows like $d^n$ where $d$ is the quantum
dimension of the anyons, in this case $d\simeq 1.6.$
Furthermore, the action of braiding Fibonacci 
anyons generates a dense
set of unitaries on this space (for $n>2$).
Therefore, at first sight it would appear that
we should not expect to be able to simulate
something as complicated as a decoding threshold.
However, we benefit from the following 
good fortune:

{\it (1)} below (bond) percolation threshold, we
expect the system to decompose into 
separate clusters of average size
$O(log(n))$ and variance $O(1)$, \cite{Bazant2000}.
Taking advantage of this, the simulation
proceeds by maintaining a set of disjoint
sub-systems. In other words: it is a (tensor) product
state, so we compute with each factor
separately.

{\it (2)} 
even though the act of error correction ({\it decoding})
joins these clusters together, every fusion also
decreases the number of anyons present. Moreover,
the goal of the error correction algorithm is to do this as
much as possible.

%\heading{Simulation}

We cover the surface of the torus with LxL disjoint squares.
These {\it tiles} are the regions over which
charge measurements occur, in order to
produce a syndrome for the decoder.

In order to keep track of the observables of the
system we maintain a set of disjoint {\it curves}.
These curves can also be thought of as a top-down
view of the fusion tree. In general, this winds around
the two dimensional tiles in a haphazard way determined by the
progress of the simulation.
For comparison,
previous work used a single fixed Z-shaped curve (row-major ordering)
\cite{Brell2013}.

%\begin{wrapfigure}{l}{0.26\textwidth}
%\includegraphics[width=0.26\textwidth]{pair-create.pdf}
%\end{wrapfigure}

\begin{center}
(i)
\includegraphics[width=0.26\textwidth]{pair-create.pdf}
\hskip 10pt
(ii)
\includegraphics[width=0.26\textwidth]{syndrome-1.pdf}
\hskip 10pt
(iii)
\includegraphics[width=0.26\textwidth]{syndrome-2.pdf}
\end{center}

Each round of simulation proceeds in four steps as follows:

(i) The noise process is modeled by
a sequence of pair-creation events distributed as
a Poisson process across each edge.

(ii) We first
join curves that participate in the same tile
in order to,

(iii) measure the charge on each tile.
Any resulting anyon is left somewhere in the tile.

(iv) The decoder examines this syndrome and clusters
nearby anyons. Each cluster is then measured (fused),
%and then we repeat this step clustering on a larger length
%scale.
and the decoder continues to cluster and fuse on larger scales until
there are no more anyons, or a non-trivial operation has occurred.
The non-trivial operations are those that involve a path that wraps
around the torus. All of these alter the encoded
state, and so in this case we abandon the
simulation round and declare failure to error correct.
This decoding algorithm is based on the clustering ``RG''
algorithm~\cite{Bravyi2011}.

\newpage

\important{Numerical Results}
We plot the performance of the decoder as a function
of error rate for varying lattice sizes.
The error rate is parameterized by the Poisson process duration $t_{\mathrm{sim}}$.
There is clear evidence of a decoding threshold below
which decoding succeeds with asymptotic certainty as the
system size increases.
This threshold is at $t_{\mathrm{sim}}\simeq 0.125 \pm 0.003.$

\begin{center}\includegraphics[width=0.6\textwidth]{anyons-kyle.pdf}\end{center}

\bibliography{refs2}{}
\bibliographystyle{abbrv}

\end{document}

### 2014-11-22 fib2.tex
new paper version fib2.tex structural changes, most non-introductory content from fibonacci.tex merged in.

% This line sets the project root file.
% 
% !TEX root = fib2.tex
% 
%------------------------------------------------------------------------------------------------------------%
\documentclass[a4paper,nofootinbib,superscriptaddress]{revtex4}

% Packages, Macros, Layout, Environments, etc.
\input{macros}
%------------------------------------------------------------------------------------------------------------%
\begin{document}

\title{Classical simulation of error correction in a Fibonacci anyon code}

\author{Simon Burton}
\affiliation{Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}
\author{Courtney G.\ Brell}
\affiliation{Institut f\"ur Theoretische Physik, Leibniz Universit\"at Hannover, Appelstra\ss e 2, 30167 Hannover, Germany}
\author{Steven T.\ Flammia}
\affiliation{Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}

\date{\today}

\begin{abstract}
We study two dimensional systems that support Fibonacci anyon excitations. In general, the braiding of Fibonacci anyons is sufficient for universal quantum computation, and so the classical simulation of their dynamics is likely to be hard. However, we show that for typical processes of interest for the study of successful error-correction in anyon systems, the relevant dynamics are in fact efficiently classically simulable, and make use of this fact to demonstrate the success of an error-correction protocol for a Fibonacci anyon computer. \cggb{Is this claim too bold?} We numerically simulate a phenomenological model of the system and noise processes on lattice sizes up to $128\times128$ sites, and demonstrate an error-correction threshold of around $0.125$ - comparable to those previously known for abelian and (non-universal) non-abelian anyon models.
\end{abstract}

\maketitle

%\vspace{-1.5cm}
% new page after abstract & TOC
%\clearpage
%\tableofcontents
%\clearpage

%------------------------------------------------------------------------------------------------------------%

%\layout % check the layout

\section{Introduction}

	\cggb{Put introduction back in.}

%------------------------------------------------------------------------------------------------------------%

\section{Modelling Fibonacci anyons}\label{s:model}

	A physical anyon model is abstractly described by a unitary modular tensor category~\cite{?}. This object contains the data describing the types of anyonic particles, as well as the results of topological operations such as braiding or fusion of these anyons. The Fibonacci anyon model consists of only one non-trivial particle type, conventionally called $\tau$. Denoting the vacuum by $\mathbb{I}$, we can describe the possible fusion outcomes of Fibonacci anyons as $\tau\times\tau=\mathbb{I}+\tau$, i.e.~two $\tau$ particles may either fuse to vacuum or to a $\tau$ particle.

	We can associate a Hilbert space with the fusion outcomes of a fixed number of $\tau$ particles, and for $n$ particles of type $\tau$, the dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ the golden ratio. Additionally, there is a global degeneracy associated with the topology of the manifold on which the anyons reside. We will consider systems with the topology of a torus, which for the Fibonacci anyons gives rise an extra 2-fold degeneracy. For convenience (in particular to minimize finite-size effects in our numerical computations), this global space is the one in which we will encode, and demonstrate protection of, quantum information.

	The fusion outcome of any particular experiment depends on the history of the particles, in particular how they have braided around one another. For this reason braiding operations are considered to act unitarily on the fusion space. Pair-creation events should be considered isometries that enlarge the fusion space, while fusion events correspond to projective measurements of combined charge of some number of particles. For details of the description of these processes in Fibonacci anyons, see Ref.~\cite{?}.

	We use a phenomenological model of Fibonacci anyon dynamics which neglects any microscopic details of the system. This is consistent with the principles of topologically ordered systems and anyonic physics, where the key universal features describing the anyon model correspond to large length-scale physics, while the microscopic physics play a less important and non-universal role. As such, we model the system simply as a square lattice of sites on which sets of anyons may reside. Allowed anyon dynamics are considered to be local on this lattice, which we take to have periodic boundary conditions. For more details of an analogous model, see~\cite{Brell2013}.

	Unlike the Ising anyon systems simulated in Ref.~\cite{Brell2013}, or the $\Phi-\Lambda$ models studied in Refs.~\cite{Wootton2013,Hutter2014}, Fibonacci anyon dynamics are known to be sufficient for universal quantum computation \cite{Freedman2002}. This is because the action of braiding Fibonacci anyons generates a dense set of unitaries on the fusion space (for $n>2$ particles). For this reason, the classsical simulation of such dynamics is expected to be hard in general. As such, it might be expected that the simulation of noise processes and error-correction routines in Fibonacci anyon systems is prohibitively time-consuming. However, we show in \Sref{s:sim} that typical noise processes and error-correction operations may in fact be efficiently simulated on a classical computer in precisely the regimes where we expect error-correction to succeed.

%------------------------------------------------------------------------------------------------------------%

\section{Noise and error-correction}\label{s:noise}

	The main noise processes we consider are pair-creation events, in which a pair of $\tau$ anyons are created from vacuum on two neighbouring sites.

	\cggb{Details. Consider merging parts of this section with parts of \Sref{s:simalg}.}

	\subsection{Logical errors}

		\cggb{Logical operators}

	\subsection{Decoding algorithm}

		\cggb{Describe decoding.}

		\cggb{How does this relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?}

%------------------------------------------------------------------------------------------------------------%

\section{Simulation}\label{s:sim}

	Although simulation of general processes involving $n$ Fibonacci anyons is BQP-complete (and thus unlikely to be classically tractable), noise and error-correction procedures have structure that we can exploit to efficiently simulate typical processes of interest. In particular, those processes in which we expect error-correction to succeed are also those that we expect to be able to efficiently simulate for the following reasons.

	Below the (bond) percolation threshold, we expect random sets of bonds to decompose into separate clusters of average size $O(log(n))$ and variance $O(1)$, \cite{Bazant2000}. In our context, the random bonds correspond to noise processes, and so separate clusters correspond to sets of anyons that could not have interacted at any point in their history. As such, we can simulate the braiding processes of each cluster separately. In other words: it is a (tensor) product state, so we compute with each factor separately. Since each cluster has only size $O(log(n))$, we may typically simulate these dynamics efficiently.

	However, random noise processes are not the only dynamics that we need consider. We must also consider the effect of the error-correction routine itself. This acts iteratively to fuse particles on increasing length scales. While this kind of fusion would typically merge clusters, forcing us to compute dynamics of larger and larger sets of anyons, at each length scale the total number of anyons present is dramatically reduced. Indeed, the goal of the error correction algorithm is to reduce the number of anyons as much as possible.

	\cggb{Can we make a concrete claim about the maximum size of clusters at each stage of the decoding procedure? Do we know anything about the distribution of separations between clusters in the sub-critical percolation regime?}

	Of course, if we were to consider noise so strong that the clusters percolate over the lattice, we would no longer be able to efficiently simulate the system. However, recall that logical errors in our system correspond to processes that act over a non-trivial loop of the torus. If the noise operations are so common to have percolated, this is an example of a situation where we expect error-correction \emph{not} to succeed. Similarly, if the noise has not yet percolated by itself, but the clusters are merged into a large (percolated) cluster by the decoding algorithm, this is again an example of a process that we expect to correspond to a failure of error-correction. So we see that the events that we are able to efficiently simulate correspond precisely to those for which we expect error-correction to succeed. We may simply declare failure on non-simulable events. This allows us to simulate and demonstrate the success of error-correction schemes for Fibonacci anyons, without explicitly simulating the failure of such schemes.

	\subsection{Simulation algorithm}\label{s:simalg}

		We cover the surface of the torus with LxL disjoint squares. These {\it tiles} are the regions over which
charge measurements occur, in order to produce a syndrome for the decoder.

		In order to keep track of the observables of the system we maintain a set of disjoint {\it curves}. These curves can also be thought of as a top-down view of the fusion tree. In general, this winds around the two dimensional tiles in a haphazard way determined by the progress of the simulation. For comparison, previous work used a single fixed Z-shaped curve (row-major ordering) \cite{Brell2013}.

		\begin{center}
		(i)
		\includegraphics[width=0.26\textwidth]{pair-create.pdf}
		\hskip 10pt
		(ii)
		\includegraphics[width=0.26\textwidth]{syndrome-1.pdf}
		\hskip 10pt
		(iii)
		\includegraphics[width=0.26\textwidth]{syndrome-2.pdf}
		\end{center}

		Each round of simulation proceeds in four steps as follows:

		\begin{enumerate}
			\item The noise process is modelled by a sequence of pair-creation events distributed as a Poisson process across each edge.
			\item We first join curves that participate in the same tile in order to,
			\item measure the charge on each tile. Any resulting anyon is left somewhere in the tile.
			\item The decoder examines this syndrome and clusters nearby anyons. Each cluster is then measured (fused), and the decoder continues to cluster and fuse on larger scales until there are no more anyons, or a non-trivial operation has occurred. The non-trivial operations are those that involve a path that wraps around the torus. All of these alter the encoded state, and so in this case we abandon the simulation round and declare failure to error correct. This decoding algorithm is based on the clustering ``RG'' algorithm~\cite{Bravyi2011}.
		\end{enumerate}

%------------------------------------------------------------------------------------------------------------%

\section{Numerical results}

	We plot the performance of the decoder as a function of error rate for varying lattice sizes. The error rate is parameterized by the Poisson process duration $t_{\mathrm{sim}}$. There is clear evidence of a decoding threshold below
which decoding succeeds with asymptotic certainty as the system size increases. This threshold is at $t_{\mathrm{sim}}\simeq 0.125 \pm 0.003.$

	\begin{center}\includegraphics[width=0.6\textwidth]{anyons-kyle.pdf}\end{center}

	\cggb{Define $t_{\mathrm{sim}}$.}

	\cggb{Comment on the effect of declaring failure on some simulations on this plot. Would we expect it to change if we simulated every event completely? If so, how?}

%------------------------------------------------------------------------------------------------------------%

\section{Discussion}

	\cggb{Comment on choice of encoding, and applicability of our simulation techniques to simulation of fusion encodings as in Fibonacci anyon computing schemes.}

	\cggb{Comment on choice of decoder, noise scheme, etc., particularly noting that the qualitative details are unlikely to be affected by these choices~\cite{Brell2013}.}

	\cggb{Comment on the fact that these methods are not restricted to Fibonacci anyons, and could be used to demonstrate the success of error-correction protocols on arbitrary anyon models.}

	\cggb{Comment on applicability of our simulation techniques to non-phenomenological models. Is it possible that the same ideas could be useful when there is more microscopic detail available, or are they restricted to exactly our phenomenological setup?}

	\cggb{Do we have much more to say?}

%------------------------------------------------------------------------------------------------------------%
\bibliographystyle{bibstyle}
\bibliography{refs2}

\end{document}

### 2014-12-03 fib2.tex
Touched up the abstract a bit.

@@
 %------------------------------------------------------------------------------------------------------------%
-\documentclass[a4paper,nofootinbib,superscriptaddress]{revtex4}
+\documentclass[aps, pra, a4paper, 11pt, nofootinbib, superscriptaddress, tightenlines, 
+notitlepage, longbibliography]{revtex4}
 
@@
 \author{Simon Burton}
-\affiliation{Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}
+\affiliation{Centre for Engineered Quantum Systems, School of Physics, 
+The University of Sydney, Sydney, Australia}
 \author{Courtney G.\ Brell}
-\affiliation{Institut f\"ur Theoretische Physik, Leibniz Universit\"at Hannover, Appelstra\ss e 2, 30167 Hannover, Germany}
+\affiliation{Institut f\"{u}r Theoretische Physik, Leibniz Universit\"{a}t Hannover, 
+Appelstra\ss{}e 2, 30167 Hannover, Germany}
 \author{Steven T.\ Flammia}
-\affiliation{Centre for Engineered Quantum Systems, School of Physics, The University of Sydney, Sydney, Australia}
+\affiliation{Centre for Engineered Quantum Systems, School of Physics, 
+The University of Sydney, Sydney, Australia}
 
@@
 \begin{abstract}
-We study two dimensional systems that support Fibonacci anyon excitations.
-In general, the braiding of Fibonacci anyons is sufficient for universal quantum computation, and so the classical simulation of their dynamics is likely to be hard.
-However, we show that for typical processes of interest for the study of successful error-correction in anyon systems, the relevant dynamics are in fact efficiently classically simulable, and make use of this fact to demonstrate the success of an error-correction protocol for a Fibonacci anyon computer.
-\cggb{Is this claim too bold?} We numerically simulate a phenomenological model of the system and noise processes on lattice sizes up to $128\times128$ sites, and demonstrate an error-correction threshold of around $0.125$ - comparable to those previously known for abelian and (non-universal) non-abelian anyon models.
+We study two-dimensional systems that support Fibonacci anyon excitations. In general, the 
+braiding of Fibonacci anyons is sufficient for universal quantum computation, and so the 
+classical simulation of their dynamics is likely to be hard. However, we show that for typical 
+processes of interest for the study of quantum error correction in anyon systems the 
+relevant dynamics can in fact be efficiently simulated classically for a wide range of system 
+parameters. We make use of this fact to demonstrate the success of an error-correction 
+protocol for a Fibonacci anyon quantum memory below a particular noise threshold. We 
+numerically simulate a phenomenological model of the system and noise processes on lattice 
+sizes of up to $128\times128$ sites, and demonstrate an error-correction threshold of around 
+$12.5\%$, a number that is comparable to those previously known for abelian and 
+(non-universal) non-abelian anyon models.
 \end{abstract}
@@
 \maketitle
-
-%\vspace{-1.5cm}
-% new page after abstract & TOC
-%\clearpage
-%\tableofcontents
-%\clearpage
 

### 2014-12-03 fib2.tex
changed style to PRL and started intro. Added our Ising paper intro just to have the references handy.

@@
 %------------------------------------------------------------------------------------------------------------%
-\documentclass[aps, pra, a4paper, 11pt, nofootinbib, superscriptaddress, tightenlines, 
-notitlepage, longbibliography]{revtex4}
+% if we want to consider a PRL-style version, use these settings
+\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage]{revtex4-1}
+\usepackage{times}
+
+% use these settings for a more reader-friendly version
+%\documentclass[aps, pra, a4paper, 11pt, onecolumn, nofootinbib, superscriptaddress, tightenlines, notitlepage, longbibliography]{revtex4-1}
 
@@
 
-\title{Classical simulation of error correction in a Fibonacci anyon code}
+\title{Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code}
 
@@
 \begin{abstract}
-We study two-dimensional systems that support Fibonacci anyon excitations. In general, the 
-braiding of Fibonacci anyons is sufficient for universal quantum computation, and so the 
-classical simulation of their dynamics is likely to be hard. However, we show that for typical 
-processes of interest for the study of quantum error correction in anyon systems the 
-relevant dynamics can in fact be efficiently simulated classically for a wide range of system 
-parameters. We make use of this fact to demonstrate the success of an error-correction 
-protocol for a Fibonacci anyon quantum memory below a particular noise threshold. We 
-numerically simulate a phenomenological model of the system and noise processes on lattice 
-sizes of up to $128\times128$ sites, and demonstrate an error-correction threshold of around 
-$12.5\%$, a number that is comparable to those previously known for abelian and 
-(non-universal) non-abelian anyon models.
+Simulating the dynamics of excitations in two-dimensional quantum systems that support 
+anyons is intractable in general because it is sufficient for universal quantum computation. 
+Here we show that for typical processes of interest for the study of quantum error correction 
+in anyon systems, the relevant dynamics can in fact be efficiently simulated classically for a 
+wide range of system parameters, even when the underlying anyon model is universal. We 
+make use of this fact to demonstrate the success of an error-correction protocol for a 
+Fibonacci anyon quantum memory. We numerically simulate a phenomenological model of 
+the system and noise processes on lattice sizes of up to $128\times128$ sites, and 
+demonstrate an error-correction threshold of around $12.5\%$, a number that is comparable 
+to those previously known for abelian and (non-universal) non-abelian anyon models.
 \end{abstract}
@@
 
-%\layout % check the layout
+%\section{Introduction}
 
-\section{Introduction}
+Anyonic excitations in two-dimensional quantum systems offer tremendous promise for long-term storage and processing of quantum information~\cite{Kitaev2003}.
+The topological features of quantum systems that support such excitations are insensitive to local perturbations~\cite{Bravyi2010, *Bravyi2011a, *Michalakis2013}, and the excitations themselves can in general be used to perform universal quantum computation~\cite{Freedman2002, *Freedman2002b}.
 
-	\cggb{Put introduction back in.}
+This remarkable power becomes a liability when we seek to simulate these systems on classical computers.
+
+One of the most interesting features of two-dimensional quantum systems with anyonic excitations~\cite{Wilczek1990} is their application to quantum information science, where the topological nature of the anyons offers some intrinsic protection of quantum coherence~\cite{Kitaev2003}.
+These topologically ordered systems are insensitive to local perturbations~\cite{Bravyi2010, *Bravyi2011a, *Michalakis2013}, have a ground-space degeneracy that is a function of the topology of the system~\cite{Wen1990, Einarsson1995} and can realize quantum gates by braiding anyons, which are naturally robust to error due to their topological nature~\cite{Kitaev2003, Nayak2008}.
+Many common anyon models such as the toric code~\cite{Kitaev2003} and the color codes~\cite{Bombin2006} have an Abelian structure that simplifies their analysis greatly.
+However, Abelian anyon models are very restricted when compared to the general class of anyonic systems.
+Notably, Abelian anyons lack the capacity to perform quantum computation by braiding of anyons alone.
+By contrast, non-Abelian anyon systems have excitations that can be used to implement topological quantum computation~\cite{Freedman2002, Freedman2002b}, and so they are of interest for quantum information processing schemes as well as quantum error correction.
+It is also known that the dynamics of Abelian anyons can significantly differ from those of non-Abelian anyons in some circumstances~\cite{Brennen2010, Lehman2011, Lehman2012, Zatloukal2012}.
+
+A particular class of non-Abelian anyonic excitations called \emph{Ising anyons} are thought to be among the most promising candidates for experimental realization of topological quantum computing.
+Ising anyons are experimentally motivated~\cite{Willett1987} as the expected excitations of the $\nu=\frac{5}{2}$ fractional quantum Hall states~\cite{Moore1991, Nayak1996}, and also appear as the excitations of several lattice models~\cite{Kitaev2006, Levin2005a, Kapit2013, Palumbo2014}.
+In particular, Ising anyons can robustly perform Clifford gates via braiding and have a high noise threshold for universal quantum computation when coupled with magic state distillation~\cite{Bravyi2006b, Freedman2006}.
+
+These general features of anyon models, and of Ising anyons in particular, have attracted a lot of attention during the past decade.
+This picture of an intrinsically robust topological quantum computer is spoiled at finite temperature, however.
+Indeed, if left unattended, thermal excitations diffusing in the system can corrupt the quantum information stored in the ground space.
+While these excitations are suppressed by a mass gap (ideally) much larger than the temperature, they nonetheless appear in a finite density at any non-zero temperature, and for scalability issues it is essential to devise a scheme that can cope with their existence.
+One approach is to engineer a mass gap that grows with the system size, leading to a self-correcting behavior of the memory.
+However, there is accumulating evidence that this cannot be realized in two spatial dimensions~\cite{Bravyi2009, Bravyi2010a, Haah2012a, Landon-Cardinal2012a}.
+Additionally, even a self-correcting system in contact with a thermal bath will accumulate a finite density of excitations over time, and it is not clear that the quantum information stored in the ground state can be manipulated or readout without first cooling back to the correct ground state~\cite{Pastawski2010}.
+
+Here we pursue a different approach that can be seen as a viable alternative to self-correction as well as a reliable method for readout of noisy stored quantum information.
+It consists of actively monitoring the presence of thermal anyons and correcting the unwanted operations resulting from their presence in the system.
+The Ising anyon model is an obvious candidate to benchmark such a proposal because it is numerically tractable via a mapping to free Majorana fermions~\cite{Bravyi2006b}.
+
+The motivation behind our work stems from two distinct potential applications.
+On the one hand, as outlined above, anyons can arise as localized gapped excitations in two-dimensional systems, e.g.,~\cite{Moore1991, Nayak1996}.
+In this setting, our method is needed to eliminate thermal defects in the systems without spoiling the topologically encoded information.
+On the other hand, our results can also be understood from a purely coding-theoretic perspective.
+Some topologically ordered systems can arise in lattice models with local commuting Hamiltonians~\cite{Kitaev2003, Levin2005a, Koenig2010b}.
+The local terms of the Hamiltonian can be thought of as check operators defining a \emph{local commuting projector code}, a class of codes going beyond the usual stabilizer formalism that has been the object of recent study~\cite{Bravyi2009, Bravyi2010a, Haah2012a, Landon-Cardinal2012a}.
+Such codes allow for the implementation of quantum error-correction schemes in a geometrically local setting~\cite{Kitaev2003, Dennis2002}.
+The local check operators can be measured using standard circuitry~\cite{Bonesteel2012} on an ordinary, circuit-model quantum computer.
+Thus, this second scenario we consider is not contingent on the existence of physical systems that naturally present topological quantum order; it could in principle be used in any quantum computing architecture with nearest-neighbor interactions on a two-dimensional lattice.
+In this setting, our results provide an efficient decoding algorithm for the corresponding quantum error-correcting code.
+To our knowledge, this provides the first efficient decoding schemes for a family of non-additive quantum codes, i.e.\ codes without explicit Pauli-matrix tensor product structure.
+
+\stf{Summary of main results} We begin by proposing a phenomenological model of dynamics in an Ising anyon system and several noise models.
+Importantly, these models encompass all of the major physical error processes associated to non-Abelian anyons, including pair-creation, hopping, braiding, and fusion of anyons.
+We define two distinct families of noise models, following the two physical applications of our method described in the previous paragraph.
+To simulate the noise affecting a topologically-ordered system at finite temperature, we use a Metropolis procedure to choose among the possible physical error processes.
+Because the Gibbs thermal equilibrium state is the fixed point of this local noise process, we believe that it captures the essential properties of a real thermalization process.
+To simulate the noise affecting a quantum computer that uses an Ising error-correcting code, we use a more generic ``white noise" model where each type of physical error process occurs at a predetermined fixed rate.
+This model is in essence an infinite temperature limit of the previous noise model, and so it probably also accurately captures the short-time dynamics of a topologically-ordered system at finite temperature.
+Note that we do not necessarily expect the physical noise occurring in a circuit-based quantum computer to be described by these physical processes.
+Nonetheless, in absence of detailed microscopic descriptions of the device, they provide a good starting point to benchmark the code (in the same sense that Pauli errors are used to benchmark stabilizer codes).
+
+We explore the effect of these noise channels on two different encoding schemes (degenerate ground spaces).
+The first encoding we examine stores the information in the degenerate ground space of a system with Ising anyonic excitations embedded in a torus while the second stores information in a degenerate space associated with the fusion space of several well-separated Ising anyons.
+Both of these encodings lend themselves equally well to the two physical scenarios described above (although embedding an actual topologically ordered system on a torus probably poses an additional challenge).
+These two encodings are motivated by topological quantum memories \cite{Dennis2002} and topological quantum computing \cite{Bravyi2006b,BR07a} schemes respectively.
+
+Following this, we adapt existing techniques from topological quantum error correction to the non-Abelian setting.
+The non-Abelian nature of the model significantly changes the decoding problem and presents a main challenge of our study.
+In an Abelian model, decoding is realized by grouping nearby excitations that fuse to the vacuum.
+In contrast, for a non-Abelian model, it is not possible to predict with certainty the outcome of a fusion process.
+Thus, decoding needs to be an \emph{iterative} process: in a first round particles are grouped in a certain way; if all groups do not fuse to the vacuum, then a second round groups the remaining particles, and so on.
+In particular, we adapt the clustering renormalization group decoder of Bravyi and Haah~\cite{Bravyi2011} and the perfect matching algorithm decoders~\cite{Dennis2002, Wang2010} to our non-Abelian topological codes to determine their error-correction thresholds and memory lifetimes under various noise channels.
+Our decoders provably run in polynomial time in the size of the lattice.
+
+Using these decoders, we explicitly calculate numerical error-correction threshold estimates for these codes and for various noise regimes, including those where hopping and braiding of anyons dominates pair-creation.
+Our results seem to indicate that the perfect matching decoder outperforms the clustering decoder, and that the thresholds are broadly comparable for both types of codes, and for various types of noise.
+We find numerical threshold estimates that vary between 13\% and 25\%, where the percentages are in terms of a total noise rate density which we define and discuss in detail in Sections~\ref{S:phenom} and~\ref{S:numerics}.
+
+These thresholds are obtained by large-scale two-dimensional simulations of the dynamics of a dense ``gas'' of non-abelian anyons on lattice sizes of up to $48 \times 48$ nodes.
+All previous results have focused on quasi-one-dimensional models or single-particle quantum walks~\cite{Brennen2010, Lehman2011, Lehman2012, Zatloukal2012}.\stf{end copy \& paste from Ising.}
 
@@
 
-	Unlike the Ising anyon systems simulated in Ref.~\cite{Brell2013}, or the $\Phi-\Lambda$ models studied in Refs.~\cite{Wootton2013,Hutter2014}, Fibonacci anyon dynamics are known to be sufficient for universal quantum computation \cite{Freedman2002}.
+	Unlike the Ising anyon systems simulated in Ref.~\cite{Brell2013}, or the $\Phi-\Lambda$ models studied in Refs.~\cite{Wootton2013, Hutter2014}, Fibonacci anyon dynamics are known to be sufficient for universal quantum computation~\cite{Freedman2002}.
 This is because the action of braiding Fibonacci anyons generates a dense set of unitaries on the fusion space (for $n>2$ particles).
@@
 
-	\begin{center}\includegraphics[width=0.6\textwidth]{anyons-kyle.pdf}\end{center}
+	\begin{center}\includegraphics[width=\columnwidth]{anyons-kyle.pdf}\end{center}
 
@@
 %------------------------------------------------------------------------------------------------------------%
-\bibliographystyle{bibstyle}
+%\bibliographystyle{bibstyle}
 \bibliography{refs2}

### 2014-12-04 fib2.tex
Added an introduction and cleaned up a couple of references.

@@
 \input{macros}
+
+% use this for multiline block comments: \/* commented text here */
+\long\def\/*#1*/{}
+%\long\def\/*#1*/{#1} % uncomment this line to load the block comments
+
 %------------------------------------------------------------------------------------------------------------%
@@
 
-%\section{Introduction}
-
-Anyonic excitations in two-dimensional quantum systems offer tremendous promise for long-term storage and processing of quantum information~\cite{Kitaev2003}.
+Anyonic excitations in two-dimensional quantum systems~\cite{Wilczek1990} offer tremendous promise for long-term storage and processing of quantum information~\cite{Kitaev2003}.
 The topological features of quantum systems that support such excitations are insensitive to local perturbations~\cite{Bravyi2010, *Bravyi2011a, *Michalakis2013}, and the excitations themselves can in general be used to perform universal quantum computation~\cite{Freedman2002, *Freedman2002b}.
 
-This remarkable power becomes a liability when we seek to simulate these systems on classical computers.
+Quantum error correction is vital to harnessing the computational power of these topologically ordered systems.
+When coupled to a heat bath at any finite temperature, thermal fluctuations will create anyons that diffuse and quickly corrupt the stored quantum information~\cite{Pastawski2010}.
+Thus, the passive protection provided by the mass gap and low temperature must be augmented by an \emph{active} procedure.
 
+Almost all of the sizable research effort on active quantum error correction for topological systems has focused on the case of abelian anyons~\cite{Terhal2014}.
+These systems are well suited to studying quantum error correction because the dynamics of excitations in abelian anyon models can be simulated numerically very efficiently, allowing lattice simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}.
+The ability to efficiently simulate these systems is a consequence of the limitation that abelian anyons cannot be used for universal quantum computation.
+
+Recent investigations have begun to explore quantum error correction for nonabelian anyon models~\cite{Brell2013, Wootton2013, Hutter2014}.
+These models are particularly interesting because braiding and fusion of anyons in these models leads in general to universal quantum computation.
+However, the initial studies have focused on models such as Ising anyons~\cite{Brell2013} and the so-called $\Phi$-$\Lambda$ model~\cite{Wootton2013, Hutter2014} which, while nonabelian, are not universal, a fact that was exploited to enable efficient classical simulation of error correction in these systems.
+The remarkable computational power of universal anyon models becomes a liability when we seek to simulate these systems on classical computers.
+
+Here we consider a full simulation of quantum error correction in a two-dimensional lattice system with Fibonacci anyons, a class of nonabelian anyons that are universal for quantum computation~\cite{Wang2010b}.
+\stf{Describe main results and why they are bad ass.}
+
+\/* % begin comment block
+
+% This was copied from our Ising paper so that we would have some references
 One of the most interesting features of two-dimensional quantum systems with anyonic excitations~\cite{Wilczek1990} is their application to quantum information science, where the topological nature of the anyons offers some intrinsic protection of quantum coherence~\cite{Kitaev2003}.
@@
 All previous results have focused on quasi-one-dimensional models or single-particle quantum walks~\cite{Brennen2010, Lehman2011, Lehman2012, Zatloukal2012}.\stf{end copy \& paste from Ising.}
+*/ % end commented block
 
@@
 
-\section{Modelling Fibonacci anyons}\label{s:model}
+\paragraph{Modelling Fibonacci anyons.}\label{s:model}
 
-	A physical anyon model is abstractly described by a unitary modular tensor category~\cite{?}.
+	A physical anyon model is abstractly described by a unitary modular tensor category~\cite{Wang2010b}.
 This object contains the data describing the types of anyonic particles, as well as the results of topological operations such as braiding or fusion of these anyons.
@@
 Pair-creation events should be considered isometries that enlarge the fusion space, while fusion events correspond to projective measurements of combined charge of some number of particles.
-For details of the description of these processes in Fibonacci anyons, see Ref.~\cite{?}.
+For details of the description of these processes in Fibonacci anyons, see Ref.~\cite{Trebst2008}.
 
@@
 
-\section{Noise and error-correction}\label{s:noise}
+\paragraph{Noise and error-correction}\label{s:noise}
 
@@
 
-	\subsection{Logical errors}
+	\paragraph{Logical errors}
 
@@
 
-	\subsection{Decoding algorithm}
+	\paragraph{Decoding algorithm}
 
@@
 
-\section{Simulation}\label{s:sim}
+\paragraph{Simulation}\label{s:sim}
 
@@
 
-	\subsection{Simulation algorithm}\label{s:simalg}
+	\paragraph{Simulation algorithm}\label{s:simalg}
 
@@
 
-\section{Numerical results}
+\paragraph{Numerical results}
 
@@
 
-\section{Discussion}
+\paragraph{Discussion}
 

### 2014-12-04 fib2.tex
cleaned up line breaks and some references.

@@
 demonstrate an error-correction threshold of around $12.5\%$, a number that is comparable 
-to those previously known for abelian and (non-universal) non-abelian anyon models.
+to those previously known for abelian and (non-universal) nonabelian anyon models.
 \end{abstract}
@@
 
-Anyonic excitations in two-dimensional quantum systems~\cite{Wilczek1990} offer tremendous promise for long-term storage and processing of quantum information~\cite{Kitaev2003}.
-The topological features of quantum systems that support such excitations are insensitive to local perturbations~\cite{Bravyi2010, *Bravyi2011a, *Michalakis2013}, and the excitations themselves can in general be used to perform universal quantum computation~\cite{Freedman2002, *Freedman2002b}.
+Anyonic excitations in two-dimensional quantum systems~\cite{Wilczek1990} offer 
+tremendous promise for long-term storage and processing of quantum 
+information~\cite{Kitaev2003}. The topological features of quantum systems that support 
+such excitations are insensitive to local 
+perturbations~\cite{Bravyi2010, *Bravyi2011a, *Michalakis2013}, and the excitations 
+themselves can in general be used to perform universal quantum 
+computation~\cite{Freedman2002, *Freedman2002b}.
 
-Quantum error correction is vital to harnessing the computational power of these topologically ordered systems.
-When coupled to a heat bath at any finite temperature, thermal fluctuations will create anyons that diffuse and quickly corrupt the stored quantum information~\cite{Pastawski2010}.
-Thus, the passive protection provided by the mass gap and low temperature must be augmented by an \emph{active} procedure.
+Quantum error correction is vital to harnessing the computational power of these topologically 
+ordered systems. When coupled to a heat bath at any finite temperature, thermal fluctuations 
+will create anyons that diffuse and quickly corrupt the stored quantum 
+information~\cite{Pastawski2010}. Thus, the passive protection provided by the mass gap 
+and low temperature must be augmented by an \emph{active} procedure.
 
-Almost all of the sizable research effort on active quantum error correction for topological systems has focused on the case of abelian anyons~\cite{Terhal2014}.
-These systems are well suited to studying quantum error correction because the dynamics of excitations in abelian anyon models can be simulated numerically very efficiently, allowing lattice simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}.
-The ability to efficiently simulate these systems is a consequence of the limitation that abelian anyons cannot be used for universal quantum computation.
+Almost all of the sizable research effort on active quantum error correction for topological 
+systems has focused on the case of abelian anyons~\cite{Terhal2014}. These systems are 
+well suited to studying quantum error correction because the dynamics of excitations in 
+abelian anyon models can be simulated numerically very efficiently, allowing lattice 
+simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. The ability to 
+efficiently simulate these systems is a consequence of the limitation that abelian anyons 
+cannot be used for universal quantum computation.
 
-Recent investigations have begun to explore quantum error correction for nonabelian anyon models~\cite{Brell2013, Wootton2013, Hutter2014}.
-These models are particularly interesting because braiding and fusion of anyons in these models leads in general to universal quantum computation.
-However, the initial studies have focused on models such as Ising anyons~\cite{Brell2013} and the so-called $\Phi$-$\Lambda$ model~\cite{Wootton2013, Hutter2014} which, while nonabelian, are not universal, a fact that was exploited to enable efficient classical simulation of error correction in these systems.
-The remarkable computational power of universal anyon models becomes a liability when we seek to simulate these systems on classical computers.
+Recent investigations have begun to explore quantum error correction for nonabelian anyon 
+models~\cite{Brell2013, Wootton2013, Hutter2014}. These models are particularly interesting 
+because braiding and fusion of anyons in these models leads in general to universal quantum 
+computation. However, the initial studies have focused on models such as Ising 
+anyons~\cite{Brell2013} and the so-called $\Phi$-$\Lambda$ 
+model~\cite{Wootton2013, Hutter2014} which, while nonabelian, are not universal, a fact 
+that was exploited to enable efficient classical simulation of error correction in these systems. 
+The remarkable computational power of universal anyon models becomes a liability when we 
+seek to simulate these systems on classical computers.
 
-Here we consider a full simulation of quantum error correction in a two-dimensional lattice system with Fibonacci anyons, a class of nonabelian anyons that are universal for quantum computation~\cite{Wang2010b}.
+Here we consider a full simulation of quantum error correction in a two-dimensional lattice 
+system with Fibonacci anyons, a class of nonabelian anyons that are universal for quantum 
+computation~\cite{Wang2010b}. Fibonacci anyons are experimentally motivated as the 
+expected excitations of the $\nu=\frac{12}{5}$ fractional quantum Hall 
+states~\cite{Slingerland2001}, and can also be realized in several spin 
+models~\cite{Levin2005, Kapit2013, Palumbo2014}. 
 \stf{Describe main results and why they are bad ass.}

### 2014-12-08 fib2.tex
minor file clean up. removed a redundant paragraph.

@@
 anyons~\cite{Brell2013} and the so-called $\Phi$-$\Lambda$ 
-model~\cite{Wootton2013, Hutter2014} which, while nonabelian, are not universal, a fact 
+model~\cite{Wootton2013, Hutter2014} that, while nonabelian, are not universal, a fact 
 that was exploited to enable efficient classical simulation of error correction in these systems. 
@@
 models~\cite{Levin2005, Kapit2013, Palumbo2014}.
-\stf{Describe main results and why they are bad ass.}
 
-\/* % begin comment block
-
-% This was copied from our Ising paper so that we would have some references
-One of the most interesting features of two-dimensional quantum systems with anyonic excitations~\cite{Wilczek1990} is their application to quantum information science, where the topological nature of the anyons offers some intrinsic protection of quantum coherence~\cite{Kitaev2003}.
-These topologically ordered systems are insensitive to local perturbations~\cite{Bravyi2010, *Bravyi2011a, *Michalakis2013}, have a ground-space degeneracy that is a function of the topology of the system~\cite{Wen1990, Einarsson1995} and can realize quantum gates by braiding anyons, which are naturally robust to error due to their topological nature~\cite{Kitaev2003, Nayak2008}.
-Many common anyon models such as the toric code~\cite{Kitaev2003} and the color codes~\cite{Bombin2006} have an Abelian structure that simplifies their analysis greatly.
-However, Abelian anyon models are very restricted when compared to the general class of anyonic systems.
-Notably, Abelian anyons lack the capacity to perform quantum computation by braiding of anyons alone.
-By contrast, non-Abelian anyon systems have excitations that can be used to implement topological quantum computation~\cite{Freedman2002, Freedman2002b}, and so they are of interest for quantum information processing schemes as well as quantum error correction.
-It is also known that the dynamics of Abelian anyons can significantly differ from those of non-Abelian anyons in some circumstances~\cite{Brennen2010, Lehman2011, Lehman2012, Zatloukal2012}.
-
-A particular class of non-Abelian anyonic excitations called \emph{Ising anyons} are thought to be among the most promising candidates for experimental realization of topological quantum computing.
-Ising anyons are experimentally motivated~\cite{Willett1987} as the expected excitations of the $\nu=\frac{5}{2}$ fractional quantum Hall states~\cite{Moore1991, Nayak1996}, and also appear as the excitations of several lattice models~\cite{Kitaev2006, Levin2005a, Kapit2013, Palumbo2014}.
-In particular, Ising anyons can robustly perform Clifford gates via braiding and have a high noise threshold for universal quantum computation when coupled with magic state distillation~\cite{Bravyi2006b, Freedman2006}.
-
-These general features of anyon models, and of Ising anyons in particular, have attracted a lot of attention during the past decade.
-This picture of an intrinsically robust topological quantum computer is spoiled at finite temperature, however.
-Indeed, if left unattended, thermal excitations diffusing in the system can corrupt the quantum information stored in the ground space.
-While these excitations are suppressed by a mass gap (ideally) much larger than the temperature, they nonetheless appear in a finite density at any non-zero temperature, and for scalability issues it is essential to devise a scheme that can cope with their existence.
-One approach is to engineer a mass gap that grows with the system size, leading to a self-correcting behavior of the memory.
-However, there is accumulating evidence that this cannot be realized in two spatial dimensions~\cite{Bravyi2009, Bravyi2010a, Haah2012a, Landon-Cardinal2012a}.
-Additionally, even a self-correcting system in contact with a thermal bath will accumulate a finite density of excitations over time, and it is not clear that the quantum information stored in the ground state can be manipulated or readout without first cooling back to the correct ground state~\cite{Pastawski2010}.
-
-Here we pursue a different approach that can be seen as a viable alternative to self-correction as well as a reliable method for readout of noisy stored quantum information.
-It consists of actively monitoring the presence of thermal anyons and correcting the unwanted operations resulting from their presence in the system.
-The Ising anyon model is an obvious candidate to benchmark such a proposal because it is numerically tractable via a mapping to free Majorana fermions~\cite{Bravyi2006b}.
-
-The motivation behind our work stems from two distinct potential applications.
-On the one hand, as outlined above, anyons can arise as localized gapped excitations in two-dimensional systems, e.g.,~\cite{Moore1991, Nayak1996}.
-In this setting, our method is needed to eliminate thermal defects in the systems without spoiling the topologically encoded information.
-On the other hand, our results can also be understood from a purely coding-theoretic perspective.
-Some topologically ordered systems can arise in lattice models with local commuting Hamiltonians~\cite{Kitaev2003, Levin2005a, Koenig2010b}.
-The local terms of the Hamiltonian can be thought of as check operators defining a \emph{local commuting projector code}, a class of codes going beyond the usual stabilizer formalism that has been the object of recent study~\cite{Bravyi2009, Bravyi2010a, Haah2012a, Landon-Cardinal2012a}.
-Such codes allow for the implementation of quantum error-correction schemes in a geometrically local setting~\cite{Kitaev2003, Dennis2002}.
-The local check operators can be measured using standard circuitry~\cite{Bonesteel2012} on an ordinary, circuit-model quantum computer.
-Thus, this second scenario we consider is not contingent on the existence of physical systems that naturally present topological quantum order; it could in principle be used in any quantum computing architecture with nearest-neighbor interactions on a two-dimensional lattice.
-In this setting, our results provide an efficient decoding algorithm for the corresponding quantum error-correcting code.
-To our knowledge, this provides the first efficient decoding schemes for a family of non-additive quantum codes, i.e.\ codes without explicit Pauli-matrix tensor product structure.
-
-\stf{Summary of main results} We begin by proposing a phenomenological model of dynamics in an Ising anyon system and several noise models.
-Importantly, these models encompass all of the major physical error processes associated to non-Abelian anyons, including pair-creation, hopping, braiding, and fusion of anyons.
-We define two distinct families of noise models, following the two physical applications of our method described in the previous paragraph.
-To simulate the noise affecting a topologically-ordered system at finite temperature, we use a Metropolis procedure to choose among the possible physical error processes.
-Because the Gibbs thermal equilibrium state is the fixed point of this local noise process, we believe that it captures the essential properties of a real thermalization process.
-To simulate the noise affecting a quantum computer that uses an Ising error-correcting code, we use a more generic ``white noise" model where each type of physical error process occurs at a predetermined fixed rate.
-This model is in essence an infinite temperature limit of the previous noise model, and so it probably also accurately captures the short-time dynamics of a topologically-ordered system at finite temperature.
-Note that we do not necessarily expect the physical noise occurring in a circuit-based quantum computer to be described by these physical processes.
-Nonetheless, in absence of detailed microscopic descriptions of the device, they provide a good starting point to benchmark the code (in the same sense that Pauli errors are used to benchmark stabilizer codes).
-
-We explore the effect of these noise channels on two different encoding schemes (degenerate ground spaces).
-The first encoding we examine stores the information in the degenerate ground space of a system with Ising anyonic excitations embedded in a torus while the second stores information in a degenerate space associated with the fusion space of several well-separated Ising anyons.
-Both of these encodings lend themselves equally well to the two physical scenarios described above (although embedding an actual topologically ordered system on a torus probably poses an additional challenge).
-These two encodings are motivated by topological quantum memories \cite{Dennis2002} and topological quantum computing \cite{Bravyi2006b,BR07a} schemes respectively.
-
-Following this, we adapt existing techniques from topological quantum error correction to the non-Abelian setting.
-The non-Abelian nature of the model significantly changes the decoding problem and presents a main challenge of our study.
-In an Abelian model, decoding is realized by grouping nearby excitations that fuse to the vacuum.
-In contrast, for a non-Abelian model, it is not possible to predict with certainty the outcome of a fusion process.
-Thus, decoding needs to be an \emph{iterative} process: in a first round particles are grouped in a certain way; if all groups do not fuse to the vacuum, then a second round groups the remaining particles, and so on.
-In particular, we adapt the clustering renormalization group decoder of Bravyi and Haah~\cite{Bravyi2011} and the perfect matching algorithm decoders~\cite{Dennis2002, Wang2010} to our non-Abelian topological codes to determine their error-correction thresholds and memory lifetimes under various noise channels.
-Our decoders provably run in polynomial time in the size of the lattice.
-
-Using these decoders, we explicitly calculate numerical error-correction threshold estimates for these codes and for various noise regimes, including those where hopping and braiding of anyons dominates pair-creation.
-Our results seem to indicate that the perfect matching decoder outperforms the clustering decoder, and that the thresholds are broadly comparable for both types of codes, and for various types of noise.
-We find numerical threshold estimates that vary between 13\% and 25\%, where the percentages are in terms of a total noise rate density which we define and discuss in detail in Sections~\ref{S:phenom} and~\ref{S:numerics}.
-
-These thresholds are obtained by large-scale two-dimensional simulations of the dynamics of a dense ``gas'' of non-abelian anyons on lattice sizes of up to $48 \times 48$ nodes.
-All previous results have focused on quasi-one-dimensional models or single-particle quantum walks~\cite{Brennen2010, Lehman2011, Lehman2012, Zatloukal2012}.\stf{end copy \& paste from Ising.}
-*/ % end commented block
+\stf{Describe main results and why they are badass.}
 
 %------------------------------------------------------------------------------------------------------------%
+\paragraph{Modelling Fibonacci anyons}
 
-\paragraph{Modelling Fibonacci anyons.}\label{s:model}
+A physical anyon model is abstractly described by a unitary modular tensor 
+category~\cite{Wang2010b}. This object contains the data describing the types of anyonic 
+particles, as well as the results of topological operations such as braiding or fusion of these 
+anyons. The Fibonacci anyon model consists of only one non-trivial particle type, 
+conventionally called $\tau$. Denoting the vacuum by $\mathbb{I}$, we can describe the 
+possible fusion outcomes of Fibonacci anyons as $\tau\times\tau=\mathbb{I}+\tau$, i.e.~two 
+$\tau$ particles may either fuse to vacuum or to a $\tau$ particle.
 
-	A physical anyon model is abstractly described by a unitary modular tensor category~\cite{Wang2010b}.
-This object contains the data describing the types of anyonic particles, as well as the results of topological operations such as braiding or fusion of these anyons.
-The Fibonacci anyon model consists of only one non-trivial particle type, conventionally called $\tau$.
-Denoting the vacuum by $\mathbb{I}$, we can describe the possible fusion outcomes of Fibonacci anyons as $\tau\times\tau=\mathbb{I}+\tau$, i.e.~two $\tau$ particles may either fuse to vacuum or to a $\tau$ particle.
+We can associate a Hilbert space with the fusion outcomes of a fixed number of $\tau$ 
+particles, and for $n$ particles of type $\tau$, the dimension of this space grows 
+asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ the golden ratio. Additionally, 
+there is a global degeneracy associated with the topology of the manifold on which the 
+anyons reside. We will consider systems with the topology of a torus, which for the Fibonacci 
+anyons gives rise an extra 2-fold degeneracy. For convenience (in particular to minimize 
+finite-size effects in our numerical computations), this global space is the one in which we will 
+encode, and demonstrate protection of, quantum information.
 
-	We can associate a Hilbert space with the fusion outcomes of a fixed number of $\tau$ particles, and for $n$ particles of type $\tau$, the dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ the golden ratio.
-Additionally, there is a global degeneracy associated with the topology of the manifold on which the anyons reside.
-We will consider systems with the topology of a torus, which for the Fibonacci anyons gives rise an extra 2-fold degeneracy.
-For convenience (in particular to minimize finite-size effects in our numerical computations), this global space is the one in which we will encode, and demonstrate protection of, quantum information.
+The fusion outcome of any particular experiment depends on the history of the particles, in 
+particular how they have braided around one another. For this reason braiding operations are 
+considered to act unitarily on the fusion space. Pair-creation events should be considered 
+isometries that enlarge the fusion space, while fusion events correspond to projective 
+measurements of combined charge of some number of particles. For details of the description 
+of these processes in Fibonacci anyons, see Ref.~\cite{Trebst2008}. 
+\stf{check that this ref is a good one...}
 
-	The fusion outcome of any particular experiment depends on the history of the particles, in particular how they have braided around one another.
-For this reason braiding operations are considered to act unitarily on the fusion space.
-Pair-creation events should be considered isometries that enlarge the fusion space, while fusion events correspond to projective measurements of combined charge of some number of particles.
-For details of the description of these processes in Fibonacci anyons, see Ref.~\cite{Trebst2008}.
-
-	We use a phenomenological model of Fibonacci anyon dynamics which neglects any microscopic details of the system.
-This is consistent with the principles of topologically ordered systems and anyonic physics, where the key universal features describing the anyon model correspond to large length-scale physics, while the microscopic physics play a less important and non-universal role.
-As such, we model the system simply as a square lattice of sites on which sets of anyons may reside.
-Allowed anyon dynamics are considered to be local on this lattice, which we take to have periodic boundary conditions.
-For more details of an analogous model, see~\cite{Brell2013}.
-
-	Unlike the Ising anyon systems simulated in Ref.~\cite{Brell2013}, or the $\Phi-\Lambda$ models studied in Refs.~\cite{Wootton2013, Hutter2014}, Fibonacci anyon dynamics are known to be sufficient for universal quantum computation~\cite{Freedman2002}.
-This is because the action of braiding Fibonacci anyons generates a dense set of unitaries on the fusion space (for $n>2$ particles).
-For this reason, the classsical simulation of such dynamics is expected to be hard in general.
-As such, it might be expected that the simulation of noise processes and error-correction routines in Fibonacci anyon systems is prohibitively time-consuming.
-However, we show in \Sref{s:sim} that typical noise processes and error-correction operations may in fact be efficiently simulated on a classical computer in precisely the regimes where we expect error-correction to succeed.
+We use a phenomenological model of Fibonacci anyon dynamics which neglects any 
+microscopic details of the system. This is consistent with the principles of topologically 
+ordered systems and anyonic physics, where the key universal features describing the anyon 
+model correspond to large length-scale physics, while the microscopic physics plays a less 
+important and non-universal role. As such, we model the system simply as a square lattice of 
+sites on which sets of anyons may reside. Allowed anyon dynamics are considered to be local 
+on this lattice, which we take to have periodic boundary conditions. For more details of an 
+analogous model, see~\cite{Brell2013}.
 
 %------------------------------------------------------------------------------------------------------------%
-
-\paragraph{Noise and error-correction}\label{s:noise}
+\paragraph{Noise and error-correction}
 
@@
 
+%------------------------------------------------------------------------------------------------------------%	
 \paragraph{Logical errors}
@@
 
+%------------------------------------------------------------------------------------------------------------%	
 \paragraph{Decoding algorithm}
@@
 %------------------------------------------------------------------------------------------------------------%	
-
-\paragraph{Simulation}\label{s:sim}
+\paragraph{Simulation}
 
@@
 
-	\paragraph{Simulation algorithm}\label{s:simalg}
+%------------------------------------------------------------------------------------------------------------%	
+\paragraph{Simulation algorithm}
 
@@
 \begin{center}
-		(i)
-		\includegraphics[width=0.26\textwidth]{pair-create.pdf}
-		\hskip 10pt
+	{\scriptsize (i)
+	\includegraphics[width=0.26\columnwidth]{pair-create.pdf}
+	\hskip 5pt
 	(ii)
-		\includegraphics[width=0.26\textwidth]{syndrome-1.pdf}
-		\hskip 10pt
-		(iii)
-		\includegraphics[width=0.26\textwidth]{syndrome-2.pdf}
+	\includegraphics[width=0.26\columnwidth]{syndrome-1.pdf}
+	\hskip 5pt
+	(iii)}
+	\includegraphics[width=0.26\columnwidth]{syndrome-2.pdf}
 \end{center}
@@
 %------------------------------------------------------------------------------------------------------------%
-
 \paragraph{Numerical results}
@@
 
-	\begin{center}\includegraphics[width=\columnwidth]{anyons-kyle.pdf}\end{center}
+\begin{center}
+	\includegraphics[width=\columnwidth]{anyons-kyle.pdf}
+\end{center}
 
@@
 %------------------------------------------------------------------------------------------------------------%
-
 \paragraph{Discussion}

### 2014-12-08 fib2.tex
some edits and a ref added.

@@
 %------------------------------------------------------------------------------------------------------------%
-\paragraph{Modelling Fibonacci anyons}
+\paragraph{Modelling Fibonacci anyons.}
 
@@
 possible fusion outcomes of Fibonacci anyons as $\tau\times\tau=\mathbb{I}+\tau$, i.e.~two 
-$\tau$ particles may either fuse to vacuum or to a $\tau$ particle.
+$\tau$ particles can either fuse to vacuum or to a $\tau$ particle.
 
@@
 important and non-universal role. As such, we model the system simply as a square lattice of 
-sites on which sets of anyons may reside. Allowed anyon dynamics are considered to be local 
+sites on which sets of anyons can reside. Allowed anyon dynamics are considered to be local 
 on this lattice, which we take to have periodic boundary conditions. For more details of an 
@@
 %------------------------------------------------------------------------------------------------------------%
-\paragraph{Noise and error-correction}
+\paragraph{Noise and error-correction.}
 
@@
 
-\cggb{Details. Consider merging parts of this section with parts of \Sref{s:simalg}.}
+\cggb{Details. Consider merging parts of this section with parts of Simulation below.}
 
 %------------------------------------------------------------------------------------------------------------%	
-\paragraph{Logical errors}
+\paragraph{Logical errors.}
 
@@
 %------------------------------------------------------------------------------------------------------------%	
-\paragraph{Decoding algorithm}
+\paragraph{Decoding algorithm.}
 
@@
 
-\cggb{How does this relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?}
+\cggb{How does this relate to other decoding schemes used 
+in~\cite{Wootton2013,Brell2013,Hutter2014}?}
 
 %------------------------------------------------------------------------------------------------------------%	
-\paragraph{Simulation}
+\paragraph{Simulation.}
 
-Although simulation of general processes involving $n$ Fibonacci anyons is BQP-complete (and thus unlikely to be classically tractable), noise and error-correction procedures have structure that we can exploit to efficiently simulate typical processes of interest.
-In particular, those processes in which we expect error-correction to succeed are also those that we expect to be able to efficiently simulate for the following reasons.
+Although simulating pair creation, braiding, and fusion of $n$ Fibonacci anyons is equivalent 
+to in computational power to universal quantum computing (and thus unlikely to be classically 
+tractable), noise and error-correction procedures have structure that we can exploit to 
+efficiently simulate typical processes of interest. In particular, those processes in which we 
+expect error-correction to succeed are also those that we expect to be able to efficiently 
+simulate for the following heuristic reasons.
 
-Below the (bond) percolation threshold, we expect random sets of bonds to decompose into separate clusters of average size $O(log(n))$ and variance $O(1)$, \cite{Bazant2000}.
-In our context, the random bonds correspond to noise processes, and so separate clusters correspond to sets of anyons that could not have interacted at any point in their history.
-As such, we can simulate the braiding processes of each cluster separately.
-In other words: it is a (tensor) product state, so we compute with each factor separately.
-Since each cluster has only size $O(log(n))$, we may typically simulate these dynamics efficiently.
+Below the (bond) percolation threshold for (say) a square lattice, we expect random sets of 
+bonds to decompose into separate clusters of average size $O(\log(n))$ and variance 
+$O(1)$,~\cite{Bazant2000}. In our context, the random bonds correspond to noise processes, 
+and so disconnected clusters correspond to sets of anyons that could not have interacted at 
+any point in their history. As such, we can simulate the braiding processes of each cluster 
+separately. In other words: the quantum state factorizes into a tensor product, and we can 
+compute with each factor separately. Since each cluster has size only $O(\log(n))$, we can 
+typically simulate these dynamics efficiently because the resulting fusion space has 
+dimension $O(\mathrm{poly}(n))$. There are rare random processes that violate this 
+reasoning, but processes such as these are suppressed exponentially in $L$, the 
+lattice size~\cite{Grimmett1989}.
 
-However, random noise processes are not the only dynamics that we need consider.
-We must also consider the effect of the error-correction routine itself.
-This acts iteratively to fuse particles on increasing length scales.
-While this kind of fusion would typically merge clusters, forcing us to compute dynamics of larger and larger sets of anyons, at each length scale the total number of anyons present is dramatically reduced.
-Indeed, the goal of the error correction algorithm is to reduce the number of anyons as much as possible.
+However, random noise processes are not the only dynamics that we need to consider. We 
+must also consider the effect of the error-correction routine itself. This acts iteratively to fuse 
+particles on increasing length scales. While this kind of fusion would typically merge clusters, 
+forcing us to compute dynamics of larger and larger sets of anyons, at each length scale the 
+total number of anyons present is dramatically reduced. Indeed, the goal of the error 
+correction algorithm is to reduce the number of anyons as much as possible.
 
-\cggb{Can we make a concrete claim about the maximum size of clusters at each stage of the decoding procedure?
-Do we know anything about the distribution of separations between clusters in the sub-critical percolation regime?}
+\cggb{Can we make a concrete claim about the maximum size of clusters at each stage of the decoding procedure?} \stf{Well, the worst case behavior has no bound, so we need a statement about expectation.} \cggb{Do we know anything about the distribution of separations between clusters in the sub-critical percolation regime?} \stf{I think the Bravyi \& Haah appendix might provide some results that would be useful in making such a statement.}
 
@@
 So we see that the events that we are able to efficiently simulate correspond precisely to those for which we expect error-correction to succeed.
-We may simply declare failure on non-simulable events.
+We can simply declare failure on non-simulable events.
 This allows us to simulate and demonstrate the success of error-correction schemes for Fibonacci anyons, without explicitly simulating the failure of such schemes.
@@
 %------------------------------------------------------------------------------------------------------------%	
-\paragraph{Simulation algorithm}
+\paragraph{Simulation algorithm.}
 
-We cover the surface of the torus with LxL disjoint squares. These {\it tiles} are the regions over which
+We cover the surface of the torus with $L\times L$ disjoint squares. These \emph{tiles} are the regions over which
 charge measurements occur, in order to produce a syndrome for the decoder.
 
-In order to keep track of the observables of the system we maintain a set of disjoint {\it curves}.
+In order to keep track of the observables of the system we maintain a set of disjoint \emph{curves}.
 These curves can also be thought of as a top-down view of the fusion tree.
 In general, this winds around the two dimensional tiles in a haphazard way determined by the progress of the simulation.
-For comparison, previous work used a single fixed Z-shaped curve (row-major ordering) \cite{Brell2013}.
+For comparison, previous work used a single fixed Z-shaped curve (row-major ordering)~\cite{Brell2013}.
 
+\begin{figure}[th!]
 \begin{center}
 	{\scriptsize (i)
-	\includegraphics[width=0.26\columnwidth]{pair-create.pdf}
-	\hskip 5pt
+	\includegraphics[width=0.27\columnwidth]{pair-create.pdf}
+	\hskip 4pt
 	(ii)
-	\includegraphics[width=0.26\columnwidth]{syndrome-1.pdf}
-	\hskip 5pt
+	\includegraphics[width=0.27\columnwidth]{syndrome-1.pdf}
+	\hskip 4pt
 	(iii)}
-	\includegraphics[width=0.26\columnwidth]{syndrome-2.pdf}
+	\includegraphics[width=0.27\columnwidth]{syndrome-2.pdf}
+\caption{default}
+\label{default}
 \end{center}
+\end{figure}
 
@@
 %------------------------------------------------------------------------------------------------------------%
-\paragraph{Numerical results}
+\paragraph{Numerical results.}
 
@@
 
+\begin{figure}[th!]
 \begin{center}
 	\includegraphics[width=\columnwidth]{anyons-kyle.pdf}
+\caption{default}
+\label{default}
 \end{center}
+\end{figure}
 
@@
 %------------------------------------------------------------------------------------------------------------%
-\paragraph{Discussion}
+\paragraph{Discussion.}
 

### 2014-12-17 fib2.tex
pushing changes from earlier.
Added two references, one to Mong et al. and one to Bonesteel & DiVincenzo.

@@
 states~\cite{Slingerland2001}, and can also be realized in several spin 
-models~\cite{Levin2005, Kapit2013, Palumbo2014}.
+models~\cite{Levin2005, Kapit2013, Palumbo2014} and composite heterostructures~\cite{Mong2014}.
 
-\stf{Describe main results and why they are badass.}
+\stf{Describe main results and why they are badass. cite:~\cite{Bonesteel2012}}
 
@@
 
-\cggb{Can we make a concrete claim about the maximum size of clusters at each stage of the decoding procedure?} \stf{Well, the worst case behavior has no bound, so we need a statement about expectation.} \cggb{Do we know anything about the distribution of separations between clusters in the sub-critical percolation regime?} \stf{I think the Bravyi \& Haah appendix might provide some results that would be useful in making such a statement.}
+\cggb{Can we make a concrete claim about the maximum size of clusters at each stage of the 
+decoding procedure?} \stf{Well, the worst case behavior has no bound, so we need a 
+statement about expectation.} \cggb{Do we know anything about the distribution of 
+separations between clusters in the sub-critical percolation regime?} \stf{I think the Bravyi \& 
+Haah appendix might provide some results that would be useful in making such a statement.}
 
@@
 
+\stf{Is there a possibility of using MPS like Rob Pfeiffer to improve the simulations or include interactions?}
+
 \cggb{Do we have much more to say?}

### 2015-01-09 fib2.tex
added acknowledgements.
new things

@@
 % if we want to consider a PRL-style version, use these settings
-\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage]{revtex4-1}
+\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
 \usepackage{times}
@@
 \begin{abstract}
-Simulating the dynamics of excitations in two-dimensional quantum systems that support 
-anyons is intractable in general because it is sufficient for universal quantum computation. 
-Here we show that for typical processes of interest for the study of quantum error correction 
-in anyon systems, the relevant dynamics can in fact be efficiently simulated classically for a 
-wide range of system parameters, even when the underlying anyon model is universal. We 
-make use of this fact to demonstrate the success of an error-correction protocol for a 
-Fibonacci anyon quantum memory. We numerically simulate a phenomenological model of 
-the system and noise processes on lattice sizes of up to $128\times128$ sites, and 
-demonstrate an error-correction threshold of around $12.5\%$, a number that is comparable 
-to those previously known for abelian and (non-universal) nonabelian anyon models.
+Classically simulating the dynamics of excitations in two-dimensional quantum systems that support anyons is likely intractable in general because such dynamics are sufficient for universal quantum computation.
+However, for typical processes of interest for the the study of quantum error correction in anyon systems, the relevant dynamics can in fact be efficiently simulated classically for a wide range of system parameters, even when the underlying anyon model is universal~\cite{RGsim}.
+We make use of this fact to demonstrate the success of an error-correction protocol for a Fibonacci anyon quantum memory.
+We numerically simulate a phenomenological model of the system and noise processes on lattice sizes of up to $128\times128$ sites, and find a lower bound on the error-correction threshold of approximately $12.5\%$, which is comparable to those previously known for abelian and (non-universal) nonabelian anyon models.
 \end{abstract}
@@
 
-A physical anyon model is abstractly described by a unitary modular tensor 
-category~\cite{Wang2010b}. This object contains the data describing the types of anyonic 
-particles, as well as the results of topological operations such as braiding or fusion of these 
-anyons. The Fibonacci anyon model consists of only one non-trivial particle type, 
-conventionally called $\tau$. Denoting the vacuum by $\mathbb{I}$, we can describe the 
-possible fusion outcomes of Fibonacci anyons as $\tau\times\tau=\mathbb{I}+\tau$, i.e.~two 
-$\tau$ particles can either fuse to vacuum or to a $\tau$ particle.
+A physical anyon model is abstractly described by a unitary modular tensor category~\cite{Wang2010b}.
+This object contains the data describing the types of anyonic particles, as well as the results of topological operations such as braiding or fusion of these anyons.
+The Fibonacci anyon model consists of only one non-trivial particle type, conventionally called $\tau$.
+Denoting the vacuum by $\mathbb{I}$, we can describe the possible fusion outcomes of Fibonacci anyons as $\tau\times\tau=\mathbb{I}+\tau$, i.e.~two $\tau$ particles can either fuse to vacuum or to a $\tau$ particle.
 
-We can associate a Hilbert space with the fusion outcomes of a fixed number of $\tau$ 
-particles, and for $n$ particles of type $\tau$, the dimension of this space grows 
-asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ the golden ratio. Additionally, 
-there is a global degeneracy associated with the topology of the manifold on which the 
-anyons reside. We will consider systems with the topology of a torus, which for the Fibonacci 
-anyons gives rise an extra 2-fold degeneracy. For convenience (in particular to minimize 
-finite-size effects in our numerical computations), this global space is the one in which we will 
-encode, and demonstrate protection of, quantum information.
+Associated with the fusion outcomes of a fixed number of $\tau$ particles is a Hilbert space, the \emph{fusion} space.
+For $n$ particles of type $\tau$, the dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ the golden ratio.
+Additionally, there is a global degeneracy associated with the topology of the manifold on which the anyons reside.
+We will consider systems with the topology of a torus, which for the Fibonacci anyons gives rise to a 2-fold degeneracy.
+For convenience (in particular to minimize finite-size effects in our numerical computations~\cite{Brell2013}), this global space is the one in which we will encode, and demonstrate protection of, quantum information.
 
-The fusion outcome of any particular experiment depends on the history of the particles, in 
-particular how they have braided around one another. For this reason braiding operations are 
-considered to act unitarily on the fusion space. Pair-creation events should be considered 
-isometries that enlarge the fusion space, while fusion events correspond to projective 
-measurements of combined charge of some number of particles. For details of the description 
-of these processes in Fibonacci anyons, see Ref.~\cite{Trebst2008}. 
-\stf{check that this ref is a good one...}
+The fusion outcome of any particular experiment depends on the history of the particles, in particular how they have braided around one another.
+For this reason braiding operations are considered to act unitarily on the fusion space.
+Pair-creation events should be considered isometries that enlarge the fusion space, while fusion events correspond to projective
+measurements of combined charge of some number of particles.
+For details of the description of these processes in Fibonacci anyons, see Ref.~\cite{Trebst2008}.
+\stf{check that this ref is a good one...} Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be sufficient to implement universal quantum computation~\cite{?}.
 
-We use a phenomenological model of Fibonacci anyon dynamics which neglects any 
-microscopic details of the system. This is consistent with the principles of topologically 
-ordered systems and anyonic physics, where the key universal features describing the anyon 
-model correspond to large length-scale physics, while the microscopic physics plays a less 
-important and non-universal role. As such, we model the system simply as a square lattice of 
-sites on which sets of anyons can reside. Allowed anyon dynamics are considered to be local 
-on this lattice, which we take to have periodic boundary conditions. For more details of an 
-analogous model, see~\cite{Brell2013}.
+We use a phenomenological model of Fibonacci anyon dynamics which neglects any microscopic details of the system.
+This is consistent with the principles of topologically ordered systems and anyonic physics, where the key universal features describing the anyon model correspond to large length-scale physics, while the microscopic physics plays a less
+important (and non-universal) role.
+As such, we model the system simply as a square lattice of sites on which sets of anyons can reside.
+Allowed anyon dynamics are considered to be local on this lattice, which we take to have periodic boundary conditions.
+For more details of an analogous model, see~\cite{Brell2013}.
 
@@
 
-The main noise processes we consider are pair-creation events, in which a pair of $\tau$ anyons are created from vacuum on two neighbouring sites.
+	We consider encoding a qubit of quantum information in the global topological degeneracy associated with the topology of the manifold of our system.
+As such, the codespace is specified as having vacuum charge at each site of the lattice.
+Typical realistic noise processes in this kind of system are pair-creation, hopping, exchange etc.~of anyons on neighbouring sites.
+It was seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only is sufficient to capture the qualitative features of an error-correction simulation, and so we will restrict to pair-creation noise processes in this study for convenience.
+These events act on neighbouring pairs of sites, and so may be associated with an edge of the lattice, chosen uniformly at random at each timestep of the simulation.
+The simulation time, and thus the error-correction threshold, will be measured in terms of average number of noise processes per edge, as opposed to an iid noise probability per edge.
+The latter measure is not appropriate for error processes in nonabelian anyon models, but the two coincide in the limit of low error rates in those cases where they are comparable (see Ref.~\cite{Brell2013}).
 
-\cggb{Details. Consider merging parts of this section with parts of Simulation below.}
+	In order to perform a logical error on our code, a noise process must have support on a ribbon running around a homologically nontrivial loop of the lattice.
+These correspond to processes in which a $\tau$ anyon is transported around the non-trivial loop before annihilating to vacuum.
+More details can be found in Ref.~\cite{?}.
+
+	Our error-correction algorithm is based on the hard-decision renormalization group (RG) decoders studied in Refs.~\cite{?}.
+Our decoder proceeds by measuring the occupations of anyons at each site of the lattice, forming clusters of nearby anyons and fusing the anyons within each cluster, and iterating at longer length scales.
+It terminates when the lattice is free of anyons (i.e.~we have returned to the codespace) or the clustering length scale exceeds the total size of the lattice.
+\cggb{A few more details?
+What is our length schedule?} \cggb{How does our decoder relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?} Note that we expect that our qualitative results may be reproduced by most alternative families of decoders, such as matching decoders~\cite{?} and soft-decisions RG decoders~\cite{?} \cggb{do we?}.
+The advantage of using a hard-decision RG decoder is its simplicity and flexibility, and the fact that this simplicity allows for a proof of efficient classical simulability of successful error-correction~\cite{RGsim}.
 
 %------------------------------------------------------------------------------------------------------------%	
-\paragraph{Logical errors.}
+\paragraph{Classical simulability.}
 
-\cggb{Logical operators}
+Although simulating pair creation, braiding, and fusion of $n$ Fibonacci anyons is equivalent in computational power to universal quantum computing (and thus unlikely to be classically tractable), noise and error-correction procedures have structure that we can exploit to efficiently simulate typical processes of interest~\cite{RGsim}.
+In particular, those processes in which we expect error-correction to succeed are also those that we expect to be able to efficiently
+simulate for the following heuristic reasons (see Ref.~\cite{RGsim} for a more rigorous analysis).
 
-%------------------------------------------------------------------------------------------------------------%	
-\paragraph{Decoding algorithm.}
+Below the (bond) percolation threshold for (say) a square lattice, we expect random sets of bonds to decompose into separate clusters of average size $O(\log(n))$ and variance $O(1)$~\cite{Bazant2000}.
+\cggb{Do we want to use the word cluster here again or switch?} Each noise process in our model is associated with a (randomly distributed) edge, and so disconnected clusters correspond to sets of anyons that could not have interacted at any point in their history.
+As such, we can simulate the braiding processes of each cluster separately.
+In other words: the quantum state in the fusion space of all anyons factorizes into a tensor product over bond clusters, and we can compute each factor separately.
+Since each cluster has size only $O(\log(n))$, we can typically simulate these dynamics efficiently because the resulting fusion space has dimension $O(\mathrm{poly}(n))$.
+There are rare random processes that violate this reasoning, but processes such as these are suppressed exponentially in $L$, the lattice size~\cite{Grimmett1989}.
 
-\cggb{Describe decoding.}
-
-\cggb{How does this relate to other decoding schemes used 
-in~\cite{Wootton2013,Brell2013,Hutter2014}?}
-
-%------------------------------------------------------------------------------------------------------------%	
-\paragraph{Simulation.}
-
-Although simulating pair creation, braiding, and fusion of $n$ Fibonacci anyons is equivalent 
-to in computational power to universal quantum computing (and thus unlikely to be classically 
-tractable), noise and error-correction procedures have structure that we can exploit to 
-efficiently simulate typical processes of interest. In particular, those processes in which we 
-expect error-correction to succeed are also those that we expect to be able to efficiently 
-simulate for the following heuristic reasons.
-
-Below the (bond) percolation threshold for (say) a square lattice, we expect random sets of 
-bonds to decompose into separate clusters of average size $O(\log(n))$ and variance 
-$O(1)$,~\cite{Bazant2000}. In our context, the random bonds correspond to noise processes, 
-and so disconnected clusters correspond to sets of anyons that could not have interacted at 
-any point in their history. As such, we can simulate the braiding processes of each cluster 
-separately. In other words: the quantum state factorizes into a tensor product, and we can 
-compute with each factor separately. Since each cluster has size only $O(\log(n))$, we can 
-typically simulate these dynamics efficiently because the resulting fusion space has 
-dimension $O(\mathrm{poly}(n))$. There are rare random processes that violate this 
-reasoning, but processes such as these are suppressed exponentially in $L$, the 
-lattice size~\cite{Grimmett1989}.
-
-However, random noise processes are not the only dynamics that we need to consider. We 
-must also consider the effect of the error-correction routine itself. This acts iteratively to fuse 
-particles on increasing length scales. While this kind of fusion would typically merge clusters, 
-forcing us to compute dynamics of larger and larger sets of anyons, at each length scale the 
-total number of anyons present is dramatically reduced. Indeed, the goal of the error 
-correction algorithm is to reduce the number of anyons as much as possible.
-
-\cggb{Can we make a concrete claim about the maximum size of clusters at each stage of the 
-decoding procedure?} \stf{Well, the worst case behavior has no bound, so we need a 
-statement about expectation.} \cggb{Do we know anything about the distribution of 
-separations between clusters in the sub-critical percolation regime?} \stf{I think the Bravyi \& 
-Haah appendix might provide some results that would be useful in making such a statement.}
+However, random noise processes are not the only dynamics that we need to consider.
+We must also consider the effect of the error-correction routine itself.
+This acts iteratively to fuse particles on increasing length scales.
+While this kind of fusion would typically merge clusters, forcing us to compute dynamics of larger and larger sets of anyons, large clusters are sparse (and thus unlikely to be merged), and in addition at each length scale the total number of anyons present is dramatically reduced by fusion, leading to a smaller number of anyons that must be simulated.
 
@@
 Similarly, if the noise has not yet percolated by itself, but the clusters are merged into a large (percolated) cluster by the decoding algorithm, this is again an example of a process that we expect to correspond to a failure of error-correction.
-So we see that the events that we are able to efficiently simulate correspond precisely to those for which we expect error-correction to succeed.
+In this way, we see that the events that we are able to efficiently simulate correspond precisely to those for which we expect error-correction to succeed.
 We can simply declare failure on non-simulable events.
@@
 
-We cover the surface of the torus with $L\times L$ disjoint squares. These \emph{tiles} are the regions over which
-charge measurements occur, in order to produce a syndrome for the decoder.
-
-In order to keep track of the observables of the system we maintain a set of disjoint \emph{curves}.
-These curves can also be thought of as a top-down view of the fusion tree.
-In general, this winds around the two dimensional tiles in a haphazard way determined by the progress of the simulation.
-For comparison, previous work used a single fixed Z-shaped curve (row-major ordering)~\cite{Brell2013}.
+	Our concrete simulation proceeds by associating a \emph{tile} with each site of the $L\times L$ periodic square lattice.
+In order to keep track of the observables of the system we maintain a set of disjoint curves, representing the history of anyons on the lattice (these curves can also be thought of as a top-down view of the fusion tree).
+The ends of curves correspond to leaves of the fusion tree, or anyons.
+In general, the curves wind around the two dimensional tiles in a haphazard way determined by the progress of the simulation.
+This allows a dynamically generated basis for the fusion space that easily allows for tensor decomposition into factors corresponding disjoint clusters.
+For comparison, previous work used a single fixed basis for the fusion space (determined by row-major ordering of sites)~\cite{Brell2013}.
 
@@
 	\includegraphics[width=0.27\columnwidth]{syndrome-2.pdf}
-\caption{default}
-\label{default}
+\caption{The simulation of noise processes proceeds by i) creating pairs of anyons on neighbouring tiles represented by open curves ii) joining the curves within a given tile iii) measuring the total charge on each tile.}
+\label{f:simex}
 \end{center}
@@
 
-Each round of simulation proceeds in four steps as follows:
+Each round of simulation proceeds in four steps as follows (an example is shown in \Fref{f:simex}).
 
-\begin{enumerate}
+\begin{enumerate}[i)]
 	\item The noise process is modelled by a sequence of pair-creation events distributed as a Poisson process across each edge.
-	\item We first join curves that participate in the same tile in order to,
+Curves are created crossing the relevent edge and terminating on the neighbouring sites.
+	\item We first join curves that participate in the same tile in order to, \cggb{maybe a couple more lines of detail on this and the next point?}
 	\item measure the charge on each tile. Any resulting anyon is left somewhere in the tile.
 	\item The decoder examines this syndrome and clusters nearby anyons.
-Each cluster is then measured (fused), and the decoder continues to cluster and fuse on larger scales until there are no more anyons, or a non-trivial operation has occurred.
-The non-trivial operations are those that involve a path that wraps around the torus.
-All of these alter the encoded state, and so in this case we abandon the simulation round and declare failure to error correct.
-This decoding algorithm is based on the clustering ``RG'' algorithm~\cite{Bravyi2011}.
+Each cluster is then measured (fused), and the decoder continues to cluster and fuse on larger scales until there are no more anyons, or a cluster includes a non-trivial loop on the lattice.
+Since operators with support on such non-trivial clusters will generally perform an undetectable error on the encoded state, in this case we abandon the simulation and declare failure to error correct.
 \end{enumerate}
@@
 
-We plot the performance of the decoder as a function of error rate for varying lattice sizes.
-The error rate is parameterized by the Poisson process duration $t_{\mathrm{sim}}$.
-There is clear evidence of a decoding threshold below
-which decoding succeeds with asymptotic certainty as the system size increases. This threshold is at $t_{\mathrm{sim}}\simeq 0.125 \pm 0.003.$
+	We plot the performance of the decoder as a function of error rate for varying lattice sizes in \Fref{f:threshold}.
+The error rate is parameterized by the Poisson process duration $t_{\mathrm{sim}}$, representing the average number of errors per edge over the simulation.
+We find evidence of a decoding threshold below which decoding succeeds with asymptotic certainty as the system size increases at $t_{\mathrm{sim}}\simeq 0.125 \pm 0.003$.
 
@@
 	\includegraphics[width=\columnwidth]{anyons-kyle.pdf}
-\caption{default}
-\label{default}
+\caption{Decoder failure as a function of simulation time for various lattice sizes, showing threshold behavior around at $t_{\mathrm{sim}}\simeq 0.125$.}
+\label{f:threshold}
 \end{center}
@@
 
-\cggb{Define $t_{\mathrm{sim}}$.}
+\cggb{Do we need to define $t_{\mathrm{sim}}$ more explicitly?}
 
@@
 
-\cggb{Comment on choice of encoding, and applicability of our simulation techniques to simulation of fusion encodings as in Fibonacci anyon computing schemes.}
+	We have demonstrated classical simulation of successful error correction in a universal anyon model.
+Though we have chosen several properties of our model and simulation in a convenient way for simplicity, we think it very unlikely that they will affect the qualitative results, similarly to Ref.~\cite{Brell2013}.
+In particular, although we have modelled our logical qubit as encoded in the global topological degrees of freedom of our system, we could have encoded it in the fusion space of several preferred $\tau$ anyons.
+This situation would be appropriate to model error-correction routines in a topological quantum computation protocol.
+Additionally, we expect our results to be stable to changes in details of the noise model, decoding algorithm, etc.
 
-\cggb{Comment on choice of decoder, noise scheme, etc., particularly noting that the qualitative details are unlikely to be affected by these choices~\cite{Brell2013}.}
-
-\cggb{Comment on the fact that these methods are not restricted to Fibonacci anyons, and could be used to demonstrate the success of error-correction protocols on arbitrary anyon models.}
+	None of our techniques are restricted to simulation of Fibonacci anyon dynamics, and could equally well be used to simulate successful error-correction protocols in an arbitrary anyon code.
 
@@
 %------------------------------------------------------------------------------------------------------------%
+\acknowledgements
+
+\cggb {People we chatted to.} This work was supported by the ARC via EQuS project number CE11001013, and by the US Army Research Office grant numbers W911NF-14-1-0098 and W911NF-14-1-0103.
+STF also acknowledges support from an ARC Future Fellowship FT130101744.
+\cggb{CGB funding.}
+
+%------------------------------------------------------------------------------------------------------------%
 %\bibliographystyle{bibstyle}

### 2015-03-30 fib2.tex
Trying out having a two-column figure just to see how it looks. Thoughts?
minor text edits

@@
 
-A physical anyon model is abstractly described by a unitary modular tensor category~\cite{Wang2010b}.
+The topological features of a physical anyon model are abstractly described by a unitary modular tensor category~\cite{Wang2010b}.
 This object contains the data describing the types of anyonic particles, as well as the results of topological operations such as braiding or fusion of these anyons.
-The Fibonacci anyon model consists of only one non-trivial particle type, conventionally called $\tau$.
+The Fibonacci anyon model consists of only one non-trivial particle type, conventionally labelled $\tau$.
 Denoting the vacuum by $\mathbb{I}$, we can describe the possible fusion outcomes of Fibonacci anyons as $\tau\times\tau=\mathbb{I}+\tau$, i.e.~two $\tau$ particles can either fuse to vacuum or to a $\tau$ particle.
 
-Associated with the fusion outcomes of a fixed number of $\tau$ particles is a Hilbert space, the \emph{fusion} space.
+Associated with each set of fusion outcomes for a fixed number of $\tau$ particles is a basis vector for a Hilbert space, the \emph{fusion} space.
 For $n$ particles of type $\tau$, the dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ the golden ratio.
@@
 The fusion outcome of any particular experiment depends on the history of the particles, in particular how they have braided around one another.
-For this reason braiding operations are considered to act unitarily on the fusion space.
+Braiding operations are treated as unitary actions on the fusion space.
 Pair-creation events should be considered isometries that enlarge the fusion space, while fusion events correspond to projective
@@
 important (and non-universal) role.
-As such, we model the system simply as a square lattice of sites on which sets of anyons can reside.
-Allowed anyon dynamics are considered to be local on this lattice, which we take to have periodic boundary conditions.
+As such, we model the system simply as a periodic $L\times L$ square lattice $\Lambda$ of sites with upon which sets of anyons can reside.
+Allowed anyon dynamics (pair-creation, braiding, and fusion) are considered to act locally on edges of $\Lambda$.
 For more details of an analogous model, see~\cite{Brell2013}.
@@
 
-	We consider encoding a qubit of quantum information in the global topological degeneracy associated with the topology of the manifold of our system.
-As such, the codespace is specified as having vacuum charge at each site of the lattice.
-Typical realistic noise processes in this kind of system are pair-creation, hopping, exchange etc.~of anyons on neighbouring sites.
+	We consider encoding a qubit of quantum information in the global degeneracy associated with the topology of the manifold of our system.
+We imagine an idealized Hamiltonian for this system of the form
+	\begin{align}
+		H=-\sum_{i\in Lambda}\proj{\mathbb{I}_i}\;,\label{e:hamiltonian}
+	\end{align}
+with $\proj{\mathbb{I}}_i$ the projector to charge $\mathmm{I}$ at site $i$, i.e.~the ground space of the model has vacuum (or no anyon) at each site.
+Given the toroidal boundary conditions, this space is two-fold degenerate as noted above.
+We identify this ground space as the codespace of our model.
+Typical realistic noise processes in this kind of system are pair-creation, hopping, exchange etc.~of anyons on neighbouring sites of $\Lambda$.
 It was seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only is sufficient to capture the qualitative features of an error-correction simulation, and so we will restrict to pair-creation noise processes in this study for convenience.
@@
 	In order to perform a logical error on our code, a noise process must have support on a ribbon running around a homologically nontrivial loop of the lattice.
-These correspond to processes in which a $\tau$ anyon is transported around the non-trivial loop before annihilating to vacuum.
+These correspond to processes in which anyonic charge is transported around the non-trivial loop before annihilating to vacuum.
 More details can be found in Ref.~\cite{?}.
@@
 The advantage of using a hard-decision RG decoder is its simplicity and flexibility, and the fact that this simplicity allows for a proof of efficient classical simulability of successful error-correction~\cite{RGsim}.
+
+\begin{figure*}[th!]
+\begin{center}
+	{\scriptsize (i)
+	\includegraphics[width=0.57\columnwidth]{pair-create.pdf}
+	\hskip 4pt
+	(ii)
+	\includegraphics[width=0.57\columnwidth]{syndrome-1.pdf}
+	\hskip 4pt
+	(iii)}
+	\includegraphics[width=0.57\columnwidth]{syndrome-2.pdf}
+\caption{The simulation of noise processes proceeds by i) creating pairs of anyons on neighbouring tiles represented by open curves ii) joining the curves within a given tile iii) measuring the total charge on each tile.}
+\label{f:simex}
+\end{center}
+\end{figure*}
 
@@
 For comparison, previous work used a single fixed basis for the fusion space (determined by row-major ordering of sites)~\cite{Brell2013}.
-
-\begin{figure}[th!]
-\begin{center}
-	{\scriptsize (i)
-	\includegraphics[width=0.27\columnwidth]{pair-create.pdf}
-	\hskip 4pt
-	(ii)
-	\includegraphics[width=0.27\columnwidth]{syndrome-1.pdf}
-	\hskip 4pt
-	(iii)}
-	\includegraphics[width=0.27\columnwidth]{syndrome-2.pdf}
-\caption{The simulation of noise processes proceeds by i) creating pairs of anyons on neighbouring tiles represented by open curves ii) joining the curves within a given tile iii) measuring the total charge on each tile.}
-\label{f:simex}
-\end{center}
-\end{figure}
 

### 2015-03-30 fib2.tex
more minor text edits. im mostly pretty happy now with the structure. intro still needs a bunch of work, refs still need to be added, and there are a few open comments to address, especially in the conclusion.

@@
 	\begin{align}
-		H=-\sum_{i\in Lambda}\proj{\mathbb{I}_i}\;,\label{e:hamiltonian}
+		H=-\sum_{i\in \Lambda}\proj{\mathbb{I}}_i\;,\label{e:hamiltonian}
 	\end{align}
-with $\proj{\mathbb{I}}_i$ the projector to charge $\mathmm{I}$ at site $i$, i.e.~the ground space of the model has vacuum (or no anyon) at each site.
+with $\proj{\mathbb{I}}_i$ the projector to charge $\mathbb{I}$ at site $i$, i.e.~the ground space of the model has vacuum (or no anyon) at each site.
 Given the toroidal boundary conditions, this space is two-fold degenerate as noted above.
@@
 	Our error-correction algorithm is based on the hard-decision renormalization group (RG) decoders studied in Refs.~\cite{?}.
-Our decoder proceeds by measuring the occupations of anyons at each site of the lattice, forming clusters of nearby anyons and fusing the anyons within each cluster, and iterating at longer length scales.
+Our decoder proceeds by measuring the occupations of anyons at each site of the lattice, forming clusters of nearby anyons and fusing the anyons within each cluster, before iterating at increasing length scales.
 It terminates when the lattice is free of anyons (i.e.~we have returned to the codespace) or the clustering length scale exceeds the total size of the lattice.
@@
 
-Although simulating pair creation, braiding, and fusion of $n$ Fibonacci anyons is equivalent in computational power to universal quantum computing (and thus unlikely to be classically tractable), noise and error-correction procedures have structure that we can exploit to efficiently simulate typical processes of interest~\cite{RGsim}.
+Although simulating pair creation, braiding, and fusion of $n$ Fibonacci anyons is equivalent in computational power to universal quantum computing (and thus unlikely to be classically tractable), noise processes and error-correction procedures have structure that we can exploit to efficiently simulate typical processes of interest~\cite{RGsim}.
 In particular, those processes in which we expect error-correction to succeed are also those that we expect to be able to efficiently
@@
 	We plot the performance of the decoder as a function of error rate for varying lattice sizes in \Fref{f:threshold}.
-The error rate is parameterized by the Poisson process duration $t_{\mathrm{sim}}$, representing the average number of errors per edge over the simulation.
+The error rate is parameterized by the Poisson process duration $t_{\mathrm{sim}}$, representing the expected number of errors per edge over the simulation.
 We find evidence of a decoding threshold below which decoding succeeds with asymptotic certainty as the system size increases at $t_{\mathrm{sim}}\simeq 0.125 \pm 0.003$.
@@
 	We have demonstrated classical simulation of successful error correction in a universal anyon model.
-Though we have chosen several properties of our model and simulation in a convenient way for simplicity, we think it very unlikely that they will affect the qualitative results, similarly to Ref.~\cite{Brell2013}.
+Though we have chosen several properties of our model and simulation in a convenient way for simplicity, we think it very unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}.
 In particular, although we have modelled our logical qubit as encoded in the global topological degrees of freedom of our system, we could have encoded it in the fusion space of several preferred $\tau$ anyons.

### 2015-04-05 fib2.tex
Consolidated the macros into the source file and hard-wrapped the lines so that git can detect changes better. No text changes.

@@
-% This line sets the project root file.
-% 
-% !TEX root = fib2.tex
-% 
-%------------------------------------------------------------------------------------------------------------%
-% if we want to consider a PRL-style version, use these settings
 \documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
@@
 
-% Packages, Macros, Layout, Environments, etc.
-\input{macros}
+%------------------------------------------------------------------------------------------------------------%
+% Packages
+%------------------------------------------------------------------------------------------------------------%
 
-% use this for multiline block comments: \/* commented text here */
-\long\def\/*#1*/{}
-%\long\def\/*#1*/{#1} % uncomment this line to load the block comments
+\usepackage{color}
+\usepackage{amsmath,amsfonts,amssymb,amsthm}
+\usepackage{graphicx}
+\usepackage[caption=false]{subfig}
+\usepackage{enumerate}
+
+%\usepackage{tikz}
+%\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit}
+%\usepackage{epstopdf} % to include .eps graphics files with pdfLaTeX
+%\usepackage{bm}  % Define \bm{} to use bold math fonts
+
+\usepackage[pdfpagelabels,pdftex,bookmarks,breaklinks]{hyperref}
+\definecolor{darkblue}{RGB}{0,0,127} % choose colors
+\definecolor{darkgreen}{RGB}{0,150,0}
+\hypersetup{colorlinks, linkcolor=darkblue, citecolor=darkgreen, filecolor=red, urlcolor=blue}
+\hypersetup{pdfauthor={Simon Burton, Courtney Brell, Steven T. Flammia}}
+%\hypersetup{pdftitle={Title\ Goes\ Here}}
+
+%------------------------------------------------------------------------------------------------------------%
+% Macros
+%------------------------------------------------------------------------------------------------------------%
+
+\newcommand{\Eref}[1]{Eq.~(\ref{#1})}
+\newcommand{\Fref}[1]{Fig.~\ref{#1}}
+\newcommand{\Aref}[1]{Appendix~\ref{#1}}
+
+\newcommand{\eps}{\epsilon}
+
+\newcommand{\ket}[1]{|{#1}\rangle}
+\newcommand{\expect}[1]{\langle{#1}\rangle}
+\newcommand{\bra}[1]{\langle{#1}|}
+\newcommand{\ketbra}[2]{\ket{#1}\!\bra{#2}}
+\newcommand{\braket}[2]{\langle{#1}|{#2}\rangle}
+\newcommand{\proj}[1]{\ketbra{#1}{#1}}
+
+%------------------------------------------------------------------------------------------------------------%
+% Comment fonts
+%------------------------------------------------------------------------------------------------------------%
+
+\newcommand{\cggb}[1]{\textcolor{blue}{#1}}
+\newcommand{\sdb}[1]{\textcolor{red}{#1}}
+\newcommand{\stf}[1]{\textcolor{green}{#1}}
 
@@
 \begin{abstract}
-Classically simulating the dynamics of excitations in two-dimensional quantum systems that support anyons is likely intractable in general because such dynamics are sufficient for universal quantum computation.
-However, for typical processes of interest for the the study of quantum error correction in anyon systems, the relevant dynamics can in fact be efficiently simulated classically for a wide range of system parameters, even when the underlying anyon model is universal~\cite{RGsim}.
-We make use of this fact to demonstrate the success of an error-correction protocol for a Fibonacci anyon quantum memory.
-We numerically simulate a phenomenological model of the system and noise processes on lattice sizes of up to $128\times128$ sites, and find a lower bound on the error-correction threshold of approximately $12.5\%$, which is comparable to those previously known for abelian and (non-universal) nonabelian anyon models.
+Classically simulating the dynamics of excitations in two-dimensional quantum systems that 
+support anyons is likely intractable in general because such dynamics are sufficient for 
+universal quantum computation. However, for typical processes of interest for the the study of 
+quantum error correction in anyon systems, the relevant dynamics can in fact be efficiently 
+simulated classically for a wide range of system parameters, even when the underlying anyon 
+model is universal~\cite{RGsim}. We make use of this fact to demonstrate the success of an 
+error-correction protocol for a Fibonacci anyon quantum memory. We numerically simulate a 
+phenomenological model of the system and noise processes on lattice sizes of up to 
+$128\times128$ sites, and find a lower bound on the error-correction threshold of 
+approximately $12.5\%$, which is comparable to those previously known for abelian and 
+(non-universal) nonabelian anyon models.
 \end{abstract}
@@
 states~\cite{Slingerland2001}, and can also be realized in several spin 
-models~\cite{Levin2005, Kapit2013, Palumbo2014} and composite heterostructures~\cite{Mong2014}.
+models~\cite{Levin2005, Kapit2013, Palumbo2014} and composite 
+heterostructures~\cite{Mong2014}.
 
@@
 
-The topological features of a physical anyon model are abstractly described by a unitary modular tensor category~\cite{Wang2010b}.
-This object contains the data describing the types of anyonic particles, as well as the results of topological operations such as braiding or fusion of these anyons.
-The Fibonacci anyon model consists of only one non-trivial particle type, conventionally labelled $\tau$.
-Denoting the vacuum by $\mathbb{I}$, we can describe the possible fusion outcomes of Fibonacci anyons as $\tau\times\tau=\mathbb{I}+\tau$, i.e.~two $\tau$ particles can either fuse to vacuum or to a $\tau$ particle.
+The topological features of a physical anyon model are abstractly described by a unitary 
+modular tensor category~\cite{Wang2010b}. This object contains the data describing the 
+types of anyonic particles, as well as the results of topological operations such as braiding or 
+fusion of these anyons. The Fibonacci anyon model consists of only one non-trivial particle 
+type, conventionally labelled $\tau$. Denoting the vacuum by $\mathbb{I}$, we can describe 
+the possible fusion outcomes of Fibonacci anyons as $\tau\times\tau=\mathbb{I}+\tau$, 
+i.e.~two $\tau$ particles can either fuse to vacuum or to a $\tau$ particle.
 
-Associated with each set of fusion outcomes for a fixed number of $\tau$ particles is a basis vector for a Hilbert space, the \emph{fusion} space.
-For $n$ particles of type $\tau$, the dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ the golden ratio.
-Additionally, there is a global degeneracy associated with the topology of the manifold on which the anyons reside.
-We will consider systems with the topology of a torus, which for the Fibonacci anyons gives rise to a 2-fold degeneracy.
-For convenience (in particular to minimize finite-size effects in our numerical computations~\cite{Brell2013}), this global space is the one in which we will encode, and demonstrate protection of, quantum information.
+Associated with each set of fusion outcomes for a fixed number of $\tau$ particles is a basis 
+vector for a Hilbert space, the \emph{fusion} space. For $n$ particles of type $\tau$, the 
+dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ 
+the golden ratio. Additionally, there is a global degeneracy associated with the topology of the 
+manifold on which the anyons reside. We will consider systems with the topology of a torus, 
+which for the Fibonacci anyons gives rise to a 2-fold degeneracy. For convenience 
+(in particular to minimize finite-size effects in our numerical computations~\cite{Brell2013}), 
+this global space is the one in which we will encode, and demonstrate protection of, quantum 
+information.
 
-The fusion outcome of any particular experiment depends on the history of the particles, in particular how they have braided around one another.
-Braiding operations are treated as unitary actions on the fusion space.
-Pair-creation events should be considered isometries that enlarge the fusion space, while fusion events correspond to projective
-measurements of combined charge of some number of particles.
-For details of the description of these processes in Fibonacci anyons, see Ref.~\cite{Trebst2008}.
-\stf{check that this ref is a good one...} Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be sufficient to implement universal quantum computation~\cite{?}.
+The fusion outcome of any particular experiment depends on the history of the particles, in 
+particular how they have braided around one another. Braiding operations are treated as 
+unitary actions on the fusion space. Pair-creation events should be considered isometries 
+that enlarge the fusion space, while fusion events correspond to projective measurements 
+of combined charge of some number of particles. For details of the description of these 
+processes in Fibonacci anyons, see Ref.~\cite{Trebst2008}. 
+\stf{check that this ref is a good one...} 
+Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be 
+sufficient to implement universal quantum computation~\cite{?}.
 
-We use a phenomenological model of Fibonacci anyon dynamics which neglects any microscopic details of the system.
-This is consistent with the principles of topologically ordered systems and anyonic physics, where the key universal features describing the anyon model correspond to large length-scale physics, while the microscopic physics plays a less
-important (and non-universal) role.
-As such, we model the system simply as a periodic $L\times L$ square lattice $\Lambda$ of sites with upon which sets of anyons can reside.
-Allowed anyon dynamics (pair-creation, braiding, and fusion) are considered to act locally on edges of $\Lambda$.
-For more details of an analogous model, see~\cite{Brell2013}.
+We use a phenomenological model of Fibonacci anyon dynamics which neglects any 
+microscopic details of the system. This is consistent with the principles of topologically 
+ordered systems and anyonic physics, where the key universal features describing the 
+anyon model correspond to large length-scale physics, while the microscopic physics plays 
+a less important (and non-universal) role. As such, we model the system simply as a 
+periodic $L\times L$ square lattice $\Lambda$ of sites with upon which sets of anyons can 
+reside. Allowed anyon dynamics (pair-creation, braiding, and fusion) are considered to act 
+locally on edges of $\Lambda$. For more details of an analogous model, see~\cite{Brell2013}.
 
@@
 
-	We consider encoding a qubit of quantum information in the global degeneracy associated with the topology of the manifold of our system.
-We imagine an idealized Hamiltonian for this system of the form
+We consider encoding a qubit of quantum information in the global degeneracy associated 
+with the topology of the manifold of our system. We imagine an idealized Hamiltonian for this 
+system of the form
 \begin{align}
@@
 \end{align}
-with $\proj{\mathbb{I}}_i$ the projector to charge $\mathbb{I}$ at site $i$, i.e.~the ground space of the model has vacuum (or no anyon) at each site.
-Given the toroidal boundary conditions, this space is two-fold degenerate as noted above.
-We identify this ground space as the codespace of our model.
-Typical realistic noise processes in this kind of system are pair-creation, hopping, exchange etc.~of anyons on neighbouring sites of $\Lambda$.
-It was seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only is sufficient to capture the qualitative features of an error-correction simulation, and so we will restrict to pair-creation noise processes in this study for convenience.
-These events act on neighbouring pairs of sites, and so may be associated with an edge of the lattice, chosen uniformly at random at each timestep of the simulation.
-The simulation time, and thus the error-correction threshold, will be measured in terms of average number of noise processes per edge, as opposed to an iid noise probability per edge.
-The latter measure is not appropriate for error processes in nonabelian anyon models, but the two coincide in the limit of low error rates in those cases where they are comparable (see Ref.~\cite{Brell2013}).
+with $\proj{\mathbb{I}}_i$ the projector to charge $\mathbb{I}$ at site $i$, i.e.~the ground 
+space of the model has vacuum (or no anyon) at each site. Given the toroidal boundary 
+conditions, this space is two-fold degenerate as noted above. We identify this ground space 
+as the codespace of our model. Typical realistic noise processes in this kind of system are 
+pair-creation, hopping, exchange etc.~of anyons on neighbouring sites of $\Lambda$. It was 
+seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only 
+is sufficient to capture the qualitative features of an error-correction simulation, and so we 
+will restrict to pair-creation noise processes in this study for convenience. These events act 
+on neighbouring pairs of sites, and so may be associated with an edge of the lattice, chosen 
+uniformly at random at each timestep of the simulation. The simulation time, and thus the 
+error-correction threshold, will be measured in terms of average number of noise processes 
+per edge, as opposed to an iid noise probability per edge. The latter measure is not 
+appropriate for error processes in nonabelian anyon models, but the two coincide in the limit 
+of low error rates in those cases where they are comparable (see Ref.~\cite{Brell2013}).
 
-	In order to perform a logical error on our code, a noise process must have support on a ribbon running around a homologically nontrivial loop of the lattice.
-These correspond to processes in which anyonic charge is transported around the non-trivial loop before annihilating to vacuum.
-More details can be found in Ref.~\cite{?}.
+In order to perform a logical error on our code, a noise process must have support on a 
+ribbon running around a homologically nontrivial loop of the lattice. These correspond to 
+processes in which anyonic charge is transported around the non-trivial loop before 
+annihilating to vacuum. More details can be found in Ref.~\cite{?}.
 
-	Our error-correction algorithm is based on the hard-decision renormalization group (RG) decoders studied in Refs.~\cite{?}.
-Our decoder proceeds by measuring the occupations of anyons at each site of the lattice, forming clusters of nearby anyons and fusing the anyons within each cluster, before iterating at increasing length scales.
-It terminates when the lattice is free of anyons (i.e.~we have returned to the codespace) or the clustering length scale exceeds the total size of the lattice.
-\cggb{A few more details?
-What is our length schedule?} \cggb{How does our decoder relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?} Note that we expect that our qualitative results may be reproduced by most alternative families of decoders, such as matching decoders~\cite{?} and soft-decisions RG decoders~\cite{?} \cggb{do we?}.
-The advantage of using a hard-decision RG decoder is its simplicity and flexibility, and the fact that this simplicity allows for a proof of efficient classical simulability of successful error-correction~\cite{RGsim}.
+Our error-correction algorithm is based on the hard-decision renormalization group (RG) 
+decoders studied in Refs.~\cite{?}. Our decoder proceeds by measuring the occupations of 
+anyons at each site of the lattice, forming clusters of nearby anyons and fusing the anyons 
+within each cluster, before iterating at increasing length scales. It terminates when the lattice 
+is free of anyons (i.e.~we have returned to the codespace) or the clustering length scale 
+exceeds the total size of the lattice. \cggb{A few more details? What is our length schedule?} 
+\cggb{How does our decoder relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?} 
+Note that we expect that our qualitative results may be reproduced by most alternative 
+families of decoders, such as matching decoders~\cite{?} and soft-decisions 
+RG decoders~\cite{?} \cggb{do we?}. The advantage of using a hard-decision RG decoder is 
+its simplicity and flexibility, and the fact that this simplicity allows for a proof of efficient 
+classical simulability of successful error-correction~\cite{RGsim}.
 
@@
 	\includegraphics[width=0.57\columnwidth]{syndrome-2.pdf}
-\caption{The simulation of noise processes proceeds by i) creating pairs of anyons on neighbouring tiles represented by open curves ii) joining the curves within a given tile iii) measuring the total charge on each tile.}
+\caption{The simulation of noise processes proceeds by i) creating pairs of anyons on 
+neighbouring tiles represented by open curves ii) joining the curves within a given tile 
+iii) measuring the total charge on each tile.}
 \label{f:simex}
@@
 
-Although simulating pair creation, braiding, and fusion of $n$ Fibonacci anyons is equivalent in computational power to universal quantum computing (and thus unlikely to be classically tractable), noise processes and error-correction procedures have structure that we can exploit to efficiently simulate typical processes of interest~\cite{RGsim}.
-In particular, those processes in which we expect error-correction to succeed are also those that we expect to be able to efficiently
-simulate for the following heuristic reasons (see Ref.~\cite{RGsim} for a more rigorous analysis).
+Although simulating pair creation, braiding, and fusion of $n$ Fibonacci anyons is equivalent 
+in computational power to universal quantum computing (and thus unlikely to be classically 
+tractable), noise processes and error-correction procedures have structure that we can 
+exploit to efficiently simulate typical processes of interest~\cite{RGsim}. In particular, those 
+processes in which we expect error-correction to succeed are also those that we expect to 
+be able to efficiently simulate for the following heuristic reasons (see Ref.~\cite{RGsim} 
+for a more rigorous analysis).
 
-Below the (bond) percolation threshold for (say) a square lattice, we expect random sets of bonds to decompose into separate clusters of average size $O(\log(n))$ and variance $O(1)$~\cite{Bazant2000}.
-\cggb{Do we want to use the word cluster here again or switch?} Each noise process in our model is associated with a (randomly distributed) edge, and so disconnected clusters correspond to sets of anyons that could not have interacted at any point in their history.
-As such, we can simulate the braiding processes of each cluster separately.
-In other words: the quantum state in the fusion space of all anyons factorizes into a tensor product over bond clusters, and we can compute each factor separately.
-Since each cluster has size only $O(\log(n))$, we can typically simulate these dynamics efficiently because the resulting fusion space has dimension $O(\mathrm{poly}(n))$.
-There are rare random processes that violate this reasoning, but processes such as these are suppressed exponentially in $L$, the lattice size~\cite{Grimmett1989}.
+Below the (bond) percolation threshold for (say) a square lattice, we expect random sets of 
+bonds to decompose into separate clusters of average size $O(\log(n))$ and variance 
+$O(1)$~\cite{Bazant2000}. \cggb{Do we want to use the word cluster here again or switch?} 
+Each noise process in our model is associated with a (randomly distributed) edge, and so 
+disconnected clusters correspond to sets of anyons that could not have interacted at any 
+point in their history. As such, we can simulate the braiding processes of each cluster 
+separately. In other words: the quantum state in the fusion space of all anyons factorizes into 
+a tensor product over bond clusters, and we can compute each factor separately. Since each 
+cluster has size only $O(\log(n))$, we can typically simulate these dynamics efficiently 
+because the resulting fusion space has dimension $O(\mathrm{poly}(n))$. There are rare 
+random processes that violate this reasoning, but processes such as these are suppressed 
+exponentially in $L$, the lattice size~\cite{Grimmett1989}.
 
-However, random noise processes are not the only dynamics that we need to consider.
-We must also consider the effect of the error-correction routine itself.
-This acts iteratively to fuse particles on increasing length scales.
-While this kind of fusion would typically merge clusters, forcing us to compute dynamics of larger and larger sets of anyons, large clusters are sparse (and thus unlikely to be merged), and in addition at each length scale the total number of anyons present is dramatically reduced by fusion, leading to a smaller number of anyons that must be simulated.
+However, random noise processes are not the only dynamics that we need to consider. We 
+must also consider the effect of the error-correction routine itself. This acts iteratively to fuse 
+particles on increasing length scales. While this kind of fusion would typically merge clusters, 
+forcing us to compute dynamics of larger and larger sets of anyons, large clusters are sparse 
+(and thus unlikely to be merged), and in addition at each length scale the total number of 
+anyons present is dramatically reduced by fusion, leading to a smaller number of anyons that 
+must be simulated.
 
-Of course, if we were to consider noise so strong that the clusters percolate over the lattice, we would no longer be able to efficiently simulate the system.
-However, recall that logical errors in our system correspond to processes that act over a non-trivial loop of the torus.
-If the noise operations are so common to have percolated, this is an example of a situation where we expect error-correction \emph{not} to succeed.
-Similarly, if the noise has not yet percolated by itself, but the clusters are merged into a large (percolated) cluster by the decoding algorithm, this is again an example of a process that we expect to correspond to a failure of error-correction.
-In this way, we see that the events that we are able to efficiently simulate correspond precisely to those for which we expect error-correction to succeed.
-We can simply declare failure on non-simulable events.
-This allows us to simulate and demonstrate the success of error-correction schemes for Fibonacci anyons, without explicitly simulating the failure of such schemes.
+Of course, if we were to consider noise so strong that the clusters percolate over the lattice, 
+we would no longer be able to efficiently simulate the system. However, recall that logical 
+errors in our system correspond to processes that act over a non-trivial loop of the torus. If 
+the noise operations are so common to have percolated, this is an example of a situation 
+where we expect error-correction \emph{not} to succeed. Similarly, if the noise has not yet 
+percolated by itself, but the clusters are merged into a large (percolated) cluster by the 
+decoding algorithm, this is again an example of a process that we expect to correspond to a 
+failure of error-correction. In this way, we see that the events that we are able to efficiently 
+simulate correspond precisely to those for which we expect error-correction to succeed. We 
+can simply declare failure on non-simulable events. This allows us to simulate and 
+demonstrate the success of error-correction schemes for Fibonacci anyons, without explicitly 
+simulating the failure of such schemes.
 
@@
 
-	Our concrete simulation proceeds by associating a \emph{tile} with each site of the $L\times L$ periodic square lattice.
-In order to keep track of the observables of the system we maintain a set of disjoint curves, representing the history of anyons on the lattice (these curves can also be thought of as a top-down view of the fusion tree).
-The ends of curves correspond to leaves of the fusion tree, or anyons.
-In general, the curves wind around the two dimensional tiles in a haphazard way determined by the progress of the simulation.
-This allows a dynamically generated basis for the fusion space that easily allows for tensor decomposition into factors corresponding disjoint clusters.
-For comparison, previous work used a single fixed basis for the fusion space (determined by row-major ordering of sites)~\cite{Brell2013}.
+Our concrete simulation proceeds by associating a \emph{tile} with each site of the 
+$L\times L$ periodic square lattice. In order to keep track of the observables of the system 
+we maintain a set of disjoint curves, representing the history of anyons on the lattice (these 
+curves can also be thought of as a top-down view of the fusion tree). The ends of curves 
+correspond to leaves of the fusion tree, or anyons. In general, the curves wind around the two 
+dimensional tiles in a haphazard way determined by the progress of the simulation. This 
+allows a dynamically generated basis for the fusion space that easily allows for tensor 
+decomposition into factors corresponding disjoint clusters. For comparison, previous work 
+used a single fixed basis for the fusion space (determined by row-major ordering of 
+sites)~\cite{Brell2013}.
 
-Each round of simulation proceeds in four steps as follows (an example is shown in \Fref{f:simex}).
+Each round of simulation proceeds in four steps as follows (an example is shown 
+in \Fref{f:simex}).
 
 \begin{enumerate}[i)]
-	\item The noise process is modelled by a sequence of pair-creation events distributed as a Poisson process across each edge.
-Curves are created crossing the relevent edge and terminating on the neighbouring sites.
-	\item We first join curves that participate in the same tile in order to, \cggb{maybe a couple more lines of detail on this and the next point?}
+	\item The noise process is modelled by a sequence of pair-creation events distributed as 
+	a Poisson process across each edge. Curves are created crossing the relevent edge 
+	and terminating on the neighbouring sites.
+	\item We first join curves that participate in the same tile in order to, 
+	\cggb{maybe a couple more lines of detail on this and the next point?}
 	\item measure the charge on each tile. Any resulting anyon is left somewhere in the tile.
-	\item The decoder examines this syndrome and clusters nearby anyons.
-Each cluster is then measured (fused), and the decoder continues to cluster and fuse on larger scales until there are no more anyons, or a cluster includes a non-trivial loop on the lattice.
-Since operators with support on such non-trivial clusters will generally perform an undetectable error on the encoded state, in this case we abandon the simulation and declare failure to error correct.
+	\item The decoder examines this syndrome and clusters nearby anyons. Each cluster 
+	is then measured (fused), and the decoder continues to cluster and fuse on larger 
+	scales until there are no more anyons, or a cluster includes a non-trivial loop on the 
+	lattice. Since operators with support on such non-trivial clusters will generally perform an 
+	undetectable error on the encoded state, in this case we abandon the simulation and 
+	declare failure to error correct.
 \end{enumerate}
@@
 
-	We plot the performance of the decoder as a function of error rate for varying lattice sizes in \Fref{f:threshold}.
-The error rate is parameterized by the Poisson process duration $t_{\mathrm{sim}}$, representing the expected number of errors per edge over the simulation.
-We find evidence of a decoding threshold below which decoding succeeds with asymptotic certainty as the system size increases at $t_{\mathrm{sim}}\simeq 0.125 \pm 0.003$.
+We plot the performance of the decoder as a function of error rate for varying lattice sizes in 
+\Fref{f:threshold}. The error rate is parameterized by the Poisson process duration 
+$t_{\mathrm{sim}}$, representing the expected number of errors per edge over the simulation. 
+We find evidence of a decoding threshold below which decoding succeeds with asymptotic 
+certainty as the system size increases at $t_{\mathrm{sim}}\simeq 0.125 \pm 0.003$.
 
@@
 	\includegraphics[width=\columnwidth]{anyons-kyle.pdf}
-\caption{Decoder failure as a function of simulation time for various lattice sizes, showing threshold behavior around at $t_{\mathrm{sim}}\simeq 0.125$.}
+\caption{Decoder failure as a function of simulation time for various lattice sizes, showing 
+threshold behavior around at $t_{\mathrm{sim}}\simeq 0.125$.}
 \label{f:threshold}
@@
 
-\cggb{Comment on the effect of declaring failure on some simulations on this plot. Would we expect it to change if we simulated every event completely? If so, how?}
+\cggb{Comment on the effect of declaring failure on some simulations on this plot. Would 
+we expect it to change if we simulated every event completely? If so, how?}
 
@@
 
-	We have demonstrated classical simulation of successful error correction in a universal anyon model.
-Though we have chosen several properties of our model and simulation in a convenient way for simplicity, we think it very unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}.
-In particular, although we have modelled our logical qubit as encoded in the global topological degrees of freedom of our system, we could have encoded it in the fusion space of several preferred $\tau$ anyons.
-This situation would be appropriate to model error-correction routines in a topological quantum computation protocol.
-Additionally, we expect our results to be stable to changes in details of the noise model, decoding algorithm, etc.
+We have demonstrated classical simulation of successful error correction in a universal anyon 
+model. Though we have chosen several properties of our model and simulation in a 
+convenient way for simplicity, we think it very unlikely that they will affect the qualitative 
+results, similarly to the results of Ref.~\cite{Brell2013}. In particular, although we have 
+modelled our logical qubit as encoded in the global topological degrees of freedom of our 
+system, we could have encoded it in the fusion space of several preferred $\tau$ anyons. 
+This situation would be appropriate to model error-correction routines in a topological 
+quantum computation protocol. Additionally, we expect our results to be stable to changes 
+in details of the noise model, decoding algorithm, etc.
 
-	None of our techniques are restricted to simulation of Fibonacci anyon dynamics, and could equally well be used to simulate successful error-correction protocols in an arbitrary anyon code.
+None of our techniques are restricted to simulation of Fibonacci anyon dynamics, and could 
+equally well be used to simulate successful error-correction protocols in an arbitrary anyon 
+code.
 
-\cggb{Comment on applicability of our simulation techniques to non-phenomenological models.
-Is it possible that the same ideas could be useful when there is more microscopic detail available, or are they restricted to exactly our phenomenological setup?}
+\cggb{Comment on applicability of our simulation techniques to non-phenomenological 
+models. Is it possible that the same ideas could be useful when there is more microscopic 
+detail available, or are they restricted to exactly our phenomenological setup?}
 
-\stf{Is there a possibility of using MPS like Rob Pfeiffer to improve the simulations or include interactions?}
+\stf{Is there a possibility of using MPS like Rob Pfeiffer to improve the simulations or 
+include interactions?}
 
@@
 
-\cggb {People we chatted to.} This work was supported by the ARC via EQuS project number CE11001013, and by the US Army Research Office grant numbers W911NF-14-1-0098 and W911NF-14-1-0103.
-STF also acknowledges support from an ARC Future Fellowship FT130101744.
-\cggb{CGB funding.}
+\cggb {People we chatted to.} This work was supported by the ARC via 
+EQuS project number CE11001013, and by the US Army Research Office grant numbers 
+W911NF-14-1-0098 and W911NF-14-1-0103. STF also acknowledges support from an 
+ARC Future Fellowship FT130101744. \cggb{CGB funding.}
 
 %------------------------------------------------------------------------------------------------------------%
-%\bibliographystyle{bibstyle}
 \bibliography{refs2}

### 2015-04-05 fib2.tex
Fixed minor typos.

@@
 \usepackage{color}
-\usepackage{amsmath,amsfonts,amssymb,amsthm}
+\usepackage{amsmath,amsfonts,amssymb}
 \usepackage{graphicx}
@@
 \newcommand{\Fref}[1]{Fig.~\ref{#1}}
-\newcommand{\Aref}[1]{Appendix~\ref{#1}}
 
@@
 on neighbouring pairs of sites, and so may be associated with an edge of the lattice, chosen 
-uniformly at random at each timestep of the simulation. The simulation time, and thus the 
+uniformly at random at each time step of the simulation. The simulation time, and thus the 
 error-correction threshold, will be measured in terms of average number of noise processes 
@@
 	\item The noise process is modelled by a sequence of pair-creation events distributed as 
-	a Poisson process across each edge. Curves are created crossing the relevent edge 
+	a Poisson process across each edge. Curves are created crossing the relevant edge 
 	and terminating on the neighbouring sites.

### 2015-04-13 fib2.tex
fixed minor typo and highlighted a sentence for Simon to fix.

@@
 we maintain a set of disjoint curves, representing the history of anyons on the lattice (these 
-curves can also be thought of as a top-down view of the fusion tree). The ends of curves 
+curves can also be thought of as a top-down view of the fusion tree). 
+\stf{this next sentence is currently incorrect.}
+The ends of curves 
 correspond to leaves of the fusion tree, or anyons. In general, the curves wind around the two 
@@
 allows a dynamically generated basis for the fusion space that easily allows for tensor 
-decomposition into factors corresponding disjoint clusters. For comparison, previous work 
+decomposition into factors corresponding to disjoint clusters. For comparison, previous work 
 used a single fixed basis for the fusion space (determined by row-major ordering of 

### 2015-04-14 fib2.tex
mostly edits of the intro, some minor changes in the main text. references still missing though

@@
 support anyons is likely intractable in general because such dynamics are sufficient for 
-universal quantum computation. However, for typical processes of interest for the the study of 
-quantum error correction in anyon systems, the relevant dynamics can in fact be efficiently 
-simulated classically for a wide range of system parameters, even when the underlying anyon 
-model is universal~\cite{RGsim}. We make use of this fact to demonstrate the success of an 
-error-correction protocol for a Fibonacci anyon quantum memory. We numerically simulate a 
-phenomenological model of the system and noise processes on lattice sizes of up to 
+universal quantum computation.
+However, processes of interest for the study of quantum error correction in anyon systems are typically drawn from a restricted class that displays significant structure over a wide range of system parameters.
+We exploit this structure to classically simulate, and thus demonstrate the success of, an error-correction protocol for a quantum memory based on a universal anyon model, the Fibonacci anyons.
+We numerically simulate a phenomenological model of the system and noise processes on lattice sizes of up to
 $128\times128$ sites, and find a lower bound on the error-correction threshold of 
@@
 
-Anyonic excitations in two-dimensional quantum systems~\cite{Wilczek1990} offer 
-tremendous promise for long-term storage and processing of quantum 
-information~\cite{Kitaev2003}. The topological features of quantum systems that support 
-such excitations are insensitive to local 
-perturbations~\cite{Bravyi2010, *Bravyi2011a, *Michalakis2013}, and the excitations 
-themselves can in general be used to perform universal quantum 
-computation~\cite{Freedman2002, *Freedman2002b}.
+Topologically ordered quantum systems in two dimensions offer tremendous promise for long-term storage and processing of quantum 
+information~\cite{Kitaev2003}.
+The topological features of such systems are insensitive to local perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have excitations displaying anyonic statistics~\cite{Wilczek1990}.
+These anyons can in general be used as quantum memories or to perform universal topological quantum computation~\cite{Freedman2002, Freedman2002b, Nayak????}.
 
@@
 ordered systems. When coupled to a heat bath at any finite temperature, thermal fluctuations 
-will create anyons that diffuse and quickly corrupt the stored quantum 
+will create spurious anyons that diffuse and quickly corrupt the stored quantum 
 information~\cite{Pastawski2010}. Thus, the passive protection provided by the mass gap 
-and low temperature must be augmented by an \emph{active} procedure.
+at low temperature must be augmented by an \emph{active} procedure.
 
@@
 well suited to studying quantum error correction because the dynamics of excitations in 
-abelian anyon models can be simulated numerically very efficiently, allowing lattice 
-simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. The ability to 
-efficiently simulate these systems is a consequence of the limitation that abelian anyons 
-cannot be used for universal quantum computation.
+abelian anyon models (at the RG fixed point) can be simulated numerically very efficiently, allowing lattice 
+simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}.
+Standard algorithms to efficiently simulate these systems rely on the abelian nature of these particles, and in particular the fact that abelian anyons cannot be used for quantum computation.
 
 Recent investigations have begun to explore quantum error correction for nonabelian anyon 
-models~\cite{Brell2013, Wootton2013, Hutter2014}. These models are particularly interesting 
-because braiding and fusion of anyons in these models leads in general to universal quantum 
-computation. However, the initial studies have focused on models such as Ising 
+models~\cite{Brell2013, Wootton2013, Hutter2014}. Nonabelian anyon models are particularly interesting 
+because braiding and fusion of these anyons in general allows for the implementation of universal quantum 
+computation. However, the initial studies of error-correction in nonabelian anyon systems have focused on specific models, such as the Ising 
 anyons~\cite{Brell2013} and the so-called $\Phi$-$\Lambda$ 
-model~\cite{Wootton2013, Hutter2014} that, while nonabelian, are not universal, a fact 
-that was exploited to enable efficient classical simulation of error correction in these systems. 
-The remarkable computational power of universal anyon models becomes a liability when we 
-seek to simulate these systems on classical computers.
+model~\cite{Wootton2013, Hutter2014} that, while nonabelian, are not universal. The general dynamics of these particular anyon models is known to be classically simulable, a fact
+that was exploited to enable efficient simulation of error correction in these systems.
+When considering more general anyon models, their ability to perform universal quantum computation would seem a significant barrier to their simulation on a classical computer.
+While simulation of general dynamics does indeed seem intractable, we argue that the kinds of processes that are typical of thermal noise are sufficiently structured to allow for their classical simulation in precisely the regimes where we expect successful error correction to be possible.
+This insight allows us to simulate both noise and error-correction for a quantum code based on a universal anyon model.
 
@@
 
-\stf{Describe main results and why they are badass. cite:~\cite{Bonesteel2012}}
+\stf{cite:~\cite{Bonesteel2012}} \cggb{what is this citation for? something about experimentally relevant in engineered systems?}
+
+We use a flexible phenomenological model of dynamics and thermal noise to describe a system with Fibonacci anyon excitations.
+Within this model, we apply existing general topological error-correction protocols to simulate the successful preservation of quantum information encoded in topological degrees of freedom.
+Topological quantum computation protocols using nonabelian anyons typically implicitly assume the existence of an error-correction protocol to correct for diffusion or unwanted creation of anyons.
+Our results are the first explicit demonstration that such a scheme will be successful when applied to a universal topological quantum computer.
 
@@
 RG decoders~\cite{?} \cggb{do we?}. The advantage of using a hard-decision RG decoder is 
-its simplicity and flexibility, and the fact that this simplicity allows for a proof of efficient 
-classical simulability of successful error-correction~\cite{RGsim}.
+its simplicity and flexibility, and the fact that its clustering scheme does is compatible with the structure in the noise processes that allows us to classically simulate them.
 
@@
 tractable), noise processes and error-correction procedures have structure that we can 
-exploit to efficiently simulate typical processes of interest~\cite{RGsim}. In particular, those 
+exploit to efficiently simulate typical processes of interest. In particular, those 
 processes in which we expect error-correction to succeed are also those that we expect to 
-be able to efficiently simulate for the following heuristic reasons (see Ref.~\cite{RGsim} 
-for a more rigorous analysis).
+be able to efficiently simulate for the following heuristic reasons (we leave a more rigorous analysis of simulability for noise and error correction processes as an open problem).
 
@@
 
-\cggb {People we chatted to.} This work was supported by the ARC via 
-EQuS project number CE11001013, and by the US Army Research Office grant numbers 
-W911NF-14-1-0098 and W911NF-14-1-0103. STF also acknowledges support from an 
-ARC Future Fellowship FT130101744. \cggb{CGB funding.}
+\cggb {People we chatted to.} This work was supported by the ARC via EQuS project number CE11001013, by the US Army Research Office grant numbers W911NF-14-1-0098 and W911NF-14-1-0103, ERC grant QFTCMPS and by the cluster of excellence EXC 201 Quantum Engineering and Space-Time Research.
+STF also acknowledges support from an ARC Future Fellowship FT130101744.
 

### 2015-04-24 fib2.tex
more minor edits, added a couple of references. apart from the comments in the paper that need to be resolved, for me this is a solid draft at this point.

@@
 However, processes of interest for the study of quantum error correction in anyon systems are typically drawn from a restricted class that displays significant structure over a wide range of system parameters.
-We exploit this structure to classically simulate, and thus demonstrate the success of, an error-correction protocol for a quantum memory based on a universal anyon model, the Fibonacci anyons.
+We exploit this structure to classically simulate, and thereby demonstrate the success of, an error-correction protocol for a quantum memory based on the universal Fibonacci anyon model.
 We numerically simulate a phenomenological model of the system and noise processes on lattice sizes of up to
@@
 Topologically ordered quantum systems in two dimensions offer tremendous promise for long-term storage and processing of quantum 
-information~\cite{Kitaev2003}.
+information~\cite{Dennis2002} \cggb{a relevant review reference?}.
 The topological features of such systems are insensitive to local perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have excitations displaying anyonic statistics~\cite{Wilczek1990}.
-These anyons can in general be used as quantum memories or to perform universal topological quantum computation~\cite{Freedman2002, Freedman2002b, Nayak????}.
+These anyons can in general be used as quantum memories or to perform universal topological quantum computation~\cite{Kitaev2003, Freedman2002, Nayak2008}.
 
@@
 Almost all of the sizable research effort on active quantum error correction for topological 
-systems has focused on the case of abelian anyons~\cite{Terhal2014}. These systems are 
+systems has focused on the case of abelian anyons~\cite{Terhal2014} \cggb{revise citations here: poulin decoding stuff, what else?}. These systems are 
 well suited to studying quantum error correction because the dynamics of excitations in 
@@
 system with Fibonacci anyons, a class of nonabelian anyons that are universal for quantum 
-computation~\cite{Wang2010b}. Fibonacci anyons are experimentally motivated as the 
+computation~\cite{Freedman2002, Nayak2008}. Fibonacci anyons are experimentally motivated as the 
 expected excitations of the $\nu=\frac{12}{5}$ fractional quantum Hall 
@@
 modular tensor category~\cite{Wang2010b}. This object contains the data describing the 
-types of anyonic particles, as well as the results of topological operations such as braiding or 
+types of anyonic particles, as well as the results of topological operations such as braiding and 
 fusion of these anyons. The Fibonacci anyon model consists of only one non-trivial particle 
@@
 of combined charge of some number of particles. For details of the description of these 
-processes in Fibonacci anyons, see Ref.~\cite{Trebst2008}. 
-\stf{check that this ref is a good one...} 
+processes in Fibonacci anyons, see e.g.~Ref.~\cite{Nayak2008} and references therein. 
 Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be 
-sufficient to implement universal quantum computation~\cite{?}.
+sufficient to implement universal quantum computation~\cite{Freedman2002, Nayak2008}.
 
@@
 seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only 
-is sufficient to capture the qualitative features of an error-correction simulation, and so we 
-will restrict to pair-creation noise processes in this study for convenience. These events act 
+is sufficient to capture the qualitative features of an error-correction simulation, and so for convenience we 
+will restrict to pair-creation noise processes in the numerical results presented in this study. Such pair-creation events act 
 on neighbouring pairs of sites, and so may be associated with an edge of the lattice, chosen 
@@
 processes in which anyonic charge is transported around the non-trivial loop before 
-annihilating to vacuum. More details can be found in Ref.~\cite{?}.
+annihilating to vacuum.
 
-Our error-correction algorithm is based on the hard-decision renormalization group (RG) 
-decoders studied in Refs.~\cite{?}. Our decoder proceeds by measuring the occupations of 
+Our error-correction algorithm is based on a hard-decision renormalization group (RG) 
+decoder~\cite{Bravyi2011}. The decoder proceeds by measuring the occupations of 
 anyons at each site of the lattice, forming clusters of nearby anyons and fusing the anyons 
@@
 \cggb{How does our decoder relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?} 
-Note that we expect that our qualitative results may be reproduced by most alternative 
-families of decoders, such as matching decoders~\cite{?} and soft-decisions 
+Note that, as was found in Ref.~\cite{Brell2013}, we expect that our qualitative results may be reproduced by most alternative families of decoders, such as matching decoders~\cite{?} and soft-decisions
 RG decoders~\cite{?} \cggb{do we?}. The advantage of using a hard-decision RG decoder is 
-its simplicity and flexibility, and the fact that its clustering scheme does is compatible with the structure in the noise processes that allows us to classically simulate them.
+its simplicity and flexibility, and the fact that its clustering scheme is compatible with the structure in the noise processes that allows us to classically simulate them.
 
@@
 
-Below the (bond) percolation threshold for (say) a square lattice, we expect random sets of 
+Below the (bond) percolation threshold for (say) a 2D square lattice, we expect random sets of 
 bonds to decompose into separate clusters of average size $O(\log(n))$ and variance 
-$O(1)$~\cite{Bazant2000}. \cggb{Do we want to use the word cluster here again or switch?} 
+$O(1)$~\cite{Bazant2000}. \cggb{Do we want to use the word cluster here again or switch? What was our alternative word again?} 
 Each noise process in our model is associated with a (randomly distributed) edge, and so 
@@
 curves can also be thought of as a top-down view of the fusion tree). 
-\stf{this next sentence is currently incorrect.}
+\stf{this next sentence is currently incorrect.} \cggb{Why?}
 The ends of curves 

### 2015-04-27 fib2.tex
yes i am finally thinking about this again

@@
 \newcommand{\cggb}[1]{\textcolor{blue}{#1}}
-\newcommand{\sdb}[1]{\textcolor{red}{#1}}
+\newcommand{\dude}[1]{\textcolor{red}{#1}}
 \newcommand{\stf}[1]{\textcolor{green}{#1}}
@@
 
+\dude{we should stress the distinction between
+simulation the fib dynamics and the simulation of
+the decoder (which is poly by design).. this is something
+that doherty completely missed at first.. the decoder is
+classical and it does not care what anyon system it is
+looking at.}
+
 %------------------------------------------------------------------------------------------------------------%
@@
 We use a phenomenological model of Fibonacci anyon dynamics which neglects any 
-microscopic details of the system. This is consistent with the principles of topologically 
+microscopic details of the system. 
+\dude{Another way of saying this is that we are doing a tqft simulation.}
+This is consistent with the principles of topologically 
 ordered systems and anyonic physics, where the key universal features describing the 
@@
 locally on edges of $\Lambda$. For more details of an analogous model, see~\cite{Brell2013}.
+
+\dude{I really need to see something about observables vs. states. Even if
+we dont mention tqft.}
 
@@
 processes in which anyonic charge is transported around the non-trivial loop before 
-annihilating to vacuum.
+annihilating to vacuum \dude{or not}.
 
 Our error-correction algorithm is based on a hard-decision renormalization group (RG) 
-decoder~\cite{Bravyi2011}. The decoder proceeds by measuring the occupations of 
+decoder~\cite{Bravyi2011}. 
+The decoder proceeds by measuring the occupations of 
 anyons at each site of the lattice, forming clusters of nearby anyons and fusing the anyons 
-within each cluster, before iterating at increasing length scales. It terminates when the lattice 
+within each cluster, before iterating at increasing length scales.
+It terminates when the lattice 
 is free of anyons (i.e.~we have returned to the codespace) or the clustering length scale 
-exceeds the total size of the lattice. \cggb{A few more details? What is our length schedule?} 
+exceeds the total size of the lattice.
+\cggb{A few more details? What is our length schedule?} 
 \cggb{How does our decoder relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?} 
 Note that, as was found in Ref.~\cite{Brell2013}, we expect that our qualitative results may be reproduced by most alternative families of decoders, such as matching decoders~\cite{?} and soft-decisions
-RG decoders~\cite{?} \cggb{do we?}. The advantage of using a hard-decision RG decoder is 
+RG decoders~\cite{?} \cggb{do we?}.
+The advantage of using a hard-decision RG decoder is 
 its simplicity and flexibility, and the fact that its clustering scheme is compatible with the structure in the noise processes that allows us to classically simulate them.
@@
 Our concrete simulation proceeds by associating a \emph{tile} with each site of the 
-$L\times L$ periodic square lattice. In order to keep track of the observables of the system 
-we maintain a set of disjoint curves, representing the history of anyons on the lattice (these 
-curves can also be thought of as a top-down view of the fusion tree). 
-\stf{this next sentence is currently incorrect.} \cggb{Why?}
-The ends of curves 
-correspond to leaves of the fusion tree, or anyons. In general, the curves wind around the two 
-dimensional tiles in a haphazard way determined by the progress of the simulation. This 
-allows a dynamically generated basis for the fusion space that easily allows for tensor 
-decomposition into factors corresponding to disjoint clusters. For comparison, previous work 
+$L\times L$ periodic square lattice.
+In order to keep track of the observables of the system 
+we maintain a set of disjoint curves, representing the history of anyons on the lattice.
+These curves can also be thought of as a top-down view of the fusion tree:
+the anyons on the leaves of the fusion tree are here displayed as points along each curve.
+%The ends of curves correspond to leaves of the fusion tree, or anyons. 
+In general, the curves wind around the two 
+dimensional tiles in a haphazard way determined by the progress of the simulation.
+This allows a dynamically generated basis for the fusion space that easily allows for tensor 
+decomposition into factors corresponding to disjoint clusters.
+For comparison, previous work 
 used a single fixed basis for the fusion space (determined by row-major ordering of 
@@
 \caption{Decoder failure as a function of simulation time for various lattice sizes, showing 
-threshold behavior around at $t_{\mathrm{sim}}\simeq 0.125$.}
+threshold behavior at around $t_{\mathrm{sim}}\simeq 0.125$.}
 \label{f:threshold}
@@
 we expect it to change if we simulated every event completely? If so, how?}
+\dude{you spend alot of effort arguing above that we can
+neglect these occurances, but i am wondering if we need to be
+this strenuous: i did many calculations of global braids/fusions
+and they all do a non-unitary on the logical space.. i could not
+see how to braid around the torus in *any* trivial way *at all*.
+This falls short of a proof, but i'm fairly convinced our sim is
+in fact 100 percent correct.}
 
@@
 include interactions?}
+\dude{Our simulation is effectively doing a contraction of a 2d peps-like network. So
+yeah, maybe there are connections.}
 
@@
 
-\cggb {People we chatted to.} This work was supported by the ARC via EQuS project number CE11001013, by the US Army Research Office grant numbers W911NF-14-1-0098 and W911NF-14-1-0103, ERC grant QFTCMPS and by the cluster of excellence EXC 201 Quantum Engineering and Space-Time Research.
+\cggb {People we chatted to.} 
+This work was supported by the ARC via EQuS project number CE11001013, by the US Army Research Office grant numbers W911NF-14-1-0098 and W911NF-14-1-0103, ERC grant QFTCMPS and by the cluster of excellence EXC 201 Quantum Engineering and Space-Time Research.
 STF also acknowledges support from an ARC Future Fellowship FT130101744.

### 2015-05-05 fib2.tex
correct spelling of "acknowledgments"
minor edits, added some refs.

@@
 support anyons is likely intractable in general because such dynamics are sufficient for 
-universal quantum computation.
-However, processes of interest for the study of quantum error correction in anyon systems are typically drawn from a restricted class that displays significant structure over a wide range of system parameters.
-We exploit this structure to classically simulate, and thereby demonstrate the success of, an error-correction protocol for a quantum memory based on the universal Fibonacci anyon model.
-We numerically simulate a phenomenological model of the system and noise processes on lattice sizes of up to
+universal quantum computation. However, processes of interest for the study of quantum 
+error correction in anyon systems are typically drawn from a restricted class that displays 
+significant structure over a wide range of system parameters.
+We exploit this structure to classically simulate, and thereby demonstrate the success of, an 
+error-correction protocol for a quantum memory based on the universal Fibonacci anyon 
+model.  We numerically simulate a phenomenological model of the system and noise 
+processes on lattice sizes of up to 
 $128\times128$ sites, and find a lower bound on the error-correction threshold of 
@@
 
-Topologically ordered quantum systems in two dimensions offer tremendous promise for long-term storage and processing of quantum 
-information~\cite{Dennis2002} \cggb{a relevant review reference?}.
-The topological features of such systems are insensitive to local perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have excitations displaying anyonic statistics~\cite{Wilczek1990}.
-These anyons can in general be used as quantum memories or to perform universal topological quantum computation~\cite{Kitaev2003, Freedman2002, Nayak2008}.
+Topologically ordered quantum systems in two dimensions offer tremendous promise for 
+long-term storage and processing of quantum information~\cite{Brown2015, Terhal2015}. 
+The topological features of such systems are insensitive to local 
+perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have excitations 
+displaying anyonic statistics~\cite{Wilczek1990}. These anyons can in general be used as 
+quantum memories~\cite{Kitaev2003, Dennis2002} or to perform universal topological 
+quantum computation~\cite{Freedman2002, Nayak2008}.
 
@@
 Almost all of the sizable research effort on active quantum error correction for topological 
-systems has focused on the case of abelian anyons~\cite{Terhal2014} \cggb{revise citations here: poulin decoding stuff, what else?}. These systems are 
+systems has focused on the case of abelian anyons~\cite{Terhal2015} \cggb{revise citations here: poulin decoding stuff~\cite{Duclos-Cianci2010, Duclos-Cianci2010a, Duclos-Cianci2013}, what else?} \stf{Dan Browne's recent work, Bravyi's recent work, Austin Fowler?
+Do we really want to cite everyone that's ever decoded the toric code?}.
+These systems are
 well suited to studying quantum error correction because the dynamics of excitations in 
@@
 a less important (and non-universal) role. As such, we model the system simply as a 
-periodic $L\times L$ square lattice $\Lambda$ of sites with upon which sets of anyons can 
+periodic $L\times L$ square lattice $\Lambda$ of sites upon which sets of anyons can 
 reside. Allowed anyon dynamics (pair-creation, braiding, and fusion) are considered to act 
@@
 %------------------------------------------------------------------------------------------------------------%
-\acknowledgements
+\acknowledgments
 

### 2015-05-06 fib2.tex
Added Refs. Addressed Simon's comment about decoder efficiency.

@@
 Topologically ordered quantum systems in two dimensions offer tremendous promise for 
-long-term storage and processing of quantum information~\cite{Brown2015, Terhal2015}. 
+long-term storage and processing of quantum information~\cite{Kitaev2003, Dennis2002, Nayak2008}. 
 The topological features of such systems are insensitive to local 
-perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have excitations 
+perturbations~\cite{Bravyi2010, *Bravyi2011a, *Michalakis2013}, and have excitations 
 displaying anyonic statistics~\cite{Wilczek1990}. These anyons can in general be used as 
@@
 information~\cite{Pastawski2010}. Thus, the passive protection provided by the mass gap 
-at low temperature must be augmented by an \emph{active} procedure.
+at low temperature must be augmented by an \emph{active} decoding procedure.
 
 Almost all of the sizable research effort on active quantum error correction for topological 
-systems has focused on the case of abelian anyons~\cite{Terhal2015} \cggb{revise citations here: poulin decoding stuff~\cite{Duclos-Cianci2010, Duclos-Cianci2010a, Duclos-Cianci2013}, what else?} \stf{Dan Browne's recent work, Bravyi's recent work, Austin Fowler?
-Do we really want to cite everyone that's ever decoded the toric code?}.
-These systems are
-well suited to studying quantum error correction because the dynamics of excitations in 
-abelian anyon models (at the RG fixed point) can be simulated numerically very efficiently, allowing lattice 
+systems has focused on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Andrist2015}.
+%~\cite{Dennis2002, Duclos-Cianci2010, Bravyi2011, Bravyi2014}.
+While decoding algorithms are generally designed to run efficiently, simulating the physical error correction procedure also requires simulating the dynamics of the noise and recovery processes. 
+Systems of abelian anyons are well suited to studying quantum error correction because (at the RG fixed point) these processes can be efficiently simulated numerically, allowing lattice 
 simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. 
-Standard algorithms to efficiently simulate these systems rely on the abelian nature of these particles, and in particular the fact that abelian anyons cannot be used for quantum computation.
+Standard algorithms are specifically tailored to exploit the abelian nature of these particles, and in particular the fact that abelian anyons cannot be used for quantum computation.
 
@@
 states~\cite{Slingerland2001}, and can also be realized in several spin 
-models~\cite{Levin2005, Kapit2013, Palumbo2014} and composite 
+models~\cite{Levin2005, Bonesteel2012, Kapit2013, Palumbo2014} and composite 
 heterostructures~\cite{Mong2014}.
-
-\stf{cite:~\cite{Bonesteel2012}} \cggb{what is this citation for? something about experimentally relevant in engineered systems?}
 
@@
 Our results are the first explicit demonstration that such a scheme will be successful when applied to a universal topological quantum computer.
-
-\dude{we should stress the distinction between
-simulation the fib dynamics and the simulation of
-the decoder (which is poly by design).. this is something
-that doherty completely missed at first.. the decoder is
-classical and it does not care what anyon system it is
-looking at.}
 
@@
 \stf{Is there a possibility of using MPS like Rob Pfeiffer to improve the simulations or 
-include interactions?}
+include interactions?}~\cite{Pfeifer2010, Pfeifer2012}
+
 \dude{Our simulation is effectively doing a contraction of a 2d peps-like network. So
@@
 
-\cggb {People we chatted to.} 
+We thank A.\ Doherty and R.\ Pfeifer for discussions. 
 This work was supported by the ARC via EQuS project number CE11001013, by the US Army Research Office grant numbers W911NF-14-1-0098 and W911NF-14-1-0103, ERC grant QFTCMPS and by the cluster of excellence EXC 201 Quantum Engineering and Space-Time Research.

### 2015-05-06 fib2.tex
edit on skype with steve. addressed a bunch of comments, added some refs, other minor stuff.

@@
 microscopic details of the system. 
-\dude{Another way of saying this is that we are doing a tqft simulation.}
 This is consistent with the principles of topologically 
@@
 anyon model correspond to large length-scale physics, while the microscopic physics plays 
-a less important (and non-universal) role. As such, we model the system simply as a 
+a less important (and non-universal) role. Effectively, we simulate a topological quantum field theory on a discrete space-time.
+As such, we model the system simply as a 
 periodic $L\times L$ square lattice $\Lambda$ of sites upon which sets of anyons can 
@@
 processes in which anyonic charge is transported around the non-trivial loop before 
-annihilating to vacuum \dude{or not}.
+annihilating to vacuum.
+% cggb{we want to define logical operators as those that map the codespace to itself, so for it to be a logical operator, they must annihilate to vacuum. they need not be unitary}.
 
@@
 \cggb{How does our decoder relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?} 
-Note that, as was found in Ref.~\cite{Brell2013}, we expect that our qualitative results may be reproduced by most alternative families of decoders, such as matching decoders~\cite{?} and soft-decisions
-RG decoders~\cite{?} \cggb{do we?}.
+Note that, as was found in Ref.~\cite{Brell2013}, we expect that our qualitative results may be reproduced by most alternative families of decoders, although it may not be clear in all cases how to extend these decoders to the non-abelian setting.
 The advantage of using a hard-decision RG decoder is 
@@
 \begin{center}
-	{\scriptsize (i)
+	{\scriptsize (a)
 	\includegraphics[width=0.57\columnwidth]{pair-create.pdf}
 	\hskip 4pt
-	(ii)
+	(b)
 	\includegraphics[width=0.57\columnwidth]{syndrome-1.pdf}
 	\hskip 4pt
-	(iii)}
+	(c)}
 	\includegraphics[width=0.57\columnwidth]{syndrome-2.pdf}
-\caption{The simulation of noise processes proceeds by i) creating pairs of anyons on 
-neighbouring tiles represented by open curves ii) joining the curves within a given tile 
-iii) measuring the total charge on each tile.}
+\caption{The simulation of noise processes proceeds by a) creating pairs of anyons on 
+neighbouring tiles represented by open curves b) joining the curves within a given tile 
+c) measuring the total charge on each tile.}
 \label{f:simex}
@@
 Below the (bond) percolation threshold for (say) a 2D square lattice, we expect random sets of 
-bonds to decompose into separate clusters of average size $O(\log(n))$ and variance 
-$O(1)$~\cite{Bazant2000}. \cggb{Do we want to use the word cluster here again or switch? What was our alternative word again?} 
+bonds to decompose into separate clusters~\footnote{Note that we use the word cluster to refer to both groupings of nearby anyons as formed by the decoding algorithm, and also to connected components of a graph under percolation, since both of these usages are standard in the literature.
+This distinction should be kept in mind, though context should remove any ambiguity regarding the meaning.} of average size $O(\log(n))$ and variance
+$O(1)$~\cite{Bazant2000}.
 Each noise process in our model is associated with a (randomly distributed) edge, and so 
@@
 Of course, if we were to consider noise so strong that the clusters percolate over the lattice, 
-we would no longer be able to efficiently simulate the system. However, recall that logical 
+we would no longer expect to be able to efficiently simulate the system. However, recall that logical 
 errors in our system correspond to processes that act over a non-trivial loop of the torus. If 
@@
 percolated by itself, but the clusters are merged into a large (percolated) cluster by the 
-decoding algorithm, this is again an example of a process that we expect to correspond to a 
+decoding algorithm, this is again an example of a process that we expect in general to correspond to a 
 failure of error-correction. In this way, we see that the events that we are able to efficiently 
-simulate correspond precisely to those for which we expect error-correction to succeed. We 
+simulate correspond to those for which we expect error-correction to succeed. We 
 can simply declare failure on non-simulable events. This allows us to simulate and 
@@
 These curves can also be thought of as a top-down view of the fusion tree:
-the anyons on the leaves of the fusion tree are here displayed as points along each curve.
+the anyons comprising the fusion tree are here displayed as points along each curve. \cggb{Is this still true?}
 %The ends of curves correspond to leaves of the fusion tree, or anyons. 
@@
 \item We first join curves that participate in the same tile in order to, 
-\cggb{maybe a couple more lines of detail on this and the next point?}
+\cggb{maybe a couple more lines of detail on this and the next point? perhaps also the previous paragraph?}
 \item measure the charge on each tile. Any resulting anyon is left somewhere in the tile.
@@
 \Fref{f:threshold}. The error rate is parameterized by the Poisson process duration 
-$t_{\mathrm{sim}}$, representing the expected number of errors per edge over the simulation. 
+$t_{\mathrm{sim}}$, representing the expected number of errors per edge during the simulation. 
 We find evidence of a decoding threshold below which decoding succeeds with asymptotic 
@@
 
-\cggb{Do we need to define $t_{\mathrm{sim}}$ more explicitly?}
+%\cggb{Do we need to define $t_{\mathrm{sim}}$ more explicitly?}
 
-\cggb{Comment on the effect of declaring failure on some simulations on this plot. Would 
-we expect it to change if we simulated every event completely? If so, how?}
-\dude{you spend alot of effort arguing above that we can
-neglect these occurances, but i am wondering if we need to be
-this strenuous: i did many calculations of global braids/fusions
-and they all do a non-unitary on the logical space.. i could not
-see how to braid around the torus in *any* trivial way *at all*.
-This falls short of a proof, but i'm fairly convinced our sim is
-in fact 100 percent correct.}
+Although we can guarantee that error-correction will succeed whenever noise does not percolate, it is possible that percolated events may still not result in an error.
+The connection between the percolation threshold and the error-correction threshold is not well understood in general~\cite{Hastings2014}, though it is clear that our threshold estimate will be a lower bound for the true threshold that may have been found if all events (including those that have percolated) were simulated.
+However, by simulating such percolated events on small lattices, our evidence suggests that for the Fibonacci anyon code that we study, the vast majority of such events will result in a logical error.
+As such we feel confident that neglecting such events does not have a significant effect on the threshold value obtained.
 
@@
 quantum computation protocol. Additionally, we expect our results to be stable to changes 
-in details of the noise model, decoding algorithm, etc.
+in details of the noise model, decoding algorithm, and so on.
 
@@
 equally well be used to simulate successful error-correction protocols in an arbitrary anyon 
-code.
+code. As such, our methods could be used to demonstrate successful error-correction in an arbitrary anyonic topological quantum computation.
+
+Applying our methods to more realistic models such as concrete microscopic spin models or models with non-topological features is an open question.
 
@@
 
-\stf{Is there a possibility of using MPS like Rob Pfeiffer to improve the simulations or 
-include interactions?}~\cite{Pfeifer2010, Pfeifer2012}
+\stf{Is there a possibility of using MPS like Rob Pfeifer to improve the simulations or 
+include interactions?}~\cite{Pfeifer2010, Pfeifer2012, Singh2014}
 

### 2015-05-06 fib2.tex
Finished the discussion section.

@@
 Below the (bond) percolation threshold for (say) a 2D square lattice, we expect random sets of 
-bonds to decompose into separate clusters~\footnote{Note that we use the word cluster to refer to both groupings of nearby anyons as formed by the decoding algorithm, and also to connected components of a graph under percolation, since both of these usages are standard in the literature.
-This distinction should be kept in mind, though context should remove any ambiguity regarding the meaning.} of average size $O(\log(n))$ and variance
+bonds to decompose into separate clusters~\footnote{We use the word cluster to refer both to groupings of nearby anyons as formed by the decoding algorithm and to connected components of a graph under percolation, since both of these usages are standard in the literature.
+The intended meaning will remain clear from context.} of average size $O(\log(n))$ and variance
 $O(1)$~\cite{Bazant2000}.
@@
 
-Although we can guarantee that error-correction will succeed whenever noise does not percolate, it is possible that percolated events may still not result in an error.
-The connection between the percolation threshold and the error-correction threshold is not well understood in general~\cite{Hastings2014}, though it is clear that our threshold estimate will be a lower bound for the true threshold that may have been found if all events (including those that have percolated) were simulated.
+We can guarantee that error-correction will succeed whenever noise does not percolate, but it is possible that percolated events may still result in no error.
+The connection between the percolation threshold and the error-correction threshold is not well understood in general~\cite{Hastings2014}, though it is clear that our threshold estimate will be a lower bound for the true threshold that may be found if all events (including those that have percolated) were simulated by an optimal decoder.
 However, by simulating such percolated events on small lattices, our evidence suggests that for the Fibonacci anyon code that we study, the vast majority of such events will result in a logical error.
-As such we feel confident that neglecting such events does not have a significant effect on the threshold value obtained.
+As such it is likely that neglecting such events does not significantly effect our observed threshold value.
 
@@
 system, we could have encoded it in the fusion space of several preferred $\tau$ anyons. 
-This situation would be appropriate to model error-correction routines in a topological 
-quantum computation protocol. Additionally, we expect our results to be stable to changes 
+This situation would be appropriate to model error-correction routines for topological 
+quantum computation. Additionally, we expect our results to be stable to changes 
 in details of the noise model, decoding algorithm, and so on.
@@
 
-Applying our methods to more realistic models such as concrete microscopic spin models or models with non-topological features is an open question.
-
-\cggb{Comment on applicability of our simulation techniques to non-phenomenological 
-models. Is it possible that the same ideas could be useful when there is more microscopic 
-detail available, or are they restricted to exactly our phenomenological setup?}
-
-\stf{Is there a possibility of using MPS like Rob Pfeifer to improve the simulations or 
-include interactions?}~\cite{Pfeifer2010, Pfeifer2012, Singh2014}
-
-\dude{Our simulation is effectively doing a contraction of a 2d peps-like network. So
-yeah, maybe there are connections.}
-
-\cggb{Do we have much more to say?}
+There are several interesting avenues for further research.
+Applying these methods to more realistic models such as concrete microscopic spin models or models with non-topological features would give direct insight into practical error rates needed for topological quantum memories in non-Abelian systems.
+Another potential direction is to incorporate tensor network methods for simulating anyons~\cite{Pfeifer2010, Pfeifer2012, Singh2014} to improve the speed and scale of the simulations.
 

### 2015-05-06 fib2.tex
Minor rewording in the discussion. Moved a citation.

@@
 
+\stf{Cite~\cite{Pfeifer2010} for braiding tricks}
+
 %------------------------------------------------------------------------------------------------------------%
@@
 There are several interesting avenues for further research.
-Applying these methods to more realistic models such as concrete microscopic spin models or models with non-topological features would give direct insight into practical error rates needed for topological quantum memories in non-Abelian systems.
-Another potential direction is to incorporate tensor network methods for simulating anyons~\cite{Pfeifer2010, Pfeifer2012, Singh2014} to improve the speed and scale of the simulations.
+Although it is not completely obvious how to do so, applying these methods to more realistic models such as concrete microscopic spin models or models with non-topological features would give direct insight into practical error rates needed for topological quantum memories in non-Abelian systems.
+Another potential direction is to incorporate tensor network methods for simulating anyons~\cite{Pfeifer2012, Singh2014} to improve the speed and scale of the simulations.
 

### 2015-05-06 fib2.tex
Slight rewording in third paragraph of intro. Added fault-tolerant decoders as an open problem.

@@
 The topological features of such systems are insensitive to local 
-perturbations~\cite{Bravyi2010, *Bravyi2011a, *Michalakis2013}, and have excitations 
+perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have excitations 
 displaying anyonic statistics~\cite{Wilczek1990}. These anyons can in general be used as 
@@
 
-Almost all of the sizable research effort on active quantum error correction for topological 
-systems has focused on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Andrist2015}.
+Decoding algorithms are generally designed to run efficiently, but simulating the physical error-correction procedure also requires simulating the dynamics of the noise and recovery processes. 
+Because of this, almost all of the sizable research effort on active quantum error correction for topological systems has focused on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Fowler2015, Andrist2015}.
 %~\cite{Dennis2002, Duclos-Cianci2010, Bravyi2011, Bravyi2014}.
-While decoding algorithms are generally designed to run efficiently, simulating the physical error correction procedure also requires simulating the dynamics of the noise and recovery processes. 
-Systems of abelian anyons are well suited to studying quantum error correction because (at the RG fixed point) these processes can be efficiently simulated numerically, allowing lattice 
-simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. 
-Standard algorithms are specifically tailored to exploit the abelian nature of these particles, and in particular the fact that abelian anyons cannot be used for quantum computation.
+Systems of abelian anyons are well suited to studying quantum error correction because (at the RG fixed point) noise and recovery processes can be efficiently simulated numerically, allowing lattice simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}.
+Standard algorithms are specifically tailored to exploit the abelian nature of these particles, and specifically that abelian anyons cannot be used for quantum computation.
 
@@
 equally well be used to simulate successful error-correction protocols in an arbitrary anyon 
-code. As such, our methods could be used to demonstrate successful error-correction in an arbitrary anyonic topological quantum computation.
+code. 
+As such, our methods could be used to demonstrate successful error-correction in an arbitrary anyonic topological quantum computation.
 
@@
 Another potential direction is to incorporate tensor network methods for simulating anyons~\cite{Pfeifer2012, Singh2014} to improve the speed and scale of the simulations. 
+Finally, perhaps the most important open question is whether \emph{fault-tolerant} decoders can be designed for nonabelian anyon codes.
 

### 2015-05-13 fib2.tex
Worked with Simon today to try to converge to a final version.
--We are going to add a figure 1(d) and another figure to explain the observables / states thing.
--We use a linear length schedule
--Decided to push some qualitative discussion of the algorithm into the figure caption, but haven't done it yet.

@@
 %------------------------------------------------------------------------------------------------------------%
-\paragraph{Modelling Fibonacci anyons.}
+\paragraph{Modeling Fibonacci anyons.}
 
@@
 as the codespace of our model. Typical realistic noise processes in this kind of system are 
-pair-creation, hopping, exchange etc.~of anyons on neighbouring sites of $\Lambda$. It was 
+pair-creation, hopping, exchange etc.~of anyons on neighboring sites of $\Lambda$. It was 
 seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only 
@@
 will restrict to pair-creation noise processes in the numerical results presented in this study. Such pair-creation events act 
-on neighbouring pairs of sites, and so may be associated with an edge of the lattice, chosen 
+on neighboring pairs of sites, and so may be associated with an edge of the lattice, chosen 
 uniformly at random at each time step of the simulation. The simulation time, and thus the 
@@
 It terminates when the lattice 
-is free of anyons (i.e.~we have returned to the codespace) or the clustering length scale 
-exceeds the total size of the lattice.
-\cggb{A few more details? What is our length schedule?} 
-\cggb{How does our decoder relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?} 
+is free of anyons (i.e.~we have returned to the codespace) or the decoder performs a homologically nontrivial operation, thereby altering the codespace.
+%\cggb{A few more details? What is our length schedule?} 
+%\cggb{How does our decoder relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?} 
 Note that, as was found in Ref.~\cite{Brell2013}, we expect that our qualitative results may be reproduced by most alternative families of decoders, although it may not be clear in all cases how to extend these decoders to the non-abelian setting.
@@
 	{\scriptsize (a)
-	\includegraphics[width=0.57\columnwidth]{pair-create.pdf}
+	\includegraphics[width=0.45\columnwidth]{pair-create.pdf}
 	\hskip 4pt
 	(b)
-	\includegraphics[width=0.57\columnwidth]{syndrome-1.pdf}
+	\includegraphics[width=0.45\columnwidth]{syndrome-1.pdf}
 	\hskip 4pt
-	(c)}
-	\includegraphics[width=0.57\columnwidth]{syndrome-2.pdf}
-\caption{The simulation of noise processes proceeds by a) creating pairs of anyons on 
-neighbouring tiles represented by open curves b) joining the curves within a given tile 
-c) measuring the total charge on each tile.}
+	(c)
+	\includegraphics[width=0.45\columnwidth]{syndrome-2.pdf}
+	\hskip 4pt
+	(d)}
+	\includegraphics[width=0.45\columnwidth]{syndrome-2.pdf}
+\caption{\stf{polish this a bit} The simulation of noise processes proceeds by a) creating pairs of anyons on neighboring tiles represented by open curves b) joining the curves within a given tile c) measuring the total charge on each tile.
+\stf{Add another graph that shows how we use syndrome info.}}
 \label{f:simex}
@@
 
-Of course, if we were to consider noise so strong that the clusters percolate over the lattice, 
-we would no longer expect to be able to efficiently simulate the system. However, recall that logical 
-errors in our system correspond to processes that act over a non-trivial loop of the torus. If 
-the noise operations are so common to have percolated, this is an example of a situation 
-where we expect error-correction \emph{not} to succeed. Similarly, if the noise has not yet 
-percolated by itself, but the clusters are merged into a large (percolated) cluster by the 
-decoding algorithm, this is again an example of a process that we expect in general to correspond to a 
-failure of error-correction. In this way, we see that the events that we are able to efficiently 
-simulate correspond to those for which we expect error-correction to succeed. We 
-can simply declare failure on non-simulable events. This allows us to simulate and 
-demonstrate the success of error-correction schemes for Fibonacci anyons, without explicitly 
-simulating the failure of such schemes.
+Of course, if we were to consider noise so strong that the clusters percolate over the entire lattice, we would no longer expect to be able to efficiently simulate the system for large $L$. 
+However, recall that logical errors in our system correspond to processes that act over a non-trivial loop of the torus. 
+Our simulation remains efficient until the point that we start to create nontrivial loops around the torus, and our simulation declares failure at this point, meaning that we can simulate large lattice sizes in this regime, including up to $L=128$.
 
@@
 \paragraph{Simulation algorithm.}
+
+\stf{Add figure about observables versus states.}
 
@@
 These curves can also be thought of as a top-down view of the fusion tree:
-the anyons comprising the fusion tree are here displayed as points along each curve. \cggb{Is this still true?}
-%The ends of curves correspond to leaves of the fusion tree, or anyons. 
+the anyons comprising the fusion tree are here displayed as points along each curve. 
 In general, the curves wind around the two 
@@
 
-\begin{enumerate}[i)]
-\item The noise process is modelled by a sequence of pair-creation events distributed as 
+\begin{enumerate}[a)]
+\item The noise process is modeled by a sequence of pair-creation events distributed as 
 a Poisson process across each edge. Curves are created crossing the relevant edge 
-and terminating on the neighbouring sites.
+and terminating on the neighboring sites.
 \item We first join curves that participate in the same tile in order to, 
@@
 We plot the performance of the decoder as a function of error rate for varying lattice sizes in 
-\Fref{f:threshold}. The error rate is parameterized by the Poisson process duration 
-$t_{\mathrm{sim}}$, representing the expected number of errors per edge during the simulation. 
+\Fref{f:threshold}. 
+The error rate is parameterized by the Poisson process duration $t_{\mathrm{sim}}$, representing the expected number of errors per edge during the simulation. 
 We find evidence of a decoding threshold below which decoding succeeds with asymptotic 
@@
 	\includegraphics[width=\columnwidth]{anyons-kyle.pdf}
-\caption{Decoder failure as a function of simulation time for various lattice sizes, showing 
+\caption{\stf{polish this a bit} Decoder failure as a function of simulation time for various lattice sizes, showing 
 threshold behavior at around $t_{\mathrm{sim}}\simeq 0.125$.}
@@
 
-%\cggb{Do we need to define $t_{\mathrm{sim}}$ more explicitly?}
-
 We can guarantee that error-correction will succeed whenever noise does not percolate, but it is possible that percolated events may still result in no error. 
 The connection between the percolation threshold and the error-correction threshold is not well understood in general~\cite{Hastings2014}, though it is clear that our threshold estimate will be a lower bound for the true threshold that may be found if all events (including those that have percolated) were simulated by an optimal decoder.
-However, by simulating such percolated events on small lattices, our evidence suggests that for the Fibonacci anyon code that we study, the vast majority of such events will result in a logical error.
-As such it is likely that neglecting such events does not significantly effect our observed threshold value.
+However, calculations of such nontrivial operations suggest that all such processes will indeed result in a logical or leakage error.
+As such it is likely that neglecting full simulation for such events does not significantly effect our observed threshold value.
 
@@
 
-We have demonstrated classical simulation of successful error correction in a universal anyon 
-model. Though we have chosen several properties of our model and simulation in a 
-convenient way for simplicity, we think it very unlikely that they will affect the qualitative 
-results, similarly to the results of Ref.~\cite{Brell2013}. In particular, although we have 
-modelled our logical qubit as encoded in the global topological degrees of freedom of our 
-system, we could have encoded it in the fusion space of several preferred $\tau$ anyons. 
-This situation would be appropriate to model error-correction routines for topological 
-quantum computation. Additionally, we expect our results to be stable to changes 
-in details of the noise model, decoding algorithm, and so on.
+We have demonstrated classical simulation of successful error correction in a universal anyon model. 
+Though we have chosen several properties of our model and simulation in a convenient way for simplicity, we think it very unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}.
+In particular, although we have modeled our logical qubit as encoded in the global topological degrees of freedom of our system, we could have encoded it in the fusion space of several preferred $\tau$ anyons.
+This situation would be appropriate to model error-correction routines for topological quantum computation. 
+Additionally, we expect our results to be stable to changes in details of the noise model, decoding algorithm, and so on.
 

### 2015-05-18 fib2.tex
show braiding and observables

@@
 
+\begin{figure}[th!]
+\begin{center}
+	\includegraphics[width=\columnwidth]{pic-syndrome.pdf}
+\caption{Four equivalent representations of a state,
+along with two syndrome observables marked with solid and dashed lines:
+(a) two pairs are joined in (b).
+Deform the curve straight to get (c),
+then effect some
+braid operations on the state so that (d) the two
+observables are now represented on the curve.
+}
+\label{f:syndrome}
+\end{center}
+\end{figure}
+
 Each round of simulation proceeds in four steps as follows (an example is shown 

### 2015-05-18 render.py

@@ -1,13 +1,35 @@
 #!/usr/bin/env python
 
 import sys
+from math import *
 
-from pyx import canvas, path, deco, trafo, style, text, color
+from pyx import canvas, path, deco, trafo, style, text, color, deformer
 
 text.set(mode="latex") 
 text.set(docopt="12pt")
 #text.preamble(r"\usepackage{amsmath}")
 #text.preamble(r"\
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, rgb(0.75, 0.75, 0)) 
+
+black = rgb(0., 0., 0.) 
+blue = rgb(0., 0., 0.8)
+lred = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.) 
+
+shade = rgb(0.75, 0.55, 0)
+
+light_shade = rgb(0.85, 0.65, 0.1)
+light_shade = rgb(0.9, 0.75, 0.4)
+
+
+
 
 st_dashed = [style.linestyle.dashed]
 st_dotted = [style.linestyle.dotted]
@@ -39,26 +61,211 @@ def harrow(x0, x1, y, extra=[], label=None):
 
 
 
-# -------------------------------------------------
+if 0:
+    # -------------------------------------------------
+    
+    c = canvas.canvas()
+    
+    c.text(0.0, 1.8, "$L_2$", [])
+    c.text(1.8, 1.8, "$D_n$", [])
+    harrow(0.6, 1.8, 2.0, label="$g$")
+    
+    c.text(0.9, 0.0, "$L_n$", [])
+    
+    arrow(0.2, 1.7, 1.0, 0.5)
+    #c.text(0.2, 0.8, "$\subset$", [])
+    c.text(0.2, 0.8, "$i$", [])
+    
+    arrow(1.2, 0.5, 1.9, 1.7)
+    c.text(1.6, 0.8, "$\phi f$", [])
+    
+    c.writeEPSfile("halftwist-factor.eps")
+    
+    # -------------------------------------------------
+
+
+#dashed = [style.linestyle.dashed]
[…]

### 2015-05-20 render.py
tweak figure

@@ -94,16 +94,17 @@ c = canvas.canvas()
 
 
 def anyon(x, y):
-    c.stroke(path.circle(x, y, 0.05), [red, style.linewidth.thick])
+    c.fill(path.circle(x, y, 0.07), [white])
+    c.stroke(path.circle(x, y, 0.07), [red, style.linewidth.thick])
 
-w, h = 2., 2.
+w, h = 1.5, 1.5
 m = 0.1
 
 # --------------------------------------------------------------------
 
 x0, y0 = 0.6, h + 10*m
 
-c.text(x0-0.6, y0, "a)")
+c.text(x0-0.8, y0, "(a)")
 
 c.stroke(path.rect(x0, y0, w, h), dashed)
 c.stroke(path.rect(x0+w+m, y0, w, h), dotted)
@@ -124,7 +125,7 @@ anyon(x0+m+1.2*w, y)
 
 x0, y0 = 0.6, 0.
     
-c.text(x0-0.6, y0, "b)")
+c.text(x0-0.8, y0, "(b)")
 
 c.stroke(path.rect(x0, y0, w, h), dashed)
 c.stroke(path.rect(x0+w+m, y0, w, h), dotted)
@@ -150,6 +151,8 @@ anyon(x0+m+1.2*w, y)
 
 # --------------------------------------------------------------------
 
+w, h = 2., 2.
+
 N = 20
 
 def dopath(ps, extra=[], fill=False, closepath=True):
@@ -161,7 +164,7 @@ def dopath(ps, extra=[], fill=False, closepath=True):
         c.fill(p, [deformer.smoothed(0.3)]+extra+[color.rgb.white])
     c.stroke(p, [deformer.smoothed(0.3)]+extra)
 
-x0, y0 = 3*w + 5*m, -2*m
+x0, y0 = 2.8*w + 0*m, -6*m
 
 dx = w
 dy = 12*m
@@ -195,7 +198,7 @@ perm = [2, 0, 1, 3]
 for i in [0, 1, 2, 3]:
     braid(x0, y0+ys[i], x1, y1+ys[perm[i]])
 
-c.text(x0-1.5, 0, "c)")
+c.text(x0-1.5, 0, "(c)")
 
 
 y2 = y0+0.95*h
@@ -237,7 +240,7 @@ for y in ys:
 
 # --------------------------------------------------------------------
 
-c.text(x0+1.2, 0.5*dy, "d)")
[…]

### 2015-05-20 render.py
add picture of decoder clustering

@@ -2,6 +2,8 @@
 
 import sys
 from math import *
+from random import *
+import numpy
 
 from pyx import canvas, path, deco, trafo, style, text, color, deformer
 
@@ -83,6 +85,166 @@ if 0:
     
     # -------------------------------------------------
 
+def anyon(x, y, r=0.07):
+    c.fill(path.circle(x, y, r), [white])
+    c.stroke(path.circle(x, y, r), [red, style.linewidth.thick])
+
+from qupy.ldpc.solve import parse
+from qupy.braid.tree import Tree
+
+l = 8
+w, h = 0.8, 0.8
+m = 0.05
+
+
+if 1:
+    seed(2)
+    data = numpy.zeros((l, l), dtype=numpy.int32)
+    
+    for count in range(10):
+      if random()<0.5:
+        i = randint(0, l-2)
+        j = randint(0, l-1)
+        data[i, j] += 1
+        data[i+1, j] += 1
+      else:
+        # horizontal
+        i = randint(0, l-1)
+        j = randint(0, l-2)
+        data[i, j] += 1
+        data[i, j+1] += 1
+    
+    for i in range(l):
+      for j in range(l):
+        if data[i,j]>1:
+          if random()<0.5:
+            data[i,j]=0
+          else:
+            data[i,j]=1
+
+else:
+    data = parse("""
+........
+........
+...1....
+...1....
+..1.....
+........
+.11.....
+........
+""")
+
+#print data
+
+data = data[1:, :7]
+l = 7
+
+sites = [(i, j) for i in range(l) for j in range(l)]
+nbd = dict(((i, j), []) for (i, j) in sites)
+for i in range(l):
+  for j in range(l):
+    items = nbd[i, j]
+    if (i+1, j) in nbd:
+        items.append((i+1, j))
+    if (i-1, j) in nbd:
+        items.append((i-1, j))
+    if (i, j+1) in nbd:
+        items.append((i, j+1))
+    if (i, j-1) in nbd:
+        items.append((i, j-1))
+
+
+def join1(clusters):
+    # join clusters using "T_1" separation
+    j = 0
+    while j < len(clusters):
+        cj = clusters[j]
+        for k in range(j+1, len(clusters)):
+            ck = clusters[k]
+            assert len(ck) == 1 
+            for c in cj.sites:
+                if ck.root in nbd[c]:
[…]

### 2015-05-21 render.py
add shading to figure

@@ -26,6 +26,7 @@ lred = rgb(1., 0.4, 0.4)
 white = rgb(1., 1., 1.) 
 
 shade = rgb(0.75, 0.55, 0)
+grey = rgb(0.75, 0.75, 0.75)
 
 light_shade = rgb(0.85, 0.65, 0.1)
 light_shade = rgb(0.9, 0.75, 0.4)
@@ -200,13 +201,34 @@ def coord(i, j):
 
 def draw(dx=0., dy=0.):
 
+    r = 4.*m
     data1 = data.copy()
+    lines = []
     for tree in trees:
       for p0 in tree.sites:
+        x0, y0 = coord(*p0)
+        c.fill(path.circle(x0+dx, y0+dy, r), [grey])
         p1 = tree.parent[p0]
-        print p0, p1
+        #print p0, p1
         if p1 is None:
             continue # root
+        lines.append((p0, p1))
+
+        x1, y1 = coord(*p1)
+        #data1[p0] = 0
+        #c.stroke(path.line(x0+dx, y0+dy, x1+dx, y1+dy),
+        #    [style.linewidth.Thick, deco.earrow(size=0.3)])
+
+        if x0==x1:
+            c.fill(path.rect(x0-r+dx, y0+dy, 2*r, y1-y0), [grey])
+        else:
+            c.fill(path.rect(x0+dx, y0-r+dy, x1-x0, 2*r), [grey])
+        c.fill(path.circle(x0+dx, y0+dy, r), [grey])
+        c.fill(path.circle(x1+dx, y1+dy, r), [grey])
+        #c.stroke(path.line(x0+dx, y0+dy, x1+dx, y1+dy),
+        #    [style.linewidth.THICK, style.linecap.round, grey])
+
+    for (p0, p1) in lines:
         x0, y0 = coord(*p0)
         x1, y1 = coord(*p1)
         data1[p0] = 0

### 2015-05-26 fib2.tex
add picture of decoder clustering
remove figure

@@
 \documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
+%\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4}
 \usepackage{times}
@@
 
-\begin{figure*}[th!]
-\begin{center}
-	{\scriptsize (a)
-	\includegraphics[width=0.45\columnwidth]{pair-create.pdf}
-	\hskip 4pt
-	(b)
-	\includegraphics[width=0.45\columnwidth]{syndrome-1.pdf}
-	\hskip 4pt
-	(c)
-	\includegraphics[width=0.45\columnwidth]{syndrome-2.pdf}
-	\hskip 4pt
-	(d)}
-	\includegraphics[width=0.45\columnwidth]{syndrome-2.pdf}
-\caption{\stf{polish this a bit} The simulation of noise processes proceeds by a) creating pairs of anyons on neighboring tiles represented by open curves b) joining the curves within a given tile c) measuring the total charge on each tile.
+%\begin{figure*}[th!]
+%\begin{center}
+%	{\scriptsize (a)
+%	\includegraphics[width=0.45\columnwidth]{pair-create.pdf}
+%	\hskip 4pt
+%	(b)
+%	\includegraphics[width=0.45\columnwidth]{syndrome-1.pdf}
+%	\hskip 4pt
+%	(c)
+%	\includegraphics[width=0.45\columnwidth]{syndrome-2.pdf}
+%	\hskip 4pt
+%	(d)}
+%	\includegraphics[width=0.45\columnwidth]{syndrome-2.pdf}
+%\caption{\stf{polish this a bit} The simulation of noise processes proceeds by a) creating pairs of anyons on neighboring tiles represented by open curves b) joining the curves within a given tile c) measuring the total charge on each tile.
 \stf{Add another graph that shows how we use syndrome info.}}
-\label{f:simex}
-\end{center}
-\end{figure*}
+%\label{f:simex}
+%\end{center}
+%\end{figure*}
 
@@
 
-\stf{Add figure about observables versus states.}
+%\stf{Add figure about observables versus states.}
 
@@
 
-Each round of simulation proceeds in four steps as follows (an example is shown 
-in \Fref{f:simex}).
+\begin{figure}[th!]
+\begin{center}
+	\includegraphics[width=\columnwidth]{pic-decode.pdf}
+\caption{The decoder works by maintaining a set of disjoint clusters (rooted trees).}
+\label{f:decode}
+\end{center}
+\end{figure}
 
-\begin{enumerate}[a)]
-\item The noise process is modeled by a sequence of pair-creation events distributed as 
-a Poisson process across each edge. Curves are created crossing the relevant edge 
-and terminating on the neighboring sites.
-\item We first join curves that participate in the same tile in order to, 
-\cggb{maybe a couple more lines of detail on this and the next point? perhaps also the previous paragraph?}
-\item measure the charge on each tile. Any resulting anyon is left somewhere in the tile.
-\item The decoder examines this syndrome and clusters nearby anyons. Each cluster 
-is then measured (fused), and the decoder continues to cluster and fuse on larger 
-scales until there are no more anyons, or a cluster includes a non-trivial loop on the 
-lattice. Since operators with support on such non-trivial clusters will generally perform an 
-undetectable error on the encoded state, in this case we abandon the simulation and 
-declare failure to error correct.
-\end{enumerate}
+%Each round of simulation proceeds in four steps as follows (an example is shown 
+%in \Fref{f:simex}).
+%
+%\begin{enumerate}[a)]
+%\item The noise process is modeled by a sequence of pair-creation events distributed as 
+%a Poisson process across each edge. Curves are created crossing the relevant edge 
+%and terminating on the neighboring sites.
+%\item We first join curves that participate in the same tile in order to, 
+%\cggb{maybe a couple more lines of detail on this and the next point? perhaps also the previous paragraph?}
+%\item measure the charge on each tile. Any resulting anyon is left somewhere in the tile.
+%\item The decoder examines this syndrome and clusters nearby anyons. Each cluster 
+%is then measured (fused), and the decoder continues to cluster and fuse on larger 
+%scales until there are no more anyons, or a cluster includes a non-trivial loop on the 
+%lattice. Since operators with support on such non-trivial clusters will generally perform an 
+%undetectable error on the encoded state, in this case we abandon the simulation and 
+%declare failure to error correct.
+%\end{enumerate}
 

### 2015-05-27 fib2.tex
many minor edits, plus included some R- and F- move diagrams, clarified a few technical points, and made comments on figures

@@
 
-%\usepackage{tikz}
-%\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit}
-%\usepackage{epstopdf} % to include .eps graphics files with pdfLaTeX
+\usepackage{tikz}
+\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit}
+\usepackage{epstopdf} % to include .eps graphics files with pdfLaTeX
 %\usepackage{bm}  % Define \bm{} to use bold math fonts
@@
 
-\newcommand{\eps}{\epsilon}
+\newcommand{\e}{\mathrm{e}}
 
@@
 Classically simulating the dynamics of excitations in two-dimensional quantum systems that 
-support anyons is likely intractable in general because such dynamics are sufficient for 
+support anyons is likely intractable in general because such dynamics are sufficient to implement 
 universal quantum computation. However, processes of interest for the study of quantum 
@@
 
-Topologically ordered quantum systems in two dimensions offer tremendous promise for 
+Topologically ordered quantum systems in two dimensions show tremendous promise for 
 long-term storage and processing of quantum information~\cite{Kitaev2003, Dennis2002, Nayak2008}. 
 The topological features of such systems are insensitive to local 
-perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have excitations 
-displaying anyonic statistics~\cite{Wilczek1990}. These anyons can in general be used as 
+perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have quasiparticle excitations 
+exhibiting anyonic statistics~\cite{Wilczek1990}. These systems can in general be used as 
 quantum memories~\cite{Kitaev2003, Dennis2002} or to perform universal topological 
@@
 
-Quantum error correction is vital to harnessing the computational power of these topologically 
+Quantum error correction is vital to harnessing the computational power of topologically 
 ordered systems. When coupled to a heat bath at any finite temperature, thermal fluctuations 
@@
 
-Decoding algorithms are generally designed to run efficiently, but simulating the physical error-correction procedure also requires simulating the dynamics of the noise and recovery processes. 
+In order to efficiently classically simulate an error-correction protocol for a topologically ordered quantum memory, it is necessary to simulate the physical noise processes, the decoding algorithm, and the physical recovery operations.
+Decoding algorithms are typically designed to run efficiently on a classical computer, but there is generally no guarantee that the noise and recovery processes should be classically simulable.
 Because of this, almost all of the sizable research effort on active quantum error correction for topological systems has focused on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Fowler2015, Andrist2015}.
@@
 Systems of abelian anyons are well suited to studying quantum error correction because (at the RG fixed point) noise and recovery processes can be efficiently simulated numerically, allowing lattice simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}.
-Standard algorithms are specifically tailored to exploit the abelian nature of these particles, and specifically that abelian anyons cannot be used for quantum computation.
+Standard algorithms are specifically tailored to exploit the abelian nature of these particles, particularly that abelian anyons cannot be used for quantum computation.
 
 Recent investigations have begun to explore quantum error correction for nonabelian anyon 
-models~\cite{Brell2013, Wootton2013, Hutter2014}. Nonabelian anyon models are particularly interesting 
+models~\cite{Brell2013, Wootton2013, Hutter2014}. Nonabelian anyon models are especially interesting 
 because braiding and fusion of these anyons in general allows for the implementation of universal quantum 
@@
 anyons~\cite{Brell2013} and the so-called $\Phi$-$\Lambda$ 
-model~\cite{Wootton2013, Hutter2014} that, while nonabelian, are not universal. The general dynamics of these particular anyon models is known to be classically simulable, a fact
+model~\cite{Wootton2013, Hutter2014} that, while nonabelian, are not universal. The general dynamics of these particular anyon models is known to be efficiently classically simulable, a fact
 that was exploited to enable efficient simulation of error correction in these systems.
 When considering more general anyon models, their ability to perform universal quantum computation would seem a significant barrier to their simulation on a classical computer.
-While simulation of general dynamics does indeed seem intractable, we argue that the kinds of processes that are typical of thermal noise are sufficiently structured to allow for their classical simulation in precisely the regimes where we expect successful error correction to be possible.
-This insight allows us to simulate both noise and error-correction for a quantum code based on a universal anyon model.
+While simulation of general dynamics does indeed seem intractable, we argue that the kinds of processes that are typical of thermal noise are sufficiently structured to allow for their classical simulation in the regimes where we expect successful error correction to be possible.
+This insight allows us to simulate the noise and recovery processes for a quantum code based on a universal anyon model.
 
-Here we consider a full simulation of quantum error correction in a two-dimensional lattice 
+Concretely, we consider the simulation of quantum error correction in a two-dimensional lattice 
 system with Fibonacci anyons, a class of nonabelian anyons that are universal for quantum 
@@
 We use a flexible phenomenological model of dynamics and thermal noise to describe a system with Fibonacci anyon excitations.
-Within this model, we apply existing general topological error-correction protocols to simulate the successful preservation of quantum information encoded in topological degrees of freedom.
+Within this model, we apply existing general topological error-correction protocols, and simulate the successful preservation of quantum information encoded in topological degrees of freedom.
 Topological quantum computation protocols using nonabelian anyons typically implicitly assume the existence of an error-correction protocol to correct for diffusion or unwanted creation of anyons.
@@
 that enlarge the fusion space, while fusion events correspond to projective measurements 
-of combined charge of some number of particles. For details of the description of these 
+of combined charge of some number of particles. For detailed description of these 
 processes in Fibonacci anyons, see e.g.~Ref.~\cite{Nayak2008} and references therein. 
@@
 sufficient to implement universal quantum computation~\cite{Freedman2002, Nayak2008}.
+
+The dynamics and history of a system of anyons can be conveniently represented by a graphical calculus, which can be regarded as a representation of the world-lines of the particles.
+These diagrams can be manipulated by $R$-moves, corresponding to braiding processes:
+	\begin{align}
+		\begin{tikzpicture}[baseline=0.5cm,scale=0.33]		
+			\draw(0,0)--(0,1);
+			\draw plot [smooth, tension=1] coordinates { (0,1) (0.75,1.8) (-0.6,2.45) (-1,3)};
+			\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
+			\draw plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
+			\node at (0,0) [anchor=north] {$c$};
+			\node at (-1,3) [anchor=south] {$b$};
+			\node at (1,3) [anchor=south] {$a$};
+		\end{tikzpicture}
+		&\;\;=\;\;R^{ab}_c\cdot\;
+		\begin{tikzpicture}[baseline=0.5cm,scale=0.33]		
+			\draw(0,0)--(0,1);
+			\draw(0,1)--(-1,2)--(-1,3);
+			\draw(0,1)--(1,2)--(1,3);
+			\node at (0,0) [anchor=north] {$c$};
+			\node at (-1,3) [anchor=south] {$b$};
+			\node at (1,3) [anchor=south] {$a$};
+		\end{tikzpicture}
+	\end{align}
+where $a$, $b$, and $c$ represent particle types, or $F$-moves, representing the associativity rule for fusion processes, denoted as
+	\begin{align}
+		\begin{tikzpicture}[baseline=0.6cm,scale=0.4]
+			\draw(0,0)--(0,1)--(-2,3);
+			\draw(0,3)--(-1,2);
+			\draw(2,3)--(0,1);
+			\node at (-0.45,1.6) [anchor=north east] {$i$};
+			\node at (0,0) [anchor=north] {$d$};
+			\node at (2,3) [anchor=south] {$c$};
+			\node at (0,3) [anchor=south] {$b$};
+			\node at (-2,3) [anchor=south] {$a$};
+		\end{tikzpicture}
+		&\;\;=\;\;\sum_j[F^{abc}_d]_{ij}\cdot\;
+		\begin{tikzpicture}[baseline=0.6cm,scale=0.4]		
+			\draw(0,0)--(0,1)--(-2,3);
+			\draw(0,3)--(1,2);
+			\draw(2,3)--(0,1);
+			\node at (0.42,1.63) [anchor=north west] {$j$};
+			\node at (0,0) [anchor=north] {$d$};
+			\node at (2,3) [anchor=south] {$c$};
+			\node at (0,3) [anchor=south] {$b$};
+			\node at (-2,3) [anchor=south] {$a$};
+		\end{tikzpicture}
+	\end{align}
+
+These manipulations encode the data of the unitary modular tensor category, and can be used to represent the state of a system of anyons as a linear combination of fusion trees.
+For the Fibonacci anyons, the non-trivial $R$ and $F$ moves are given by
+\begin{align}
+	R_{\mathbb{I}}^{\tau\tau}&= \e^{\frac{-4\pi i}{5}}\qquad R_\tau^{\tau\tau}= \e^{\frac{3\pi i}{5}}\\
+	F_{\tau}^{\tau\tau\tau} &= \begin{pmatrix}\varphi^{-1}&\varphi^{-\frac{1}{2}}\\\varphi^{-\frac{1}{2}}&-\varphi^{-1}\end{pmatrix} \,,
+\end{align}
+where in the last expression, $\varphi=\frac{1+\sqrt{5}}{2}$ is the golden ratio, and the matrix is given in a basis labelled $(\mathbb{I},\tau)$.
 
@@
 anyon model correspond to large length-scale physics, while the microscopic physics plays 
-a less important (and non-universal) role. Effectively, we simulate a topological quantum field theory on a discrete space-time.
+a less important (and non-universal) role. Effectively, we simulate a $(2+1)$-dimensional topological quantum field theory on a discrete space-time.
 As such, we model the system simply as a 
@@
 anyons at each site of the lattice, forming clusters of nearby anyons and fusing the anyons 
-within each cluster, before iterating at increasing length scales.
+within each cluster, before iterating at linearly increasing length scales.
 It terminates when the lattice 
-is free of anyons (i.e.~we have returned to the codespace) or the decoder performs a homologically nontrivial operation, thereby altering the codespace.
+is free of anyons (i.e.~we have returned to the codespace) or the clustering length scale exceeds the size of the lattice.
+%the decoder performs a homologically nontrivial operation, thereby altering the codespace.
+%\cggb{our simulation may terminate when the decoder performs a nontrivial operation, but here we're just describing the decoder, which can't know that.}
 %\cggb{A few more details? What is our length schedule?} 
@@
 disconnected clusters correspond to sets of anyons that could not have interacted at any 
-point in their history. As such, we can simulate the braiding processes of each cluster 
+point in their history.
+Although normally anyons can interact by braiding without ever coming into contact with one another, in this case charge conservation implies that each distinct cluster must have trivial total charge, and so all such interactions are trivial.
+This allows us to simulate the braiding processes within each cluster 
 separately. In other words: the quantum state in the fusion space of all anyons factorizes into 
@@
 random processes that violate this reasoning, but processes such as these are suppressed 
-exponentially in $L$, the lattice size~\cite{Grimmett1989}.
+exponentially in the lattice size $L$\cite{Grimmett1989}.
 
@@
 particles on increasing length scales. While this kind of fusion would typically merge clusters, 
-forcing us to compute dynamics of larger and larger sets of anyons, large clusters are sparse 
+forcing us to compute dynamics of larger and larger sets of anyons, large clusters are sparsely distributed 
 (and thus unlikely to be merged), and in addition at each length scale the total number of 
@@
 
-Of course, if we were to consider noise so strong that the clusters percolate over the entire lattice, we would no longer expect to be able to efficiently simulate the system for large $L$. 
+Of course, if we were to consider noise so strong that the clusters percolate over the entire lattice, we would no longer expect to be able to efficiently simulate the noise and recovery processes in the system.
 However, recall that logical errors in our system correspond to processes that act over a non-trivial loop of the torus. 
-Our simulation remains efficient until the point that we start to create nontrivial loops around the torus, and our simulation declares failure at this point, meaning that we can simulate large lattice sizes in this regime, including up to $L=128$.
+Our simulation remains efficient until the point that we start to create nontrivial loops around the torus, and our simulation begins to declare failure whenever non-trivial logical operations occur, meaning that we can simulate large lattice sizes in the successful error-correction (sub-percolated) regime, including up to $L=128$.
 
@@
 observables are now represented on the curve.
-}
+\cggb{I'm not totally clear on what I'm looking at here.
+Is this the diagram where we want to explain the whole simulation algorithm?
+Is the idea that we start with a), which is given by the set of noise processes that have happened, then we connect stuff up arbitrarily into b) to make some fusion tree.
+Then c) is what's happening after linearizing the picture?
+And d) is c) after some R and F moves so you go into the standard basis for the fusion tree?
+Are the red lines between c) and d) just denoting leaves with the same identity or do they have some more precise meaning wrt the braid moves that relate c) and d)?}}
 \label{f:syndrome}
@@
 	\includegraphics[width=\columnwidth]{pic-decode.pdf}
-\caption{The decoder works by maintaining a set of disjoint clusters (rooted trees).}
+\caption{The decoder works by maintaining a set of disjoint clusters (rooted trees).
+\cggb{Is this diagram where we want to explain the decoding algorithm?
+Is part a) round one of clustering and part b) round 2 of clustering?
+Do the arrow directions just denote the direction stuff goes when we try to fuse it all together or does it have some deeper meaning?}}
 \label{f:decode}
@@
 However, calculations of such nontrivial operations suggest that all such processes will indeed result in a logical or leakage error.
-As such it is likely that neglecting full simulation for such events does not significantly effect our observed threshold value.
+As such it is likely that neglecting full simulation for such events does not significantly affect our observed threshold value.
 
@@
 We have demonstrated classical simulation of successful error correction in a universal anyon model. 
-Though we have chosen several properties of our model and simulation in a convenient way for simplicity, we think it very unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}.
+Though we have chosen several properties of our model and simulation in a convenient way for simplicity, it seems highly unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}.
 In particular, although we have modeled our logical qubit as encoded in the global topological degrees of freedom of our system, we could have encoded it in the fusion space of several preferred $\tau$ anyons.
 This situation would be appropriate to model error-correction routines for topological quantum computation. 
-Additionally, we expect our results to be stable to changes in details of the noise model, decoding algorithm, and so on.
+Additionally, we expect our results to be stable to changes in details of the noise model and decoding algorithm.
 

### 2015-05-27 fib2.tex
trivial changes.

@@
 \documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
-%\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4}
 \usepackage{times}
@@
 random processes that violate this reasoning, but processes such as these are suppressed 
-exponentially in the lattice size $L$\cite{Grimmett1989}.
+exponentially in the lattice size $L$~\cite{Grimmett1989}.
 

### 2015-05-31 fib2.tex
edits. add a ref.

--- 2015-05-27 fib2.tex
@@
 
-\usepackage{tikz}
-\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit}
+%\usepackage{tikz}
+%\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit}
+
 \usepackage{epstopdf} % to include .eps graphics files with pdfLaTeX
@@
 
+\dude{these equations are too big... i was hoping for something tight, like
+in http://arxiv.org/abs/1504.02868
+any ideas? i might just generate a bunch of little pdf's...
+}
+
 These manipulations encode the data of the unitary modular tensor category, and can be used to represent the state of a system of anyons as a linear combination of fusion trees.
@@
 anyon model correspond to large length-scale physics, while the microscopic physics plays 
-a less important (and non-universal) role. Effectively, we simulate a $(2+1)$-dimensional topological quantum field theory on a discrete space-time.
-As such, we model the system simply as a 
-periodic $L\times L$ square lattice $\Lambda$ of sites upon which sets of anyons can 
-reside. Allowed anyon dynamics (pair-creation, braiding, and fusion) are considered to act 
-locally on edges of $\Lambda$. For more details of an analogous model, see~\cite{Brell2013}.
-
-\dude{I really need to see something about observables vs. states. Even if
-we dont mention tqft.}
+a less important (and non-universal) role.
+We simulate a $(2+1)$-dimensional topological quantum field theory.
+%Effectively, we simulate a $(2+1)$-dimensional topological quantum field theory on a discrete space-time.
+%As such, we model the system simply as a 
+%periodic $L\times L$ square lattice $\Lambda$ of sites upon which sets of anyons can 
+%reside. 
+%Allowed anyon dynamics (pair-creation, braiding, and fusion) are considered to act 
+%locally on edges of $\Lambda$. 
+%For more details of an analogous model, see~\cite{Brell2013}.
+\dude{something about observables vs. states.}
 
@@
 is sufficient to capture the qualitative features of an error-correction simulation, and so for convenience we 
-will restrict to pair-creation noise processes in the numerical results presented in this study. Such pair-creation events act 
-on neighboring pairs of sites, and so may be associated with an edge of the lattice, chosen 
+will restrict to pair-creation noise processes in the numerical results presented in this study. 
+Such pair-creation events act on neighboring pairs of sites,
+and so may be associated with an edge of the lattice, chosen 
 uniformly at random at each time step of the simulation. The simulation time, and thus the 
@@
 
-Our error-correction algorithm is based on a hard-decision renormalization group (RG) 
-decoder~\cite{Bravyi2011}. 
+Our error-correction algorithm is
+based on a heirarchical clustering algorithm~\cite{Hastie2009},
+and has some 
+similarities to the hard-decision renormalization group (RG) decoder~\cite{Bravyi2011}. 
 The decoder proceeds by measuring the occupations of 
-anyons at each site of the lattice, forming clusters of nearby anyons and fusing the anyons 
-within each cluster, before iterating at linearly increasing length scales.
-It terminates when the lattice 
-is free of anyons (i.e.~we have returned to the codespace) or the clustering length scale exceeds the size of the lattice.
-%the decoder performs a homologically nontrivial operation, thereby altering the codespace.
+anyons at each site of the lattice, forming clusters of nearby anyons and 
+%fusing the anyons within each cluster. 
+measureing the total charge within each cluster.
+Clusters with trivial charge are discarded, and
+the rest are joined (agglomeratively~\cite{Hastie2009})
+at linearly increasing length scales.
+See FIG. \ref{f:decode}.
+Note that unlike the abelian case, the decoder
+cannot know the charge of each cluster based only
+on the syndrome information (as in \cite{Bravyi2011}),
+and so will query (measure) the system to find this.
+The simulation proceeds in this way as a dialogue between decoder
+and system, terminating when the lattice 
+is free of anyons (i.e.~we have returned to the codespace) 
+or the decoder performs a homologically nontrivial operation, thereby altering the codespace.
+%or the clustering length scale exceeds the size of the lattice.
 %\cggb{our simulation may terminate when the decoder performs a nontrivial operation, but here we're just describing the decoder, which can't know that.}
+%\dude{in our sim the decoder stops when there is one cluster. Ie., it never gives up.}
 %\cggb{A few more details? What is our length schedule?} 
@@
 Note that, as was found in Ref.~\cite{Brell2013}, we expect that our qualitative results may be reproduced by most alternative families of decoders, although it may not be clear in all cases how to extend these decoders to the non-abelian setting.
-The advantage of using a hard-decision RG decoder is 
+The advantage of using a hard-decision decoder is 
 its simplicity and flexibility, and the fact that its clustering scheme is compatible with the structure in the noise processes that allows us to classically simulate them.
+
+\begin{figure}[th!]
+\begin{center}
+	\includegraphics[width=1.0\columnwidth]{pic-decode.eps}
+\caption{The decoder works by maintaining a set of disjoint clusters as rooted trees.
+(a) Trees are formed from neighboring sites that contain a charge.
+(b) For each successive round, we grow all trees, 
+and overlapping trees are joined to form
+a single tree. Arrows denote movement of charge to the root of the tree.
+The root of each tree is chosen arbitrarily.
+}
+\label{f:decode}
+\end{center}
+\end{figure}
 
@@
 Below the (bond) percolation threshold for (say) a 2D square lattice, we expect random sets of 
-bonds to decompose into separate clusters~\footnote{We use the word cluster to refer both to groupings of nearby anyons as formed by the decoding algorithm and to connected components of a graph under percolation, since both of these usages are standard in the literature.
-The intended meaning will remain clear from context.} of average size $O(\log(n))$ and variance
+bonds to decompose into separate clusters~\footnote{
+We use the word cluster to refer both to groupings 
+of nearby anyons as formed by the decoding algorithm and 
+to connected components of a graph under percolation\dude{confusing}, since both 
+of these usages are standard in the literature. The intended 
+meaning will remain clear from context.} of average size $O(\log(n))$ and variance 
 $O(1)$~\cite{Bazant2000}.
@@
 point in their history. 
-Although normally anyons can interact by braiding without ever coming into contact with one another, in this case charge conservation implies that each distinct cluster must have trivial total charge, and so all such interactions are trivial.
+Although normally anyons can interact by braiding without ever coming 
+into contact with one another \dude{um um um}, in this case charge conservation 
+implies that each distinct cluster must have trivial total charge, and so all such interactions are trivial.
 This allows us to simulate the braiding processes within each cluster 
@@
 
-Of course, if we were to consider noise so strong that the clusters percolate over the entire lattice, we would no longer expect to be able to efficiently simulate the noise and recovery processes in the system.
+Of course, if we were to consider noise so strong that 
+the clusters percolate over the entire lattice, we would no 
+longer expect to be able to efficiently simulate the noise and recovery processes in the system. 
 However, recall that logical errors in our system correspond to processes that act over a non-trivial loop of the torus. 
-Our simulation remains efficient until the point that we start to create nontrivial loops around the torus, and our simulation begins to declare failure whenever non-trivial logical operations occur, meaning that we can simulate large lattice sizes in the successful error-correction (sub-percolated) regime, including up to $L=128$.
+Our simulation remains efficient \dude{efficiency has nothing to do with it}
+until the point that we start to create nontrivial loops around the torus, 
+and our simulation begins to declare failure whenever non-trivial logical 
+operations occur, meaning that we can simulate large lattice sizes 
+in the successful error-correction (sub-percolated) regime, including up to $L=128$.
 
@@
 This allows a dynamically generated basis for the fusion space that easily allows for tensor 
-decomposition into factors corresponding to disjoint clusters.
+decomposition into factors corresponding 
+to disjoint clusters \dude{confusing use of this word}.
 For comparison, previous work 
@@
 \begin{center}
-	\includegraphics[width=\columnwidth]{pic-syndrome.pdf}
+	\includegraphics[width=1.0\columnwidth]{pic-syndrome.eps}
 \caption{Four equivalent representations of a state,
@@
 observables are now represented on the curve. 
-\cggb{I'm not totally clear on what I'm looking at here.
+%\cggb{I'm not totally clear on what I'm looking at here.
 Is this the diagram where we want to explain the whole simulation algorithm?
@@
 And d) is c) after some R and F moves so you go into the standard basis for the fusion tree?
-Are the red lines between c) and d) just denoting leaves with the same identity or do they have some more precise meaning wrt the braid moves that relate c) and d)?}}
+Are the red lines between c) and d) just denoting leaves with the same identity or do they have some more precise meaning wrt the braid moves that relate c) and d)?}
+}
 \label{f:syndrome}
@@
 
-\begin{figure}[th!]
-\begin{center}
-	\includegraphics[width=\columnwidth]{pic-decode.pdf}
-\caption{The decoder works by maintaining a set of disjoint clusters (rooted trees).
-\cggb{Is this diagram where we want to explain the decoding algorithm?
-Is part a) round one of clustering and part b) round 2 of clustering?
-Do the arrow directions just denote the direction stuff goes when we try to fuse it all together or does it have some deeper meaning?}}
-\label{f:decode}
-\end{center}
-\end{figure}
+In FIG. \ref{f:syndrome} we show two adjacent sites
+involved in a syndrome measurement.
+%This will be the total charge on each site, ie. either $\tau$ or $\mathbb{I}.$
+The error process has resulted in two pair
+creation events along the edge joining these sites.
+\dude{i'd like to write out the equations for each of
+these 4 steps, but we'd need to keep it tight somehow.}
+First, (a) we show the state as a tensor product of two pairs $\tau\tau\otimes\tau\tau$.
+Then, (b) these two pairs are embedded into a single larger fusion
+tree $\tau\tau\tau\tau$.
+This is continuosly deformable into the picture in (c).
+It is now clear the two braid operations required so
+that the observables are represented on the fusion tree.
+The general algorithm and datastructures used
+for this proceedure will be discussed elsewhere.
+
+\dude{Arrgh, what do we say about how to simulate moving anyons around
+the lattice ?}
 

### 2015-06-01 fib2.tex
This version compiles for me.
I changed to pdf figures since there is a problem with eps2pdf package, and I put the tikz figures back in, but smaller.
Tried to make the fusion and braid diagrams a little more compact.
Copied and pasted the tikz code from Jiannis's paper in case we want to use that instead.
Removed Jiannis diagrams and changed "bond cluster" to "connected component"

@@
 
-%\usepackage{tikz}
-%\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit}
+\usepackage{tikz}
+\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit,shapes.misc}
 
@@
 	\begin{align}
-		\begin{tikzpicture}[baseline=0.5cm,scale=0.33]		
+		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
 			\draw(0,0)--(0,1);
@@
 			\draw plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
-			\node at (0,0) [anchor=north] {$c$};
-			\node at (-1,3) [anchor=south] {$b$};
-			\node at (1,3) [anchor=south] {$a$};
+			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
+			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
+			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
 		\end{tikzpicture}
 		&\;\;=\;\;R^{ab}_c\cdot\;
-		\begin{tikzpicture}[baseline=0.5cm,scale=0.33]		
+		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
 			\draw(0,0)--(0,1);
@@
 			\draw(0,1)--(1,2)--(1,3);
-			\node at (0,0) [anchor=north] {$c$};
-			\node at (-1,3) [anchor=south] {$b$};
-			\node at (1,3) [anchor=south] {$a$};
+			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
+			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
+			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
 		\end{tikzpicture}
@@
 	\begin{align}
-		\begin{tikzpicture}[baseline=0.6cm,scale=0.4]
+		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]
 			\draw(0,0)--(0,1)--(-2,3);
@@
 			\draw(2,3)--(0,1);
-			\node at (-0.45,1.6) [anchor=north east] {$i$};
-			\node at (0,0) [anchor=north] {$d$};
-			\node at (2,3) [anchor=south] {$c$};
-			\node at (0,3) [anchor=south] {$b$};
-			\node at (-2,3) [anchor=south] {$a$};
+			\node at (-0.45,1.6) [anchor=north east] {{\scriptsize $i$}};
+			\node at (0,0) [anchor=west] {{\scriptsize $d$}};
+			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
+			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
+			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
 		\end{tikzpicture}
 		&\;\;=\;\;\sum_j[F^{abc}_d]_{ij}\cdot\;
-		\begin{tikzpicture}[baseline=0.6cm,scale=0.4]		
+		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]		
 			\draw(0,0)--(0,1)--(-2,3);
@@
 			\draw(2,3)--(0,1);
-			\node at (0.42,1.63) [anchor=north west] {$j$};
-			\node at (0,0) [anchor=north] {$d$};
-			\node at (2,3) [anchor=south] {$c$};
-			\node at (0,3) [anchor=south] {$b$};
-			\node at (-2,3) [anchor=south] {$a$};
+			\node at (0.42,1.63) [anchor=north west] {{\scriptsize $j$}};
+			\node at (0,0) [anchor=east] {{\scriptsize $d$}};
+			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
+			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
+			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
 		\end{tikzpicture}
 	\end{align}
-
-\dude{these equations are too big... i was hoping for something tight, like
-in http://arxiv.org/abs/1504.02868
-any ideas? i might just generate a bunch of little pdf's...
-}
 
@@
 Our error-correction algorithm is
-based on a heirarchical clustering algorithm~\cite{Hastie2009},
+based on a hierarchical clustering algorithm~\cite{Hastie2009},
 and has some 
@@
 %fusing the anyons within each cluster. 
-measureing the total charge within each cluster.
+measuring the total charge within each cluster.
 Clusters with trivial charge are discarded, and
@@
 
-\begin{figure}[th!]
+\begin{figure}[t!]
 \begin{center}
-	\includegraphics[width=1.0\columnwidth]{pic-decode.eps}
+	\includegraphics[width=1.0\columnwidth]{pic-decode.pdf}
 \caption{The decoder works by maintaining a set of disjoint clusters as rooted trees.
@@
 Below the (bond) percolation threshold for (say) a 2D square lattice, we expect random sets of 
-bonds to decompose into separate clusters~\footnote{
-We use the word cluster to refer both to groupings 
-of nearby anyons as formed by the decoding algorithm and 
-to connected components of a graph under percolation\dude{confusing}, since both 
-of these usages are standard in the literature. The intended 
-meaning will remain clear from context.} of average size $O(\log(n))$ and variance 
-$O(1)$~\cite{Bazant2000}.
+bonds to decompose into separate connected components 
+%~\footnote{We use the word cluster to refer both to groupings of nearby anyons as formed by the decoding algorithm and to connected components of a graph under percolation\dude{confusing}, since both of these usages are standard in the literature.
+The intended meaning will remain clear from context.}
+of average size $O(\log(n))$ and variance $O(1)$~\cite{Bazant2000}.
 Each noise process in our model is associated with a (randomly distributed) edge, and so 
-disconnected clusters correspond to sets of anyons that could not have interacted at any 
+disconnected components correspond to sets of anyons that could not have interacted at any 
 point in their history. 
@@
 into contact with one another \dude{um um um}, in this case charge conservation 
-implies that each distinct cluster must have trivial total charge, and so all such interactions are trivial.
-This allows us to simulate the braiding processes within each cluster 
+implies that each distinct component must have trivial total charge, and so all such interactions are trivial.
+This allows us to simulate the braiding processes within each component 
 separately. In other words: the quantum state in the fusion space of all anyons factorizes into 
-a tensor product over bond clusters, and we can compute each factor separately. Since each 
-cluster has size only $O(\log(n))$, we can typically simulate these dynamics efficiently 
+a tensor product over components, and we can compute each factor separately. Since each 
+component has size only $O(\log(n))$, we can typically simulate these dynamics efficiently 
 because the resulting fusion space has dimension $O(\mathrm{poly}(n))$. There are rare 
@@
 \begin{center}
-	\includegraphics[width=1.0\columnwidth]{pic-syndrome.eps}
+	\includegraphics[width=1.0\columnwidth]{pic-syndrome.pdf}
 \caption{Four equivalent representations of a state,

### 2015-06-01 fib2.tex
addressing a couple of comments discussed over skype

@@
 \hypersetup{colorlinks, linkcolor=darkblue, citecolor=darkgreen, filecolor=red, urlcolor=blue}
-\hypersetup{pdfauthor={Simon Burton, Courtney Brell, Steven T. Flammia}}
+\hypersetup{pdfauthor={Simon Burton, Courtney G. Brell, Steven T. Flammia}}
 %\hypersetup{pdftitle={Title\ Goes\ Here}}
@@
 a less important (and non-universal) role.
-We simulate a $(2+1)$-dimensional topological quantum field theory.
+Our simulation is in effect that of a $(2+1)$-dimensional topological quantum field theory, which allows for topological processes such as pair-creation, braiding, and fusion of anyonic charges.
+This is modelled on a periodic $L\times L$ square lattice $\Lambda$ of \emph{tiles} on which anyons can reside.
+For more details of an analogous model, see~\cite{Brell2013}.
 %Effectively, we simulate a $(2+1)$-dimensional topological quantum field theory on a discrete space-time.
@@
 based on a hierarchical clustering algorithm~\cite{Hastie2009},
-and has some 
-similarities to the hard-decision renormalization group (RG) decoder~\cite{Bravyi2011}. 
+and follows a similar strategy to the hard-decision renormalization group (RG) decoder~\cite{Bravyi2011}. 
 The decoder proceeds by measuring the occupations of 
-anyons at each site of the lattice, forming clusters of nearby anyons and 
+anyons at each site of the lattice, producing a \emph{syndrome} of occupied sites. Following this, it forms clusters of nearby anyons and 
 %fusing the anyons within each cluster. 
-measuring the total charge within each cluster.
+measures the total charge within each cluster.
 Clusters with trivial charge are discarded, and
 the rest are joined (agglomeratively~\cite{Hastie2009})
-at linearly increasing length scales.
-See FIG. \ref{f:decode}.
-Note that unlike the abelian case, the decoder
-cannot know the charge of each cluster based only
-on the syndrome information (as in \cite{Bravyi2011}),
+at linearly increasing length scales. This iterative process concludes when there is at most a single cluster remaining (see \Fref{f:decode}).
+Note that unlike the case of abelian anyons, the decoder
+cannot determine the charge of each cluster given only the syndrome information (as in \cite{Bravyi2011}),
 and so will query (measure) the system to find this.
-The simulation proceeds in this way as a dialogue between decoder
-and system, terminating when the lattice 
-is free of anyons (i.e.~we have returned to the codespace) 
-or the decoder performs a homologically nontrivial operation, thereby altering the codespace.
+Our simulation proceeds in this way as a dialogue between decoder
+and system, terminating when either the decoder itself terminates or when it performs a homologically nontrivial operation, thereby altering the codespace (and failing to perform successful information recovery).
 %or the clustering length scale exceeds the size of the lattice.
@@
 Note that, as was found in Ref.~\cite{Brell2013}, we expect that our qualitative results may be reproduced by most alternative families of decoders, although it may not be clear in all cases how to extend these decoders to the non-abelian setting.
-The advantage of using a hard-decision decoder is 
+The advantage of using a clustering decoder is 
 its simplicity and flexibility, and the fact that its clustering scheme is compatible with the structure in the noise processes that allows us to classically simulate them.
@@
 \caption{The decoder works by maintaining a set of disjoint clusters as rooted trees.
-(a) Trees are formed from neighboring sites that contain a charge.
-(b) For each successive round, we grow all trees, 
-and overlapping trees are joined to form
-a single tree. Arrows denote movement of charge to the root of the tree.
-The root of each tree is chosen arbitrarily.
+(a) At the initial clustering stage, these trees are formed from neighboring sites that contain charges.
+Within each cluster, the charges are transported to the root of the tree (chosen arbitrarily), and their combined charge measured.
+The direction of transport (towards the root) is denoted by arrows.
+(b) At each successive round, all trees are grown in every direction, and overlapping trees are joined.
+Again, any charges within a cluster are transported to the root of the tree and measured.
+\cggb{Do we delete the clusters that do not contain any charges (fuse to vacuum) or leave them around?}
 }
@@
 However, recall that logical errors in our system correspond to processes that act over a non-trivial loop of the torus. 
-Our simulation remains efficient \dude{efficiency has nothing to do with it}
-until the point that we start to create nontrivial loops around the torus, 
-and our simulation begins to declare failure whenever non-trivial logical 
-operations occur, meaning that we can simulate large lattice sizes 
+Below the point at which the decoder begins to create such nontrivial loops, our simulation remains efficient,
+%\dude{efficiency has nothing to do with it}
+while it begins to declare failure whenever non-trivial logical 
+operations occur. This allows us to simulate large lattice sizes 
 in the successful error-correction (sub-percolated) regime, including up to $L=128$.
@@
 
-Our concrete simulation proceeds by associating a \emph{tile} with each site of the 
+Our concrete simulation proceeds by associating a tile with each site of the 
 $L\times L$ periodic square lattice.

### 2015-06-02 fib2.tex
remove some comments from the latex source
cluster -> component; fix caption

@@
 For more details of an analogous model, see~\cite{Brell2013}.
-%Effectively, we simulate a $(2+1)$-dimensional topological quantum field theory on a discrete space-time.
-%As such, we model the system simply as a 
-%periodic $L\times L$ square lattice $\Lambda$ of sites upon which sets of anyons can 
-%reside. 
-%Allowed anyon dynamics (pair-creation, braiding, and fusion) are considered to act 
-%locally on edges of $\Lambda$. 
-%For more details of an analogous model, see~\cite{Brell2013}.
 \dude{something about observables vs. states.}
@@
 anyons at each site of the lattice, producing a \emph{syndrome} of occupied sites. Following this, it forms clusters of nearby anyons and 
-%fusing the anyons within each cluster. 
 measures the total charge within each cluster.
@@
 \caption{The decoder works by maintaining a set of disjoint clusters as rooted trees.
-(a) At the initial clustering stage, these trees are formed from neighboring sites that contain charges.
-Within each cluster, the charges are transported to the root of the tree (chosen arbitrarily), and their combined charge measured.
-The direction of transport (towards the root) is denoted by arrows.
-(b) At each successive round, all trees are grown in every direction, and overlapping trees are joined.
-Again, any charges within a cluster are transported to the root of the tree and measured.
-\cggb{Do we delete the clusters that do not contain any charges (fuse to vacuum) or leave them around?}
-}
+(a) At the initial clustering stage, these trees are formed 
+from neighboring sites that contain charges. Within each cluster, the 
+charges are transported to the root of the tree (chosen 
+arbitrarily), and their combined charge measured. The direction of transport 
+(towards the root) is denoted by arrows.
+(b) At each successive round, all trees are grown in 
+every direction, and overlapping trees are joined. Again, any charges 
+within a cluster are transported to the root of the 
+tree and measured. Any clusters with vacuum total charge are deleted.
 \label{f:decode}
@@
 \end{figure}
-
-%\begin{figure*}[th!]
-%\begin{center}
-%	{\scriptsize (a)
-%	\includegraphics[width=0.45\columnwidth]{pair-create.pdf}
-%	\hskip 4pt
-%	(b)
-%	\includegraphics[width=0.45\columnwidth]{syndrome-1.pdf}
-%	\hskip 4pt
-%	(c)
-%	\includegraphics[width=0.45\columnwidth]{syndrome-2.pdf}
-%	\hskip 4pt
-%	(d)}
-%	\includegraphics[width=0.45\columnwidth]{syndrome-2.pdf}
-%\caption{\stf{polish this a bit} The simulation of noise processes proceeds by a) creating pairs of anyons on neighboring tiles represented by open curves b) joining the curves within a given tile c) measuring the total charge on each tile.
-\stf{Add another graph that shows how we use syndrome info.}}
-%\label{f:simex}
-%\end{center}
-%\end{figure*}
 
@@
 bonds to decompose into separate connected components 
-%~\footnote{We use the word cluster to refer both to groupings of nearby anyons as formed by the decoding algorithm and to connected components of a graph under percolation\dude{confusing}, since both of these usages are standard in the literature.
-The intended meaning will remain clear from context.}
 of average size $O(\log(n))$ and variance $O(1)$~\cite{Bazant2000}.
@@
 must also consider the effect of the error-correction routine itself. This acts iteratively to fuse 
-particles on increasing length scales. While this kind of fusion would typically merge clusters, 
-forcing us to compute dynamics of larger and larger sets of anyons, large clusters are sparsely distributed 
+particles on increasing length scales. While this kind of fusion would typically merge components, 
+forcing us to compute dynamics of larger and larger sets of anyons, large components are sparsely distributed 
 (and thus unlikely to be merged), and in addition at each length scale the total number of 
@@
 Of course, if we were to consider noise so strong that 
-the clusters percolate over the entire lattice, we would no 
+the components percolate over the entire lattice, we would no 
 longer expect to be able to efficiently simulate the noise and recovery processes in the system. 
@@
 
-%\stf{Add figure about observables versus states.}
-
 Our concrete simulation proceeds by associating a tile with each site of the 
@@
 decomposition into factors corresponding 
-to disjoint clusters \dude{confusing use of this word}.
+to disjoint components.
 For comparison, previous work 
@@
 observables are now represented on the curve. 
-%\cggb{I'm not totally clear on what I'm looking at here.
-Is this the diagram where we want to explain the whole simulation algorithm?
-Is the idea that we start with a), which is given by the set of noise processes that have happened, then we connect stuff up arbitrarily into b) to make some fusion tree.
-Then c) is what's happening after linearizing the picture?
-And d) is c) after some R and F moves so you go into the standard basis for the fusion tree?
-Are the red lines between c) and d) just denoting leaves with the same identity or do they have some more precise meaning wrt the braid moves that relate c) and d)?}
 }
@@
 the lattice ?}
-
-%Each round of simulation proceeds in four steps as follows (an example is shown 
-%in \Fref{f:simex}).
-%
-%\begin{enumerate}[a)]
-%\item The noise process is modeled by a sequence of pair-creation events distributed as 
-%a Poisson process across each edge. Curves are created crossing the relevant edge 
-%and terminating on the neighboring sites.
-%\item We first join curves that participate in the same tile in order to, 
-%\cggb{maybe a couple more lines of detail on this and the next point? perhaps also the previous paragraph?}
-%\item measure the charge on each tile. Any resulting anyon is left somewhere in the tile.
-%\item The decoder examines this syndrome and clusters nearby anyons. Each cluster 
-%is then measured (fused), and the decoder continues to cluster and fuse on larger 
-%scales until there are no more anyons, or a cluster includes a non-trivial loop on the 
-%lattice. Since operators with support on such non-trivial clusters will generally perform an 
-%undetectable error on the encoded state, in this case we abandon the simulation and 
-%declare failure to error correct.
-%\end{enumerate}
 

### 2015-06-02 fib2.tex
more edits

@@
 For more details of an analogous model, see~\cite{Brell2013}.
-\dude{something about observables vs. states.}
+
+As was noted in~\cite{Pfeifer2014}, when dealing with two-dimensional 
+anyon dynamics, it is not sufficient to consider only
+the algebraic (fusion/braiding) properties of the anyons,
+one must also account for the algebra of observables.
 
@@
 based on a hierarchical clustering algorithm~\cite{Hastie2009},
-and follows a similar strategy to the hard-decision renormalization group (RG) decoder~\cite{Bravyi2011}. 
+and follows a similar strategy to the hard-decision renormalization group decoder~\cite{Bravyi2011}. 
 The decoder proceeds by measuring the occupations of 
@@
 within a cluster are transported to the root of the 
-tree and measured. Any clusters with vacuum total charge are deleted.
+tree and measured. All clusters with vacuum total charge are deleted.
 \label{f:decode}
+}
 \end{center}
@@
 
-In FIG. \ref{f:syndrome} we show two adjacent sites
+In \Fref{f:syndrome} we show two adjacent sites
 involved in a syndrome measurement.
@@
 Although it is not completely obvious how to do so, applying these methods to more realistic models such as concrete microscopic spin models or models with non-topological features would give direct insight into practical error rates needed for topological quantum memories in non-Abelian systems.
-Another potential direction is to incorporate tensor network methods for simulating anyons~\cite{Pfeifer2012, Singh2014} to improve the speed and scale of the simulations. 
-Finally, perhaps the most important open question is whether \emph{fault-tolerant} decoders can be designed for nonabelian anyon codes.
+\dude{This doesn't make much sense to me:} Another potential direction is to incorporate tensor network methods for simulating anyons~\cite{Pfeifer2012, Singh2014} to improve the speed and scale of the simulations.
+Finally, perhaps the most important open question is whether 
+\emph{fault-tolerant} decoders can be designed for nonabelian anyon codes. 
+\dude{Another important question is wether this error
+correction process can be mapped to a classical stat mech problem, like RBIM.}
 

### 2015-06-02 fib2.tex
polishing text.

@@
 \end{align}
-where in the last expression, $\varphi=\frac{1+\sqrt{5}}{2}$ is the golden ratio, and the matrix is given in a basis labelled $(\mathbb{I},\tau)$.
+where the matrix is given in a basis labelled $(\mathbb{I},\tau)$.
 
@@
 point in their history. 
-Although normally anyons can interact by braiding without ever coming 
-into contact with one another \dude{um um um}, in this case charge conservation 
-implies that each distinct component must have trivial total charge, and so all such interactions are trivial.
-This allows us to simulate the braiding processes within each component 
-separately. In other words: the quantum state in the fusion space of all anyons factorizes into 
-a tensor product over components, and we can compute each factor separately. Since each 
+We are free to neglect the degrees of freedom associated with braiding between components because each component has trivial total charge.
+This allows us to simulate the braiding processes within each component separately. 
+In other words: the quantum state in the fusion space of all anyons factorizes into 
+a tensor product over components. 
+Since each 
 component has size only $O(\log(n))$, we can typically simulate these dynamics efficiently 
@@
 tree $\tau\tau\tau\tau$.
-This is continuosly deformable into the picture in (c).
+This is continuously deformable into the picture in (c).
 It is now clear the two braid operations required so
 that the observables are represented on the fusion tree.
-The general algorithm and datastructures used
-for this proceedure will be discussed elsewhere.
+The general algorithm and data structures used
+for this procedure will be discussed elsewhere.
 
@@
 
-\stf{Cite~\cite{Pfeifer2010} for braiding tricks}
+\stf{Cite~\cite{Pfeifer2012} for braiding tricks}
 
@@
 Although it is not completely obvious how to do so, applying these methods to more realistic models such as concrete microscopic spin models or models with non-topological features would give direct insight into practical error rates needed for topological quantum memories in non-Abelian systems.
-\dude{This doesn't make much sense to me:} Another potential direction is to incorporate tensor network methods for simulating anyons~\cite{Pfeifer2012, Singh2014} to improve the speed and scale of the simulations.
+It would be extremely interesting to find \emph{classical} spin models whose phase diagram encodes the threshold for error correction in these systems~\cite{Dennis2002}.
+%Another potential direction is to incorporate tensor network methods for simulating anyons~\cite{Pfeifer2012, Singh2014} to improve the speed and scale of the simulations. 
 Finally, perhaps the most important open question is whether 
 \emph{fault-tolerant} decoders can be designed for nonabelian anyon codes.
-\dude{Another important question is wether this error
-correction process can be mapped to a classical stat mech problem, like RBIM.}
 

### 2015-06-02 fib2.tex
Changed equation.
added (very rough) potential sequence of fusion diagrams to explain figure 2.

@@
 For the Fibonacci anyons, the non-trivial $R$ and $F$ moves are given by
-\begin{align}
-	R_{\mathbb{I}}^{\tau\tau}&= \e^{\frac{-4\pi i}{5}}\qquad R_\tau^{\tau\tau}= \e^{\frac{3\pi i}{5}}\\
-	F_{\tau}^{\tau\tau\tau} &= \begin{pmatrix}\varphi^{-1}&\varphi^{-\frac{1}{2}}\\\varphi^{-\frac{1}{2}}&-\varphi^{-1}\end{pmatrix} \,,
-\end{align}
+\begin{equation*}
+	R_{\mathbb{I}}^{\tau\tau} = \e^{\frac{-4\pi i}{5}} 
+	\ \ , \ \
+	R_\tau^{\tau\tau}= \e^{\frac{3\pi i}{5}} 
+	\ \ , \ \
+	F_{\tau}^{\tau\tau\tau} = \begin{pmatrix}\varphi^{-1}&\varphi^{-\frac{1}{2}}\\\varphi^{-\frac{1}{2}}&-\varphi^{-1}\end{pmatrix} \,,
+\end{equation*}
 where the matrix is given in a basis labelled $(\mathbb{I},\tau)$.
@@
 these 4 steps, but we'd need to keep it tight somehow.}
+
+\newcommand{\verteq}{\rotatebox{90}{$\,=$}}
+\begin{align*}
+		&\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
+			\draw(1,0)--(0,1)[dashed];
+			\draw(0,1)--(-1,2)--(-1,3);
+			\draw(0,1)--(1,2)--(1,3);
+			\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
+			\node at (1,3) [anchor=west] {{\scriptsize $2$}};
+			%			
+			\begin{scope}[xshift=4cm]
+				\draw(1,0)--(0,1)[dashed];
+				\draw(0,1)--(-1,2)--(-1,3);
+				\draw(0,1)--(1,2)--(1,3);
+				\node at (-1,3) [anchor=west] {{\scriptsize $3$}};
+				\node at (1,3) [anchor=west] {{\scriptsize $4$}};
+			\end{scope}
+		\end{tikzpicture}\\
+		&\qquad\;\downarrow\\
+		&\begin{tikzpicture}[baseline=0.5cm,scale=0.3]
+			\begin{scope}[xshift=2cm,yshift=2cm]		
+				\draw(1,0)--(0,1)[dashed];
+				\draw(0,1)--(-1,2)--(-1,3);
+				\draw(0,1)--(1,2)--(1,3);
+				\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
+				\node at (1,3) [anchor=west] {{\scriptsize $2$}};
+			\end{scope}
+			%			
+			\begin{scope}[xshift=4cm]
+				\draw(1,0)--(0,1)[dashed];
+				\draw(0,1)--(-1,2)--(1,4)--(1,5);
+				\draw(0,1)--(3,4)--(3,5);
+				\node at (1,5) [anchor=west] {{\scriptsize $3$}};
+				\node at (3,5) [anchor=west] {{\scriptsize $4$}};
+			\end{scope}
+		\end{tikzpicture}\\
+		&\qquad\downarrow\\
+		&\begin{tikzpicture}[baseline=1.5cm,scale=0.3]
+			\begin{scope}[xshift=2cm,yshift=2cm]		
+				\draw(1,0)--(0,1)[dashed];
+				\draw(0,1)--(-1,2)--(-1,7);
+				\draw(0,1)--(1,2)--(1,5);
+				\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
+				\node at (1,3) [anchor=west] {{\scriptsize $2$}};
+				\node at (-1,7) [anchor=west] {{\scriptsize $1$}};
+				\node at (1,7) [anchor=west] {{\scriptsize $4$}};
+			\end{scope}
+			%			
+			\begin{scope}[xshift=4cm]
+				\draw(1,0)--(0,1)[dashed];
+				\draw(0,1)--(-1,2)--(1,4)--(1,5);
+				\draw(0,1)--(3,4)--(3,5);
+				\draw(3,7)--(3,9);
+				\node at (1,5) [anchor=west] {{\scriptsize $3$}};
+				\node at (3,5) [anchor=west] {{\scriptsize $4$}};
+				\node at (1,9) [anchor=west] {{\scriptsize $2$}};
+				\node at (3,9) [anchor=west] {{\scriptsize $3$}};
+			\end{scope}
+			%
+			\begin{scope}[xshift=6cm,yshift=2cm]
+				\draw plot [smooth, tension=1] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
+				\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
+				\draw plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
+			\end{scope}
+			\begin{scope}[xshift=4cm,yshift=4cm]
+				\draw plot [smooth, tension=1] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
+				\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
+				\draw plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
+			\end{scope}
+		\end{tikzpicture}\\
+		&\qquad\verteq\\
+		\sum_{j,j'\in\{\mathbb{I},\tau\}}R^{\tau\tau}_{\mathbb{I}}[F^{\tau\tau\tau}_{\tau}]_{\mathbb{I}j}R^{\tau\tau}_{j}[F^{\tau\tau\tau}_{\tau}]^{-1}_{jj'}\;\;
+		&\begin{tikzpicture}[baseline=0.8cm,scale=0.3]
+			\begin{scope}[xshift=2cm,yshift=2cm]		
+				\draw(1,0)--(0,1)[dotted];
+				\draw(0,1)--(-1,2)--(-1,3);
+				\draw(0,1)--(1,2)--(1,3);
+				\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
+				\node at (1,3) [anchor=west] {{\scriptsize $4$}};
+				\node at (0.7,0.2) [anchor=east] {{\scriptsize $j'$}};
+			\end{scope}
+			%			
+			\begin{scope}[xshift=4cm]
+				\draw(1,0)--(0,1)[dashed];
+				\draw(0,1)--(-1,2)--(1,4)--(1,5);
+				\draw(0,1)--(3,4)--(3,5);
+				\node at (1,5) [anchor=west] {{\scriptsize $2$}};
+				\node at (3,5) [anchor=west] {{\scriptsize $3$}};
+			\end{scope}
+		\end{tikzpicture}\\
+		&\qquad\verteq\\
+		\sum_{j,j'\in\{\mathbb{I},\tau\}}R^{\tau\tau}_{\mathbb{I}}[F^{\tau\tau\tau}_{\tau}]_{\mathbb{I}j}R^{\tau\tau}_{j}[F^{\tau\tau\tau}_{\tau}]^{-1}_{jj'}\;\;
+		&\begin{tikzpicture}[baseline=0.2cm,scale=0.3]		
+			\draw(2,-1)--(0,1)[dotted];
+			\draw(0,1)--(-1,2)--(-1,3);
+			\draw(0,1)--(1,2)--(1,3);
+			\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
+			\node at (1,3) [anchor=west] {{\scriptsize $4$}};
+			\node at (1,0) [anchor=east] {{\scriptsize $j'$}};
+			\draw(2,-1)--(2,-2)[dashed];
+			%			
+			\begin{scope}[xshift=4cm]
+				\draw(-2,-1)--(0,1)[dotted];
+				\draw(0,1)--(-1,2)--(-1,3);
+				\draw(0,1)--(1,2)--(1,3);
+				\node at (-1,3) [anchor=west] {{\scriptsize $2$}};
+				\node at (1,3) [anchor=west] {{\scriptsize $3$}};
+				\node at (-1,0) [anchor=west] {{\scriptsize $\bar{j'}$}};
+			\end{scope}
+		\end{tikzpicture}
+\end{align*}
+\cggb{Here 1,2,3,4 are meant to refer to the 4 different leaves in \Fref{f:syndrome} a) taken clockwise from the top left (equivalently those in c) taken down the page).
+The first diagram represents a), the second b) and c) together, and the last three d).
+Is this correct?
+Of course I would clean and explain these properly if this is the kind of thing we want.
+Also I haven't been very careful with the calculation.
+I would need to check if there is a Frobenius-Schur indicator missing on the last line.
+We could also do something like make circles above 1,4 and 2,3 at the end to show the measurements being made in the figure or something.}
+
+	\begin{align}
+		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
+			\draw(0,0)--(0,1);
+			\draw plot [smooth, tension=1] coordinates { (0,1) (0.75,1.8) (-0.6,2.45) (-1,3)};
+			\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
+			\draw plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
+			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
+			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
+			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
+		\end{tikzpicture}
+		&\;\;=\;\;R^{ab}_c\cdot\;
+		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
+			\draw(0,0)--(0,1);
+			\draw(0,1)--(-1,2)--(-1,3);
+			\draw(0,1)--(1,2)--(1,3);
+			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
+			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
+			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
+		\end{tikzpicture}
+	\end{align}
+where $a$, $b$, and $c$ represent particle types, or $F$-moves, representing the associativity rule for fusion processes, denoted as
+	\begin{align}
+		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]
+			\draw(0,0)--(0,1)--(-2,3);
+			\draw(0,3)--(-1,2);
+			\draw(2,3)--(0,1);
+			\node at (-0.45,1.6) [anchor=north east] {{\scriptsize $i$}};
+			\node at (0,0) [anchor=west] {{\scriptsize $d$}};
+			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
+			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
+			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
+		\end{tikzpicture}
+		&\;\;=\;\;\sum_j[F^{abc}_d]_{ij}\cdot\;
+		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]		
+			\draw(0,0)--(0,1)--(-2,3);
+			\draw(0,3)--(1,2);
+			\draw(2,3)--(0,1);
+			\node at (0.42,1.63) [anchor=north west] {{\scriptsize $j$}};
+			\node at (0,0) [anchor=east] {{\scriptsize $d$}};
+			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
+			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
+			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
+		\end{tikzpicture}
+	\end{align}
+
 First, (a) we show the state as a tensor product of two pairs $\tau\tau\otimes\tau\tau$.

### 2015-06-03 fib2.tex
deleted leftover working from diagram making
revised fusion diagram thing, made it into a figure completed discussion of simulation added new jw00t ref deleted comments in tex file other minor edits  - its now a couple paragraphs too long, but that should be fairly easy to fix.

@@
 \begin{abstract}
-Classically simulating the dynamics of excitations in two-dimensional quantum systems that 
-support anyons is likely intractable in general because such dynamics are sufficient to implement 
+Classically simulating the dynamics of anyonic excitations in two-dimensional quantum systems is likely intractable in general because such dynamics are sufficient to implement 
 universal quantum computation. However, processes of interest for the study of quantum 
@@
 Recent investigations have begun to explore quantum error correction for nonabelian anyon 
-models~\cite{Brell2013, Wootton2013, Hutter2014}. Nonabelian anyon models are especially interesting 
+models~\cite{Brell2013, Wootton2013, Hutter2014, Wootton2015}. Nonabelian anyon models are especially interesting 
 because braiding and fusion of these anyons in general allows for the implementation of universal quantum 
@@
 	\begin{align}
+	\label{e:rmove}
 		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
@@
 	\begin{align}
+		\label{e:fmove}
 		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]
@@
 This is modelled on a periodic $L\times L$ square lattice $\Lambda$ of \emph{tiles} on which anyons can reside.
+This treatment applies equally well to lattice models, where anyons can only be located at a discrete set of points, or continuum models, where a discretization of the manifold must be chosen in order to perform charge measurements.
+In the former case, each tile of $\Lambda$ represents a lattice site, while in the latter case each tile represents a measurement region.
 For more details of an analogous model, see~\cite{Brell2013}.
@@
 the algebraic (fusion/braiding) properties of the anyons,
-one must also account for the algebra of observables.
+one must also account for the algebra of observables. \cggb{This sentence seems odd here. Consider moving?}
 
@@
 \end{align}
-with $\proj{\mathbb{I}}_i$ the projector to charge $\mathbb{I}$ at site $i$, i.e.~the ground 
+with $\proj{\mathbb{I}}_i$ the projector to charge $\mathbb{I}$ at site (or tile) $i$, i.e.~the ground 
 space of the model has vacuum (or no anyon) at each site. Given the toroidal boundary 
@@
 annihilating to vacuum.
-% cggb{we want to define logical operators as those that map the codespace to itself, so for it to be a logical operator, they must annihilate to vacuum. they need not be unitary}.
 
 Our error-correction algorithm is
-based on a hierarchical clustering algorithm~\cite{Hastie2009},
+based on a hierarchical clustering algorithm~\cite{Hastie2009, Wootton2015},
 and follows a similar strategy to the hard-decision renormalization group decoder~\cite{Bravyi2011}. 
@@
 and system, terminating when either the decoder itself terminates or when it performs a homologically nontrivial operation, thereby altering the codespace (and failing to perform successful information recovery).
-%or the clustering length scale exceeds the size of the lattice.
-%\cggb{our simulation may terminate when the decoder performs a nontrivial operation, but here we're just describing the decoder, which can't know that.}
-%\dude{in our sim the decoder stops when there is one cluster. Ie., it never gives up.}
-%\cggb{A few more details? What is our length schedule?} 
-%\cggb{How does our decoder relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?} 
 Note that, as was found in Ref.~\cite{Brell2013}, we expect that our qualitative results may be reproduced by most alternative families of decoders, although it may not be clear in all cases how to extend these decoders to the non-abelian setting.
@@
 Below the point at which the decoder begins to create such nontrivial loops, our simulation remains efficient,
-%\dude{efficiency has nothing to do with it}
 while it begins to declare failure whenever non-trivial logical 
@@
 
-Our concrete simulation proceeds by associating a tile with each site of the 
-$L\times L$ periodic square lattice.
-In order to keep track of the observables of the system 
-we maintain a set of disjoint curves, representing the history of anyons on the lattice.
+%Our concrete simulation proceeds by associating a tile with each site of the 
+%$L\times L$ periodic square lattice $\Lambda$.
+
+In order to keep track of the state of the system 
+we maintain a set of disjoint curves, \cggb{do they need to be directed, or is that just for the figure?} representing the history of anyons on the lattice.
 These curves can also be thought of as a top-down view of the fusion tree:
 the anyons comprising the fusion tree are here displayed as points along each curve. 
-In general, the curves wind around the two 
-dimensional tiles in a haphazard way determined by the progress of the simulation.
+In general, the curves wind around our two 
+dimensional manifold in a haphazard way determined by the progress of the simulation.
 This allows a dynamically generated basis for the fusion space that easily allows for tensor 
@@
 to disjoint components. 
-For comparison, previous work 
 used a single fixed basis for the fusion space (determined by row-major ordering of 
@@
 
+The application of a pair-creation noise process corresponds to the addition of an extra piece of curve to the lattice, along with two preferred points on it denoting the anyon locations.
+Following the noise processes, our simulation must proceed to measure the total charge within each tile (the results of these measurements will form the error syndrome).
+This requires joining any curves within that tile, and performing braid moves along the curves until all anyons within the tile have been localized within a contiguous region of the curve.
+Following this, the total charge can (probabilistically) simply be read off the relevant section of the fusion tree.
+An example of this procedure for a simple noise process is shown in \Fref{f:syndrome}, and the corresponding braid moves are shown in \Fref{f:syndrome2}.
+The technical details of the algorithm and data structures used
+for this procedure will be discussed elsewhere.
+Braiding processes that encircle a non-trivial loop of our (toric) manifold can also be treated in an analogous way, following e.g.~\cite{Pfeifer2012}.
+\cggb{This paragraph and the next still needs another look.}
+
 \begin{figure}[th!]
 \begin{center}
-	\includegraphics[width=1.0\columnwidth]{pic-syndrome.pdf}
-\caption{Four equivalent representations of a state,
-along with two syndrome observables marked with solid and dashed lines:
-(a) two pairs are joined in (b).
-Deform the curve straight to get (c),
-then effect some
-braid operations on the state so that (d) the two
-observables are now represented on the curve. 
-}
+	\includegraphics[width=1.0\columnwidth]{pic-syndrome.pdf}\\
+\caption{(a) Noise processes initially form isolated sets of pair-created anyons, each crossing the boundary of a tile.
+These events are each represented by curves, where anyons are denoted by specific points on these curves.
+(b) In order to measure the total charge contained within each tile, we must first join the fusion trees associated with all such pairs.
+This corresponds to joining the edges associated with each pair into a continuous path, representing a basis for the fusion space chosen arbitrarily.
+(c) The total charge of each tile can then be found by braiding anyons around each other until all charges within a tile are neighbours on the path, as in (d).
+\cggb{We should think about the best way to represent the transition from (c) to (d).
+I think the current red lines might be confusing, but I don't have any great ideas.}}
 \label{f:syndrome}
@@
 
-In \Fref{f:syndrome} we show two adjacent sites
-involved in a syndrome measurement.
-%This will be the total charge on each site, ie. either $\tau$ or $\mathbb{I}.$
-The error process has resulted in two pair
-creation events along the edge joining these sites.
-\dude{i'd like to write out the equations for each of
-these 4 steps, but we'd need to keep it tight somehow.}
-
-\newcommand{\verteq}{\rotatebox{90}{$\,=$}}
-\begin{align*}
-		&\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
-			\draw(1,0)--(0,1)[dashed];
-			\draw(0,1)--(-1,2)--(-1,3);
-			\draw(0,1)--(1,2)--(1,3);
-			\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
-			\node at (1,3) [anchor=west] {{\scriptsize $2$}};
-			%			
-			\begin{scope}[xshift=4cm]
-				\draw(1,0)--(0,1)[dashed];
-				\draw(0,1)--(-1,2)--(-1,3);
-				\draw(0,1)--(1,2)--(1,3);
-				\node at (-1,3) [anchor=west] {{\scriptsize $3$}};
-				\node at (1,3) [anchor=west] {{\scriptsize $4$}};
-			\end{scope}
-		\end{tikzpicture}\\
-		&\qquad\;\downarrow\\
-		&\begin{tikzpicture}[baseline=0.5cm,scale=0.3]
+\begin{figure}[th!]
+\begin{center}
+			\begin{tikzpicture}[baseline=0.7cm,scale=0.3, xscale=0.9]
 			\begin{scope}[xshift=2cm,yshift=2cm]		
@@
 			\begin{scope}[xshift=4cm]
-				\draw(1,0)--(0,1)[dashed];
+				\draw(0,0)--(0,1)[dashed];
 				\draw(0,1)--(-1,2)--(1,4)--(1,5);
@@
 			\end{scope}
-		\end{tikzpicture}\\
-		&\qquad\downarrow\\
-		&\begin{tikzpicture}[baseline=1.5cm,scale=0.3]
+		\end{tikzpicture}
+		\hspace{-3mm}$\longrightarrow$\hspace{1mm}
+		\begin{tikzpicture}[baseline=1.5cm,scale=0.3, xscale=1]
 			\begin{scope}[xshift=2cm,yshift=2cm]		
@@
 			\end{scope}
-		\end{tikzpicture}\\
-		&\qquad\verteq\\
-		\sum_{j,j'\in\{\mathbb{I},\tau\}}R^{\tau\tau}_{\mathbb{I}}[F^{\tau\tau\tau}_{\tau}]_{\mathbb{I}j}R^{\tau\tau}_{j}[F^{\tau\tau\tau}_{\tau}]^{-1}_{jj'}\;\;
-		&\begin{tikzpicture}[baseline=0.8cm,scale=0.3]
-			\begin{scope}[xshift=2cm,yshift=2cm]		
-				\draw(1,0)--(0,1)[dotted];
+		\end{tikzpicture}
+		$\xrightarrow{R, F}$
+		\begin{tikzpicture}[baseline=0.2cm,scale=0.3,xscale=0.9]		
+			\draw(2,-1)--(0,1)[];
 			\draw(0,1)--(-1,2)--(-1,3);
@@
 			\node at (1,3) [anchor=west] {{\scriptsize $4$}};
-				\node at (0.7,0.2) [anchor=east] {{\scriptsize $j'$}};
-			\end{scope}
-			%			
-			\begin{scope}[xshift=4cm]
-				\draw(1,0)--(0,1)[dashed];
-				\draw(0,1)--(-1,2)--(1,4)--(1,5);
-				\draw(0,1)--(3,4)--(3,5);
-				\node at (1,5) [anchor=west] {{\scriptsize $2$}};
-				\node at (3,5) [anchor=west] {{\scriptsize $3$}};
-			\end{scope}
-		\end{tikzpicture}\\
-		&\qquad\verteq\\
-		\sum_{j,j'\in\{\mathbb{I},\tau\}}R^{\tau\tau}_{\mathbb{I}}[F^{\tau\tau\tau}_{\tau}]_{\mathbb{I}j}R^{\tau\tau}_{j}[F^{\tau\tau\tau}_{\tau}]^{-1}_{jj'}\;\;
-		&\begin{tikzpicture}[baseline=0.2cm,scale=0.3]		
-			\draw(2,-1)--(0,1)[dotted];
-			\draw(0,1)--(-1,2)--(-1,3);
-			\draw(0,1)--(1,2)--(1,3);
-			\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
-			\node at (1,3) [anchor=west] {{\scriptsize $4$}};
-			\node at (1,0) [anchor=east] {{\scriptsize $j'$}};
+			\node at (1,-0.05) [anchor=east] {{\scriptsize $q$}};
 			\draw(2,-1)--(2,-2)[dashed];
@@
 			\begin{scope}[xshift=4cm]
-				\draw(-2,-1)--(0,1)[dotted];
+				\draw(-2,-1)--(0,1)[];
 				\draw(0,1)--(-1,2)--(-1,3);
@@
 				\node at (1,3) [anchor=west] {{\scriptsize $3$}};
-				\node at (-1,0) [anchor=west] {{\scriptsize $\bar{j'}$}};
+				\node at (-1,0) [anchor=west] {{\scriptsize $q'$}};
 			\end{scope}
 		\end{tikzpicture}
-\end{align*}
-\cggb{Here 1,2,3,4 are meant to refer to the 4 different leaves in \Fref{f:syndrome} a) taken clockwise from the top left (equivalently those in c) taken down the page).
-The first diagram represents a), the second b) and c) together, and the last three d).
-Is this correct?
-Of course I would clean and explain these properly if this is the kind of thing we want.
-Also I haven't been very careful with the calculation.
-I would need to check if there is a Frobenius-Schur indicator missing on the last line.
-We could also do something like make circles above 1,4 and 2,3 at the end to show the measurements being made in the figure or something.}
+\caption{In order to transform from the configuration shown in \Fref{f:syndrome}(c) to \ref{f:syndrome}(d), several operations must be performed.
+The labels of the four leaves of these fusion trees correspond to the four anyons taken from the top of the path in \Fref{f:syndrome}(c) to the bottom.
+Vacuum charges are denoted by dashed lines.
+In order to rearrange the anyons so that particles 1 and 4 are neighbors, several braid moves must be performed as shown.
+The effect of these on the fusion tree can then be evaluated by the application of several $R$ and $F$ moves as defined in equations (\ref{e:rmove}) and (\ref{e:fmove}).
+After the manipulations shown, the total charges within each tile can be read off the diagram as $q$ and $q'$.}
+\label{f:syndrome2}
+\end{center}
+\end{figure}
 
-	\begin{align}
-		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
-			\draw(0,0)--(0,1);
-			\draw plot [smooth, tension=1] coordinates { (0,1) (0.75,1.8) (-0.6,2.45) (-1,3)};
-			\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
-			\draw plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
-			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
-			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
-			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
-		\end{tikzpicture}
-		&\;\;=\;\;R^{ab}_c\cdot\;
-		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
-			\draw(0,0)--(0,1);
-			\draw(0,1)--(-1,2)--(-1,3);
-			\draw(0,1)--(1,2)--(1,3);
-			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
-			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
-			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
-		\end{tikzpicture}
-	\end{align}
-where $a$, $b$, and $c$ represent particle types, or $F$-moves, representing the associativity rule for fusion processes, denoted as
-	\begin{align}
-		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]
-			\draw(0,0)--(0,1)--(-2,3);
-			\draw(0,3)--(-1,2);
-			\draw(2,3)--(0,1);
-			\node at (-0.45,1.6) [anchor=north east] {{\scriptsize $i$}};
-			\node at (0,0) [anchor=west] {{\scriptsize $d$}};
-			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
-			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
-			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
-		\end{tikzpicture}
-		&\;\;=\;\;\sum_j[F^{abc}_d]_{ij}\cdot\;
-		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]		
-			\draw(0,0)--(0,1)--(-2,3);
-			\draw(0,3)--(1,2);
-			\draw(2,3)--(0,1);
-			\node at (0.42,1.63) [anchor=north west] {{\scriptsize $j$}};
-			\node at (0,0) [anchor=east] {{\scriptsize $d$}};
-			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
-			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
-			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
-		\end{tikzpicture}
-	\end{align}
-
-First, (a) we show the state as a tensor product of two pairs $\tau\tau\otimes\tau\tau$.
-Then, (b) these two pairs are embedded into a single larger fusion
-tree $\tau\tau\tau\tau$.
-This is continuously deformable into the picture in (c).
-It is now clear the two braid operations required so
-that the observables are represented on the fusion tree.
-The general algorithm and data structures used
-for this procedure will be discussed elsewhere.
-
-\dude{Arrgh, what do we say about how to simulate moving anyons around
-the lattice ?}
-
-\stf{Cite~\cite{Pfeifer2012} for braiding tricks}
+Following the result of these charge measurements, the decoder determines a recovery operation that involves fusion of subsets of anyons.
+These fusion results can be calculated in an analogous way, and the output charge placed at an appropriate point in the lattice.
+This procedure is iterated until either the decoder terminates successfully, or the simulation itself declares failure.
 
@@
 	\includegraphics[width=\columnwidth]{anyons-kyle.pdf}
-\caption{\stf{polish this a bit} Decoder failure as a function of simulation time for various lattice sizes, showing 
-threshold behavior at around $t_{\mathrm{sim}}\simeq 0.125$.}
+\caption{The decoder failure rate (a lower bound on the logical error probability) is shown as a function of simulation time for linear lattice sizes from $L=16$ to $128$.
+This exhibits threshold behaviour at a critical memory lifetime of $t_{\mathrm{sim}}^*\simeq 0.125$.
+This implies the Fibonacci anyon code simulated here is able to perfectly reliably store quantum information for times less than $t_{\mathrm{sim}}^*$ in the $L\to \infty$ limit.}
 \label{f:threshold}

### 2015-06-03 fib2.tex
resolved bibkey conflict for new jw00t ref

@@
 Recent investigations have begun to explore quantum error correction for nonabelian anyon 
-models~\cite{Brell2013, Wootton2013, Hutter2014, Wootton2015}. Nonabelian anyon models are especially interesting 
+models~\cite{Brell2013, Wootton2013, Hutter2014, Wootton2015b}. Nonabelian anyon models are especially interesting 
 because braiding and fusion of these anyons in general allows for the implementation of universal quantum 
@@
 Our error-correction algorithm is
-based on a hierarchical clustering algorithm~\cite{Hastie2009, Wootton2015},
+based on a hierarchical clustering algorithm~\cite{Hastie2009, Wootton2015b},
 and follows a similar strategy to the hard-decision renormalization group decoder~\cite{Bravyi2011}. 

### 2015-06-03 fib2.tex
Consolidated figures 2 & 3. Fixed a couple of typos and added a few line breaks to make it more git friendly.

@@
 \usepackage{tikz}
-\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit,shapes.misc}
+\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit}
 
@@
 \hypersetup{pdfauthor={Simon Burton, Courtney G. Brell, Steven T. Flammia}}
-%\hypersetup{pdftitle={Title\ Goes\ Here}}
+\hypersetup{pdftitle={Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code}}
 
@@
 	\end{align}
-where $a$, $b$, and $c$ represent particle types, or $F$-moves, representing the associativity rule for fusion processes, denoted as
+where $a$, $b$, and $c$ represent particle types, or $F$-moves, representing the associativity rule for fusion processes, 
 	\begin{align}
@@
 These manipulations encode the data of the unitary modular tensor category, and can be used to represent the state of a system of anyons as a linear combination of fusion trees.
-For the Fibonacci anyons, the non-trivial $R$ and $F$ moves are given by
+For the Fibonacci anyons, the non-trivial $R$ and $F$ moves are
 \begin{equation*}
@@
 Our simulation is in effect that of a $(2+1)$-dimensional topological quantum field theory, which allows for topological processes such as pair-creation, braiding, and fusion of anyonic charges. 
-This is modelled on a periodic $L\times L$ square lattice $\Lambda$ of \emph{tiles} on which anyons can reside.
+This is modeled on a periodic $L\times L$ square lattice $\Lambda$ of \emph{tiles} on which anyons can reside. 
 This treatment applies equally well to lattice models, where anyons can only be located at a discrete set of points, or continuum models, where a discretization of the manifold must be chosen in order to perform charge measurements.
-In the former case, each tile of $\Lambda$ represents a lattice site, while in the latter case each tile represents a measurement region.
-For more details of an analogous model, see~\cite{Brell2013}.
+In the former case, each tile of $\Lambda$ represents a lattice site, while in the latter case each tile represents a measurement region. For more details of an analogous model, see~\cite{Brell2013}.
 
@@
 
-In order to keep track of the state of the system 
-we maintain a set of disjoint curves, \cggb{do they need to be directed, or is that just for the figure?} representing the history of anyons on the lattice.
+In order to keep track of the state of the system we maintain a set of disjoint curves, 
+\cggb{do they need to be directed, or is that just for the figure?} 
+representing the history of anyons on the lattice.
 These curves can also be thought of as a top-down view of the fusion tree:
@@
 dimensional manifold in a haphazard way determined by the progress of the simulation.
-This allows a dynamically generated basis for the fusion space that easily allows for tensor 
-decomposition into factors corresponding 
-to disjoint components. 
-used a single fixed basis for the fusion space (determined by row-major ordering of 
-sites)~\cite{Brell2013}.
+This creates a dynamically generated basis for the fusion space that easily allows for tensor factorization of disjoint components. 
+%For comparison, previous work used a single fixed basis for the fusion space determined by row-major ordering of sites~\cite{Brell2013}.
 
@@
 Following this, the total charge can (probabilistically) simply be read off the relevant section of the fusion tree.
-An example of this procedure for a simple noise process is shown in \Fref{f:syndrome}, and the corresponding braid moves are shown in \Fref{f:syndrome2}.
-The technical details of the algorithm and data structures used
-for this procedure will be discussed elsewhere.
+An example of this procedure for a simple noise process is shown in \Fref{f:syndrome}, and the corresponding braid moves are shown in \Fref{f:syndrome}(e).
+The technical details of the algorithm and data structures used for this procedure will be discussed elsewhere.
 Braiding processes that encircle a non-trivial loop of our (toric) manifold can also be treated in an analogous way, following e.g.~\cite{Pfeifer2012}.
@@
 
-\begin{figure}[th!]
+\begin{figure}[t!]
 \begin{center}
-	\includegraphics[width=1.0\columnwidth]{pic-syndrome.pdf}\\
-\caption{(a) Noise processes initially form isolated sets of pair-created anyons, each crossing the boundary of a tile.
-These events are each represented by curves, where anyons are denoted by specific points on these curves.
-(b) In order to measure the total charge contained within each tile, we must first join the fusion trees associated with all such pairs.
-This corresponds to joining the edges associated with each pair into a continuous path, representing a basis for the fusion space chosen arbitrarily.
-(c) The total charge of each tile can then be found by braiding anyons around each other until all charges within a tile are neighbours on the path, as in (d).
-\cggb{We should think about the best way to represent the transition from (c) to (d).
-I think the current red lines might be confusing, but I don't have any great ideas.}}
-\label{f:syndrome}
-\end{center}
-\end{figure}
-
-\begin{figure}[th!]
-\begin{center}
+	\includegraphics[width=1.0\columnwidth]{pic-syndrome.pdf}\\[10pt]
+	(e)\ \ 
 	\begin{tikzpicture}[baseline=0.7cm,scale=0.3, xscale=0.9]
@@
 			\begin{scope}[xshift=6cm,yshift=2cm]
-				\draw plot [smooth, tension=1] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
+				\draw plot [smooth, tension=.6] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
 				\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
-				\draw plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
+				\draw plot [smooth, tension=.6] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
 			\end{scope}
 			\begin{scope}[xshift=4cm,yshift=4cm]
-				\draw plot [smooth, tension=1] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
+				\draw plot [smooth, tension=.6] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
 				\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
-				\draw plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
+				\draw plot [smooth, tension=.6] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
 			\end{scope}
@@
 		\end{tikzpicture}
-\caption{In order to transform from the configuration shown in \Fref{f:syndrome}(c) to \ref{f:syndrome}(d), several operations must be performed.
-The labels of the four leaves of these fusion trees correspond to the four anyons taken from the top of the path in \Fref{f:syndrome}(c) to the bottom.
+\caption{(a) Noise processes initially form isolated sets of pair-created anyons, each crossing the boundary of a tile. 
+These events are each represented by curves, where anyons are denoted by specific points on these curves. 
+(b) In order to measure the total charge contained within each tile, we must first join the fusion trees associated with all such pairs. 
+This corresponds to joining the edges associated with each pair into a continuous path, representing a basis for the fusion space chosen arbitrarily. 
+(c) The total charge of each tile can then be found by braiding anyons around each other until all charges within a tile are neighbors on the path, as in (d). 
+The red lines correspond to the worldline braids that perform this step.
+(e) The specific braids required to transform (c) to (d), where the labels of the four leaves of these fusion trees correspond to the four anyons taken from the top of the path in (c) to the bottom. 
 Vacuum charges are denoted by dashed lines. 
-In order to rearrange the anyons so that particles 1 and 4 are neighbors, several braid moves must be performed as shown.
-The effect of these on the fusion tree can then be evaluated by the application of several $R$ and $F$ moves as defined in equations (\ref{e:rmove}) and (\ref{e:fmove}).
-After the manipulations shown, the total charges within each tile can be read off the diagram as $q$ and $q'$.}
-\label{f:syndrome2}
+After applying several $R$ and $F$ moves from equations (\ref{e:rmove}) and (\ref{e:fmove}), the total charges within each tile can be read off the diagram as $q$ and $q'$.}
+\label{f:syndrome}
 \end{center}
@@
 
-\begin{figure}[th!]
+\begin{figure}[t!]
 \begin{center}
@@
 \caption{The decoder failure rate (a lower bound on the logical error probability) is shown as a function of simulation time for linear lattice sizes from $L=16$ to $128$. 
-This exhibits threshold behaviour at a critical memory lifetime of $t_{\mathrm{sim}}^*\simeq 0.125$.
+This exhibits threshold behavior at a critical memory lifetime of $t_{\mathrm{sim}}^*\simeq 0.125$. 
 This implies the Fibonacci anyon code simulated here is able to perfectly reliably store quantum information for times less than $t_{\mathrm{sim}}^*$ in the $L\to \infty$ limit.}

### 2015-06-04 fib2.tex
Small changes.

@@
 expected excitations of the $\nu=\frac{12}{5}$ fractional quantum Hall 
-states~\cite{Slingerland2001}, and can also be realized in several spin 
+states~\cite{Slingerland2001}, and can be realized in several spin 
 models~\cite{Levin2005, Bonesteel2012, Kapit2013, Palumbo2014} and composite 
@@
 \end{center}
+\vspace{-10pt}
 \end{figure}
@@
 These events are each represented by curves, where anyons are denoted by specific points on these curves. 
-(b) In order to measure the total charge contained within each tile, we must first join the fusion trees associated with all such pairs. 
+(b) To measure the total charge contained within each tile, we must first join the fusion trees associated with all such pairs. 
 This corresponds to joining the edges associated with each pair into a continuous path, representing a basis for the fusion space chosen arbitrarily. 
@@
 (e) The specific braids required to transform (c) to (d), where the labels of the four leaves of these fusion trees correspond to the four anyons taken from the top of the path in (c) to the bottom. 
-Vacuum charges are denoted by dashed lines. 
-After applying several $R$ and $F$ moves from equations (\ref{e:rmove}) and (\ref{e:fmove}), the total charges within each tile can be read off the diagram as $q$ and $q'$.}
+Dashed lines denote vacuum charges. 
+After applying several $R$ and $F$ moves (see Eqs.~(\ref{e:rmove}) and (\ref{e:fmove})), the total charges within each tile can be read off the diagram as $q$ and $q'$.}
 \label{f:syndrome}
 \end{center}
+\vspace{-10pt}
 \end{figure}

### 2015-06-08 fib2.tex
i think it was a previous typo of mine that got this line commented, or was it on purpose? also trivial image rescaling.
take out all fusion trees and try to explain things using curve diagrams.

@@
-\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
+%\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
+\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4}
 \usepackage{times}
@@
 
-\usepackage{tikz}
-\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit}
+%\usepackage{tikz}
+%\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit}
 
@@
 
+\usepackage[normalem]{ulem}
+
 %------------------------------------------------------------------------------------------------------------%
@@
 \newcommand{\e}{\mathrm{e}}
+\newcommand{\vac}{\mathbb{I}}
 
@@
 error correction in anyon systems are typically drawn from a restricted class that displays 
-significant structure over a wide range of system parameters.
-We exploit this structure to classically simulate, and thereby demonstrate the success of, an 
+significant structure \dude{sparsity?} over a wide range of system parameters.
+We exploit this structure \dude{sparsity?} to classically simulate, and thereby demonstrate the success of, an 
 error-correction protocol for a quantum memory based on the universal Fibonacci anyon 
@@
 
-In order to efficiently classically simulate an error-correction protocol for a topologically ordered quantum memory, it is necessary to simulate the physical noise processes, the decoding algorithm, and the physical recovery operations.
-Decoding algorithms are typically designed to run efficiently on a classical computer, but there is generally no guarantee that the noise and recovery processes should be classically simulable.
-Because of this, almost all of the sizable research effort on active quantum error correction for topological systems has focused on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Fowler2015, Andrist2015}.
-%~\cite{Dennis2002, Duclos-Cianci2010, Bravyi2011, Bravyi2014}.
-Systems of abelian anyons are well suited to studying quantum error correction because (at the RG fixed point) noise and recovery processes can be efficiently simulated numerically, allowing lattice simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}.
-Standard algorithms are specifically tailored to exploit the abelian nature of these particles, particularly that abelian anyons cannot be used for quantum computation.
+In order to efficiently classically simulate an error-correction protocol for 
+a topologically ordered quantum memory, it is necessary to simulate 
+the physical noise processes, the decoding algorithm, and the physical recovery operations. 
+Decoding algorithms are typically designed to run efficiently on a 
+classical computer, but there is generally no guarantee that the 
+noise and recovery processes should be classically simulable.
+Because of this, almost all of the sizable research effort 
+on active quantum error correction for topological systems has focused 
+on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Fowler2015, Andrist2015}.
+Systems of abelian anyons are well suited to studying quantum 
+error correction because (at the RG fixed point) noise and 
+recovery processes can be efficiently simulated numerically, allowing lattice simulations 
+of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. 
+Standard algorithms are specifically tailored to exploit the abelian nature 
+of these particles, particularly that abelian anyons cannot be used for quantum computation.
 
@@
 model~\cite{Wootton2013, Hutter2014} that, while nonabelian, are not universal. The general dynamics of these particular anyon models is known to be efficiently classically simulable, a fact
-that was exploited to enable efficient simulation of error correction in these systems.
-When considering more general anyon models, their ability to perform universal quantum computation would seem a significant barrier to their simulation on a classical computer.
-While simulation of general dynamics does indeed seem intractable, we argue that the kinds of processes that are typical of thermal noise are sufficiently structured to allow for their classical simulation in the regimes where we expect successful error correction to be possible.
-This insight allows us to simulate the noise and recovery processes for a quantum code based on a universal anyon model.
+that was exploited to enable efficient simulation of error correction 
+in these systems. When considering more general anyon models, their 
+ability to perform universal quantum computation would seem a significant 
+barrier to their simulation on a classical computer. While simulation 
+of general dynamics does indeed seem intractable, we argue that 
+the kinds of processes that are typical of thermal noise 
+are sufficiently structured  \dude{sparse?} to allow for their classical simulation 
+in the regimes where we expect successful error correction to 
+be possible. This insight allows us to simulate the noise 
+and recovery processes for a quantum code based on a universal anyon model.
 
@@
 
-We use a flexible phenomenological model of dynamics and thermal noise to describe a system with Fibonacci anyon excitations.
-Within this model, we apply existing general topological error-correction protocols, and simulate the successful preservation of quantum information encoded in topological degrees of freedom.
-Topological quantum computation protocols using nonabelian anyons typically implicitly assume the existence of an error-correction protocol to correct for diffusion or unwanted creation of anyons.
-Our results are the first explicit demonstration that such a scheme will be successful when applied to a universal topological quantum computer.
+We use a flexible phenomenological model of dynamics and thermal 
+noise to describe a system with Fibonacci anyon excitations. Within 
+this model, we apply existing general topological error-correction protocols, and 
+simulate the successful preservation of quantum information encoded in topological 
+degrees of freedom. Topological quantum computation protocols using nonabelian anyons 
+typically implicitly assume the existence of an error-correction protocol to 
+correct for diffusion or unwanted creation of anyons. Our results 
+are the first explicit demonstration that such a scheme will 
+be successful when applied to a universal topological quantum computer.
 
 %------------------------------------------------------------------------------------------------------------%
-\paragraph{Modeling Fibonacci anyons.}
+%\paragraph{Modeling Fibonacci anyons.}
+%\paragraph{Topological quantum field theory.}
+\paragraph{Topological model.}
 
-The topological features of a physical anyon model are abstractly described by a unitary 
-modular tensor category~\cite{Wang2010b}. This object contains the data describing the 
-types of anyonic particles, as well as the results of topological operations such as braiding and 
-fusion of these anyons. The Fibonacci anyon model consists of only one non-trivial particle 
-type, conventionally labelled $\tau$. Denoting the vacuum by $\mathbb{I}$, we can describe 
-the possible fusion outcomes of Fibonacci anyons as $\tau\times\tau=\mathbb{I}+\tau$, 
-i.e.~two $\tau$ particles can either fuse to vacuum or to a $\tau$ particle.
+%The topological features of a physical anyon model are abstractly described by a unitary 
+%modular tensor category~\cite{Wang2010b}. This object contains the data describing the 
+%types of anyonic particles, as well as the results of topological operations such as braiding and 
+%fusion of these anyons. The Fibonacci anyon model consists of only one non-trivial particle 
+%type, conventionally labelled $\tau$. Denoting the vacuum by $\vac$, we can describe 
+%the possible fusion outcomes of Fibonacci anyons as $\tau\times\tau=\vac+\tau$, 
+%i.e.~two $\tau$ particles can either fuse to vacuum or to a $\tau$ particle.
+%
+%Associated with each set of fusion outcomes for a fixed number of $\tau$ particles is a basis 
+%vector for a Hilbert space, the \emph{fusion} space. For $n$ particles of type $\tau$, the 
+%dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ 
+%the golden ratio. Additionally, there is a global degeneracy associated with the topology of the 
+%manifold on which the anyons reside. We will consider systems with the topology of a torus, 
+%which for the Fibonacci anyons gives rise to a 2-fold degeneracy. For convenience 
+%(in particular to minimize finite-size effects in our numerical computations~\cite{Brell2013}), 
+%this global space is the one in which we will encode, and demonstrate protection of, quantum 
+%information.
+%
+%The fusion outcome of any particular experiment depends on the history of the particles, in 
+%particular how they have braided around one another. Braiding operations are treated as 
+%unitary actions on the fusion space. Pair-creation events should be considered isometries 
+%that enlarge the fusion space, while fusion events correspond to projective measurements 
+%of combined charge of some number of particles. For detailed description of these 
+%processes in Fibonacci anyons, see e.g.~Ref.~\cite{Nayak2008} and references therein. 
+%Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be 
+%sufficient to implement universal quantum computation~\cite{Freedman2002, Nayak2008}.
 
-Associated with each set of fusion outcomes for a fixed number of $\tau$ particles is a basis 
-vector for a Hilbert space, the \emph{fusion} space. For $n$ particles of type $\tau$, the 
-dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ 
-the golden ratio. Additionally, there is a global degeneracy associated with the topology of the 
-manifold on which the anyons reside. We will consider systems with the topology of a torus, 
-which for the Fibonacci anyons gives rise to a 2-fold degeneracy. For convenience 
-(in particular to minimize finite-size effects in our numerical computations~\cite{Brell2013}), 
-this global space is the one in which we will encode, and demonstrate protection of, quantum 
-information.
+% From Picture TQFTs paper:
+%Within physics, TQFTs are referred to as “anyonic systems” [Wil][DFNSS]. These are
+%2-dimensional quantum mechanical systems with point like excitations (variously
+%called “quas-particle” or just “particle”, anyon, or perhaps “nonabelion”) which
+%under exchange exhibit exotic statistics: a nontrival representation of the braid
+%groups acting on a finite dimensional Hilbert space V consisting of “internal de-
+%grees of freedom”. Since these “internal degrees of freedom” sound mysterious,
+%we note that this information is accessed by fusion: fuse pairs of anyons along
+%a well defined trajectory and observe the outcome.
+%Statistics of anyons is described by unitary representations of the braid groups
 
-The fusion outcome of any particular experiment depends on the history of the particles, in 
-particular how they have braided around one another. Braiding operations are treated as 
-unitary actions on the fusion space. Pair-creation events should be considered isometries 
-that enlarge the fusion space, while fusion events correspond to projective measurements 
-of combined charge of some number of particles. For detailed description of these 
-processes in Fibonacci anyons, see e.g.~Ref.~\cite{Nayak2008} and references therein. 
-Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be 
-sufficient to implement universal quantum computation~\cite{Freedman2002, Nayak2008}.
+We consider a 
+2-dimensional system with
+point-like excitations or quasiparticles known as anyons.
+These anyons show exotic statistics under exchange.
+The worldlines of these exchanges form \emph{braids}
+in (2+1)-dimensions
+which act unitarily on (the Hilbert space of) degrees of freedom known as the \emph{fusion space.}
+To access this space we define
+the \emph{observables} of the system: these
+are regions bounded by circles (Wilson loops)
+and measure the total charge of the region.
+%The algebraic properties of these processes
+These dynamics and observables obey algebraic rules
+given by a unitary modular tensor category~\cite{Wang2010b} (UMTC).
 
-The dynamics and history of a system of anyons can be conveniently represented by a graphical calculus, which can be regarded as a representation of the world-lines of the particles.
-These diagrams can be manipulated by $R$-moves, corresponding to braiding processes:
+%As was noted in~\cite{Pfeifer2014}, when dealing with two-dimensional 
+%anyon dynamics, it is not sufficient to consider only
+%the algebraic (fusion/braiding) properties of the anyons,
+%one must also account for the algebra of observables. \cggb{This sentence seems odd here. Consider moving?}
+
+From the perspective of
+\emph{topological quantum field theory}
+(TQFT), anyons are modelled
+as punctures in a surface~\cite{Pfeifer2014}, and it is not
+the anyons themselves that braid, but the space
+around the anyons that becomes braided (twisted).
+The generators corresponding to the braid
+group generators are called half-twists.
+This is the perspective we adopt.
+In particular, this shows the action of braiding
+on arbitrary observables (Wilson loops) as
+these occupy the space around the anyons.
+
+The state of a collection of anyons
+can be described by the observables of the system.
+An important difference between abelian and non-abelian
+theories is this: the outcome of measurements in an abelian theory
+are determined by particle content only.
+That is, the fusion space is one-dimensional (a phase).
+This is no longer the case in a non-abelian theory.
+An example is Fibonacci: $\tau\times\tau=\tau+\vac$
+\emph{picture here?}
+%specify a state requires nesting multiple wilson lines.
+
+Non-intersecting loops commute (why?), and so
+a basis for the state can be built from a maximal
+%set of non-intersecting loops.
+set of disjoint and nested loops.
+\emph{picture?}
+%Observables measure the charge within a
+%region bounded by a directed closed loop.
+For three anyons, we relate two
+possible ways of nesting loops %these measurements
+via $F$-moves:
+\begin{align}
+\label{e:fmove}
+\includegraphics[]{pic-fmove.pdf}
+\end{align}
+Here we have shown particles with charges $a$, $b$, and $c$
+as well as total charge $d$.
+The lhs shows a state where the anyons with charge $a$ and $b$ are
+observed to have total charge $i$.
+The rhs involves a superposition (summation)
+over charge states $j$ of the anyons with charge $b$ and $c$.
+The green line serves to linearly
+order the anyons, and track
+deformations in the underlying space 
+(the history of braiding processes).
+It also denotes the direction along
+which $F$-moves occur.
+
+%Here we show how braids effect observables:
+%Here we show the $R$-move, corresponding to a (clockwise) braiding processes:
+A clockwise braiding process is represented by an $R$-move:
 \begin{align}
 \label{e:rmove}
-		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
-			\draw(0,0)--(0,1);
-			\draw plot [smooth, tension=1] coordinates { (0,1) (0.75,1.8) (-0.6,2.45) (-1,3)};
-			\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
-			\draw plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
-			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
-			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
-			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
-		\end{tikzpicture}
-		&\;\;=\;\;R^{ab}_c\cdot\;
-		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
-			\draw(0,0)--(0,1);
-			\draw(0,1)--(-1,2)--(-1,3);
-			\draw(0,1)--(1,2)--(1,3);
-			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
-			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
-			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
-		\end{tikzpicture}
+\includegraphics[]{pic-rmove.pdf}
 \end{align}
-where $a$, $b$, and $c$ represent particle types, or $F$-moves, representing the associativity rule for fusion processes, 
-	\begin{align}
-		\label{e:fmove}
-		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]
-			\draw(0,0)--(0,1)--(-2,3);
-			\draw(0,3)--(-1,2);
-			\draw(2,3)--(0,1);
-			\node at (-0.45,1.6) [anchor=north east] {{\scriptsize $i$}};
-			\node at (0,0) [anchor=west] {{\scriptsize $d$}};
-			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
-			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
-			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
-		\end{tikzpicture}
-		&\;\;=\;\;\sum_j[F^{abc}_d]_{ij}\cdot\;
-		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]		
-			\draw(0,0)--(0,1)--(-2,3);
-			\draw(0,3)--(1,2);
-			\draw(2,3)--(0,1);
-			\node at (0.42,1.63) [anchor=north west] {{\scriptsize $j$}};
-			\node at (0,0) [anchor=east] {{\scriptsize $d$}};
-			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
-			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
-			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
-		\end{tikzpicture}
-	\end{align}
+%where $a$, $b$, and $c$ represent particle types, and $F$-moves,
+%representing the associativity rule for fusion processes, 
+This is meant to show a \emph{half-twist} of the space
+inside the observable with value $c$
+holding two anyons (punctures) with charges $a$ and $b$.
+We are free to draw loops around charges,
+and in general braiding will twist these loops in different
+ways.
+\emph{picture?}
 
-These manipulations encode the data of the unitary modular tensor category, and can be used to represent the state of a system of anyons as a linear combination of fusion trees.
+These pictures (sans quantum) are called 
+\emph{curve diagrams} and are used in
+the study of braid groups \cite{Dehornoy2002}.
+In general, such a curve diagram is 
+a continuous embedding of a line that passes through 
+each puncture once. 
+Remarkably, any two such linear orderings are related by
+braiding (half-twists).
+
+The $R$ and $F$-moves obey composition of diagrams.
+\emph{picture?}
+Fusion is the ``reverse'' of composition: replace the
+interior of a disc by a single charge.
+\emph{picture?}
+
+%The dynamics and history of a system of anyons can be conveniently represented by a graphical calculus, which can be regarded as a representation of the world-lines of the particles.
+These diagrams can be manipulated by $R$-moves, corresponding to braiding processes:
+%	\begin{align}
+%	\label{e:rmove}
+%		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
+%			\draw(0,0)--(0,1);
+%			\draw plot [smooth, tension=1] coordinates { (0,1) (0.75,1.8) (-0.6,2.45) (-1,3)};
+%			\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
+%			\draw plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
+%			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
+%			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
+%			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
+%		\end{tikzpicture}
+%		&\;\;=\;\;R^{ab}_c\cdot\;
+%		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
+%			\draw(0,0)--(0,1);
+%			\draw(0,1)--(-1,2)--(-1,3);
+%			\draw(0,1)--(1,2)--(1,3);
+%			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
+%			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
+%			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
+%		\end{tikzpicture}
+%	\end{align}
+%where $a$, $b$, and $c$ represent particle types, or $F$-moves, representing the associativity rule for fusion processes, 
+%	\begin{align}
+%		\label{e:fmove}
+%		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]
+%			\draw(0,0)--(0,1)--(-2,3);
+%			\draw(0,3)--(-1,2);
+%			\draw(2,3)--(0,1);
+%			\node at (-0.45,1.6) [anchor=north east] {{\scriptsize $i$}};
+%			\node at (0,0) [anchor=west] {{\scriptsize $d$}};
+%			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
+%			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
+%			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
+%		\end{tikzpicture}
+%		&\;\;=\;\;\sum_j[F^{abc}_d]_{ij}\cdot\;
+%		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]		
+%			\draw(0,0)--(0,1)--(-2,3);
+%			\draw(0,3)--(1,2);
+%			\draw(2,3)--(0,1);
+%			\node at (0.42,1.63) [anchor=north west] {{\scriptsize $j$}};
+%			\node at (0,0) [anchor=east] {{\scriptsize $d$}};
+%			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
+%			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
+%			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
+%		\end{tikzpicture}
+%	\end{align}
+
+%These manipulations encode the data of the unitary modular tensor 
+%category, and can be used to represent the state of 
+%a system of anyons as a linear combination of fusion trees.
+
 For the Fibonacci anyons, the non-trivial $R$ and $F$ moves are 
 \begin{equation*}
-	R_{\mathbb{I}}^{\tau\tau} = \e^{\frac{-4\pi i}{5}} 
+	R_{\vac}^{\tau\tau} = \e^{\frac{-4\pi i}{5}} 
 	\ \ , \ \
@@
 \end{equation*}
-where the matrix is given in a basis labelled $(\mathbb{I},\tau)$.
+where the matrix is given in a basis labelled $(\vac,\tau)$.
 
-We use a phenomenological model of Fibonacci anyon dynamics which neglects any 
-microscopic details of the system. 
-This is consistent with the principles of topologically 
-ordered systems and anyonic physics, where the key universal features describing the 
-anyon model correspond to large length-scale physics, while the microscopic physics plays 
-a less important (and non-universal) role.
-Our simulation is in effect that of a $(2+1)$-dimensional topological quantum field theory, which allows for topological processes such as pair-creation, braiding, and fusion of anyonic charges. 
-This is modeled on a periodic $L\times L$ square lattice $\Lambda$ of \emph{tiles} on which anyons can reside. 
-This treatment applies equally well to lattice models, where anyons can only be located at a discrete set of points, or continuum models, where a discretization of the manifold must be chosen in order to perform charge measurements.
-In the former case, each tile of $\Lambda$ represents a lattice site, while in the latter case each tile represents a measurement region. For more details of an analogous model, see~\cite{Brell2013}.
-
-As was noted in~\cite{Pfeifer2014}, when dealing with two-dimensional 
-anyon dynamics, it is not sufficient to consider only
-the algebraic (fusion/braiding) properties of the anyons,
-one must also account for the algebra of observables. \cggb{This sentence seems odd here. Consider moving?}
+%We use a phenomenological model of Fibonacci anyon dynamics which neglects any 
+%microscopic details of the system. 
+%This is consistent with the principles of topologically 
+%ordered systems and anyonic physics, where the key universal features describing the 
+%anyon model correspond to large length-scale physics, while the microscopic physics plays 
+%a less important (and non-universal) role.
+%Our simulation is in effect that of a $(2+1)$-dimensional topological 
+%quantum field theory, which allows for topological processes such as 
+%pair-creation, braiding, and fusion of anyonic charges. 
+%This is modeled on a periodic $L\times L$ square lattice $\Lambda$ of \emph{tiles} on which anyons can reside. 
+%This treatment applies equally well to lattice models, where anyons 
+%can only be located at a discrete set of points, 
+%or continuum models, where a discretization of the manifold must 
+%be chosen in order to perform charge measurements. 
+%In the former case, each tile of $\Lambda$ represents a 
+%lattice site, while in the latter case each tile represents 
+%a measurement region. For more details of an analogous model, see~\cite{Brell2013}.
 
@@
 \begin{align}
-	H=-\sum_{i\in \Lambda}\proj{\mathbb{I}}_i\;,\label{e:hamiltonian}
+	H=-\sum_{i\in \Lambda}\proj{\vac}_i\;,\label{e:hamiltonian}
 \end{align}
-with $\proj{\mathbb{I}}_i$ the projector to charge $\mathbb{I}$ at site (or tile) $i$, i.e.~the ground 
+with $\proj{\vac}_i$ the projector to charge $\vac$ at site (or tile) $i$, i.e.~the ground 
 space of the model has vacuum (or no anyon) at each site. Given the toroidal boundary 
@@
 In order to perform a logical error on our code, a noise process must have support on a 
-ribbon running around a homologically nontrivial loop of the lattice. These correspond to 
+ribbon running around a homologically nontrivial loop of the lattice.
+\dude{any homologically nontrivial region is allowed for this, not just ribbons}
+These correspond to 
 processes in which anyonic charge is transported around the non-trivial loop before 
@@
 The decoder proceeds by measuring the occupations of 
-anyons at each site of the lattice, producing a \emph{syndrome} of occupied sites. Following this, it forms clusters of nearby anyons and 
+anyons at each site of the lattice, producing a \emph{syndrome} 
+of occupied sites. Following this, it forms clusters of nearby anyons and 
 measures the total charge within each cluster.
@@
 the rest are joined (agglomeratively~\cite{Hastie2009})
-at linearly increasing length scales. This iterative process concludes when there is at most a single cluster remaining (see \Fref{f:decode}).
+at linearly increasing length scales. This iterative process concludes when 
+there is at most a single cluster remaining (see \Fref{f:decode}).
 Note that unlike the case of abelian anyons, the decoder
@@
 Our simulation proceeds in this way as a dialogue between decoder
-and system, terminating when either the decoder itself terminates or when it performs a homologically nontrivial operation, thereby altering the codespace (and failing to perform successful information recovery).
-Note that, as was found in Ref.~\cite{Brell2013}, we expect that our qualitative results may be reproduced by most alternative families of decoders, although it may not be clear in all cases how to extend these decoders to the non-abelian setting.
+and system, terminating when either the decoder itself terminates or 
+when it performs a homologically nontrivial operation, thereby altering the 
+codespace (and failing to perform successful information recovery).
+Note that, as was found in Ref.~\cite{Brell2013}, we expect that 
+our qualitative results may be reproduced by most alternative families 
+of decoders, although it may not be clear in all cases how to extend these decoders to the non-abelian setting.
 The advantage of using a clustering decoder is 
-its simplicity and flexibility, and the fact that its clustering scheme is compatible with the structure in the noise processes that allows us to classically simulate them.
+its simplicity and flexibility, and the fact that its clustering 
+scheme is compatible with the structure \dude{sparsity?} in the noise 
+processes that allows us to classically simulate them.
 
@@
 in computational power to universal quantum computing (and thus unlikely to be classically 
-tractable), noise processes and error-correction procedures have structure that we can 
+tractable), noise processes and error-correction procedures have structure \dude{sparsity?} that we can 
 exploit to efficiently simulate typical processes of interest. In particular, those 
 processes in which we expect error-correction to succeed are also those that we expect to 
-be able to efficiently simulate for the following heuristic reasons (we leave a more rigorous analysis of simulability for noise and error correction processes as an open problem).
+be able to efficiently simulate for the following heuristic reasons 
+(we leave a more rigorous analysis of simulability for noise 
+and error correction processes as an open problem).
 
@@
 point in their history. 
-We are free to neglect the degrees of freedom associated with braiding between components because each component has trivial total charge.
+We are free to neglect the degrees of freedom associated with braiding between components 
+because each component has trivial total charge.
 This allows us to simulate the braiding processes within each component separately. 
@@
 component has size only $O(\log(n))$, we can typically simulate these dynamics efficiently 
-because the resulting fusion space has dimension $O(\mathrm{poly}(n))$. There are rare 
+because the resulting fusion space has dimension $O(\mathrm{poly}(n))$. There are \sout{rare}
 random processes that violate this reasoning, but processes such as these are suppressed 
@@
 longer expect to be able to efficiently simulate the noise and recovery processes in the system. 
-However, recall that logical errors in our system correspond to processes that act over a non-trivial loop of the torus. 
-Below the point at which the decoder begins to create such nontrivial loops, our simulation remains efficient,
+However, recall that logical errors in our system correspond to 
+processes that act over a non-trivial loop of the torus. 
+Below the point at which the decoder begins to create 
+such nontrivial loops, our simulation remains efficient \dude{why are we still conflating these},
 while it begins to declare failure whenever non-trivial logical 
@@
 
+%In order to keep track of the state of the system we maintain a set of disjoint curves, 
+%\cggb{do they need to be directed, or is that just for the figure?} 
+%representing the history of anyons on the lattice.
+%These curves can also be thought of as a top-down view of the fusion tree:
+%the anyons comprising the fusion tree are here displayed as points along each curve. 
+%In general, the curves wind around our two 
+%dimensional manifold in a haphazard way determined by the progress of the simulation.
+%This creates a dynamically generated basis for the fusion space 
+%that easily allows for tensor factorization of disjoint components. 
+%For comparison, previous work used a single fixed basis for 
+%the fusion space determined by row-major ordering of sites~\cite{Brell2013}.
+
 In order to keep track of the state of the system we maintain a set of disjoint curves, 
-\cggb{do they need to be directed, or is that just for the figure?} 
-representing the history of anyons on the lattice.
-These curves can also be thought of as a top-down view of the fusion tree:
-the anyons comprising the fusion tree are here displayed as points along each curve. 
-In general, the curves wind around our two 
-dimensional manifold in a haphazard way determined by the progress of the simulation.
-This creates a dynamically generated basis for the fusion space that easily allows for tensor factorization of disjoint components. 
-%For comparison, previous work used a single fixed basis for the fusion space determined by row-major ordering of sites~\cite{Brell2013}.
-
-The application of a pair-creation noise process corresponds to the addition of an extra piece of curve to the lattice, along with two preferred points on it denoting the anyon locations. 
-Following the noise processes, our simulation must proceed to measure the total charge within each tile (the results of these measurements will form the error syndrome). 
-This requires joining any curves within that tile, and performing braid moves along the curves until all anyons within the tile have been localized within a contiguous region of the curve. 
-Following this, the total charge can (probabilistically) simply be read off the relevant section of the fusion tree.
-An example of this procedure for a simple noise process is shown in \Fref{f:syndrome}, and the corresponding braid moves are shown in \Fref{f:syndrome}(e).
-The technical details of the algorithm and data structures used for this procedure will be discussed elsewhere.
-Braiding processes that encircle a non-trivial loop of our (toric) manifold can also be treated in an analogous way, following e.g.~\cite{Pfeifer2012}.
-\cggb{This paragraph and the next still needs another look.}
+one for each connected component with trivial total charge.
+The application of a pair-creation noise process corresponds to the 
+addition of an extra piece of curve to the lattice supporting
+two new anyons.
+%along with two preferred points on it denoting the anyon locations. 
+Following the noise processes, our simulation must %proceed to 
+measure the total charge within each tile; the results of 
+these measurements will form the error syndrome. 
+This requires joining (arbitrarily) any curves that intersect that tile, 
+and then performing $R$ and $F$-moves on the resulting
+curve so that 
+all anyons within the tile have been 
+localized within a contiguous region of the curve. 
+(Heisenberg picture...)
+The observable corresponding to the tile is then
+represented in the state ...
+%The total charge is then (probabilistically) read off the 
+%relevant section of the fusion tree. 
+An example of this 
+procedure for a simple noise process is shown in \Fref{f:syndrome}.
+%and the corresponding braid moves are shown in \Fref{f:syndrome}(e).
+The combinatorial derivation of the algorithm and data structures used for 
+this procedure will be discussed elsewhere.
+%Braiding processes that encircle 
+%a non-trivial loop of our (toric) manifold can also be 
+%treated in an analogous way, following e.g.~\cite{Pfeifer2012}.
+%\cggb{This paragraph and the next still needs another look.}
 
@@
 \begin{center}
-	\includegraphics[width=1.0\columnwidth]{pic-syndrome.pdf}\\[10pt]
-	(e)\ \ 
-	\begin{tikzpicture}[baseline=0.7cm,scale=0.3, xscale=0.9]
-			\begin{scope}[xshift=2cm,yshift=2cm]		
-				\draw(1,0)--(0,1)[dashed];
-				\draw(0,1)--(-1,2)--(-1,3);
-				\draw(0,1)--(1,2)--(1,3);
-				\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
-				\node at (1,3) [anchor=west] {{\scriptsize $2$}};
-			\end{scope}
-			%			
-			\begin{scope}[xshift=4cm]
-				\draw(0,0)--(0,1)[dashed];
-				\draw(0,1)--(-1,2)--(1,4)--(1,5);
-				\draw(0,1)--(3,4)--(3,5);
-				\node at (1,5) [anchor=west] {{\scriptsize $3$}};
-				\node at (3,5) [anchor=west] {{\scriptsize $4$}};
-			\end{scope}
-		\end{tikzpicture}
-		\hspace{-3mm}$\longrightarrow$\hspace{1mm}
-		\begin{tikzpicture}[baseline=1.5cm,scale=0.3, xscale=1]
-			\begin{scope}[xshift=2cm,yshift=2cm]		
-				\draw(1,0)--(0,1)[dashed];
-				\draw(0,1)--(-1,2)--(-1,7);
-				\draw(0,1)--(1,2)--(1,5);
-				\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
-				\node at (1,3) [anchor=west] {{\scriptsize $2$}};
-				\node at (-1,7) [anchor=west] {{\scriptsize $1$}};
-				\node at (1,7) [anchor=west] {{\scriptsize $4$}};
-			\end{scope}
-			%			
-			\begin{scope}[xshift=4cm]
-				\draw(0,0)--(0,1)[dashed];
-				\draw(0,1)--(-1,2)--(1,4)--(1,5);
-				\draw(0,1)--(3,4)--(3,5);
-				\draw(3,7)--(3,9);
-				\node at (1,5) [anchor=west] {{\scriptsize $3$}};
-				\node at (3,5) [anchor=west] {{\scriptsize $4$}};
-				\node at (1,9) [anchor=west] {{\scriptsize $2$}};
-				\node at (3,9) [anchor=west] {{\scriptsize $3$}};
-			\end{scope}
-			%
-			\begin{scope}[xshift=6cm,yshift=2cm]
-				\draw plot [smooth, tension=.6] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
-				\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
-				\draw plot [smooth, tension=.6] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
-			\end{scope}
-			\begin{scope}[xshift=4cm,yshift=4cm]
-				\draw plot [smooth, tension=.6] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
-				\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
-				\draw plot [smooth, tension=.6] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
-			\end{scope}
-		\end{tikzpicture}
-		$\xrightarrow{R, F}$
-		\begin{tikzpicture}[baseline=0.2cm,scale=0.3,xscale=0.9]		
-			\draw(2,-1)--(0,1)[];
-			\draw(0,1)--(-1,2)--(-1,3);
-			\draw(0,1)--(1,2)--(1,3);
-			\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
-			\node at (1,3) [anchor=west] {{\scriptsize $4$}};
-			\node at (1,-0.05) [anchor=east] {{\scriptsize $q$}};
-			\draw(2,-1)--(2,-2)[dashed];
-			%			
-			\begin{scope}[xshift=4cm]
-				\draw(-2,-1)--(0,1)[];
-				\draw(0,1)--(-1,2)--(-1,3);
-				\draw(0,1)--(1,2)--(1,3);
-				\node at (-1,3) [anchor=west] {{\scriptsize $2$}};
-				\node at (1,3) [anchor=west] {{\scriptsize $3$}};
-				\node at (-1,0) [anchor=west] {{\scriptsize $q'$}};
-			\end{scope}
-		\end{tikzpicture}
-\caption{(a) Noise processes initially form isolated sets of pair-created anyons, each crossing the boundary of a tile. 
-These events are each represented by curves, where anyons are denoted by specific points on these curves. 
-(b) To measure the total charge contained within each tile, we must first join the fusion trees associated with all such pairs. 
-This corresponds to joining the edges associated with each pair into a continuous path, representing a basis for the fusion space chosen arbitrarily. 
-(c) The total charge of each tile can then be found by braiding anyons around each other until all charges within a tile are neighbors on the path, as in (d). 
+	\includegraphics[width=0.8\columnwidth]{pic-syndrome.pdf} %\\[10pt]
+%	(e)\ \ 
+%	\begin{tikzpicture}[baseline=0.7cm,scale=0.3, xscale=0.9]
+%			\begin{scope}[xshift=2cm,yshift=2cm]		
+%				\draw(1,0)--(0,1)[dashed];
+%				\draw(0,1)--(-1,2)--(-1,3);
+%				\draw(0,1)--(1,2)--(1,3);
+%				\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
+%				\node at (1,3) [anchor=west] {{\scriptsize $2$}};
+%			\end{scope}
+%			%			
+%			\begin{scope}[xshift=4cm]
+%				\draw(0,0)--(0,1)[dashed];
+%				\draw(0,1)--(-1,2)--(1,4)--(1,5);
+%				\draw(0,1)--(3,4)--(3,5);
+%				\node at (1,5) [anchor=west] {{\scriptsize $3$}};
+%				\node at (3,5) [anchor=west] {{\scriptsize $4$}};
+%			\end{scope}
+%		\end{tikzpicture}
+%		\hspace{-3mm}$\longrightarrow$\hspace{1mm}
+%		\begin{tikzpicture}[baseline=1.5cm,scale=0.3, xscale=1]
+%			\begin{scope}[xshift=2cm,yshift=2cm]		
+%				\draw(1,0)--(0,1)[dashed];
+%				\draw(0,1)--(-1,2)--(-1,7);
+%				\draw(0,1)--(1,2)--(1,5);
+%				\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
+%				\node at (1,3) [anchor=west] {{\scriptsize $2$}};
+%				\node at (-1,7) [anchor=west] {{\scriptsize $1$}};
+%				\node at (1,7) [anchor=west] {{\scriptsize $4$}};
+%			\end{scope}
+%			%			
+%			\begin{scope}[xshift=4cm]
+%				\draw(0,0)--(0,1)[dashed];
+%				\draw(0,1)--(-1,2)--(1,4)--(1,5);
+%				\draw(0,1)--(3,4)--(3,5);
+%				\draw(3,7)--(3,9);
+%				\node at (1,5) [anchor=west] {{\scriptsize $3$}};
+%				\node at (3,5) [anchor=west] {{\scriptsize $4$}};
+%				\node at (1,9) [anchor=west] {{\scriptsize $2$}};
+%				\node at (3,9) [anchor=west] {{\scriptsize $3$}};
+%			\end{scope}
+%			%
+%			\begin{scope}[xshift=6cm,yshift=2cm]
+%				\draw plot [smooth, tension=.6] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
+%				\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
+%				\draw plot [smooth, tension=.6] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
+%			\end{scope}
+%			\begin{scope}[xshift=4cm,yshift=4cm]
+%				\draw plot [smooth, tension=.6] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
+%				\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
+%				\draw plot [smooth, tension=.6] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
+%			\end{scope}
+%		\end{tikzpicture}
+%		$\xrightarrow{R, F}$
+%		\begin{tikzpicture}[baseline=0.2cm,scale=0.3,xscale=0.9]		
+%			\draw(2,-1)--(0,1)[];
+%			\draw(0,1)--(-1,2)--(-1,3);
+%			\draw(0,1)--(1,2)--(1,3);
+%			\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
+%			\node at (1,3) [anchor=west] {{\scriptsize $4$}};
+%			\node at (1,-0.05) [anchor=east] {{\scriptsize $q$}};
+%			\draw(2,-1)--(2,-2)[dashed];
+%			%			
+%			\begin{scope}[xshift=4cm]
+%				\draw(-2,-1)--(0,1)[];
+%				\draw(0,1)--(-1,2)--(-1,3);
+%				\draw(0,1)--(1,2)--(1,3);
+%				\node at (-1,3) [anchor=west] {{\scriptsize $2$}};
+%				\node at (1,3) [anchor=west] {{\scriptsize $3$}};
+%				\node at (-1,0) [anchor=west] {{\scriptsize $q'$}};
+%			\end{scope}
+%		\end{tikzpicture}
+\caption{
+(a) Noise processes initially form isolated sets of pair-created anyons, 
+each crossing the boundary of a tile. 
+%These events are 
+%each represented by curves, where anyons are denoted by specific 
+%points on these curves. 
+(b) To measure the total charge 
+contained within each tile, 
+we first join the participating curve 
+diagrams arbitrarily into a single curve diagram.
+%we must first join the fusion 
+%trees associated with all such pairs. 
+%This corresponds to joining 
+%the edges associated with each pair into a continuous path, 
+%representing a basis for the fusion space chosen arbitrarily. 
+(c) The total charge of each tile can then be found 
+by braiding anyons around each other until all charges within 
+a tile are neighbors on the path, as in (d).  
 The red lines correspond to the worldline braids that perform this step.
-(e) The specific braids required to transform (c) to (d), where the labels of the four leaves of these fusion trees correspond to the four anyons taken from the top of the path in (c) to the bottom. 
-Dashed lines denote vacuum charges. 
-After applying several $R$ and $F$ moves (see Eqs.~(\ref{e:rmove}) and (\ref{e:fmove})), the total charges within each tile can be read off the diagram as $q$ and $q'$.}
+%(e) The specific braids required to transform (c) 
+%to (d), where the labels of the four leaves of 
+%these fusion trees correspond to the four anyons taken from 
+%the top of the path in (c) to the bottom. 
+%Dashed lines denote vacuum charges. 
+%After applying several $R$ and $F$ moves (see Eqs.~(\ref{e:rmove}) and 
+%(\ref{e:fmove})), the total charges within each tile can be read off the diagram as $q$ and $q'$.
+}
 \label{f:syndrome}
@@
 
-Following the result of these charge measurements, the decoder determines a recovery operation that involves fusion of subsets of anyons. 
-These fusion results can be calculated in an analogous way, and the output charge placed at an appropriate point in the lattice. 
-This procedure is iterated until either the decoder terminates successfully, or the simulation itself declares failure.
+Following the result of these charge measurements, the decoder determines 
+a recovery operation that involves fusion of subsets of anyons. 
+These fusion results can be calculated in \sout{an analogous} the same way, 
+and the output charge placed at an appropriate point in the lattice. 
+This procedure is iterated until either the decoder terminates successfully, 
+or the simulation itself declares failure.
 
@@
 
-We can guarantee that error-correction will succeed whenever noise does not percolate, but it is possible that percolated events may still result in no error. 
-The connection between the percolation threshold and the error-correction threshold is not well understood in general~\cite{Hastings2014}, though it is clear that our threshold estimate will be a lower bound for the true threshold that may be found if all events (including those that have percolated) were simulated by an optimal decoder.
-However, calculations of such nontrivial operations suggest that all such processes will indeed result in a logical or leakage error.
-As such it is likely that neglecting full simulation for such events does not significantly affect our observed threshold value.
+We can guarantee that error-correction will succeed whenever noise does 
+not percolate \dude{um, what?}, 
+but it is possible that percolated events may still result in no error. 
+The connection between the percolation threshold and the error-correction threshold 
+is not well understood in general~\cite{Hastings2014}, though it is clear 
+that our threshold estimate will be a lower bound for 
+the true threshold that may be found if all events 
+(including those that have percolated) were simulated by an optimal decoder. 
+However, calculations of such nontrivial operations suggest that all such 
+processes will indeed result in a logical or leakage error.
+As such it is likely that neglecting full simulation for 
+such events does not significantly affect our observed threshold value.
 
@@
 We have demonstrated classical simulation of successful error correction in a universal anyon model. 
-Though we have chosen several properties of our model and simulation in a convenient way for simplicity, it seems highly unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}.
-In particular, although we have modeled our logical qubit as encoded in the global topological degrees of freedom of our system, we could have encoded it in the fusion space of several preferred $\tau$ anyons.
+Though we have chosen several properties of our model and 
+simulation in a convenient way for simplicity, it seems \sout{highly}
+unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}. 
+In particular, although we have modeled our logical qubit as 
+encoded in the global topological degrees of freedom of our 
+system, we could have encoded it in the fusion space of several preferred $\tau$\dude{?} anyons. 
 This situation would be appropriate to model error-correction routines for topological quantum computation. 
@@
 None of our techniques are restricted to simulation of Fibonacci anyon dynamics, and could 
-equally well be used to simulate successful error-correction protocols in an arbitrary anyon 
-code. 
-As such, our methods could be used to demonstrate successful error-correction in an arbitrary anyonic topological quantum computation.
+equally well be used to simulate successful error-correction protocols in an arbitrary anyon code. 
+As such, our methods could be used to demonstrate successful 
+error-correction in an arbitrary anyonic topological quantum computation.
 
 There are several interesting avenues for further research. 
-Although it is not completely obvious how to do so, applying these methods to more realistic models such as concrete microscopic spin models or models with non-topological features would give direct insight into practical error rates needed for topological quantum memories in non-Abelian systems.
-It would be extremely interesting to find \emph{classical} spin models whose phase diagram encodes the threshold for error correction in these systems~\cite{Dennis2002}.
-%Another potential direction is to incorporate tensor network methods for simulating anyons~\cite{Pfeifer2012, Singh2014} to improve the speed and scale of the simulations. 
+Although it is not completely obvious how to do so, 
+applying these methods to more realistic models such as concrete 
+microscopic spin models or models with non-topological features would give 
+direct insight into practical error rates needed for topological quantum memories in non-Abelian systems. 
+It would be extremely interesting to find \emph{classical} spin models 
+whose phase diagram encodes the threshold for error correction in these systems~\cite{Dennis2002}.
+%Another potential direction is to incorporate tensor network methods for 
+%simulating anyons~\cite{Pfeifer2012, Singh2014} to improve the speed and scale of the simulations. 
 Finally, perhaps the most important open question is whether 

### 2015-06-08 render.py

@@ -10,7 +10,6 @@ from pyx import canvas, path, deco, trafo, style, text, color, deformer
 text.set(mode="latex") 
 text.set(docopt="12pt")
 #text.preamble(r"\usepackage{amsmath}")
-#text.preamble(r"\
 
 rgb = color.rgb
 rgbfromhexstring = color.rgbfromhexstring
@@ -32,6 +31,15 @@ light_shade = rgb(0.85, 0.65, 0.1)
 light_shade = rgb(0.9, 0.75, 0.4)
 
 
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
 
 
 st_dashed = [style.linestyle.dashed]
@@ -54,7 +62,6 @@ def varrow(x, y0, y1, extra=[], label=None):
     arrow(x, y0, x, y1, extra)
     if label:
         c.text(x-0.1, (y0+y1)/2., label, [text.halign.boxright])
-
 
 def harrow(x0, x1, y, extra=[], label=None):
     arrow(x0, y, x1, y, extra)
@@ -84,7 +91,10 @@ if 0:
     
     c.writeEPSfile("halftwist-factor.eps")
     
-    # -------------------------------------------------
+#############################################################################
+#
+#
+
 
 text.set(docopt="12pt")
 
@@ -263,8 +273,13 @@ c.text(x-0.7, 0., "(b)")
 draw(x, 0.)
 
 
-c.writePDFfile("pic-decode.pdf")
+#c.writePDFfile("pic-decode.pdf")
 c.writeEPSfile("pic-decode.eps")
+
+
[…]

### 2015-06-08 fib2.tex
revtex 4-1
edits from skype call

@@
-%\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
-\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4}
+\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
+%\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4}
 \usepackage{times}
@@
 error correction in anyon systems are typically drawn from a restricted class that displays 
-significant structure \dude{sparsity?} over a wide range of system parameters.
-We exploit this structure \dude{sparsity?} to classically simulate, and thereby demonstrate the success of, an 
+significant structure over a wide range of system parameters.
+We exploit this structure to classically simulate, and thereby demonstrate the success of, an 
 error-correction protocol for a quantum memory based on the universal Fibonacci anyon 
@@
 the kinds of processes that are typical of thermal noise 
-are sufficiently structured  \dude{sparse?} to allow for their classical simulation 
+are sufficiently structured  to allow for their classical simulation 
 in the regimes where we expect successful error correction to 
@@
 
-These pictures (sans quantum) are called 
-\emph{curve diagrams} and are used in
+These pictures, abstracted from the quantum context,
+are called \emph{curve diagrams} and are used in
 the study of braid groups \cite{Dehornoy2002}.
@@
 In order to perform a logical error on our code, a noise process must have support on a 
-ribbon running around a homologically nontrivial loop of the lattice.
-\dude{any homologically nontrivial region is allowed for this, not just ribbons}
-These correspond to 
-processes in which anyonic charge is transported around the non-trivial loop before 
+a homologically nontrivial region of the lattice.
+These correspond to processes in which anyonic charge is transported around a non-trivial loop before 
 annihilating to vacuum.
@@
 its simplicity and flexibility, and the fact that its clustering 
-scheme is compatible with the structure \dude{sparsity?} in the noise 
+scheme is compatible with the structure in the noise 
 processes that allows us to classically simulate them.
@@
 in computational power to universal quantum computing (and thus unlikely to be classically 
-tractable), noise processes and error-correction procedures have structure \dude{sparsity?} that we can 
+tractable), noise processes and error-correction procedures have structure that we can 
 exploit to efficiently simulate typical processes of interest. In particular, those 
@@
 component has size only $O(\log(n))$, we can typically simulate these dynamics efficiently 
-because the resulting fusion space has dimension $O(\mathrm{poly}(n))$. There are \sout{rare}
+because the resulting fusion space has dimension $O(\mathrm{poly}(n))$. 
+There are 
 random processes that violate this reasoning, but processes such as these are suppressed 
@@
 particles on increasing length scales. While this kind of fusion would typically merge components, 
-forcing us to compute dynamics of larger and larger sets of anyons, large components are sparsely distributed 
+forcing us to compute dynamics of larger and larger sets of anyons,
+large components are sparsely distributed 
 (and thus unlikely to be merged), and in addition at each length scale the total number of 
@@
 
-Of course, if we were to consider noise so strong that 
-the components percolate over the entire lattice, we would no 
-longer expect to be able to efficiently simulate the noise and recovery processes in the system. 
-However, recall that logical errors in our system correspond to 
-processes that act over a non-trivial loop of the torus. 
-Below the point at which the decoder begins to create 
-such nontrivial loops, our simulation remains efficient \dude{why are we still conflating these},
-while it begins to declare failure whenever non-trivial logical 
-operations occur. This allows us to simulate large lattice sizes 
-in the successful error-correction (sub-percolated) regime, including up to $L=128$.
+At some point, with noise strong enough, the state will
+no longer decompose at all and computing dynamics will
+become exponentially difficult in the system size.
+However, for finite lattice size, this regime is somewhere
+beyond the decoder threshold, which is the 
+point at which the decoder creates nontrivial (extensive) loops.
+We can view the system state as a tensor network, on which
+the decoder is performing an (efficiently simulable) contraction.
+This enables simulation of error correction in
+the area around decoder threshold for lattice sizes up to $L=128.$
+\dude{more polish needed...}
+
+%Of course, if we were to consider noise so strong that 
+%the components percolate over the entire lattice, we would no 
+%longer expect to be able to efficiently simulate the noise and recovery processes in the system. 
+%However, recall that logical errors in our system correspond to 
+%processes that act over a non-trivial loop of the torus. 
+%Below the point at which the decoder begins to create 
+%such nontrivial loops, our simulation remains efficient
+%while it begins to declare failure whenever non-trivial logical 
+%operations occur. This allows us to simulate large lattice sizes 
+%in the successful error-correction (sub-percolated) regime, including up to $L=128$.
 
@@
 a recovery operation that involves fusion of subsets of anyons. 
-These fusion results can be calculated in \sout{an analogous} the same way, 
+These fusion results can be calculated in the same way, 
 and the output charge placed at an appropriate point in the lattice. 
@@
 
-We can guarantee that error-correction will succeed whenever noise does 
-not percolate \dude{um, what?}, 
+We can guarantee that error-correction will succeed whenever
+the action of noise plus decoder 
+does not percolate the anyons accross the lattice,
 but it is possible that percolated events may still result in no error. 
@@
 Though we have chosen several properties of our model and 
-simulation in a convenient way for simplicity, it seems \sout{highly}
-unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}. 
+simulation in a convenient way for simplicity,
+Ref.~\cite{Brell2013} presents good evidence that it is
+unlikely that these choices will affect our results qualitatively.
+%it seems highly
+%unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}. 
 In particular, although we have modeled our logical qubit as 
 encoded in the global topological degrees of freedom of our 
-system, we could have encoded it in the fusion space of several preferred $\tau$\dude{?} anyons. 
+system, we could have encoded it in the fusion space of several preferred anyons. 
 This situation would be appropriate to model error-correction routines for topological quantum computation. 

### 2015-06-08 render.py

@@ -550,9 +550,9 @@ c.stroke(path.line(x-1.2*r, y, x+1.5*r, y), grarrow)
 ellipse(x, y, r, r)
 
 anyon(x-0.4*r, 0)
-c.text(x-0.3*r, 0.3*r, "$\scriptstyle b$", south)
+c.text(x-0.3*r, 0.3*r, "$\scriptstyle a$", south)
 anyon(x+0.4*r, 0)
-c.text(x+0.3*r, -0.3*r, "$\scriptstyle a$", north)
+c.text(x+0.3*r, -0.3*r, "$\scriptstyle b$", north)
 
 c.text(x+r, y-r, "$\scriptstyle c$", southwest)
 

### 2015-06-08 fib2.tex
more editing; shrink fig 2; add another diagram

@@
 These dynamics and observables obey algebraic rules
-given by a unitary modular tensor category~\cite{Wang2010b} (UMTC).
+given by a unitary modular tensor category~\cite{Wang2010b}. % (UMTC).
 
@@
 This is no longer the case in a non-abelian theory.
-An example is Fibonacci: $\tau\times\tau=\tau+\vac$
-\emph{picture here?}
+%An example is Fibonacci: $\tau\times\tau=\tau+\vac$
+%\emph{picture here?}
 %specify a state requires nesting multiple wilson lines.
+In particular, we consider a system supporting Fibonacci
+anyon excitations, denoted by $\tau.$
+Two such anyons can have total charge
+that is a superposition of $\tau$ and $\vac$ (vacuum),
+so the fusion space in this case is 2-dimensional:
+\begin{align*}
+\includegraphics[]{pic-fibonacci.pdf}
+\end{align*}
+For $n$ anyons of type $\tau$, the 
+dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ 
+the golden ratio. Additionally, there is a global degeneracy associated with the topology of the 
+manifold on which the anyons reside. We will consider systems with the topology of a torus, 
+which for the Fibonacci anyons gives rise to a 2-fold degeneracy.
+%For convenience 
+%(in particular to minimize finite-size effects in our numerical computations~\cite{Brell2013}), 
+This global space is the one in which we will encode, and demonstrate protection of, quantum 
+information.
 
-Non-intersecting loops commute (why?), and so
+Non-intersecting loops commute, and so
 a basis for the state can be built from a maximal
-%set of non-intersecting loops.
-set of disjoint and nested loops.
-\emph{picture?}
-%Observables measure the charge within a
-%region bounded by a directed closed loop.
+set of disjoint, nested loops.
 For three anyons, we relate two
@@
 ways.
-\emph{picture?}
+\dude{picture? ref Fig 2?}
 
@@
 braiding (half-twists).
+\dude{optional paragraph..}
 
 The $R$ and $F$-moves obey composition of diagrams.
-\emph{picture?}
+\dude{picture?}
 Fusion is the ``reverse'' of composition: replace the
 interior of a disc by a single charge.
-\emph{picture?}
-
-%The dynamics and history of a system of anyons can be conveniently represented by a graphical calculus, which can be regarded as a representation of the world-lines of the particles.
-These diagrams can be manipulated by $R$-moves, corresponding to braiding processes:
-%	\begin{align}
-%	\label{e:rmove}
-%		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
-%			\draw(0,0)--(0,1);
-%			\draw plot [smooth, tension=1] coordinates { (0,1) (0.75,1.8) (-0.6,2.45) (-1,3)};
-%			\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
-%			\draw plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
-%			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
-%			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
-%			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
-%		\end{tikzpicture}
-%		&\;\;=\;\;R^{ab}_c\cdot\;
-%		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
-%			\draw(0,0)--(0,1);
-%			\draw(0,1)--(-1,2)--(-1,3);
-%			\draw(0,1)--(1,2)--(1,3);
-%			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
-%			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
-%			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
-%		\end{tikzpicture}
-%	\end{align}
-%where $a$, $b$, and $c$ represent particle types, or $F$-moves, representing the associativity rule for fusion processes, 
-%	\begin{align}
-%		\label{e:fmove}
-%		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]
-%			\draw(0,0)--(0,1)--(-2,3);
-%			\draw(0,3)--(-1,2);
-%			\draw(2,3)--(0,1);
-%			\node at (-0.45,1.6) [anchor=north east] {{\scriptsize $i$}};
-%			\node at (0,0) [anchor=west] {{\scriptsize $d$}};
-%			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
-%			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
-%			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
-%		\end{tikzpicture}
-%		&\;\;=\;\;\sum_j[F^{abc}_d]_{ij}\cdot\;
-%		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]		
-%			\draw(0,0)--(0,1)--(-2,3);
-%			\draw(0,3)--(1,2);
-%			\draw(2,3)--(0,1);
-%			\node at (0.42,1.63) [anchor=north west] {{\scriptsize $j$}};
-%			\node at (0,0) [anchor=east] {{\scriptsize $d$}};
-%			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
-%			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
-%			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
-%		\end{tikzpicture}
-%	\end{align}
-
-%These manipulations encode the data of the unitary modular tensor 
-%category, and can be used to represent the state of 
-%a system of anyons as a linear combination of fusion trees.
+\dude{picture?}
 
@@
 where the matrix is given in a basis labelled $(\vac,\tau)$.
+%unitary actions on the fusion space. Pair-creation events should be considered isometries 
+%that enlarge the fusion space, while fusion events correspond to projective measurements 
+%of combined charge of some number of particles.
+For detailed description of these 
+processes in Fibonacci anyons, see e.g.~Ref.~\cite{Nayak2008} and references therein. 
+Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be 
+sufficient to implement universal quantum computation~\cite{Freedman2002, Nayak2008}.
+
+This treatment of anyon dynamics we consider to be a phenomenological model;
+it neglects any microscopic details of the system.
+This is consistent with the principles of topologically 
+ordered systems and anyonic physics, where the key universal features describing the 
+anyon model correspond to large length-scale physics, while the microscopic physics plays 
+a less important (and non-universal) role.
 
@@
 localized within a contiguous region of the curve. 
-(Heisenberg picture...)
+\dude{Heisenberg picture?}
 The observable corresponding to the tile is then
-represented in the state ...
+represented in the state \dude{polish}.
 %The total charge is then (probabilistically) read off the 
@@
 \begin{center}
-	\includegraphics[width=0.8\columnwidth]{pic-syndrome.pdf} %\\[10pt]
-%	(e)\ \ 
-%	\begin{tikzpicture}[baseline=0.7cm,scale=0.3, xscale=0.9]
-%			\begin{scope}[xshift=2cm,yshift=2cm]		
-%				\draw(1,0)--(0,1)[dashed];
-%				\draw(0,1)--(-1,2)--(-1,3);
-%				\draw(0,1)--(1,2)--(1,3);
-%				\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
-%				\node at (1,3) [anchor=west] {{\scriptsize $2$}};
-%			\end{scope}
-%			%			
-%			\begin{scope}[xshift=4cm]
-%				\draw(0,0)--(0,1)[dashed];
-%				\draw(0,1)--(-1,2)--(1,4)--(1,5);
-%				\draw(0,1)--(3,4)--(3,5);
-%				\node at (1,5) [anchor=west] {{\scriptsize $3$}};
-%				\node at (3,5) [anchor=west] {{\scriptsize $4$}};
-%			\end{scope}
-%		\end{tikzpicture}
-%		\hspace{-3mm}$\longrightarrow$\hspace{1mm}
-%		\begin{tikzpicture}[baseline=1.5cm,scale=0.3, xscale=1]
-%			\begin{scope}[xshift=2cm,yshift=2cm]		
-%				\draw(1,0)--(0,1)[dashed];
-%				\draw(0,1)--(-1,2)--(-1,7);
-%				\draw(0,1)--(1,2)--(1,5);
-%				\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
-%				\node at (1,3) [anchor=west] {{\scriptsize $2$}};
-%				\node at (-1,7) [anchor=west] {{\scriptsize $1$}};
-%				\node at (1,7) [anchor=west] {{\scriptsize $4$}};
-%			\end{scope}
-%			%			
-%			\begin{scope}[xshift=4cm]
-%				\draw(0,0)--(0,1)[dashed];
-%				\draw(0,1)--(-1,2)--(1,4)--(1,5);
-%				\draw(0,1)--(3,4)--(3,5);
-%				\draw(3,7)--(3,9);
-%				\node at (1,5) [anchor=west] {{\scriptsize $3$}};
-%				\node at (3,5) [anchor=west] {{\scriptsize $4$}};
-%				\node at (1,9) [anchor=west] {{\scriptsize $2$}};
-%				\node at (3,9) [anchor=west] {{\scriptsize $3$}};
-%			\end{scope}
-%			%
-%			\begin{scope}[xshift=6cm,yshift=2cm]
-%				\draw plot [smooth, tension=.6] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
-%				\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
-%				\draw plot [smooth, tension=.6] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
-%			\end{scope}
-%			\begin{scope}[xshift=4cm,yshift=4cm]
-%				\draw plot [smooth, tension=.6] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
-%				\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
-%				\draw plot [smooth, tension=.6] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
-%			\end{scope}
-%		\end{tikzpicture}
-%		$\xrightarrow{R, F}$
-%		\begin{tikzpicture}[baseline=0.2cm,scale=0.3,xscale=0.9]		
-%			\draw(2,-1)--(0,1)[];
-%			\draw(0,1)--(-1,2)--(-1,3);
-%			\draw(0,1)--(1,2)--(1,3);
-%			\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
-%			\node at (1,3) [anchor=west] {{\scriptsize $4$}};
-%			\node at (1,-0.05) [anchor=east] {{\scriptsize $q$}};
-%			\draw(2,-1)--(2,-2)[dashed];
-%			%			
-%			\begin{scope}[xshift=4cm]
-%				\draw(-2,-1)--(0,1)[];
-%				\draw(0,1)--(-1,2)--(-1,3);
-%				\draw(0,1)--(1,2)--(1,3);
-%				\node at (-1,3) [anchor=west] {{\scriptsize $2$}};
-%				\node at (1,3) [anchor=west] {{\scriptsize $3$}};
-%				\node at (-1,0) [anchor=west] {{\scriptsize $q'$}};
-%			\end{scope}
-%		\end{tikzpicture}
+	\includegraphics[width=1.0\columnwidth]{pic-syndrome.pdf}
 \caption{
@@
 each crossing the boundary of a tile. 
-%These events are 
-%each represented by curves, where anyons are denoted by specific 
-%points on these curves. 
 (b) To measure the total charge 
@@
 diagrams arbitrarily into a single curve diagram.
-%we must first join the fusion 
-%trees associated with all such pairs. 
-%This corresponds to joining 
-%the edges associated with each pair into a continuous path, 
-%representing a basis for the fusion space chosen arbitrarily. 
 (c) The total charge of each tile can then be found 
 by braiding anyons around each other until all charges within 
-a tile are neighbors on the path, as in (d).  
+a tile are neighbors on the curve, as in (d).  
 The red lines correspond to the worldline braids that perform this step.
-%(e) The specific braids required to transform (c) 
-%to (d), where the labels of the four leaves of 
-%these fusion trees correspond to the four anyons taken from 
-%the top of the path in (c) to the bottom. 
-%Dashed lines denote vacuum charges. 
-%After applying several $R$ and $F$ moves (see Eqs.~(\ref{e:rmove}) and 
-%(\ref{e:fmove})), the total charges within each tile can be read off the diagram as $q$ and $q'$.
 }

### 2015-06-08 render.py

@@ -9,7 +9,7 @@ from pyx import canvas, path, deco, trafo, style, text, color, deformer
 
 text.set(mode="latex") 
 text.set(docopt="12pt")
-#text.preamble(r"\usepackage{amsmath}")
+text.preamble(r"\usepackage{amsmath,amsfonts,amssymb}")
 
 rgb = color.rgb
 rgbfromhexstring = color.rgbfromhexstring
@@ -91,12 +91,12 @@ if 0:
     
     c.writeEPSfile("halftwist-factor.eps")
     
+    text.set(docopt="12pt")
+
+
 #############################################################################
 #
 #
-
-
-text.set(docopt="12pt")
 
 def anyon(x, y, r=0.07):
     c.fill(path.circle(x, y, r), [white])
@@ -283,27 +283,36 @@ c.writeEPSfile("pic-decode.eps")
 
 
 #sys.exit(0)
-
-
-
-#dashed = [style.linestyle.dashed]
-#dotted = [style.linestyle.dotted]
+#text.set(docopt="10pt")
 
 dashed = []
 dotted = [style.linestyle.dashed]
 
-text.set(docopt="10pt")
 c = canvas.canvas()
+old_c = None
+def push():
+    global c, old_c
+    assert old_c is None
+    old_c = c
+    c = canvas.canvas()
+    
+def pop(extra=[]):
+    global c, old_c
+    old_c.insert(c, extra)
+    c = old_c
+    old_c = None
 
-
-w, h = 1.5, 1.5
-m = 0.1
 
 # --------------------------------------------------------------------
 
-x0, y0 = 0.6, h + 10*m
+w, h = 1.0, 1.0
+m = 0.1
 
-c.text(x0-0.8, y0, "(a)")
+#x0, y0 = 0.6, h + 10*m
+x0, y0 = 0., 0.
+
+push()
+#c.text(x0-0.8, y0, "(a)")
 
 c.stroke(path.rect(x0, y0, w, h), dashed)
 c.stroke(path.rect(x0+w+m, y0, w, h), dotted)
@@ -320,11 +329,15 @@ c.stroke(path.line(x0+1.5*w+m, y, x0+0.5*w, y), grarrow)
 anyon(x0+0.8*w, y)
 anyon(x0+m+1.2*w, y)
 
[…]

### 2015-06-08 fib2.tex
picture of braiding a loop

@@
-\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
-%\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4}
+%\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
+\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4}
 \usepackage{times}
@@
 \dude{picture? ref Fig 2?}
+
+Braiding within an observable will only change the phase
+of that observable \dude{???}, otherwise may twist these
+loops in various ways:
+\begin{align*}
+\includegraphics[]{pic-braid-loop.pdf}
+\end{align*}
 

### 2015-06-08 render.py
python code

@@ -70,6 +70,33 @@ def harrow(x0, x1, y, extra=[], label=None):
             [text.valign.bottom, text.halign.boxcenter])
 
 
+def anyon(x, y, r=0.07):
+    c.fill(path.circle(x, y, r), [white])
+    c.stroke(path.circle(x, y, r), [red, style.linewidth.thick])
+
+
+N = 20
+
+def dopath(ps, extra=[], fill=False, closepath=True):
+    ps = [path.moveto(*ps[0])]+[path.lineto(*p) for p in ps[1:]]
+    if closepath:
+        ps.append(path.closepath())
+    p = path.path(*ps)
+    if fill:
+        c.fill(p, [deformer.smoothed(0.3)]+extra+[color.rgb.white])
+    c.stroke(p, [deformer.smoothed(0.3)]+extra)
+
+def ellipse(x0, y0, rx, ry, extra=[], fill=False):
+    ps = []
+    for i in range(N):
+        theta = 2*pi*i / (N-1)
+        ps.append((x0+rx*sin(theta), y0+ry*cos(theta)))
+    dopath(ps, extra, fill)
+
+
+#############################################################################
+#
+#
 
 if 0:
     # -------------------------------------------------
@@ -98,9 +125,115 @@ if 0:
 #
 #
 
-def anyon(x, y, r=0.07):
-    c.fill(path.circle(x, y, r), [white])
-    c.stroke(path.circle(x, y, r), [red, style.linewidth.thick])
+c = canvas.canvas()
+
+
+r = 0.5
+w = 3.0
+
+ellipse(w, 0., 1.0*r, 1.8*r)
+
+class Tracer(object):
+    def __init__(self, x0, y0, r, theta):
+        self.x0 = x0
+        self.y0 = y0
+        self.theta = theta
+        self.r = r
+        self.ps = []
+
+    def get(self):
+        theta = self.theta
+        r = self.r
+        x = self.x0 + r*sin(theta)
+        y = self.y0 + r*cos(theta)
+        return x, y
+
+    def reset(self, r):
+        # recalculate x0, y0
+        if r==self.r:
+            return
+        x1, y1 = self.get()
+        theta = self.theta
+        self.x0 = x1 - r*sin(theta)
[…]

### 2015-06-10 fib2.tex
Some minor wordsmithing.

@@
 To access this space we define
-the \emph{observables} of the system: these
-are regions bounded by circles (Wilson loops)
-and measure the total charge of the region.
+the topological observables of the system: these
+are total charge measurements within regions bounded by closed loops (Wilson loops).
 %The algebraic properties of these processes
@@
 as punctures in a surface~\cite{Pfeifer2014}, and it is not
-the anyons themselves that braid, but the space
-around the anyons that becomes braided (twisted).
-The generators corresponding to the braid
-group generators are called half-twists.
+the anyons themselves that braid, but the manifold in which the anyons embed 
+is considered deformed (twisted) by these braid moves.
+%The generators corresponding to the braid
+%group generators are called half-twists.
+% -we thought this was a getting ahead of ourselves since we haven't introduced this stuff yet.
 This is the perspective we adopt.
@@
 on arbitrary observables (Wilson loops) as
-these occupy the space around the anyons.
+these deform with the manifold.
 
@@
 can be described by the observables of the system.
-An important difference between abelian and non-abelian
-theories is this: the outcome of measurements in an abelian theory
-are determined by particle content only.
-That is, the fusion space is one-dimensional (a phase).
-This is no longer the case in a non-abelian theory.
+The difference between abelian and non-abelian
+anyon theories is that the outcomes of measurements in an abelian theory
+are determined uniquely particle content only.
+That is, the fusion space is one-dimensional for abelian anyons, and generally larger for non-abelian anyons.
 %An example is Fibonacci: $\tau\times\tau=\tau+\vac$
@@
 %specify a state requires nesting multiple wilson lines.
-In particular, we consider a system supporting Fibonacci
+In particular, we consider a system supporting (non-abelian) Fibonacci
 anyon excitations, denoted by $\tau.$
@@
 that is a superposition of $\tau$ and $\vac$ (vacuum),
-so the fusion space in this case is 2-dimensional:
+so the fusion space in this case is 2-dimensional.
+We can represent basis states for this space using diagrams of definite total charge for the Wilson loops, and arbitrary states as linear combinations of these diagrams:
 \begin{align*}
@@
 \end{align*}
+
 For $n$ anyons of type $\tau$, the 
@@
 
-Non-intersecting loops commute, and so
-a basis for the state can be built from a maximal
+Observables associated to non-intersecting loops commute, and so
+a basis for the space can be built from a maximal
 set of disjoint, nested loops.
-For three anyons, we relate two
-possible ways of nesting loops %these measurements
+For three anyons, two
+possible ways of nesting loops are related %these measurements
 via $F$-moves:
@@
 as well as total charge $d$.
-The lhs shows a state where the anyons with charge $a$ and $b$ are
+The lefthand side shows a state where the anyons with charge $a$ and $b$ are
 observed to have total charge $i$.
-The rhs involves a superposition (summation)
-over charge states $j$ of the anyons with charge $b$ and $c$.
+The righthand side involves a superposition 
+over total charge $j$ of the anyons with charge $b$ and $c$.
 The green line serves to linearly
@@
 \dude{picture? ref Fig 2?}
-
-Braiding within an observable will only change the phase
-of that observable \dude{???}, otherwise may twist these
-loops in various ways:
+%
+%
+%Braiding within an observable will only change the phase
+%of that observable \dude{???}, otherwise may twist these
+%loops in various ways:
 \begin{align*}
@@
 \end{align*}
-
+%
+%
+These diagrams can be composed, and the fusion operation replaces the 
+interior of a disc by a single charge.
 These pictures, abstracted from the quantum context,
@@
 the study of braid groups \cite{Dehornoy2002}.
-In general, such a curve diagram is 
-a continuous embedding of a line that passes through 
-each puncture once. 
-Remarkably, any two such linear orderings are related by
-braiding (half-twists).
-\dude{optional paragraph..}
-
-The $R$ and $F$-moves obey composition of diagrams.
-\dude{picture?}
-Fusion is the ``reverse'' of composition: replace the
-interior of a disc by a single charge.
-\dude{picture?}
+%In general, such a curve diagram is 
+%a continuous embedding of a line that passes through 
+%each puncture once. 
+%Remarkably, any two such linear orderings are related by
+%braiding (half-twists).
+%\dude{optional paragraph..}
 
@@
 %pair-creation, braiding, and fusion of anyonic charges.
-%This is modeled on a periodic $L\times L$ square lattice $\Lambda$ of \emph{tiles} on which anyons can reside. 
-%This treatment applies equally well to lattice models, where anyons 
-%can only be located at a discrete set of points, 
-%or continuum models, where a discretization of the manifold must 
-%be chosen in order to perform charge measurements. 
-%In the former case, each tile of $\Lambda$ represents a 
-%lattice site, while in the latter case each tile represents 
-%a measurement region. For more details of an analogous model, see~\cite{Brell2013}.
 
@@
 \paragraph{Noise and error-correction.}
+
+We model the system on a periodic $L\times L$ square lattice $\Lambda$ of \emph{tiles} on which anyons can reside. 
+This treatment applies equally well to lattice models, where anyons 
+can only be located at a discrete set of points, 
+or continuum models, where a discretization of the manifold must 
+be chosen in order to perform charge measurements. 
+In the former case, each tile of $\Lambda$ represents a 
+lattice site, while in the latter case each tile represents 
+a measurement region. For more details of an analogous model, see~\cite{Brell2013}.
 
@@
 
-At some point, with noise strong enough, the state will
+At some point, with strong enough noise, the state will
 no longer decompose at all and computing dynamics will
@@
 point at which the decoder creates nontrivial (extensive) loops.
+\stf{CGB and I are still not confident in the previous sentence or the next one}
 We can view the system state as a tensor network, on which
@@
 
-%Of course, if we were to consider noise so strong that 
-%the components percolate over the entire lattice, we would no 
-%longer expect to be able to efficiently simulate the noise and recovery processes in the system. 
 %However, recall that logical errors in our system correspond to 
@@
 
-In order to keep track of the state of the system we maintain a set of disjoint curves, 
+In order to keep track of the state of the system we maintain 
+a set of disjoint directed curves, 
 one for each connected component with trivial total charge.

### 2015-06-10 fib2.tex
hopefully approaching a fixed point

@@
 
-We model the system on a periodic $L\times L$ square lattice $\Lambda$ of \emph{tiles} on which anyons can reside. 
-This treatment applies equally well to lattice models, where anyons 
-can only be located at a discrete set of points, 
-or continuum models, where a discretization of the manifold must 
-be chosen in order to perform charge measurements. 
-In the former case, each tile of $\Lambda$ represents a 
-lattice site, while in the latter case each tile represents 
-a measurement region. For more details of an analogous model, see~\cite{Brell2013}.
+%We model the system on a periodic $L\times L$ square lattice $\Lambda$ of \emph{tiles} on which anyons can reside. 
+%This treatment applies equally well to lattice models, where anyons 
+%can only be located at a discrete set of points, 
+%or continuum models, where a discretization of the manifold must 
+%be chosen in order to perform charge measurements. 
+%In the former case, each tile of $\Lambda$ represents a 
+%lattice site, while in the latter case each tile represents 
+%a measurement region. For more details of an analogous model, see~\cite{Brell2013}.
 
 We consider encoding a qubit of quantum information in the global degeneracy associated 
-with the topology of the manifold of our system. We imagine an idealized Hamiltonian for this 
-system of the form
+with the topology of the manifold of our system.
+We endow this manifold with a finite set of $L\times L$ observables arranged in
+a square lattice tiling $\Lambda$.
+These \emph{tiles} will be the oservables accesible to the error-correction procedure (\emph{decoder}).
+We imagine an idealized Hamiltonian for this system of the form
 \begin{align}
@@
 \end{align}
-with $\proj{\vac}_i$ the projector to charge $\vac$ at site (or tile) $i$, i.e.~the ground 
-space of the model has vacuum (or no anyon) at each site. Given the toroidal boundary 
-conditions, this space is two-fold degenerate as noted above. We identify this ground space 
-as the codespace of our model. Typical realistic noise processes in this kind of system are 
-pair-creation, hopping, exchange etc.~of anyons on neighboring sites of $\Lambda$. It was 
-seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only 
+with $\proj{\vac}_i$ the projector to charge $\vac$ at tile $i$, i.e.~the ground 
+space of the model has vacuum total charge in each tile.
+\dude{ouch this no longer works..}
+Given the toroidal boundary 
+conditions, this space is two-fold degenerate as noted above.
+We identify this ground space as the codespace of our model. 
+Typical realistic noise processes in this kind of system are 
+pair-creation, hopping, exchange etc.~of anyons on neighboring sites of $\Lambda$.
+It was seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only 
 is sufficient to capture the qualitative features of an error-correction simulation, and so for convenience we 
@@
 become exponentially difficult in the system size.
-However, for finite lattice size, this regime is somewhere
-beyond the decoder threshold, which is the 
-point at which the decoder creates nontrivial (extensive) loops.
-\stf{CGB and I are still not confident in the previous sentence or the next one}
-We can view the system state as a tensor network, on which
-the decoder is performing an (efficiently simulable) contraction.
+However, for finite lattice size, we use heuristics
+to minimize non-local braid moves, which helps to
+maintain the state as a separable product. \dude{???}
 This enables simulation of error correction in
 the area around decoder threshold for lattice sizes up to $L=128.$
-\dude{more polish needed...}
+%However, for finite lattice size, this regime is somewhere
+%beyond the decoder threshold, which is the 
+%point at which the decoder creates nontrivial (extensive) loops.
+%\stf{CGB and I are still not confident in the previous sentence or the next one}
+%We can view the system state as a tensor network, on which
+%the decoder is performing an (efficiently simulable) contraction.
+%This enables simulation of error correction in
+%the area around decoder threshold for lattice sizes up to $L=128.$
+%\dude{more polish needed...}
 
@@
 localized within a contiguous region of the curve. 
-\dude{Heisenberg picture?}
-The observable corresponding to the tile is then
-represented in the state \dude{polish}.
+%\dude{Heisenberg picture?}
+%The observable corresponding to the tile is then
+%represented in the state \dude{polish}.
 %The total charge is then (probabilistically) read off the 

### 2015-06-10 fib2.tex
edits: looking good to me

@@
 \emph{topological quantum field theory}
-(TQFT), anyons are modelled
+anyons are modelled
 as punctures in a surface~\cite{Pfeifer2014}, and it is not
-the anyons themselves that braid, but the manifold in which the anyons embed 
-is considered deformed (twisted) by these braid moves.
-%The generators corresponding to the braid
-%group generators are called half-twists.
-% -we thought this was a getting ahead of ourselves since we haven't introduced this stuff yet.
+the anyons themselves that braid, but the manifold in which the anyons reside 
+becomes deformed (twisted) by these braid moves.
 This is the perspective we adopt.
@@
 and in general braiding will twist these loops in different
-ways.
-\dude{picture? ref Fig 2?}
-%
-%
-%Braiding within an observable will only change the phase
-%of that observable \dude{???}, otherwise may twist these
-%loops in various ways:
+ways:
 \begin{align*}
@@
 These \emph{tiles} will be the oservables accesible to the error-correction procedure (\emph{decoder}).
-We imagine an idealized Hamiltonian for this system of the form
+We can use these observables to construct an idealized Hamiltonian for this system of the form
 \begin{align}
-	H=-\sum_{i\in \Lambda}\proj{\vac}_i\;,\label{e:hamiltonian}
+	H=-\sum_{T\in \Lambda}\proj{\vac}_T\;,\label{e:hamiltonian}
 \end{align}
-with $\proj{\vac}_i$ the projector to charge $\vac$ at tile $i$, i.e.~the ground 
+with $\proj{\vac}_T$ the projector to charge $\vac$ at tile $T$, i.e.~the ground 
 space of the model has vacuum total charge in each tile.
-\dude{ouch this no longer works..}
 Given the toroidal boundary 
-conditions, this space is two-fold degenerate as noted above.
-We identify this ground space as the codespace of our model. 
+conditions, this space contains the two-fold degenerate codespace.
+%We identify this ground space as the codespace of our model. 
 Typical realistic noise processes in this kind of system are 
@@
 to minimize non-local braid moves, which helps to
-maintain the state as a separable product. \dude{???}
+maintain the state as a separable product.
 This enables simulation of error correction in

### 2015-06-10 fib2.tex
more edits

@@
 
+% We need to relate this to discrete models: toric code, string nets, etc.
+
 We consider encoding a qubit of quantum information in the global degeneracy associated 
 with the topology of the manifold of our system.
-We endow this manifold with a finite set of $L\times L$ observables arranged in
+We endow this manifold with a finite set of $L\times L$ Wilson loops arranged in
 a square lattice tiling $\Lambda$.
-These \emph{tiles} will be the oservables accesible to the error-correction procedure (\emph{decoder}).
+%We tile the manifols with  a finite set of $L\times L$ Wilson loops arranged in
+These \emph{tiles} will be the observables accesible to the error-correction procedure (\emph{decoder}).
 We can use these observables to construct an idealized Hamiltonian for this system of the form
@@
 %We identify this ground space as the codespace of our model.
+
 Typical realistic noise processes in this kind of system are 
@@
 
-At some point, with strong enough noise, the state will
+In the regime where the action of noise plus decoder does not percolate it is
+clear that the simulation is efficient.
+However at some point, with strong enough noise, the state will
 no longer decompose at all and computing dynamics will
 become exponentially difficult in the system size.
-However, for finite lattice size, we use heuristics
-to minimize non-local braid moves, which helps to
-maintain the state as a separable product.
+Despite this, we use heuristics %for finite lattice size, we use heuristics
+that minimize non-local braid moves, which helps to
+maintain the state as a separable product beyond the
+sub-percolated regime.
 This enables simulation of error correction in

### 2015-06-10 fib2.tex
many more edits.

@@
 %------------------------------------------------------------------------------------------------------------%
-%\paragraph{Modeling Fibonacci anyons.}
-%\paragraph{Topological quantum field theory.}
 \paragraph{Topological model.}
@@
 the topological observables of the system: these
-are total charge measurements within regions bounded by closed loops (Wilson loops).
+are total charge measurements within regions bounded by \dude{directed} closed loops (Wilson loops).
 %The algebraic properties of these processes
@@
 given by a unitary modular tensor category~\cite{Wang2010b}. % (UMTC). 
+However, from the perspective of
+\emph{topological quantum field theory}
+anyons are modelled
+as punctures in a surface~\cite{Pfeifer2014}, and it is not
+the anyons themselves that braid,
+but the manifold in which the anyons reside 
+that becomes deformed (twisted) by these braid moves.
+This is the perspective we adopt (see \Fref{f:braidloop}).
+\dude{Fig or FIG ?}
+%In particular, this shows the action of braiding
+%on arbitrary observables (Wilson loops) as
+%these deform with the manifold.
 
@@
 
-From the perspective of
-\emph{topological quantum field theory}
-anyons are modelled
-as punctures in a surface~\cite{Pfeifer2014}, and it is not
-the anyons themselves that braid, but the manifold in which the anyons reside 
-becomes deformed (twisted) by these braid moves.
-This is the perspective we adopt.
-In particular, this shows the action of braiding
-on arbitrary observables (Wilson loops) as
-these deform with the manifold.
+\begin{figure}[t!]
+\begin{center}
+    \includegraphics[]{pic-braid-loop.pdf}
+\caption{
+%The perspective of TQFT.
+Here we show the world lines of a braid.
+%This braid relates two different ways of observing the same charges.
+In this case, we see how it relates two different ways of observing (or fusing) the top two charges.
+%This braid relates two different ways of observing the same charges.
+%We are free to draw these loops around charges,
+In general braiding will twist these loops in different ways
+according to how the manifold itself is being deformed.
+\label{f:braidloop}
+}
+\end{center}
+\vspace{-10pt}
+\end{figure}
 
-The state of a collection of anyons
-can be described by the observables of the system.
-The difference between abelian and non-abelian
+%The state \dude{space?} of a collection of anyons
+%can be described by the observables of the system.
+The \dude{key?} difference between abelian and non-abelian
 anyon theories is that the outcomes of measurements in an abelian theory
 are determined uniquely particle content only.
+%The defining characteristic of a \emph{non-abelian}
+%anyon theory is that ...
 That is, the fusion space is one-dimensional for abelian anyons, and generally larger for non-abelian anyons.
-%An example is Fibonacci: $\tau\times\tau=\tau+\vac$
-%\emph{picture here?}
-%specify a state requires nesting multiple wilson lines.
 In particular, we consider a system supporting (non-abelian) Fibonacci
@@
 so the fusion space in this case is 2-dimensional.
-We can represent basis states for this space using diagrams of definite total charge for the Wilson loops, and arbitrary states as linear combinations of these diagrams:
+We can represent basis states for this space using diagrams 
+of definite total charge for the Wilson loops, 
+and arbitrary states as linear combinations of these diagrams:
 \begin{align*}
@@
 \end{align*}
-
 For $n$ anyons of type $\tau$, the 
 dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ 
-the golden ratio. Additionally, there is a global degeneracy associated with the topology of the 
-manifold on which the anyons reside. We will consider systems with the topology of a torus, 
-which for the Fibonacci anyons gives rise to a 2-fold degeneracy.
-%For convenience 
-%(in particular to minimize finite-size effects in our numerical computations~\cite{Brell2013}), 
-This global space is the one in which we will encode, and demonstrate protection of, quantum 
-information.
+the golden ratio.
 
@@
 For three anyons, two
-possible ways of nesting loops are related %these measurements
+possible ways of nesting loops are related
 via $F$-moves:
@@
 over total charge $j$ of the anyons with charge $b$ and $c$.
+
+A clockwise braiding process is represented by an $R$-move:
+\begin{align}
+\label{e:rmove}
+\includegraphics[]{pic-rmove.pdf}
+\end{align}
+This is meant to show a \emph{half-twist} of the space
+inside the observable with value $c$
+holding two anyons (punctures) with charges $a$ and $b$.
+
 The green line serves to linearly
@@
 
-%Here we show how braids effect observables:
-%Here we show the $R$-move, corresponding to a (clockwise) braiding processes:
-A clockwise braiding process is represented by an $R$-move:
-\begin{align}
-\label{e:rmove}
-\includegraphics[]{pic-rmove.pdf}
-\end{align}
-%where $a$, $b$, and $c$ represent particle types, and $F$-moves,
-%representing the associativity rule for fusion processes, 
-This is meant to show a \emph{half-twist} of the space
-inside the observable with value $c$
-holding two anyons (punctures) with charges $a$ and $b$.
-We are free to draw loops around charges,
-and in general braiding will twist these loops in different
-ways:
-\begin{align*}
-\includegraphics[]{pic-braid-loop.pdf}
-\end{align*}
-%
-%
-These diagrams can be composed, and the fusion operation replaces the 
-interior of a disc by a single charge.
-These pictures, abstracted from the quantum context,
-are called \emph{curve diagrams} and are used in
-the study of braid groups \cite{Dehornoy2002}.
+These diagrams can be composed (glued)
+by regarding the outermost observable
+as a charge in another diagram.
+This operation distributes multiplicatively
+over superpositions, and it also respects the $R$ and $F$-moves.
+Conversely, \emph{fusion} of anyons corresponds to 
+replacing the interior of a loop by a single charge.
+%and conversely, the fusion operation acts by replacing the 
+%interior of a loop by a single charge.
+
+%Abstracted from the quantum context,
+%these \emph{curve diagrams} are used in
+%the study of braid groups \cite{Dehornoy2002}.
 %In general, such a curve diagram is 
@@
 %\dude{optional paragraph..}
+
+%Pair-creation events should be considered isometries 
+%that enlarge the fusion space, while fusion events correspond to projective measurements 
+%of combined charge of some number of particles.
 
@@
 where the matrix is given in a basis labelled $(\vac,\tau)$.
-%unitary actions on the fusion space. Pair-creation events should be considered isometries 
-%that enlarge the fusion space, while fusion events correspond to projective measurements 
-%of combined charge of some number of particles.
+
+Finally, there is a global degeneracy associated with the topology of the 
+manifold on which the anyons reside. We will consider systems with the topology of a torus, 
+which for the Fibonacci anyons gives rise to a 2-fold degeneracy.
+This global space is the one in which we will encode, and demonstrate protection of, quantum 
+information. 
 For detailed description of these 
@@
 a less important (and non-universal) role.
-
-%We use a phenomenological model of Fibonacci anyon dynamics which neglects any 
-%microscopic details of the system. 
-%This is consistent with the principles of topologically 
-%ordered systems and anyonic physics, where the key universal features describing the 
-%anyon model correspond to large length-scale physics, while the microscopic physics plays 
-%a less important (and non-universal) role.
-%Our simulation is in effect that of a $(2+1)$-dimensional topological 
-%quantum field theory, which allows for topological processes such as 
-%pair-creation, braiding, and fusion of anyonic charges.
+\dude{but how do we relate to discrete models: toric code, string nets, etc.
+microscopic lattice models.}
 
@@
 %a measurement region. For more details of an analogous model, see~\cite{Brell2013}.
-
-% We need to relate this to discrete models: toric code, string nets, etc.
 
@@
 There are 
-random processes that violate this reasoning, but processes such as these are suppressed 
+random processes that violate this reasoning, but these are suppressed 
 exponentially in the lattice size $L$~\cite{Grimmett1989}.
@@
 must also consider the effect of the error-correction routine itself. This acts iteratively to fuse 
-particles on increasing length scales. While this kind of fusion would typically merge components, 
+anyons on increasing length scales. While this kind of fusion would typically merge components, 
 forcing us to compute dynamics of larger and larger sets of anyons,
@@
 
-In the regime where the action of noise plus decoder does not percolate it is
-clear that the simulation is efficient.
-However at some point, with strong enough noise, the state will
+In the regime where the action of noise plus decoder does not percolate
+it is clear \dude{check this} that the simulation is efficient.
+However, with strong enough noise the state will
 no longer decompose at all and computing dynamics will
@@
 the area around decoder threshold for lattice sizes up to $L=128.$
-%However, for finite lattice size, this regime is somewhere
-%beyond the decoder threshold, which is the 
-%point at which the decoder creates nontrivial (extensive) loops.
-%\stf{CGB and I are still not confident in the previous sentence or the next one}
-%We can view the system state as a tensor network, on which
-%the decoder is performing an (efficiently simulable) contraction.
-%This enables simulation of error correction in
-%the area around decoder threshold for lattice sizes up to $L=128.$
-%\dude{more polish needed...}
 
@@
 direct insight into practical error rates needed for topological quantum memories in non-Abelian systems. 
-It would be extremely interesting to find \emph{classical} spin models 
+It would also be interesting to find \emph{classical} spin models 
 whose phase diagram encodes the threshold for error correction in these systems~\cite{Dennis2002}.
@@
 %simulating anyons~\cite{Pfeifer2012, Singh2014} to improve the speed and scale of the simulations. 
-Finally, perhaps the most important open question is whether 
+%Finally, perhaps the most important open question is whether 
+Finally, we could ask whether 
 \emph{fault-tolerant} decoders can be designed for nonabelian anyon codes.

### 2015-06-10 fib2.tex
quite a few miscellaneous edits. its now a few paragraphs too long again.

@@
 The topological features of such systems are insensitive to local 
-perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have quasiparticle excitations 
+perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and they have quasiparticle excitations 
 exhibiting anyonic statistics~\cite{Wilczek1990}. These systems can in general be used as 
@@
 Quantum error correction is vital to harnessing the computational power of topologically 
-ordered systems. When coupled to a heat bath at any finite temperature, thermal fluctuations 
+ordered systems. When coupled to a heat bath at any non-zero temperature, thermal fluctuations 
 will create spurious anyons that diffuse and quickly corrupt the stored quantum 
@@
 anyons~\cite{Brell2013} and the so-called $\Phi$-$\Lambda$ 
-model~\cite{Wootton2013, Hutter2014} that, while nonabelian, are not universal. The general dynamics of these particular anyon models is known to be efficiently classically simulable, a fact
+model~\cite{Wootton2013, Hutter2014} that, while nonabelian, are not universal for quantum computation.
+The general dynamics of these particular anyon models is known to be efficiently classically simulable, a fact
 that was exploited to enable efficient simulation of error correction 
@@
 2-dimensional system with
-point-like excitations or quasiparticles known as anyons.
-These anyons show exotic statistics under exchange.
+point-like anyonic quasiparticle excitations, which exhibit exotic statistics under exchange.
 The worldlines of these exchanges form \emph{braids}
@@
 are total charge measurements within regions bounded by \dude{directed} closed loops (Wilson loops).
+The possible results of such a charge measurement correspond to different anyon particle types in the model.
 %The algebraic properties of these processes
@@
 %The perspective of TQFT.
-Here we show the world lines of a braid.
+The deformation of observables corresponding to the implementation of a braid process on three anyons is shown.
+The configurations before and after are connected by world lines shown in red, while the observable Wilson loops are shown in black.
+%Here we show the world lines of a braid.
 %This braid relates two different ways of observing the same charges.
-In this case, we see how it relates two different ways of observing (or fusing) the top two charges.
+%In this case, we see how it relates two different ways of observing (or fusing) the top two charges.
+This process relates two different ways of observing (or fusing) the top two charges.
 %This braid relates two different ways of observing the same charges.
 %We are free to draw these loops around charges,
-In general braiding will twist these loops in different ways
-according to how the manifold itself is being deformed.
+In general, braiding will wind or unwind the Wilson loops, following
+the deformation of the manifold itself.
 \label{f:braidloop}
@@
 %can be described by the observables of the system.
-The \dude{key?} difference between abelian and non-abelian
-anyon theories is that the outcomes of measurements in an abelian theory
-are determined uniquely particle content only.
-%The defining characteristic of a \emph{non-abelian}
+The \dude{key?} difference between abelian and nonabelian
+anyon theories is that outcomes of total charge measurements in an abelian theory
+are determined uniquely by particle content only.
+In contrast, outcomes for nonabelian charge measurements depend on the history of the particles as well as their type.
+%The defining characteristic of a \emph{nonabelian}
 %anyon theory is that ...
-That is, the fusion space is one-dimensional for abelian anyons, and generally larger for non-abelian anyons.
-In particular, we consider a system supporting (non-abelian) Fibonacci
-anyon excitations, denoted by $\tau.$
+That is, the fusion space is one-dimensional for abelian anyons, and generally larger for nonabelian anyons.
+In particular, we consider a system supporting (nonabelian) Fibonacci
+anyon excitations, denoted by $\tau$.
 Two such anyons can have total charge
-that is a superposition of $\tau$ and $\vac$ (vacuum),
+that is either $\tau$ or $\vac$ (vacuum), or any superposition of these, and
 so the fusion space in this case is 2-dimensional.
@@
 
+The green line serves to linearly
+order the anyons, and track
+deformations in the underlying space 
+(the history of braiding processes).
+It also denotes the direction along
+which $F$-moves occur.
+
 A clockwise braiding process is represented by an $R$-move:
@@
 inside the observable with value $c$
-holding two anyons (punctures) with charges $a$ and $b$.
-
-The green line serves to linearly
-order the anyons, and track
-deformations in the underlying space 
-(the history of braiding processes).
-It also denotes the direction along
-which $F$-moves occur.
+holding two anyons (punctures) with charges $a$ and $b$. \cggb{This statement isn't quite true. I suggest just deleting.}
 
@@
 \end{equation*}
-where the matrix is given in a basis labelled $(\vac,\tau)$.
+where the matrix is given in a basis labelled $(\vac,\tau)$. For more details of the Fibonacci anyon theory, see e.g.~Ref.~\cite{Nayak2008} and references therein. 
+Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be 
+sufficient to implement universal quantum computation~\cite{Freedman2002, Nayak2008}.
 
-Finally, there is a global degeneracy associated with the topology of the 
+Finally, in addition to the fusion space of any anyons present, there is also a global degeneracy associated with the topology of the 
 manifold on which the anyons reside. We will consider systems with the topology of a torus, 
@@
 information.
-For detailed description of these 
-processes in Fibonacci anyons, see e.g.~Ref.~\cite{Nayak2008} and references therein. 
-Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be 
-sufficient to implement universal quantum computation~\cite{Freedman2002, Nayak2008}.
 
-This treatment of anyon dynamics we consider to be a phenomenological model;
+We consider this treatment of anyon dynamics to be a phenomenological model in that
 it neglects any microscopic details of the system.
@@
 a less important (and non-universal) role.
-\dude{but how do we relate to discrete models: toric code, string nets, etc.
-microscopic lattice models.}
+Additionally, while we model a continuum anyon theory, our analysis can be trivially reinterpreted to apply directly to lattice spin models or other systems where space is fundamentally discrete.
+%\dude{but how do we relate to discrete models: toric code, string nets, etc.
+%microscopic lattice models.}
 
@@
 \begin{align}
-	H=-\sum_{T\in \Lambda}\proj{\vac}_T\;,\label{e:hamiltonian}
+	H=-\sum_{t\in \Lambda}\proj{\vac}_t\;,\label{e:hamiltonian}
 \end{align}
-with $\proj{\vac}_T$ the projector to charge $\vac$ at tile $T$, i.e.~the ground 
+with $\proj{\vac}_t$ the projector to charge $\vac$ at tile $t$, i.e.~the ground 
 space of the model has vacuum total charge in each tile.
 Given the toroidal boundary 
-conditions, this space contains the two-fold degenerate codespace.
+conditions, this space \cggb{is} the two-fold degenerate codespace. \cggb{Subtlety in that there could be anyons around in the ground space.}
 %We identify this ground space as the codespace of our model.
 
-Typical realistic noise processes in this kind of system are 
-pair-creation, hopping, exchange etc.~of anyons on neighboring sites of $\Lambda$.
+Typical noise processes in this kind of system are 
+pair-creation, hopping, exchange etc.~of anyons.
 It was seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only 
@@
 will restrict to pair-creation noise processes in the numerical results presented in this study.
-Such pair-creation events act on neighboring pairs of sites,
-and so may be associated with an edge of the lattice, chosen 
-uniformly at random at each time step of the simulation. The simulation time, and thus the 
+
+Pair-creation events acting within a single tile do not affect the corresponding observable, and so the only pair-creation events we need explicitly consider act between neighboring pairs of tiles.
+These are then each associated with an edge of the lattice $\Lambda$, chosen
+uniformly at random. The simulation time, and thus the 
 error-correction threshold, will be measured in terms of average number of noise processes 
@@
 and follows a similar strategy to the hard-decision renormalization group decoder~\cite{Bravyi2011}. 
-The decoder proceeds by measuring the occupations of 
-anyons at each site of the lattice, producing a \emph{syndrome} 
-of occupied sites. Following this, it forms clusters of nearby anyons and 
+The decoder proceeds by measuring the charge on 
+each tile of the lattice, producing a \emph{syndrome} 
+of occupied sites. Following this, it forms clusters of nearby occupied tiles and 
 measures the total charge within each cluster.
@@
 there is at most a single cluster remaining (see \Fref{f:decode}).
+
 Note that unlike the case of abelian anyons, the decoder
 cannot determine the charge of each cluster given only the syndrome information (as in \cite{Bravyi2011}),
-and so will query (measure) the system to find this.
+and so will query the system by measuring these charges.
 Our simulation proceeds in this way as a dialogue between decoder
@@
 our qualitative results may be reproduced by most alternative families 
-of decoders, although it may not be clear in all cases how to extend these decoders to the non-abelian setting.
+of decoders, although it may not be clear in all cases how to extend these decoders to the nonabelian setting.
 The advantage of using a clustering decoder is 
@@
 
-Although simulating pair creation, braiding, and fusion of $n$ Fibonacci anyons is equivalent 
+Although simulating pair creation, braiding, and fusion of Fibonacci anyons is equivalent 
 in computational power to universal quantum computing (and thus unlikely to be classically 
@@
 anyons present is dramatically reduced by fusion, leading to a smaller number of anyons that 
-must be simulated.
+must be simulated. \cggb{is this really helping the simulation so much as it seems? is it clear that we don't still need to simulate the entire set of anyons even though they arent there anymore?}
 
-In the regime where the action of noise plus decoder does not percolate
+In the regime where the combined action of noise and error-correction does not percolate
 it is clear \dude{check this} that the simulation is efficient.
-However, with strong enough noise the state will
+However, with strong enough noise the state in the fusion space will
 no longer decompose at all and computing dynamics will
@@
 Despite this, we use heuristics %for finite lattice size, we use heuristics
-that minimize non-local braid moves, which helps to
+that minimize non-local braid moves \cggb{what does minimize mean here?}, which helps to
 maintain the state as a separable product beyond the
@@
 This enables simulation of error correction in
-the area around decoder threshold for lattice sizes up to $L=128.$
+the regime around the error-correction threshold for linear lattice sizes up to $L=128$.
 
@@
 
-In order to keep track of the state of the system we maintain 
+In order to track the state of the system we maintain 
 a set of disjoint directed curves, 
@@
 The application of a pair-creation noise process corresponds to the 
-addition of an extra piece of curve to the lattice supporting
+addition of an extra curve to the lattice, supporting
 two new anyons.
@@
 This requires joining (arbitrarily) any curves that intersect that tile, 
-and then performing $R$ and $F$-moves on the resulting
+and then performing $R$- and $F$-moves on the resulting
 curve so that 
@@
 %treated in an analogous way, following e.g.~\cite{Pfeifer2012}.
+\cggb{what does the combinatorial comment mean?}
+\cggb{why did the Pfeifer ref get commented? it should certainly go somewhere.}
 %\cggb{This paragraph and the next still needs another look.}
@@
 a tile are neighbors on the curve, as in (d).  
-The red lines correspond to the worldline braids that perform this step.
+The red lines correspond to the worldlines for these braids.
 }
@@
 
-Following the result of these charge measurements, the decoder determines 
+Following the results of the charge measurements, the decoder determines 
 a recovery operation that involves fusion of subsets of anyons. 
-These fusion results can be calculated in the same way, 
+These fusions can be simulated and their results calculated in the same way, 
 and the output charge placed at an appropriate point in the lattice. 
@@
 
-We plot the performance of the decoder as a function of error rate for varying lattice sizes in 
+We plot the performance of the decoder as a function of noise strength for varying lattice sizes in 
 \Fref{f:threshold}. 
-The error rate is parameterized by the Poisson process duration $t_{\mathrm{sim}}$, representing the expected number of errors per edge during the simulation. 
+The noise strength is parameterized by the Poisson process duration $t_{\mathrm{sim}}$, representing the expected number of errors per edge during the simulation. 
 We find evidence of a decoding threshold below which decoding succeeds with asymptotic 
@@
 the action of noise plus decoder 
-does not percolate the anyons accross the lattice,
+does not percolate the anyons over the lattice,
 but it is possible that percolated events may still result in no error. 
@@
 (including those that have percolated) were simulated by an optimal decoder. 
-However, calculations of such nontrivial operations suggest that all such 
+However, calculations of such nontrivial operations for small lattice sizes suggest that almost all such 
 processes will indeed result in a logical or leakage error.
-As such it is likely that neglecting full simulation for 
+As such it is likely that neglecting the full simulation of 
 such events does not significantly affect our observed threshold value.
@@
 Ref.~\cite{Brell2013} presents good evidence that it is
-unlikely that these choices will affect our results qualitatively.
+unlikely these choices will affect our results qualitatively.
 %it seems highly
@@
 As such, our methods could be used to demonstrate successful 
-error-correction in an arbitrary anyonic topological quantum computation.
+error-correction for an arbitrary anyonic topological quantum computer.
 
@@
 Although it is not completely obvious how to do so, 
-applying these methods to more realistic models such as concrete 
+applying similar methods to more realistic models such as concrete 
 microscopic spin models or models with non-topological features would give 
-direct insight into practical error rates needed for topological quantum memories in non-Abelian systems. 
+direct insight into practical error rates needed for topological quantum memories in nonabelian systems. 
 It would also be interesting to find \emph{classical} spin models 
@@
 %Finally, perhaps the most important open question is whether 
-Finally, we could ask whether 
-\emph{fault-tolerant} decoders can be designed for nonabelian anyon codes.
+Finally, an important extension of this work would be to the simulation of \emph{fault-tolerant} error-correction protocols for nonabelian anyon codes.
 

### 2015-06-10 fib2.tex
a couple more comments
minor

--- 2015-06-10 fib2.tex
@@
 This is the perspective we adopt (see \Fref{f:braidloop}).
-\dude{Fig or FIG ?}
+%\dude{Fig or FIG ?} -- it's Fig.
 %In particular, this shows the action of braiding
@@
 anyon theories is that the outcomes of measurements in an abelian theory
-are determined uniquely particle content only.
+are determined uniquely by particle content only.
 %The defining characteristic of a \emph{non-abelian}

### 2015-06-11 fib2.tex
some more minor rewording

--- 2015-06-10 fib2.tex
@@
 in (2+1)-dimensions
-which act unitarily on (the Hilbert space of) degrees of freedom known as the \emph{fusion space.}
+which act unitarily on the Hilbert space of degrees of freedom known as the \emph{fusion space}.
 To access this space we define
 the topological observables of the system: these
-are total charge measurements within regions bounded by \dude{directed} closed loops (Wilson loops).
+are total charge measurements within regions bounded by %\dude{directed} 
+closed loops (Wilson loops).
 The possible results of such a charge measurement correspond to different anyon particle types in the model.
@@
 \emph{topological quantum field theory}
-anyons are modelled
+anyons are modeled
 as punctures in a surface~\cite{Pfeifer2014}, and it is not
@@
 This is the perspective we adopt (see \Fref{f:braidloop}).
-\dude{Fig or FIG ?}
+%\dude{Fig or FIG ?}
 %In particular, this shows the action of braiding
@@
 %can be described by the observables of the system.
-The \dude{key?} difference between abelian and nonabelian
-anyon theories is that outcomes of total charge measurements in an abelian theory
-are determined uniquely by particle content only.
+The defining %\dude{key?} 
+difference between abelian and nonabelian
+anyon theories is that in an abelian theory particle content alone uniquely determines the outcome of total charge measurements.
 In contrast, outcomes for nonabelian charge measurements depend on the history of the particles as well as their type.
@@
 For $n$ anyons of type $\tau$, the 
-dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ 
-the golden ratio.
+dimension of this space grows asymptotically as $\varphi^n$, where $\varphi=\frac{1+\sqrt{5}}{2}$ 
+is the golden ratio.
 
@@
 over total charge $j$ of the anyons with charge $b$ and $c$. 
-
 The green line serves to linearly
 order the anyons, and track
-deformations in the underlying space 
-(the history of braiding processes).
+deformations in the underlying space, 
+i.e.\ the history of braiding processes.
 It also denotes the direction along
-which $F$-moves occur.
-
-A clockwise braiding process is represented by an $R$-move:
+which $F$-moves occur. A clockwise braiding process is represented by an $R$-move:
 \begin{align}
@@
 \end{align}
-This is meant to show a \emph{half-twist} of the space
-inside the observable with value $c$
-holding two anyons (punctures) with charges $a$ and $b$. \cggb{This statement isn't quite true. I suggest just deleting.}
+%This is meant to show a \emph{half-twist} of the space
+%inside the observable with value $c$
+%holding two anyons (punctures) with charges $a$ and $b$. \cggb{This statement isn't quite true. I suggest just deleting.}
 
@@
 
-For the Fibonacci anyons, the non-trivial $R$ and $F$ moves are 
+For Fibonacci anyons, the non-trivial $R$ and $F$ moves are 
 \begin{equation*}
@@
 \end{equation*}
-where the matrix is given in a basis labelled $(\vac,\tau)$. For more details of the Fibonacci anyon theory, see e.g.~Ref.~\cite{Nayak2008} and references therein. 
-Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be 
-sufficient to implement universal quantum computation~\cite{Freedman2002, Nayak2008}.
+where the matrix is given in a basis labelled $(\vac,\tau)$. For more details of the Fibonacci anyon theory, see e.g.\ Ref.~\cite{Nayak2008} and references therein. 
+%Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be 
+%sufficient to implement universal quantum computation~\cite{Freedman2002, Nayak2008}.
+% -- we already said this in the intro and we're pressed for space, so I cut this sentence
 
-Finally, in addition to the fusion space of any anyons present, there is also a global degeneracy associated with the topology of the 
-manifold on which the anyons reside. We will consider systems with the topology of a torus, 
+In addition to the fusion space there is also a global degeneracy associated with the topology of the 
+manifold on which the anyons reside. We consider systems with the topology of a torus, 
 which for the Fibonacci anyons gives rise to a 2-fold degeneracy.
-This global space is the one in which we will encode, and demonstrate protection of, quantum 
-information.
+%This global space is the one in which we will encode, and demonstrate protection of, quantum information. 
+% -- we say this again in the paragraph after next.
 
@@
 %lattice site, while in the latter case each tile represents 
-%a measurement region. For more details of an analogous model, see~\cite{Brell2013}.
+%a measurement region. 
+%For more details of an analogous model, see~\cite{Brell2013}.
+\cggb{I would consider restoring the sentence that refers the reader to our previous paper for details of the phenomenological model.}
 
@@
 a square lattice tiling $\Lambda$.
-%We tile the manifols with  a finite set of $L\times L$ Wilson loops arranged in
+%We tile the manifold with a finite set of $L\times L$ Wilson loops arranged in
 These \emph{tiles} will be the observables accesible to the error-correction procedure (\emph{decoder}).
@@
 Given the toroidal boundary 
-conditions, this space \cggb{is} the two-fold degenerate codespace. \cggb{Subtlety in that there could be anyons around in the ground space.}
+conditions, this space is the two-fold degenerate codespace. \cggb{Subtlety in that there could be anyons around in the ground space.}
 %We identify this ground space as the codespace of our model.
@@
 %the fusion space determined by row-major ordering of sites~\cite{Brell2013}.
+\cggb{I would be an advocate for restoring the sentences that compare the dynamically generated basis here to our previous work's fixed fusion basis.}
 

### 2015-06-11 fib2.tex
more things

@@
 
-We consider this treatment of anyon dynamics to be a phenomenological model in that
-it neglects any microscopic details of the system.
-This is consistent with the principles of topologically 
-ordered systems and anyonic physics, where the key universal features describing the 
-anyon model correspond to large length-scale physics, while the microscopic physics plays 
-a less important (and non-universal) role.
-Additionally, while we model a continuum anyon theory, our analysis can be trivially reinterpreted to apply directly to lattice spin models or other systems where space is fundamentally discrete.
 %\dude{but how do we relate to discrete models: toric code, string nets, etc.
@@
 %For more details of an analogous model, see~\cite{Brell2013}.
-\cggb{I would consider restoring the sentence that refers the reader to our previous paper for details of the phenomenological model.}
+%\cggb{I would consider restoring the sentence that refers the reader to our previous paper for details of the phenomenological model.}
 
@@
 %We tile the manifold with a finite set of $L\times L$ Wilson loops arranged in
-These \emph{tiles} will be the observables accesible to the error-correction procedure (\emph{decoder}).
+These \emph{tiles} will be the observables accessible to the error-correction procedure (\emph{decoder}).
 We can use these observables to construct an idealized Hamiltonian for this system of the form
-\begin{align}
-	H=-\sum_{t\in \Lambda}\proj{\vac}_t\;,\label{e:hamiltonian}
-\end{align}
+%\begin{align}
+	$H=-\sum_{t\in \Lambda}\proj{\vac}_t\;,$
+%\end{align}
 with $\proj{\vac}_t$ the projector to charge $\vac$ at tile $t$, i.e.~the ground 
@@
 Given the toroidal boundary 
-conditions, this space is the two-fold degenerate codespace. \cggb{Subtlety in that there could be anyons around in the ground space.}
+conditions, this space contains the two-fold degenerate codespace.
+%\cggb{Subtlety in that there could be anyons around in the ground space.}
 %We identify this ground space as the codespace of our model.
@@
 Typical noise processes in this kind of system are 
-pair-creation, hopping, exchange etc.~of anyons.
-It was seen in~\cite{Brell2013} that a simplified noise model consisting of pair-creation events only 
+pair-creation, hopping, exchange etc.~of anyons. Such a model was analyzed in detail for Ising anyons in Ref.~\cite{Brell2013}.
+It was seen that a simplified noise model consisting of pair-creation events only 
 is sufficient to capture the qualitative features of an error-correction simulation, and so for convenience we 
@@
 of low error rates in those cases where they are comparable (see Ref.~\cite{Brell2013}).
+
+We consider this treatment of anyon dynamics to be a phenomenological model in that
+it neglects any microscopic details of the system.
+This is consistent with the principles of topologically 
+ordered systems and anyonic physics, where the key universal features describing the 
+anyon model correspond to large length-scale physics, while the microscopic physics plays 
+a less important (and non-universal) role.
+Additionally, while we model a continuum anyon theory, our analysis can be trivially reinterpreted to apply directly to lattice spin models or other systems where space is fundamentally discrete.
 
@@
 anyons present is dramatically reduced by fusion, leading to a smaller number of anyons that 
-must be simulated. \cggb{is this really helping the simulation so much as it seems? is it clear that we don't still need to simulate the entire set of anyons even though they arent there anymore?}
+must be simulated.
 
 In the regime where the combined action of noise and error-correction does not percolate
-it is clear \dude{check this} that the simulation is efficient.
+it is reasonable to expect that the simulation is efficient.
 However, with strong enough noise the state in the fusion space will
@@
 Despite this, we use heuristics %for finite lattice size, we use heuristics
-that minimize non-local braid moves \cggb{what does minimize mean here?}, which helps to
-maintain the state as a separable product beyond the
+that minimize braid moves, which helps to
+track the state beyond the
 sub-percolated regime.
@@
 %the fusion space determined by row-major ordering of sites~\cite{Brell2013}.
-\cggb{I would be an advocate for restoring the sentences that compare the dynamically generated basis here to our previous work's fixed fusion basis.}
+%\cggb{I would be an advocate for restoring the sentences that compare the dynamically generated basis here to our previous work's fixed fusion basis.}
 
@@
 one for each connected component with trivial total charge.
+Unlike previous work~\cite{Brell2013}, this creates a dynamically generated basis for the fusion space 
+that easily allows for tensor factorization of disjoint components.
 The application of a pair-creation noise process corresponds to the 
@@
 this procedure will be discussed elsewhere.
-%Braiding processes that encircle 
-%a non-trivial loop of our (toric) manifold can also be 
-%treated in an analogous way, following e.g.~\cite{Pfeifer2012}.
+Braiding processes that encircle 
+a non-trivial loop of our (toric) manifold can also be 
+treated in an analogous way, following e.g.~\cite{Pfeifer2012}.
 \cggb{what does the combinatorial comment mean?}

### 2015-06-11 fib2.tex
near-final draft?
Version 1.0!  Woohoo!

@@
 %We are free to draw these loops around charges,
-In general, braiding will wind or unwind the Wilson loops, following
+In general, braiding will twist these loops in different ways following
 the deformation of the manifold itself.
@@
 It also denotes the direction along
-which $F$-moves occur. A clockwise braiding process is represented by an $R$-move:
+which $F$-moves occur. A clockwise braiding process, or \emph{half-twist}, is effected by an $R$-move:
 \begin{align}
@@
 Unlike previous work~\cite{Brell2013}, this creates a dynamically generated basis for the fusion space 
-that easily allows for tensor factorization of disjoint components.
+that allows for tensor factorization of disjoint components.
 The application of a pair-creation noise process corresponds to the 
@@
 %and the corresponding braid moves are shown in \Fref{f:syndrome}(e).
-The combinatorial derivation of the algorithm and data structures used for 
+The details of the algorithm and data structures used for 
 this procedure will be discussed elsewhere.
@@
 treated in an analogous way, following e.g.~\cite{Pfeifer2012}.
-\cggb{what does the combinatorial comment mean?}
-\cggb{why did the Pfeifer ref get commented? it should certainly go somewhere.}
+%\cggb{what does the combinatorial comment mean?}
+%\cggb{why did the Pfeifer ref get commented? it should certainly go somewhere.}
 %\cggb{This paragraph and the next still needs another look.}
@@
 This situation would be appropriate to model error-correction routines for topological quantum computation. 
-Additionally, we expect our results to be stable to changes in details of the noise model and decoding algorithm.
+Additionally, we expect our results to be stable to changes in details of the noise model and decoding algorithm, again following Ref.~\cite{Brell2013}.
 

### 2015-06-11 fib2.tex
Same as v1.0, but with all of the commented text removed. It's arXiv ready!

@@
 
-%\usepackage{tikz}
-%\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit}
-
-\usepackage{epstopdf} % to include .eps graphics files with pdfLaTeX
-%\usepackage{bm}  % Define \bm{} to use bold math fonts
+%\usepackage{epstopdf} % to include .eps graphics files with pdfLaTeX
 
@@
 
-%The topological features of a physical anyon model are abstractly described by a unitary 
-%modular tensor category~\cite{Wang2010b}. This object contains the data describing the 
-%types of anyonic particles, as well as the results of topological operations such as braiding and 
-%fusion of these anyons. The Fibonacci anyon model consists of only one non-trivial particle 
-%type, conventionally labelled $\tau$. Denoting the vacuum by $\vac$, we can describe 
-%the possible fusion outcomes of Fibonacci anyons as $\tau\times\tau=\vac+\tau$, 
-%i.e.~two $\tau$ particles can either fuse to vacuum or to a $\tau$ particle.
-%
-%Associated with each set of fusion outcomes for a fixed number of $\tau$ particles is a basis 
-%vector for a Hilbert space, the \emph{fusion} space. For $n$ particles of type $\tau$, the 
-%dimension of this space grows asymptotically as $\varphi^n$ for $\varphi=\frac{1+\sqrt{5}}{2}$ 
-%the golden ratio. Additionally, there is a global degeneracy associated with the topology of the 
-%manifold on which the anyons reside. We will consider systems with the topology of a torus, 
-%which for the Fibonacci anyons gives rise to a 2-fold degeneracy. For convenience 
-%(in particular to minimize finite-size effects in our numerical computations~\cite{Brell2013}), 
-%this global space is the one in which we will encode, and demonstrate protection of, quantum 
-%information.
-%
-%The fusion outcome of any particular experiment depends on the history of the particles, in 
-%particular how they have braided around one another. Braiding operations are treated as 
-%unitary actions on the fusion space. Pair-creation events should be considered isometries 
-%that enlarge the fusion space, while fusion events correspond to projective measurements 
-%of combined charge of some number of particles. For detailed description of these 
-%processes in Fibonacci anyons, see e.g.~Ref.~\cite{Nayak2008} and references therein. 
-%Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be 
-%sufficient to implement universal quantum computation~\cite{Freedman2002, Nayak2008}.
-
-% From Picture TQFTs paper:
-%Within physics, TQFTs are referred to as “anyonic systems” [Wil][DFNSS]. These are
-%2-dimensional quantum mechanical systems with point like excitations (variously
-%called “quas-particle” or just “particle”, anyon, or perhaps “nonabelion”) which
-%under exchange exhibit exotic statistics: a nontrival representation of the braid
-%groups acting on a finite dimensional Hilbert space V consisting of “internal de-
-%grees of freedom”. Since these “internal degrees of freedom” sound mysterious,
-%we note that this information is accessed by fusion: fuse pairs of anyons along
-%a well defined trajectory and observe the outcome.
-%Statistics of anyons is described by unitary representations of the braid groups
-
 We consider a 
@@
 the topological observables of the system: these
-are total charge measurements within regions bounded by %\dude{directed} 
+are total charge measurements within regions bounded by 
 closed loops (Wilson loops).
 The possible results of such a charge measurement correspond to different anyon particle types in the model.
-%The algebraic properties of these processes
 These dynamics and observables obey algebraic rules
-given by a unitary modular tensor category~\cite{Wang2010b}. % (UMTC). 
+given by a unitary modular tensor category~\cite{Wang2010b}. 
 However, from the perspective of
@@
 This is the perspective we adopt (see \Fref{f:braidloop}).
-%\dude{Fig or FIG ?}
-%In particular, this shows the action of braiding
-%on arbitrary observables (Wilson loops) as
-%these deform with the manifold.
-
-%As was noted in~\cite{Pfeifer2014}, when dealing with two-dimensional 
-%anyon dynamics, it is not sufficient to consider only
-%the algebraic (fusion/braiding) properties of the anyons,
-%one must also account for the algebra of observables. \cggb{This sentence seems odd here. Consider moving?}
 
@@
 \caption{
-%The perspective of TQFT.
 The deformation of observables corresponding to the implementation of a braid process on three anyons is shown.
 The configurations before and after are connected by world lines shown in red, while the observable Wilson loops are shown in black.
-%Here we show the world lines of a braid.
-%This braid relates two different ways of observing the same charges.
-%In this case, we see how it relates two different ways of observing (or fusing) the top two charges.
 This process relates two different ways of observing (or fusing) the top two charges.
-%This braid relates two different ways of observing the same charges.
-%We are free to draw these loops around charges,
 In general, braiding will twist these loops in different ways following
@@
 
-%The state \dude{space?} of a collection of anyons
-%can be described by the observables of the system.
-The defining %\dude{key?} 
-difference between abelian and nonabelian
+The defining difference between abelian and nonabelian
 anyon theories is that in an abelian theory particle content alone uniquely determines the outcome of total charge measurements.
 In contrast, outcomes for nonabelian charge measurements depend on the history of the particles as well as their type.
-%The defining characteristic of a \emph{nonabelian}
-%anyon theory is that ...
 That is, the fusion space is one-dimensional for abelian anyons, and generally larger for nonabelian anyons.
@@
 \end{align}
-%This is meant to show a \emph{half-twist} of the space
-%inside the observable with value $c$
-%holding two anyons (punctures) with charges $a$ and $b$. \cggb{This statement isn't quite true. I suggest just deleting.}
 
@@
 replacing the interior of a loop by a single charge.
-%and conversely, the fusion operation acts by replacing the 
-%interior of a loop by a single charge.
-
-%Abstracted from the quantum context,
-%these \emph{curve diagrams} are used in
-%the study of braid groups \cite{Dehornoy2002}.
-%In general, such a curve diagram is 
-%a continuous embedding of a line that passes through 
-%each puncture once. 
-%Remarkably, any two such linear orderings are related by
-%braiding (half-twists).
-%\dude{optional paragraph..}
-
-%Pair-creation events should be considered isometries 
-%that enlarge the fusion space, while fusion events correspond to projective measurements 
-%of combined charge of some number of particles.
 
@@
 where the matrix is given in a basis labelled $(\vac,\tau)$. For more details of the Fibonacci anyon theory, see e.g.\ Ref.~\cite{Nayak2008} and references therein.
-%Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be 
-%sufficient to implement universal quantum computation~\cite{Freedman2002, Nayak2008}.
-% -- we already said this in the intro and we're pressed for space, so I cut this sentence
 
@@
 which for the Fibonacci anyons gives rise to a 2-fold degeneracy.
-%This global space is the one in which we will encode, and demonstrate protection of, quantum information. 
-% -- we say this again in the paragraph after next.
-
-%\dude{but how do we relate to discrete models: toric code, string nets, etc.
-%microscopic lattice models.}
 
@@
 \paragraph{Noise and error-correction.}
-
-%We model the system on a periodic $L\times L$ square lattice $\Lambda$ of \emph{tiles} on which anyons can reside. 
-%This treatment applies equally well to lattice models, where anyons 
-%can only be located at a discrete set of points, 
-%or continuum models, where a discretization of the manifold must 
-%be chosen in order to perform charge measurements. 
-%In the former case, each tile of $\Lambda$ represents a 
-%lattice site, while in the latter case each tile represents 
-%a measurement region. 
-%For more details of an analogous model, see~\cite{Brell2013}.
-%\cggb{I would consider restoring the sentence that refers the reader to our previous paper for details of the phenomenological model.}
 
@@
 a square lattice tiling $\Lambda$.
-%We tile the manifold with a finite set of $L\times L$ Wilson loops arranged in
 These \emph{tiles} will be the observables accessible to the error-correction procedure (\emph{decoder}).
 We can use these observables to construct an idealized Hamiltonian for this system of the form
-%\begin{align}
  $H=-\sum_{t\in \Lambda}\proj{\vac}_t\;,$ 
-%\end{align}
 with $\proj{\vac}_t$ the projector to charge $\vac$ at tile $t$, i.e.~the ground 
@@
 conditions, this space contains the two-fold degenerate codespace.
-%\cggb{Subtlety in that there could be anyons around in the ground space.}
-%We identify this ground space as the codespace of our model.
 
@@
 become exponentially difficult in the system size.
-Despite this, we use heuristics %for finite lattice size, we use heuristics
+Despite this, we use heuristics 
 that minimize braid moves, which helps to
@@
 
-%However, recall that logical errors in our system correspond to 
-%processes that act over a non-trivial loop of the torus. 
-%Below the point at which the decoder begins to create 
-%such nontrivial loops, our simulation remains efficient
-%while it begins to declare failure whenever non-trivial logical 
-%operations occur. This allows us to simulate large lattice sizes 
-%in the successful error-correction (sub-percolated) regime, including up to $L=128$.
-
 %------------------------------------------------------------------------------------------------------------%	
 \paragraph{Simulation algorithm.}
-
-%Our concrete simulation proceeds by associating a tile with each site of the 
-%$L\times L$ periodic square lattice $\Lambda$.
-
-%In order to keep track of the state of the system we maintain a set of disjoint curves, 
-%\cggb{do they need to be directed, or is that just for the figure?} 
-%representing the history of anyons on the lattice.
-%These curves can also be thought of as a top-down view of the fusion tree:
-%the anyons comprising the fusion tree are here displayed as points along each curve. 
-%In general, the curves wind around our two 
-%dimensional manifold in a haphazard way determined by the progress of the simulation.
-%This creates a dynamically generated basis for the fusion space 
-%that easily allows for tensor factorization of disjoint components. 
-%For comparison, previous work used a single fixed basis for 
-%the fusion space determined by row-major ordering of sites~\cite{Brell2013}.
-%\cggb{I would be an advocate for restoring the sentences that compare the dynamically generated basis here to our previous work's fixed fusion basis.}
 
@@
 two new anyons.
-%along with two preferred points on it denoting the anyon locations. 
-Following the noise processes, our simulation must %proceed to 
+Following the noise processes, our simulation must 
 measure the total charge within each tile; the results of 
@@
 localized within a contiguous region of the curve. 
-%\dude{Heisenberg picture?}
-%The observable corresponding to the tile is then
-%represented in the state \dude{polish}.
-%The total charge is then (probabilistically) read off the 
-%relevant section of the fusion tree. 
 An example of this 
 procedure for a simple noise process is shown in \Fref{f:syndrome}.
-%and the corresponding braid moves are shown in \Fref{f:syndrome}(e).
 The details of the algorithm and data structures used for 
@@
 treated in an analogous way, following e.g.~\cite{Pfeifer2012}.
-%\cggb{what does the combinatorial comment mean?}
-%\cggb{why did the Pfeifer ref get commented? it should certainly go somewhere.}
-%\cggb{This paragraph and the next still needs another look.}
 
@@
 unlikely these choices will affect our results qualitatively.
-%it seems highly
-%unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}. 
 In particular, although we have modeled our logical qubit as 
@@
 whose phase diagram encodes the threshold for error correction in these systems~\cite{Dennis2002}.
-%Another potential direction is to incorporate tensor network methods for 
-%simulating anyons~\cite{Pfeifer2012, Singh2014} to improve the speed and scale of the simulations. 
-%Finally, perhaps the most important open question is whether 
 Finally, an important extension of this work would be to the simulation of \emph{fault-tolerant} error-correction protocols for nonabelian anyon codes.

### 2015-06-11 arxiv_v1/fibonacci.tex
REAL arXiv v1

--- 2015-06-11 fib2.tex
@@
 \newcommand{\proj}[1]{\ketbra{#1}{#1}}
-
-%------------------------------------------------------------------------------------------------------------%
-% Comment fonts
-%------------------------------------------------------------------------------------------------------------%
-
-\newcommand{\cggb}[1]{\textcolor{blue}{#1}}
-\newcommand{\dude}[1]{\textcolor{red}{#1}}
-\newcommand{\stf}[1]{\textcolor{green}{#1}}
 
@@
 which act unitarily on the Hilbert space of degrees of freedom known as the \emph{fusion space}.
-To access this space we define
+To describe this space we define
 the topological observables of the system: these
@@
 For $n$ anyons of type $\tau$, the 
-dimension of this space grows asymptotically as $\varphi^n$, where $\varphi=\frac{1+\sqrt{5}}{2}$ 
+dimension of the fusion space grows asymptotically as $\varphi^n$, where $\varphi=\frac{1+\sqrt{5}}{2}$ 
 is the golden ratio.
@@
 
-Typical noise processes in this kind of system are 
+Typical thermal noise processes in this kind of system are 
 pair-creation, hopping, exchange etc.~of anyons. Such a model was analyzed in detail for Ising anyons in Ref.~\cite{Brell2013}.
@@
 These are then each associated with an edge of the lattice $\Lambda$, chosen
-uniformly at random. The simulation time, and thus the 
+uniformly at random to model high-temperature, short timescale thermalizing dynamics. The simulation time, and thus the 
 error-correction threshold, will be measured in terms of average number of noise processes 
@@
 In order to perform a logical error on our code, a noise process must have support on a 
-a homologically nontrivial region of the lattice.
+a homologically nontrivial region of the manifold.
 These correspond to processes in which anyonic charge is transported around a non-trivial loop before 
@@
 the true threshold that may be found if all events 
-(including those that have percolated) were simulated by an optimal decoder. 
-However, calculations of such nontrivial operations for small lattice sizes suggest that almost all such 
+(including those that have percolated) were simulated. 
+However, calculations of homologically nontrivial operations for small lattice sizes suggest that almost all such 
 processes will indeed result in a logical or leakage error.
 As such it is likely that neglecting the full simulation of 
-such events does not significantly affect our observed threshold value.
+these events does not significantly affect our observed threshold value.
 
@@
 %------------------------------------------------------------------------------------------------------------%
-\bibliography{refs2}
+\bibliography{fibonacci}
 

### 2015-09-07 fib2.tex
added placeholder for supplemental material.
first pass at addressing ref B's comments

@@
 heterostructures~\cite{Mong2014}.
+Any of these kinds of physical systems could be used to perform universal topological quantum computation \cggb{citations?}.
+Natural sources of noise from thermal fluctuations or external perturbations will be suppressed by the energy gap but must still be corrected to allow for scalable computation.
 
@@
 be successful when applied to a universal topological quantum computer.
+Although it is not surprising that the standard topological error-correction techniques we use successfully correct errors in universal nonabelian anyon systems, the ability to simulate the precise details of how and when these techniques succeed on finite system sizes has not previously been available.
+\cggb{Would a comment about the importance of locality in topological codes (compared to abstract QEC) maybe help Ref.~B's confusion about why we don't use ``conventional'' QEC?
+I'm not totally sure what he wants.}
 
@@
 
+\cggb{I don't know how to address Ref.~B's comment here.}
+
 These diagrams can be composed (glued)
@@
 which for the Fibonacci anyons gives rise to a 2-fold degeneracy.
+This extra degree of freedom can be thought of being associated with the total anyonic charge (or flux) running through the torus itself.
+Since there are two different possible charges in the Fibonacci anyon model, the global degeneracy is 2.
 
@@
 These are then each associated with an edge of the lattice $\Lambda$, chosen
-uniformly at random to model high-temperature, short timescale thermalizing dynamics. The simulation time, and thus the 
-error-correction threshold, will be measured in terms of average number of noise processes 
-per edge, as opposed to an iid noise probability per edge. The latter measure is not 
-appropriate for error processes in nonabelian anyon models, but the two coincide in the limit 
-of low error rates in those cases where they are comparable (see Ref.~\cite{Brell2013}).
+uniformly at random to model high-temperature, short timescale thermalizing dynamics.
+In studies of codes based on abelian anyon models, the error correction threshold or memory lifetime is typically quoted in terms of an iid noise strength per edge.
+This measure is not appropriate in a nonabelian anyon setting, where noise processes on neighbouring edges do not commute.
+We thus measure the error correction threshold and memory lifetime in terms of the average number of noise processes per edge.
+It is easy to see that, in those cases where they are both appropriate, these two methods coincide in the limit of low error rates (see Ref.~\cite{Brell2013} for more details).
+The thresholds we consider in this paper are on the order of $0.1$ noise processes per edge.
+In models where both noise strength measures are appropriate, such as the toric code under bit-flip errors, the discrepancy between the two values is around $10%$ at these strengths.
 
@@
 because the resulting fusion space has dimension $O(\mathrm{poly}(n))$. 
-There are 
-random processes that violate this reasoning, but these are suppressed 
-exponentially in the lattice size $L$~\cite{Grimmett1989}.
+Of course, this is only a probabilistic statement, and so there may be cases where there exist components with size larger than $O(\log(n))$.
+However, the likelihood of this is suppressed exponentially in the lattice size $L$~\cite{Grimmett1989}.
 
@@
 However, calculations of homologically nontrivial operations for small lattice sizes suggest that almost all such 
-processes will indeed result in a logical or leakage error.
-As such it is likely that neglecting the full simulation of 
+processes will indeed either cause a logical error or a complete failure to return to the codespace.
+As such we expect that neglecting the full simulation of 
 these events does not significantly affect our observed threshold value.
@@
 
+\appendix
+
+\section*{Supplementary Material}
+
+\section{Details on the algorithm}
+
 \end{document}

### 2015-09-07 fib2.tex
first pass at addressing ref A's comments

@@
 pair-creation, hopping, exchange etc.~of anyons. Such a model was analyzed in detail for Ising anyons in Ref.~\cite{Brell2013}.
-It was seen that a simplified noise model consisting of pair-creation events only 
-is sufficient to capture the qualitative features of an error-correction simulation, and so for convenience we 
-will restrict to pair-creation noise processes in the numerical results presented in this study.
+For convenience, in the numerical results presented in this study we will restrict to a simplified noise model consisting of pair-creation events only, though all of our simulation techniques could be applied directly to the more general families of noise models considered in Ref.~\cite{Brell2013} as desired.
+It was seen in Ref.~\cite{Brell2013} that the pair-creation-only setting was sufficient to capture the qualitative features of an error-correction simulation for the Ising anyons and we have no reason to expect that this would change when considering the Fibonacci anyon model.
 
@@
 \caption{The decoder failure rate (a lower bound on the logical error probability) is shown as a function of simulation time for linear lattice sizes from $L=16$ to $128$. 
-This exhibits threshold behavior at a critical memory lifetime of $t_{\mathrm{sim}}^*\simeq 0.125$. 
-This implies the Fibonacci anyon code simulated here is able to perfectly reliably store quantum information for times less than $t_{\mathrm{sim}}^*$ in the $L\to \infty$ limit.}
+This provides strong evidence of threshold behavior at a critical memory lifetime of $t_{\mathrm{sim}}^*\simeq 0.125$. 
+The existence of such a threshold implies that the Fibonacci anyon code simulated here is able to perfectly reliably store quantum information for times less than $t_{\mathrm{sim}}^*$ in the $L\to \infty$ limit.
+\cggb{Is this hedged enough?
+Maybe replace ``implies'' with ``would imply''?}}
 \label{f:threshold}
@@
 processes will indeed either cause a logical error or a complete failure to return to the codespace.
+\cggb{Some kind of graph here to address Ref.~A's comment 3?}
 As such we expect that neglecting the full simulation of 

### 2015-09-07 fib2.tex
fixed compilation errors and added new woo-tang clan reference

@@
 \newcommand{\proj}[1]{\ketbra{#1}{#1}}
+
+\newcommand{\cggb}[1]{\textcolor{blue}{#1}}
 
@@
 Recent investigations have begun to explore quantum error correction for nonabelian anyon 
-models~\cite{Brell2013, Wootton2013, Hutter2014, Wootton2015b}. Nonabelian anyon models are especially interesting 
+models~\cite{Brell2013, Wootton2013, Hutter2014, Wootton2015b, Hutter2015continuous}. Nonabelian anyon models are especially interesting 
 because braiding and fusion of these anyons in general allows for the implementation of universal quantum 
 computation. However, the initial studies of error-correction in nonabelian anyon systems have focused on specific models, such as the Ising 
-anyons~\cite{Brell2013} and the so-called $\Phi$-$\Lambda$ 
+anyons~\cite{Brell2013, Hutter2015continuous} and the so-called $\Phi$-$\Lambda$ 
 model~\cite{Wootton2013, Hutter2014} that, while nonabelian, are not universal for quantum computation.
@@
 The thresholds we consider in this paper are on the order of $0.1$ noise processes per edge.
-In models where both noise strength measures are appropriate, such as the toric code under bit-flip errors, the discrepancy between the two values is around $10%$ at these strengths.
+In models where both noise strength measures are appropriate, such as the toric code under bit-flip errors, the discrepancy between the two values is around $10\%$ at these strengths.
 

### 2015-09-08 fib2.tex
start to explain topological ops

@@
 
+\section{Computation of logical operators}
+
+Here we show a process where a 
+tau anyon is wrapped around the torus twice.
+The vertical lines represent a periodic
+identification, and we leave anyons paths
+as undirected because Fibonacci anyons are
+self-inverse.
+The dotted lines represent vacuum charges,
+and we are free to include these lines or
+not.
+\begin{align*}
+\includegraphics[]{pic-logops.pdf}
+\end{align*}
+
+The state is not normalized.
+Also involves post-selection, as there is
+another process that involves leakage...
+The first equation is an $F$-move, 
+the second equation is a translation in the
+horizontal direction, and the last equation
+follows from the rule for collapsing bubbles.
+
+Continuing in this way, we compute the $k$-fold
+logical operator:
+\begin{align*}
+\includegraphics[]{pic-kfold.pdf}
+\end{align*}
+
+where $f_k$ is the $k$-th element of the Fibonacci
+sequence $\{1, 1, 2, 3...\}.$
+
 \section{Details on the algorithm}

### 2015-09-08 supplement.py

@@ -1,0 +1,198 @@
+#!/usr/bin/env python
+
+import sys
+from math import *
+from random import *
+import numpy
+
+from pyx import canvas, path, deco, trafo, style, text, color, deformer
+
+text.set(mode="latex") 
+text.set(docopt="12pt")
+text.preamble(r"\usepackage{amsmath,amsfonts,amssymb}")
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, rgb(0.75, 0.75, 0)) 
+
+black = rgb(0., 0., 0.) 
+blue = rgb(0., 0., 0.8)
+lred = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.) 
+
+shade = rgb(0.75, 0.55, 0)
+grey = rgb(0.75, 0.75, 0.75)
+
+light_shade = rgb(0.85, 0.65, 0.1)
+light_shade = rgb(0.9, 0.75, 0.4)
+
+
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
+
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+def arrow(x0, y0, x1, y1, extra=[]):
+    c.stroke(path.line(x0, y0, x1, y1),
+        extra+[deco.earrow(size=0.1)])
+
+
+w = 1.7
[…]

### 2015-09-08 supplement.py
bubbles look better

@@ -57,22 +57,25 @@ x, y = 0., 0.
 dx = 1.2*w
 
 
+st_tau = [style.linewidth.Thick, green, style.linecap.round]
+st_vac = [style.linewidth.thick, green]+st_dotted
+
 def frame():
     extra = [style.linewidth.thick]
     c.stroke(path.line(x, y, x, y+h), extra)
     c.stroke(path.line(x+w, y, x+w, y+h), extra)
 
+
+# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
 c = canvas.canvas()
 
 frame()
 
-st_tau = [style.linewidth.Thick, green, style.linecap.round]
-st_vac = [style.linewidth.thick, green]+st_dotted
-
 c.stroke(path.line(x, y+0.3*h, x+w, y+0.4*h), st_tau)
 c.stroke(path.line(x, y+0.7*h, x+w, y+0.8*h), st_tau)
 
-c.stroke(path.line(x+0.3*w, y+0.05*h, x+0.4*w, y+0.35*h), st_vac)
+#c.stroke(path.line(x+0.3*w, y+0.05*h, x+0.4*w, y+0.35*h), st_vac)
 c.stroke(path.line(x+0.7*w, y+0.4*h, x+0.6*w, y+0.75*h), st_vac)
 
 x += 1.1*w
@@ -80,11 +83,14 @@ c.text(x, y+0.5*h, r"$= \phi^{-1}$", west)
 
 x += 0.7*w
 frame()
-c.stroke(path.line(x,   y+0.2*h, x+0.3*w, y+0.5*h), st_tau)
-c.stroke(path.line(x,   y+0.8*h, x+0.3*w, y+0.5*h), st_tau)
-c.stroke(path.line(x+w, y+0.2*h, x+0.7*w, y+0.5*h), st_tau)
-c.stroke(path.line(x+w, y+0.8*h, x+0.7*w, y+0.5*h), st_tau)
-c.stroke(path.line(x+0.3*w, y+0.5*h, x+0.7*w, y+0.5*h), st_vac)
+#c.stroke(path.line(x,   y+0.2*h, x+0.3*w, y+0.5*h), st_tau)
[…]

### 2015-09-08 supplement.py
anyon paths are red

@@ -57,8 +57,8 @@ x, y = 0., 0.
 dx = 1.2*w
 
 
-st_tau = [style.linewidth.Thick, green, style.linecap.round]
-st_vac = [style.linewidth.thick, green]+st_dotted
+st_tau = [style.linewidth.Thick, red, style.linecap.round]
+st_vac = [style.linewidth.thick, red]+st_dotted
 
 def frame():
     extra = [style.linewidth.thick]
@@ -72,11 +72,11 @@ c = canvas.canvas()
 
 frame()
 
-c.stroke(path.line(x, y+0.3*h, x+w, y+0.4*h), st_tau)
-c.stroke(path.line(x, y+0.7*h, x+w, y+0.8*h), st_tau)
+c.stroke(path.line(x, y+0.3*h, x+w, y+0.3*h), st_tau)
+c.stroke(path.line(x, y+0.7*h, x+w, y+0.7*h), st_tau)
 
 #c.stroke(path.line(x+0.3*w, y+0.05*h, x+0.4*w, y+0.35*h), st_vac)
-c.stroke(path.line(x+0.7*w, y+0.4*h, x+0.6*w, y+0.75*h), st_vac)
+c.stroke(path.line(x+0.5*w, y+0.3*h, x+0.5*w, y+0.7*h), st_vac)
 
 x += 1.1*w
 c.text(x, y+0.5*h, r"$= \phi^{-1}$", west)
@@ -171,18 +171,18 @@ x, y = 0., 0.
 frame()
 
 for i in range(3):
-    a = 0.1*i+0.2
-    c.stroke(path.line(x, y+a*h, x+w, y+(a+0.1)*h), st_tau)
+    a = 0.1*i+0.3
+    c.stroke(path.line(x, y+a*h, x+w, y+(a+0.0)*h), st_tau)
 
 
 dx = 0.2*w
 for i in range(3, 6):
-    a = 0.1*i+0.25
-    c.stroke(path.line(x+0.18*w+dx, y+a*h, x+0.20*w+dx, y+(a+0.01)*h), st_tau)
+    a = 0.1*i+0.3
+    c.stroke(path.line(x+0.18*w+dx, y+a*h, x+0.20*w+dx, y+(a+0.00)*h), st_tau)
 
 c.fill(path.rect(x+0.2*w+dx, y, x+0.25*w+dx, y+h), [white])
 
[…]

### 2015-09-09 fib2.tex
anyon paths are red
more pictures

@@
 
-\section{Computation of logical operators}
+\section{Computation of homologically non-trivial operators}
+
+Specializing to the Fibonacci case,
+we write the non-trivial $F$-moves as the following
+skein relations:
+\begin{align*}
+\includegraphics[]{pic-skein1.pdf}
+\end{align*}
+
+The sollid lines represent Fibonacci world-lines.
+The dotted lines represent vacuum charges,
+and we are free to include these lines or not.
+The non-trivial $R$-moves are:
+\begin{align*}
+\includegraphics[]{pic-skein2.pdf}
+\end{align*}
+
+Removing bubbles:
+\begin{align*}
+\includegraphics[]{pic-bubble.pdf}
+\end{align*}
 
 Here we show a process where a 
-tau anyon is wrapped around the torus twice.
+Fibonacci anyon travels around the torus and
+anihilates itself. Twice.
 The vertical lines represent a periodic
@@
 self-inverse.
-The dotted lines represent vacuum charges,
-and we are free to include these lines or
-not.
 \begin{align*}
@@
 
-\section{Details on the algorithm}
+\section{Details on the simulation algorithm}
 

### 2015-09-09 supplement.py

@@ -194,7 +194,7 @@ frame()
 
 c.stroke(path.line(x, y+0.5*h, x+w, y+0.5*h), st_vac)
 
-x += 1.2*w
+x += 1.1*w
 c.text(x, y+0.5*h, r"$+ f_k$", west)
 
 x += 0.5*w
@@ -205,6 +205,203 @@ c.stroke(path.line(x, y+0.5*h, x+w, y+0.5*h), st_tau)
 
 c.writePDFfile("pic-kfold.pdf")
 
+
+# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+c = canvas.canvas()
+
+x, y = 0., 0.
+dx = 1.0
+dy = 1.0
+
+
+#        90
+#         ^
+#         |
+#         |
+# 180<--- . ----> 0
+#         |
+#         |
+#         v
+#       -90
+#
+# Arcs go anti-clockwise
+#
+
+d = 2.4
+
+r = 0.2*d
+r2 = 2**0.5*r
+
+c.stroke(path.path(path.arc(x+0.5*d, y+r2, r, -135, -45)), st_tau)
+c.stroke(path.path(path.arc(x+0.5*d, y-r2, r, +45, +135)), st_tau)
+c.stroke(path.line(x+0.5*d, y-r2+r, x+0.5*d, y+r2-r), st_vac)
+
+x += 1.0*d
+c.text(x, y-0.1*d, "$= \phi^{-1}$", south)
+
+x += 0.5*d
+
+c.stroke(path.path(path.arc(x-r2, y+0.0*d, r, -45, +45)), st_tau)
+c.stroke(path.path(path.arc(x+r2, y+0.0*d, r, +135, -135)), st_tau)
+c.stroke(path.line(x-r2+r, y+0.0*d, x+r2-r, y+0.0*d), st_vac)
+
+x += 0.5*d
+c.text(x, y-0.1*d, r"$+ \phi^{-\frac{1}{2}}$", south)
+
+x += 0.5*d
+
+c.stroke(path.path(path.arc(x-r2, y+0.0*d, r, -45, +45)), st_tau)
+c.stroke(path.path(path.arc(x+r2, y+0.0*d, r, +135, -135)), st_tau)
[…]

### 2015-09-10 supplement.py
outline of supp material

@@ -305,7 +305,7 @@ c.stroke(path.line(x-r12, y+1.0*d+r12, x-r12+1.5*r, y+1.0*d+r12+1.5*r), st_tau)
 c.stroke(path.line(x, y-0.0*d, x, y+1.0*d-r), st_vac)
 
 x += 1.8*d
-c.text(x, y+0.8*d, r"$= R_{\mathbb{I}^{\tau\tau}}$", south)
+c.text(x, y+0.8*d, r"$= R_{\mathbb{I}}^{\tau\tau}$", south)
 
 x += 1.6*d
 c.stroke(path.path(path.arc(x, y+1.8*d, r, -155, -25)), st_tau)

### 2015-09-15 fib2.tex
outline of supp material
more pictures. anyons are still red.

@@
 
-%------------------------------------------------------------------------------------------------------------%
-\bibliography{refs2}
-
 \appendix
@@
 \section*{Supplementary Material}
+
+We give an informal introduction to
+the easy (picture) topological quantum
+field theory in $(2+1)$-dimensions.
+Note that these theories give rise to
+\emph{doubled} anyonic charges, and so
+the example in the main text only simulates
+one half of such a system...
+
+\section{Interaction picture}
+
+In two spacial dimensions, particle exchange is
+captured by the braid group.
+World lines of such particles 
+become tangled (braided) in $(2+1)$-dimensions.
+For example, three particle statistics is captured
+by the braid group on three strands $B_3.$
+This group is generated by elements $\sigma_1$
+and $\sigma_2$ which we represent pictorially as:
+\begin{center}
+\includegraphics[]{pic-braid-group.pdf}
+\end{center}
+
+These pictures make clear how the group
+multiplication works, for example:
+\begin{center}
+\includegraphics[]{pic-braid-group-1.pdf}
+\end{center}
+\begin{center}
+\includegraphics[]{pic-braid-relation.pdf}
+\end{center}
+
+Braid group acts (naturally) on states.
+
+These diagrams are to be understood up to
+continuous deformation of the ambient space.
+That is, we allow the ambient $(2+1)$-dimensional
+space with these worldlines subtracted to be continuously
+deformed.
+At the top and bottom of this space is 
+a $2$-dimensional space (a disc) with holes in it.
+Such a closed disc with $n$ holes we denote as $D_n.$
+So this is how we arrive at modelling the system as
+a disc with holes in it.
+The observables of the system measure charge within
+a region bounded by a directed closed curve.
+\begin{center}
+\includegraphics[]{pic-observable.pdf}
+\end{center}
+
+The defining feature of an Abelian anyon theory
+is that the state is completely determined once
+we measure the charge of each hole.
+In the language of the toric code (homology),
+logical operators (1-chains)
+cancel where they overlap
+with opposite orientation:
+\begin{center}
+\includegraphics[width=0.7\columnwidth]{pic-abelian.pdf}
+
+\end{center}
+
+This is not at all the case in general;
+for non-Abelian theories there can be extra
+degrees of freedom associated with these
+observables. For example, in
+the Fibonacci anyon case
+\begin{center}
+\includegraphics[]{pic-fusion.pdf}
+\end{center}
+so the state space of two fibonacci anyons
+is $2$-dimensional.
+Such a space assocated with observing total charge
+of multiple anyons is called the \emph{fusion} space
+of those charges.
+
+These observables satisfy various relations,
+but in particular, non-overlapping observables commute.
+So if we nest a maximal set of these observables together
+we can pin-down a basis for the fusion space.
+Such a nesting is tree-like, and if we confuse the distinction
+between holes and observables, this gives rise to the
+fusion tree notation.
+\begin{center}
+\includegraphics[]{pic-tree-0.pdf}\includegraphics[]{pic-tree-1.pdf}
+\end{center}
+
+\section{Combinatorial curve diagrams}
+
+We use curve diagrams...
+Combinatorial formulation...
+
+\section{Simulation algorithm}
 
@@
 and we are free to include these lines or not.
+We leave these anyon paths
+as undirected because Fibonacci anyons are
+self-inverse.
 The non-trivial $R$-moves are:
@@
 The vertical lines represent a periodic
-identification, and we leave anyons paths
-as undirected because Fibonacci anyons are
-self-inverse.
+identification.
 \begin{align*}
@@
 
-\section{Details on the simulation algorithm}
+%------------------------------------------------------------------------------------------------------------%
+\bibliography{refs2}
 

### 2015-09-15 tqft.py

@@ -1,0 +1,1103 @@
+#!/usr/bin/env python
+
+import sys
+import os
+
+from math import *
+from random import *
+
+from pyx import canvas, path, deco, trafo, style, text, color, unit, epsfile, deformer, bitmap
+
+from PIL import Image
+
+
+text.set(mode="latex")
+text.set(docopt="12pt")
+text.preamble(r'\usepackage{amsmath,amsfonts,amssymb}')
+#text.preamble(r"\def\I{\mathbb{I}}")
+text.preamble(r"\def\ket #1{|#1\rangle}")
+
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow, orange = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, 
+    rgb(0.75, 0.75, 0),
+    rgb(0.75, 0.55, 0),
+    )
+
+blue = rgb(0., 0., 0.8)
+pale_blue = rgb(0.7, 0.7, 1.0)
+pink = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.)
+grey = rgb(0.8, 0.8, 0.8)
+
+brown = rgbfromhexstring("#AA6C39"),
+
+light_shade = rgb(0.85, 0.65, 0.1)
+
+#shade = brown
+#shade = orange
+shade = grey
+
+
+st_tau = [style.linewidth.Thick, red, style.linecap.round]
+#st_vac = [style.linewidth.thick, red]+st_dotted
+
+
+###############################################################################
+
+def ellipse(x, y, radius, sx=1., sy=1., color=None, extra=[], arrow=None):
+    p = path.circle(x, y, radius)
+    t = trafo.scale(sx=sx, sy=sy)
+    if color:
+        c.fill(p, [t, shade]+extra)
+    c.stroke(p, [t]+extra)
+    if arrow is not None:
+        c.stroke(p, [t]+extra+[deco.earrow(size=arrow)])
+
+#def clip_ellipse(x, y, radius, sx=1., sy=1., extra=[]):
+#    p = path.circle(x, y, radius)
+#    t = trafo.scale(sx=sx, sy=sy)
+#    c.clip(p, [t]+extra)
+
+
+def hole(x, y, radius, msg=None, extra=[], arrow=None):
[…]

### 2015-09-15 fib2.tex
whack whack

@@
 \includegraphics[width=0.7\columnwidth]{pic-abelian.pdf}
-
 \end{center}
@@
 
+Given a disc with $n$ holes, we define the \emph{mapping
+class group} $MCG(D_n)$ as the group of topological
+symmetries (homeomorphisms) of the space $D_n,$
+modulo continuous deformations (isotopy).
+Such symmetries we require to fix the boundary
+of the disc, but not necessarily to fix the holes.
+Elements $f\in MCG(D_n)$ will also act on anything that
+resides in $D_n.$ 
+In particular, if we draw a line
+connecting the holes:
+\begin{center}
+\includegraphics[]{pic-twist.pdf}
+\end{center}
+
+Such an embedding $c : [0, 1] \to D$ with $c(0), c(1) \in \partial D$
+and touching all holes in $D_n$ we call a \emph{curve diagram}~\cite{Dehornoy2002}.
+
+\begin{center}
+\includegraphics[]{pic-interaction.pdf}
+\end{center}
+
 \section{Combinatorial curve diagrams}
 
-We use curve diagrams...
 Combinatorial formulation...

### 2015-09-15 tqft.py

@@ -48,6 +48,146 @@ st_tau = [style.linewidth.Thick, red, style.linecap.round]
 #st_vac = [style.linewidth.thick, red]+st_dotted
 
 
+
+def anyon(x, y, r=0.07):
+    c.fill(path.circle(x, y, r), [white])
+    c.stroke(path.circle(x, y, r), [red, style.linewidth.thick])
+
+
+N = 20
+
+def dopath(ps, extra=[], fill=False, closepath=True):
+    ps = [path.moveto(*ps[0])]+[path.lineto(*p) for p in ps[1:]]
+    if closepath:
+        ps.append(path.closepath())
+    p = path.path(*ps)
+    if fill:
+        c.fill(p, [deformer.smoothed(0.3)]+extra+[color.rgb.white])
+    c.stroke(p, [deformer.smoothed(0.3)]+extra)
+
+def ellipse(x0, y0, rx, ry, extra=[], fill=False):
+    ps = []
+    for i in range(N):
+        theta = 2*pi*i / (N-1)
+        ps.append((x0+rx*sin(theta), y0+ry*cos(theta)))
+    dopath(ps, extra, fill)
+
+
+#############################################################################
+#
+#
+
+class Tracer(object):
+    def __init__(self, x0, y0, r, theta):
+        self.x0 = x0
+        self.y0 = y0
+        self.theta = theta
+        self.r = r
+        self.ps = []
+
+    def get(self):
+        theta = self.theta
+        r = self.r
+        x = self.x0 + r*sin(theta)
+        y = self.y0 + r*cos(theta)
+        return x, y
+
+    def reset(self, r):
+        # recalculate x0, y0
+        if r==self.r:
+            return
+        x1, y1 = self.get()
+        theta = self.theta
+        self.x0 = x1 - r*sin(theta)
+        self.y0 = y1 - r*cos(theta)
+        self.r = r
+
+    def trace(self, r=None, dtheta=0.05*pi):
+        theta = self.theta
+        if r is not None:
+            self.reset(r)
[…]

### 2015-09-16 fib2.tex
more pictures, more words

@@
 
+We can think of braids acting on states in a Schrodinger picture,
+or alternatively, elements of the mapping class group acting on
+observables in a Heisenberg picture:
 \begin{center}
@@
 \end{center}
+
+We would hope that the groups $B_n$ and $MCG(D_n)$ are
+isomorphic, and this is indeed the case~\cite{Kassel2010}.
+One can see this as follows. Dragging the space $D_n$ along
+a braid creates a deformation, the end point of which is a
+homeomorphism in $MCG(D_n).$ Going the other direction,
+given $f\in MCG(D_n)$ and a curve diagram $c,$ we think of
+pulling the ends of $fc$, thereby moving (braiding) the holes,
+until we are back at the original curve $c.$
 

### 2015-09-16 tqft.py

@@ -10,6 +10,21 @@ from pyx import canvas, path, deco, trafo, style, text, color, unit, epsfile, de
 
 from PIL import Image
 
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
+
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+
 
 text.set(mode="latex")
 text.set(docopt="12pt")
@@ -42,6 +57,8 @@ light_shade = rgb(0.85, 0.65, 0.1)
 #shade = brown
 #shade = orange
 shade = grey
+
+
 
 
 st_tau = [style.linewidth.Thick, red, style.linecap.round]
@@ -124,65 +141,137 @@ class Tracer(object):
     def dopath(self, *args, **kw):
         dopath(self.ps, *args, **kw)
 
-c = canvas.canvas()
+
+
+
+stack = []
+def push():
+    global c
+    stack.append(c)
+    c = canvas.canvas()
+
+def pop(*args):
+    global c
+    c1 = stack.pop()
+    c1.insert(c, *args)
+    c = c1
 
 r = 0.5
 w = 2.0
 
-ellipse(w, 0., 1.0*r, 1.8*r)
+c = canvas.canvas()
 
-tracer = Tracer(w, r, 0.4*r, -0.8*pi)
-tracer(21.5, 0.4*r)
-tracer(8, 2.2*r)
-tracer(15.5, 0.6*r)
-tracer(5, 1.7*r)
-tracer(22, 0.3*r)
-#tracer(2., 2*r)
-tracer(5.1, -1*r)
-tracer(17.5, -0.3*r)
-tracer(10.4, -1.28*r)
+push()
 
[…]

### 2015-09-17 fib2.tex
start describing the paper-clip algorithm

--- 2015-09-15 fib2.tex
@@
 
+We would hope that the groups $B_n$ and $MCG(D_n)$ are
+isomorphic, and this is indeed the case~\cite{Kassel2010}.
+One can see this as follows. Dragging the space $D_n$ along
+a braid creates a deformation, the end point of which is a
+homeomorphism in $MCG(D_n).$ Going the other direction,
+given $f\in MCG(D_n)$ and a curve diagram $c,$ we think of
+pulling the ends of $f\circ c$, thereby moving (braiding) the holes,
+until we are back at the original curve $c.$
+
 \section{Combinatorial curve diagrams}
 
-Combinatorial formulation...
+Combinatorial formulation... \cite{Abramsky2007}
+\begin{center}
+\includegraphics[]{pic-cells.pdf}
+\end{center}
+Reading from the top-left corner, the words for these
+two cells are $(())()$ and $()*(()).$
 
 \section{Simulation algorithm}
+
+Paperclip algorithm:
+\begin{center}
+\includegraphics[]{pic-paperclip.pdf}
+\end{center}
 

### 2015-09-17 tqft.py

@@ -60,6 +60,7 @@ shade = grey
 
 
 
+g_arrow = [green, style.linewidth.THick]
 
 st_tau = [style.linewidth.Thick, red, style.linecap.round]
 #st_vac = [style.linewidth.thick, red]+st_dotted
@@ -73,16 +74,16 @@ def anyon(x, y, r=0.07):
 
 N = 20
 
-def dopath(ps, extra=[], fill=False, closepath=True):
+def dopath(ps, extra=[], fill=[], closepath=True, smooth=0.3):
     ps = [path.moveto(*ps[0])]+[path.lineto(*p) for p in ps[1:]]
     if closepath:
         ps.append(path.closepath())
     p = path.path(*ps)
     if fill:
-        c.fill(p, [deformer.smoothed(0.3)]+extra+[color.rgb.white])
-    c.stroke(p, [deformer.smoothed(0.3)]+extra)
+        c.fill(p, [deformer.smoothed(smooth)]+extra+fill)
+    c.stroke(p, [deformer.smoothed(smooth)]+extra)
 
-def ellipse(x0, y0, rx, ry, extra=[], fill=False):
+def ellipse(x0, y0, rx, ry, extra=[], fill=[]):
     ps = []
     for i in range(N):
         theta = 2*pi*i / (N-1)
@@ -90,9 +91,224 @@ def ellipse(x0, y0, rx, ry, extra=[], fill=False):
     dopath(ps, extra, fill)
 
 
+
+stack = []
+def push():
+    global c
+    stack.append(c)
+    c = canvas.canvas()
+
+def pop(*args):
+    global c
+    c1 = stack.pop()
+    c1.insert(c, *args)
+    c = c1
+
+
+
 #############################################################################
 #
 #
+
+w = 1.5
+h = 1.5
+
+c = canvas.canvas()
+
+
+x = 0.
+y = 0.
+m = 0.1*w
+m0 = m/2
+r = 0.3*w
+
+c.fill(path.rect(x-m0, y-m0, 2*m0+w, 2*m0+h), [shade])
+c.stroke(path.rect(x, y, w, h))
+
+p = path.path(
+    path.moveto(x+r, y-m), 
+    path.lineto(x+r, y),
[…]

### 2015-09-17 fib2.tex
revised responses to referee comments

@@
 \newcommand{\Fref}[1]{Fig.~\ref{#1}}
+\newcommand{\Aref}[1]{Appendix~\ref{#1}}
 
@@
 heterostructures~\cite{Mong2014}.
-Any of these kinds of physical systems could be used to perform universal topological quantum computation \cggb{citations?}.
+Any of these kinds of physical systems could be used to perform universal topological quantum computation \cggb{citations?}, and can be modelled by our simulations.
 Natural sources of noise from thermal fluctuations or external perturbations will be suppressed by the energy gap but must still be corrected to allow for scalable computation.
@@
 typically implicitly assume the existence of an error-correction protocol to 
-correct for diffusion or unwanted creation of anyons. Our results 
-are the first explicit demonstration that such a scheme will 
-be successful when applied to a universal topological quantum computer.
-Although it is not surprising that the standard topological error-correction techniques we use successfully correct errors in universal nonabelian anyon systems, the ability to simulate the precise details of how and when these techniques succeed on finite system sizes has not previously been available.
-\cggb{Would a comment about the importance of locality in topological codes (compared to abstract QEC) maybe help Ref.~B's confusion about why we don't use ``conventional'' QEC?
-I'm not totally sure what he wants.}
+correct for diffusion or unwanted creation of anyons. 
+The ability to simulate the details of how and when these techniques succeed on finite system sizes has not previously been available, and so our results are the first explicit demonstration that such a scheme will be successful when applied to a universal topological quantum computer.
 
@@
 
-\cggb{I don't know how to address Ref.~B's comment here.}
-
 These diagrams can be composed (glued)
@@
 
-Our error-correction algorithm is
-based on a hierarchical clustering algorithm~\cite{Hastie2009, Wootton2015b},
+Our error-correction algorithm begins by measuring the charge on 
+each tile of the lattice, producing a \emph{syndrome} 
+of occupied sites. Following this, it joins nearby occupied tiles into clusters, and measures the total charge within each cluster.
+Clusters with trivial charge are discarded, and then nearby clusters are merged (agglomeratively~\cite{Hastie2009}).
+The merging process iterates at linearly increasing length scales, at each step measuring total charge and discarding trivial clusters, before concluding when 
+there is at most a single cluster remaining (see \Fref{f:decode}).
+This decoder is based on a hierarchical clustering algorithm~\cite{Hastie2009, Wootton2015b},
 and follows a similar strategy to the hard-decision renormalization group decoder~\cite{Bravyi2011}.
-The decoder proceeds by measuring the charge on 
-each tile of the lattice, producing a \emph{syndrome} 
-of occupied sites. Following this, it forms clusters of nearby occupied tiles and 
-measures the total charge within each cluster.
-Clusters with trivial charge are discarded, and
-the rest are joined (agglomeratively~\cite{Hastie2009})
-at linearly increasing length scales. This iterative process concludes when 
-there is at most a single cluster remaining (see \Fref{f:decode}).
 
@@
 cannot determine the charge of each cluster given only the syndrome information (as in \cite{Bravyi2011}),
-and so will query the system by measuring these charges.
+and so must repeatedly physically query the system to measure these charges.
+This is also in contrast to abstract quantum codes, where syndrome extraction can typically be performed in one step.
 Our simulation proceeds in this way as a dialogue between decoder
@@
 This provides strong evidence of threshold behavior at a critical memory lifetime of $t_{\mathrm{sim}}^*\simeq 0.125$. 
-The existence of such a threshold implies that the Fibonacci anyon code simulated here is able to perfectly reliably store quantum information for times less than $t_{\mathrm{sim}}^*$ in the $L\to \infty$ limit.
-\cggb{Is this hedged enough?
-Maybe replace ``implies'' with ``would imply''?}}
+The existence of such a threshold implies that the Fibonacci anyon code simulated here is able to perfectly reliably store quantum information for times less than $t_{\mathrm{sim}}^*$ in the $L\to \infty$ limit.}
 \label{f:threshold}
@@
 (including those that have percolated) were simulated.
-However, calculations of homologically nontrivial operations for small lattice sizes suggest that almost all such 
-processes will indeed either cause a logical error or a complete failure to return to the codespace.
-\cggb{Some kind of graph here to address Ref.~A's comment 3?}
-As such we expect that neglecting the full simulation of 
+However, naively computing the effect of the simplest possible homologically nontrivial operations consistently yields either a logical error or a complete failure to return to the codespace (see \Aref{s:homnontrivial}).
+As such it seems reasonable to suggest that neglecting the full simulation of
 these events does not significantly affect our observed threshold value.
@@
 
-\section{Computation of homologically non-trivial operators}
+\section{Computation of homologically non-trivial operators}\label{s:homnontrivial}
 

### 2015-09-18 fib2.tex
another picture

@@
 
-Paperclip algorithm:
+Transport of an anyon can be decomposed into
+moves between adjacent components of the curve
+diagram,
+\begin{center}
+\includegraphics[]{pic-move-anyon.pdf}
+\end{center}
+This move is (homotopic to) equivalent to one of the following:
 \begin{center}
@@
 \end{center}
+which can be distinguished between using the
+winding number. We count the number of right-hand
+turns made on the curve diagram (a left-hand turn counts as $-1$).
 

### 2015-09-18 tqft.py

@@ -182,6 +182,32 @@ c.stroke(p, g_arrow)
 c.writePDFfile("pic-cells.pdf")
 
 
+c = canvas.canvas()
+
+
+x = 0.
+y = 0.
+m = 0.1*w
+m0 = m/2
+r = 0.3*w
+
+
+c.fill(path.rect(x-m0, y-m0, 2*m0+w, 2*m0+h), [shade])
+c.stroke(path.rect(x, y, w, h))
+
+c.stroke(path.line(x+1.3*w, y+0.6*h, x+w+m, y+0.6*h), g_arrow+st_dotted)
+c.stroke(path.line(x+w+m, y+0.6*h, x+0.5*w, y+0.6*h), g_arrow) #+[deco.earrow(size=0.2)])
+c.stroke(path.line(x+w+m, y+0.6*h, x+0.6*w, y+0.6*h), g_arrow+[deco.earrow(size=0.2)])
+c.stroke(path.line(x+0.5*w, y+0.6*h, x+0.2*w, y+0.6*h), g_arrow+st_dotted)
+c.stroke(path.line(x+w-m, y+0.6*h, x+w-m, 0.2*h), st_tau+[deco.earrow(size=0.2)])
+anyon(x+w-m, y+0.6*h)
+
+c.stroke(path.line(x+1.3*w, y+0.2*h, x+w+m, y+0.2*h), g_arrow+st_dotted)
+c.stroke(path.line(x+w+m, y+0.2*h, x+0.5*w, y+0.2*h), g_arrow) #+[deco.earrow(size=0.2)])
+c.stroke(path.line(x+w+m, y+0.2*h, x+0.6*w, y+0.2*h), g_arrow)
+c.stroke(path.line(x+0.5*w, y+0.2*h, x+0.2*w, y+0.2*h), g_arrow+st_dotted)
+
+c.writePDFfile("pic-move-anyon.pdf")
 
 #############################################################################
 #

### 2015-09-20 fib2.tex
more wordsmithing

--- 2015-09-17 fib2.tex
@@
 Such an embedding $c : [0, 1] \to D$ with $c(0), c(1) \in \partial D$
-and touching all holes in $D_n$ we call a \emph{curve diagram}~\cite{Dehornoy2002}.
+and touching all holes in $D_n$ we call a \emph{curve diagram}~\cite{Dehornoy2002},
+(or just a \emph{curve} when the context is clear).
 
@@
 
-Combinatorial formulation... \cite{Abramsky2007}
+The basic data structure involved in the
+simulation we term a \emph{combinatorial curve
+diagram.}
+For each cell in the lattice,
+we store a combinatorial
+description of the curve intersected with that cell.
+This will be insensitive to any continuous deformation of the interior of the cell,
+but the simulation does not need to track any of these degrees of freedom.
 \begin{center}
@@
 \end{center}
-Reading from the top-left corner, the words for these
-two cells are $(())()$ and $()*(()).$
+We follow essentially the same approach as taken in \cite{Abramsky2007} 
+to describe elements of a Temperley-Leib algebra, but
+with some extra decorations.
+The key idea is to store a \emph{word} for each cell, comprised of
+the letters $<$ and $>$.
+When these brackets are balanced,
+each such word will correspond one-to-one with an intersection
+of a curve in a cell (up to any continuous deformation of the interior of the cell).
+The encoding works as follows.
+Reading in a clockwise direction around the edge of
+the cell from the top-left corner,
+we record our encouters with each piece of curve diagram,
+writing a $<$ for the first encounter, and $>$ for the
+second. We may also encounter a dangling piece of curve
+diagram (the head or the tail), so we use another symbol $*$ for this.
+The words for the above two cells will then be $<<>><>$ and $<>*<<>>.$
+Getting more elaborate, we will also need to record the direction
+of each piece of curve,
+and we allow anyons to reside on the curve
+close to the edge. (This means we cannot have more than two anyons
+per piece, but if that is needed we will have added another curve diagram.)
+We will also record,
+for each intersection with the cell edge, which side the
+intersection occurs on.
 
-\section{Simulation algorithm}
+Various other consistency relations are enforced on a combinatorial curve diagram,
+such as requiring two
+adjacent cells to agree on their boundaries, and every curve diagram
+having two ends.
+(Note that in general we will have many disjoint curve diagrams.)
+We also require every curve diagram to intersect 
+the edges of cells transversally.
+This will mean in particular that a curve will not touch a cell corner.
 
-Paperclip algorithm:
+Two disjoint curves can be joined by...
+
+Curves can be simplified along sections without any anyons, ...
+
+% Each piece will have +1, +2, 0, -1, -2 right-hand turns...
+
+% mention Jones' planar algebras ?
+
+\section{The paperclip algorithm}
+
+Anyons are transported around the lattice
+by moving them along cell edges.
+In general, such a transport will intersect with a
+curve diagram in many places.
+Each such intersection is transverse,
+and we use each intersection point to cut
+the entire transport into smaller paths each of
+which touch the curve diagram twice.
+%Each intersection with a curve diagram
+%will then be transverse, and we
+%decompose the entire path into a sequence of
+%paths each of which 
+%join consecutive intersections.
+%Transport of an anyon can be decomposed into
+%moves between adjacent components of a curve
+%diagram.
+The origin and destination of such an anyon path
+now splits the curve diagram $c:[0, 1]\to D_n$ 
+into three disjoint pieces which we term
+\emph{head}, \emph{body} and \emph{tail}, where
+the head contains the point $c(1)$, the tail
+contains $c(0)$ and the body is the third piece.
+These arise with various arrangements, but here
+we focus on one instructive case, the
+other cases are similar:
+%We look at the particular case of moving along
+%one edge of a cell,
+transporting along one edge of a cell \emph{forwards} 
+(from tail to head) along a curve diagram:
+\begin{center}
+\includegraphics[]{pic-move-anyon.pdf}
+\end{center}
+
+This arrangement is equivalent (homotopic) to one of four 
+``paperclips'', which we distinguish between by counting how
+many \emph{right-hand turns} are made along the body of the curve diagram.
+We also show an equivalent (homotopic) picture where the
+curve diagram has been straightened, and the resulting distortion
+in the anyon path:
 \begin{center}
@@
 \end{center}
+The sequence of anyons along the head, body and tail, we denote as $H, B$ and $T,$
+respectively.
+These sequences have the same order as the underlying curve diagram, and 
+we use
+$H^r, B^r$ and $T^r$ to denote the same anyons with the reversed order.
+Using the above diagram, we can now read off the $R$-moves for each
+of the four paperclips:
+\begin{align*}
+-2:&\ R[B] \\
+-4:&\ R[H^r] R[H] R[B] \\
++4:&\ R[B] R[T] R[T^r] \\
++6:&\ R[H^r] R[H] R[B] R[T] R[T^r] \\
+\end{align*}
+where notation such as $R[B]$ is understood as sequentially clockwise braiding around
+each anyon in $B$.
+
+That these four paperclips exhaust all possibilities can be seen by
+considering the winding number of the simple closed curve made
+by combining the body of the curve diagram with the path followed by
+the anyon (appropriately reversing direction as needed).
 

### 2015-09-20 tqft.py

@@ -275,8 +275,9 @@ a = st_tau+[deco.earrow(size=0.2)]
 Turtle(x, y, -pi/2).fwd(w).left(pi, r).fwd(w).stroke(g)
 Turtle(x-0.5, y, pi).fwd(2*r).stroke(a)
 anyon(x-0.5*w, y)
-c.text(x-2.2*w, y-r, r"$-2$", east)
+c.text(x-2.2*w, y-r, r"$-2:$", east)
 
+c.text(x+1.2*w, y, r"$=$", center)
 Turtle(x+5*w, y, -pi/2).fwd(3*w).stroke(g)
 Turtle(x+4.5*w, y, 7*pi/6).right(2./3*pi, 1.1*w).stroke(a)
 anyon(x+4.5*w, y)
@@ -285,8 +286,10 @@ y -= 4*r
 Turtle(x, y, -pi/2).fwd(w).left(pi, 2*r).fwd(w).left(pi, r).fwd(w).stroke(g)
 Turtle(x-0.5, y, pi).fwd(2*r).stroke(a)
 anyon(x-0.5*w, y)
-c.text(x-2.2*w, y-2*r, r"$-4$", east)
+c.text(x-2.2*w, y-2*r, r"$-4:$", east)
 
+y -= 2*r
+c.text(x+1.2*w, y, r"$=$", center)
 Turtle(x+5*w, y, -pi/2).fwd(3*w).stroke(g)
 Turtle(x+4.5*w, y, 5*pi/4)\
     .right(0.35*pi, 2.2*w)\
@@ -295,11 +298,12 @@ Turtle(x+4.5*w, y, 5*pi/4)\
     .right(pi, 0.45*w).stroke(a)
 anyon(x+4.5*w, y)
 
-y -= 8*r
+y -= 6*r
 Turtle(x, y, -pi/2).fwd(w).right(pi, r).fwd(w).right(pi, 2*r).fwd(w).stroke(g)
 Turtle(x-0.5, y, pi).fwd(2*r).stroke(a)
 anyon(x-0.5*w, y)
-c.text(x-2.2*w, y, r"$+4$", east)
+c.text(x-2.2*w, y, r"$+4:$", east)
+c.text(x+1.2*w, y, r"$=$", center)
 
 Turtle(x+5*w, y, -pi/2).fwd(3*w).stroke(g)
 Turtle(x+4.5*w, y, pi)\
@@ -314,7 +318,8 @@ y -= 6*r
[…]

### 2015-10-18 fib2.tex
more words

@@
 
+The goal here is to describe the algorithm for
+computing charge contained regions built from 
+arbitrary collection of tiles.
+To do this we first describe our approach
+to topological quantum field theory,
+then we discuss the data structure 
+(combinatorial curve diagrams) and the algorithm
+that operates on these structures.
+
 We give an informal introduction to
-the easy (picture) topological quantum
+anyonic topological quantum
 field theory in $(2+1)$-dimensions.
+See \cite{beverland2014} for a similar treatment.
 Note that these theories give rise to
 \emph{doubled} anyonic charges, and so
-the example in the main text only simulates
-one half of such a system...
+the Fibonacci example in the main text simulates
+one half of such a system.
 
-\section{Interaction picture}
+%\section{Interaction picture}
+\section{Topological quantum field theory}
 
@@
 
-Braid group acts (naturally) on states.
+%Braid group acts (naturally) on states.
 
@@
 until we are back at the original curve $c.$
+
+%This discussion makes it clear we have picked out a
+%specific curve $c$ that we use as a reference point for
+%other curves.
+
+The importance of this isomorphism: the simulation
+algorithm calculates outcomes of observations. This
+boils down to a change of basis, to one that includes
+the required observable.
+$F$-moves allow us to re-assocate observables along
+a curve diagram. The mapping class group acts
+transitively on curve diagrams (\emph{why??}).
 

### 2015-10-21 fib2.tex
more words

@@
 observables. For example, in
-the Fibonacci anyon case
+a system supporting Fibonacci anyons,
+we can have two Fibonacci anyons with total
+charge either vacuum or Fibonacci:
 \begin{center}
@@
 we store a combinatorial
-description of the curve intersected with that cell.
-This will be insensitive to any continuous deformation of the interior of the cell,
+description of the curve(s) intersected with that cell.
+This data structure 
+will be insensitive to any continuous deformation of the interior of the cell,
 but the simulation does not need to track any of these degrees of freedom.
@@
 The key idea is to store a \emph{word} for each cell, comprised of
-the letters $<$ and $>$.
+the letters $\bigl<$ and $\bigr>$.
 When these brackets are balanced,
@@
 the cell from the top-left corner,
-we record our encouters with each piece of curve diagram,
-writing a $<$ for the first encounter, and $>$ for the
+we record our encounters with each piece of curve diagram,
+writing~$\bigl<$ for the first encounter, and~$\bigr>$ for the
 second. We may also encounter a dangling piece of curve
 diagram (the head or the tail), so we use another symbol $*$ for this.
-The words for the above two cells will then be $<<>><>$ and $<>*<<>>.$
-Getting more elaborate, we will also need to record the direction
-of each piece of curve,
-and we allow anyons to reside on the curve
-close to the edge. (This means we cannot have more than two anyons
-per piece, but if that is needed we will have added another curve diagram.)
-We will also record,
-for each intersection with the cell edge, which side the
+The words for the above two cells will then be 
+$\bigl<\bigl<\bigr>\bigr>\bigl<\bigr>$ and $\bigl<\bigr>*\bigl<\bigl<\bigr>\bigr>.$
+
+We will also need to record
+various other attributes of these curves,
+and to do this we make this notation more elaborate
+in the paragraphs {\bf (I)}, {\bf(II)} and {\bf(III)} below.
+Each symbol in the word describes an intersection of
+the curve with the cell boundary,
+and so as we decorate these symbols these decorations will
+apply to such intersection points.
+
+{\bf (I)} We will record the direction of each piece of curve,
+this will be either an {\tt in} or {\tt out} decoration for each symbol.
+Such decorations need to balance according to the brackets,
+eg. $\bigl<_{\mbox{\tt in}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}\bigr>_{\mbox{\tt out}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}$.
+Similarly, the decorated symbols $*_{\mbox{\tt in}}$ and 
+$*_{\mbox{\tt out}}$ 
+will denote respectively either
+the head, $c(1)$ or the tail $c(0)$ of a curve.
+
+{\bf (II)} We will record,
+for each intersection with the cell edge, which of the four
+sides of the cell the
 intersection occurs on.
+Numbering these clockwise from the top as $1, 2, 3, 4$ we have for the above curves: 
+$\bigl<_1\bigl<_2\bigr>_2\bigr>_3\bigl<_3\bigr>_4$ 
+and $\bigl<_1\bigr>_1*_2\bigl<_3\bigl<_3\bigr>_4\bigr>_4.$
+This will require every curve diagram to intersect 
+the edges of cells transversally,
+and in particular a curve will not touch a cell corner.
 
-Various other consistency relations are enforced on a combinatorial curve diagram,
+{\bf (III)} Finally, we will also decorate these symbols with anyons.
+This will be an index to a leaf of a (sum of) fusion tree(s).
+This means that anyons only reside on the curve close
+to the cell boundary,
+and so we cannot have more than two anyons
+for each piece of curve. 
+The number of such pieces is arbitrary, and so this
+is no restriction on generality.
+
+Various other consistency relations are enforced on such a combinatorial curve diagram,
 such as requiring two
@@
 (Note that in general we will have many disjoint curve diagrams.)
-We also require every curve diagram to intersect 
-the edges of cells transversally.
-This will mean in particular that a curve will not touch a cell corner.
 
-Two disjoint curves can be joined by...
-
-Curves can be simplified along sections without any anyons, ...
+%Two disjoint curves can be joined by...
+%
+%Curves can be simplified along sections without any anyons, ...
 

### 2015-10-26 fib2.tex
more about Combinatorial curve diagrams

@@
 diagram.}
-For each cell in the lattice,
+For each tile in the lattice,
 we store a combinatorial
-description of the curve(s) intersected with that cell.
-This data structure 
-will be insensitive to any continuous deformation of the interior of the cell,
-but the simulation does not need to track any of these degrees of freedom.
+description of the curve(s) intersected with that tile.
+To this end, we will require each such curve to intersect 
+the edges of tiles transversally,
+and in particular a curve will not touch a tile corner.
 \begin{center}
@@
 \end{center}
+
 We follow essentially the same approach as taken in \cite{Abramsky2007} 
@@
 with some extra decorations.
-The key idea is to store a \emph{word} for each cell, comprised of
+The key idea is to store a \emph{word} for each tile, comprised of
 the letters $\bigl<$ and $\bigr>$.
-When these brackets are balanced,
-each such word will correspond one-to-one with an intersection
-of a curve in a cell (up to any continuous deformation of the interior of the cell).
-The encoding works as follows.
+%The encoding works as follows.
 Reading in a clockwise direction around the edge of
-the cell from the top-left corner,
+the tile from the top-left corner,
 we record our encounters with each piece of curve diagram,
 writing~$\bigl<$ for the first encounter, and~$\bigr>$ for the
-second. We may also encounter a dangling piece of curve
+second.
+We may also encounter a dangling piece of curve
 diagram (the head or the tail), so we use another symbol $*$ for this.
-The words for the above two cells will then be 
+The words for the above two tiles will then be 
 $\bigl<\bigl<\bigr>\bigr>\bigl<\bigr>$ and $\bigl<\bigr>*\bigl<\bigl<\bigr>\bigr>.$
+When the brackets are balanced,
+each such word will correspond one-to-one with an intersection
+of a curve in a tile, up to a continuous deformation of the interior of the tile.
+Ie. the data structure 
+will be insensitive to any continuous deformation of the interior of the tile,
+but the simulation does not need to track any of these degrees of freedom.
+
+\begin{center}
+\includegraphics[]{pic-cells-0.pdf}
+\end{center}
 
@@
 Each symbol in the word describes an intersection of
-the curve with the cell boundary,
+the curve with the tile boundary,
 and so as we decorate these symbols these decorations will
@@
 
+\begin{center}
+\includegraphics[]{pic-cells-1.pdf}
+\end{center}
+
 {\bf (I)} We will record the direction of each piece of curve,
 this will be either an {\tt in} or {\tt out} decoration for each symbol.
-Such decorations need to balance according to the brackets,
-eg. $\bigl<_{\mbox{\tt in}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}\bigr>_{\mbox{\tt out}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}$.
-Similarly, the decorated symbols $*_{\mbox{\tt in}}$ and 
+Such decorations need to balance according to the brackets.
+The decorated symbols $*_{\mbox{\tt in}}$ and 
 $*_{\mbox{\tt out}}$ 
 will denote respectively either
-the head, $c(1)$ or the tail $c(0)$ of a curve.
+%the head, $c(1)$ or the tail $c(0)$ of a curve.
+the head or the tail of a curve.
+The words for these diagrams now read as
+$ \bigl<_{\mbox{\tt in}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}
+    \bigr>_{\mbox{\tt out}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}$
+and
+$ \bigl<_{\mbox{\tt in}}\bigl>_{\mbox{\tt out}}*_{\mbox{\tt in}}
+    \bigr<_{\mbox{\tt out}}
+    \bigr<_{\mbox{\tt in}}\bigl>_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}.
+$
 
 {\bf (II)} We will record,
-for each intersection with the cell edge, which of the four
-sides of the cell the
+for each intersection with the tile edge, which of the four
+sides of the tile the
 intersection occurs on.
@@
 and $\bigl<_1\bigr>_1*_2\bigl<_3\bigl<_3\bigr>_4\bigr>_4.$
-This will require every curve diagram to intersect 
-the edges of cells transversally,
-and in particular a curve will not touch a cell corner.
 
@@
 This means that anyons only reside on the curve close
-to the cell boundary,
+to the tile boundary,
 and so we cannot have more than two anyons
@@
 
-Various other consistency relations are enforced on such a combinatorial curve diagram,
-such as requiring two
-adjacent cells to agree on their boundaries, and every curve diagram
-having two ends.
-(Note that in general we will have many disjoint curve diagrams.)
+\begin{center}
+\includegraphics[]{pic-cells-2.pdf}
+\end{center}
+
+In joining tiles together to make a tiling we will
+require adjacent tiles to agree on their shared boundary.
+This will entail sequentially pairing symbols in the
+words for adjacent tiles
+and requiring that 
+the {\tt in} and {\tt out} decorations are matched.
+Because the word for a tile proceeds conter-clockwise
+around the tile, this pairing will always reverse the
+sequential order of the symbols of adjacent tiles.
+For example, given the above two tiles we sequentially pair the 
+$\bigl<_{\mbox{\tt out},2}\bigr>_{\mbox{\tt in},2}$ 
+and $\bigr>_{\mbox{\tt out},4}\bigr>_{\mbox{\tt in},4}$
+symbols with opposite order so that
+$\bigl<_{\mbox{\tt out},2}\sim\bigr>_{\mbox{\tt in},4}$
+and $\bigr>_{\mbox{\tt in},2} \sim \bigr>_{\mbox{\tt out},4}.$
+
+%Two other consistency relations are enforced on such a combinatorial curve diagram:
+%we require adjacent tiles to agree on their boundaries, 
+%and every curve diagram
+%must have two ends.
+%One final consistency
+%relation is enforced by requiring 
+%We require every curve diagram to have two ends, this means
+%that there are no loops.
+
+Note that in general we will have many disjoint curve diagrams
+$c_i:[0,1]\to D_{n_i}$ within a disc $D_m$ where $\sum n_i = m.$
 
@@
 Anyons are transported around the lattice
-by moving them along cell edges.
+by moving them along tile edges.
 In general, such a transport will intersect with a
@@
 %We look at the particular case of moving along
-%one edge of a cell,
-transporting along one edge of a cell \emph{forwards} 
+%one edge of a tile,
+transporting along one edge of a tile \emph{forwards} 
 (from tail to head) along a curve diagram:

### 2015-10-26 tqft.py

@@ -60,7 +60,7 @@ shade = grey
 
 
 
-g_arrow = [green, style.linewidth.THick]
+g_curve = [green, style.linewidth.THick]
 
 st_tau = [style.linewidth.Thick, red, style.linecap.round]
 #st_vac = [style.linewidth.thick, red]+st_dotted
@@ -131,9 +131,9 @@ p = path.path(
     path.arc(x, y, r, 0, 90),
     path.lineto(x-m, y+r), 
 )
-c.stroke(p, g_arrow+[trafo.scale(1.0, 1.3, x=x, y=y-m)])
+c.stroke(p, g_curve+[trafo.scale(1.0, 1.3, x=x, y=y-m)])
 
-c.stroke(path.line(x+0.5*w, y-m, x+0.5*w, y+h+m), g_arrow)
+c.stroke(path.line(x+0.5*w, y-m, x+0.5*w, y+h+m), g_curve)
 
 r = 0.2*w
 p = path.path(
@@ -142,7 +142,7 @@ p = path.path(
     path.arc(x+w, y+0.5*h, r, 90, 270),
     path.lineto(x+w+m, y+0.5*h-r), 
 )
-c.stroke(p, g_arrow+[trafo.scale(1.4, 1.0, x=x+1.*w+m, y=y+0.5*h)])
+c.stroke(p, g_curve+[trafo.scale(1.4, 1.0, x=x+1.*w+m, y=y+0.5*h)])
 
 
 x += w + 6*m
@@ -157,9 +157,9 @@ p = path.path(
     path.arc(x+0.6*w, y+1.0*h, r, 180, 0),
     path.lineto(x+0.8*w, y+1.0*h+m), 
 )
-c.stroke(p, g_arrow+[trafo.scale(1.0, 1.5, x=x+0.3*w, y=y+1.0*h+m)])
+c.stroke(p, g_curve+[trafo.scale(1.0, 1.5, x=x+0.3*w, y=y+1.0*h+m)])
 
-c.stroke(path.line(x+w+m, y+0.5*h, x+w-1.6*r, y+0.5*h), g_arrow) #+[deco.earrow(size=0.2)])
+c.stroke(path.line(x+w+m, y+0.5*h, x+w-1.6*r, y+0.5*h), g_curve) #+[deco.earrow(size=0.2)])
 
 r = 0.7*h
 p = path.path(
@@ -168,7 +168,7 @@ p = path.path(
[…]

### 2015-10-28 twist.py
add file

@@ -1,0 +1,380 @@
+#!/usr/bin/env python
+
+import sys, os
+
+from random import random, seed
+from math import *
+
+EPSILON = 1e-8
+
+def _bump(x):
+
+    assert 0.<=x<=1.
+    if x<EPSILON:
+        return 0.
+
+    A = exp(-1)
+    x = 1.-x
+    y = exp(-1./(1-x**2))
+    y /= A
+    assert 0.<=y<=1.+EPSILON
+    return y
+
+def bump(x):
+
+    y = 0.5 * (_bump(x) + 1.-_bump(1.-x))
+
+    return y
+
+
+def bump0(x):
+    if abs(x) < 1-EPSILON:
+        y = exp(-1./(1-x**2))
+    else:
+        y = 0.
+    return y
+
+for i in range(11):
+    v = i/10.
+    bump(v)
+
+
+def c2p(x, y):
+
+    r = sqrt(x**2+y**2)
+
+    if abs(x) > EPSILON:
+        theta = atan(y/x)
+    elif x<=0:
+        if y>=0:
+            theta = -pi/2
+        else:
+            theta = pi/2
+    elif y>=0:
+        theta = pi/2
+    else:
+        theta = -pi/2
+
+    if x <= 0:
+        if y>=0:
+            #print "+pi",
+            theta += pi
+        else:
+            #print "-pi",
+            theta -= pi
+            
+    return r, theta
+
+
+def p2c(r, theta):
+
+    x = r*cos(theta)
+    y = r*sin(theta)
+
+    return x, y
+
+
+def rnd(r=1.):
+    x = (random() * 2 - 1.) * r
+    return x
+
+def str(a, b):
+    s = "%.2f,%.2f"%(a, b)
+    s = s.rjust(11)
+    return s
+
+def twist(x, y, phi=0., r1=1., r2=2., x0=0., y0=0.):
+
+    x -= x0
+    y -= y0
+    r, theta = c2p(x, y)
+
+    assert r2-r1>EPSILON
+
+    if r <= r1:
+        theta += phi
+    elif r <= r2:
+        theta += phi*bump((r2-r)/(r2-r1))
+
+    x, y = p2c(r, theta)
+
+    x += x0
+    y += y0
+    return x, y
+
+
+seed(0)
+
+for i in range(10):
+    x, y = rnd(), rnd()
+    r, theta = c2p(x, y)
+    x1, y1 = p2c(r, theta)
+    assert abs(x1-x) + abs(y1-y) < EPSILON
+
[…]

### 2015-11-09 fib2.tex
start on modular functors
more about the curves

@@
 
+\section{Modular Functors}
+
+As in algebraic topology, we wish to extract
+algebraic information about topological objects.
+This can be viewed as a kind of representation theory
+of topological objects: homeomorphisms of surfaces.
+
+We list the axioms for a \emph{2-dimensional unitary modular functor}
+\cite{Turaev1994}, \cite{Walker1991}.
+
 %\section{Interaction picture}
@@
 
+%
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+%
+
 \section{Combinatorial curve diagrams}
@@
 diagram.}
+% XXX define "piece of curve"
+Firstly, we will require each curve to intersect 
+the edges of tiles transversally,
+and in particular a curve will not touch a tile corner.
+
 For each tile in the lattice,
@@
 description of the curve(s) intersected with that tile.
-To this end, we will require each such curve to intersect 
-the edges of tiles transversally,
-and in particular a curve will not touch a tile corner.
+Each component of such an intersection we call a \emph{piece-of-curve.}
 \begin{center}
@@
 the tile from the top-left corner,
-we record our encounters with each piece of curve diagram,
+we record our encounters with each piece-of-curve,
 writing~$\bigl<$ for the first encounter, and~$\bigr>$ for the
 second.
-We may also encounter a dangling piece of curve
-diagram (the head or the tail), so we use another symbol $*$ for this.
+We may also encounter a dangling piece-of-curve
+(the head or the tail), so we use another symbol $*$ for this.
 The words for the above two tiles will then be 
@@
 
-{\bf (I)} We will record the direction of each piece of curve,
+{\bf (I)} We will record the direction of each piece-of-curve,
 this will be either an {\tt in} or {\tt out} decoration for each symbol.
@@
 the head or the tail of a curve.
-The words for these diagrams now read as
+The words for the diagrams above now read as
 $ \bigl<_{\mbox{\tt in}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}
@@
 {\bf (II)} We will record,
-for each intersection with the tile edge, which of the four
+for each intersection with the tile edge, 
+a numeral indicating which of the four
 sides of the tile the
@@
 and so we cannot have more than two anyons
-for each piece of curve. 
+for each piece-of-curve. 
 The number of such pieces is arbitrary, and so this
@@
 
-Note that in general we will have many disjoint curve diagrams
+Note that in general this data structure will store many disjoint curve diagrams
 $c_i:[0,1]\to D_{n_i}$ within a disc $D_m$ where $\sum n_i = m.$
+
+%For a given piece-of-curve, we can subtract the numeral with
+%the {\tt in} label from the numeral with the {\tt out} label
+%to get an integer in $\{ \}$ WRONG
+%We can also just use the numerals of the boundary edges
+%that the piece-of-curve intersects with, subtracting the
+%``exit'' boundary numeral from the ``entry'' boundary numeral. WRONG
+
+For each piece-of-curve, apart from a head or tail, there is an associated 
+number we call the \emph{turn number}. This counts the number
+of ``right-hand turns'' the piece-of-curve makes as it
+traverses the tile, with a ``left-hand turn'' counting as $-1.$
+(To be more rigorous, we would define this number using the
+winding number of the simple closed curve formed by the
+piece-of-curve adjoined to a segment of the boundary of the tile 
+traversed in a clockwise direction.)
+This number will take one of the values $-2, -1, 0, 1, 2:$
+\begin{center}
+\includegraphics[]{pic-cells-3.pdf}
+\end{center}
 
@@
 % mention Jones' planar algebras ?
+
+%
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+%
 
@@
 -2:&\ R[B] \\
--4:&\ R[H^r] R[H] R[B] \\
-+4:&\ R[B] R[T] R[T^r] \\
-+6:&\ R[H^r] R[H] R[B] R[T] R[T^r] \\
+-4:&\ R[H^r]\ R[H]\ R[B] \\
++4:&\ R[B]\ R[T]\ R[T^r] \\
++6:&\ R[H^r]\ R[H]\ R[B]\ R[T]\ R[T^r] \\
 \end{align*}

### 2015-11-09 tqft.py

@@ -311,6 +311,16 @@ c.writePDFfile("pic-cells-0.pdf")
 
 g_arrow = g_curve + [deco.earrow(size=0.3)]
 
+def up_arrow(x, y):
+    c.stroke(path.line(x, y-m0, x, y+m0), g_arrow)
+def dn_arrow(x, y):
+    c.stroke(path.line(x, y+m0, x, y-m0), g_arrow)
+def le_arrow(x, y):
+    c.stroke(path.line(x+m0, y, x-m0, y), g_arrow)
+def ri_arrow(x, y):
+    c.stroke(path.line(x-m0, y, x+m0, y), g_arrow)
+
+
 w = 1.5
 h = 1.5
 
@@ -322,15 +332,6 @@ y = 0.
 m = 0.1*w
 m0 = m/2
 r = 0.3*w
-
-def up_arrow(x, y):
-    c.stroke(path.line(x, y-m0, x, y+m0), g_arrow)
-def dn_arrow(x, y):
-    c.stroke(path.line(x, y+m0, x, y-m0), g_arrow)
-def le_arrow(x, y):
-    c.stroke(path.line(x+m0, y, x-m0, y), g_arrow)
-def ri_arrow(x, y):
-    c.stroke(path.line(x-m0, y, x+m0, y), g_arrow)
 
 c.fill(path.rect(x-m0, y-m0, 2*m0+w, 2*m0+h), [shade])
 c.stroke(path.rect(x, y, w, h))
@@ -410,6 +411,111 @@ ri_arrow(x, y+r)
 dn_arrow(x+r, y)
 
 c.writePDFfile("pic-cells-1.pdf")
+
+
+#############################################################################
+#
+#
+
+
+w = 1.5
+h = 1.5
+
+c = canvas.canvas()
+
+
+x = 0.
+y = 0.
+m = 0.1*w
+m0 = m/2
+r = 0.3*w
+
+c.fill(path.rect(x-m0, y-m0, 2*m0+w, 2*m0+h), [shade])
+c.stroke(path.rect(x, y, w, h))
+
+p = path.path(
+    path.moveto(x+r, y), 
+    path.lineto(x+r, y),
+    path.arc(x, y, r, 0, 90),
+    path.lineto(x, y+r), 
+)
[…]

### 2015-11-09 fib2.tex
start on modular functors

@@
 \usepackage{enumerate}
+\usepackage{mathrsfs}
 
@@
 
-We give an informal introduction to
-anyonic topological quantum
-field theory in $(2+1)$-dimensions.
-See \cite{beverland2014} for a similar treatment.
-Note that these theories give rise to
-\emph{doubled} anyonic charges, and so
-the Fibonacci example in the main text simulates
-one half of such a system.
+%We give an informal introduction to
+%anyonic topological quantum
+%field theory in $(2+1)$-dimensions.
+%See \cite{beverland2014} for a similar treatment.
+%Note that these theories give rise to
+%\emph{doubled} anyonic charges, and so
+%the Fibonacci example in the main text simulates
+%one half of such a system. % MEH!
 
@@
 
-We list the axioms for a \emph{2-dimensional unitary modular functor}
-\cite{Turaev1994}, \cite{Walker1991}.
+We list the axioms for a \emph{2-dimensional unitary topological modular functor}.
+ % abbreviated as \emph{MF}.
+For the details of this construction, see
+\cite{Turaev1994}, \cite{Walker1991} or \cite{Bakalov2000}.
+For a more pedestrian treatment, see \cite{Freedman2002simulation} or \cite{Beverland2004.}
+
+For our purposes a \emph{surface} will be an
+oriented $2$-dimensional manifold with boundary.
+Each boundary component is labelled with
+an element from a finite set $\mathbb{A}=\{1, a, b, c ...\}.$
+This is the set of ``anyon labels'', and comes
+equiped with an involution $\hat{}$ such that $\hat{1}=1.$
+Each boundary component is oriented (either explicitly or
+otherwise by using the orientation of the manifold)
+and contains a distinguished point.
+
+We will mostly be concerned with \emph{planar} such
+surfaces, ie. a disc with zero or more holes.
+
+\newcommand{\F}{\mathscr{H}} % H or F ?
+
+A modular functor $\F$ associates to every
+surface $M$ a finite dimensional complex
+vector space $\F(M)$, called the \emph{fusion space} of $M$.
+A map of surfaces $f:M\to N$ will be understood to be
+a topological homeomorphism that preserves boundary
+labels and orientation, and
+the modular functor assocates such an $f$ to a
+unitary transformation $\F(f) : \F(M)\to\F(N).$
+Functoriality requires that $\F$
+respect composition of homeomorphisms.
+
+We have the following axioms for $\F.$
+
+{\bf Axiom I.}
+The disjoint union of two surfaces $M$ and $N$ 
+is assocated with
+the tensor product of fusion spaces:
+$$
+    \F(M\amalg N) = \F(M)\otimes \F(N).
+$$
+This is natural from the point of view of quantum
+physics, where the Hilbert space of two disjoint
+systems is the tensor product of the space for
+each system.
+
+{\bf Axiom II.}
+The fusion space of an empty surface is one dimensional: 
+$\F(\phi) \cong \mathbb{C}.$
+
+{\bf Axiom III.}
+Gluing.
 

### 2015-11-10 fib2.tex
finish MF axioms

@@
 equiped with an involution $\hat{}$ such that $\hat{1}=1.$
-Each boundary component is oriented (either explicitly or
-otherwise by using the orientation of the manifold)
+%Each boundary component is oriented (either explicitly or
+%otherwise by using the orientation of the manifold)
+Each boundary component inherits the manifold orientation 
 and contains a distinguished point.
@@
 We will mostly be concerned with \emph{planar} such
-surfaces, ie. a disc with zero or more holes.
+surfaces, ie. disc(s) with zero or more holes.
+Note that we will not require surfaces themselves to be connected.
 
 \newcommand{\F}{\mathscr{H}} % H or F ?
+\newcommand{\C}{\mathbb{C}}
 
@@
 {\bf Axiom I.}
+The fusion space of an empty surface is one dimensional, 
+$\F(\phi) \cong \C.$
+For $M_a$ a disc with boundary label $a$ we have
+$\F(M_1)\cong \C$ and 
+$\F(M_a)\cong 0$ for $a\ne 1.$
+For annulus $M_{a,b}$ with boundary labels
+$a, b$ we have
+$\F(M_{a,\hat{a}})\cong \C$ and 
+$\F(M_{a,b})\cong 0$ for $a\ne \hat{b}.$
+
+{\bf Axiom II.}
 The disjoint union of two surfaces $M$ and $N$ 
@@
 $$
-    \F(M\amalg N) = \F(M)\otimes \F(N).
+    \F(M\amalg N) \cong \F(M)\otimes \F(N).
 $$
@@
 
-{\bf Axiom II.}
-The fusion space of an empty surface is one dimensional: 
-$\F(\phi) \cong \mathbb{C}.$
-
 {\bf Axiom III.}
-Gluing.
+%Gluing.
+Denote a surface $M$ with (at least) two boundary
+components labelled $a, b$ as $M_{a,b}$. 
+Let $N$ be the surface obtained from $M$ by gluing
+these two boundary components together.
+If we constrain $b=\hat{a}$ then the fusion space
+of $M_{a,\hat{a}}$ embedds unitarily in the fusion
+space of $N.$ Moreover, there is a unitary map
+$$
+    \bigoplus_{a\in\mathbb{A}} \F(M_{a,\hat{a}}) \to \F(N).
+$$
+A common operation is to glue two separate surfaces.
+We can do this by first taking disjoint union (tensoring
+the fusion spaces)
+and then gluing.
 

### 2015-11-10 fib2.tex
show a glueing map

@@
 
-We list the axioms for a \emph{2-dimensional unitary topological modular functor}.
+We list the axioms for a 
+\emph{2-dimensional unitary topological modular functor}.
  % abbreviated as \emph{MF}.
-For the details of this construction, see
+There are quite alot of details that we leave out,
+%For the details of this construction, see
+see
 \cite{Turaev1994}, \cite{Walker1991} or \cite{Bakalov2000}.
@@
 $$
-    \bigoplus_{a\in\mathbb{A}} \F(M_{a,\hat{a}}) \to \F(N).
+    \bigoplus_{a\in\mathbb{A}} \F(M_{a,\hat{a}}) \xrightarrow{\cong} \F(N).
 $$
@@
 and then gluing.
+
+Here we show this process applied to the disjoint union
+%of two surfaces $M_a$ and $N_{\hat{a}}$. 
+of two surfaces $M$ and $N$. 
+We display the surface $N$ with the $\hat{a}$
+boundary on the outside, to show more clearly how $N$ fits into $M$.
+In the glued manifold we
+indicate the placement of $M$ and $N$ and the seam
+along which glueing occured.
+\begin{center}
+\includegraphics[]{pic-glue.pdf}
+\end{center}
+
+\emph{XXX show marked point on boundaries ?}
+
+\emph{XXX show orientation of boundaries ?}
 

### 2015-11-10 modular.py

@@ -1,0 +1,193 @@
+#!/usr/bin/env python
+
+import sys
+import os
+
+from math import *
+from random import *
+
+from pyx import canvas, path, deco, trafo, style, text, color, unit, epsfile, deformer, bitmap
+
+from PIL import Image
+
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
+
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+
+
+text.set(mode="latex")
+text.set(docopt="12pt")
+text.preamble(r'\usepackage{amsmath,amsfonts,amssymb}')
+text.preamble(r'\usepackage{mathrsfs}')
+#text.preamble(r"\def\I{\mathbb{I}}")
+text.preamble(r"\def\ket #1{|#1\rangle}")
+text.preamble(r"\def\H{\mathscr{H}}")
+
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow, orange = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, 
+    rgb(0.75, 0.75, 0),
+    rgb(0.75, 0.55, 0),
+    )
+
+blue = rgb(0., 0., 0.8)
+pale_blue = rgb(0.7, 0.7, 1.0)
+pink = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.)
+grey = rgb(0.8, 0.8, 0.8)
+
+brown = rgbfromhexstring("#AA6C39"),
+
+light_shade = rgb(0.85, 0.65, 0.1)
+
+#shade = brown
+#shade = orange
+shade = grey
+
+
+
[…]

### 2015-11-11 fib2.tex
show how gluing gives F-move

--- 2015-11-10 fib2.tex
@@
 
+%
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+%
+
 \section{Modular Functors}
@@
 
-We list the axioms for a \emph{2-dimensional unitary topological modular functor}.
+We list the axioms for a 
+\emph{2-dimensional unitary topological modular functor}.
  % abbreviated as \emph{MF}.
-For the details of this construction, see
+There are quite alot of details that we leave out,
+%For the details of this construction, see
+see
 \cite{Turaev1994}, \cite{Walker1991} or \cite{Bakalov2000}.
-For a more pedestrian treatment, see \cite{Freedman2002simulation} or \cite{Beverland2004.}
+For a more pedestrian treatment, see \cite{Freedman2002simulation} or \cite{Beverland2014}.
+
+\newcommand{\F}{\mathscr{H}} % H or F ?
+\newcommand{\C}{\mathbb{C}}
+\newcommand{\A}{\mathcal{A}}
 
@@
 oriented $2$-dimensional manifold with boundary.
-Each boundary component is labelled with
-an element from a finite set $\mathbb{A}=\{1, a, b, c ...\}.$
-This is the set of ``anyon labels'', and comes
-equiped with an involution $\hat{}$ such that $\hat{1}=1.$
+We will not require surfaces to be connected.
 %Each boundary component is oriented (either explicitly or
 %otherwise by using the orientation of the manifold)
-Each boundary component inherits the manifold orientation 
-and contains a distinguished point.
+Each boundary component will inherit the manifold orientation,
+contain a distinguished point,
+and be labelled with
+%an element from a finite set $\mathbb{A}=\{1, a, b, c ...\}.$
+an element from a finite set $\A.$
+This is the set of ``anyon labels'', and comes
+equiped with a vacuum element $\vac$ 
+and an involution $\ \widehat{}\ $ such that $\widehat{\vac}=\vac.$
 
@@
 surfaces, ie. disc(s) with zero or more holes.
-Note that we will not require surfaces themselves to be connected.
-
-\newcommand{\F}{\mathscr{H}} % H or F ?
-\newcommand{\C}{\mathbb{C}}
 
@@
 For $M_a$ a disc with boundary label $a$ we have
-$\F(M_1)\cong \C$ and 
-$\F(M_a)\cong 0$ for $a\ne 1.$
+$\F(M_\vac)\cong \C$ and 
+$\F(M_a)\cong 0$ for $a\ne \vac.$
 For annulus $M_{a,b}$ with boundary labels
 $a, b$ we have
-$\F(M_{a,\hat{a}})\cong \C$ and 
-$\F(M_{a,b})\cong 0$ for $a\ne \hat{b}.$
+$\F(M_{a,\widehat{a}})\cong \C$ and 
+$\F(M_{a,b})\cong 0$ for $a\ne \widehat{b}.$
 
@@
 these two boundary components together.
-If we constrain $b=\hat{a}$ then the fusion space
-of $M_{a,\hat{a}}$ embedds unitarily in the fusion
+Glueing must respect the orientation of the two boundary
+components as well as identifying their distinguished points.
+If we constrain $b=\widehat{a}$ then the fusion space
+of $M_{a,\widehat{a}}$ embedds unitarily in the fusion
 space of $N.$ Moreover, there is a unitary map
 $$
-    \bigoplus_{a\in\mathbb{A}} \F(M_{a,\hat{a}}) \to \F(N).
+    \bigoplus_{a\in\A} \F(M_{a,\widehat{a}}) \xrightarrow{\cong} \F(N).
 $$
@@
 and then gluing.
+
+Here we show this process applied to two surfaces $M$ and $N$. 
+\begin{center}
+\includegraphics[]{pic-glue.pdf}
+\end{center}
+We display the surface $N$ with the $\widehat{a}$
+boundary on the outside, 
+to show more clearly how it fits into $M$.
+In the glued manifold we
+indicate the placement of $M$ and $N$ and the seam
+along which glueing occured,
+as well as the identification of distinguished points.
+
+%\emph{XXX show marked point on boundaries ?}
+
+\emph{XXX show orientation of boundaries ?}
+\emph{XXX displaymath direct sum}
+\emph{XXX $N...$ show ellipses?}
+
+A most important linear map, called an $F-$move,
+is constructed from two applications of the
+gluing isomorphism as follows.
+
+\begin{widetext}
+\begin{center}
+\includegraphics[]{pic-glue-fmove.pdf}
+\end{center}
+\end{widetext}
+
+Here we have shown a manifold $M_{abc}$ with 
+three labelled boundaries, as well as two separate
+ways of gluing pairs-of-pants to get $M.$
+
+%
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+%
 

### 2015-11-11 modular.py

@@ -130,16 +130,19 @@ x += 0.0*w
 p = path.circle(x+r, y+0.5*h, r)
 c.fill(p, [shade])
 c.stroke(p)
+c.fill(path.circle(x+2*r, y+0.5*h, 0.06))
 
 x += 0.3*w
 p = path.circle(x+0.1*w, y+0.5*h, 0.4*r)
 c.fill(p, [white])
 c.stroke(p)
+p = path.circle(x+0.1*w+0.4*r, y+0.5*h, 0.06)
+c.fill(p)
 
 c.text(x+0.6*w, y+0.5*h, "...")
 
 #c.text(x+0.1*w, y+0.0*h, "$M_a$", west)
-c.text(x+0.1*w, y+0.0*h, "$M$", west)
+c.text(x+0.2*w, y+0.0*h, "$M$", west)
 
 c.text(x+0.3*w, y+0.7*h, "$a$", southwest)
 
@@ -149,6 +152,8 @@ r = 0.7
 p = path.circle(x+r, y+0.5*h, r)
 c.fill(p, [shade])
 c.stroke(p)
+p = path.circle(x+2*r, y+0.5*h, 0.06)
+c.fill(p)
 
 x += 0.3*w
 
@@ -174,11 +179,17 @@ r = 1.0
 p = path.circle(x+r, y+0.5*h, r)
 c.fill(p, [shade])
 c.stroke(p)
+c.stroke(p)
+c.fill(path.circle(x+2*r, y+0.5*h, 0.06))
 
 x += 0.3*w
 p = path.circle(x+0.1*w, y+0.5*h, 0.4*r)
 c.stroke(p, st_dashed)
+p = path.circle(x+0.1*w+0.4*r, y+0.5*h, 0.06)
+c.stroke(p, st_dashed)
+
 c.text(x+0.1*w, y+0.5*h, r"$N$", center)
+#c.text(x+0.2*w, y+0.5*h, r"$...$", center)
 
 c.text(x+0.6*w, y+0.5*h, "...")
 
@@ -189,5 +200,84 @@ c.text(x, y+0.5*h, r"$\Bigr)$", east)
 
 
 c.writePDFfile("pic-glue.pdf")
+
+
+#############################################################################
+#
+#
+
+w = 1.5
+h = 1.5
+
+x = 0
+y = 0
+
+c = canvas.canvas()
+
+
+def surface(x, y, r, fill=shade, mark=False):
[…]

### 2015-11-16 fib2.tex
update

@@
 a topological homeomorphism that preserves boundary
-labels and orientation, and
-the modular functor assocates such an $f$ to a
-unitary transformation $\F(f) : \F(M)\to\F(N).$
+labels, orientation, and distinguished points.
+The modular functor associates such an $f$ to a
+unitary transformation $\F(f) : \F(M)\to\F(N)$
+that only depends on the isotopy class of $f.$
 Functoriality requires that $\F$
@@
 The disjoint union of two surfaces $M$ and $N$ 
-is assocated with
+is associated with
 the tensor product of fusion spaces:
@@
 
+Any oriented simple closed path contained in the interior of $M$ we will
+call an \emph{observable}.
+Such a path that encloses two boundary components 
+we call a \emph{2-observable}.
+A function $c:[0,1]\to M$ such that $c(0)\in \partial M$ and $c(1)\in \partial M$
+are two separate components of the boundary we call a \emph{2-curve.}
+The following important fact will be used extensively
+in the combinatorial formulation of a modular functor below:
+up to isotopy (not preserving $\partial M$),
+there is a (natural) bijection between
+$2$-observables and $2$-curves.
+
 %
@@
 is $2$-dimensional.
-Such a space assocated with observing total charge
+Such a space associated with observing total charge
 of multiple anyons is called the \emph{fusion} space
@@
 the required observable.
-$F$-moves allow us to re-assocate observables along
+$F$-moves allow us to re-associate observables along
 a curve diagram. The mapping class group acts

### 2015-11-17 fib2.tex
f-moves and curves emerge

@@
 Each boundary component will inherit the manifold orientation,
-contain a distinguished point,
+contain a distinguished \emph{base point},
 and be labelled with
@@
 a topological homeomorphism that preserves boundary
-labels, orientation, and distinguished points.
+labels, orientation, and base points.
 The modular functor associates such an $f$ to a
@@
 Glueing must respect the orientation of the two boundary
-components as well as identifying their distinguished points.
+components as well as identifying their base points.
 If we constrain $b=\widehat{a}$ then the fusion space
 of $M_{a,\widehat{a}}$ embedds unitarily in the fusion
-space of $N.$ Moreover, there is a unitary map
+space of $N.$ Moreover, there is an isomorphism called
+a \emph{gluing map}:
 $$
@@
 $$
+The seam along which gluing occurs can be associated
+with an observable as follows.
+We take a gluing map $g$. Projectors $P_a$ onto the
+summands in the above direct sum:
+$$
+    P_a: \bigoplus_{b\in\A} \F(M_{b,\widehat{b}}) \to \F(M_{a,\widehat{a}}).
+$$
+then the observable will be the set of operators $\{P_a g^{-1}\}_{a\in\A}.$
+
 A common operation is to glue two separate surfaces.
@@
 and then gluing.
-
 Here we show this process applied to two surfaces $M$ and $N$. 
@@
 boundary on the outside, 
-to show more clearly how it fits into $M$.
+to show more clearly how $N$ fits into $M$.
 In the glued manifold we
@@
 along which glueing occured,
-as well as the identification of distinguished points.
-
-%\emph{XXX show marked point on boundaries ?}
-
-\emph{XXX show orientation of boundaries ?}
-\emph{XXX displaymath direct sum}
-\emph{XXX $N...$ show ellipses?}
+as well as the identification of base points.
+
+%\emph{XXX show orientation of boundaries ?}
+%\emph{XXX displaymath direct sum}
+%\emph{XXX $N...$ show ellipses?}
 
 A most important linear map, called an $F-$move,
-is constructed from two applications of the
-gluing isomorphism as follows.
+is constructed from two applications of a
+gluing map as follows.
 
@@
 
-Any oriented simple closed path contained in the interior of $M$ we will
-call an \emph{observable}.
+As we have seen, an oriented simple closed path 
+ contained in the interior of $M$ can serve as
+the seam along which gluing occurs and so we call
+these paths \emph{observables}.
+%Any oriented simple closed path contained in the interior of $M$ we will
+%call an \emph{observable}.
 Such a path that encloses two boundary components 
 we call a \emph{2-observable}.
+\emph{(what does enclose mean exactly?)}
 A function $c:[0,1]\to M$ such that $c(0)\in \partial M$ and $c(1)\in \partial M$
@@
 $2$-observables and $2$-curves.
+\emph{(restrict to $M$ a disc with at least two holes?)}
+Here we show two such instances of this
+bijection:
+\begin{center}
+\includegraphics[]{pic-2-curve.pdf}
+\end{center}
+The bijections works as follows.
+To construct a $2$-observable from a $2$-curve $c$ that
+joins two boundary components $M_1$ and $M_2$,
+take a small neighbourhood of
+the union $c([0,1])\cup M_1 \cup M_2.$
+This neighbourhood will have boundary a simple closed
+curve that encloses $M_1$ and $M_2.$
+\emph{(check the orientation of the $2$-observable has the correct interior)}
+\emph{(the $2$-observable forgets the direction of the $2$-curve)}
+Going the other direction...
+
+The end points of $2$-curves are free to terminate anywhere
+on the boundary component, but we can fix the endpoints using
+the base points.
+A simple way to do this is to just require the
+$2$-curve to begin and end on base points.
+
+By a \emph{hole} of $M$ we mean a component of $\partial M$.
+
+A single $F$-move is seen to relate a pair of $2$-curves
+that share a hole.
+Continuing in this way, we can chain these $2$-curves together:
+\begin{center}
+\includegraphics[]{pic-chain.pdf}
+\end{center}
 

### 2015-11-17 modular.py

@@ -162,7 +162,7 @@ c.text(x+0.0*w, y+0.5*h, "...")
 #c.text(x+0.0*w, y+0.2*h, "$N_{\hat{a}}$", west)
 c.text(x+0.0*w, y+0.2*h, "$N$", west)
 
-c.text(x+0.1*w, y+0.7*h, "$\hat{a}$", southwest)
+c.text(x+0.5*w, y+0.9*h, "$\widehat{a}$", southwest)
 
 x += 1.8*r
 c.text(x, y+0.5*h, r"$\Bigr)$", east)
@@ -171,7 +171,12 @@ x -= 0*r
 y -= 3*r
 
 #c.text(x, y+0.5*h, r"$\to\H\Bigl($", east)
-c.text(x, y+0.5*h, r"$\xrightarrow{\cong}\H\Bigl($", east)
+#c.text(x, y+0.5*h, r"$\xrightarrow{\cong}\H\Bigl($", east)
+c.text(x-0.8, y+0.5*h, r"$\H\Bigl($", west)
+c.stroke(path.line(x-2.0, y+0.5*h, x-0.9, y+0.5*h), [deco.arrow()])
+c.text(x-1.5, y+0.6*h, r"$\cong$", south)
+
+print dir(deco)
 
 r = 1.0
 #x += 0.5*w
@@ -279,5 +284,154 @@ c.stroke(path.line(+3.4*r, -2.0*r, +1.9*r, -0.8*r), [deco.earrow()])
 c.text(+3.0*r, -1.4*r, "$\cong$", center)
 
 c.writePDFfile("pic-glue-fmove.pdf")
+
+
+#############################################################################
+#
+#
+
+
+
+class Turtle(object):
+    def __init__(self, x, y, theta):
+        self.x = x
+        self.y = y
+        self.theta = theta
+        self.ps = [(x, y)]
+
+    def fwd(self, d):
+        self.x += d*sin(self.theta)
+        self.y += d*cos(self.theta)
+        self.ps.append((self.x, self.y))
+        return self
+
+    def reverse(self, d):
+        self.fwd(-d)
+        return self
+
+    def right(self, dtheta, r=0.):
+        theta = self.theta
+        self.theta += dtheta
+        if r==0.:
+            return
+        N = 20
+        x, y = self.x, self.y
+        x0 = x - r*sin(theta-pi/2)
+        y0 = y - r*cos(theta-pi/2)
[…]

### 2015-11-17 modular.py
f-moves and curves emerge

@@ -393,18 +393,18 @@ c = canvas.canvas()
 
 r0 = 1.3
 
-c.fill(path.circle(x, y, r0), [shade, trafo.scale(1.4, 0.7)])
 
-
-r = 0.15
+r = 0.2
 dx = 4*r
 x1 = x-1.5*dx
 
+c.fill(path.circle(x+0.3*dx, y, r0), [shade, trafo.scale(1.6, 0.7)])
 
-r = 0.14
 
-t = Turtle(x1-1.0*dx, y+r, pi/2)
-t.fwd(5*dx)
+r = 0.20
+
+t = Turtle(x1-0.0*dx, y+r, pi/2)
+t.fwd(4*dx)
 #t.stroke(g_curve+st_dotted)
 t.stroke(g_curve)
 
@@ -423,8 +423,8 @@ surface(x1, y, r, white)
 c.fill(path.circle(x1, y+r, 0.04))
 
 
-c.text(x-2.2*dx, y-r, "...", north)
-c.text(x+2.2*dx, y-r, "...", north)
+#c.text(x-2.2*dx, y-r, "...", north)
+c.text(x+2.4*dx, y-2*r, "...", north)
 
 c.writePDFfile("pic-chain.pdf")
 

### 2015-11-18 fib2.tex
holes, 2-curves,..

@@
 
-For our purposes a \emph{surface} will be an
+For our purposes a \emph{surface} will be a compact
 oriented $2$-dimensional manifold with boundary.
@@
 %otherwise by using the orientation of the manifold)
-Each boundary component will inherit the manifold orientation,
+By a \emph{hole} of $M$ we mean a component of its boundary. % $\partial M$.
+Each hole will inherit the manifold orientation,
 contain a distinguished \emph{base point},
@@
 %an element from a finite set $\mathbb{A}=\{1, a, b, c ...\}.$
-an element from a finite set $\A.$
+an element from a (fixed) finite set $\A.$
 This is the set of ``anyon labels'', and comes
@@
 
+A map of surfaces $f:M\to N$ will be understood to be
+a topological homeomorphism that preserves
+manifold orientation, hole labels, and base points.
+
 A modular functor $\F$ associates to every
@@
 vector space $\F(M)$, called the \emph{fusion space} of $M$.
-A map of surfaces $f:M\to N$ will be understood to be
-a topological homeomorphism that preserves boundary
-labels, orientation, and base points.
-The modular functor associates such an $f$ to a
+For each map $f:M\to N$
+The modular functor associates a
 unitary transformation $\F(f) : \F(M)\to\F(N)$
@@
 Functoriality requires that $\F$
-respect composition of homeomorphisms.
+respect composition of maps.
 
@@
 %Gluing.
-Denote a surface $M$ with (at least) two boundary
-components labelled $a, b$ as $M_{a,b}$. 
+Denote a surface $M$ with (at least) two holes
+labelled $a, b$ as $M_{a,b}$. 
 Let $N$ be the surface obtained from $M$ by gluing
-these two boundary components together.
-Glueing must respect the orientation of the two boundary
-components as well as identifying their base points.
+these two holes together.
+Gluing must respect the orientation of the two holes
+as well as identifying their base points.
 If we constrain $b=\widehat{a}$ then the fusion space
@@
 indicate the placement of $M$ and $N$ and the seam
-along which glueing occured,
+along which gluing occured,
 as well as the identification of base points.
@@
 ways of gluing pairs-of-pants to get $M.$
+\emph{XXX define pair-of-pants}
 
@@
 contained in the interior of $M$ can serve as
-the seam along which gluing occurs and so we call
+the seam along which gluing occurs and we call
 these paths \emph{observables}.
@@
 %call an \emph{observable}.
-Such a path that encloses two boundary components 
+Such a path that encloses two holes
 we call a \emph{2-observable}.
 \emph{(what does enclose mean exactly?)}
-A function $c:[0,1]\to M$ such that $c(0)\in \partial M$ and $c(1)\in \partial M$
-are two separate components of the boundary we call a \emph{2-curve.}
-The following important fact will be used extensively
-in the combinatorial formulation of a modular functor below:
-up to isotopy (not preserving $\partial M$),
+A function $c:[0,1]\to M$ such that 
+$c(0)\in \partial M$ and $c(1)\in \partial M$
+are distinct basepoints (of two holes)
+we call a \emph{2-curve.}
+%The following important fact will be used extensively
+%in the combinatorial formulation of a modular functor below:
+Up to isotopy, % (not preserving $\partial M$),
 there is a (natural) bijection between
 $2$-observables and $2$-curves.
-\emph{(restrict to $M$ a disc with at least two holes?)}
+\emph{(XXX we really need undirected $2$-curves)}
+%\emph{(restrict to $M$ a disc with at least two holes?)}
 Here we show two such instances of this
@@
 To construct a $2$-observable from a $2$-curve $c$ that
-joins two boundary components $M_1$ and $M_2$,
+joins two holes $M_1$ and $M_2$,
 take a small neighbourhood of
@@
 curve that encloses $M_1$ and $M_2.$
+\emph{(is this really how to prove this? do we care?)}
 \emph{(check the orientation of the $2$-observable has the correct interior)}
-\emph{(the $2$-observable forgets the direction of the $2$-curve)}
-Going the other direction...
-
-The end points of $2$-curves are free to terminate anywhere
-on the boundary component, but we can fix the endpoints using
-the base points.
-A simple way to do this is to just require the
-$2$-curve to begin and end on base points.
-
-By a \emph{hole} of $M$ we mean a component of $\partial M$.
+Going the other direction we can take
+any $2$-curve contained within the interior of a $2$-observable,
+\emph{but how do we show these are all isotopic?}
+
+%The end points of $2$-curves are free to terminate anywhere
+%on the hole, but we can fix the endpoints using
+%the base points.
+%A simple way to do this is to just require the
+%$2$-curve to begin and end on base points.
 

### 2015-11-20 modular.py
fix displaymath

@@ -112,6 +112,13 @@ def pop(*args):
 #
 #
 
+def mathtext(x, y, text, *extra):
+    if text[0]=='$':
+        text = text[1:]
+    if text[-1]=='$':
+        text = text[:-1]
+    c.text(x, y, r"$\displaystyle %s$"%text, *extra)
+
 w = 1.5
 h = 1.5
 
@@ -121,8 +128,7 @@ y = 0
 c = canvas.canvas()
 
 #c.text(x+0.5*h, y, r"\bigoplus_a \H\bigl(", text.mathmode) #east)
-c.text(x, y+0.5*h, r"$\bigoplus_a \H\Bigl($", east)
-# XXX fix display math XXX
+mathtext(x, y+0.4*h, r"$\bigoplus_a \H\Bigl($", east)
 
 r = 1.0
 x += 0.0*w
@@ -165,7 +171,7 @@ c.text(x+0.0*w, y+0.2*h, "$N$", west)
 c.text(x+0.5*w, y+0.9*h, "$\widehat{a}$", southwest)
 
 x += 1.8*r
-c.text(x, y+0.5*h, r"$\Bigr)$", east)
+mathtext(x, y+0.5*h, r"$\Bigr)$", east)
 
 x -= 0*r
 y -= 3*r
@@ -257,7 +263,7 @@ for i, x0 in enumerate([x-0.9*r, x-0.5*r, x+0.5*r, x+0.9*r]):
     c.text(x0, y+0.2, "$%s$"%labels[i], south)
 c.text(x+1.1*r, y+0.7, "$\widehat{d}$", west)
 
-c.text(x-1.5*r, y, r"$\bigoplus_d\H\Bigl($", east)
+mathtext(x-1.5*r, y-0.13, r"$\bigoplus_d\H\Bigl($", east)
 c.text(x+1.7*r, y, r"$\Bigr)$", center)
 
 
@@ -274,7 +280,7 @@ for i, x0 in enumerate([x-0.9*r, x-0.5*r, x+0.5*r, x+0.9*r]):
     c.text(x0, y+0.2, "$%s$"%labels[i], south)
 c.text(x-1.1*r, y+0.7, "$\widehat{e}$", east)
 
-c.text(x-1.5*r, y, r"$\bigoplus_e\H\Bigl($", east)
+mathtext(x-1.5*r, y-0.13, r"$\bigoplus_e\H\Bigl($", east)
[…]

### 2015-11-24 fib2.tex
commit edits

@@
 For our purposes a \emph{surface} will be a compact
-oriented $2$-dimensional manifold with boundary.
+oriented $2$-dimensional manifold with boundary. % smooth or topological ?
 We will not require surfaces to be connected.
@@
 The fusion space of an empty surface is one dimensional, 
-$\F(\phi) \cong \C.$
+$\F(\phi) \cong \C.$ % preserves the identity of tensor
 For $M_a$ a disc with boundary label $a$ we have

### 2016-01-11 modular.py
commit edits

@@ -106,6 +106,7 @@ def pop(*args):
     c1.insert(c, *args)
     c = c1
 
+SINGLE_COLUMN = False
 
 
 #############################################################################
@@ -173,8 +174,12 @@ c.text(x+0.5*w, y+0.9*h, "$\widehat{a}$", southwest)
 x += 1.8*r
 mathtext(x, y+0.5*h, r"$\Bigr)$", east)
 
-x -= 0*r
-y -= 3*r
+if SINGLE_COLUMN:
+    x -= 0*r
+    y -= 3*r
+else:
+    x += 3*r
+
 
 #c.text(x, y+0.5*h, r"$\to\H\Bigl($", east)
 #c.text(x, y+0.5*h, r"$\xrightarrow{\cong}\H\Bigl($", east)

### 2016-01-19 fib2.tex
try single column
commit edits
more changes

--- 2015-11-17 fib2.tex
@@
 
-\appendix
-
-\section*{Supplementary Material}
-
-The goal here is to describe the algorithm for
-computing charge contained regions built from 
-arbitrary collection of tiles.
-To do this we first describe our approach
-to topological quantum field theory,
-then we discuss the data structure 
-(combinatorial curve diagrams) and the algorithm
-that operates on these structures.
-
-%We give an informal introduction to
-%anyonic topological quantum
-%field theory in $(2+1)$-dimensions.
-%See \cite{beverland2014} for a similar treatment.
-%Note that these theories give rise to
-%\emph{doubled} anyonic charges, and so
-%the Fibonacci example in the main text simulates
-%one half of such a system. % MEH!
-
-%
-% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-%
-
-\section{Modular Functors}
-
-As in algebraic topology, we wish to extract
-algebraic information about topological objects.
-This can be viewed as a kind of representation theory
-of topological objects: homeomorphisms of surfaces.
-
-We list the axioms for a 
-\emph{2-dimensional unitary topological modular functor}.
- % abbreviated as \emph{MF}.
-There are quite alot of details that we leave out,
-%For the details of this construction, see
-see
-\cite{Turaev1994}, \cite{Walker1991} or \cite{Bakalov2000}.
-For a more pedestrian treatment, see \cite{Freedman2002simulation} or \cite{Beverland2014}.
-
-\newcommand{\F}{\mathscr{H}} % H or F ?
-\newcommand{\C}{\mathbb{C}}
-\newcommand{\A}{\mathcal{A}}
-
-For our purposes a \emph{surface} will be an
-oriented $2$-dimensional manifold with boundary.
-We will not require surfaces to be connected.
-%Each boundary component is oriented (either explicitly or
-%otherwise by using the orientation of the manifold)
-Each boundary component will inherit the manifold orientation,
-contain a distinguished \emph{base point},
-and be labelled with
-%an element from a finite set $\mathbb{A}=\{1, a, b, c ...\}.$
-an element from a finite set $\A.$
-This is the set of ``anyon labels'', and comes
-equiped with a vacuum element $\vac$ 
-and an involution $\ \widehat{}\ $ such that $\widehat{\vac}=\vac.$
-
-We will mostly be concerned with \emph{planar} such
-surfaces, ie. disc(s) with zero or more holes.
-
-A modular functor $\F$ associates to every
-surface $M$ a finite dimensional complex
-vector space $\F(M)$, called the \emph{fusion space} of $M$.
-A map of surfaces $f:M\to N$ will be understood to be
-a topological homeomorphism that preserves boundary
-labels, orientation, and base points.
-The modular functor associates such an $f$ to a
-unitary transformation $\F(f) : \F(M)\to\F(N)$
-that only depends on the isotopy class of $f.$
-Functoriality requires that $\F$
-respect composition of homeomorphisms.
-
-We have the following axioms for $\F.$
-
-{\bf Axiom I.}
-The fusion space of an empty surface is one dimensional, 
-$\F(\phi) \cong \C.$
-For $M_a$ a disc with boundary label $a$ we have
-$\F(M_\vac)\cong \C$ and 
-$\F(M_a)\cong 0$ for $a\ne \vac.$
-For annulus $M_{a,b}$ with boundary labels
-$a, b$ we have
-$\F(M_{a,\widehat{a}})\cong \C$ and 
-$\F(M_{a,b})\cong 0$ for $a\ne \widehat{b}.$
-
-{\bf Axiom II.}
-The disjoint union of two surfaces $M$ and $N$ 
-is associated with
-the tensor product of fusion spaces:
-$$
-    \F(M\amalg N) \cong \F(M)\otimes \F(N).
-$$
-This is natural from the point of view of quantum
-physics, where the Hilbert space of two disjoint
-systems is the tensor product of the space for
-each system.
-
-{\bf Axiom III.}
-%Gluing.
-Denote a surface $M$ with (at least) two boundary
-components labelled $a, b$ as $M_{a,b}$. 
-Let $N$ be the surface obtained from $M$ by gluing
-these two boundary components together.
-Glueing must respect the orientation of the two boundary
-components as well as identifying their base points.
-If we constrain $b=\widehat{a}$ then the fusion space
-of $M_{a,\widehat{a}}$ embedds unitarily in the fusion
-space of $N.$ Moreover, there is an isomorphism called
-a \emph{gluing map}:
-$$
-    \bigoplus_{a\in\A} \F(M_{a,\widehat{a}}) \xrightarrow{\cong} \F(N).
-$$
-The seam along which gluing occurs can be associated
-with an observable as follows.
-We take a gluing map $g$. Projectors $P_a$ onto the
-summands in the above direct sum:
-$$
-    P_a: \bigoplus_{b\in\A} \F(M_{b,\widehat{b}}) \to \F(M_{a,\widehat{a}}).
-$$
-then the observable will be the set of operators $\{P_a g^{-1}\}_{a\in\A}.$
-
-A common operation is to glue two separate surfaces.
-We can do this by first taking disjoint union (tensoring
-the fusion spaces)
-and then gluing.
-Here we show this process applied to two surfaces $M$ and $N$. 
-\begin{center}
-\includegraphics[]{pic-glue.pdf}
-\end{center}
-We display the surface $N$ with the $\widehat{a}$
-boundary on the outside, 
-to show more clearly how $N$ fits into $M$.
-In the glued manifold we
-indicate the placement of $M$ and $N$ and the seam
-along which glueing occured,
-as well as the identification of base points.
-
-%\emph{XXX show orientation of boundaries ?}
-%\emph{XXX displaymath direct sum}
-%\emph{XXX $N...$ show ellipses?}
-
-A most important linear map, called an $F-$move,
-is constructed from two applications of a
-gluing map as follows.
-
-\begin{widetext}
-\begin{center}
-\includegraphics[]{pic-glue-fmove.pdf}
-\end{center}
-\end{widetext}
-
-Here we have shown a manifold $M_{abc}$ with 
-three labelled boundaries, as well as two separate
-ways of gluing pairs-of-pants to get $M.$
-
-As we have seen, an oriented simple closed path 
- contained in the interior of $M$ can serve as
-the seam along which gluing occurs and so we call
-these paths \emph{observables}.
-%Any oriented simple closed path contained in the interior of $M$ we will
-%call an \emph{observable}.
-Such a path that encloses two boundary components 
-we call a \emph{2-observable}.
-\emph{(what does enclose mean exactly?)}
-A function $c:[0,1]\to M$ such that $c(0)\in \partial M$ and $c(1)\in \partial M$
-are two separate components of the boundary we call a \emph{2-curve.}
-The following important fact will be used extensively
-in the combinatorial formulation of a modular functor below:
-up to isotopy (not preserving $\partial M$),
-there is a (natural) bijection between
-$2$-observables and $2$-curves.
-\emph{(restrict to $M$ a disc with at least two holes?)}
-Here we show two such instances of this
-bijection:
-\begin{center}
-\includegraphics[]{pic-2-curve.pdf}
-\end{center}
-The bijections works as follows.
-To construct a $2$-observable from a $2$-curve $c$ that
-joins two boundary components $M_1$ and $M_2$,
-take a small neighbourhood of
-the union $c([0,1])\cup M_1 \cup M_2.$
-This neighbourhood will have boundary a simple closed
-curve that encloses $M_1$ and $M_2.$
-\emph{(check the orientation of the $2$-observable has the correct interior)}
-\emph{(the $2$-observable forgets the direction of the $2$-curve)}
-Going the other direction...
-
-The end points of $2$-curves are free to terminate anywhere
-on the boundary component, but we can fix the endpoints using
-the base points.
-A simple way to do this is to just require the
-$2$-curve to begin and end on base points.
-
-By a \emph{hole} of $M$ we mean a component of $\partial M$.
-
-A single $F$-move is seen to relate a pair of $2$-curves
-that share a hole.
-Continuing in this way, we can chain these $2$-curves together:
-\begin{center}
-\includegraphics[]{pic-chain.pdf}
-\end{center}
-
-%
-% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-%
-
-%\section{Interaction picture}
-\section{Topological quantum field theory}
-
-In two spacial dimensions, particle exchange is
-captured by the braid group.
-World lines of such particles 
-become tangled (braided) in $(2+1)$-dimensions.
-For example, three particle statistics is captured
-by the braid group on three strands $B_3.$
-This group is generated by elements $\sigma_1$
-and $\sigma_2$ which we represent pictorially as:
-\begin{center}
-\includegraphics[]{pic-braid-group.pdf}
-\end{center}
-
-These pictures make clear how the group
-multiplication works, for example:
-\begin{center}
-\includegraphics[]{pic-braid-group-1.pdf}
-\end{center}
-\begin{center}
-\includegraphics[]{pic-braid-relation.pdf}
-\end{center}
-
-%Braid group acts (naturally) on states.
-
-These diagrams are to be understood up to
-continuous deformation of the ambient space.
-That is, we allow the ambient $(2+1)$-dimensional
-space with these worldlines subtracted to be continuously
-deformed.
-At the top and bottom of this space is 
-a $2$-dimensional space (a disc) with holes in it.
-Such a closed disc with $n$ holes we denote as $D_n.$
-So this is how we arrive at modelling the system as
-a disc with holes in it.
-The observables of the system measure charge within
-a region bounded by a directed closed curve.
-\begin{center}
-\includegraphics[]{pic-observable.pdf}
-\end{center}
-
-The defining feature of an Abelian anyon theory
-is that the state is completely determined once
-we measure the charge of each hole.
-In the language of the toric code (homology),
-logical operators (1-chains)
-cancel where they overlap
-with opposite orientation:
-\begin{center}
-\includegraphics[width=0.7\columnwidth]{pic-abelian.pdf}
-\end{center}
-
-This is not at all the case in general;
-for non-Abelian theories there can be extra
-degrees of freedom associated with these
-observables. For example, in
-a system supporting Fibonacci anyons,
-we can have two Fibonacci anyons with total
-charge either vacuum or Fibonacci:
-\begin{center}
-\includegraphics[]{pic-fusion.pdf}
-\end{center}
-so the state space of two fibonacci anyons
-is $2$-dimensional.
-Such a space associated with observing total charge
-of multiple anyons is called the \emph{fusion} space
-of those charges.
-
-These observables satisfy various relations,
-but in particular, non-overlapping observables commute.
-So if we nest a maximal set of these observables together
-we can pin-down a basis for the fusion space.
-Such a nesting is tree-like, and if we confuse the distinction
-between holes and observables, this gives rise to the
-fusion tree notation.
-\begin{center}
-\includegraphics[]{pic-tree-0.pdf}\includegraphics[]{pic-tree-1.pdf}
-\end{center}
-
-Given a disc with $n$ holes, we define the \emph{mapping
-class group} $MCG(D_n)$ as the group of topological
-symmetries (homeomorphisms) of the space $D_n,$
-modulo continuous deformations (isotopy).
-Such symmetries we require to fix the boundary
-of the disc, but not necessarily to fix the holes.
-Elements $f\in MCG(D_n)$ will also act on anything that
-resides in $D_n.$ 
-In particular, if we draw a line
-connecting the holes:
-\begin{center}
-\includegraphics[]{pic-twist.pdf}
-\end{center}
-
-Such an embedding $c : [0, 1] \to D$ with $c(0), c(1) \in \partial D$
-and touching all holes in $D_n$ we call a \emph{curve diagram}~\cite{Dehornoy2002},
-(or just a \emph{curve} when the context is clear).
-
-We can think of braids acting on states in a Schrodinger picture,
-or alternatively, elements of the mapping class group acting on
-observables in a Heisenberg picture:
-\begin{center}
-\includegraphics[]{pic-interaction.pdf}
-\end{center}
-
-We would hope that the groups $B_n$ and $MCG(D_n)$ are
-isomorphic, and this is indeed the case~\cite{Kassel2010}.
-One can see this as follows. Dragging the space $D_n$ along
-a braid creates a deformation, the end point of which is a
-homeomorphism in $MCG(D_n).$ Going the other direction,
-given $f\in MCG(D_n)$ and a curve diagram $c,$ we think of
-pulling the ends of $f\circ c$, thereby moving (braiding) the holes,
-until we are back at the original curve $c.$
-
-%This discussion makes it clear we have picked out a
-%specific curve $c$ that we use as a reference point for
-%other curves.
-
-The importance of this isomorphism: the simulation
-algorithm calculates outcomes of observations. This
-boils down to a change of basis, to one that includes
-the required observable.
-$F$-moves allow us to re-associate observables along
-a curve diagram. The mapping class group acts
-transitively on curve diagrams (\emph{why??}).
-
-%
-% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-%
-
-\section{Combinatorial curve diagrams}
-
-The basic data structure involved in the
-simulation we term a \emph{combinatorial curve
-diagram.}
-% XXX define "piece of curve"
-Firstly, we will require each curve to intersect 
-the edges of tiles transversally,
-and in particular a curve will not touch a tile corner.
-
-For each tile in the lattice,
-we store a combinatorial
-description of the curve(s) intersected with that tile.
-Each component of such an intersection we call a \emph{piece-of-curve.}
-\begin{center}
-\includegraphics[]{pic-cells.pdf}
-\end{center}
-
-We follow essentially the same approach as taken in \cite{Abramsky2007} 
-to describe elements of a Temperley-Leib algebra, but
-with some extra decorations.
-The key idea is to store a \emph{word} for each tile, comprised of
-the letters $\bigl<$ and $\bigr>$.
-%The encoding works as follows.
-Reading in a clockwise direction around the edge of
-the tile from the top-left corner,
-we record our encounters with each piece-of-curve,
-writing~$\bigl<$ for the first encounter, and~$\bigr>$ for the
-second.
-We may also encounter a dangling piece-of-curve
-(the head or the tail), so we use another symbol $*$ for this.
-The words for the above two tiles will then be 
-$\bigl<\bigl<\bigr>\bigr>\bigl<\bigr>$ and $\bigl<\bigr>*\bigl<\bigl<\bigr>\bigr>.$
-When the brackets are balanced,
-each such word will correspond one-to-one with an intersection
-of a curve in a tile, up to a continuous deformation of the interior of the tile.
-Ie. the data structure 
-will be insensitive to any continuous deformation of the interior of the tile,
-but the simulation does not need to track any of these degrees of freedom.
-
-\begin{center}
-\includegraphics[]{pic-cells-0.pdf}
-\end{center}
-
-We will also need to record
-various other attributes of these curves,
-and to do this we make this notation more elaborate
-in the paragraphs {\bf (I)}, {\bf(II)} and {\bf(III)} below.
-Each symbol in the word describes an intersection of
-the curve with the tile boundary,
-and so as we decorate these symbols these decorations will
-apply to such intersection points.
-
-\begin{center}
-\includegraphics[]{pic-cells-1.pdf}
-\end{center}
-
-{\bf (I)} We will record the direction of each piece-of-curve,
-this will be either an {\tt in} or {\tt out} decoration for each symbol.
-Such decorations need to balance according to the brackets.
-The decorated symbols $*_{\mbox{\tt in}}$ and 
-$*_{\mbox{\tt out}}$ 
-will denote respectively either
-%the head, $c(1)$ or the tail $c(0)$ of a curve.
-the head or the tail of a curve.
-The words for the diagrams above now read as
-$ \bigl<_{\mbox{\tt in}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}
-    \bigr>_{\mbox{\tt out}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}$
-and
-$ \bigl<_{\mbox{\tt in}}\bigl>_{\mbox{\tt out}}*_{\mbox{\tt in}}
-    \bigr<_{\mbox{\tt out}}
-    \bigr<_{\mbox{\tt in}}\bigl>_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}.
-$
-
-{\bf (II)} We will record,
-for each intersection with the tile edge, 
-a numeral indicating which of the four
-sides of the tile the
-intersection occurs on.
-Numbering these clockwise from the top as $1, 2, 3, 4$ we have for the above curves: 
-$\bigl<_1\bigl<_2\bigr>_2\bigr>_3\bigl<_3\bigr>_4$ 
-and $\bigl<_1\bigr>_1*_2\bigl<_3\bigl<_3\bigr>_4\bigr>_4.$
-
-{\bf (III)} Finally, we will also decorate these symbols with anyons.
-This will be an index to a leaf of a (sum of) fusion tree(s).
-This means that anyons only reside on the curve close
-to the tile boundary,
-and so we cannot have more than two anyons
-for each piece-of-curve. 
-The number of such pieces is arbitrary, and so this
-is no restriction on generality.
-
-\begin{center}
-\includegraphics[]{pic-cells-2.pdf}
-\end{center}
-
-In joining tiles together to make a tiling we will
-require adjacent tiles to agree on their shared boundary.
-This will entail sequentially pairing symbols in the
-words for adjacent tiles
-and requiring that 
-the {\tt in} and {\tt out} decorations are matched.
-Because the word for a tile proceeds conter-clockwise
-around the tile, this pairing will always reverse the
-sequential order of the symbols of adjacent tiles.
-For example, given the above two tiles we sequentially pair the 
-$\bigl<_{\mbox{\tt out},2}\bigr>_{\mbox{\tt in},2}$ 
-and $\bigr>_{\mbox{\tt out},4}\bigr>_{\mbox{\tt in},4}$
-symbols with opposite order so that
-$\bigl<_{\mbox{\tt out},2}\sim\bigr>_{\mbox{\tt in},4}$
-and $\bigr>_{\mbox{\tt in},2} \sim \bigr>_{\mbox{\tt out},4}.$
-
-%Two other consistency relations are enforced on such a combinatorial curve diagram:
-%we require adjacent tiles to agree on their boundaries, 
-%and every curve diagram
-%must have two ends.
-%One final consistency
-%relation is enforced by requiring 
-%We require every curve diagram to have two ends, this means
-%that there are no loops.
-
-Note that in general this data structure will store many disjoint curve diagrams
-$c_i:[0,1]\to D_{n_i}$ within a disc $D_m$ where $\sum n_i = m.$
-
-%For a given piece-of-curve, we can subtract the numeral with
-%the {\tt in} label from the numeral with the {\tt out} label
-%to get an integer in $\{ \}$ WRONG
-%We can also just use the numerals of the boundary edges
-%that the piece-of-curve intersects with, subtracting the
-%``exit'' boundary numeral from the ``entry'' boundary numeral. WRONG
-
-For each piece-of-curve, apart from a head or tail, there is an associated 
-number we call the \emph{turn number}. This counts the number
-of ``right-hand turns'' the piece-of-curve makes as it
-traverses the tile, with a ``left-hand turn'' counting as $-1.$
-(To be more rigorous, we would define this number using the
-winding number of the simple closed curve formed by the
-piece-of-curve adjoined to a segment of the boundary of the tile 
-traversed in a clockwise direction.)
-This number will take one of the values $-2, -1, 0, 1, 2:$
-\begin{center}
-\includegraphics[]{pic-cells-3.pdf}
-\end{center}
-
-%Two disjoint curves can be joined by...
-%
-%Curves can be simplified along sections without any anyons, ...
-
-% Each piece will have +1, +2, 0, -1, -2 right-hand turns...
-
-% mention Jones' planar algebras ?
-
-%
-% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-%
-
-\section{The paperclip algorithm}
-
-Anyons are transported around the lattice
-by moving them along tile edges.
-In general, such a transport will intersect with a
-curve diagram in many places.
-Each such intersection is transverse,
-and we use each intersection point to cut
-the entire transport into smaller paths each of
-which touch the curve diagram twice.
-%Each intersection with a curve diagram
-%will then be transverse, and we
-%decompose the entire path into a sequence of
-%paths each of which 
-%join consecutive intersections.
-%Transport of an anyon can be decomposed into
-%moves between adjacent components of a curve
-%diagram.
-The origin and destination of such an anyon path
-now splits the curve diagram $c:[0, 1]\to D_n$ 
-into three disjoint pieces which we term
-\emph{head}, \emph{body} and \emph{tail}, where
-the head contains the point $c(1)$, the tail
-contains $c(0)$ and the body is the third piece.
-These arise with various arrangements, but here
-we focus on one instructive case, the
-other cases are similar:
-%We look at the particular case of moving along
-%one edge of a tile,
-transporting along one edge of a tile \emph{forwards} 
-(from tail to head) along a curve diagram:
-\begin{center}
-\includegraphics[]{pic-move-anyon.pdf}
-\end{center}
-
-This arrangement is equivalent (homotopic) to one of four 
-``paperclips'', which we distinguish between by counting how
-many \emph{right-hand turns} are made along the body of the curve diagram.
-We also show an equivalent (homotopic) picture where the
-curve diagram has been straightened, and the resulting distortion
-in the anyon path:
-\begin{center}
-\includegraphics[]{pic-paperclip.pdf}
-\end{center}
-The sequence of anyons along the head, body and tail, we denote as $H, B$ and $T,$
-respectively.
-These sequences have the same order as the underlying curve diagram, and 
-we use
-$H^r, B^r$ and $T^r$ to denote the same anyons with the reversed order.
-Using the above diagram, we can now read off the $R$-moves for each
-of the four paperclips:
-\begin{align*}
--2:&\ R[B] \\
--4:&\ R[H^r]\ R[H]\ R[B] \\
-+4:&\ R[B]\ R[T]\ R[T^r] \\
-+6:&\ R[H^r]\ R[H]\ R[B]\ R[T]\ R[T^r] \\
-\end{align*}
-where notation such as $R[B]$ is understood as sequentially clockwise braiding around
-each anyon in $B$.
-
-That these four paperclips exhaust all possibilities can be seen by
-considering the winding number of the simple closed curve made
-by combining the body of the curve diagram with the path followed by
-the anyon (appropriately reversing direction as needed).
-
-\section{Computation of homologically non-trivial operators}\label{s:homnontrivial}
-
-Specializing to the Fibonacci case,
-we write the non-trivial $F$-moves as the following
-skein relations:
-\begin{align*}
-\includegraphics[]{pic-skein1.pdf}
-\end{align*}
-
-The sollid lines represent Fibonacci world-lines.
-The dotted lines represent vacuum charges,
-and we are free to include these lines or not.
-We leave these anyon paths
-as undirected because Fibonacci anyons are
-self-inverse.
-The non-trivial $R$-moves are:
-\begin{align*}
-\includegraphics[]{pic-skein2.pdf}
-\end{align*}
-
-Removing bubbles:
-\begin{align*}
-\includegraphics[]{pic-bubble.pdf}
-\end{align*}
-
-Here we show a process where a 
-Fibonacci anyon travels around the torus and
-anihilates itself. Twice.
-The vertical lines represent a periodic
-identification.
-\begin{align*}
-\includegraphics[]{pic-logops.pdf}
-\end{align*}
-
-The state is not normalized.
-Also involves post-selection, as there is
-another process that involves leakage...
-The first equation is an $F$-move, 
-the second equation is a translation in the
-horizontal direction, and the last equation
-follows from the rule for collapsing bubbles.
-
-Continuing in this way, we compute the $k$-fold
-logical operator:
-\begin{align*}
-\includegraphics[]{pic-kfold.pdf}
-\end{align*}
-
-where $f_k$ is the $k$-th element of the Fibonacci
-sequence $\{1, 1, 2, 3...\}.$
-
-%------------------------------------------------------------------------------------------------------------%
 \bibliography{refs2}

### 2016-01-19 modular.py

@@ -109,6 +109,53 @@ def pop(*args):
 SINGLE_COLUMN = False
 
 
+
+
+class Turtle(object):
+    def __init__(self, x, y, theta):
+        self.x = x
+        self.y = y
+        self.theta = theta
+        self.ps = [(x, y)]
+
+    def fwd(self, d):
+        self.x += d*sin(self.theta)
+        self.y += d*cos(self.theta)
+        self.ps.append((self.x, self.y))
+        return self
+
+    def reverse(self, d):
+        self.fwd(-d)
+        return self
+
+    def right(self, dtheta, r=0.):
+        theta = self.theta
+        self.theta += dtheta
+        if r==0.:
+            return
+        N = 20
+        x, y = self.x, self.y
+        x0 = x - r*sin(theta-pi/2)
+        y0 = y - r*cos(theta-pi/2)
+        for i in range(N):
+            theta += (1./(N))*dtheta
+            x = x0 - r*sin(theta+pi/2)
+            y = y0 - r*cos(theta+pi/2)
+            self.ps.append((x, y))
+        self.x = x
+        self.y = y
+        return self
+
+    def left(self, dtheta, r=0.):
+        self.right(-dtheta, -r)
+        return self
+
+    def stroke(self, extra=[], fill=[], closepath=False):
+        dopath(self.ps, extra, fill, closepath, smooth=0.)
+        return self
+
+
+
 #############################################################################
 #
 #
@@ -301,53 +348,6 @@ c.writePDFfile("pic-glue-fmove.pdf")
 #
 #
 
-
-
-class Turtle(object):
-    def __init__(self, x, y, theta):
-        self.x = x
-        self.y = y
-        self.theta = theta
-        self.ps = [(x, y)]
-
-    def fwd(self, d):
-        self.x += d*sin(self.theta)
-        self.y += d*cos(self.theta)
-        self.ps.append((self.x, self.y))
-        return self
-
-    def reverse(self, d):
-        self.fwd(-d)
-        return self
-
-    def right(self, dtheta, r=0.):
-        theta = self.theta
[…]

### 2016-01-23 pants.py
start to draw the pants

@@ -1,0 +1,263 @@
+#!/usr/bin/env python
+
+import sys
+from math import *
+from random import *
+import numpy
+import scipy
+
+from pyx import canvas, path, deco, trafo, style, text, color, deformer
+
+text.set(mode="latex") 
+text.set(docopt="12pt")
+text.preamble(r"\usepackage{amsmath,amsfonts,amssymb}")
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, rgb(0.75, 0.75, 0)) 
+
+black = rgb(0., 0., 0.) 
+blue = rgb(0., 0., 0.8)
+lred = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.) 
+
+shade = rgb(0.75, 0.55, 0)
+grey = rgb(0.75, 0.75, 0.75)
+
+light_shade = rgb(0.85, 0.65, 0.1)
+light_shade = rgb(0.9, 0.75, 0.4)
+
+
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
+
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+st_tau = [style.linewidth.Thick, red, style.linecap.round]
+st_vac = [style.linewidth.thick, red]+st_dotted
+
+
+
+###############################################################################
+#
+#
+
+from scipy.sparse import lil_matrix
+from scipy.sparse.linalg import spsolve
+from numpy.linalg import solve, norm
[…]

### 2016-01-23 pants.py
commit edits

@@ -25,7 +25,9 @@ blue = rgb(0., 0., 0.8)
 lred = rgb(1., 0.4, 0.4)
 white = rgb(1., 1., 1.) 
 
-shade = rgb(0.75, 0.55, 0)
+shade0 = rgb(0.75, 0.55, 0)
+shade1 = rgb(0.70, 0.55, 0)
+shade2 = rgb(0.65, 0.50, 0)
 grey = rgb(0.75, 0.75, 0.75)
 
 light_shade = rgb(0.85, 0.65, 0.1)
@@ -45,6 +47,9 @@ center = [text.halign.boxcenter, text.valign.middle]
 
 st_dashed = [style.linestyle.dashed]
 st_dotted = [style.linestyle.dotted]
+
+st_thick = [style.linewidth.thick]
+st_Thick = [style.linewidth.Thick]
 
 st_tau = [style.linewidth.Thick, red, style.linecap.round]
 st_vac = [style.linewidth.thick, red]+st_dotted
@@ -184,7 +189,7 @@ def getgrad(x, y):
 
 def normalize(dv):
     x, y = dv
-    r = (x**2+y**2)**0.5
+    r = (x**2.0+y**2.0)**0.5
     return x/r, y/r
 
 def rotate(dv):
@@ -197,27 +202,49 @@ def getlevel(x, y):
     dv = rotate(dv)
     return dv
 
+def dot(d0, d1):
+    return d0[0]*d1[0] + d0[1]*d1[1]
 
-#print getv(5.5, 5.5), getv(5.6, 5.5)
-#print getv(5.5, 5.6), getv(5.6, 5.6)
-#print getgrad(5.5, 5.5)
 
-c = canvas.canvas()
-dx = 0.1
-dy = 0.1
+#def getline(x0, y0, x1, y1):
+def getline(*args):
 
-for i in range(H):
-  for j in range(W):
-    r = v[i, j]
-    cl = rgb(r, r, r)
-    #cl = color.gradient.RedBlue
-    c.fill(path.rect(j*dx, i*dy, 1.2*dx, 1.2*dy), [cl])
+    args1 = []
+    for arg in args:
+        if isinstance(arg, (list, tuple)):
+            args1 += list(arg)
+        else:
+            args1.append(arg)
+    assert len(args1)==4, repr( args1)
+    x0, y0, x1, y1 = args1
 
-def plotlevelset(x, y, length=100):
[…]

### 2016-01-23 pants.py
commit edits

@@ -25,10 +25,12 @@ blue = rgb(0., 0., 0.8)
 lred = rgb(1., 0.4, 0.4)
 white = rgb(1., 1., 1.) 
 
-shade0 = rgb(0.75, 0.55, 0)
-shade1 = rgb(0.70, 0.55, 0)
-shade2 = rgb(0.65, 0.50, 0)
+shade = rgb(0.75, 0.55, 0)
+
 grey = rgb(0.75, 0.75, 0.75)
+shade0 = rgb(0.75, 0.75, 0.75)
+shade1 = rgb(0.80, 0.80, 0.80)
+shade2 = rgb(0.85, 0.85, 0.85)
 
 light_shade = rgb(0.85, 0.65, 0.1)
 light_shade = rgb(0.9, 0.75, 0.4)

### 2016-01-24 hexagon.py
commit edits

@@ -1,0 +1,252 @@
+#!/usr/bin/env python
+
+import sys
+from math import *
+from random import *
+import numpy
+import scipy
+
+from pyx import canvas, path, deco, trafo, style, text, color, deformer
+
+text.set(mode="latex") 
+text.set(docopt="12pt")
+text.preamble(r"\usepackage{amsmath,amsfonts,amssymb}")
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, rgb(0.75, 0.75, 0)) 
+
+black = rgb(0., 0., 0.) 
+blue = rgb(0., 0., 0.8)
+lred = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.) 
+
+#shade = rgb(0.75, 0.55, 0)
+
+grey = rgb(0.75, 0.75, 0.75)
+shade = grey
+shade0 = rgb(0.75, 0.75, 0.75)
+shade1 = rgb(0.80, 0.80, 0.80)
+shade2 = rgb(0.85, 0.85, 0.85)
+
+light_shade = rgb(0.85, 0.65, 0.1)
+light_shade = rgb(0.9, 0.75, 0.4)
+
+
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
+
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+st_thick = [style.linewidth.thick]
+st_Thick = [style.linewidth.Thick]
+
+st_tau = [style.linewidth.Thick, red, style.linecap.round]
+st_vac = [style.linewidth.thick, red]+st_dotted
+
+
+def dopath(ps, extra=[], fill=[], closepath=True, smooth=0.3):
[…]

### 2016-01-24 pants.py

@@ -291,40 +291,43 @@ def getlevelset(x, y, length=None):
 #   pick a coordinate system:
 #
 
-c = canvas.canvas()
-dx = 0.1
-dy = 0.1
+dx = 0.08
+dy = 0.08
 
-def transform(x, y, z):
-    x1 = x + 0.3*y
-    y1 = 0.5*y + 4*H*z
 
-    return x1*dx, y1*dy
+#def transform(x, y, z):
+#    x1 = 1.0*x + 0.3*y + 0.0*z
+#    y1 = 0.0*x + 0.5*y + 4*H*z
+#    return x1*dx, y1*dy
 
 #def transform(x, y, z):
 #    return x*dx, y*dy
 
+def transform(x, y, z):
+    x1 = A[0][0]*x + A[0][1]*y + A[0][2]*z
+    y1 = A[1][0]*x + A[1][1]*y + A[1][2]*z
+    return x1*dx, y1*dy
 
-for y in range(H-2,0,-1):
-  for x in range(W-1):
-    z00 = v[y, x]
-    z01 = v[y+1, x]
-    z10 = v[y, x+1]
-    z11 = v[y+1, x+1]
-    if max(z00,z01,z10,z11)>0.5:
-        continue
-    r = 2*z00
-    cl = rgb(r,r,r)
-    #c.fill(path.rect(x*dx, y*dy, 1.2*dx, 1.2*dy), [cl])
 
-    ps = [
-        path.moveto(*transform(x, y, z00)),
-        path.lineto(*transform(x+1.2, y, z10)),
-        path.lineto(*transform(x+1.2, y+1.2, z11)),
-        path.lineto(*transform(x, y+1.2, z01)),
-        path.closepath()]
-
-    #c.fill(path.path(*ps), [cl])
+def plot_scalar_field():
+    for y in range(H-2,0,-1): # paint back to front
+      for x in range(W-1):
+        z00 = v[y, x]
+        z01 = v[y+1, x]
+        z10 = v[y, x+1]
+        z11 = v[y+1, x+1]
+        if max(z00,z01,z10,z11)>0.5:
+            continue
+        r = 2*z00
+        cl = rgb(r,r,r)
+        ps = [
+            path.moveto(*transform(x, y, z00)),
+            path.lineto(*transform(x+1.2, y, z10)),
+            path.lineto(*transform(x+1.2, y+1.2, z11)),
+            path.lineto(*transform(x, y+1.2, z01)),
+            path.closepath()]
+    
[…]

### 2016-01-27 hexagon.py
commit edits

@@ -114,13 +114,16 @@ class Turtle(object):
 
 
 
-g_curve = [green, style.linewidth.THick]
-g_curve = g_curve + [deco.earrow(size=0.2)]
+st_curve = [green, style.linewidth.THick]
+st_curve = st_curve + [deco.earrow(size=0.2)]
 
-def circle(x, y, r, shade, deco=[]):
+
+def circle(x, y, r, shade, deco=[], mark=False):
     p = path.circle(x, y, r)
     c.fill(p, [shade])
     c.stroke(p, deco)
+    if mark:
+        c.fill(path.circle(x, y-r, 0.05))
 
 
 w, h = 1.5, 1.5
@@ -138,9 +141,9 @@ c = canvas.canvas()
 x, y = 0., 0.
 
 r = 0.7*w
-r0 = 0.06*w
+r0 = 0.07*w
 
-circle(x, y, r, shade)
+circle(x, y, r, shade, mark=True)
 
 r1 = 0.29*w
 theta = 1.8*pi
@@ -152,14 +155,14 @@ Turtle(x-1.2*r, y, 1*pi/2).\
     fwd(0.1*r).left(0.2*theta, r1).right(+0.4*theta, r1).left(0.2*theta, r1).\
     fwd(0.1*r).right(theta1, r2).right(theta2, r3).left(theta2, r3).left(theta1, r2).fwd(0.1*r).\
     right(0.2*theta, r1).left(0.4*theta, r1).right(0.2*theta, r1).fwd(0.2*r).\
-    stroke(g_curve)
+    stroke(st_curve)
 
-circle(x-0.5*r, y, r0, white)
-circle(x+0.5*r, y, r0, white)
+circle(x-0.5*r, y, r0, white, mark=True)
+circle(x+0.5*r, y, r0, white, mark=True)
 
-c.text(x-0.5*r, y-0.1*h, r"$b$", northeast)
-c.text(x+0.5*r, y+0.1*h, r"$a$", southwest)
-c.text(x+r, y-r, r"$c$", southeast)
+c.text(x+0.5*r, y+0.14*h, r"$a$", southwest)
+c.text(x-0.5*r, y-0.14*h, r"$b$", northeast)
+c.text(x+r, y-r, r"$\widehat{c}$", southeast)
 
 x += 1.5*w
 
@@ -169,16 +172,16 @@ c.text(x, y+0.3*h, r"$R_c^{ab}$", center)
 
[…]

### 2016-01-27 modular.py

@@ -33,6 +33,7 @@ text.preamble(r'\usepackage{mathrsfs}')
 #text.preamble(r"\def\I{\mathbb{I}}")
 text.preamble(r"\def\ket #1{|#1\rangle}")
 text.preamble(r"\def\H{\mathscr{H}}")
+text.preamble(r"\def\A{\mathcal{A}}")
 
 
 rgb = color.rgb
@@ -184,19 +185,21 @@ x += 0.0*w
 p = path.circle(x+r, y+0.5*h, r)
 c.fill(p, [shade])
 c.stroke(p)
-c.fill(path.circle(x+2*r, y+0.5*h, 0.06))
+#c.fill(path.circle(x+2*r, y+0.5*h, 0.06))
+c.fill(path.circle(x+r, y+0.5*h-r, 0.06))
 
 x += 0.3*w
 p = path.circle(x+0.1*w, y+0.5*h, 0.4*r)
 c.fill(p, [white])
 c.stroke(p)
-p = path.circle(x+0.1*w+0.4*r, y+0.5*h, 0.06)
+#p = path.circle(x+0.1*w+0.4*r, y+0.5*h, 0.06)
+p = path.circle(x+0.1*w, y+0.5*h-0.4*r, 0.06)
 c.fill(p)
 
 c.text(x+0.6*w, y+0.5*h, "...")
 
 #c.text(x+0.1*w, y+0.0*h, "$M_a$", west)
-c.text(x+0.2*w, y+0.0*h, "$M$", west)
+c.text(x+0.3*w, y+0.1*h, "$M$", west)
 
 c.text(x+0.3*w, y+0.7*h, "$a$", southwest)
 
@@ -206,7 +209,8 @@ r = 0.7
 p = path.circle(x+r, y+0.5*h, r)
 c.fill(p, [shade])
 c.stroke(p)
-p = path.circle(x+2*r, y+0.5*h, 0.06)
+#p = path.circle(x+2*r, y+0.5*h, 0.06)
+p = path.circle(x+r, y+0.5*h-r, 0.06)
 c.fill(p)
 
 x += 0.3*w
@@ -214,7 +218,7 @@ x += 0.3*w
 c.text(x+0.0*w, y+0.5*h, "...")
 
 #c.text(x+0.0*w, y+0.2*h, "$N_{\hat{a}}$", west)
-c.text(x+0.0*w, y+0.2*h, "$N$", west)
+c.text(x+0.1*w, y+0.3*h, "$N$", west)
 
[…]

### 2016-01-28 skein.py
commit edits

@@ -1,0 +1,244 @@
+#!/usr/bin/env python
+
+import sys
+from math import *
+from random import *
+import numpy
+import scipy
+
+from pyx import canvas, path, deco, trafo, style, text, color, deformer
+
+text.set(mode="latex") 
+text.set(docopt="12pt")
+text.preamble(r"\usepackage{amsmath,amsfonts,amssymb}")
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, rgb(0.75, 0.75, 0)) 
+
+black = rgb(0., 0., 0.) 
+blue = rgb(0., 0., 0.8)
+lred = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.) 
+
+#shade = rgb(0.75, 0.55, 0)
+
+grey = rgb(0.75, 0.75, 0.75)
+shade = grey
+shade0 = rgb(0.75, 0.75, 0.75)
+shade1 = rgb(0.80, 0.80, 0.80)
+shade2 = rgb(0.85, 0.85, 0.85)
+
+light_shade = rgb(0.85, 0.65, 0.1)
+light_shade = rgb(0.9, 0.75, 0.4)
+
+
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
+
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+st_thick = [style.linewidth.thick]
+st_Thick = [style.linewidth.Thick]
+st_round = [style.linecap.round]
+
+st_tau = [style.linewidth.Thick, red, style.linecap.round]
+st_vac = [style.linewidth.thick, red]+st_dotted
+
+
[…]

### 2016-01-31 skein.py
commit edits

@@ -59,59 +59,16 @@ st_tau = [style.linewidth.Thick, red, style.linecap.round]
 st_vac = [style.linewidth.thick, red]+st_dotted
 
 
-def dopath(ps, extra=[], fill=[], closepath=False, smooth=0.3):
+def dopath(ps, extra=[], fill=[], closepath=False, smooth=0.3, stroke=True):
     ps = [path.moveto(*ps[0])]+[path.lineto(*p) for p in ps[1:]]
     if closepath:
         ps.append(path.closepath())
     p = path.path(*ps)
     if fill:
         c.fill(p, [deformer.smoothed(smooth)]+extra+fill)
-    c.stroke(p, [deformer.smoothed(smooth)]+extra)
+    if stroke:
+        c.stroke(p, [deformer.smoothed(smooth)]+extra)
 
-
-
-class Turtle(object):
-    def __init__(self, x, y, theta):
-        self.x = x
-        self.y = y
-        self.theta = theta
-        self.ps = [(x, y)]
-
-    def fwd(self, d):
-        self.x += d*sin(self.theta)
-        self.y += d*cos(self.theta)
-        self.ps.append((self.x, self.y))
-        return self
-
-    def reverse(self, d):
-        self.fwd(-d)
-        return self
-
-    def right(self, dtheta, r=0.):
-        theta = self.theta
-        self.theta += dtheta
-        if r==0.:
-            return
-        N = 20
-        x, y = self.x, self.y
-        x0 = x - r*sin(theta-pi/2)
-        y0 = y - r*cos(theta-pi/2)
-        for i in range(N):
-            theta += (1./(N))*dtheta
-            x = x0 - r*sin(theta+pi/2)
-            y = y0 - r*cos(theta+pi/2)
-            self.ps.append((x, y))
-        self.x = x
-        self.y = y
-        return self
-
-    def left(self, dtheta, r=0.):
[…]

### 2016-02-01 hexagon.py
commit edits

@@ -290,4 +290,45 @@ for i in range(6):
 c.writePDFfile("pic-hexagon.pdf")
 
 
+###############################################################################
+#
+#
+
+c = canvas.canvas()
+
+x, y = 0., 0.
+
+w, h = 1.5, 1.5
+
+r0 = 0.8*w
+r1 = 0.4*r0
+r2 = 0.1*r0
+
+
+circle(x, y, 1.2*r0, shade)
+
+circle(x+r1, y+r1, r2, white)
+circle(x-r1, y+r1, r2, white)
+circle(x-r1, y-r1, r2, white)
+circle(x+r1, y-r1, r2, white)
+
+
+r3 = 2*r2
+Turtle(x-r1, y+r1+r3, pi/2).fwd(2*r1).right(pi, r3).fwd(2*r1).right(pi, r3).stroke()
+
+r3 = 2.8*r2
+Turtle(x-r1, y+r1+r3, pi/2).fwd(2*r1).right(3*pi/4, r3).\
+    fwd(1.42*2*r1).right(3*pi/4, r3).fwd(2*r1).right(pi/2, r3).stroke(closepath=True)
+
+
+r3 = 3.4*r2
+Turtle(x+r1+r3, y+r1, pi).fwd(2*r1).right(pi, r3)\
+    .fwd(2*r1).right(pi, r3).stroke(st_dashed)
+
+
+c.text(x+1.9*r1, y, "$\gamma$", west)
+
+c.writePDFfile("pic-refactor.pdf")
+
+
 

### 2016-02-08 modular.py
more changes

@@ -27,7 +27,7 @@ st_dotted = [style.linestyle.dotted]
 
 
 text.set(mode="latex")
-text.set(docopt="12pt")
+text.set(docopt="10pt")
 text.preamble(r'\usepackage{amsmath,amsfonts,amssymb}')
 text.preamble(r'\usepackage{mathrsfs}')
 #text.preamble(r"\def\I{\mathbb{I}}")
@@ -284,11 +284,15 @@ y = 0
 c = canvas.canvas()
 
 
-def surface(x, y, r, fill=shade, mark=False):
+def surface(x, y, r, fill=shade, mark=False, orient=None):
     p = path.circle(x, y, r)
     if fill is not None:
         c.fill(p, [fill])
     c.stroke(p)
+    if orient == True:
+        c.stroke(p, [deco.earrow()])
+    elif orient == False:
+        c.stroke(p, [deco.earrow(), trafo.scale(x=x, y=y, sx=1, sy=-1)])
     if mark:
         p = path.circle(x, y-r, 0.06)
         c.fill(p)
@@ -351,6 +355,35 @@ c.stroke(path.line(+3.4*r, -2.0*r, +1.9*r, -0.8*r), [deco.earrow()])
 c.text(+3.0*r, -1.4*r, "$\cong$", center)
 
 c.writePDFfile("pic-glue-fmove.pdf")
+
+
+#############################################################################
+#
+#
+
+w = 1.5
+h = 1.5
+
+x = 0
+y = 0
+
+c = canvas.canvas()
+
+
+r = 1.4
+
+surface(x+0, y, r, mark=True, orient=True)
+surface(x-0.6*r, y, 0.2*r, fill=white, mark=True, orient=False)
+c.text(x-0.6*r, y+0.3*r, "$a_1$", south)
+#surface(x+0.0*r, y, 0.2*r, fill=white, mark=True, orient=False)
+c.text(x, y, "...", center)
+surface(x+0.6*r, y, 0.2*r, fill=white, mark=True, orient=False)
+c.text(x+0.6*r, y+0.3*r, "$a_n$", south)
+c.text(x+0.9*r, y-0.7*r, "$b$", north)
+
+c.stroke(path.path(path.arc(x+0.2*r, y-0.5*r, 0.15*r, 20, 330)), [deco.earrow()])
+
+c.writePDFfile("pic-disc.pdf")
 
 
 #############################################################################

### 2016-02-08 pants.py

@@ -9,7 +9,7 @@ import scipy
 from pyx import canvas, path, deco, trafo, style, text, color, deformer
 
 text.set(mode="latex") 
-text.set(docopt="12pt")
+text.set(docopt="10pt")
 text.preamble(r"\usepackage{amsmath,amsfonts,amssymb}")
 
 rgb = color.rgb

### 2016-02-08 skein.py

@@ -4,12 +4,11 @@ import sys
 from math import *
 from random import *
 import numpy
-import scipy
 
 from pyx import canvas, path, deco, trafo, style, text, color, deformer
 
 text.set(mode="latex") 
-text.set(docopt="12pt")
+text.set(docopt="10pt")
 text.preamble(r"\usepackage{amsmath,amsfonts,amssymb}")
 
 rgb = color.rgb

### 2016-02-08 supplement.py

@@ -8,7 +8,7 @@ import numpy
 from pyx import canvas, path, deco, trafo, style, text, color, deformer
 
 text.set(mode="latex") 
-text.set(docopt="12pt")
+text.set(docopt="10pt")
 text.preamble(r"\usepackage{amsmath,amsfonts,amssymb}")
 
 rgb = color.rgb

### 2016-02-08 tqft.py

@@ -27,7 +27,7 @@ st_dotted = [style.linestyle.dotted]
 
 
 text.set(mode="latex")
-text.set(docopt="12pt")
+text.set(docopt="10pt")
 text.preamble(r'\usepackage{amsmath,amsfonts,amssymb}')
 #text.preamble(r"\def\I{\mathbb{I}}")
 text.preamble(r"\def\ket #1{|#1\rangle}")

### 2016-02-10 hexagon.py
commit edits

@@ -190,7 +190,7 @@ c.writePDFfile("pic-rmove-1.pdf")
 #
 #
 
-def tetra(x, y, count=None, subcount=None, rev=1, back=True, front=True):
+def tetra(x, y, count=None, subcount=None, rev=1, back=True, front=True, reflect=False):
 
     if back:
         circle(x, y, r, shade)
@@ -229,10 +229,18 @@ def tetra(x, y, count=None, subcount=None, rev=1, back=True, front=True):
 
     if count is not None:
 
+        assert 0<=count<=2
         s = 0.86*r
         r1 = 3*r0
-        Turtle(x1, y1-r1, -pi/2).right(pi, r1).fwd(s).right(pi, r1).fwd(s).\
-            stroke([trafo.rotate(-count*120, x=x, y=y)])
+        extra = []
+        #c.text(x, y, count)
+        if reflect:
+            #count = [0, 1, 2][count]
+            extra.append(trafo.scale(x=x, y=y, sx=-1, sy=1))
+        extra += [trafo.rotate(-count*120, x=x, y=y)]
+        t = Turtle(x1, y1-r1, -pi/2).right(pi, r1).fwd(s).right(pi, r1).fwd(s)
+        t.stroke(extra)
+        t.stroke(extra+[deco.earrow()])
 
 
 c = canvas.canvas()
@@ -242,7 +250,7 @@ R = 1.7*r
 for i in range(3):
     theta = 2*i*pi/3
     x, y = R*sin(theta), R*cos(theta)
-    tetra(x, y, [1, 0, 2][i])
+    tetra(x, y, [1, 0, 2][i], reflect=(i in [0,1]))
 
     w = 30 + 120*i
     c.stroke(path.path(path.arc(0., 0., 1.1*R, w-20, w+20)), [deco.earrow()])
@@ -252,6 +260,26 @@ for i in range(3):
     c.text(x, y, "$F$", center)
 
 c.writePDFfile("pic-fmove-relation.pdf")
+
+
+c = canvas.canvas()
+
+R = 1.7*r
+
+for i in range(3):
+    theta = 2*i*pi/3
+    x, y = R*sin(theta), R*cos(theta)
+    tetra(x, y, [2, 1, 0][i], reflect=(i in [0,2]))
+
+    w = 30 + 120*i
+    c.stroke(path.path(path.arc(0., 0., 1.1*R, w-20, w+20)), [deco.earrow()])
[…]

### 2016-02-10 refactoring.py
commit edits

@@ -1,0 +1,251 @@
+#!/usr/bin/env python
+
+import sys
+from math import *
+from random import *
+import numpy
+
+from pyx import canvas, path, deco, trafo, style, text, color, deformer
+
+text.set(mode="latex") 
+text.set(docopt="10pt")
+text.preamble(r"\usepackage{amsmath,amsfonts,amssymb}")
+text.preamble(r'\usepackage{mathrsfs}')
+#text.preamble(r"\def\I{\mathbb{I}}")
+text.preamble(r"\def\ket #1{|#1\rangle}")
+text.preamble(r"\def\H{\mathscr{H}}")
+text.preamble(r"\def\A{\mathcal{A}}")
+
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, rgb(0.75, 0.75, 0)) 
+
+black = rgb(0., 0., 0.) 
+blue = rgb(0., 0., 0.8)
+lred = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.) 
+
+#shade = rgb(0.75, 0.55, 0)
+
+grey = rgb(0.75, 0.75, 0.75)
+shade = grey
+shade0 = rgb(0.75, 0.75, 0.75)
+shade1 = rgb(0.80, 0.80, 0.80)
+shade2 = rgb(0.85, 0.85, 0.85)
+
+light_shade = rgb(0.85, 0.65, 0.1)
+light_shade = rgb(0.9, 0.75, 0.4)
+
+
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
+
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+st_thick = [style.linewidth.thick]
+st_Thick = [style.linewidth.Thick]
+
+st_tau = [style.linewidth.Thick, red, style.linecap.round]
[…]

### 2016-02-15 refactoring.py
commit edits

@@ -14,6 +14,7 @@ text.preamble(r'\usepackage{mathrsfs}')
 #text.preamble(r"\def\I{\mathbb{I}}")
 text.preamble(r"\def\ket #1{|#1\rangle}")
 text.preamble(r"\def\H{\mathscr{H}}")
+text.preamble(r"\def\F{\mathscr{H}}")
 text.preamble(r"\def\A{\mathcal{A}}")
 
 
@@ -246,6 +247,112 @@ manifold(x + w, y, "abc")
 
 
 c.writePDFfile("pic-refactoring.pdf")
+
+
+
+###############################################################################
+#
+#
+
+w, h = 2.2, 2.4
+
+c = canvas.canvas()
+
+r0 = 0.4*w # second hole
+
+count = 0
+
+def manifold(x, y, labels):
+
+    global count
+
+    p = path.circle(x+r0/2, y, r0)
+    extra = [trafo.scale(x=x+r0/2, y=y, sx=1.0, sy=0.8)]
+    c.fill(p, extra+[shade])
+    c.stroke(p, extra)
+
+    if count in [0, 2]:
+        c.stroke(path.line(x-0.5*r0, y, x+r0+0.5*r0, y), st_curve)
+    else:
+        extra = list(st_curve)
+        if count==3:
+            extra.append(trafo.scale(x=x, y=y, sx=1, sy=-1))
+        Turtle(x-0.85*r0+0.3, y, pi/2).\
+            right(0.25*pi, 0.4).left(0.50*pi, 0.73).left(0.88*pi, 0.15).\
+            fwd(0.55).\
+            right(0.88*pi, 0.15).right(0.50*pi, 0.73).left(0.25*pi, 0.4).\
+            stroke(extra)
+
+    for i in range(2):
+        _x = [x, x+r0][i]
+        p = path.circle(_x, y, 0.08)
+        c.fill(p, [white])
+        c.stroke(p)
+        ydelta = 0.25
+        xdelta = 0.00
+        if count==1  and labels[i]=="a":
+            ydelta = -0.35
+            xdelta = +0.1
+        if count==3  and labels[i]=="a":
+            ydelta = -0.35
[…]

### 2016-02-18 modular.py
commit edits

@@ -390,6 +390,8 @@ c.writePDFfile("pic-disc.pdf")
 #
 #
 
+st_arrow = [deco.earrow()]
+
 w = 1.5
 h = 1.5
 
@@ -418,9 +420,14 @@ t.right(pi, 1.9*dx)
 t.right(pi, 0.4*dx)
 t.left(pi, 1.1*dx)
 t.right(pi, 0.4*dx)
-t.stroke(st_dashed)
+t.stroke()
 
-c.stroke(path.circle(x, y, dx), st_dashed+[trafo.scale(0.9, 0.7)])
+t = Turtle(x1-0.4*dx, y, pi)
+t.fwd(0.01)
+t.stroke(st_arrow)
+
+c.stroke(path.circle(x, y, dx), [trafo.scale(0.9, 0.7)])
+c.stroke(path.circle(x, y, dx), st_arrow+[trafo.scale(0.9, 0.7)])
 
 r = 0.12
 
@@ -464,12 +471,13 @@ t.stroke(g_curve)
 for i in range(3):
     t = Turtle(x1, y, pi/2)
     t.fwd(dx)
-    t.stroke(g_curve+[style.linecap.round])
+    #t.stroke(g_curve+[style.linecap.round])
 
     surface(x1, y, r, white)
     #c.fill(path.circle(x1, y+r, 0.04))
 
-    c.stroke(path.circle(x1+0.5*dx, y, dx), st_dashed+[trafo.scale(0.9, 0.6, x=x1+0.5*dx, y=0)])
+    c.stroke(path.circle(x1+0.5*dx, y, dx), [trafo.scale(0.9, 0.6, x=x1+0.5*dx, y=0)])
+    c.stroke(path.circle(x1+0.5*dx, y, dx), st_arrow+[trafo.scale(0.9, 0.6, x=x1+0.5*dx, y=0)])
     x1 += dx
 
 surface(x1, y, r, white)

### 2016-02-18 modular.py
commit edits

@@ -252,10 +252,10 @@ c.fill(path.circle(x+r, y+0.5*h-r, 0.06))
 
 x += 0.3*w
 p = path.circle(x+0.1*w, y+0.5*h, 0.4*r)
-c.stroke(p, st_dashed)
+c.stroke(p)
 #p = path.circle(x+0.1*w+0.4*r, y+0.5*h, 0.06)
 p = path.circle(x+0.1*w, y+0.5*h-0.4*r, 0.06)
-c.stroke(p, st_dashed)
+c.fill(p)
 
 c.text(x+0.1*w, y+0.5*h, r"$N$", center)
 #c.text(x+0.2*w, y+0.5*h, r"$...$", center)
@@ -309,8 +309,8 @@ c.text(x,       y+0.2, "$b$", south)
 c.text(x+0.6*r, y+0.2, "$c$", south)
 c.text(x+0.9*r, y-0.6, "$\widehat{d}$", northwest)
 
-c.stroke(path.circle(x-0.3*r, y, 0.6*r), st_dashed+[trafo.scale(1., 1.1, x, y)])
-c.stroke(path.circle(x+0.3*r, y, 0.6*r), st_dashed+[trafo.scale(1., 1.1, x, y)])
+c.stroke(path.circle(x-0.3*r, y, 0.6*r), [trafo.scale(1., 1.1, x, y)])
+c.stroke(path.circle(x+0.3*r, y, 0.6*r), [trafo.scale(1., 1.1, x, y)])
 
 c.text(x-1.5*r, y, r"$\H\Bigl($", center)
 c.text(x+1.3*r, y, r"$\Bigr)$", center)
@@ -372,16 +372,23 @@ c = canvas.canvas()
 
 r = 1.4
 
-surface(x+0, y, r, mark=True, orient=True)
-surface(x-0.6*r, y, 0.2*r, fill=white, mark=True, orient=False)
+ccw = False # counter clockwise
+
+surface(x+0, y, r, mark=True, orient=ccw)
+surface(x-0.6*r, y, 0.2*r, fill=white, mark=True, orient=not ccw)
+surface(x+0.6*r, y, 0.2*r, fill=white, mark=True, orient=not ccw)
+
+
 c.text(x-0.6*r, y+0.3*r, "$a_1$", south)
-#surface(x+0.0*r, y, 0.2*r, fill=white, mark=True, orient=False)
 c.text(x, y, "...", center)
[…]

### 2016-02-22 hexagon.py
towards MVP

@@ -85,7 +85,7 @@ class Turtle(object):
         self.fwd(-d)
         return self
 
-    def right(self, dtheta, r=0.):
+    def right(self, dtheta, r=0., penup=False):
         theta = self.theta
         self.theta += dtheta
         if r==0.:
@@ -98,13 +98,16 @@ class Turtle(object):
             theta += (1./(N))*dtheta
             x = x0 - r*sin(theta+pi/2)
             y = y0 - r*cos(theta+pi/2)
-            self.ps.append((x, y))
+            if not penup:
+                self.ps.append((x, y))
         self.x = x
         self.y = y
+        if penup:
+            self.ps = [(x, y)] # HACK
         return self
 
-    def left(self, dtheta, r=0.):
-        self.right(-dtheta, -r)
+    def left(self, dtheta, r=0., penup=False):
+        self.right(-dtheta, -r, penup=penup)
         return self
 
     def stroke(self, extra=[], fill=[], closepath=False):
@@ -150,10 +153,11 @@ theta1 = 1.05*pi
 r2 = 0.09*w
 theta2 = 0.2*pi
 r3 = 0.6*w
-Turtle(x-1.2*r, y, 1*pi/2).\
-    fwd(0.1*r).left(0.2*theta, r1).right(+0.4*theta, r1).left(0.2*theta, r1).\
+Turtle(x-1.1*r, y, 1*pi/2).\
+    left(0.05*theta, r1, penup=True).\
+    left(0.15*theta, r1).right(+0.4*theta, r1).left(0.2*theta, r1).\
     fwd(0.1*r).right(theta1, r2).right(theta2, r3).left(theta2, r3).left(theta1, r2).fwd(0.1*r).\
-    right(0.2*theta, r1).left(0.4*theta, r1).right(0.2*theta, r1).fwd(0.2*r).\
+    right(0.2*theta, r1).left(0.4*theta, r1).right(0.15*theta, r1).\
     stroke(st_curve)
 
 circle(x-0.5*r, y, r0, white, mark=True)
@@ -173,7 +177,7 @@ x += 1.5*w
 
 circle(x, y, r, shade, mark=True)
 
-c.stroke(path.line(x-1.2*r, y, x+1.3*r, y), st_curve)
+c.stroke(path.line(x-1.0*r, y, x+1.0*r, y), st_curve)
 
 circle(x-0.5*r, y, r0, white, mark=True)
 circle(x+0.5*r, y, r0, white, mark=True)
[…]

### 2016-02-22 modular.py

@@ -63,10 +63,12 @@ shade = grey
 
 
 
-g_curve = [green, style.linewidth.THick]
+st_curve = g_curve = [green, style.linewidth.THick]
 
 st_tau = [style.linewidth.Thick, red, style.linecap.round]
 #st_vac = [style.linewidth.thick, red]+st_dotted
+
+st_arrow = [deco.earrow()]
 
 
 
@@ -177,7 +179,7 @@ y = 0
 c = canvas.canvas()
 
 #c.text(x+0.5*h, y, r"\bigoplus_a \H\bigl(", text.mathmode) #east)
-mathtext(x, y+0.4*h, r"$\bigoplus_a \H\Bigl($", east)
+mathtext(x-0.1*w, y+0.4*h, r"$\bigoplus_a \H\Bigl($", east)
 
 r = 1.0
 x += 0.0*w
@@ -203,7 +205,9 @@ c.text(x+0.3*w, y+0.1*h, "$M$", west)
 
 c.text(x+0.3*w, y+0.7*h, "$a$", southwest)
 
-x += 1.8*r
+c.text(x+1.33*w, y+0.5*h, r"$\amalg$", center)
+
+x += 2.4*r
 
 r = 0.7
 p = path.circle(x+r, y+0.5*h, r)
@@ -323,7 +327,10 @@ surface(x+0.7*r, y, 0.6*r)
 labels = "aybc"
 for i, x0 in enumerate([x-0.9*r, x-0.5*r, x+0.5*r, x+0.9*r]):
     surface(x0, y, 0.1*r, fill=white)
-    c.text(x0, y+0.2, "$%s$"%labels[i], south)
+    if i==1:
+        c.text(x0, y+0.13, "$%s$"%labels[i], south)
+    else:
+        c.text(x0, y+0.2, "$%s$"%labels[i], south)
 c.text(x+1.1*r, y+0.7, "$\widehat{y}$", west)
 c.text(x-1.1*r, y+0.7, "$\widehat{d}$", east)
 
@@ -379,10 +386,10 @@ surface(x-0.6*r, y, 0.2*r, fill=white, mark=True, orient=not ccw)
 surface(x+0.6*r, y, 0.2*r, fill=white, mark=True, orient=not ccw)
 
 
-c.text(x-0.6*r, y+0.3*r, "$a_1$", south)
+#c.text(x-0.6*r, y+0.3*r, "$a_1$", south)
 c.text(x, y, "...", center)
[…]

### 2016-02-22 pentagon.py

@@ -1,0 +1,157 @@
+#!/usr/bin/env python
+
+import sys
+import os
+
+from math import *
+from random import *
+
+from pyx import canvas, path, deco, trafo, style, text, color, unit, epsfile, deformer, bitmap
+
+from PIL import Image
+
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
+
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+
+
+text.set(mode="latex")
+text.set(docopt="10pt")
+text.preamble(r'\usepackage{amsmath,amsfonts,amssymb}')
+text.preamble(r'\usepackage{mathrsfs}')
+#text.preamble(r"\def\I{\mathbb{I}}")
+text.preamble(r"\def\ket #1{|#1\rangle}")
+text.preamble(r"\def\H{\mathscr{H}}")
+text.preamble(r"\def\A{\mathcal{A}}")
+
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow, orange = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, 
+    rgb(0.75, 0.75, 0),
+    rgb(0.75, 0.55, 0),
+    )
+
+blue = rgb(0., 0., 0.8)
+pale_blue = rgb(0.7, 0.7, 1.0)
+pink = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.)
+grey = rgb(0.8, 0.8, 0.8)
+
+brown = rgbfromhexstring("#AA6C39"),
+
+light_shade = rgb(0.85, 0.65, 0.1)
+
+#shade = brown
+#shade = orange
[…]

### 2016-02-23 modular.py
commit edits

@@ -545,7 +545,7 @@ c.writePDFfile("pic-chain.pdf")
 #
 
 
-w = 1.5
+w = 1.2
 h = 1.5
 
 x = 0
@@ -553,31 +553,25 @@ y = 0
 
 c = canvas.canvas()
 
-c.text(x, y+0.5*h, r"$V^{ab}_{c} = \H\Bigl($", east)
+c.text(x, y+0.5*h, r"$V^{ab}_{c} := \H\Bigl($", east)
 
-r = 1.0
+r = 2*w/3.
 x += 0.0*w
 
 surface(x+r, y+0.5*h, r, mark=True)
-#c.fill(p, [shade])
-#c.stroke(p)
 
 x += 0.3*w
-surface(x+0.1*w, y+0.5*h, 0.3*r, white, mark=True)
-#c.fill(p, [white])
-#c.stroke(p)
+surface(x+0.1*w, y+0.5*h, 0.2*r, white, mark=True)
 
-c.text(x+0.1*w, y+0.75*h, "$a$", south)
+c.text(x+0.1*w, y+0.65*h, "$a$", south)
 
 x += 0.6*w
-surface(x+0.1*w, y+0.5*h, 0.3*r, white, mark=True)
-#c.fill(p, [white])
-#c.stroke(p)
+surface(x+0.1*w, y+0.5*h, 0.2*r, white, mark=True)
 
-c.text(x+0.1*w, y+0.75*h, "$b$", south)
+c.text(x+0.1*w, y+0.65*h, "$b$", south)
 
 
-c.text(x+0.3*w, y+1.0*h, "$\widehat{c}$", southwest)
+c.text(x+0.25*w, y+1.0*h, "$\widehat{c}$", southwest)
 
 x += 1.0*r
 mathtext(x, y+0.5*h, r"$\Bigr)$", east)

### 2016-02-25 hexagon.py
commit edits

@@ -170,7 +170,9 @@ c.text(x+r, y-r, r"$\widehat{c}$", southeast)
 x += 1.5*w
 
 #c.text(x, y, r"$\to$", center)
-c.stroke(path.line(x-0.4*w, y, x+0.4*w, y), [deco.earrow()])
+x0 = x-0.4*w
+c.stroke(path.line(x0, y, x+0.4*w, y), [deco.earrow()])
+c.stroke(path.line(x0, y-0.1, x0, y+0.1))
 c.text(x, y+0.3*h, r"$R_c^{ab}$", center)
 
 x += 1.5*w

### 2016-02-25 skein.py

@@ -190,7 +190,9 @@ circ(x+0.4*w, h, "$a$")
 
 ####### >>>>
 
-c.stroke(path.line(x+2*r0, y+r0, x+3*w-2*r0, y+r0), [deco.earrow()])
+x0 = x+2*r0
+c.stroke(path.line(x0, y+r0, x+3*w-2*r0, y+r0), [deco.earrow()])
+c.stroke(path.line(x0, y+r0-0.1, x0, y+r0+0.1))
 c.text(x+1.5*w, y+1.8*r0, "$R^{ab}_c$", center)
 
 x += 3*w

### 2016-02-25 syndrome.py

@@ -1,0 +1,346 @@
+#!/usr/bin/env python
+
+import sys
+import os
+
+from math import *
+from random import *
+
+from pyx import canvas, path, deco, trafo, style, text, color, unit, epsfile, deformer, bitmap
+
+
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
+
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+
+
+text.set(mode="latex")
+text.set(docopt="10pt")
+text.preamble(r'\usepackage{amsmath,amsfonts,amssymb}')
+text.preamble(r'\usepackage{mathrsfs}')
+#text.preamble(r"\def\I{\mathbb{I}}")
+text.preamble(r"\def\ket #1{|#1\rangle}")
+text.preamble(r"\def\H{\mathscr{H}}")
+text.preamble(r"\def\A{\mathcal{A}}")
+
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow, orange = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, 
+    rgb(0.75, 0.75, 0),
+    rgb(0.75, 0.55, 0),
+    )
+
+blue = rgb(0., 0., 0.8)
+pale_blue = rgb(0.7, 0.7, 1.0)
+pink = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.)
+grey = rgb(0.8, 0.8, 0.8)
+
+brown = rgbfromhexstring("#AA6C39"),
+
+light_shade = rgb(0.85, 0.65, 0.1)
+
+#shade = brown
+#shade = orange
+shade = grey
+
+
+
+
+st_tau = [style.linewidth.Thick, red, style.linecap.round]
[…]

### 2016-02-27 modular.py
commit edits

@@ -580,5 +580,54 @@ mathtext(x, y+0.5*h, r"$\Bigr)$", east)
 c.writePDFfile("pic-pop.pdf")
 
 
+#############################################################################
+#
+#
+
+
+w = 1.2
+h = 1.5
+
+x = 0
+y = 0
+
+c = canvas.canvas()
+
+
+r = 1.0
+r1 = 0.4*r
+
+surface(x, y, r, shade, mark=True)
+surface(x, y, r1, white, mark=True)
+
+c.stroke(path.line(x, y-r, x, y-r1))
+
+c.text(x-r, y+r, "$\widehat{a}$", northwest)
+c.text(x-r1, y+r1, "${a}$")
+
+c.stroke(path.line(x+1.4*r, y, x+2.6*r, y), [deco.earrow()])
+c.text(x+2.0*r, y+0.4*r, "$f_a$", center)
+
+x += 4*r
+
+surface(x, y, r, shade, mark=True)
+surface(x, y, r1, white, mark=True)
+
+t = Turtle(x, y-r, -0.45*pi)
+
+dr = 0.15
+r0 = 0.9*r
+for i in range(4):
+    t.right(0.53*pi, r0)
+    r0 -= dr
+t.stroke()
+
+c.text(x-r, y+r, "$\widehat{a}$", northwest)
+c.text(x-0.8*r1, y-r1, "${a}$", north)
+
+c.writePDFfile("pic-dehn-twist.pdf")
+
+
+
 
 

### 2016-02-27 tqft.py

@@ -69,7 +69,7 @@ st_tau = [style.linewidth.Thick, red, style.linecap.round]
 
 def anyon(x, y, r=0.07):
     c.fill(path.circle(x, y, r), [white])
-    c.stroke(path.circle(x, y, r), [red, style.linewidth.thick])
+    c.stroke(path.circle(x, y, r), [style.linewidth.thick])
 
 
 N = 20

### 2016-02-28 modular.py
start to explain the refactoring theorem

@@ -614,13 +614,13 @@ surface(x, y, r, shade, mark=True)
 surface(x, y, r1, white, mark=True)
 
 t = Turtle(x, y-r, -0.45*pi)
-
 dr = 0.15
 r0 = 0.9*r
 for i in range(4):
     t.right(0.53*pi, r0)
     r0 -= dr
 t.stroke()
+#t.stroke(st_curve + [trafo.rotate(90, x=x, y=y), deco+earrow()])
 
 c.text(x-r, y+r, "$\widehat{a}$", northwest)
 c.text(x-0.8*r1, y-r1, "${a}$", north)

### 2016-02-28 refactoring.py

@@ -354,5 +354,102 @@ c.text(x0-0.3, y0, r"$\H(f)$", east)
 c.writePDFfile("pic-natural.pdf")
 
 
+###############################################################################
+#
+#
+
+w, h = 2.2, 2.4
+
+c = canvas.canvas()
+
+r0 = 0.4*w # second hole
+r1 = 1.4*w # last hole
+
+#st_target = st_curve+st_dashed
+#st_target = [red, style.linewidth.THick, deco.earrow(size=0.2)]
+st_target = st_curve+st_dashed
+
+def manifold(x, y, labels, count):
+
+    if count in [0, 2]:
+        c.stroke(path.line(x-r0, y, x+r1+r0, y), st_curve)
+    else:
+        extra = list(st_curve)
+        #if count==3:
+        #    extra.append(trafo.scale(x=x, y=y, sx=1, sy=-1))
+        Turtle(x-0.85*r0, y, pi/2).\
+            fwd(0.3).\
+            right(0.25*pi, 0.4).left(0.50*pi, 0.73).left(0.88*pi, 0.15).\
+            fwd(0.55).\
+            right(0.88*pi, 0.15).right(0.50*pi, 0.73).\
+            left(0.25*pi, 0.52).goto(x+r1+r0, y).\
+            stroke(extra)
+
+    if count==0:
+        c.text(x+r1+r0, y-0.2, "$f$", northwest)
+    else:
+        c.text(x+r1+r0, y-0.2, "$R^{a_1a_2}_bf$", northwest)
+
+    c.text(x+(r0+r1)/2, y+0.7, "$f'$", southwest)
+
+    if count == 0:
+        Turtle(x, y, 3*pi/4).left(0.95*pi/2, 2**0.5/2*r1).stroke(st_target+[trafo.scale(x=x, y=y, sx=1, sy=-1)])
+    elif count == 3:
+        Turtle(x-0.05, y, 0.90*pi).left(0.30*pi, 0.8).left(0.3*pi, 2.8).\
+            stroke(st_target+[trafo.scale(x=x, y=y, sx=1, sy=-1)])
+    else:
+        Turtle(x+r0, y, 3*pi/4).left(0.95*pi/2, 2**0.5/2*(r1-r0)).stroke(st_target)
+
+    for i in range(3):
+        _x = [x, x+r0, x+r1][i]
[…]

### 2016-02-29 refactoring.py
more changes

@@ -388,7 +388,7 @@ def manifold(x, y, labels, count):
     if count==0:
         c.text(x+r1+r0, y-0.2, "$f$", northwest)
     else:
-        c.text(x+r1+r0, y-0.2, "$R^{a_1a_2}_bf$", northwest)
+        c.text(x+r1+r0, y-0.2, "$R^{a_1a_2}_{b_1}f$", northwest)
 
     c.text(x+(r0+r1)/2, y+0.7, "$f'$", southwest)
 
@@ -423,7 +423,7 @@ def manifold(x, y, labels, count):
 
     c.stroke(path.circle(x+r0/2, y, r0), [trafo.scale(x=x+r0/2, y=y, sx=1.0, sy=0.8)])
 
-    c.text(x, y+0.3*h, "$b$", southeast)
+    c.text(x, y+0.3*h, "$b_1$", southeast)
 
 
 x, y = 0., 4*h
@@ -438,10 +438,10 @@ x0, y0 = x + 0.7 + 0.2*dx, y - 0.2 + 0.2*dy
 c.stroke(path.line(x0, y0, x0+0.6*dx, y0+0.6*dy), [deco.earrow()])
 c.stroke(path.line(x0+0.03*dy, y0-0.03*dx, x0-0.03*dy, y0+0.03*dx), st_thick)
 
-c.text(x0-0.2+0.3*dx, y0+0.3*dy, "$R^{a_1a_2}_b$", northeast)
+c.text(x0-0.2+0.3*dx, y0+0.3*dy, "$R^{a_1a_2}_{b_1}$", northeast)
 
 
-x += dx
+x += 0.8*dx
 y += dy
 
 manifold(x + w, y, labels, 3)

### 2016-03-01 modular.py
commit edits

@@ -153,8 +153,9 @@ class Turtle(object):
         self.right(-dtheta, -r)
         return self
 
-    def stroke(self, extra=[], fill=[], closepath=False):
-        dopath(self.ps, extra, fill, closepath, smooth=0.)
+    def stroke(self, extra=[], fill=[], closepath=False, reverse=False):
+        ps = list(reversed(self.ps)) if reverse else self.ps
+        dopath(ps, extra, fill, closepath, smooth=0.)
         return self
 
 
@@ -163,129 +164,129 @@ class Turtle(object):
 #
 #
 
-def mathtext(x, y, text, *extra):
-    if text[0]=='$':
-        text = text[1:]
-    if text[-1]=='$':
-        text = text[:-1]
-    c.text(x, y, r"$\displaystyle %s$"%text, *extra)
-
-w = 1.5
-h = 1.5
-
-x = 0
-y = 0
-
-c = canvas.canvas()
-
-#c.text(x+0.5*h, y, r"\bigoplus_a \H\bigl(", text.mathmode) #east)
-mathtext(x-0.1*w, y+0.4*h, r"$\bigoplus_a \H\Bigl($", east)
-
-r = 1.0
-x += 0.0*w
-
-p = path.circle(x+r, y+0.5*h, r)
-c.fill(p, [shade])
-c.stroke(p)
-#c.fill(path.circle(x+2*r, y+0.5*h, 0.06))
-c.fill(path.circle(x+r, y+0.5*h-r, 0.06))
-
-x += 0.3*w
-p = path.circle(x+0.1*w, y+0.5*h, 0.4*r)
-c.fill(p, [white])
-c.stroke(p)
-#p = path.circle(x+0.1*w+0.4*r, y+0.5*h, 0.06)
-p = path.circle(x+0.1*w, y+0.5*h-0.4*r, 0.06)
-c.fill(p)
-
-c.text(x+0.6*w, y+0.5*h, "...")
-
-#c.text(x+0.1*w, y+0.0*h, "$M_a$", west)
-c.text(x+0.3*w, y+0.1*h, "$M$", west)
-
-c.text(x+0.3*w, y+0.7*h, "$a$", southwest)
-
[…]

### 2016-03-02 refactoring.py
more changes

@@ -367,7 +367,9 @@ r1 = 1.4*w # last hole
 
 #st_target = st_curve+st_dashed
 #st_target = [red, style.linewidth.THick, deco.earrow(size=0.2)]
-st_target = st_curve+st_dashed
+#st_target = st_curve+st_dashed
+st_target = st_curve+[
+    style.linestyle(style.linecap.butt, style.dash([2], offset=1, rellengths=False))]
 
 def manifold(x, y, labels, count):
 

### 2016-03-02 tqft.py

@@ -66,7 +66,6 @@ st_tau = [style.linewidth.Thick, red, style.linecap.round]
 #st_vac = [style.linewidth.thick, red]+st_dotted
 
 
-
 def anyon(x, y, r=0.07):
     c.fill(path.circle(x, y, r), [white])
     c.stroke(path.circle(x, y, r), [style.linewidth.thick])
@@ -624,6 +623,10 @@ m = 0.1*w
 m0 = m/2
 r = 0.3*w
 
+#st_curve_p = g_curve + st_dashed
+st_curve_p = g_curve + [
+    style.linestyle(style.linecap.butt, style.dash([2], offset=1, rellengths=False))]
+
 
 c.fill(path.rect(x-m0, y-m0, 2*m0+w, 2*m0+h), [shade])
 c.stroke(path.rect(x, y, w, h))
@@ -632,7 +635,7 @@ c.stroke(path.line(x+1.3*w, y+0.6*h, x+w+m, y+0.6*h), g_curve+st_dotted)
 c.stroke(path.line(x+w+m, y+0.6*h, x+0.5*w, y+0.6*h), g_curve) #+[deco.earrow(size=0.2)])
 c.stroke(path.line(x+w+m, y+0.6*h, x+0.6*w, y+0.6*h), g_curve+[deco.earrow(size=0.2)])
 c.stroke(path.line(x+0.5*w, y+0.6*h, x+0.2*w, y+0.6*h), g_curve+st_dotted)
-c.stroke(path.line(x+w-m, y+0.6*h, x+w-m, 0.2*h), st_tau+[deco.earrow(size=0.2)])
+c.stroke(path.line(x+w-m, y+0.6*h, x+w-m, 0.2*h), st_curve_p+[deco.earrow(size=0.2)])
 anyon(x+w-m, y+0.6*h)
 
 c.stroke(path.line(x+1.3*w, y+0.2*h, x+w+m, y+0.2*h), g_curve+st_dotted)
@@ -704,7 +707,8 @@ y = 0.
 #c.fill(path.circle(-w, 0, 0.1))
 
 g = g_curve+[deco.earrow(size=0.2)]
-a = st_tau+[deco.earrow(size=0.2)]
+#a = st_tau+[deco.earrow(size=0.2)]
+a = st_curve_p+[deco.earrow(size=0.2)]
[…]

### 2016-03-08 hexagon.py
remove involution of label on exterior hole

@@ -165,7 +165,7 @@ circle(x+0.5*r, y, r0, white, mark=True)
 
 c.text(x+0.5*r, y+0.14*h, r"$a$", southwest)
 c.text(x-0.5*r, y-0.14*h, r"$b$", northeast)
-c.text(x+r, y-r, r"$\widehat{c}$", southeast)
+c.text(x+r, y-r, r"${c}$", southeast)
 
 x += 1.5*w
 
@@ -186,7 +186,7 @@ circle(x+0.5*r, y, r0, white, mark=True)
 
 c.text(x-0.5*r, y-0.14*h, r"$b$", northeast)
 c.text(x+0.5*r, y+0.14*h, r"$a$", southwest)
-c.text(x+r, y-r, r"$\widehat{c}$", southeast)
+c.text(x+r, y-r, r"${c}$", southeast)
 
 
 c.writePDFfile("pic-rmove-1.pdf")

### 2016-03-08 modular.py

@@ -164,129 +164,129 @@ class Turtle(object):
 #
 #
 
-#def mathtext(x, y, text, *extra):
-#    if text[0]=='$':
-#        text = text[1:]
-#    if text[-1]=='$':
-#        text = text[:-1]
-#    c.text(x, y, r"$\displaystyle %s$"%text, *extra)
+def mathtext(x, y, text, *extra):
+    if text[0]=='$':
+        text = text[1:]
+    if text[-1]=='$':
+        text = text[:-1]
+    c.text(x, y, r"$\displaystyle %s$"%text, *extra)
+
+w = 1.5
+h = 1.5
+
+x = 0
+y = 0
+
+c = canvas.canvas()
+
+#c.text(x+0.5*h, y, r"\bigoplus_a \H\bigl(", text.mathmode) #east)
+mathtext(x-0.1*w, y+0.4*h, r"$\bigoplus_a \H\Bigl($", east)
+
+r = 1.0
+x += 0.0*w
+
+p = path.circle(x+r, y+0.5*h, r)
+c.fill(p, [shade])
+c.stroke(p)
+#c.fill(path.circle(x+2*r, y+0.5*h, 0.06))
+c.fill(path.circle(x+r, y+0.5*h-r, 0.06))
+
+x += 0.3*w
+p = path.circle(x+0.1*w, y+0.5*h, 0.4*r)
+c.fill(p, [white])
+c.stroke(p)
+#p = path.circle(x+0.1*w+0.4*r, y+0.5*h, 0.06)
+p = path.circle(x+0.1*w, y+0.5*h-0.4*r, 0.06)
+c.fill(p)
+
+c.text(x+0.6*w, y+0.5*h, "...")
+
+#c.text(x+0.1*w, y+0.0*h, "$M_a$", west)
+c.text(x+0.3*w, y+0.1*h, "$M$", west)
+
+c.text(x+0.3*w, y+0.7*h, "$a$", southwest)
+
+c.text(x+1.33*w, y+0.5*h, r"$\amalg$", center)
+
+x += 2.4*r
+
+r = 0.7
+p = path.circle(x+r, y+0.5*h, r)
+c.fill(p, [shade])
+c.stroke(p)
+#p = path.circle(x+2*r, y+0.5*h, 0.06)
+p = path.circle(x+r, y+0.5*h-r, 0.06)
+c.fill(p)
+
+x += 0.3*w
+
[…]

### 2016-03-08 skein.py

@@ -133,7 +133,7 @@ def ucirc():
     x2, y2 = x1-0.5*dx*sy*r0, y1-0.5*sy*r0
     c.stroke(path.line(x, y, x2, y2))
     c.fill(path.circle(x2, y2, 0.05))
-    c.text(x2-0.5*r0, y2-0.5*r0, "$\widehat{c}$", southeast)
+    c.text(x2-0.5*r0, y2-0.5*r0, "${c}$", southeast)
 
 
 w, h = 1.5, 2.5

### 2016-03-11 process.py
more changes

@@ -1,0 +1,113 @@
+#!/usr/bin/env python
+
+import sys
+from math import *
+from random import *
+import numpy
+
+from pyx import canvas, path, deco, trafo, style, text, color, deformer
+
+text.set(mode="latex") 
+text.set(docopt="10pt")
+text.preamble(r"\usepackage{amsmath,amsfonts,amssymb}")
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, rgb(0.75, 0.75, 0)) 
+
+black = rgb(0., 0., 0.) 
+blue = rgb(0., 0., 0.8)
+lred = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.) 
+
+#shade = rgb(0.75, 0.55, 0)
+
+grey = rgb(0.75, 0.75, 0.75)
+shade = grey
+shade0 = rgb(0.75, 0.75, 0.75)
+shade1 = rgb(0.80, 0.80, 0.80)
+shade2 = rgb(0.85, 0.85, 0.85)
+
+light_shade = rgb(0.85, 0.65, 0.1)
+light_shade = rgb(0.9, 0.75, 0.4)
+
+
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
+
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+st_thick = [style.linewidth.thick]
+st_Thick = [style.linewidth.Thick]
+
+
+###############################################################################
+#
+#
+
+c = canvas.canvas()
+
+
+W = 3.4
+H = 5.0
+
+dy = 0.9
+
+x, y = 0., 0.
+r = 0.3
+
[…]

### 2016-03-11 decode.py
more changes

@@ -1,0 +1,352 @@
+#!/usr/bin/env python
+
+import sys
+from math import *
+from random import *
+import numpy
+
+from pyx import canvas, path, deco, trafo, style, text, color, deformer
+
+text.set(mode="latex") 
+text.set(docopt="12pt")
+text.preamble(r"\usepackage{amsmath,amsfonts,amssymb}")
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, rgb(0.75, 0.75, 0)) 
+
+black = rgb(0., 0., 0.) 
+blue = rgb(0., 0., 0.8)
+lred = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.) 
+
+shade = rgb(0.75, 0.55, 0)
+grey = rgb(0.75, 0.75, 0.75)
+
+light_shade = rgb(0.85, 0.65, 0.1)
+light_shade = rgb(0.9, 0.75, 0.4)
+
+
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
+
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+def arrow(x0, y0, x1, y1, extra=[]):
+    c.stroke(path.line(x0, y0, x1, y1),
+        extra+[deco.earrow(size=0.1)])
+
+#c.stroke(
+#    path.curve(0, 0, 0, 4, 2, 4, 3, 3),
+#    [style.linewidth.THICK, style.linestyle.dashed, color.rgb.blue,
+#    deco.earrow([deco.stroked([color.rgb.red, style.linejoin.round]),
+#                       deco.filled([color.rgb.green])], size=1)])
+
+def line(x0, y0, x1, y1, extra=[]):
+    c.stroke(path.line(x0, y0, x1, y1), extra)
+
[…]

### 2016-03-11 decode.py
commit edits

@@ -72,7 +72,7 @@ def harrow(x0, x1, y, extra=[], label=None):
 
 def anyon(x, y, r=0.07):
     c.fill(path.circle(x, y, r), [white])
-    c.stroke(path.circle(x, y, r), [red, style.linewidth.thick])
+    c.stroke(path.circle(x, y, r), [style.linewidth.thick])
 
 
 N = 20
@@ -264,12 +264,19 @@ def draw(dx=0., dy=0., use_arrows=True):
         #    [style.linewidth.THICK, style.linecap.round, grey])
 
     if use_arrows:
+      t = 0.1
+      s = 1.-t
       for (p0, p1) in lines:
         x0, y0 = coord(*p0)
         x1, y1 = coord(*p1)
+        #x0, x1 = s*x0+t*x1, s*x1+t*x0
+        #y0, y1 = s*y0+t*y1, s*y1+t*y0
+        if syndrome[p1]:
+            x1 = s*x1+t*x0
+            y1 = s*y1+t*y0
         syndrome1[p0] = 0
         c.stroke(path.line(x0+dx, y0+dy, x1+dx, y1+dy),
-            [style.linewidth.Thick, deco.earrow(size=0.3)])
+            [style.linewidth.Thick, style.linecap.round, deco.earrow(size=0.2)])
 
     for i, j in sites:
         c.stroke(path.rect(j*w+dx, i*h+dy, w-2*m, h-2*m))

### 2016-05-09 modular.py
more changes

@@ -109,7 +109,7 @@ def pop(*args):
     c1.insert(c, *args)
     c = c1
 
-SINGLE_COLUMN = False
+DOUBLE_COLUMN = False
 
 
 
@@ -160,16 +160,18 @@ class Turtle(object):
 
 
 
-#############################################################################
-#
-#
-
 def mathtext(x, y, text, *extra):
     if text[0]=='$':
         text = text[1:]
     if text[-1]=='$':
         text = text[:-1]
     c.text(x, y, r"$\displaystyle %s$"%text, *extra)
+
+#############################################################################
+#
+#
+
+EXTERIOR_HOLE = False
 
 w = 1.5
 h = 1.5
@@ -187,14 +189,17 @@ x += 0.0*w
 
 p = path.circle(x+r, y+0.5*h, r)
 c.fill(p, [shade])
-c.stroke(p)
-#c.fill(path.circle(x+2*r, y+0.5*h, 0.06))
-c.fill(path.circle(x+r, y+0.5*h-r, 0.06))
+
+if EXTERIOR_HOLE:
+    c.stroke(p)
+    #c.fill(path.circle(x+2*r, y+0.5*h, 0.06))
+    c.fill(path.circle(x+r, y+0.5*h-r, 0.06))
 
 x += 0.3*w
 p = path.circle(x+0.1*w, y+0.5*h, 0.4*r)
 c.fill(p, [white])
 c.stroke(p)
+
 #p = path.circle(x+0.1*w+0.4*r, y+0.5*h, 0.06)
 p = path.circle(x+0.1*w, y+0.5*h-0.4*r, 0.06)
 c.fill(p)
@@ -230,7 +235,7 @@ c.text(x+0.5*w, y+0.9*h, "$\widehat{a}$", southwest)
 x += 1.8*r
 mathtext(x, y+0.5*h, r"$\Bigr)$", east)
 
-if SINGLE_COLUMN:
+if DOUBLE_COLUMN:
     x -= 0*r
     y -= 3*r
 else:
@@ -250,10 +255,57 @@ r = 1.0
 
 p = path.circle(x+r, y+0.5*h, r)
 c.fill(p, [shade])
+if EXTERIOR_HOLE:
+    c.stroke(p)
[…]

### 2016-05-11 braid.py
more changes

@@ -1,0 +1,281 @@
+#!/usr/bin/env python
+
+import sys
+import os
+
+from math import *
+from random import *
+
+from pyx import canvas, path, deco, trafo, style, text, color, unit, epsfile, deformer, bitmap
+
+from PIL import Image
+
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
+
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+st_Thick = [style.linewidth.Thick]
+
+
+text.set(mode="latex")
+text.set(docopt="10pt")
+text.preamble(r'\usepackage{amsmath,amsfonts,amssymb}')
+#text.preamble(r"\def\I{\mathbb{I}}")
+text.preamble(r"\def\ket #1{|#1\rangle}")
+
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow, orange = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, 
+    rgb(0.75, 0.75, 0),
+    rgb(0.75, 0.55, 0),
+    )
+
+blue = rgb(0., 0., 0.8)
+pale_blue = rgb(0.7, 0.7, 1.0)
+pink = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.)
+grey = rgb(0.8, 0.8, 0.8)
+
+brown = rgbfromhexstring("#AA6C39"),
+
+light_shade = rgb(0.85, 0.65, 0.1)
+
+#shade = brown
+#shade = orange
+shade = grey
+
+
+
+g_curve = [green, style.linewidth.THick]
+
+st_tau = [style.linewidth.Thick, red, style.linecap.round]
+#st_vac = [style.linewidth.thick, red]+st_dotted
+
+
+def anyon(x, y, r=0.07):
+    c.fill(path.circle(x, y, r), [white])
[…]

### 2016-05-13 braid.py
more about braids

@@ -75,6 +75,9 @@ def anyon(x, y, r=0.07):
 N = 20
 
 def dopath(ps, extra=[], fill=[], closepath=False, smooth=0.0):
+    if not ps:
+        print "dopath: empty"
+        return
     ps = [path.moveto(*ps[0])]+[path.lineto(*p) for p in ps[1:]]
     if closepath:
         ps.append(path.closepath())
@@ -153,6 +156,66 @@ class Turtle(object):
         dopath(self.ps, extra, fill, closepath, smooth=0.)
         return self
 
+
+
+def occluded(ps0, pss, radius=0.2):
+
+    ps = []
+
+    flag = True
+    for i, p in enumerate(ps0):
+
+        flag1 = True
+        x, y = p
+        for ps1 in pss:
+            x1, y1 = ps1[i]
+            if abs(x1-x)<radius:
+                flag1 = False
+        #print int(flag1),
+
+        if flag1 == flag:
+            ps.append(p)
+        elif ps:
+            yield flag, ps
+            ps = [p]
+        flag = flag1
+
+    if ps:
+        yield flag, ps
+
+
+def draw(ps0, pss, descs, radius=0.25):
+
+    descs = list(descs)
+    desc = descs.pop(0) if descs else True
+    _ps = []
+    for flag, ps in occluded(ps0, pss, radius):
+        #print '/',
+        if flag or desc:
+            _ps += ps
+        else:
+            yield _ps
+            _ps = []
+        if not flag:
+            desc = descs.pop(0) if descs else True
+    if _ps:
+        yield _ps
+
+
+def bump(x0, alpha=0.4):
+    x1 = 0.5 - 0.5*cos(pi*x0)
+    x = alpha*x0 + (1-alpha)*x1
+    return x
+
+def timeslice(x, y, transparency=0., label="", W=3):
+    dopath([(-1.1, y0), (-0.1, y1), (W + .2, y1), (W -0.8, y0)],
+        fill=[shade, color.transparency(0.3)],
+        extra=[trafo.translate(x, y)], closepath=True)
+    if label:
[…]

### 2016-05-17 braid.py
commit edits

@@ -119,11 +119,23 @@ class Turtle(object):
         self.y = y
         self.theta = theta
         self.ps = [(x, y)]
+        self.pen = True
+
+    def penup(self):
+        self.pen = False
+        self.ps = []
+        return self
+
+    def pendown(self):
+        self.pen = True
+        self.ps = [(self.x, self.y)]
+        return self
 
     def fwd(self, d):
         self.x += d*sin(self.theta)
         self.y += d*cos(self.theta)
-        self.ps.append((self.x, self.y))
+        if self.pen:
+            self.ps.append((self.x, self.y))
         return self
 
     def reverse(self, d):
@@ -134,7 +146,7 @@ class Turtle(object):
         theta = self.theta
         self.theta += dtheta
         if r==0.:
-            return
+            return self
         N = 20
         x, y = self.x, self.y
         x0 = x - r*sin(theta-pi/2)
@@ -143,7 +155,8 @@ class Turtle(object):
             theta += (1./(N))*dtheta
             x = x0 - r*sin(theta+pi/2)
             y = y0 - r*cos(theta+pi/2)
-            self.ps.append((x, y))
+            if self.pen:
+                self.ps.append((x, y))
         self.x = x
         self.y = y
         return self
@@ -214,6 +227,65 @@ def timeslice(x, y, transparency=0., label="", W=3):
     if label:
         c.text(W+0.2, 0., label, west+[trafo.translate(x, y)])
 
+
+
+#############################################################################
+#
+#
+
+
+c = canvas.canvas()
+
+W = 5.
+H = 3.
+
+c.stroke(path.line(0.0, -0.2, 0., H), [deco.earrow()])
+c.stroke(path.line(-0.2, 0., W, 0), [deco.earrow()])
+my = 0.25
+c.stroke(path.line(-0.2, -my*0.2, 0.9*W, my*W), [deco.earrow()])
+
+x0, y0 = 0.3*W, 0.3*H
+x1, y1 = x0+0.3*W, y0+my*0.3*W
+
+
+#t = Turtle(x0, y0, pi/4)
+#t.penup().fwd(0.2).pendown()
+#theta, r = 0.25*pi, 2.0
+#t.right(theta, r).right(0.8*pi, 0.2).right(theta, r)
[…]

### 2016-05-17 braid.py
commit edits

@@ -282,7 +282,7 @@ for i in range(10):
     #tpy += 0.05
     theta -= 0.06*pi
     #r1 = 0.9*r1
-    r1 -= 0.15
+    r1 -= 0.17
     theta1 += 0.01*pi
 
 c.writePDFfile("pic-monodromy3d.pdf")

### 2016-05-24 braid.py
commit edits

@@ -49,6 +49,7 @@ blue = rgb(0., 0., 0.8)
 pale_blue = rgb(0.7, 0.7, 1.0)
 pink = rgb(1., 0.4, 0.4)
 white = rgb(1., 1., 1.)
+black = rgb(0., 0., 0.)
 grey = rgb(0.8, 0.8, 0.8)
 
 brown = rgbfromhexstring("#AA6C39"),
@@ -74,7 +75,7 @@ def anyon(x, y, r=0.07):
 
 N = 20
 
-def dopath(ps, extra=[], fill=[], closepath=False, smooth=0.0):
+def dopath(ps, extra=[], fill=[], closepath=False, smooth=0.0, stroke=True):
     if not ps:
         print "dopath: empty"
         return
@@ -87,7 +88,8 @@ def dopath(ps, extra=[], fill=[], closepath=False, smooth=0.0):
         extra.append(deformer.smoothed(smooth))
     if fill:
         c.fill(p, extra+fill)
-    c.stroke(p, extra)
+    if stroke:
+        c.stroke(p, extra)
 
 
 def ellipse(x0, y0, rx, ry, extra=[], fill=[]):
@@ -264,10 +266,10 @@ def loop(x0, y0, r1, theta0, theta1, tpy):
     #theta = 0.55*pi
     theta = theta1
     r2 = 2*r1*sin(theta - 0.5*pi)
-    t.penup().fwd(0.2*r1).pendown()
-    t.fwd(0.8*r1).right(theta).fwd(r2).right(theta).fwd(0.8*r1) 
+    t.penup().fwd(0.1*r1).pendown()
+    t.fwd(0.9*r1).right(theta).fwd(r2).right(theta).fwd(0.9*r1) 
     t.stroke([deco.earrow(), 
-        deformer.smoothed(2.0), style.linewidth.Thick,
+        deformer.smoothed(4.0), style.linewidth.Thick,
         color.transparency(tpy), tr])
 
 r1 = 2.0
@@ -286,6 +288,42 @@ for i in range(10):
     theta1 += 0.01*pi
 
 c.writePDFfile("pic-monodromy3d.pdf")
+
+
+#############################################################################
+#
+#
+
+
+c = canvas.canvas()
+
+W = 5.
+H = 3.
+
+tr = trafo.scale(x=0.0*W, y=0.0*H, sx=0.6, sy=0.6)
[…]

### 2016-05-26 braid.py
more changes

@@ -58,8 +58,7 @@ light_shade = rgb(0.85, 0.65, 0.1)
 
 #shade = brown
 #shade = orange
-shade = grey
-
+shade = rgb(0.8, 0.8, 0.8)
 
 
 g_curve = [green, style.linewidth.THick]
@@ -849,7 +848,8 @@ def gethpath(mx):
     return ps
 
 
-highlight = white
+highlight = rgb(0.6, 0.6, 0.6)
+#highlight = white
 #highlight = rgb(1,1,0)
 
 HH = 0.6*H

### 2016-08-15 braid.py
commit edits

@@ -853,10 +853,10 @@ highlight = rgb(0.6, 0.6, 0.6)
 #highlight = rgb(1,1,0)
 
 HH = 0.6*H
-X0 = -10
+X0 = -10.
+X1 = 0.
 
-
-for X in [X0, 0.]:
+for X in [X0, X1]:
 
     tr = trafo.translate(X, 0.)
     
@@ -881,7 +881,6 @@ c.text(X0-r, -0.4, "$i$", center)
 c.text(X0+r, -0.4, "$i+1$", center)
 c.text(X0+3*r, -0.4, "$...$", center)
 
-
 p = path.circle(0., 0., R)
 tr = trafo.scale(1., Rmin/Rmaj)
 c.fill(p, [shade, tr])
@@ -901,6 +900,11 @@ dopath(ps, fill=[highlight], stroke=False)
 
 for x in [-3*r, -r, r, 3*r]:
     c.fill(path.circle(x, 0., radius), [tr]) # focus
+
+c.text(X1-3*r, -0.4, "$...$", center)
+c.text(X1-r, -0.4, "$i+1$", center)
+c.text(X1+r, -0.4, "$i$", center)
+c.text(X1+3*r, -0.4, "$...$", center)
 
 
 

### 2016-08-17 braid.py
commit edits

@@ -296,6 +296,70 @@ c.writePDFfile("pic-monodromy3d.pdf")
 
 c = canvas.canvas()
 
+
+def mkpath(x, y, radius=1.):
+
+    pts = [
+        ((x+0.05*radius, y+0.04*radius)),
+        ((x+0.5*radius, y+0.20*radius)),
+        ((x+0.5*radius, y-0.20*radius)),
+        ((x+0.07*radius, y-0.05*radius)),
+    ]
+
+    pts = [(xx+0.8*yy, yy) for (xx, yy) in pts]
+
+    pts = [path.moveto(*pts[0])] + [path.lineto(*p) for p in pts[1:]]
+
+    pts = path.path(*pts)
+    return pts
+
+
+
+def dorect(x, y, W=2, H=0.6):
+    dopath([(x-1.1, y-H), (x-0.1, y+H), (x+W+.2, y+H), (x+W-0.8, y-H)],
+        fill=[shade, color.transparency(0.3)],
+        closepath=True)
+
+
+x, y = 0., 0.
+radius = 0.06 
+
+dorect(x, y)
+
+c.fill(path.circle(x, y, radius), [style.linewidth.thick])
+c.fill(path.circle(x+1, y, radius), [style.linewidth.thick])
+c.stroke(mkpath(x, y, 3),
+    [deformer.smoothed(2.0),
+    style.linewidth.Thick, deco.earrow(size=0.2)])
+
+x += 3 
+
+c.text(x-0.1, y-0.1, r"$\ne$")
+
+x += 2 
+
+dorect(x, y)
+
+c.fill(path.circle(x, y, radius), [style.linewidth.thick])
+c.fill(path.circle(x+1, y, radius), [style.linewidth.thick])
+c.stroke(mkpath(x, y, 1.4),
+    [deformer.smoothed(2.0),
+    style.linewidth.Thick, deco.earrow(size=0.2)])
+
+
+c.writePDFfile("pic-monodromy2d.pdf")
+
+if "exit" in sys.argv:
+    sys.exit(0)
+
+
+#############################################################################
+#
+#
+
+
+c = canvas.canvas()
+
 W = 5.
 H = 3.
 

### 2016-08-20 framed.py
commit edits

@@ -1,0 +1,400 @@
+#!/usr/bin/env python
+
+import sys
+import os
+
+from math import *
+from random import *
+
+from pyx import canvas, path, deco, trafo, style, text, color, unit, epsfile, deformer, bitmap
+
+from PIL import Image
+
+north = [text.halign.boxcenter, text.valign.top]
+northeast = [text.halign.boxright, text.valign.top]
+northwest = [text.halign.boxleft, text.valign.top]
+south = [text.halign.boxcenter, text.valign.bottom]
+southeast = [text.halign.boxright, text.valign.bottom]
+southwest = [text.halign.boxleft, text.valign.bottom]
+east = [text.halign.boxright, text.valign.middle]
+west = [text.halign.boxleft, text.valign.middle]
+center = [text.halign.boxcenter, text.valign.middle]
+
+
+st_dashed = [style.linestyle.dashed]
+st_dotted = [style.linestyle.dotted]
+
+st_Thick = [style.linewidth.Thick]
+
+
+text.set(mode="latex")
+text.set(docopt="10pt")
+text.preamble(r'\usepackage{amsmath,amsfonts,amssymb}')
+#text.preamble(r"\def\I{\mathbb{I}}")
+text.preamble(r"\def\ket #1{|#1\rangle}")
+
+
+rgb = color.rgb
+rgbfromhexstring = color.rgbfromhexstring
+
+red, green, blue, yellow, orange = (
+    rgbfromhexstring("#d00000"),
+    rgbfromhexstring("#006000"),
+    rgb.blue, 
+    rgb(0.75, 0.75, 0),
+    rgb(0.75, 0.55, 0),
+    )
+
+blue = rgb(0., 0., 0.8)
+pale_blue = rgb(0.7, 0.7, 1.0)
+pink = rgb(1., 0.4, 0.4)
+white = rgb(1., 1., 1.)
+black = rgb(0., 0., 0.)
+grey = rgb(0.8, 0.8, 0.8)
+
+brown = rgbfromhexstring("#AA6C39"),
+
+light_shade = rgb(0.85, 0.65, 0.1)
+
+#shade = brown
+#shade = orange
+shade = rgb(0.8, 0.8, 0.8)
+
+
+g_curve = [green, style.linewidth.THick]
+
+st_tau = [style.linewidth.Thick, red, style.linecap.round]
+#st_vac = [style.linewidth.thick, red]+st_dotted
+
+
+def anyon(x, y, r=0.07):
[…]

### 2016-08-21 framed.py
commit edits

@@ -398,3 +398,138 @@ c.writePDFfile("pic-framed.pdf")
 
 
 
+#############################################################################
+#
+#
+
+class Tracer(object):
+    def __init__(self, x0, y0, r, theta):
+        self.x0 = x0
+        self.y0 = y0
+        self.theta = theta
+        self.r = r
+        self.ps = []
+
+    def get(self):
+        theta = self.theta
+        r = self.r
+        x = self.x0 + r*sin(theta)
+        y = self.y0 + r*cos(theta)
+        return x, y
+
+    def reset(self, r):
+        # recalculate x0, y0
+        if r==self.r:
+            return
+        x1, y1 = self.get()
+        theta = self.theta
+        self.x0 = x1 - r*sin(theta)
+        self.y0 = y1 - r*cos(theta)
+        self.r = r
+
+    def trace(self, r=None, dtheta=0.05*pi):
+        theta = self.theta
+        if r is not None:
+            self.reset(r)
+        self.ps.append(self.get())
+        if self.r > 0:
+            self.theta = theta + dtheta
+        else:
+            self.theta = theta - dtheta
+
+    def __call__(self, count=1, r=None):
+        icount = int(count)
+        for i in range(icount):
+            self.trace(r)
+        fcount = count - icount
+        if fcount<1e-6:
+            return
+        self.trace(r, fcount*0.05*pi)
+
+    def dopath(self, *args, **kw):
+        dopath(self.ps, *args, **kw)
+
+
+
+c = canvas.canvas()
+
+
+r = 1.0
+w = 5.0
+
+#ellipse(w, 0., 1.0*r, 1.8*r)
+
+def tslice(x, y, W=0.9, H=2.2, transparency=0.3):
+    slope = 0.8
+    p = path.path(
+        path.moveto(x-W, y-H+slope),
+        path.lineto(x-W, y+H+slope),
+        path.lineto(x+W, y+H-slope),
+        path.lineto(x+W, y-H-slope),
+        path.closepath())
[…]

### 2016-08-21 framed.py
commit edits

@@ -455,11 +455,11 @@ c = canvas.canvas()
 
 
 r = 1.0
-w = 5.0
+w = 4.0
 
 #ellipse(w, 0., 1.0*r, 1.8*r)
 
-def tslice(x, y, W=0.9, H=2.2, transparency=0.3):
+def tslice(x, y, W=0.7, H=2.2, transparency=0.3):
     slope = 0.8
     p = path.path(
         path.moveto(x-W, y-H+slope),
@@ -505,14 +505,17 @@ for ps in (ps2[:N/4-1], ps2[N/4+1:]):
 
 #ellipse(0., 0.,    1.0*r, 1.8*r, [white], fill=[white])
 #ellipse(0., 0.,    1.0*r, 1.8*r)
-ellipse(0., 0.5*r, 0.7*r, 1.0*r)
+#ellipse(0., 0.5*r, 0.7*r, 1.0*r)
+
+c.stroke(path.circle(0., 0.5*r, r), 
+    [trafo.scale(0.5, 1., 0., 0.5*r)])
 
 def anyon(x, y):
     c.fill(path.circle(x, y, 0.05))
 
 tslice(w, 0)
 
-tracer.dopath([trafo.scale(-1, 1, x=w, y=0)],
+tracer.dopath([trafo.scale(-0.7, 1, x=w, y=0)],
     closepath=True)
 
 anyon(0., r)

### 2016-08-24 framed.py
commit edits

@@ -222,7 +222,7 @@ def bump(x0, alpha=0.4):
     return x
 
 
-def timeslice(x, y, transparency=0., label="", W=3.5, H=1.):
+def timeslice(x, y, transparency=0., label="", W=3.0, H=1.):
     y0 = -0.5*H
     y1 = +0.5*H
     x0 = -0.5*W
@@ -240,7 +240,7 @@ def timeslice(x, y, transparency=0., label="", W=3.5, H=1.):
 #
 
 
-W = 5.
+W = 4.3
 H = 4.
 
 r = 0.4 # radius of ribbon
@@ -255,7 +255,36 @@ c = canvas.canvas()
 x = 0.
 y = 0. # ---------------
 
+timeslice(x, y)
 
+c.fill(path.circle(x, y, 0.04))
+
+t = Turtle(x, y, 0)
+theta = 2*pi
+
+t.fwd(0.26*H)
+t.right(0.1*theta, 0.4*H)
+t.right(0.1*theta, 0.4*H)
+t.right(0.3*theta, 0.15*H)
+
+t.right(0.3*theta, 0.15*H)
+t.right(0.08*theta, 0.4*H)
+t.stroke(extra=st_Thick)
+t.penup()
+t.right(0.04*theta, 0.4*H)
+t.pendown()
+t.right(0.08*theta, 0.4*H)
+t.fwd(0.26*H)
+
+t.stroke(extra=st_Thick)
+
+
+timeslice(x, y+H, 0.5)
+
+c.fill(path.circle(x, y+H, 0.04))
+
+
+x += W # ---------------
 
 timeslice(x, y)
 
@@ -338,8 +367,11 @@ x += W # ---------------
 
 timeslice(x, y)
 
+cyl = rgb(0.6,0.6,0.6)
+
 sy = 0.4
 t = trafo.scale(1., sy, x, y)
+c.fill(path.circle(x, y, r), [t, cyl])
 c.stroke(path.circle(x, y, r), [t])
 c.fill(path.circle(x, y-sy*r, 0.05))
 
@@ -348,7 +380,7 @@ c.fill(path.path(
     path.lineto(x+r, y),
     path.lineto(x+r, y+H),
     path.lineto(x-r, y+H),
-    path.closepath()), [shade])
+    path.closepath()), [cyl])
 
 #c.stroke(path.circle(x, y, r), [t, rgb(0.5,0.5,0.5)])
[…]

### 2016-09-22 guide.tex
an attempt to excise the modular functor stuff

\documentclass[aps, letterpaper, onecolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
\usepackage{times}

% use these settings for a more reader-friendly version
%\documentclass[aps, pra, a4paper, 11pt, onecolumn, nofootinbib, superscriptaddress, tightenlines, notitlepage, longbibliography]{revtex4-1}

%------------------------------------------------------------------------------------------------------------%
% Packages
%------------------------------------------------------------------------------------------------------------%

\usepackage{xcolor}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{enumitem}

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,calc}
%\usepackage{epstopdf} % to include .eps graphics files with pdfLaTeX

\usepackage[pdfpagelabels,pdftex,bookmarks,breaklinks]{hyperref}
\definecolor{darkblue}{RGB}{0,0,127} % choose colors
\definecolor{darkgreen}{RGB}{0,150,0}
\hypersetup{colorlinks, linkcolor=darkblue, citecolor=darkgreen, filecolor=red, urlcolor=blue}
\hypersetup{pdfauthor={Simon Burton, Courtney G. Brell, Steven T. Flammia}}
\hypersetup{pdftitle={Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code}}

\usepackage[normalem]{ulem}

%------------------------------------------------------------------------------------------------------------%
\begin{document}

\title{A Short Guide To Modular Functors, Anyons, etc.}

\author{Simon Burton}
\affiliation{Centre for Engineered Quantum Systems, School of Physics, 
The University of Sydney, Sydney, Australia}
%\author{Courtney G.\ Brell}
%\affiliation{Institut f\"{u}r Theoretische Physik, Leibniz Universit\"{a}t Hannover, 
%Appelstra\ss{}e 2, 30167 Hannover, Germany}
%%\affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada}
%\author{Steven T.\ Flammia}
%\affiliation{Centre for Engineered Quantum Systems, School of Physics, 
%The University of Sydney, Sydney, Australia}

\date{\today}

\maketitle

% CUT HERE

%------------------------------------------------------------------------------------------------------------%
% Macros
%------------------------------------------------------------------------------------------------------------%

\newcommand{\Eref}[1]{Eq.~(\ref{#1})}
\newcommand{\Fref}[1]{Fig.~\ref{#1}}
\newcommand{\Aref}[1]{Appendix~\ref{#1}}

\newcommand{\e}{\mathrm{e}}
\newcommand{\vac}{\mathbb{I}}

\newcommand{\ket}[1]{|{#1}\rangle}
\newcommand{\expect}[1]{\langle{#1}\rangle}
\newcommand{\bra}[1]{\langle{#1}|}
\newcommand{\ketbra}[2]{\ket{#1}\!\bra{#2}}
\newcommand{\braket}[2]{\langle{#1}|{#2}\rangle}
\newcommand{\proj}[1]{\ketbra{#1}{#1}}

\newcommand{\cggb}[1]{\textcolor{blue}{#1}}
\newcommand{\simon}[1]{\textcolor{red}{#1}}
\newcommand{\stf}[1]{\textcolor{green}{#1}}

\newcommand{\F}{\mathscr{H}} % H or F ?
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\Hom}{{\mathrm{Hom}}}

\newcommand{\subsub}[1]{{\bf #1}}

%------------------------------------------------------------------------------------------------------------%

% CUT HERE
%\onecolumngrid
%\appendix
% CUT HERE

%The goal here is to describe the algorithm for
%computing charge contained in regions built from 
%arbitrary collections of tiles.
%To do this we first describe our approach
%to topological quantum field theory,
%then we discuss the data structure 
%(combinatorial curve diagrams) and the algorithm
%that operates on these structures.

%We give an informal introduction to
%anyonic topological quantum
%field theory in $(2+1)$-dimensions.
%See \cite{beverland2014} for a similar treatment.
%Note that these theories give rise to
%\emph{doubled} anyonic charges, and so
%the Fibonacci example in the main text simulates
%one half of such a system. % MEH!

%\section{A TQFT warmup}
%
%In two spatial dimensions, particle exchange is
%captured by the braid group.
%World lines of such particles 
%become tangled (braided) in $(2+1)$-dimensions.
%For example, three particle statistics is captured
%by the braid group on three strands $B_3.$
%This group is generated by elements $\sigma_1$
%and $\sigma_2$ which we represent pictorially as:
%\begin{center}
%\includegraphics[]{pic-braid-group.pdf}
%\end{center}
%
%These pictures make clear how the group
%multiplication works, for example:
%\begin{center}
%\includegraphics[]{pic-braid-group-1.pdf}
%\end{center}
%\begin{center}
%\includegraphics[]{pic-braid-relation.pdf}
%\end{center}
%
%
%These diagrams are to be understood up to
%continuous deformation of the ambient space.
%That is, we allow the ambient $(2+1)$-dimensional
%space with these worldlines subtracted to be continuously
%deformed.
%At the top and bottom of this space is 
%a $2$-dimensional space (a disc) with holes in it.
%Such a closed disc with $n$ holes we denote as $D_n.$
%So this is how we arrive at modelling the system as
%a disc with holes in it.
%The observables of the system measure charge within
%a region bounded by a directed closed curve.
%\begin{center}
%\includegraphics[]{pic-observable.pdf}
%\end{center}
%
%The defining feature of an Abelian anyon theory
%is that the state is completely determined once
%we measure the charge of each hole.
%In the language of the toric code (homology),
%logical operators (1-chains)
%cancel where they overlap
%with opposite orientation:
%\begin{center}
%\includegraphics[width=0.4\columnwidth]{pic-abelian.pdf}
%\end{center}
%
%This is not at all the case in general;
%for non-Abelian theories there can be extra
%degrees of freedom associated with these
%observables. For example, in
%a system supporting Fibonacci anyons,
%we can have two Fibonacci anyons with total
%charge either vacuum or Fibonacci:
%\begin{center}
%\includegraphics[]{pic-fusion.pdf}
%\end{center}
%so the state space of two fibonacci anyons
%is $2$-dimensional.
%Such a space associated with observing total charge
%of multiple anyons is called the \emph{fusion} space
%of those charges.
%
%These observables satisfy various relations,
%but in particular, non-overlapping observables commute.
%So if we nest a maximal set of these observables together
%we can pin-down a basis for the fusion space.
%Such a nesting is tree-like, and if we confuse the distinction
%between holes and observables, this gives rise to the
%fusion tree notation.
%\begin{center}
%\includegraphics[]{pic-tree-0.pdf}\includegraphics[]{pic-tree-1.pdf}
%\end{center}
%
%Given a disc with $n$ holes, we define the \emph{mapping
%class group} $MCG(D_n)$ as the group of topological
%symmetries (homeomorphisms) of the space $D_n,$
%modulo continuous deformations (isotopy).
%Such symmetries we require to fix the boundary
%of the disc, but not necessarily to fix the holes.
%Elements $f\in MCG(D_n)$ will also act on anything that
%resides in $D_n.$ 
%In particular, if we draw a line
%connecting the holes:
%\begin{center}
%\includegraphics[]{pic-twist.pdf}
%\end{center}
%
%Such an embedding $c : [0, 1] \to D$ with $c(0), c(1) \in \partial D$
%and touching all holes in $D_n$ we call a \emph{curve diagram}~\cite{Dehornoy2002},
%(or just a \emph{curve} when the context is clear).
%
%We can think of braids acting on states in a Schrodinger picture,
%or alternatively, elements of the mapping class group acting on
%observables in a Heisenberg picture:
%\begin{center}
%\includegraphics[]{pic-interaction.pdf}
%\end{center}
%
%We would hope that the groups $B_n$ and $MCG(D_n)$ are
%isomorphic, and this is indeed the case~\cite{Kassel2010}.
%One can see this as follows. Dragging the space $D_n$ along
%a braid creates a deformation, the end point of which is a
%homeomorphism in $MCG(D_n).$ Going the other direction,
%given $f\in MCG(D_n)$ and a curve diagram $c,$ we think of
%pulling the ends of $f\circ c$, thereby moving (braiding) the holes,
%until we are back at the original curve $c.$
%
%%This discussion makes it clear we have picked out a
%%specific curve $c$ that we use as a reference point for
%%other curves. 
%
%The importance of this isomorphism: the simulation
%algorithm calculates outcomes of observations. This
%boils down to a change of basis, to one that includes
%the required observable.
%$F$-moves allow us to re-associate observables along
%a curve diagram. The mapping class group acts
%transitively on curve diagrams (\emph{why??}).

%
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
%

%\section{A physicist's primer on the description of (2+1)TQFTs}\label{secAbstract}

%\cggb{I reworded a few comments that I thought were a bit flowery for a technical appendix.}

In this section we will describe abstractly the theory of two-dimensional topologically ordered systems
with anyonic excitations.
There are two main approaches to defining these,
one being more algebraic and the other more topological.

The algebraic side is known to mathematicians as the study of braided
tensor categories, or more specifically, modular tensor categories.
This algebraic language appears to be more commonly used 
in the physics literature~\cite{Kitaev2006}.
Such algebraic calculations can be interpreted as
manipulations of string diagrams~\cite{Baez2010},
or \emph{skeins}, which begins to hint at
how knot theory and topology comes into play.

Coming from the other direction, one starts with
a topological space (of low dimension) and attempts
to extract a combinatorial or algebraic description of how this
space can be built from joining smaller (simpler) pieces together.
%This is perhaps more difficult to grapple with.
These topologically rooted constructs are known as modular functors, 
or the closely related topological quantum field theories (TQFT's).
%The much older study of Homology also extracts algebraic
%information out of topological spaces, but

It is not obvious a priori that these two approaches -- algebraic and topological -- should meet, hinting at a deep underlying structure.
%That these two approaches -- algebraic versus topological -- meet is one of the great
%miracles of modern mathematics and physics.

%There is somewhat of a gap between the algebraic/skein-theoretic
%approach and the topological approach

Modular functors can be constructed from skein theory.
In the physics literature, 
this appears as skeins growing out of manifolds \cite{Pfeifer2012},
or as motivated by renormalization group considerations \cite{Levin2005}.
A further physical motivation is this: if a skein 
is supposed to correspond to the $(2+1)$-dimensional
world-lines of particles
as in the Schr\"{o}dinger picture,
modular functors would
correspond to the algebra of observables, as in
a Heisenberg picture.

In the physics literature, modular functors are
explicitly used in Refs.~\cite{Freedman2002, Freedman2002simulation, Beverland2014, Kitaev2006topo} (in some of these references modular functors are simply called TQFTs).
%Also, \cite{Beverland2014} and \cite{Kitaev2006topo}
%use the language of modular functors but they call them TQFT's.
%This is in fact reasonable because a modular functor can be
%seen as part of a TQFT, but is quite confusing to the
%novice who attempts to delve into the mathematical literature.

The definition of a modular functor appears to
be well motivated physically.
Unfortunately, there are many such definitions
in the mathematical literature 
\cite{Walker1991,Turaev1994,Bakalov2001,Tillmann1998}.
According to \cite{Bartlett2015} section 1.2 and 1.3,
there are several open questions involved in 
rigorously establishing the connection between these different axiomatizations.
%In particular, what physicists call anyon theory,
%and mathematicians call a modular tensor category,
Furthermore, the concept of modular tensor category 
has not been established to correspond exactly
(bijectively) to any of these modular functor variants. 
We try not to concern ourselves too much with these details, 
but merely note these facts as a warning to the reader
who may go searching for the ``one true formulation'' of
topological quantum field theory.

Of the many variants of modular functor found in the literature,
one important distinction to be made is
the way anyons are labeled.
In the mathematical works \cite{Turaev1994, Bakalov2001, Tillmann1998} 
we see that anyons are allowed to have superpositions
of charge states. 
However, in this work we restrict anyons to have
definite charge states, as in \cite{Walker1991,Freedman2002simulation,Beverland2014}. 
This seems to be motivated physically as such configurations
would be more stable. % \simon{citation?}.

In this section we will sketch how a 
braided tensor category arises from a modular functor.
In the mathematical literature,
this is covered in \cite{Turaev1994,Tillmann1998,Bakalov2001}
but as we just noted they use a different formulation for a
modular functor.
%The much more ambitious task of deriving a modular
%functor from a braided tensor category is

%Turaev derives a ribbon category
%from his definition of a modular functor, but this
%definition is different to the one given here 
%and is not known to be equivalent.
%Our definition is based on \cite{Walker1991},
%Walker \cite{Walker1991}
%(and others \cite{Bakalov2001}) perform the much more
%difficult task of deriving a modular functor from
%an appropriate braided tensor category,
%but do not seem to say much about going in the other direction.

%As in algebraic topology, we wish to extract
%algebraic information about topological objects.
%This can be viewed as a kind of representation theory
%of topological objects: diffeomorphisms of surfaces.

%\begin{quotation}
%``People these days have a tendency 
%to actually define a subfactor as being some kind of
%tensor category.
%But these guys [subfactors] are the algebras of observables
%of your physical system, and if you want to
%ignore them and throw them out then you strongly
%risk throwing out the baby with the bathwater.''
%- Vaughan Jones~\cite{Jones2015}
%\end{quotation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%

\subsection{Topological Exchange Statistics}

In this section we try to motivate 
the formalism of modular functor presented
below.
Our focus will be to show some of the close connections between
the algebraic and topological approaches to
particle exchange statistics.

In three spatial dimensions, the process of winding one
particle around another, a \emph{monodromy}, is topologically trivial.
This is because the path can be deformed back to the
identity; there is no obstruction:
\begin{center}
\includegraphics[]{pic-monodromy3d.pdf}
\end{center}
The square root of this operation is a swap:
\begin{center}
\includegraphics[]{pic-swap.pdf}
\end{center}
For identical particles this is a symmetry of the system. \cggb{What does symmetry mean here? Since a swap of non-bosons will pick up a phase.}
Continuing with this line of thought 
leads to consideration of the \emph{symmetric group}
on $n$ letters, $S_n$. 
This group is generated by the $n-1$ swap operations
$s_1,...,s_{n-1}$ that obey the relations
\begin{align*}
    s_i^2 &= 1, \\
    s_i s_j &= s_j s_i \ \ \ \mbox{for}\ \ |i-j|>1,\\
    s_i s_{i+1} s_i &= s_{i+1} s_i s_{i+1} \ \ \ \mbox{for}\ \ 1\le i \le n-2.
\end{align*}
This group acts on the statespace of $n$ particles $\F_n$
via unitaries $U(\F_n)$:
$$
    \Phi : S_n \to U(\F_n).
$$

When the above monodromy is constrained to two dimensions
we can no longer deform this process to the identity:
\begin{center}
\includegraphics[]{pic-monodromy2d.pdf}
\end{center}
and so in two dimensions we cannot expect a swap to square to the identity.
To see this more clearly,
we consider the world-lines of these particles.
Here we show three particles undergoing an exchange and then
returning to the original location:
\begin{center}
\includegraphics[]{pic-braid-worldlines.pdf}
\end{center}
Note that if we allow the particles to move in one extra
dimension then we can untangle these braided world lines.
%The question is, how has the wavefunction of the system
%changed from $t_0$ to $t_1$?
The question is now, what is the group that acts on the
state space from $t_0$ to $t_1$?
Examining the structure of these processes more closely,
we see that we can compose them by sequentially performing
two such braids, one after the other:
\begin{center}
\includegraphics[]{pic-braid-compose.pdf}
\end{center}
And, by ``reversing time'', we can undo the effect of
any braid:
\begin{center}
\includegraphics[]{pic-braid-inverse.pdf}
\end{center}
This shows that these processes do form a group,
known as the \emph{braid group.}
For $n$ particle worldlines we denote this group as $B_n.$
For identicle particles this group acts as symmetries of the
state space:
%Now we would expect to see an action on the statespace $\F_n:$
$$
    \Phi : B_n \to U(\F_n).
$$

What we have given is a topological description of the group $B_n$.
More formally, we can describe these braid world lines as
paths in the \emph{configuration space} of $n$ points.
\newcommand{\Conf}{\mathcal{C}}
\newcommand{\UConf}{\mathcal{UC}}
This space is defined as the product of
a two dimensional space $M$ for each point, minus the subspace where points overlap:
$$
    \Conf_n = \bigl( \prod_{1}^{n} M \bigr) - \Delta, \ \ 
    \Delta = \{(x_1, ..., x_n) | x_i = x_j \ \ \mbox{for some} \ \ i\ne j \}.
$$
Because we are considering identicle particles (so far)
we use the \emph{unlabelled configuration space}
$\UConf_n$ which is the quotient of $\Conf_n$ by the natural action of the
permutation group $S_n:$
\cggb{I was a bit confused by when we care about unlabelled configuration space and when we care about the labelled configuration space. What if we have some but not all particles identical? Do the two formalisms unify by considering some subgroups of the permutation group that preserve particle label or something?}
$$
    \UConf_n = \Conf_n / S_n.
$$
The \emph{geometric braid group} as we have so far informally described it 
can now be rigorously defined as the fundamental group:
$$
    B_n = \pi_1 ( \UConf_n, x )
$$
where $x$ is some reference configuration in $\UConf_n.$
See \cite{Ghrist2014} for further discussion.

%The \emph{braid group} on $n$ strands is denoted $B_n.$
%This group can also be described purely algebraically.
This group also has a purely algebraic description via
generators and relations, as was shown by Artin in 1947, \cite{Artin1947,Birman1974}.
$B_n$ has $n-1$ generators $\sigma_1,..,\sigma_{n-1}$ that satisfy
the following relations:
\begin{align*}
    \sigma_i \sigma_j &= \sigma_j \sigma_i \ \ \ \mbox{for}\ \ |i-j|>1,\\
    \sigma_i \sigma_{i+1} \sigma_i &= \sigma_{i+1} \sigma_i \sigma_{i+1} \ \ \ \mbox{for}\ \ 1\le i \le n-2.
\end{align*}
So these relations are the same as for $S_n$ above, except 
we no longer have the relation $\sigma_i^2 = 1.$

%The easiest way to understand these relations is to consider the
It is easy to see that the geometric braid group satisfies these
relations. Here we show the braids corresponing to the generators $\sigma_i:$
\begin{center}
\includegraphics[]{pic-braid-sigma.pdf}
\end{center}
So that 
$\sigma_i \sigma_j = \sigma_j \sigma_i \ \ \ \mbox{for}\ \ |i-j|>1$
because the two braids are operating on disjoint strands.
The second relation is also easy to see:
\begin{center}
\includegraphics[]{pic-braid-YB.pdf}
\end{center}

There is another important geometric representation of
the braid group which is purely two-dimensional.
%We denote the two-dimensional space 
%The two dimensional space within which the particles reside we denote 
We pick an $n$-point finite subset $Q_n \subset M$
and consider diffeomorphisms \cggb{why diffeomorphisms and not homeomorphisms?} $f : M \to M$
that map $Q_n$ to itself.
The \emph{mapping class group} of $M$ relative to $Q_n$
is the set of all such diffeomorphisms up to an equivalence relation $\sim_{\mbox{iso}}$:
$$
    MCG(M, Q_n) = \{ f : M \to M \ \ \mbox{such that}\ \ f(Q_n)=Q_n \} / \sim_{\mbox{iso}}
$$
The equivalence relation $\sim_{\mbox{iso}}$ is called \emph{isotopy}
which allows for any continuous deformation of $f:M\to M$ that
fixes each point in $Q_n.$
Each generator $\sigma_i$ of the braid group is found in $MCG(M, Q_n)$
as a \emph{half-twist} that swaps two points $i, i+1 \in Q_n$:
\begin{center}
\includegraphics[]{pic-halftwist.pdf}
\end{center}
In order to show
the action of
this half-twist we have 
decorated the manifold with
a a checkered pattern,
but there is a more important
object that lives on the manifold
itself.
An \emph{observable} is a simple
closed curve in $M$ that does
not intersect $Q_n.$
Such a closed curve is called an
observable because these will be
associated to measurements
that measure the charge on the
interior of the curve.
The importance of understanding the
braid group as identicle to the mapping class group
is now manifest:
whereas geometric braids act on states
as in a Schr\"{o}dinger picture,
elements of the mapping class group
act on the observables as in
a Heisenberg picture.
\begin{center}
\includegraphics[]{pic-heisenberg.pdf}
\end{center}
This diagram should give the reader some idea as
to why these two definitions of the braid group are
equivelant, but the actual proof of this is somewhat involved.
We refer the reader to \cite{Kassel2010} for an excellent contemporary
reference that fills in these gaps.

%We have given three different descriptions of the braid group, and
%part of the depth of the subject comes from the fact that there are
%so many alternative perspectives on these groups.

The definition given above for the geometric braid group
and the mapping class group make sense for any two dimensional
manifold $M$ but for concreteness we consider $M$ to be
a flat disc. 
The corresponding algebraic definition of the braid group
will in general be altered depending on the underlying manifold
$M.$

So far we have been studying the exchange statistics
for $n$ identical particles. Without this restriction, one needs to
constrain the allowed exchange processes so as to preserve particle type.
For example, if all particles are different we would use the
\emph{pure braid group} $PB_n.$
The geometric description of
this group is as the fundamental group of the labelled
configuration space
$$
    PB_n = \pi_1 ( \Conf_n, x ).
$$
Loops in $\Conf_n$ correspond to braids where each strand returns
to the point it started from.
The algebraic description of this group is somewhat complicated and
we omit this.
In terms of the mapping class group, we can describe $PB_n$
as the \emph{pure mapping class group}:
$$
    PMCG(M, Q_n) = \{ f : M \to M \ \ \mbox{such that}\ \ f(x)=x \ \ \mbox{for}\ x\in Q_n\} / \sim_{\mbox{iso}}.
$$
%we can write generators of this group in terms of Dehn twists which
%we discuss below.

One further complication arises when particles have a rotational
degree of freedom: ie., they can be rotated by $2\pi$ in-place and
this effects the state of the system.
To capture this action, we use the \emph{framed braid group} $FB_n.$
This group can be presented algebraically using the same generators
and relations as for the braid group $B_n,$ along with
``twist'' generators $\theta_i$ for $i=1,..,n.$
These must satisfy the further relations
\begin{align*}
    \theta_i \theta_j &= \theta_j \theta_i \\
    \theta_i\sigma_j &= \sigma_j\theta_i 
    \ \ \mbox{if}\ \ i<j \ \ \mbox{or}\ \ i\ge j+2\\
    \theta_{i+1}\sigma_i &= \sigma_i\theta_i \\
    \theta_{i}\sigma_i &= \sigma_i\theta_{i+1}.
\end{align*}

Here we show four 
geometric approaches to representing a twist.
Anyone that has struggled to untangle their headphone cable
will immediately see what is going on here.
On the left we have a loop; it is not a braid because it
travels backwards in time.
If we pull on this loop to make it straight, we introduce a twist.
This is shown in the next figure, 
where we show a \emph{framing} which is a non-degenerate \cggb{What's a non-degenerate vector field? What goes wrong if its degenerate?}
vector field along the world-lines of a braid.
The initial and final vectors in the vector field must be the same.
In the next figure we show a \emph{ribbon}:
instead of point particles we have short one-dimensional curves in $M$.
%This is another way to encode a twist without using the differential
%structure of $M.$
On the right the particle is represented as a boundary
component of $M$ with a distinguished point.
In this picture the world-line looks like a tube.
%It is not difficult to see that these 
All these representations of twists carry
essentially the same information.
\begin{center}
\includegraphics[]{pic-framed.pdf}
\end{center}
In the sequal we will stick
to thinking of particles as boundary
components because this fits well
with the way we are formulating 
observables as simple closed curves in $M$.
%More concretely,
%we augment the configuration space
%with tangent vectors. For each point $x_i$
%in a configuration $(x_1,...,x_n)\in \prod M$ we
%attach a non-zero tangent vector $v_i\in T_{x_i}M.$
%In terms of a mapping class group, we will
%consider not just a manifold $M$ with
%distinguished points $Q_n,$ but a manifold with $n$ disjoint
%boundary componends, or ``holes''.
%Each of these boundary components comes
%with a distinguished point.

At this point in the narative we are 
close to our next destination.
All of these considerations,
of framed or unframed, 
labelled or not,
with possibly different underlying manifolds,
together with observables,
is mean to
be captured by the formalism of a modular functor which we turn to next.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%

\subsection{Modular Functors}

We list the axioms for a 
\emph{2-dimensional unitary topological modular functor}.
 % abbreviated as \emph{MF}.
%There are quite alot of details that we leave out,
%%For the details of this construction, see
%see
%\cite{Turaev1994}, \cite{Walker1991} or \cite{Bakalov2001}.
%For a more pedestrian treatment, see \cite{Freedman2002simulation} or \cite{Beverland2014}.

For our purposes a \emph{surface} will be a compact
oriented $2$-dimensional differentiable manifold with boundary. % smooth or topological ?
We will not require surfaces to be connected.
%Each boundary component is oriented (either explicitly or
%otherwise by using the orientation of the manifold)
By a \emph{hole} of $M$ we mean a component of its boundary. % $\partial M$.
Each hole will inherit the manifold orientation,
contain a distinguished \emph{base point},
and be labeled with
%an element from a finite set $\mathbb{A}=\{1, a, b, c ...\}.$
an element from a fixed finite set $\A.$
This is the set of ``anyon labels'', and comes
equiped with a vacuum element $\vac$ 
and an involution $\ \widehat{}\ $ such that $\widehat{\vac}=\vac.$
The involution maps an anyon label to the ``antiparticle'' label.

We will mostly be concerned with planar such
surfaces, that is, a \emph{disc} with holes removed from the
interior.
%\cggb{Do we actually restrict to considering only such surfaces?}
%\simon{Only when we get to standard surfaces and POPs...}
Such surfaces will be given a clockwise 
orientation, which induces a counterclockwise orientation on
any \emph{interior} hole and a clockwise orientation
on the \emph{exterior} hole.
\begin{center}
\includegraphics[]{pic-disc.pdf}
\end{center}
Although it helps to draw such a surface as a disc with holes,
we stress that there is no real distinction to be made between
interior holes and the exterior hole.
That is, 
a disc with $n$ interior holes is (equivalent to) a sphere with $n+1$ holes.
We merely take advantage of the fact that a sphere with at least one hole
can be flattened onto the page by ``choosing'' one of the holes to
serve as the exterior hole.

By a \emph{map of surfaces} $f:M\to N$ we mean 
a diffeomorphism that preserves
manifold orientation, hole labels, and base points.
%\cggb{If we require that the map preserves base points and so on, are we restricting to maps between manifolds with the same number of holes?}
%\simon{Yes, a diffeomorphism is also a homeomorphism, so these manifolds are
%topologically equivalent.}
Note that we also deal with maps of various other objects
(vector spaces, sets, etc.)
but a map of surfaces will have these specific
requirements.

%By an \emph{isotopy} of $f:M\to N$ we mean a 
%map $g:M\to N$
%that is a continuos deformation of $f.$
Two maps of surfaces $f:M\to N$ and $f':M\to N$
will be called \emph{isotopic}
when one is a continuous deformation of the other.
In detail,
we have a continuously
parametrized family of maps $f_t:M\to N$ for $t\in [0, 1]$
such that $f_0=f,\ f_1=f'$
and the restriction of $f_t$ to the 
set of marked points $X\subset\partial M$ is constant:
$f_t|_{X} = f|_{X}$ for $t\in [0, 1].$
%and the restriction of $f_t$ to the boundary is constant:
%$f_t|_{\partial M} = f|_{\partial M}$ for $t\in [0, 1].$
Such a family $\{f_t\}_{t\in [0,1]}$ is called an \emph{isotopy}
of $f.$
This is an equivalence relation on maps $M\to N$, and the equivalence
class of $f$ under isotopy is called the \emph{isotopy class} of $f.$ \cggb{I didn't quite see why this more formal definition is the same as equivalent up to continuous deformation. Why can I restrict to maps where the base points are fixed along the whole path?}

A \emph{modular functor} $\F$ associates to every
surface $M$ a finite dimensional complex
vector space $\F(M)$, called the \emph{fusion space} of $M$.
For each map $f:M\to N$
the modular functor associates a
unitary transformation $\F(f) : \F(M)\to\F(N)$
that only depends on the isotopy class of $f.$
Functoriality requires that $\F$
respect composition of maps.

We have the following axioms for $\F.$

{\bf Unit axioms.}
The fusion space of an empty surface is one dimensional, 
$\F(\phi) \cong \C.$ % preserves the identity of tensor
%\cggb{Does a modular functor have to be over $\C$?}
%\simon{No, mathematicians do this over any ring $k.$}
For $M_a$ a disc with boundary label $a$ we have
$\F(M_\vac)\cong \C$ and 
$\F(M_a)\cong 0$ for $a\ne \vac.$
For an annulus $M_{a,b}$ with boundary labels
$a, b$ we have
$\F(M_{a,\widehat{a}})\cong \C$ and 
$\F(M_{a,b})\cong 0$ for $a\ne \widehat{b}.$

{\bf Monoidal axiom.}
The disjoint union of two surfaces $M$ and $N$ 
is associated with
the tensor product of fusion spaces:
$$
    \F(M\amalg N) \cong \F(M)\otimes \F(N).
$$
This is natural from the point of view of quantum
physics, where the Hilbert space of two disjoint
systems is the tensor product of the space for
each system.

{\bf Gluing axiom.}
Denote a surface $M$ with (at least) two holes
labeled $a, b$ as $M_{a,b}$. 
If we constrain $b=\widehat{a}$ 
then we may \emph{glue} these two holes together
to form a new surface $N$.
%Let $N$ be the surface obtained from $M$ by gluing
%these two holes together.
%By this we mean there is a homeomorphism from one
To construct $N$ we choose a diffeomorphism from one
hole to the other that maps base point to base point 
and reverses orientation.
Identifying the two holes along this diffeomorphism
gives the glued surface $N$.
(There is a slight technicality in ensuring that $N$ is
then differentiable, but we will gloss over this detail.)
The image of these holes in $N$ we call a \emph{seam}.
%Gluing must reverse the orientation of the two holes
%as well as identifying their base points.
The fusion space of $M_{a,\widehat{a}}$ then embeds unitarily in the fusion
space of $N$.
Moreover, there is an isomorphism called
a \emph{gluing map}:
$$
    \bigoplus_{a\in\A} \F(M_{a,\widehat{a}}) \xrightarrow{\cong} \F(N)
$$
and this isomorphism depends only on the isotopy class of 
the seam in $N.$
%\simon{say something about isotopy of gluing}

{\bf Unitarity axiom.}
Reversing the orientation of the surface $M$
to form $\overline{M}$ we get the dual of the fusion space:
$\F(\overline{M})=\F(M)^*.$
%\simon{i don't think we use this for anything}

\subsub{Compatibility axioms.}
%We have left out various compatibility requirements of the axioms.
Loosely put, we require that the above operations play nicely together,
and commute with maps of surfaces.
For example,
a sequence of gluing operations 
applied to a surface can
be performed regardless of the order (gluing is associative)
and we require the various gluing maps for these operations to similarly agree.
For another example, we require $\F$ to respect that gluing
commutes with disjoint union.
%performing a gluing on $M$ and then forming $M\amalg N$
%produces the same surface as forming the disjoint union and
%then gluing the 
%\cggb{I guess we should try to keep a consistent level of precision, and so probably be more explicit here.}
%\simon{I agree it is a bit jarring to suddenly switch to being more informal...}

\subsub{Observables.}
The seam along which gluing occurs can be associated
with an observable as follows.
We take a gluing map $g$ and projectors $P_a$ onto the
summands in the above direct sum:
$$
    P_a: \bigoplus_{b\in\A} \F(M_{b,\widehat{b}}) \to \F(M_{a,\widehat{a}}).
$$
then the observable will be the set of operators 
$\{P_a g^{-1}\}_{a\in\A}.$
For each $a\in A$
we call the image of $P_a$ 
a \emph{charge sector} for that observable.
Note that in the glued surface $N$ the seam has no
preferred orientation (or base point).
If we choose an orientation 
for the seam this corresponds to choosing one of the
two boundary components in the original surface $M_{a,\widehat{a}}.$
If these boundary components come from disconnected components of 
$M_{a,\widehat{a}}$ the seam cuts $N$ into two pieces and the
orientation chooses an \emph{interior:}
following the orientation around the seam presents
the interior to the left.
%The projectors associated to each cuff commute.
%Non-overlapping observables commute.
We intentionally confuse the distinction between an
observable as a set of operators,
and the associated seam along which gluing occurs.
%Any simple closed curve within the interior of $M$
%can serve as the seam along which gluing occurs...
%If we now take $M$ to be an arbitrary surface, and $\gamma$ an
%observable on $M,$
%we can write $M$ as the gluing of another surface $N$...
%\simon{XXX}

\subsub{Consequences of axioms.}
A common operation is to glue two separate surfaces.
We can do this by first taking disjoint union (tensoring
the fusion spaces)
and then gluing.
Here we show this process applied to two surfaces $M$ and $N$. 
\begin{center}
\includegraphics[]{pic-glue.pdf}
\end{center}
We display the surface $N$ with the $\widehat{a}$
boundary on the outside, 
to show more clearly how $N$ fits into $M$.
In the glued surface we
indicate the placement of $M$ and $N$ and the seam
along which gluing occurred,
as well as the identification of base points.

We note two other consequences of the axioms.
A hole of $M$ labeled with $\vac$ can be replaced with a disk (by gluing)
and this does not change the fusion space of $M.$
That is, a hole that carries no charge can be ``filled-in''.
And, the dimensionality of the fusion space of a torus is the
cardinality of $\A.$
This can be seen by gluing one end
of an annulus (cylinder) to the other.

\subsub{Fusion.}
When a surface can be presented as the gluing of
two separate surfaces, we have projectors onto the
fusion space of either glued surface:
\begin{center}
\includegraphics[]{pic-fuse.pdf}
\end{center}
In this case, we define 
the operation of \emph{fusion} to replace the interior
of an observable by a single hole.
This is an operation on the manifold itself,
and we will only do this when the interior piece is a
disc with zero or more holes.

%
%We are thinking of the holes as modelling particles
%known as \emph{anyons}.
%We have defined a collection of observables.
%We think of these as measuring the total charge of the
%anyons within a simple closed curve.
%The measurement process associated to these observables
%we call \emph{fusion}.
%When the observable is understood,
%we call this fusion of anyons.
%Such a measurement applies a projector to a state in
%some fusion space $\F(M),$ and furthermore, we modify
%the manifold $M$ by excising the interior of the observable
%to produce another manifold $N.$
%This gives a state in the fusion space $\F(N).$

%\subsub{Pair-of-pants.}
\subsub{F-move.}
The fusion space of the disc and annulus are
specified by the axioms, and we define the fusion
space of the disc with two holes, or \emph{pair-of-pants} as:
\begin{center}
\includegraphics[]{pic-pop.pdf}
\end{center}

The \emph{$F$-move}
is constructed from two applications of a
gluing map (one in reverse) as the following commutative diagram shows:
\begin{center}
\includegraphics[]{pic-glue-fmove.pdf}
\end{center}
%\cggb{Is it easy to show that such an F-move can be guaranteed to exist and be unique for a given modular functor?}
%\simon{An F-move *is* two applications of a gluing map (where one is reversed).. these maps are given in the axioms. There's no trickery involved.}
Here we have a surface $M^{abc}_d$ with 
four labeled boundary components, as well as two separate
ways of gluing pairs-of-pants to get $M^{abc}_d.$
We can also write this out in terms of the fusion spaces of pair-of-pants:
$$
    F^{abc}_d : \bigoplus_{x\in\A} V^{ab}_{\widehat{x}}\otimes V^{xc}_d 
        \to \bigoplus_{y\in\A} V^{ay}_d\otimes V^{bc}_{\widehat{y}}.
$$
By using gluing, and summing over charge sectors,
we can extend this operation %to more complicated manifolds
to apply where any of the boundary components $a, b, c$ or $d$ are merely 
seams in a larger manifold.
%\simon{tensor with identity to extend this map under gluing}

%\simon{***at this point we specialize to considering only discs with holes***}

\subsub{POP decomposition.}
%The reverse process of cutting a surface up
%into pair-of-pants induces a direct sum decomposition
%of the fusion space.
Given a manifold $M$ which is
a disc with two or more holes, 
we show how to present $M$ as the gluing of various
pair-of-pants. Such an arangement will be termed a \emph{POP decomposition.}
(We refer to \cite{Ivanov2001} for more details on this construction,
and \cite{Ghrist2014} for a leisurely description of Morse theory.)
This will yield a decomposition of $\F(M)$ into a direct
sum of fusion spaces of pair-of-pants. % $V_{ab}^c$'s.
%The pair-of-pants can be found using Morse theory.
%We proceed using Morse theory.
%Note that we need $M$ to be a differentiable manifold for
%this to work.
The key idea is to choose a ``height'' function $h:M\to\R$
with some specific properties that allow us to
cut the manifold up along level sets of $h.$
First, we need that critical points of $h$ are isolated.
This is the defining condition for $h$ to be a \emph{Morse function}.
%Choose a Morse function (a generic ``height'' function) $h:M\to\R$
Also, we need that $h$ is constant on $\partial M,$
and the values of $h$ at different critical points are distinct.
Now choose a sequence of non-critical values $a_1<a_2<...<a_n$ in $\R$
such that every interval $[a_{i-1}, a_i]$ 
contains exactly one critical value of $h$ and the image
of $h$ lies within $[a_1, a_n].$
%cuts the manifold into pieces $f^{-1}[a,b]$.
Each component of $h^{-1}([a_{i-1}, a_i])$ is then either
an annulus, a disc, or a pair-of-pants depending on the index of (any)
critical point it contains.
We then re-glue any annuli or discs until there are no more of these
and we have only pair-of-pants. \cggb{Is this always possible? What if I have something like a cylinder? Then I just get a bunch of annuli however I cut.}
% note: we may still get annuli in a *component* of the pre-image.
\begin{center}
\includegraphics[]{pic-pants.pdf}\ \ \ \ \ \ \ \ \includegraphics[]{pic-pants-1.pdf}
\end{center}

Clearly such a POP decomposition is not unique,
and the goal here is to understand how to switch between decompositions,
and in particular, given an observable $\gamma$,
and a given POP decomposition, find a sequence
of ``moves'' such that $\gamma$ is in the resulting POP
decomposition:
\begin{center}
\includegraphics[]{pic-refactor.pdf}
\end{center}

One way to achieve this is via Cerf theory, which is the theory
of how one may deform Morse functions into other Morse functions
and the kind of transitions involved in their critical point structure.
This was the approach used in \cite{Freedman2002simulation}.
In this work we use a simpler method,
which is essentially the same as {skein theory.} \cggb{Is all this curve diagrams and refactoring theorem and and so on original work, or is it collecting known facts? If its original, this should be an independent paper because otherwise nobody from the math phys community will ever find it. Actually maybe in either case it should be an independent arxiv post at least so that more people find and learn from it.}
%Read on to find out how this works!
This is the {refactoring theorem} that we describe below.

\subsub{Dehn twist.}
Consider a surface $M_{a,\widehat{a}}$
with two boundary components, $a$ and $\widehat{a}.$
Let $f$ be a map $M_{a,\widehat{a}}\to M_{a,\widehat{a}}$
which performs a clockwise $2\pi$ full-twist or \emph{Dehn twist}.
Here we show the action of $f$ by highlighting the
equator of the annulus:
%line between the base points:
\begin{center}
\includegraphics[]{pic-dehn-twist.pdf}
\end{center}
We define the 
induced map on fusion spaces as $\theta_a := \F(f).$
Because $\F(M_{a,\widehat{a}})$ is one-dimensional
this will be multiplication by a complex number which we also
write as $\theta_a.$

If we now take $M$ to be an arbitrary surface, and $\gamma$ an
observable on $M,$ we can consider a neighbourhood of $\gamma$
which will be an annulus, and perform a Dehn twist there,
which we denote as $f_\gamma : M\to M.$
Writing $M$ as a gluing along $\gamma$ of another
manifold $N_{a,\widehat{a}},$
the action of $\F(f_\gamma)$ will decompose as a direct sum over charge 
sectors:
$$
\bigoplus_{a\in\A} \theta_a \F(N_{a,\widehat{a}}).
$$
%$$
%    \F(f_\gamma) : \bigoplus_{a\in\A}
%        \F(N_{a,\widehat{a}}) \to
%        \bigoplus_{a\in\A} \theta_a \F(N_{a,\widehat{a}})
%$$

\newcommand{\StdM}{M^{a_1...a_n}_{b}}

\subsub{Standard surfaces.}
For each $n=0,1,...$ and every ordered sequence of
anyon labels $a_1,...,a_n,b$ we choose a \emph{standard surface}.
This is a surface with
$n+1$ boundary components labeled $a_1,...,a_n,{b}$ 
which we denote $\StdM.$ 
For concreteness, we 
let this surface be the subset of
the complex plane defined by
$\bigl\{x\in\C \ \mathrm{st.}\  |x-\frac{1}{2}|\le \frac{1}{2}\bigr\}$
with $n$ discs
$\bigl\{x\in\C \ \mathrm{st.}\  |x-\frac{2i-1}{2n}|< \frac{1}{4n}\bigr\}_{i=1,...n}$
removed. \cggb{Why is this easier to describe on $\mathbb{C}$ rather than $\mathbb{R}^2$? If its all the same, I think it could be safer to rephrase on $\R^2$.}
We then label the interior holes $a_1,...,a_n$ in order of
increasing real coordinate, and the exterior hole is labeled ${b}$.
The base points are placed in the direction of the negative imaginary axis.
As a notational convenience we highlight the \emph{equator}
of the surface %$\StdM$ 
which is the intersection of
the real axis with the surface:
\begin{center}
\includegraphics[]{pic-disc-standard.pdf}
\end{center}

Each standard surface comes with a collection of
\emph{standard POP decompositions}:
these will be POP decompositions where we require each
observable to cross the
equator twice and have counterclockwise orientation.
Up to isotopy, a given standard surface will have only finitely many of these.
On a standard surface with three
interior holes there are two standard POP decompositions,
and one $F$-move that relates these.
On a standard surface with four interior holes there are five 
standard POP decompositions and five $F$-moves that relate these.
In this case the $F$-moves themselves satisfy an equation
that is a trivial consequence of the way we have defined $F$-moves.
%enforced by the axioms of the modular functor.
This is known as the pentagon equation, which we depict as
the following commutative diagram:
\begin{center}
\includegraphics[]{pic-pentagon.pdf}
\end{center}
We are now starting to confuse the notation 
for the topological space $M$ and the fusion space $\F(M).$
Also, each of these $F$-moves is refering to an isomorphism 
that is block decomposed according to the charge sectors 
of the indicated observables.

We define the vector spaces 
$ V^{a_1...a_n}_{b} := \F(\StdM).$ 
We now choose a basis for each of the
%$V^{ab}_c$ to be $\{v^{ab}_{c,\mu}\}_{\mu}.$
%$V^{a'_1a'_2}_{b'}$ to be $\{v^{a'_1a'_2}_{b',\mu}\}_{\mu}.$
$V^{a_1a_2}_{b}$ to be $\{v^{a_1a_2}_{b,\mu}\}_{\mu}.$
For every standard POP decomposition of $\StdM,$
we get a decomposition of 
$V^{a_1...a_n}_{b}$ into direct sums of various %$V^{a'b'}_{c'}.$
$V^{a'_1a'_2}_{b'}.$ 
This then gives a \emph{standard basis} of $V^{a_1...a_n}_{b}$
relative to this standard POP decomposition
using the corresponding  $\{v^{a'_1a'_2}_{b',\mu}\}_{\mu}$
for each of the $V^{a'_1a'_2}_{b'}.$ % $V^{a'b'}_{c'}.$
%\simon{...ugh}

Note that for any standard surface $\StdM$ 
and any choice of $k$ contiguous holes $a_j,...,a_{j+k-1}$
we can find an observable that encloses exactly these holes
in at least one of the standard POP decompositions of $\StdM.$

%We next define the gluing of two standard surfaces
We next show how to glue the exterior hole of
a standard surface $M$
to an interior hole of another standard surface $N.$
To do this within $\C$ we rescale and translate the two surfaces so
that the exterior hole of $M$ coincides with the interior hole of $N.$
At this point the union is not in general going to
produce another standard surface,
%However, we can ... \simon{fix this}
and so we remedy this by applying any isotopy within $\C$
that fixes the real axis while moving the surface to a standard surface. \cggb{Does "fix the real" axis here mean that it fixes every point on the real axis, or just maps the real axis to itself?}
%while moving the holes so as to produce
%a standard surface.

\subsub{Curve diagram.}
We next study maps from standard surfaces to arbitrary surfaces. \cggb{I was a bit confused what this means. Maps means between surfaces with the same holes and base points, right? So then don't we only care about maps from standard surfaces to standard surfaces? Is it maybe more like maps from equatorial curve diagrams on standard surfaces to arbitrary curve diagrams on standard surfaces that we want?}
The set of all maps from $\StdM$ 
to a surface $N$ will be denoted as $\Hom(\StdM, N).$ 
We call each such map a \emph{curve diagram},
or more specifically, a curve diagram on $N$.
The reason for this terminology is that we can reconstruct (up to isotopy)
any map $f:\StdM\to N$ from
the restriction of $f$ to the equator of $\StdM.$ \cggb{citation? or obvious?}
In other words, we can uniquely specify any map
$f:\StdM\to N$ by indicating the action of
$f$ on the equator. We take full advantage of this
fact in our notation: any figure of a surface
with a ``green line'' drawn therein is actually notating a 
diffeomorphism, not a surface!

Any curve diagram will act on a standard POP decomposition
of $\StdM$ sending it to a POP decomposition of $N.$
Surprisingly, the converse of this statement also holds:
any POP decomposition of $N$ (a disc with holes)
comes from some curve diagram
acting on a standard POP decomposition.
%\cggb{This is true for any $N$ that is homeomorphic to a punctured disc?}
%\simon{Right, I should be more clear about when exactly we specialize to discs.}
The proof of this is constructive, and we call this
the refactoring theorem below. \cggb{citation? or original work?} %\simon{XXX} 
%The proof of this is constructive and forms the heart of
%our algorithm below.

%\simon{show how to glue two curve diagrams together to get another curve diagram}
The operation of 
gluing of surfaces can be extended to gluing of curve diagrams as
long as we are careful with the way we identify along the seam:
the identification map needs to respect the equator of the curve
diagram. \cggb{Is respecting the equator the same as respecting whatever canonical curve diagram we choose?}

%Any curve diagram will send a standard POP decomposition
%of $\StdM$ to a POP decompositions of $N,$ and therefore
%(via $\F$) will also send the standard basis to a basis
%of $\F(N).$
%This is how to understand the sense in which a curve diagram 
%(together with a standard POP decomposition) 
%``picks out'' a basis of $\F(N).$
%Remarkably, the converse of this result also obtains

We note in passing two connections to the mathematical literature.
Such curve diagrams have been 
used in the study of braid groups \cite{Dehornoy2002}, and this
is where the name comes from, although our
curve diagrams respect the base points and so could be further
qualified as ``framed'' curve diagrams.
And, we note the similarity of curve diagrams and associated
modular functor 
to the definition of a planar algebra \cite{Jones1999},
the main difference being that planar algebras allow for 
not just two but any even number of curve intersections at each hole. \cggb{What's a planar algebra and is there an easier place for me to learn about it than from the Jones paper?}

\subsub{Z-move.}
We let $z$ be a diffeomorphism of standard surfaces 
$z : M^{a_1...a_n}_{b} \to  M^{a_2...a_n{b}}_{{a_1}}$
that preserves the equator.
(Considering the standard surface as a sphere with holes
placed uniformly around a great circle, $z$ is seen to
be a ``rotation''.)
This acts by pre-composition to
send a curve diagram $f\in \Hom(\StdM, N)$ to 
$fz \in \Hom(M^{a_2...a_n{b}}_{{a_1}}, N).$
This we call a $Z$-move of $f.$

In this way, any curve diagram can be seen as another
curve diagram that has a cyclic permutation of the labels of
the underlying standard surface.

\subsub{R-move.}
%This is a (collection of) linear operator(s)
Given anyon labels $a, b$ and $c$, and arbitrary
surface $N,$
we now define the following map of curve diagrams on $N:$
$$R^{ab}_c: \Hom(M^{ab}_c, N)\to \Hom(M^{ba}_c, N).$$
%\simon{do we need to restrict the term ``map'' as only applying to maps of surfaces?}
This map works by taking a curve diagram 
$f:M^{ab}_c\to N$ to the composition $f\sigma$ where
$\sigma:M^{ba}_c\to M^{ab}_c$
is a counterclockwise ``half-twist'' map that exchanges
the $a$ and $b$ holes.
Here we show the action of $R^{ab}_c$ on one particular curve diagram:
\begin{center}
\includegraphics[]{pic-rmove-1.pdf}
\end{center}
Such an application of $R^{ab}_c$ to a particular
curve diagram we call an \emph{R-move.}
As noted above, a curve diagram serves to pick out
a basis for the fusion space, and the point of this $R$-move is
to switch between different curve diagrams for the same surface.
This is highlighted to draw the readers attention to
the fact that the $R$-move does not swap the labels on the holes:
the surface itself stays the same.
%\cggb{Should the $a$ and $b$ labels be swapped on the second diagram?}
%\simon{No. This is quite tricky and took me months to work out (ouch) so take care...}

%\simon{Extend $R$-move under gluing.}
As we extended Dehn twists under gluing,
and $F$-moves under gluing,
we also do this for $R$-moves.
%Given any pair-of-pants in $M$ ... \simon{keep going}

%\simon{When do we start confusing the distinction between
%topological operations and the corresponding vector space
%operation via $\F$ ?}

\subsub{Skeins.}
The preivious figure can be seen as a ``top-down'' view of the
following three dimensional arrangement:
%At this point we can show the relation to skein theory:
\begin{center}
\includegraphics[]{pic-rmove-skein.pdf}
\end{center}
This figure is intended to be topologically
the same as the previous flat figure,
with the addition of a third dimension,
and the $c$ boundary has been shrunk.
Also note thin black lines
connecting the base points.
The black lines do not add any extra structure, they can
be seen as a part of the hexagon cut out by
the green line and boundary components.
But notice this: the black lines are ``framed'' by the green lines. 
These are the ribbons used in skein theory!
Note that all the holes are created equal: there is
no distinction between ``input'' holes and ``output'' holes
(as there is with cobordisms or string diagrams.)

%We can get monodromy operators, and theta operators...
%\begin{center}
%\includegraphics[]{pic-natural.pdf}
%\end{center}
%However, such a natural transform would be notated as 
%%category theorists would write this as
%$ R^{ab}_c : \F\to\F,$
%and this looks good because natural transformations
%can be thought of as $2-$morphisms (a morphism of morphisms) and we
%do expect the braiding to be somehow one level up
%in the $n-$categorical sense.

\subsub{Hexagon equation.}
For a surface with three interior holes there are
infinitely many POP decompositions (up to isotopy).
These are all made by choosing an observable 
that encloses two holes.
The $F$-moves allow us to switch between 
these POP decompositions,
and the axioms for the modular
functor make these consistent.
Here we show two such triangle consistency requirements
(they are reflections of each other):
\begin{center}
\includegraphics[width=0.25\columnwidth]{pic-fmove-relation.pdf}
\ \ \ \ \ \ \ \ \ \ \ \ \ 
\includegraphics[width=0.25\columnwidth]{pic-fmove-relation-r.pdf}
\end{center}
Given a POP decomposition of a surface $N$
there are various curve diagrams on $N$ that
produce this decomposition from 
a standard POP decomposition, and there are certain $R$-moves
that will map between these.
Once again, these moves must be consistent, and
here we note the two ``hexagon equations'' 
%for curve diagrams corresponding to the above triangles:
corresponding to the above two triangles:
\begin{center}
\includegraphics[width=0.4\columnwidth]{pic-hexagon.pdf}
\ \ \ \ \ \ \ \ \ \ \ \ 
\includegraphics[width=0.4\columnwidth]{pic-hexagon-r.pdf}
\end{center}
Note that we have neglected to indicate the base points here.
Given a curve diagram, we can agree that base points
occur ``to the right'' of the image of the equator.
But in notating diagrams such as these, there is still
an ambiguity: the position of the base points should be the
same in each surface in the diagram.
If we try to correct for this post-hoc
by rotating individual holes,
we will then be correct
only up to possible Dehn twist(s) around each hole.
We can certainly track these twists if we wanted to,
but in the interests of simplicity we do not.
This introduces a global phase ambiguity into the
calculations. \cggb{Do we need to worry about this if we are pasting other surfaces (whose total charge might be ambiguous) into a hole?}
%What we have done here is to forget that the holes
%have width, and shrunk them to points.

The reason why we mention the pentagon and hexagon
equations is that these become important in an
algebraic description of the theory.
Because we have defined everything in terms of
a modular functor we get these equations ``for free''.

%
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
%

%\subsub{Refactoring theorem.}
\subsection{Refactoring theorem}
In this section we specialize to considering planar surfaces only.
The theorem we are building towards shows that
the $R$-moves act transitively \cggb{what do we mean here by transitively} on curve diagrams.
%\simon{We don't much care about transitivity. Should specialize this.}
That is, given two curve diagrams $f$ and $f'$ on $N$ we can find
a sequence of $R$-moves that transform $f$ to $f'.$
%We consider surface $N$ with $n$ boundary components
%$a_1,...,a_n.$
The key idea is to consider the (directed) image of the equator under
%the curve diagrams $f$ and $f'$.
these curve diagrams.
As mentioned previously, this image is sufficient to
define the entire diffeomorphism (up to isotopy) and so we are free
to work with just this image, or \emph{curve},
and we confuse the distinction between 
a curve diagram (a diffeomorphism)
and its curve.
%which we refer to as a \emph{curve.}
%Each such image will touch all the holes of $N.$

The construction proceeds by considering adjacent
pairs of holes along $f'$ and then acting on the
portion of $f$ between these same two holes so that
they then become adjacent on the resulting curve.
Continuing this
process for each two adjacent holes of $f'$ will then
show a sequence of $R$-moves that sends $f$ to $f'.$
%\simon{still not obvious: what if some such $R$-move
%destroys a previously adjacentized pair of holes?}

To this end, consider a sequence of holes $a_1,...,a_n$
appearing sequentially along $f$
such that $a_1$ and $a_n$ appear sequentially on $f'.$
We may need to apply some $Z$-moves to $f$ to ensure
that $a_1$ appears sequentially before $a_n$.
Now consider the case such that
along $f'$ between these two holes there is
no intersection with $f.$
We form a closed path $\xi$ by
following the $f'$ curve between $a_1$ and $a_n$ and then
following the $f$ curve in reverse from $a_n$ back to $a_1.$
(Note that to be completely rigorous here we would need to include segments
of path contained within boundary components.)
The resulting closed path bounds a disc.
If $\xi$ has clockwise orientation % \simon{XX define clockwise XX}
we apply the following sequence of $R$-moves to $f$:
$$
    R^{a_1a_2}_{b_1}, R^{a_1a_3}_{b_2}, ..., R^{a_1a_{n-1}}_{b_{n-1}}.
$$
Depicted here is the first such move:
\begin{center}
\includegraphics[]{pic-theorem.pdf}
\end{center}
After each of these $R$-moves the closed path
formed by 
following the $f'$ curve between $a_1$ and $a_n$ and then
following the $R$-moved $f$ curve back to $a_1$ will
traverse one less hole, and still bound a disc.
After all of the $R$-moves this path will only
touch $a_1$ and $a_n,$ and bound a disc.
Therefore, we have acted on the $f$ curve so that
the resulting curve has $a_1$ and $a_n$ adjacent
and the bounded disc gives an isotopy for that
segment of the curve.

When the closed curve $\xi$ has anti-clockwise orientation
we use the same sequence of $R$-moves but with $R$ replaced by $R^{-1}.$

Generalizing further,
when the $f'$ curve between $a_1$ and $a_n$ has (transverse) intersections
with $f$ we use every such intersection to indicate a switch
between using $R$ and $R^{-1}.$

We continue in this way moving backwards (from
head to tail) sequentially applying this procedure.

%\simon{what if the direction of $f$ is reversed??
%eg. $f$ and $f'$ are the same except one has reverse direction?}

%% http://mathoverflow.net/questions/49963/is-the-action-of-the-mapping-class-group-transitive-on-embedded-arcs?rq=1
%An alternative way to understand transitivity involves the
%mapping class group of $M.$
%First we need to switch to thinking of the anyons not as boundary
%components of $M$ but as marked points in $M.$
%Elements of the mapping class group
%act on curve diagrams in the obvious way, and if one believes that
%this action is generated by $R$-moves then we can easily show
%that $R$-moves act transitively on curve diagrams. This is because
%any curve diagram will separate the manifold $M$ into two discs.
%Any such pair of discs whose marked boundary points agree are homeomorphic
%and so we have an element of the mapping class group of $M.$
%XXX i don't see how to get the anyon labels to match up here XXX

The combinatorial ``paperclip algorithm'' presented in section \ref{secAlgo} can be considered to be a constructive reformulation of the refactoring theorem, where a curve diagram is represented as a function
from the unit interval into a disc with $n$ marked points:
$$
    c : [0, 1] \to D_n.  
$$

%
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
%
%------------------------------------------------------------------------------------------------------------%
\bibliography{refs2}

\end{document}

### 2016-09-22 guide.tex
commit edits

@@
 In the physics literature, modular functors are
-explicitly used in Refs.~\cite{Freedman2002, Freedman2002simulation, Beverland2014, Kitaev2006topo} (in some of these references modular functors are simply called TQFTs).
-%Also, \cite{Beverland2014} and \cite{Kitaev2006topo}
-%use the language of modular functors but they call them TQFT's.
-%This is in fact reasonable because a modular functor can be
-%seen as part of a TQFT, but is quite confusing to the
-%novice who attempts to delve into the mathematical literature.
+explicitly used in Refs.~\cite{Freedman2002, Freedman2002simulation}.
+Also, \cite{Beverland2014} and \cite{Kitaev2006topo}
+use the language of modular functors but they call them TQFT's.
+This is in fact reasonable because a modular functor can be
+seen as part of a TQFT, but is quite confusing to the
+novice who attempts to delve into the mathematical literature.
 
@@
 rigorously establishing the connection between these different axiomatizations.
-%In particular, what physicists call anyon theory,
-%and mathematicians call a modular tensor category,
-Furthermore, the concept of modular tensor category 
+In particular, what physicists call anyon theory,
+and mathematicians call a modular tensor category,
 has not been established to correspond exactly
@@
 
-In this section we will sketch how a 
+The main goal of the present work is to sketch how a
 braided tensor category arises from a modular functor.
@@
 \end{center}
-For identical particles this is a symmetry of the system. \cggb{What does symmetry mean here? Since a swap of non-bosons will pick up a phase.}
+For identical particles this is a symmetry of the system. 
+%%%%%% \cggb{What does symmetry mean here? Since a swap of non-bosons will pick up a phase.}
 Continuing with this line of thought 
@@
 permutation group $S_n:$
-\cggb{I was a bit confused by when we care about unlabelled configuration space and when we care about the labelled configuration space.
-What if we have some but not all particles identical?
-Do the two formalisms unify by considering some subgroups of the permutation group that preserve particle label or something?}
+%\cggb{I was a bit confused by when we care about
+%unlabelled configuration space and when we care about the labelled
+%configuration space. What if we have some but not all
+%particles identical? Do the two formalisms unify by considering some
+%subgroups of the permutation group that preserve particle label or something?}
 $$
@@
 the braid group which is purely two-dimensional.
-%We denote the two-dimensional space 
-%The two dimensional space within which the particles reside we denote 
 We pick an $n$-point finite subset $Q_n \subset M$
-and consider diffeomorphisms \cggb{why diffeomorphisms and not homeomorphisms?} $f : M \to M$
+and consider diffeomorphisms 
+%\cggb{why diffeomorphisms and not homeomorphisms?}
+$f : M \to M$
 that map $Q_n$ to itself.
@@
 This is shown in the next figure, 
-where we show a \emph{framing} which is a non-degenerate \cggb{What's a non-degenerate vector field? What goes wrong if its degenerate?}
+where we show a \emph{framing} which is a non-degenerate 
 vector field along the world-lines of a braid.
 The initial and final vectors in the vector field must be the same.
+By non-degenerate we mean that the vector field is everywhere
+non-zero and also not tangent to the world-line.
 In the next figure we show a \emph{ribbon}:
@@
 manifold orientation, hole labels, and base points.
-%\cggb{If we require that the map preserves base points and so on, are we restricting to maps between manifolds with the same number of holes?}
-%\simon{Yes, a diffeomorphism is also a homeomorphism, so these manifolds are
-%topologically equivalent.}
 Note that we also deal with maps of various other objects
@@
 This is an equivalence relation on maps $M\to N$, and the equivalence
-class of $f$ under isotopy is called the \emph{isotopy class} of $f.$ \cggb{I didn't quite see why this more formal definition is the same as equivalent up to continuous deformation.
-Why can I restrict to maps where the base points are fixed along the whole path?}
+class of $f$ under isotopy is called the \emph{isotopy class} of $f.$
+%\cggb{I didn't quite see why this more formal definition is
+%the same as equivalent up to continuous deformation. Why can
+%I restrict to maps where the base points are fixed along the whole path?}
 
@@
 %\cggb{Does a modular functor have to be over $\C$?}
-%\simon{No, mathematicians do this over any ring $k.$}
+%\simon{No, mathematicians do this over any field $k.$}
 For $M_a$ a disc with boundary label $a$ we have
@@
 We then re-glue any annuli or discs until there are no more of these
-and we have only pair-of-pants. \cggb{Is this always possible? What if I have something like a cylinder? Then I just get a bunch of annuli however I cut.}
+and we have only pair-of-pants.
+%\cggb{Is this always possible? What if I have something like
+%a cylinder? Then I just get a bunch of annuli however I cut.}
 % note: we may still get annuli in a *component* of the pre-image.
@@
 In this work we use a simpler method,
-which is essentially the same as {skein theory.} \cggb{Is all this curve diagrams and refactoring theorem and and so on original work, or is it collecting known facts?
-If its original, this should be an independent paper because otherwise nobody from the math phys community will ever find it.
-Actually maybe in either case it should be an independent arxiv post at least so that more people find and learn from it.}
+which is essentially the same as {skein theory.}
+%    \cggb{Is all this curve diagrams and refactoring theorem and and
+%    so on original work, or is it collecting known facts?
+%    If its original, this should be an independent paper because
+%    otherwise nobody from the math phys community will ever find
+%    it. Actually maybe in either case it should be an
+%    independent arxiv post at least so that more people find and learn from it.}
 %Read on to find out how this works!
@@
 which we denote $\StdM.$
-For concreteness, we 
-let this surface be the subset of
-the complex plane defined by
-$\bigl\{x\in\C \ \mathrm{st.}\  |x-\frac{1}{2}|\le \frac{1}{2}\bigr\}$
-with $n$ discs
-$\bigl\{x\in\C \ \mathrm{st.}\  |x-\frac{2i-1}{2n}|< \frac{1}{4n}\bigr\}_{i=1,...n}$
-removed. \cggb{Why is this easier to describe on $\mathbb{C}$ rather than $\mathbb{R}^2$? If its all the same, I think it could be safer to rephrase on $\R^2$.}
+
+%For concreteness, we 
+%let this surface be the following subset of
+%the real plane:
+For concreteness
+we define this surface using the following 
+expression for a closed disc less $n$ open discs:
+$$
+\Bigl\{(x,y)\in\R^2 \ \mathrm{st.}\  \Bigl|(x,y)-\Bigl(\frac{1}{2},0\Bigr)\Bigr|\le \frac{1}{2}\Bigr\} -
+\Bigl\{(x,y)\in\R^2 \ \mathrm{st.}\  \Bigl|(x,y)-\Bigl(\frac{2i-1}{2n},0\Bigr)\Bigr| < \frac{1}{4n}\Bigr\}_{i=1,...n}.
+$$
+%For concreteness, we 
+%let this surface be the subset of
+%the complex plane defined by
+%$\bigl\{x\in\C \ \mathrm{st.}\  |x-\frac{1}{2}|\le \frac{1}{2}\bigr\}$
+%with $n$ discs
+%$\bigl\{x\in\C \ \mathrm{st.}\  |x-\frac{2i-1}{2n}|< \frac{1}{4n}\bigr\}_{i=1,...n}$
+%removed.
+%\cggb{Why is this easier to describe on $\mathbb{C}$ rather than
+%$\mathbb{R}^2$? If its all the same, I think it could
+%be safer to rephrase on $\R^2$.}
+%We then label the interior holes $a_1,...,a_n$ in order of
+%increasing real coordinate, and the exterior hole is labeled ${b}$.
+%The base points are placed in the direction of the negative imaginary axis.
+%As a notational convenience we highlight the \emph{equator}
+%of the surface %$\StdM$ 
+%which is the intersection of
+%the real axis with the surface:
 We then label the interior holes $a_1,...,a_n$ in order of
-increasing real coordinate, and the exterior hole is labeled ${b}$.
-The base points are placed in the direction of the negative imaginary axis.
+increasing $x$ coordinate, and the exterior hole is labeled $b$.
+The base points are placed in the direction of negative $y$ coordinate.
 As a notational convenience we highlight the \emph{equator}
@@
 which is the intersection of
-the real axis with the surface:
+the $x$ axis with the surface:
 \begin{center}
@@
 to an interior hole of another standard surface $N.$
-To do this within $\C$ we rescale and translate the two surfaces so
+To do this within $\R^2$ we rescale and translate the two surfaces so
 that the exterior hole of $M$ coincides with the interior hole of $N.$
@@
 %However, we can ... \simon{fix this}
-and so we remedy this by applying any isotopy within $\C$
-that fixes the real axis while moving the surface to a standard surface. \cggb{Does "fix the real" axis here mean that it fixes every point on the real axis, or just maps the real axis to itself?}
-%while moving the holes so as to produce
-%a standard surface.
+and so we remedy this by applying any isotopy within $\R^2$
+that fixes the $x$-axis while moving the surface to a standard surface.
+%\cggb{Does "fix the real" axis here mean that it fixes
+%every point on the real axis, or just maps the
+%real axis to itself?}
 
@@
 We next study maps from standard surfaces to arbitrary surfaces.
-\cggb{I was a bit confused what this means.
-Maps means between surfaces with the same holes and base points, right?
-So then don't we only care about maps from standard surfaces to standard surfaces?
-Is it maybe more like maps from equatorial curve diagrams on standard surfaces to arbitrary curve diagrams on standard surfaces that we want?}
+%\cggb{I was a bit confused what this means. Maps means
+%between surfaces with the same holes and base points, right?
+%So then don't we only care about maps from standard
+%surfaces to standard surfaces? Is it maybe more like maps
+%from equatorial curve diagrams on standard surfaces to arbitrary curve
+%diagrams on standard surfaces that we want?}
+The reader should think of this as akin to choosing a basis
+for a vector space.
 The set of all maps from $\StdM$ 
@@
 any map $f:\StdM\to N$ from
-the restriction of $f$ to the equator of $\StdM.$ \cggb{citation? or obvious?}
+the restriction of $f$ to the equator of $\StdM.$ % XXX XXX XXX \cggb{citation? or obvious?}
 In other words, we can uniquely specify any map
@@
 The proof of this is constructive, and we call this
-the refactoring theorem below. \cggb{citation? or original work?} %\simon{XXX} 
-%The proof of this is constructive and forms the heart of
-%our algorithm below.
+the refactoring theorem below. %\cggb{citation? or original work?}
 
@@
 long as we are careful with the way we identify along the seam:
-the identification map needs to respect the equator of the curve
-diagram. \cggb{Is respecting the equator the same as respecting whatever canonical curve diagram we choose?}
+the identification map needs to respect the equator of the curve diagram. 
+(Keep in mind that a curve diagram is really a map of surfaces,
+and so gluing two such maps involves two separate gluing operations.)
 
@@
 the main difference being that planar algebras allow for 
-not just two but any even number of curve intersections at each hole. \cggb{What's a planar algebra and is there an easier place for me to learn about it than from the Jones paper?}
+not just two but any even number of curve intersections at each hole.
+%\cggb{What's a planar algebra and is there an easier place for me to learn about it than from the Jones paper?}
 
@@
 This introduces a global phase ambiguity into the
-calculations. \cggb{Do we need to worry about this if we are pasting other surfaces (whose total charge might be ambiguous) into a hole?}
+calculations.
+%\cggb{Do we need to worry about this if we are
+%pasting other surfaces (whose total charge might be ambiguous) into a hole?}
+
 %What we have done here is to forget that the holes
@@
 The theorem we are building towards shows that
-the $R$-moves act transitively \cggb{what do we mean here by transitively} on curve diagrams.
-%\simon{We don't much care about transitivity. Should specialize this.}
-That is, given two curve diagrams $f$ and $f'$ on $N$ we can find
+the $R$-moves act transitively
+on curve diagrams.
+By transitive we mean that
+given two curve diagrams $f$ and $f'$ on $N$ we can find
 a sequence of $R$-moves that transform $f$ to $f'.$
@@
 
-The combinatorial ``paperclip algorithm'' presented in section \ref{secAlgo} can be considered to be a constructive reformulation of the refactoring theorem, where a curve diagram is represented as a function
-from the unit interval into a disc with $n$ marked points:
-$$
-    c : [0, 1] \to D_n.  
-$$
+%The combinatorial ``paperclip algorithm'' presented in section 
+%\ref{secAlgo} can be considered to be a constructive reformulation 
+%of the refactoring theorem, where a curve diagram is represented as a function
+%from the unit interval into a disc with $n$ marked points:
+%$$
+%    c : [0, 1] \to D_n.  
+%$$
 

### 2016-09-24 guide.tex
commit edits

@@
-\documentclass[aps, letterpaper, onecolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
+\documentclass[aps, letterpaper, onecolumn, superscriptaddress, notitlepage, 11pt, groupedaddress]{revtex4-1}
 \usepackage{times}
@@
 
-\title{A Short Guide To Modular Functors, Anyons, etc.}
+\title{A Short Guide to Anyons and Modular Functors}
 
@@
 The University of Sydney, Sydney, Australia}
-%\author{Courtney G.\ Brell}
-%\affiliation{Institut f\"{u}r Theoretische Physik, Leibniz Universit\"{a}t Hannover, 
-%Appelstra\ss{}e 2, 30167 Hannover, Germany}
-%%\affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada}
-%\author{Steven T.\ Flammia}
-%\affiliation{Centre for Engineered Quantum Systems, School of Physics, 
-%The University of Sydney, Sydney, Australia}
 
 \date{\today}
+
+\begin{abstract}
+To the working physicist, anyon theory is meant to describe
+certain quasi-particle excitations occuring in two dimensional
+topologically ordered systems. 
+A typical calculation using this theory will involve operations
+such as $\otimes$ to combine anyons, 
+$F^{abc}_{d}$ to re-associate such combinations,
+and $R^{ab}_c$ to commute or braid these anyons. 
+Although there is a powerful string-diagram notation that greatly assists these
+manipulations, we still appear to be operating on particles
+arranged on a one-dimensional line, algebraically ordered from left to right.
+The obvious question is, where is the other dimension?
+The topological framework for considering these anyons as truly living in a
+two dimensional space is known as a modular functor, or topological
+quantum field theory. 
+In this work we show how the apparently one-dimensional algebraic anyon theory
+is secretly the theory of anyons living in a fully two-dimensional system.
+The mathematical literature covering this secret is vast, 
+and we try to distil this down into something more manageable.
+%While avoiding much of the
+%category theoretic jargon found in the mathematical literature.
+%To the physicist, anyons are manipulated algebraically, using operations
+%such as $\otimes$ to combine, $F^{abc}_{de}$ to re-associate, and $R^{ab}_c$
+%to commute or braid. 
+%Although there are string-diagram notations that greatly assist these
+%manipulations, such calculations still appear to be operating on particles
+%arranged in a one-dimensional line, algebraically ordered from left to right.
+%The correct notion for considering these anyons as truly living in a
+%two dimensional space is known as a modular functor, or topological
+%quantum field theory. 
+%In this work we show how the apparently one-dimensional algebraic theory
+%is secretly a fully-two dimensional theory, while avoiding much of the
+%category theoretic jargon found in the mathematical literature.
+\end{abstract}
 
@@
 
-In this section we will describe abstractly the theory of two-dimensional topologically ordered systems
+In this work we describe the theory of two-dimensional topologically ordered systems
 with anyonic excitations. 
@@
 This algebraic language appears to be more commonly used 
-in the physics literature~\cite{Kitaev2006}.
+in the physics literature, such as the well cited Appendix E of Kitaev~\cite{Kitaev2006}.
 Such algebraic calculations can be interpreted as
 manipulations of string diagrams~\cite{Baez2010},
-or \emph{skeins}, which begins to hint at
-how knot theory and topology comes into play.
-
-Coming from the other direction, one starts with
+or \emph{skeins}.
+These strings encode connections in the algebra, for example 
+the Einstein summation convention. But they also faithfully
+encode the twisting that occurs when anyons are re-ordered or
+braided around each other. And these kinds of spatial relationships
+are fruitfully studied using topological methods.
+
+Working from the other direction, one starts with
 a topological space (of low dimension) and attempts
@@
 
-It is not obvious a priori that these two approaches -- algebraic and topological -- should meet, hinting at a deep underlying structure.
-%That these two approaches -- algebraic versus topological -- meet is one of the great
-%miracles of modern mathematics and physics.
+%It is not obvious a priori that these two approaches -- algebraic and topological -- should meet, hinting at a deep underlying structure.
+That these two approaches -- algebraic versus topological -- meet is one of the great
+surprises of modern mathematics and physics.
 
@@
 
-In this section we try to motivate 
-the formalism of modular functor presented
-below.
-Our focus will be to show some of the close connections between
-the algebraic and topological approaches to
-particle exchange statistics.
+In this section we begin with the familiar question 
+of particle exchange in three dimensions, whose answer is bosons and fermions.
+We then show how in restricting the particles to two dimensions many
+more possibilities arise.
+Our focus will be on the close connection between the algebraic and the topological viewpoints,
+aiming to motivate the definition of a modular functor given in the next section.
 
@@
 \end{align*}
-This group acts on the statespace of $n$ particles $\F_n$
-via unitaries $U(\F_n)$:
-$$
-    \Phi : S_n \to U(\F_n).
-$$
+%This group acts on the statespace of $n$ particles $\F_n$
+%via unitaries $U(\F_n)$:
+%$$
+%    \Phi : S_n \to U(\F_n).
+%$$
+Writing the Hilbert space of the system as $V$ 
+we would then expect $S_n$ to act on this space via unitary transformations $U(V):$
+$$
+    \F : S_n \to U(V).
+$$
+% For bosons this is ... for fermions it is ...
+This is the first example of the kind of functor we will be talking about. 
+In this case it is a group representation; $\F$ is a homomorphism between
+two groups.
 
@@
 To see this more clearly,
-we consider the world-lines of these particles.
-Here we show three particles undergoing an exchange and then
-returning to the original location:
+we must examine the entire (2+1)-dimensional \emph{world-lines} of these particles.
+For an example, here we show the world-lines of three particles undergoing an exchange and then
+returning to their original positions:
 \begin{center}
@@
 $$
-    \Phi : B_n \to U(\F_n).
+%    \Phi : B_n \to U(\F_n).
+    \F : B_n \to U(V).
 $$
@@
 $\sigma_i \sigma_j = \sigma_j \sigma_i \ \ \ \mbox{for}\ \ |i-j|>1$
-because the two braids are operating on disjoint strands.
+because the two braids are operating on disjoint world-lines.
 The second relation is also easy to see:
@@
 equivelant, but the actual proof of this is somewhat involved.
-We refer the reader to \cite{Kassel2010} for an excellent contemporary
+We refer to \cite{Kassel2010} for an excellent contemporary
 reference that fills in these gaps.
@@
 $$
-Loops in $\Conf_n$ correspond to braids where each strand returns
+Loops in $\Conf_n$ correspond to braids where each world-line returns
 to the point it started from.
@@
 geometric approaches to representing a twist.
-Anyone that has struggled to untangle their headphone cable
+Any person that has struggled to untangle their headphone cable
 will immediately see what is going on here.
+\begin{center}
+\includegraphics[]{pic-framed.pdf}
+\end{center}
 On the left we have a loop; it is not a braid because it
@@
 By non-degenerate we mean that the vector field is everywhere
-non-zero and also not tangent to the world-line.
+non-zero and non-tangent to the world-line.
 In the next figure we show a \emph{ribbon}:
@@
 On the right the particle is represented as a boundary
-component of $M$ with a distinguished point.
+component (a hole) of $M$ with a distinguished point.
 In this picture the world-line looks like a tube.
 %It is not difficult to see that these
+
 All these representations of twists carry
 essentially the same information.
-\begin{center}
-\includegraphics[]{pic-framed.pdf}
-\end{center}
 In the sequal we will stick

### 2016-09-25 guide.tex
spell check

@@
 To the working physicist, anyon theory is meant to describe
-certain quasi-particle excitations occuring in two dimensional
+certain quasi-particle excitations occurring in two dimensional
 topologically ordered systems. 
@@
 The mathematical literature covering this secret is vast, 
-and we try to distil this down into something more manageable.
+and we try to distill this down into something more manageable.
 %While avoiding much of the
@@
 For $n$ particle worldlines we denote this group as $B_n.$
-For identicle particles this group acts as symmetries of the
+For identical particles this group acts as symmetries of the
 state space:
@@
 $$
-Because we are considering identicle particles (so far)
+Because we are considering identical particles (so far)
 we use the \emph{unlabelled configuration space}
@@
 generators and relations, as was shown by Artin in 1947, \cite{Artin1947,Birman1974}.
-$B_n$ has $n-1$ generators $\sigma_1,..,\sigma_{n-1}$ that satisfy
+In this description, 
+$B_n$ is generated by $n-1$ elements $\sigma_1,..,\sigma_{n-1}$ that satisfy
 the following relations:
@@
 \end{align*}
-So these relations are the same as for $S_n$ above, except 
-we no longer have the relation $\sigma_i^2 = 1.$
+These relations are the same as for $S_n$ above, except 
+we do not require $\sigma_i^2 = 1.$
 
@@
 It is easy to see that the geometric braid group satisfies these
-relations. Here we show the braids corresponing to the generators $\sigma_i:$
+relations. Here we show the braids corresponding to the generators $\sigma_i:$
 \begin{center}
@@
 The importance of understanding the
-braid group as identicle to the mapping class group
+braid group as identical to the mapping class group
 is now manifest:
@@
 to why these two definitions of the braid group are
-equivelant, but the actual proof of this is somewhat involved.
+equivalent, but the actual proof of this is somewhat involved.
 We refer to \cite{Kassel2010} for an excellent contemporary
@@
 essentially the same information.
-In the sequal we will stick
+In the sequel we will stick
 to thinking of particles as boundary
@@
 
-At this point in the narative we are 
+At this point in the narrative we are 
 close to our next destination.
@@
 This is the set of ``anyon labels'', and comes
-equiped with a vacuum element $\vac$ 
+equipped with a vacuum element $\vac$ 
 and an involution $\ \widehat{}\ $ such that $\widehat{\vac}=\vac.$
@@
 we show how to present $M$ as the gluing of various
-pair-of-pants. Such an arangement will be termed a \emph{POP decomposition.}
+pair-of-pants. Such an arrangement will be termed a \emph{POP decomposition.}
 (We refer to \cite{Ivanov2001} for more details on this construction,
@@
 for the topological space $M$ and the fusion space $\F(M).$
-Also, each of these $F$-moves is refering to an isomorphism 
+Also, each of these $F$-moves is referring to an isomorphism 
 that is block decomposed according to the charge sectors 
@@
 \subsub{Skeins.}
-The preivious figure can be seen as a ``top-down'' view of the
+The previous figure can be seen as a ``top-down'' view of the
 following three dimensional arrangement:

### 2016-09-25 guide.tex
commit edits

@@
 %That is, we allow the ambient $(2+1)$-dimensional
-%space with these worldlines subtracted to be continuously
+%space with these world-lines subtracted to be continuously
 %deformed.
@@
 known as the \emph{braid group.}
-For $n$ particle worldlines we denote this group as $B_n.$
+For $n$ particle world-lines we denote this group as $B_n.$
 For identical particles this group acts as symmetries of the

### 2016-09-25 guide.tex
commit edits

@@
 any map $f:\StdM\to N$ from
-the restriction of $f$ to the equator of $\StdM.$ % XXX XXX XXX \cggb{citation? or obvious?}
+the restriction of $f$ to the equator of $\StdM.$
 In other words, we can uniquely specify any map
 $f:\StdM\to N$ by indicating the action of
-$f$ on the equator. We take full advantage of this
+$f$ on the equator.
+(This reconstruction works because a simple closed curve on a sphere cuts 
+the sphere into two discs.)
+We take full advantage of this
 fact in our notation: any figure of a surface

### 2016-10-09 fib2.tex
shortened the main text to 4 pages

@@
 Appelstra\ss{}e 2, 30167 Hannover, Germany}
+\affiliation{Perimeter Institute for Theoretical Physics, 
+Waterloo, Canada}
 \author{Steven T.\ Flammia}
@@
 
-Topologically ordered quantum systems in two dimensions show tremendous promise for 
+Topologically ordered quantum systems in two dimensions show great promise for 
 long-term storage and processing of quantum information~\cite{Kitaev2003, Dennis2002, Nayak2008}. 
@@
 perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and they have quasiparticle excitations 
-exhibiting anyonic statistics~\cite{Wilczek1990}. These systems can in general be used as 
+exhibiting anyonic statistics~\cite{Wilczek1990}. These systems can be used as 
 quantum memories~\cite{Kitaev2003, Dennis2002} or to perform universal topological 
@@
 on active quantum error correction for topological systems has focused 
-on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Fowler2015, Andrist2015}.
-Systems of abelian anyons are well suited to studying quantum 
-error correction because (at the RG fixed point) noise and 
-recovery processes can be efficiently simulated numerically, allowing lattice simulations 
-of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. 
-Standard algorithms are specifically tailored to exploit the abelian nature 
-of these particles, particularly that abelian anyons cannot be used for quantum computation.
+on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Fowler2015, Andrist2015}, which can be efficiently simulated due to the fact that they cannot be used for quantum computation.
+%Systems of abelian anyons are well suited to studying quantum 
+%error correction because (at the RG fixed point) noise and 
+%recovery processes can be efficiently simulated numerically, allowing lattice simulations 
+%of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. 
+%Standard algorithms are specifically tailored to exploit the abelian nature 
+%of these particles, particularly that abelian anyons cannot be used for quantum computation.
 
@@
 
-Concretely, we consider the simulation of quantum error correction in a two-dimensional lattice 
+Concretely, we consider quantum error correction in a two-dimensional 
 system with Fibonacci anyons, a class of nonabelian anyons that are universal for quantum 
@@
 heterostructures~\cite{Mong2014}.
-Any of these kinds of physical systems could be used to perform universal topological quantum computation \cggb{citations?}, and can be modelled by our simulations.
+Any of these physical systems could be used to perform universal topological quantum computation, and can be modelled by our simulations.
 Natural sources of noise from thermal fluctuations or external perturbations will be suppressed by the energy gap but must still be corrected to allow for scalable computation.
@@
 2-dimensional system with
-point-like anyonic quasiparticle excitations, which exhibit exotic statistics under exchange.
-The worldlines of these exchanges form \emph{braids}
+point-like anyonic quasiparticle excitations.%, which exhibit exotic statistics under exchange.
+The worldlines of these particles form \emph{braids}
 in (2+1)-dimensions
 which act unitarily on the Hilbert space of degrees of freedom known as the \emph{fusion space}.
-To describe this space we define
+This space is associated with
 the topological observables of the system: these
 are total charge measurements within regions bounded by 
-closed loops (Wilson loops).
+closed loops.% (Wilson loops).
 The possible results of such a charge measurement correspond to different anyon particle types in the model.
@@
 given by a unitary modular tensor category~\cite{Wang2010b}.
-However, from the perspective of
-\emph{topological quantum field theory}
-anyons are modeled
-as punctures in a surface~\cite{Pfeifer2014}, and it is not
-the anyons themselves that braid,
-but the manifold in which the anyons reside 
-that becomes deformed (twisted) by these braid moves.
-This is the perspective we adopt (see \Fref{f:braidloop}).
+In contrast to the approach often taken, we consider the topological observables, rather than the anyons themselves, to be affected by braiding processes (see \Fref{f:braidloop}).
+%From the perspective of
+%\emph{topological quantum field theory},
+%anyons are modeled
+%as punctures in a surface~\cite{Pfeifer2014}, 
+%and the observables, rather than the anyons themselves, are considered to be deformed by braiding processes (see \Fref{f:braidloop}).
+%and it is not
+%the anyons themselves that braid,
+%but the manifold in which the anyons reside 
+%that becomes deformed (twisted) by these braid moves.
+%This is the perspective we adopt (see \Fref{f:braidloop}).
 
@@
 The deformation of observables corresponding to the implementation of a braid process on three anyons is shown.
-The configurations before and after are connected by world lines shown in red, while the observable Wilson loops are shown in black.
-This process relates two different ways of observing (or fusing) the top two charges.
-In general, braiding will twist these loops in different ways following
-the deformation of the manifold itself.
+Configurations before and after are connected by world lines shown in red, while the charge observables are shown in black.
+This process relates two different ways of fusing the top two charges.
+%In general, braiding will twist these loops in different ways following
+%the deformation of the manifold itself.
 \label{f:braidloop}
@@
 The defining difference between abelian and nonabelian
-anyon theories is that in an abelian theory particle content alone uniquely determines the outcome of total charge measurements.
+anyon theories is that in an abelian theory particle content alone uniquely determines the outcome of joint charge measurements.
 In contrast, outcomes for nonabelian charge measurements depend on the history of the particles as well as their type.
-That is, the fusion space is one-dimensional for abelian anyons, and generally larger for nonabelian anyons.
-In particular, we consider a system supporting (nonabelian) Fibonacci
+%That is, the fusion space is one-dimensional for abelian anyons, and generally larger for nonabelian anyons.
+We consider a system supporting nonabelian Fibonacci
 anyon excitations, denoted by $\tau$.
@@
 \end{align*}
-For $n$ anyons of type $\tau$, the 
-dimension of the fusion space grows asymptotically as $\varphi^n$, where $\varphi=\frac{1+\sqrt{5}}{2}$ 
-is the golden ratio.
+%For $n$ anyons of type $\tau$, the 
+%dimension of the fusion space grows asymptotically as $\varphi^n$, where $\varphi=\frac{1+\sqrt{5}}{2}$ 
+%is the golden ratio.
 
@@
 order the anyons, and track
-deformations in the underlying space, 
-i.e.\ the history of braiding processes.
-It also denotes the direction along
-which $F$-moves occur. A clockwise braiding process, or \emph{half-twist}, is effected by an $R$-move:
+%deformations in the underlying space, 
+%i.e.\ 
+the history of braiding processes (see Ref.~\cite{CurveDiagrams} for a more comprehensive discussion).
+%It also denotes the direction along which $F$-moves occur. 
+A clockwise braiding process, or \emph{half-twist}, is effected by an $R$-move:
 \begin{align}
@@
 as a charge in another diagram.
-This operation distributes multiplicatively
-over superpositions, and it also respects the $R$ and $F$-moves.
+This operation distributes over superpositions, and it also respects the $R$- and $F$-moves.
 Conversely, \emph{fusion} of anyons corresponds to 
@@
 In addition to the fusion space there is also a global degeneracy associated with the topology of the 
-manifold on which the anyons reside. We consider systems with the topology of a torus, 
+manifold on which the anyons reside. We consider systems on a torus, 
 which for the Fibonacci anyons gives rise to a 2-fold degeneracy.
@@
 pair-creation, hopping, exchange etc.~of anyons. Such a model was analyzed in detail for Ising anyons in Ref.~\cite{Brell2013}.
-For convenience, in the numerical results presented in this study we will restrict to a simplified noise model consisting of pair-creation events only, though all of our simulation techniques could be applied directly to the more general families of noise models considered in Ref.~\cite{Brell2013} as desired.
+For convenience, in the numerical results presented in this study we will restrict to considering pair-creation events only, though all of our simulation techniques could be applied directly to the more general noise considered in Ref.~\cite{Brell2013} as desired.
 It was seen in Ref.~\cite{Brell2013} that the pair-creation-only setting was sufficient to capture the qualitative features of an error-correction simulation for the Ising anyons and we have no reason to expect that this would change when considering the Fibonacci anyon model.
@@
 We thus measure the error correction threshold and memory lifetime in terms of the average number of noise processes per edge.
-It is easy to see that, in those cases where they are both appropriate, these two methods coincide in the limit of low error rates (see Ref.~\cite{Brell2013} for more details).
-The thresholds we consider in this paper are on the order of $0.1$ noise processes per edge.
+It is easy to see that, in those cases where they are both appropriate, these two methods coincide in the limit of low error rates, and for the typical noise strengths we encounter in this paper, the discrepancy is around $10\%$ (see Ref.~\cite{Brell2013} for more details).
+%The thresholds we consider in this paper are on the order of $0.1$ noise processes per edge.
 In models where both noise strength measures are appropriate, such as the toric code under bit-flip errors, the discrepancy between the two values is around $10\%$ at these strengths.
@@
 anyon model correspond to large length-scale physics, while the microscopic physics plays 
-a less important (and non-universal) role.
-Additionally, while we model a continuum anyon theory, our analysis can be trivially reinterpreted to apply directly to lattice spin models or other systems where space is fundamentally discrete.
+a less important (and non-universal) role. Note also that our analysis applies equally well to either a continuum setting, or to discrete lattice models supporting anyonic excitations.
+%Additionally, while we model a continuum anyon theory, our analysis can be trivially reinterpreted to apply directly to lattice spin models or other systems where space is fundamentally discrete.
 
@@
 and follows a similar strategy to the hard-decision renormalization group decoder~\cite{Bravyi2011}. 
+The error-correction protocol and simulation procedure are discussed in more depth in the supplementary material.
 
@@
 and so must repeatedly physically query the system to measure these charges.
-This is also in contrast to abstract quantum codes, where syndrome extraction can typically be performed in one step.
+%This is also in contrast to abstract quantum codes, where syndrome extraction can typically be performed in one step.
 Our simulation proceeds in this way as a dialogue between decoder
 and system, terminating when either the decoder itself terminates or 
-when it performs a homologically nontrivial operation, thereby altering the 
-codespace (and failing to perform successful information recovery).
-Note that, as was found in Ref.~\cite{Brell2013}, we expect that 
-our qualitative results may be reproduced by most alternative families 
-of decoders, although it may not be clear in all cases how to extend these decoders to the nonabelian setting.
-The advantage of using a clustering decoder is 
-its simplicity and flexibility, and the fact that its clustering 
-scheme is compatible with the structure in the noise 
-processes that allows us to classically simulate them.
+when it performs a homologically nontrivial operation, thereby performing a potential logical error.
+%altering the 
+%codespace (and failing to perform successful recovery).
+%Note that, as was found in Ref.~\cite{Brell2013}, we expect that 
+%our qualitative results may be reproduced by most alternative families 
+%of decoders, although it may not be clear in all cases how to extend these decoders to the nonabelian setting.
+%The advantage of using a clustering decoder is 
+%its simplicity and flexibility, and the fact that its clustering 
+%scheme is compatible with the structure in the noise 
+%processes that allows us to classically simulate them.
 
@@
 bonds to decompose into separate connected components 
-of average size $O(\log(n))$ and variance $O(1)$~\cite{Bazant2000}.
+of average size $O(\log(L))$ and variance $O(1)$~\cite{Bazant2000}.
 Each noise process in our model is associated with a (randomly distributed) edge, and so 
@@
 Since each 
-component has size only $O(\log(n))$, we can typically simulate these dynamics efficiently 
-because the resulting fusion space has dimension $O(\mathrm{poly}(n))$. 
-Of course, this is only a probabilistic statement, and so there may be cases where there exist components with size larger than $O(\log(n))$.
+component has size only $O(\log(L))$, we can typically simulate these dynamics efficiently 
+because the resulting fusion space has dimension $O(\mathrm{poly}(L))$. 
+Of course, this is only a probabilistic statement, and so there may be cases where there exist components with size larger than $O(\log(L))$.
 However, the likelihood of this is suppressed exponentially in the lattice size $L$~\cite{Grimmett1989}.
@@
 become exponentially difficult in the system size.
-Despite this, we use heuristics 
-that minimize braid moves, which helps to
-track the state beyond the
-sub-percolated regime.
-This enables simulation of error correction in
+%Despite this, we use heuristics 
+%that minimize braid moves, which helps to
+%track the state beyond the
+%sub-percolated regime.
+%This enables simulation of error correction in
+Nevertheless, we are able to simulate error-correction in
 the regime around the error-correction threshold for linear lattice sizes up to $L=128$.
@@
 
-In order to track the state of the system we maintain 
+In order to track the state of the system we represent the state of the fusion space with 
 a set of disjoint directed curves, 
@@
 that allows for tensor factorization of disjoint components.
-The application of a pair-creation noise process corresponds to the 
+A pair-creation noise process corresponds to the 
 addition of an extra curve to the lattice, supporting
@@
 these measurements will form the error syndrome. 
-This requires joining (arbitrarily) any curves that intersect that tile, 
+This requires joining the curves that intersect that tile, 
 and then performing $R$- and $F$-moves on the resulting
@@
 procedure for a simple noise process is shown in \Fref{f:syndrome}.
-The details of the algorithm and data structures used for 
-this procedure will be discussed elsewhere.
+This procedure is discussed in more detail in the supplementary material, and the theoretical framework underlying it is expanded in Ref.~\cite{CurveDiagrams}.
+%The details of the algorithm and data structures used for 
+%this procedure will be discussed elsewhere.
 Braiding processes that encircle 
@@
 is not well understood in general~\cite{Hastings2014}, though it is clear 
-that our threshold estimate will be a lower bound for 
+that our threshold estimate would be a lower bound for 
 the true threshold that may be found if all events 
 (including those that have percolated) were simulated. 
-However, naively computing the effect of the simplest possible homologically nontrivial operations consistently yields either a logical error or a complete failure to return to the codespace (see \Aref{s:homnontrivial}).
+In any case, we do not expect this possible discrepancy to be significant in our simulations.
+%However, naively computing the effect of the simplest possible homologically nontrivial operations consistently yields either a logical error or a complete failure to return to the codespace (see \Aref{s:homnontrivial}).
 As such it seems reasonable to suggest that neglecting the full simulation of
-these events does not significantly affect our observed threshold value.
+%these events does not significantly affect our observed threshold value.
 
@@
 unlikely these choices will affect our results qualitatively.
-In particular, although we have modeled our logical qubit as 
-encoded in the global topological degrees of freedom of our 
+In particular, although we have considered a logical qubit encoded in the global topological degrees of freedom of our 
 system, we could have encoded it in the fusion space of several preferred anyons. 
@@
 microscopic spin models or models with non-topological features would give 
-direct insight into practical error rates needed for topological quantum memories in nonabelian systems. 
+direct insight into practical error rates needed for nonabelian topological quantum memories.% in nonabelian systems. 
 It would also be interesting to find \emph{classical} spin models 
@@
 STF also acknowledges support from an ARC Future Fellowship FT130101744.
+This research was supported in part by Perimeter Institute for Theoretical Physics.
+Research at Perimeter Institute is supported by the Government of Canada through Industry Canada and by the Province of Ontario through the Ministry of Research and Innovation.
 

### 2016-10-10 process.py
measure -> recovery

@@ -80,7 +80,7 @@ c.text(x+1.5*W, y+0.1, "noise", south)
 
 y += 0.5*dy
 c.stroke(path.line(x+r, y, x+W-r, y), [deco.earrow()])
-c.text(x+0.5*W, y+0.1, "measure", south)
+c.text(x+0.5*W, y+0.1, "recovery", south)
 
 y += dy
 c.stroke(path.line(x+W-r, y, x+r, y), [deco.earrow()])
@@ -92,7 +92,7 @@ c.stroke(path.line(x+0.5*W, y+0.2, x+0.5*W, y-0.2+dy), st_dotted)
 y += dy
 
 c.stroke(path.line(x+r, y, x+W-r, y), [deco.earrow()])
-c.text(x+0.5*W, y+0.1, "measure", south)
+c.text(x+0.5*W, y+0.1, "recovery", south)
 
 y += dy
 c.stroke(path.line(x+W-r, y, x+r, y), [deco.earrow()])

### 2016-10-11 guide.tex
more changes
some fixes from DW

@@
-\documentclass[aps, letterpaper, onecolumn, superscriptaddress, notitlepage, 11pt, groupedaddress]{revtex4-1}
+\documentclass[aps, tightenlines, letterpaper, onecolumn, superscriptaddress, notitlepage, 11pt, groupedaddress]{revtex4-1}
 \usepackage{times}
@@
 The algebraic side is known to mathematicians as the study of braided
-tensor categories, or more specifically, modular tensor categories.
+fusion tensor categories, or more specifically, modular tensor categories.
 This algebraic language appears to be more commonly used 
@@
 The main goal of the present work is to sketch how a
-braided tensor category arises from a modular functor.
+braided fusion tensor category arises from a modular functor.
 In the mathematical literature,
@@
 In this section we begin with the familiar question 
-of particle exchange in three dimensions, whose answer is bosons and fermions.
+of particle exchange statistics in three dimensions, whose answer is bosons and fermions.
 We then show how in restricting the particles to two dimensions many
@@
 %otherwise by using the orientation of the manifold)
-By a \emph{hole} of $M$ we mean a component of its boundary. % $\partial M$.
+By a \emph{hole} of $M$ we mean a connected component of its boundary. % $\partial M$.
 Each hole will inherit the manifold orientation,

### 2016-10-11 referee comments/Response.txt
initial draft of response to referee comments

Referee A:

1) As suggested by the referee, we have included supplementary material that significantly expands the discussion of the simulation algorithm, as well as providing a reference to a new manuscript that explains the theoretical underpinnings of our simulation.

2) We clarify this claim to simply note that we do not see a particular reason why we should expect any fundamental distinctions between the Ising and Fibonacci anyons, and that our methods could equally well be used to investigate alternative noise models if desired.

3) We agree that this statement was vague, and so we soften it to simply note that we do not expect our threshold estimates to be particularly biased by this effect, as well as clarifying the surrounding discussion.

4) We clarify the language to make it clear that we only find evidence for a threshold, rather than prove its existence, and that it is the existence of the threshold which would imply the asymptotically perfect storage of quantum information.

Referee B:

We believe that the ability to simulate error-correction in universal anyon models is a key development in the study of topological quantum computation. While the previous analogous calculations for non-universal nonabelian anyon codes are superficially similar, the structure of the present simuulations is significantly different and even the possibility of performing such a simulation may have been previously regarded as intractable. We hope that the extended discussion of the simulation algorithm provided in the supplementary material will demonstrate the novel approach we have taken to this problem, as compared to our previous work.
Since universal nonabelian anyons (and Fibonacci anyons in particular) are being pursued in many experimental architectures for the purpose of topological quantum computation, we believe that the ability to numerically benchmark topological error-correction protocols will have a significant impact on the field.

- We have expanded the discussion of the measure of memory lifetime used, and how it compares to iid noise strength (in particular noting that when comparable, the discrepancy would be of the order of 10% of the value for the kinds of lifetimes we consider). We also clarify the abstract to make it clear that the quoted threshold is given in terms of average errors per edge.

- We agree that in principle, given a sufficiently low physical error rate in a topological system, conventional quantum codes and error-correction techniques could be used to provide error-correction of a topological qubit. However, this would fail to exploit the inherent protection provided by the topological nature of the system. Most protocols for fault-tolerant quantum computation are motivated precisely by the lack of a need to perform standard fault-tolerant quantum circuity constructions since the topological features can be exploited to provide protection. We demonstrate how to simulate this.

- We have noted that our analysis applies to both continuum and lattice systems with anyonic excitations, including several experimental systems such as fractional quantum Hall systems, lattice spin models, and composite heterostructures. Obviously, the experimental details of an implementation of our error-correction protocol would vary significantly from architecture to architecture, but our protocol only makes use of basic topological operations (such as joint charge measurements and charge transport) which are natural in any system where anyonic excitations arise. Since more precide descriptions of how to implement these operations would unecessarily require restricting to a single experimental setup, we intentionally leave this question for future work. Our noise model is similarly vague but flexible, again accounting for sources of noise that are expected from generic topological systems with a mass gap. Again, if an analysis for a specific experimental apparatus were desired, our methods could be tailored to such a setting. We note as an open question tailoring our simulation to "realistic" microscopic lattice models, for example.

- While equations 1 and 2 may seem imprecise due to their graphical presentation, they are actually a precise representation of the corresponding topological processes. Due to space constraints, we have not been able to expand on this notation to the desired degree, but we have attempted to clarify this slightly, and provided a reference to a new manuscript where this presentation of topological operations is discussed in more detail. We have also attempted to explain the origin of the topological degeneracy as a flux through the non-trivial loop of the manifold.

- We hope that the more extensive discussion of the error-correction protocol and simulation algorithm provided in the supplementary material clarifies the terse description in the main text.

- We have clarified this remark.

- ????? We agree that this was poorly phrased, and have removed this remark. Our intention was merely to note that our reasoning for expecting the simulations to be efficient was of course an asymptotic argument, and that in the finite systems we study, we are nevertheless able to simulate in situations which could fall outside these nice cases, up to the lattice sizes shown.

- In response to another comment we have removed this argument. What we had meant was the error-correction protocol failing to return to the codespace.

### 2016-10-11 fib2.tex
initial draft of response to referee comments

@@
 $128\times128$ sites, and find a lower bound on the error-correction threshold of 
-approximately $12.5\%$, which is comparable to those previously known for abelian and 
+approximately $0.125$ errors per edge, which is comparable to those previously known for abelian and 
 (non-universal) nonabelian anyon models.

### 2016-10-17 guide.tex
more tweaking

@@
 explicitly used in Refs.~\cite{Freedman2002, Freedman2002simulation}.
-Also, \cite{Beverland2014} and \cite{Kitaev2006topo}
+Also, Refs.~\cite{Beverland2014} and \cite{Kitaev2006topo}
 use the language of modular functors but they call them TQFT's.
@@
 where $x$ is some reference configuration in $\UConf_n.$
-See \cite{Ghrist2014} for further discussion.
+See Ref.~\cite{Ghrist2014} for further discussion.
 
@@
 \begin{center}
-\includegraphics[]{pic-halftwist.pdf}
+\includegraphics[width=1.0\columnwidth]{pic-halftwist.pdf}
 \end{center}
@@
 associated to measurements
-that measure the charge on the
+of the total anyonic charge on the
 interior of the curve.
@@
 equivalent, but the actual proof of this is somewhat involved.
-We refer to \cite{Kassel2010} for an excellent contemporary
-reference that fills in these gaps.
+We cite Ref.~\cite{Kassel2010} for an excellent contemporary
+account that fills in these gaps.
 
@@
 %I restrict to maps where the base points are fixed along the whole path?}
+The weaker notion of \emph{homotopy} of maps will not be used
+here, but for the maps we use
+it turns out that homotopy is equivalent to isotopy.
+Furthermore, we can weaken the requirement that maps be differentiable,
+because every continuous map $f:M\to N$ is (continuously)
+isotopic to a differentiable map~\cite{Farb2011}.
 
@@
 pair-of-pants. Such an arrangement will be termed a \emph{POP decomposition.}
-(We refer to \cite{Ivanov2001} for more details on this construction,
-and \cite{Ghrist2014} for a leisurely description of Morse theory.)
+(We refer to Ref.~\cite{Ivanov2001} for more details on this construction,
+and Ref.~\cite{Ghrist2014} for a leisurely description of Morse theory.)
 This will yield a decomposition of $\F(M)$ into a direct
@@
 and the kind of transitions involved in their critical point structure.
-This was the approach used in \cite{Freedman2002simulation}.
+This was the approach used in Ref.~\cite{Freedman2002simulation}.
 In this work we use a simpler method,
@@
 In this case the $F$-moves themselves satisfy an equation
-that is a trivial consequence of the way we have defined $F$-moves.
+that is an immediate consequence of the way we have defined $F$-moves.
 %enforced by the axioms of the modular functor.
@@
 
+% See also: Lantern relation \cite{Farb2011},
+% involving seven Dehn twists on the sphere with 4 holes.
+
 %
@@
 
+\begin{acknowledgments}
+
+The author wishes to thank 
+Andrew Doherty, Courtney Brell, Steven Flammia and Dominic Williamson
+for helpful discussions and inspiration.
+
+\end{acknowledgments}
+
 %

### 2016-10-17 guide.tex
final tweaks

@@
 \end{center}
-For identical particles this is a symmetry of the system. 
+For identical particles this is a \emph{symmetry} of the system. 
 %%%%%% \cggb{What does symmetry mean here? Since a swap of non-bosons will pick up a phase.}
@@
 %I restrict to maps where the base points are fixed along the whole path?}
-The weaker notion of \emph{homotopy} of maps will not be used
+The weaker notion of homotopy of maps will not be used
 here, but for the maps we use

### 2016-10-25 resubmit/Response.txt
resubmitted

--- 2016-10-11 referee comments/Response.txt
@@
+We thank the editors for their consideration and the referees for their comments.
+Our manuscript has been significantly revised in response to the concerns of the referees, and we have added a significant supplementary text to flesh out the details of the simulation algorithm as suggested.
+We believe that we have now addressed the referees comments sufficiently to warrant reconsideration for publication.
+More specific responses to each referee are as follows:
+
 Referee A:
 
-1) As suggested by the referee, we have included supplementary material that significantly expands the discussion of the simulation algorithm, as well as providing a reference to a new manuscript that explains the theoretical underpinnings of our simulation.
+We thank the referee for their generous comments about our manuscript.
+The referee's main concern is that the details of our simulation algorithm were not presented in enough detail to judge our manuscript's validity, and states that after overcoming this problem, our manuscript will be "an excellent contribution to PRL".
+We have revised the main text to clarify several points, but our primary remedy to this deficiency is by appending supplementary material that we hope addresses the referee's concerns.
+Additionally, one of the authors has recently posted a separate manuscript to the arXiv (1610.05384) that details some of the theoretical underpinnings of our simulation.
 
+In response to the referee's specific concerns:
+1) As suggested by the referee, we have included supplementary material that significantly expands the discussion of the simulation algorithm, as well as providing a reference to a new manuscript that explains the theoretical basis of our simulation.
 2) We clarify this claim to simply note that we do not see a particular reason why we should expect any fundamental distinctions between the Ising and Fibonacci anyons, and that our methods could equally well be used to investigate alternative noise models if desired.
-
-3) We agree that this statement was vague, and so we soften it to simply note that we do not expect our threshold estimates to be particularly biased by this effect, as well as clarifying the surrounding discussion.
-
+3) We agree that this statement was vague, and so we soften it to simply note that we do not expect our threshold estimates to be particularly biased by the effect under consideration, as well as clarifying the surrounding discussion.
 4) We clarify the language to make it clear that we only find evidence for a threshold, rather than prove its existence, and that it is the existence of the threshold which would imply the asymptotically perfect storage of quantum information.
@@
 
-We believe that the ability to simulate error-correction in universal anyon models is a key development in the study of topological quantum computation.
-While the previous analogous calculations for non-universal nonabelian anyon codes are superficially similar, the structure of the present simuulations is significantly different and even the possibility of performing such a simulation may have been previously regarded as intractable.
+We thank the referee for their thoughtful comments on our manuscript.
+Though the referee is of the opinion that our present work is incremental and of restricted interest, we believe that the ability to simulate error-correction in universal anyon models is a key development in the study of topological quantum computation.
+While previous analogous calculations for non-universal nonabelian anyon codes are superficially similar, the structure of the present simulations is significantly different and even the possibility of performing such a simulation may have been previously regarded as intractable.
 We hope that the extended discussion of the simulation algorithm provided in the supplementary material will demonstrate the novel approach we have taken to this problem, as compared to our previous work.
-Since universal nonabelian anyons (and Fibonacci anyons in particular) are being pursued in many experimental architectures for the purpose of topological quantum computation, we believe that the ability to numerically benchmark topological error-correction protocols will have a significant impact on the field.
+Since universal nonabelian anyons (and Fibonacci anyons in particular) are being pursued in many diverse experimental architectures for the purpose of topological quantum computation, we believe that the ability to numerically benchmark topological error-correction protocols will have a significant impact on the field.
+
+In response to the referee's specific concerns:
 
@@
 Most protocols for fault-tolerant quantum computation are motivated precisely by the lack of a need to perform standard fault-tolerant quantum circuity constructions since the topological features can be exploited to provide protection.
-We demonstrate how to simulate this.
+We demonstrate how to simulate these schemes.
 
@@
 Obviously, the experimental details of an implementation of our error-correction protocol would vary significantly from architecture to architecture, but our protocol only makes use of basic topological operations (such as joint charge measurements and charge transport) which are natural in any system where anyonic excitations arise.
-Since more precide descriptions of how to implement these operations would unecessarily require restricting to a single experimental setup, we intentionally leave this question for future work.
-Our noise model is similarly vague but flexible, again accounting for sources of noise that are expected from generic topological systems with a mass gap.
+Since more precide descriptions of how to implement these operations (such as a circuit description) would unecessarily require restricting to a single experimental setup, we intentionally leave this question for future work.
+Our noise model is similarly vague but flexible, again accounting for sources of noise that are expected from generic topological systems with a mass gap, such as thermal excitations or stray fields.
 Again, if an analysis for a specific experimental apparatus were desired, our methods could be tailored to such a setting.
@@
 Due to space constraints, we have not been able to expand on this notation to the desired degree, but we have attempted to clarify this slightly, and provided a reference to a new manuscript where this presentation of topological operations is discussed in more detail.
-We have also attempted to explain the origin of the topological degeneracy as a flux through the non-trivial loop of the manifold.
+We have also explained the origin of the topological degeneracy as a flux through the non-trivial loop of the manifold.
 
@@
 
-- ?????
-We agree that this was poorly phrased, and have removed this remark.
+- We agree that this was poorly phrased, and have removed this remark.
 Our intention was merely to note that our reasoning for expecting the simulations to be efficient was of course an asymptotic argument, and that in the finite systems we study, we are nevertheless able to simulate in situations which could fall outside these nice cases, up to the lattice sizes shown.
@@
 - In response to another comment we have removed this argument. What we had meant was the error-correction protocol failing to return to the codespace.
+
+Summary of main changes made:
+- In abstract, clarified the error-correction threshold quoted
+- Added a note about physical systems that our work applies to
+- Cite the new manuscript arXiv:1610.05384 that includes more detailed discussion of the representation of topological operations used, and how it relates to our simulation algorithm
+- Described the origin of the topological degeneracy as a flux through the torus
+- Expanded the discussion of our justification for presenting pair-creation-only results
+- Expanded the discussion of the measure of noise strength useed
+- Added supplementary materials greatly expanding on the details of the simulation algorithm

### 2016-10-25 resubmit/main text/fib2.tex
resubmitted

--- 2016-10-11 fib2.tex
@@
 \usepackage{mathrsfs}
-
-%\usepackage{epstopdf} % to include .eps graphics files with pdfLaTeX
 
@@
 on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Fowler2015, Andrist2015}, which can be efficiently simulated due to the fact that they cannot be used for quantum computation.
-%Systems of abelian anyons are well suited to studying quantum 
-%error correction because (at the RG fixed point) noise and 
-%recovery processes can be efficiently simulated numerically, allowing lattice simulations 
-%of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. 
-%Standard algorithms are specifically tailored to exploit the abelian nature 
-%of these particles, particularly that abelian anyons cannot be used for quantum computation.
 
@@
 2-dimensional system with
-point-like anyonic quasiparticle excitations.%, which exhibit exotic statistics under exchange.
+point-like anyonic quasiparticle excitations.
 The worldlines of these particles form \emph{braids}
@@
 are total charge measurements within regions bounded by 
-closed loops.% (Wilson loops).
+closed loops.
 The possible results of such a charge measurement correspond to different anyon particle types in the model.
@@
 In contrast to the approach often taken, we consider the topological observables, rather than the anyons themselves, to be affected by braiding processes (see \Fref{f:braidloop}).
-%From the perspective of
-%\emph{topological quantum field theory},
-%anyons are modeled
-%as punctures in a surface~\cite{Pfeifer2014}, 
-%and the observables, rather than the anyons themselves, are considered to be deformed by braiding processes (see \Fref{f:braidloop}).
-%and it is not
-%the anyons themselves that braid,
-%but the manifold in which the anyons reside 
-%that becomes deformed (twisted) by these braid moves.
-%This is the perspective we adopt (see \Fref{f:braidloop}).
 
@@
 This process relates two different ways of fusing the top two charges.
-%In general, braiding will twist these loops in different ways following
-%the deformation of the manifold itself.
 \label{f:braidloop}
@@
 In contrast, outcomes for nonabelian charge measurements depend on the history of the particles as well as their type.
-%That is, the fusion space is one-dimensional for abelian anyons, and generally larger for nonabelian anyons.
+
 We consider a system supporting nonabelian Fibonacci
@@
 \end{align*}
-%For $n$ anyons of type $\tau$, the 
-%dimension of the fusion space grows asymptotically as $\varphi^n$, where $\varphi=\frac{1+\sqrt{5}}{2}$ 
-%is the golden ratio.
 
@@
 order the anyons, and track
-%deformations in the underlying space, 
-%i.e.\ 
-the history of braiding processes (see Ref.~\cite{CurveDiagrams} for a more comprehensive discussion).
-%It also denotes the direction along which $F$-moves occur. 
+the history of braiding processes (see Ref.~\cite{Burton2016} for a more comprehensive discussion).
 A clockwise braiding process, or \emph{half-twist}, is effected by an $R$-move:
@@
 It is easy to see that, in those cases where they are both appropriate, these two methods coincide in the limit of low error rates, and for the typical noise strengths we encounter in this paper, the discrepancy is around $10\%$ (see Ref.~\cite{Brell2013} for more details).
-%The thresholds we consider in this paper are on the order of $0.1$ noise processes per edge.
-In models where both noise strength measures are appropriate, such as the toric code under bit-flip errors, the discrepancy between the two values is around $10\%$ at these strengths.
 
@@
 a less important (and non-universal) role. Note also that our analysis applies equally well to either a continuum setting, or to discrete lattice models supporting anyonic excitations.
-%Additionally, while we model a continuum anyon theory, our analysis can be trivially reinterpreted to apply directly to lattice spin models or other systems where space is fundamentally discrete.
 
@@
 and so must repeatedly physically query the system to measure these charges.
-%This is also in contrast to abstract quantum codes, where syndrome extraction can typically be performed in one step.
 Our simulation proceeds in this way as a dialogue between decoder
@@
 when it performs a homologically nontrivial operation, thereby performing a potential logical error.
-%altering the 
-%codespace (and failing to perform successful recovery).
-%Note that, as was found in Ref.~\cite{Brell2013}, we expect that 
-%our qualitative results may be reproduced by most alternative families 
-%of decoders, although it may not be clear in all cases how to extend these decoders to the nonabelian setting.
-%The advantage of using a clustering decoder is 
-%its simplicity and flexibility, and the fact that its clustering 
-%scheme is compatible with the structure in the noise 
-%processes that allows us to classically simulate them.
 
@@
 become exponentially difficult in the system size.
-%Despite this, we use heuristics 
-%that minimize braid moves, which helps to
-%track the state beyond the
-%sub-percolated regime.
-%This enables simulation of error correction in
 Nevertheless, we are able to simulate error-correction in
@@
 procedure for a simple noise process is shown in \Fref{f:syndrome}.
-This procedure is discussed in more detail in the supplementary material, and the theoretical framework underlying it is expanded in Ref.~\cite{CurveDiagrams}.
-%The details of the algorithm and data structures used for 
-%this procedure will be discussed elsewhere.
+This procedure is discussed in more detail in the supplementary material, and the theoretical framework underlying it is expanded in Ref.~\cite{Burton2016}.
 Braiding processes that encircle 
@@
 In any case, we do not expect this possible discrepancy to be significant in our simulations.
-%However, naively computing the effect of the simplest possible homologically nontrivial operations consistently yields either a logical error or a complete failure to return to the codespace (see \Aref{s:homnontrivial}).
-As such it seems reasonable to suggest that neglecting the full simulation of
-%these events does not significantly affect our observed threshold value.
 
@@
 microscopic spin models or models with non-topological features would give 
-direct insight into practical error rates needed for nonabelian topological quantum memories.% in nonabelian systems. 
+direct insight into practical error rates needed for nonabelian topological quantum memories.
 It would also be interesting to find \emph{classical} spin models 
@@
 %------------------------------------------------------------------------------------------------------------%
-\acknowledgments
+\begin{acknowledgments}
 
@@
 
-\bibliography{refs2}
+\end{acknowledgments}
+
+%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{42}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Kitaev}(2003)}]{Kitaev2003}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~Y.}\ \bibnamefont
+  {Kitaev}},\ }\href {\doibase 10.1016/S0003-4916(02)00018-0} {\bibfield
+  {journal} {\bibinfo  {journal} {Ann. Phys.}\ }\textbf {\bibinfo {volume}
+  {303}},\ \bibinfo {pages} {2} (\bibinfo {year} {2003})},\ \Eprint
+  {http://arxiv.org/abs/quant-ph/9707021} {arXiv:quant-ph/9707021} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Dennis}\ \emph {et~al.}(2002)\citenamefont {Dennis},
+  \citenamefont {Kitaev}, \citenamefont {Landahl},\ and\ \citenamefont
+  {Preskill}}]{Dennis2002}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Dennis}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kitaev}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Landahl}}, \ and\
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Preskill}},\ }\href
+  {\doibase 10.1063/1.1499754} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Math. Phys.}\ }\textbf {\bibinfo {volume} {43}},\ \bibinfo {pages} {4452}
+  (\bibinfo {year} {2002})},\ \Eprint {http://arxiv.org/abs/quant-ph/0110143}
+  {arXiv:quant-ph/0110143} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Nayak}\ \emph {et~al.}(2008)\citenamefont {Nayak},
+  \citenamefont {Simon}, \citenamefont {Stern}, \citenamefont {Freedman},\ and\
+  \citenamefont {Das~Sarma}}]{Nayak2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Nayak}}, \bibinfo {author} {\bibfnamefont {S.~H.}\ \bibnamefont {Simon}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Stern}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Freedman}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Das~Sarma}},\ }\href {\doibase
+  10.1103/RevModPhys.80.1083} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
+  Mod. Phys.}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages} {1083}
+  (\bibinfo {year} {2008})},\ \Eprint {http://arxiv.org/abs/0707.1889}
+  {arXiv:0707.1889} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bravyi}\ \emph {et~al.}(2010)\citenamefont {Bravyi},
+  \citenamefont {Hastings},\ and\ \citenamefont {Michalakis}}]{Bravyi2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Bravyi}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Hastings}}, \
+  and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Michalakis}},\
+  }\href {\doibase 10.1063/1.3490195} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Math. Phys.}\ }\textbf {\bibinfo {volume} {51}},\ \bibinfo
+  {pages} {093512} (\bibinfo {year} {2010})},\ \Eprint
+  {http://arxiv.org/abs/1001.0344} {arXiv:1001.0344} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bravyi}\ and\ \citenamefont
+  {Hastings}(2011)}]{Bravyi2011a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Bravyi}}\ and\ \bibinfo {author} {\bibfnamefont {M.~B.}\ \bibnamefont
+  {Hastings}},\ }\href {\doibase 10.1007/s00220-011-1346-2} {\bibfield
+  {journal} {\bibinfo  {journal} {Comm. Math. Phys.}\ }\textbf {\bibinfo
+  {volume} {307}},\ \bibinfo {pages} {609} (\bibinfo {year} {2011})},\ \Eprint
+  {http://arxiv.org/abs/arXiv:1001.4363} {arXiv:1001.4363} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Michalakis}\ and\ \citenamefont
+  {Zwolak}(2013)}]{Michalakis2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Michalakis}}\ and\ \bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont
+  {Zwolak}},\ }\href {\doibase 10.1007/s00220-013-1762-6} {\bibfield  {journal}
+  {\bibinfo  {journal} {Comm. Math. Phys.}\ }\textbf {\bibinfo {volume}
+  {322}},\ \bibinfo {pages} {277} (\bibinfo {year} {2013})},\ \Eprint
+  {http://arxiv.org/abs/1109.1588} {arXiv:1109.1588} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wilczek}(1990)}]{Wilczek1990}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Wilczek}},\ }\href@noop {} {\emph {\bibinfo {title} {Fractional Statistics
+  and Anyon Superconductivity}}}\ (\bibinfo  {publisher} {World Scientific},\
+  \bibinfo {address} {Singapore},\ \bibinfo {year} {1990})\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Freedman}\ \emph {et~al.}(2002)\citenamefont
+  {Freedman}, \citenamefont {Larsen},\ and\ \citenamefont
+  {Wang}}]{Freedman2002}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~H.}\ \bibnamefont
+  {Freedman}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Larsen}}, \
+  and\ \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Wang}},\ }\href
+  {\doibase 10.1007/s002200200645} {\bibfield  {journal} {\bibinfo  {journal}
+  {Comm. Math. Phys.}\ }\textbf {\bibinfo {volume} {227}},\ \bibinfo {pages}
+  {605} (\bibinfo {year} {2002})},\ \Eprint
+  {http://arxiv.org/abs/quant-ph/0001108} {arXiv:quant-ph/0001108} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Pastawski}\ \emph {et~al.}(2010)\citenamefont
+  {Pastawski}, \citenamefont {Kay}, \citenamefont {Schuch},\ and\ \citenamefont
+  {Cirac}}]{Pastawski2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Pastawski}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kay}},
+  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Schuch}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {J.~I.}\ \bibnamefont {Cirac}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Quant. Inf. Comput.}\ }\textbf
+  {\bibinfo {volume} {10}},\ \bibinfo {pages} {580} (\bibinfo {year} {2010})},\
+  \Eprint {http://arxiv.org/abs/0911.3843} {arXiv:0911.3843} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Duclos-Cianci}\ and\ \citenamefont
+  {Poulin}(2010{\natexlab{a}})}]{Duclos-Cianci2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Duclos-Cianci}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Poulin}},\ }\href {\doibase 10.1103/PhysRevLett.104.050504} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {104}},\ \bibinfo {pages} {050504} (\bibinfo {year}
+  {2010}{\natexlab{a}})},\ \Eprint {http://arxiv.org/abs/0911.0581}
+  {arXiv:0911.0581} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Duclos-Cianci}\ and\ \citenamefont
+  {Poulin}(2010{\natexlab{b}})}]{Duclos-Cianci2010a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Duclos-Cianci}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Poulin}},\ }in\ \href {\doibase 10.1109/CIG.2010.5592866} {\emph {\bibinfo
+  {booktitle} {Information Theory Workshop (ITW), 2010 IEEE}}}\ (\bibinfo
+  {year} {2010})\ pp.\ \bibinfo {pages} {1--5},\ \Eprint
+  {http://arxiv.org/abs/1006.1362} {arXiv:1006.1362} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wang}\ \emph
+  {et~al.}(2010{\natexlab{a}})\citenamefont {Wang}, \citenamefont {Fowler},
+  \citenamefont {Stephens},\ and\ \citenamefont {Hollenberg}}]{Wang2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~S.}\ \bibnamefont
+  {Wang}}, \bibinfo {author} {\bibfnamefont {A.~G.}\ \bibnamefont {Fowler}},
+  \bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont {Stephens}}, \ and\
+  \bibinfo {author} {\bibfnamefont {L.~C.~L.}\ \bibnamefont {Hollenberg}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Quant. Inf.
+  Comput.}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {456}
+  (\bibinfo {year} {2010}{\natexlab{a}})},\ \Eprint
+  {http://arxiv.org/abs/0905.0531} {arXiv:0905.0531} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wang}\ \emph
+  {et~al.}(2010{\natexlab{b}})\citenamefont {Wang}, \citenamefont {Fowler},
+  \citenamefont {Hill},\ and\ \citenamefont {Hollenberg}}]{Wang2010a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~S.}\ \bibnamefont
+  {Wang}}, \bibinfo {author} {\bibfnamefont {A.~G.}\ \bibnamefont {Fowler}},
+  \bibinfo {author} {\bibfnamefont {C.~D.}\ \bibnamefont {Hill}}, \ and\
+  \bibinfo {author} {\bibfnamefont {L.~C.~L.}\ \bibnamefont {Hollenberg}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Quant. Inf.
+  Comput.}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {780}
+  (\bibinfo {year} {2010}{\natexlab{b}})},\ \Eprint
+  {http://arxiv.org/abs/0907.1708} {arXiv:0907.1708} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Duclos-Cianci}\ and\ \citenamefont
+  {Poulin}(2013)}]{Duclos-Cianci2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Duclos-Cianci}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Poulin}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Quant.
+  Inf. Comput.}\ } (\bibinfo {year} {2013})},\ \Eprint
+  {http://arxiv.org/abs/1304.6100} {arXiv:1304.6100} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bravyi}\ and\ \citenamefont
+  {Haah}(2013)}]{Bravyi2011}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Bravyi}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Haah}},\
+  }\href {\doibase 10.1103/PhysRevLett.111.200501} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {111}},\
+  \bibinfo {pages} {200501} (\bibinfo {year} {2013})},\ \Eprint
+  {http://arxiv.org/abs/1112.3252} {arXiv:1112.3252} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bombin}\ \emph {et~al.}(2012)\citenamefont {Bombin},
+  \citenamefont {Duclos-Cianci},\ and\ \citenamefont {Poulin}}]{Bombin2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Bombin}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Duclos-Cianci}}, \ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Poulin}},\ }\href {http://stacks.iop.org/1367-2630/14/i=7/a=073048}
+  {\bibfield  {journal} {\bibinfo  {journal} {New J. Phys.}\ }\textbf {\bibinfo
+  {volume} {14}},\ \bibinfo {pages} {073048} (\bibinfo {year} {2012})},\
+  \Eprint {http://arxiv.org/abs/1103.4606} {arXiv:1103.4606} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Wootton}\ and\ \citenamefont
+  {Loss}(2012)}]{Wootton2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont
+  {Wootton}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Loss}},\
+  }\href {\doibase 10.1103/PhysRevLett.109.160503} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {109}},\
+  \bibinfo {pages} {160503} (\bibinfo {year} {2012})},\ \Eprint
+  {http://arxiv.org/abs/1202.4316} {arXiv:1202.4316} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Anwar}\ \emph {et~al.}(2014)\citenamefont {Anwar},
+  \citenamefont {Brown}, \citenamefont {Campbell},\ and\ \citenamefont
+  {Browne}}]{Anwar2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Anwar}}, \bibinfo {author} {\bibfnamefont {B.~J.}\ \bibnamefont {Brown}},
+  \bibinfo {author} {\bibfnamefont {E.~T.}\ \bibnamefont {Campbell}}, \ and\
+  \bibinfo {author} {\bibfnamefont {D.~E.}\ \bibnamefont {Browne}},\ }\href
+  {\doibase 10.1088/1367-2630/16/6/063038} {\bibfield  {journal} {\bibinfo
+  {journal} {New J. Phys.}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo
+  {pages} {063038} (\bibinfo {year} {2014})},\ \Eprint
+  {http://arxiv.org/abs/1311.4895} {arXiv:1311.4895} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Watson}\ \emph {et~al.}(2014)\citenamefont {Watson},
+  \citenamefont {Anwar},\ and\ \citenamefont {Browne}}]{Watson2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.~H.~E.}\
+  \bibnamefont {Watson}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Anwar}}, \ and\ \bibinfo {author} {\bibfnamefont {D.~E.}\ \bibnamefont
+  {Browne}},\ }\href@noop {} {\  (\bibinfo {year} {2014})},\ \Eprint
+  {http://arxiv.org/abs/1411.3028} {arXiv:1411.3028} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hutter}\ \emph {et~al.}(2014)\citenamefont {Hutter},
+  \citenamefont {Wootton},\ and\ \citenamefont {Loss}}]{Hutter2014a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Hutter}}, \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Wootton}},
+  \ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Loss}},\ }\href
+  {\doibase 10.1103/PhysRevA.89.022326} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {89}},\ \bibinfo
+  {pages} {022326} (\bibinfo {year} {2014})},\ \Eprint
+  {http://arxiv.org/abs/1302.2669} {arXiv:1302.2669} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bravyi}\ \emph {et~al.}(2014)\citenamefont {Bravyi},
+  \citenamefont {Suchara},\ and\ \citenamefont {Vargo}}]{Bravyi2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Bravyi}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Suchara}}, \
+  and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Vargo}},\ }\href
+  {\doibase 10.1103/PhysRevA.90.032326} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {90}},\ \bibinfo
+  {pages} {032326} (\bibinfo {year} {2014})},\ \Eprint
+  {http://arxiv.org/abs/1405.4883} {arXiv:1405.4883} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wootton}(2015)}]{Wootton2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont
+  {Wootton}},\ }\href {\doibase 10.3390/e17041946} {\bibfield  {journal}
+  {\bibinfo  {journal} {Entropy}\ }\textbf {\bibinfo {volume} {17}},\ \bibinfo
+  {pages} {1946} (\bibinfo {year} {2015})},\ \Eprint
+  {http://arxiv.org/abs/1310.2393} {arXiv:1310.2393} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Fowler}(2015)}]{Fowler2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~G.}\ \bibnamefont
+  {Fowler}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Quant.
+  Inf. Comput.}\ }\textbf {\bibinfo {volume} {15}},\ \bibinfo {pages} {0145}
+  (\bibinfo {year} {2015})},\ \Eprint {http://arxiv.org/abs/1307.1740}
+  {arXiv:1307.1740} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Andrist}\ \emph {et~al.}(2015)\citenamefont
+  {Andrist}, \citenamefont {Wootton},\ and\ \citenamefont
+  {Katzgraber}}]{Andrist2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~S.}\ \bibnamefont
+  {Andrist}}, \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont
+  {Wootton}}, \ and\ \bibinfo {author} {\bibfnamefont {H.~G.}\ \bibnamefont
+  {Katzgraber}},\ }\href {\doibase 10.1103/PhysRevA.91.042331} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume}
+  {91}},\ \bibinfo {pages} {042331} (\bibinfo {year} {2015})},\ \Eprint
+  {http://arxiv.org/abs/1406.5974} {arXiv:1406.5974} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Brell}\ \emph {et~al.}(2014)\citenamefont {Brell},
+  \citenamefont {Burton}, \citenamefont {Dauphinais}, \citenamefont {Flammia},\
+  and\ \citenamefont {Poulin}}]{Brell2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~G.}\ \bibnamefont
+  {Brell}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Burton}},
+  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Dauphinais}}, \bibinfo
+  {author} {\bibfnamefont {S.~T.}\ \bibnamefont {Flammia}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Poulin}},\ }\href {\doibase
+  10.1103/PhysRevX.4.031058} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. X}\ }\textbf {\bibinfo {volume} {4}},\ \bibinfo {pages} {031058}
+  (\bibinfo {year} {2014})},\ \Eprint {http://arxiv.org/abs/1311.0019}
+  {arXiv:1311.0019} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wootton}\ \emph {et~al.}(2014)\citenamefont
+  {Wootton}, \citenamefont {Burri}, \citenamefont {Iblisdir},\ and\
+  \citenamefont {Loss}}]{Wootton2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont
+  {Wootton}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Burri}},
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Iblisdir}}, \ and\
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Loss}},\ }\href {\doibase
+  10.1103/PhysRevX.4.011051} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. X}\ }\textbf {\bibinfo {volume} {4}},\ \bibinfo {pages} {011051}
+  (\bibinfo {year} {2014})},\ \Eprint {http://arxiv.org/abs/1310.3846}
+  {arXiv:1310.3846} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hutter}\ \emph {et~al.}(2015)\citenamefont {Hutter},
+  \citenamefont {Loss},\ and\ \citenamefont {Wootton}}]{Hutter2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Hutter}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Loss}}, \ and\
+  \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Wootton}},\ }\href
+  {http://stacks.iop.org/1367-2630/17/i=3/a=035017} {\bibfield  {journal}
+  {\bibinfo  {journal} {New J. Phys.}\ }\textbf {\bibinfo {volume} {17}},\
+  \bibinfo {pages} {035017} (\bibinfo {year} {2015})},\ \Eprint
+  {http://arxiv.org/abs/1410.4478} {arXiv:1410.4478} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wootton}\ and\ \citenamefont
+  {Hutter}(2015)}]{Wootton2015b}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont
+  {Wootton}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Hutter}},\ }\href@noop {} {\  (\bibinfo {year} {2015})},\ \Eprint
+  {http://arxiv.org/abs/1506.00524} {arXiv:1506.00524} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hutter}\ and\ \citenamefont
+  {Wootton}(2015)}]{Hutter2015continuous}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Hutter}}\ and\ \bibinfo {author} {\bibfnamefont {J.~R.}\ \bibnamefont
+  {Wootton}},\ }\href@noop {} {\  (\bibinfo {year} {2015})},\ \Eprint
+  {http://arxiv.org/abs/1508.04033} {arXiv:1508.04033} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Slingerland}\ and\ \citenamefont
+  {Bais}(2001)}]{Slingerland2001}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~K.}\ \bibnamefont
+  {Slingerland}}\ and\ \bibinfo {author} {\bibfnamefont {F.~A.}\ \bibnamefont
+  {Bais}},\ }\href {\doibase 10.1016/S0550-3213(01)00308-X} {\bibfield
+  {journal} {\bibinfo  {journal} {Nucl. Phys. B}\ }\textbf {\bibinfo {volume}
+  {612}},\ \bibinfo {pages} {229} (\bibinfo {year} {2001})},\ \Eprint
+  {http://arxiv.org/abs/cond-mat/0104035} {arXiv:cond-mat/0104035} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Levin}\ and\ \citenamefont {Wen}(2005)}]{Levin2005}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Levin}}\ and\ \bibinfo {author} {\bibfnamefont {X.-G.}\ \bibnamefont
+  {Wen}},\ }\href {\doibase 10.1103/PhysRevB.71.045110} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {71}},\
+  \bibinfo {pages} {045110} (\bibinfo {year} {2005})},\ \Eprint
+  {http://arxiv.org/abs/cond-mat/0404617} {arXiv:cond-mat/0404617} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Bonesteel}\ and\ \citenamefont
+  {DiVincenzo}(2012)}]{Bonesteel2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
+  {Bonesteel}}\ and\ \bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont
+  {DiVincenzo}},\ }\href {\doibase 10.1103/PhysRevB.86.165113} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {86}},\ \bibinfo {pages} {165113} (\bibinfo {year} {2012})},\ \Eprint
+  {http://arxiv.org/abs/1206.6048} {arXiv:1206.6048} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kapit}\ and\ \citenamefont
+  {Simon}(2013)}]{Kapit2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Kapit}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Simon}},\
+  }\href {\doibase 10.1103/PhysRevB.88.184409} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {88}},\ \bibinfo
+  {pages} {184409} (\bibinfo {year} {2013})},\ \Eprint
+  {http://arxiv.org/abs/1307.3485} {arXiv:1307.3485} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Palumbo}\ and\ \citenamefont
+  {Pachos}(2014)}]{Palumbo2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Palumbo}}\ and\ \bibinfo {author} {\bibfnamefont {J.~K.}\ \bibnamefont
+  {Pachos}},\ }\href {\doibase 10.1103/PhysRevD.90.027703} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. D}\ }\textbf {\bibinfo {volume}
+  {90}},\ \bibinfo {pages} {027703} (\bibinfo {year} {2014})},\ \Eprint
+  {http://arxiv.org/abs/1311.2871} {arXiv:1311.2871} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mong}\ \emph {et~al.}(2014)\citenamefont {Mong},
+  \citenamefont {Clarke}, \citenamefont {Alicea}, \citenamefont {Lindner},
+  \citenamefont {Fendley}, \citenamefont {Nayak}, \citenamefont {Oreg},
+  \citenamefont {Stern}, \citenamefont {Berg}, \citenamefont {Shtengel},\ and\
+  \citenamefont {Fisher}}]{Mong2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~S.~K.}\
+  \bibnamefont {Mong}}, \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
+  {Clarke}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Alicea}},
+  \bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont {Lindner}}, \bibinfo
+  {author} {\bibfnamefont {P.}~\bibnamefont {Fendley}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Nayak}}, \bibinfo {author} {\bibfnamefont
+  {Y.}~\bibnamefont {Oreg}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Stern}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Berg}},
+  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Shtengel}}, \ and\
+  \bibinfo {author} {\bibfnamefont {M.~P.~A.}\ \bibnamefont {Fisher}},\ }\href
+  {\doibase 10.1103/PhysRevX.4.011036} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {4}},\ \bibinfo {pages}
+  {011036} (\bibinfo {year} {2014})},\ \Eprint {http://arxiv.org/abs/1307.4403}
+  {arXiv:1307.4403} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wang}(2010)}]{Wang2010b}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
+  {Wang}},\ }\href@noop {} {\emph {\bibinfo {title} {Topological quantum
+  computation}}}\ (\bibinfo  {publisher} {American Mathematical Society},\
+  \bibinfo {year} {2010})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Burton}(2016)}]{Burton2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Burton}},\ }\href {http://arxiv.org/abs/1610.05384} {\  (\bibinfo {year}
+  {2016})},\ \Eprint {http://arxiv.org/abs/arXiv:1610.05384} {arXiv:1610.05384}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hastie}\ \emph {et~al.}(2009)\citenamefont {Hastie},
+  \citenamefont {Tibshirani},\ and\ \citenamefont {Friedman}}]{Hastie2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Hastie}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Tibshirani}},
+  \ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Friedman}},\
+  }\href@noop {} {\emph {\bibinfo {title} {The elements of statistical
+  learning}}}\ (\bibinfo  {publisher} {Springer},\ \bibinfo {year}
+  {2009})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bazant}(2000)}]{Bazant2000}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~Z.}\ \bibnamefont
+  {Bazant}},\ }\href {\doibase 10.1103/PhysRevE.62.1660} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. E}\ }\textbf {\bibinfo {volume} {62}},\
+  \bibinfo {pages} {1660} (\bibinfo {year} {2000})},\ \Eprint
+  {http://arxiv.org/abs/cond-mat/9905191} {arXiv:cond-mat/9905191} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Grimmett}(1989)}]{Grimmett1989}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Grimmett}},\ }\href@noop {} {\emph {\bibinfo {title} {Percolation}}},\
+  \bibinfo {edition} {2nd}\ ed.\ (\bibinfo  {publisher} {Springer},\ \bibinfo
+  {year} {1989})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Pfeifer}\ \emph {et~al.}(2012)\citenamefont
+  {Pfeifer}, \citenamefont {Buerschaper}, \citenamefont {Trebst}, \citenamefont
+  {Ludwig}, \citenamefont {Troyer},\ and\ \citenamefont {Vidal}}]{Pfeifer2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~N.~C.}\
+  \bibnamefont {Pfeifer}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
+  {Buerschaper}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Trebst}},
+  \bibinfo {author} {\bibfnamefont {A.~W.~W.}\ \bibnamefont {Ludwig}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Troyer}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {G.}~\bibnamefont {Vidal}},\ }\href {\doibase
+  10.1103/PhysRevB.86.155111} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. B}\ }\textbf {\bibinfo {volume} {86}},\ \bibinfo {pages} {155111}
+  (\bibinfo {year} {2012})},\ \Eprint {http://arxiv.org/abs/1005.5486}
+  {arXiv:1005.5486} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hastings}\ \emph {et~al.}(2014)\citenamefont
+  {Hastings}, \citenamefont {Watson},\ and\ \citenamefont
+  {Melko}}]{Hastings2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~B.}\ \bibnamefont
+  {Hastings}}, \bibinfo {author} {\bibfnamefont {G.~H.}\ \bibnamefont
+  {Watson}}, \ and\ \bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
+  {Melko}},\ }\href {\doibase 10.1103/PhysRevLett.112.070501} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {112}},\ \bibinfo {pages} {070501} (\bibinfo {year} {2014})},\
+  \Eprint {http://arxiv.org/abs/1309.2680} {arXiv:1309.2680} \BibitemShut
+  {NoStop}%
+\end{thebibliography}%
 

### 2016-10-25 resubmit/supp/supplement.tex
resubmitted

\documentclass[aps, letterpaper, onecolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
\usepackage{times}

% use these settings for a more reader-friendly version
%\documentclass[aps, pra, a4paper, 11pt, onecolumn, nofootinbib, superscriptaddress, tightenlines, notitlepage, longbibliography]{revtex4-1}

%------------------------------------------------------------------------------------------------------------%
% Packages
%------------------------------------------------------------------------------------------------------------%

\usepackage{xcolor}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{enumitem}

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,calc}

\usepackage[pdfpagelabels,pdftex,bookmarks,breaklinks]{hyperref}
\definecolor{darkblue}{RGB}{0,0,127} % choose colors
\definecolor{darkgreen}{RGB}{0,150,0}
\hypersetup{colorlinks, linkcolor=darkblue, citecolor=darkgreen, filecolor=red, urlcolor=blue}
\hypersetup{pdfauthor={Simon Burton, Courtney G. Brell, Steven T. Flammia}}
\hypersetup{pdftitle={Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code}}

\usepackage[normalem]{ulem}

%------------------------------------------------------------------------------------------------------------%
\begin{document}

\title{Supplemental material for ``Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code''}

\author{Simon Burton}
\affiliation{Centre for Engineered Quantum Systems, School of Physics, 
The University of Sydney, Sydney, Australia}
\author{Courtney G.\ Brell}
\affiliation{Institut f\"{u}r Theoretische Physik, Leibniz Universit\"{a}t Hannover, 
Appelstra\ss{}e 2, 30167 Hannover, Germany}
\affiliation{Perimeter Institute for Theoretical Physics, 
Waterloo, Canada}
\author{Steven T.\ Flammia}
\affiliation{Centre for Engineered Quantum Systems, School of Physics, 
The University of Sydney, Sydney, Australia}

\date{\today}

\maketitle

%------------------------------------------------------------------------------------------------------------%
% Macros
%------------------------------------------------------------------------------------------------------------%

\newcommand{\Eref}[1]{Eq.~(\ref{#1})}
\newcommand{\Fref}[1]{Fig.~\ref{#1}}
\newcommand{\Aref}[1]{Appendix~\ref{#1}}

\newcommand{\e}{\mathrm{e}}
\newcommand{\vac}{\mathbb{I}}

\newcommand{\ket}[1]{|{#1}\rangle}
\newcommand{\expect}[1]{\langle{#1}\rangle}
\newcommand{\bra}[1]{\langle{#1}|}
\newcommand{\ketbra}[2]{\ket{#1}\!\bra{#2}}
\newcommand{\braket}[2]{\langle{#1}|{#2}\rangle}
\newcommand{\proj}[1]{\ketbra{#1}{#1}}

\newcommand{\cggb}[1]{\textcolor{blue}{#1}}
\newcommand{\simon}[1]{\textcolor{red}{#1}}
\newcommand{\stf}[1]{\textcolor{green}{#1}}

\newcommand{\F}{\mathscr{H}} % H or F ?
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\Hom}{{\mathrm{Hom}}}

\newcommand{\subsub}[1]{{\bf #1}}

%------------------------------------------------------------------------------------------------------------%

\newcommand{\ntikzmark}[2]{#2\thinspace\tikz[overlay,remember picture,baseline=(#1.base)]{\node[inner sep=0pt] (#1) {};}}

\newcommand{\makebrace}[3]{%
    \begin{tikzpicture}[overlay, remember picture]
        \draw [decoration={brace,amplitude=0.5em},decorate]
        let \p1=(#1), \p2=(#2) in
        ({max(\x1,\x2)}, {\y1+0.8em}) -- node[right=0.6em] {#3} ({max(\x1,\x2)}, {\y2});
    \end{tikzpicture}
}

In order to estimate the error-correction threshold of Fibonacci anyon codes, we perform monte-carlo simulations of noise and recovery operations on systems of various sizes. For a given sample, the simulation can be broken down into several stages:
\begin{itemize}[noitemsep, topsep=0pt]
\item \ntikzmark{N}{Noise}
\item \ntikzmark{S}{Syndrome extraction}
\item \ntikzmark{D}{Decoding}
\item \ntikzmark{R}{Recovery}
\end{itemize}
\makebrace{S}{R}{Error-correction}
After application of noise, the subsequent three steps (forming the error-correction routine) are iterated until success or failure, as will be described in more detail below.

It should be noted that while the noise, syndrome extraction, and recovery steps of this procedure are intended to really be a simulation of the physics of an anyon system, the decoding step is better thought of as an implementation of the classical processing that a successful error-correction experiment will require. Furthermore, the simulation of the noise and recovery steps will be rendered straightforward by the way we model our system in the first place. As such, the main novelty of our simulations is in the model itself, and the syndrome extraction step.

The key to simulating these processes effectively is the ability to describe topological operations by \emph{curve diagrams}. This is an alternative representation of topological operations that is particularly suited to these kinds of numerical simulations of sparsely populated 2-dimensional anyon systems. The theoretical framework underpinning this description and the relation to to other representations of topological operations is discussed in Ref.~\cite{Burton2016}.

In this supplementary material, we first describe our physical model of an anyon system and the corresponding noise, before showing how to simulate joint charge measurements (the core of syndrome extraction) within this model. The use of curve-diagrams is presented in an intuitive but ad-hoc way. Finally we describe our decoder and detail holistically how the different parts of the simulation interact.

\section{Physical model}

We consider anyon systems defined on a torus.
We endow this with a $L\times L$ square lattice of observables:
$$
    \Lambda := \bigl\{ \gamma_{ij} \bigr\}_{i,j=1,...,L}
$$
These observables are the physically accessible charge observables that will be measured during syndrome extraction, before being passed to the decoder which will in turn determine physical recovery operations to be performed on the system.

We call each $\gamma_{ij}$ a \emph{tile.}
In figures we show a small gap between the tiles but this is not meant
to reflect an actual physical gap.

As noted above, the key to our model is to represent anyons and topological operations with curve diagrams. A curve diagram is a directed path that connects several anyons, which are denoted by preferred points along these paths. A curve diagram specifies a linear ordering of the anyons that allows us to define a basis for the corresponding fusion space, as well as to keep track of topological operations on this ordering. See Ref.~\cite{Burton2016} for a more formal introduction to curve diagrams.

The main noise processes we consider in our simulations are pair-creation events, though other topological processes such as hopping, exchange, etc.~can also be implemented straightforwardly.
The pair-creation process acts to populate the manifold with
a randomly distributed set of anyon pairs,
whose separation is much smaller than the size of a tile.

Each such pair will have vacuum total charge and so the observables
$\gamma_{ij}$ will only be affected by pairs that cross a tile boundary, i.e.~we
need only consider distributing these pairs along edges of the tiles:
\begin{center}
\includegraphics[width=0.3\columnwidth ]{pic-pair-create.pdf}
\end{center}

In simulating system undergoing noise for time $T$, we place a Poisson-distributed number of pair-creation events on the edges of tiles, with mean $2L^2T$.

In order to allow us to later calculate fusion outcomes for sets of anyons, in addition to locations of created anyons we also assign each pair a (directed) piece of curve, denoted in green. This curve can be thought of as a choice of fusion basis for the anyons along it. Since the total charge of any newly-created particle-antiparticle pair is vacuum, each of their fusion spaces can be treated independently. This results in our being able to consider independent disconnected curves for each such pair. We only need consider the joint state in the fusion space of different sets of anyons if they have interacted, and so it is with curve diagrams. Using this picture, it is easy to track the effects of moving anyons, which essentially are represented by appropriate extensions or deformations of the curve along which the anyon lies. These kinds of straightforward processes are all that are required to describe the noise and recovery steps of our simulation.

\section{Syndrome extraction}

Syndrome extraction in this model corresponds to simulating measurements of the observables $\gamma_{ij}$, which represent the total charge contained within the corresponding tile.

In order to compute measurement outcomes for the $\gamma_{ij}$
we first need to concatenate any two curve diagrams that 
participate in the same $\gamma_{ij}.$
Because each curve has vacuum total charge this can be
done in an arbitrary way:
\begin{center}
\includegraphics[width=0.3\columnwidth ]{pic-join-pairs.pdf}
\end{center}

Working in the basis picked out by the resulting curve
diagrams, we will show how to calculate measurement outcomes for each tile,
the result of which is recorded on the original curve:
\begin{center}
\includegraphics[width=0.3\columnwidth ]{pic-curve-uniq.pdf}
\end{center}

%
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
%

The basic data structure involved in the
simulation we term a \emph{combinatorial curve diagram.}
Firstly, we will require each curve to intersect 
the edges of tiles transversally,
and in particular a curve will not touch a tile corner.

For each tile in the lattice,
we store a combinatorial
description of the curve(s) intersected with that tile.
Each component of such an intersection we call a \emph{piece-of-curve.}
\begin{center}
\includegraphics[]{pic-cells.pdf}
\end{center}

We follow essentially the same approach as taken in \cite{Abramsky2007} 
to describe elements of a Temperley-Leib algebra, but
with some extra decorations.
The key idea is to store a \emph{word} for each tile, comprised of
the letters $\bigl<$ and $\bigr>$.
Reading in a clockwise direction around the edge of
the tile from the top-left corner,
we record our encounters with each piece-of-curve,
writing~$\bigl<$ for the first encounter, and~$\bigr>$ for the
second.
We may also encounter a dangling piece-of-curve
(the head or the tail), so we use another symbol $*$ for this.
The words for the above two tiles will then be 
$\bigl<\bigl<\bigr>\bigr>\bigl<\bigr>$ and $\bigl<\bigr>*\bigl<\bigl<\bigr>\bigr>.$
When the brackets are balanced,
each such word will correspond one-to-one with an intersection
of a curve in a tile, up to a continuous deformation of the interior of the tile.
Ie. the data structure 
will be insensitive to any continuous deformation of the interior of the tile,
but the simulation does not need to track any of these degrees of freedom.

\begin{center}
\includegraphics[]{pic-cells-0.pdf}
\end{center}

We will also need to record
various other attributes of these curves,
and to do this we make this notation more elaborate
in the paragraphs {\bf (I)}, {\bf(II)} and {\bf(III)} below.
Each symbol in the word describes an intersection of
the curve with the tile boundary,
and so as we decorate these symbols these decorations will
apply to such intersection points.

\begin{center}
\includegraphics[]{pic-cells-1.pdf}
\end{center}

{\bf (I)} We will record the direction of each piece-of-curve,
this will be either an {\tt in} or {\tt out} decoration for each symbol.
Such decorations need to balance according to the brackets.
The decorated symbols $*_{\mbox{\tt in}}$ and 
$*_{\mbox{\tt out}}$ 
will denote respectively either
the head or the tail of a curve.
The words for the diagrams above now read as
$ \bigl<_{\mbox{\tt in}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}
    \bigr>_{\mbox{\tt out}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}$
and
$ \bigl<_{\mbox{\tt in}}\bigl>_{\mbox{\tt out}}*_{\mbox{\tt in}}
    \bigr<_{\mbox{\tt out}}
    \bigr<_{\mbox{\tt in}}\bigl>_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}.
$

{\bf (II)} We will record,
for each intersection with the tile edge, 
a numeral indicating which of the four
sides of the tile the
intersection occurs on.
Numbering these clockwise from the top as $1, 2, 3, 4$ we have for the above curves: 
$\bigl<_1\bigl<_2\bigr>_2\bigr>_3\bigl<_3\bigr>_4$ 
and $\bigl<_1\bigr>_1*_2\bigl<_3\bigl<_3\bigr>_4\bigr>_4.$

{\bf (III)} Finally, we will also decorate these symbols with anyons.
This will be an index to a leaf of a (sum of) fusion tree(s).
This means that anyons only reside on the curve close
to the tile boundary,
and so we cannot have more than two anyons
for each piece-of-curve. 
The number of such pieces is arbitrary, and so this
is no restriction on generality.

\begin{center}
\includegraphics[]{pic-cells-2.pdf}
\end{center}

In joining tiles together to make a tiling we will
require adjacent tiles to agree on their shared boundary.
This will entail sequentially pairing symbols in the
words for adjacent tiles
and requiring that 
the {\tt in} and {\tt out} decorations are matched.
Because the word for a tile proceeds conter-clockwise
around the tile, this pairing will always reverse the
sequential order of the symbols of adjacent tiles.
For example, given the above two tiles we sequentially pair the 
$\bigl<_{\mbox{\tt out},2}\bigr>_{\mbox{\tt in},2}$ 
and $\bigr>_{\mbox{\tt out},4}\bigr>_{\mbox{\tt in},4}$
symbols with opposite order so that
$\bigl<_{\mbox{\tt out},2}\sim\bigr>_{\mbox{\tt in},4}$
and $\bigr>_{\mbox{\tt in},2} \sim \bigr>_{\mbox{\tt out},4}.$

Note that in general, this will allow us to store the multiple disjoint curve diagrams that cover the lattice.

For each piece-of-curve, apart from a head or tail, there is an associated 
number we call the \emph{turn number}. This counts the number
of ``right-hand turns'' the piece-of-curve makes as it
traverses the tile, with a ``left-hand turn'' counting as $-1.$
This number will take one of the values $-2, -1, 0, 1, 2:$
\begin{center}
\includegraphics[]{pic-cells-3.pdf}
\end{center}

%
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
%

\section{The paperclip algorithm}

In order to calculate the total charge of each tile, we must transport all anyons within the tile until they are neighbours along their curve. In doing so, it will be convenient to consider transporting these anyons by moving them along tile edges. This is equivalent to a ``refactoring'' of the fusion space, as described in Ref.~\cite{Burton2016}. We can further break down transport along the tile edge into a sequence of transports between neighbouring pieces of curve at that edge.
The origin and destination of such a path
now splits the curve diagram
into three disjoint pieces which we term
\emph{head}, \emph{body} and \emph{tail}, where
the head contains the endpoint of the curve, the tail
contains the beginning of the curve and the body is the remainder.
Here we consider transport forwards along the curve (from tail towards head), but the reverse case is analogous.
\begin{center}
\includegraphics[]{pic-move-anyon.pdf}
\end{center}

This arrangement is equivalent (isotopic) to one of four 
``paperclips'', which we distinguish between by counting how
many \emph{right-hand turns} are made along the body of the curve diagram.
We also show an equivalent (isotopic) picture where the
curve diagram has been straightened, and the resulting distortion
in the anyon path:
\begin{center}
\includegraphics[]{pic-paperclip.pdf}
\end{center}
In order to perform the desired transport, we must braid the anyon under consideration around the other anyons along the curve diagram. Denoting the sequence of anyons along the head, body and tail, $H, B$ and $T,$
respectively, and using
$H^r, B^r$ and $T^r$ to denote the same anyons with the reversed order, the appropriate braiding transformation ($R$-move) can be read off for each
of the four paperclips:
\begin{align*}
-2:&\ R[B] \\
-4:&\ R[H^r]\ R[H]\ R[B] \\
+4:&\ R[B]\ R[T]\ R[T^r] \\
+6:&\ R[H^r]\ R[H]\ R[B]\ R[T]\ R[T^r] \\
\end{align*}
where notation such as $R[B]$ is understood as sequentially clockwise braiding around
each anyon in $B$.

Once all the anyons within a tile have been brought into a sequential piece of the curve, their total charge can easily be read off by an appropriate $F$-move. This allows us to perform syndrome extraction, by repeating this procedure for each tile of the lattice.

%
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
%

\section{Decoding and error-correction}

After the noise process is applied to the system,
the error correction routine attempts to annihilate all the anyons on the lattice in a way that does not affect the encoded information. It proceeds as a dialogue between the
decoder and the system. The syndrome extraction procedure provides information to the decoder, which suggests a recovery procedure, the results of which are found by a subsequent syndrome extraction step, and so on. This iterative procedure continues until the extracted syndrome is empty (i.e.~i.e. there are no remaining anyons on the lattice), or the decoder declares failure.
Here we show this in a process diagram, with time running up
the page:
\begin{center}
\includegraphics[]{pic-process.pdf}
\end{center}

So far we have discussed the simulation of the (quantum) system
and now we turn to the decoder algorithm. This is similar to other clustering-type decoders used in the literature~\cite{Bravyi2011}, in that it attempts to form and fuse together clusters of anyons on larger and larger length scales, declaring failure if anyons remain after fusion at the largest length scale. Our simulation also declares failure if at any point the curve diagrams describing the state of the system form a homologically non-trivial loop (span the lattice), this being a necessary condition for error-correction failure.

The structure of the error-correction routine is as follows, and will be illustrated by an example below.

\begin{verbatim}
 1:  def error_correct():
 2:      syndrome = get_syndrome()
 3:      
 4:      # build a cluster for each charge
 5:      clusters = [Cluster(charge) for charge in syndrome]
 6:  
 7:      # join any neighbouring clusters
 8:      join(clusters, 1)
 9:      
10:      while clusters:
11:      
12:          # find total charge on each cluster
13:          for cluster in clusters:
14:              fuse_cluster(cluster)
15:      
16:          # discard vacuum clusters
17:          clusters = [cluster for cluster in clusters if non_vacuum(cluster)]
18:      
19:          # grow each cluster by 1 unit
20:          for cluster in clusters:
21:              grow_cluster(cluster, 1)
22:      
23:          # join any intersecting clusters
24:          join(clusters, 0)
25:  
26:      # success !
27:      return True
\end{verbatim}

First, we show the result of the initial call to {\tt get\_syndrome()}, on line 2. This is computed using the syndrome extraction step as described above.
The locations of anyon charges are highlighted in red.
For each of these charges we build a {\tt Cluster}, on line 5.
Each cluster is shown as a gray shaded area.
\begin{center}
\includegraphics[]{pic-decode-0.pdf}
\end{center}
The next step is the call to {\tt join(clusters, 1)}, on line 8,
which joins clusters that are separated by at most one lattice
spacing. We now have seven clusters:
\begin{center}
\includegraphics[]{pic-decode-1.pdf}
\end{center}
Each cluster is structured as a rooted tree, as indicated by
the arrows which point in the direction from the leaves to
the root of the tree. 
This tree structure is used in the call to {\tt fuse\_cluster()},
on line 14.
This moves anyons in the tree along the arrows to the root, 
fusing with the charge at the root. This movement of anyons is a physical recovery operation that is easily simulated by extending the curve diagram along the transport path, and moving the anyons along it.
\begin{center}
\includegraphics[]{pic-decode-2.pdf}
\end{center}
For each cluster, the charge is then measured using the syndrome extraction procedure, and the resulting charge at the root is taken as the charge of
that cluster. Any cluster with vacuum total charge is then discarded (line 17).
In our example, we find two clusters with vacuum charge and we discard these.
The next step is to grow the remaining clusters by one lattice spacing (line 20-21),
and join (merge) any overlapping clusters (line 24).
\begin{center}
\includegraphics[]{pic-decode-3.pdf}
\end{center}
Note that we can choose the root of each cluster arbitrarily
since we are only interested in the total charge of each cluster, and also that for simplicity we have neglected the boundary of the lattice in
this example.

We repeat these steps of fusing, growing and then joining clusters (lines 10-24.)
If at any point this causes a topologically 
non-trivial operation, the simulation aborts and a failure
to decode is recorded.
Otherwise we eventually run out
of non-vacuum clusters, and the decoder succeeds (line 27).

By repeatedly performing this simulation of noise and error-correction on different sized lattices, and for different noise rates (or memory lifetimes), we are able to estimate the error-correction threshold for this type of system.

%------------------------------------------------------------------------------------------------------------%

%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (8) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (-1) disabled
%Control: page (0) single
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\begin{thebibliography}{3}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{http://dx.doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Burton}(2016)}]{Burton2016}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Burton}},\ }\href {http://arxiv.org/abs/1610.05384} {\  (\bibinfo {year}
  {2016})},\ \Eprint {http://arxiv.org/abs/arXiv:1610.05384} {arXiv:1610.05384}
  \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Abramsky}(2007)}]{Abramsky2007}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Abramsky}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Mathematics of
  Quantum Computing and Technology}}},\ \bibinfo {editor} {edited by\ \bibinfo
  {editor} {\bibfnamefont {L.~K.}\ \bibnamefont {G.~Chen}}\ and\ \bibinfo
  {editor} {\bibfnamefont {S.}~\bibnamefont {Lomonaco}}}\ (\bibinfo
  {publisher} {Taylor \& Francis},\ \bibinfo {year} {2007})\ pp.\ \bibinfo
  {pages} {415--458}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Bravyi}\ and\ \citenamefont
  {Haah}(2013)}]{Bravyi2011}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Bravyi}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Haah}},\
  }\href {\doibase 10.1103/PhysRevLett.111.200501} {\bibfield  {journal}
  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {111}},\
  \bibinfo {pages} {200501} (\bibinfo {year} {2013})},\ \Eprint
  {http://arxiv.org/abs/1112.3252} {arXiv:1112.3252} \BibitemShut {NoStop}%
\end{thebibliography}%

\end{document}

### 2016-12-06 reresubmit/Response.txt
Reresubmission draft: merged supplementary material with main text, draft response to referee

We believe that, given the comments of the three referees, this manuscript may now be appropriate for publication in PR. We have previously addressed the substantive concerns of Referees A and B, and we believe that our current submission has addressed the main concerns of Referee C. Relevant comments from the referees:

Referee A
"The article is very well written and solves a substantial open problem"
"After [revision], the article will be an excellent contribution"

Referee B
"I suggest that the paper is submitted to PRA"

Referee C
"The topic is important both for quantum information science and condensed matter physics"
"I highly suggest the authors to submit the manuscript to PRX"

Response to Referee C:

We thank the referee for their thoughtful comments. We hope that our response clarifies the applicability and scope of our work. Our responses to each comment follow:

(1) It is unclear that the estimated logical error probability
reflects the true logical error probability appropriately. Suppose two
pair creations occur simultaneously nearby, two anyons are braided
with each other, and then syndrome is measured after that. If pair
annihilations are done by the decoder, the original information seems
to be restored according to the authors analysis. But it does not
return to the original one because of the braiding of two anyons. From
what reason, the authors can neglect the braiding process of anyons,
which occurs with a high probability around the threshold? How can the
authors fairly validate their simulation neglecting the braiding
dynamics of the anyons?

Response: In fact, treating the effects that the referee describes was the main challenge of our work. In the model that we used in this paper, the logical state was encoded in the non-trivial topology of the manifold. This meant that only braids that form homologically non-trivial loops will affect the encoded information. In any case, we have simulated completely all the outcomes of braids between anyons (including any effect on the logical state), which was our main technical achievement, and so we have been careful not to neglect any important effects that they may have on the error-correction process.

(2) Do the authors assume that quantum computation is done by anyonic
excitations? If so, we have to consider the dynamics between the
anyons which are employed for quantum computation and undesired
excitations. In the case of the topological codes consisting of qubits
or qudits, we can enlarge the topological defects (and hence the code
distance). However this is not the case for the "physical" anyons
encoding the logical quantum information. If a pair creation occur
nearby it and the excitation is braided around the anyon encoding the
logical quantum information, the logical information would be
destroyed. This seems to worsen the threshold.

Response: Our results apply equally well to a code where the information is stored in the topology of the manifold as to a code where the information is stored in the fusion outcomes of several non-abelian anyons, as would be the case in an anyonic quantum computer. We explicitly treated both cases in our previous work for non-universal non-abelian anyons (Phys. Rev. X 4, 031058). If the information were stored in fusion outcomes of multiple anyons, one might be concerned about braid processes where "noise" anyons braid around the "code" anyons. However, in comparison to topological defects like punctures, such a braid is not a logical error. Since the logical degree of freedom is the joint fusion channel of a pair of anyons, only braid processes that go around the entire pair will contribute to a logical error. A braid that goes around a single code anyon may interact with the charge of that anyon, but it will not interact with the logical state. This is the principal strength of topological fault tolerance for anyonic computation. In our error-correction procedure, we fuse each code anyon with any charges that lie near it, and this reverses any effects of small braids around that code anyons. The fact that one need not enlarge the size of an anyon to increase the distance of the code (as would be the case with punctures) can actually be an advantage in some circumstances by reducing the overhead.

(3) While the introduction of the non-Abelian anyon system is quite
pedagogical and is well mathematically organized, the main
contribution of the manuscript, that is, the proposed efficient
algorithm to sample the non-Abelian anyons on the lattice is described
unclearly. The authors should write down the procedure more explicitly
by using equations and mathematics. The lack of the concrete
description unfortunately make it hard to justify the novelty of the
proposal.

Response: We have attempted to address this concern by merging the supplementary material, where the main discussion of our algorithm takes place, with the main text.

### 2016-12-06 reresubmit/main text/fib2.tex
Reresubmission draft: merged supplementary material with main text, draft response to referee

--- 2016-10-11 fib2.tex
@@
-\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
+\documentclass[aps, pra, letterpaper, onecolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
 \usepackage{times}
@@
 
-\usepackage{color}
+\usepackage{xcolor}
 \usepackage{amsmath,amsfonts,amssymb}
@@
 \usepackage{mathrsfs}
+\usepackage{enumitem}
 
-%\usepackage{epstopdf} % to include .eps graphics files with pdfLaTeX
+\usepackage{tikz}
+\usetikzlibrary{decorations.pathreplacing,calc}
 
@@
 
-\newcommand{\cggb}[1]{\textcolor{blue}{#1}}
+\newcommand{\F}{\mathscr{H}} % H or F ?
+\newcommand{\C}{\mathbb{C}}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\A}{\mathcal{A}}
+\newcommand{\Hom}{{\mathrm{Hom}}}
+
+\newcommand{\subsub}[1]{{\bf #1}}
 
@@
 
+We will first introduce our setting and notation by giving a brief review of the background of Fibonacci anyons and error-correction for such systems in Section \ref{s:background}, before sketching an argument for why we expect these dynamics to be classically simulable in the regime of interest and outlining our simulation algorithm in Section \ref{s:simulation}.
+We then present numerical results and a discussion in Section \ref{s:results}.
+A more detailed explanation of our model, simulation algorithm, and error-correction protocol follows in Section \ref{s:technical}.
+
 %------------------------------------------------------------------------------------------------------------%
-\paragraph{Topological model.}
+
+\section{Background}\label{s:background}
+
+\subsection{Topological model}
 
@@
 In contrast, outcomes for nonabelian charge measurements depend on the history of the particles as well as their type.
-%That is, the fusion space is one-dimensional for abelian anyons, and generally larger for nonabelian anyons.
+That is, the fusion space of a set of abelian anyons is one-dimensional, while it is generally larger for nonabelian anyons.
+
 We consider a system supporting nonabelian Fibonacci
@@
 \end{align*}
-%For $n$ anyons of type $\tau$, the 
-%dimension of the fusion space grows asymptotically as $\varphi^n$, where $\varphi=\frac{1+\sqrt{5}}{2}$ 
-%is the golden ratio.
+For $n$ anyons of type $\tau$, the dimension of the fusion space grows asymptotically as $\varphi^n$, where $\varphi=\frac{1+\sqrt{5}}{2}$ is the golden ratio.
 
@@
 order the anyons, and track
-%deformations in the underlying space, 
-%i.e.\ 
-the history of braiding processes (see Ref.~\cite{CurveDiagrams} for a more comprehensive discussion).
-%It also denotes the direction along which $F$-moves occur. 
+the history of braiding processes (see Ref.~\cite{Burton2016} for a more comprehensive discussion). It also denotes the direction along with $F$-moves occur.
 A clockwise braiding process, or \emph{half-twist}, is effected by an $R$-move:
@@
 In addition to the fusion space there is also a global degeneracy associated with the topology of the 
-manifold on which the anyons reside. We consider systems on a torus, 
+manifold on which the anyons reside. We consider systems with the topology of a torus, 
 which for the Fibonacci anyons gives rise to a 2-fold degeneracy.
@@
 %------------------------------------------------------------------------------------------------------------%
-\paragraph{Noise and error-correction.}
+\subsection{Noise and error-correction}
 
@@
 and follows a similar strategy to the hard-decision renormalization group decoder~\cite{Bravyi2011}. 
-The error-correction protocol and simulation procedure are discussed in more depth in the supplementary material.
+The error-correction protocol and simulation procedure are discussed in more depth in Section \ref{s:technical}.
 
@@
 when it performs a homologically nontrivial operation, thereby performing a potential logical error.
-%altering the 
-%codespace (and failing to perform successful recovery).
-%Note that, as was found in Ref.~\cite{Brell2013}, we expect that 
-%our qualitative results may be reproduced by most alternative families 
-%of decoders, although it may not be clear in all cases how to extend these decoders to the nonabelian setting.
-%The advantage of using a clustering decoder is 
-%its simplicity and flexibility, and the fact that its clustering 
-%scheme is compatible with the structure in the noise 
-%processes that allows us to classically simulate them.
+Note that, as was found in Ref.~\cite{Brell2013}, we expect that our qualitative results may be reproduced by most alternative families of decoders, although it may not be clear in all cases how to extend these decoders to the nonabelian setting.
+The advantage of using a clustering decoder is its simplicity and flexibility, and the fact that its clustering scheme is compatible with the structure of the noise processes that allows us to classically simulate them.
 
@@
 \begin{center}
-	\includegraphics[width=1.0\columnwidth]{pic-decode.pdf}
+	\includegraphics[width=0.7\columnwidth]{pic-decode.pdf}
 \caption{The decoder works by maintaining a set of disjoint clusters as rooted trees.
@@
 %------------------------------------------------------------------------------------------------------------%
-\paragraph{Classical simulability.}
+\section{Simulation}\label{s:simulation}
+
+\subsection{Classical simulability}
 
@@
 %------------------------------------------------------------------------------------------------------------%	
-\paragraph{Simulation algorithm.}
+\subsection{Simulation algorithm}
 
@@
 procedure for a simple noise process is shown in \Fref{f:syndrome}.
-This procedure is discussed in more detail in the supplementary material, and the theoretical framework underlying it is expanded in Ref.~\cite{CurveDiagrams}.
-%The details of the algorithm and data structures used for 
-%this procedure will be discussed elsewhere.
+This procedure is discussed in more detail in Section \ref{s:technical}, and the theoretical framework underlying it is expanded in Ref.~\cite{Burton2016}.
 Braiding processes that encircle 
@@
 \begin{center}
-	\includegraphics[width=1.0\columnwidth]{pic-syndrome.pdf}
+	\includegraphics[width=0.7\columnwidth]{pic-syndrome.pdf}
 \caption{
@@
 %------------------------------------------------------------------------------------------------------------%
-\paragraph{Numerical results.}
+
+\section{Results}\label{s:results}
+
+\subsection{Numerical results}
 
@@
 \begin{center}
-	\includegraphics[width=\columnwidth]{anyons-kyle.pdf}
+	\includegraphics[width=0.7\columnwidth]{anyons-kyle.pdf}
 \caption{The decoder failure rate (a lower bound on the logical error probability) is shown as a function of simulation time for linear lattice sizes from $L=16$ to $128$. 
@@
 In any case, we do not expect this possible discrepancy to be significant in our simulations.
-%However, naively computing the effect of the simplest possible homologically nontrivial operations consistently yields either a logical error or a complete failure to return to the codespace (see \Aref{s:homnontrivial}).
-As such it seems reasonable to suggest that neglecting the full simulation of
-%these events does not significantly affect our observed threshold value.
 
 %------------------------------------------------------------------------------------------------------------%
-\paragraph{Discussion.}
+\subsection{Discussion}
 
@@
 %------------------------------------------------------------------------------------------------------------%
-\acknowledgments
+
+\section{Technical details}\label{s:technical}
+
+\newcommand{\ntikzmark}[2]{#2\thinspace\tikz[overlay,remember picture,baseline=(#1.base)]{\node[inner sep=0pt] (#1) {};}}
+
+\newcommand{\makebrace}[3]{%
+    \begin{tikzpicture}[overlay, remember picture]
+        \draw [decoration={brace,amplitude=0.5em},decorate]
+        let \p1=(#1), \p2=(#2) in
+        ({max(\x1,\x2)}, {\y1+0.8em}) -- node[right=0.6em] {#3} ({max(\x1,\x2)}, {\y2});
+    \end{tikzpicture}
+}
+
+In order to estimate the error-correction threshold of Fibonacci anyon codes, we perform monte-carlo simulations of noise and recovery operations on systems of various sizes.
+For a given sample, the simulation can be broken down into several stages:
+\begin{itemize}[noitemsep, topsep=0pt]
+\item \ntikzmark{N}{Noise}
+\item \ntikzmark{S}{Syndrome extraction}
+\item \ntikzmark{D}{Decoding}
+\item \ntikzmark{R}{Recovery}
+\end{itemize}
+\makebrace{S}{R}{Error-correction}
+After application of noise, the subsequent three steps (forming the error-correction routine) are iterated until success or failure, as will be described in more detail below.
+
+It should be noted that while the noise, syndrome extraction, and recovery steps of this procedure are intended to really be a simulation of the physics of an anyon system, the decoding step is better thought of as an implementation of the classical processing that a successful error-correction experiment will require.
+Furthermore, the simulation of the noise and recovery steps will be rendered straightforward by the way we model our system in the first place.
+As such, the main novelty of our simulations is in the model itself, and the syndrome extraction step.
+
+The key to simulating these processes effectively is the ability to describe topological operations by \emph{curve diagrams}.
+This is an alternative representation of topological operations that is particularly suited to these kinds of numerical simulations of sparsely populated 2-dimensional anyon systems.
+The theoretical framework underpinning this description and the relation to to other representations of topological operations is discussed in Ref.~\cite{Burton2016}.
+
+In this section, we first describe our physical model of an anyon system and the corresponding noise, before showing how to simulate joint charge measurements (the core of syndrome extraction) within this model.
+The use of curve-diagrams is presented in an intuitive but ad-hoc way.
+Finally we describe our decoder and detail holistically how the different parts of the simulation interact.
+
+\subsection{Physical model}
+
+We consider anyon systems defined on a torus.
+We endow this with a $L\times L$ square lattice of observables:
+$$
+    \Lambda := \bigl\{ \gamma_{ij} \bigr\}_{i,j=1,...,L}
+$$
+These observables are the physically accessible charge observables that will be measured during syndrome extraction, before being passed to the decoder which will in turn determine physical recovery operations to be performed on the system.
+
+We call each $\gamma_{ij}$ a \emph{tile.}
+In figures we show a small gap between the tiles but this is not meant
+to reflect an actual physical gap.
+
+As noted above, the key to our model is to represent anyons and topological operations with curve diagrams.
+A curve diagram is a directed path that connects several anyons, which are denoted by preferred points along these paths.
+A curve diagram specifies a linear ordering of the anyons that allows us to define a basis for the corresponding fusion space, as well as to keep track of topological operations on this ordering.
+See Ref.~\cite{Burton2016} for a more formal introduction to curve diagrams.
+
+The main noise processes we consider in our simulations are pair-creation events, though other topological processes such as hopping, exchange, etc.~can also be implemented straightforwardly.
+The pair-creation process acts to populate the manifold with
+a randomly distributed set of anyon pairs,
+whose separation is much smaller than the size of a tile.
+
+Each such pair will have vacuum total charge and so the observables
+$\gamma_{ij}$ will only be affected by pairs that cross a tile boundary, i.e.~we
+need only consider distributing these pairs along edges of the tiles:
+\begin{center}
+\includegraphics[width=0.3\columnwidth ]{pic-pair-create.pdf}
+\end{center}
+
+In simulating system undergoing noise for time $T$, we place a Poisson-distributed number of pair-creation events on the edges of tiles, with mean $2L^2T$.
+
+In order to allow us to later calculate fusion outcomes for sets of anyons, in addition to locations of created anyons we also assign each pair a (directed) piece of curve, denoted in green.
+This curve can be thought of as a choice of fusion basis for the anyons along it.
+Since the total charge of any newly-created particle-antiparticle pair is vacuum, each of their fusion spaces can be treated independently.
+This results in our being able to consider independent disconnected curves for each such pair.
+We only need consider the joint state in the fusion space of different sets of anyons if they have interacted, and so it is with curve diagrams.
+Using this picture, it is easy to track the effects of moving anyons, which essentially are represented by appropriate extensions or deformations of the curve along which the anyon lies.
+These kinds of straightforward processes are all that are required to describe the noise and recovery steps of our simulation.
+
+\subsection{Syndrome extraction}
+
+Syndrome extraction in this model corresponds to simulating measurements of the observables $\gamma_{ij}$, which represent the total charge contained within the corresponding tile.
+
+In order to compute measurement outcomes for the $\gamma_{ij}$
+we first need to concatenate any two curve diagrams that 
+participate in the same $\gamma_{ij}.$
+Because each curve has vacuum total charge this can be
+done in an arbitrary way:
+\begin{center}
+\includegraphics[width=0.3\columnwidth ]{pic-join-pairs.pdf}
+\end{center}
+
+Working in the basis picked out by the resulting curve
+diagrams, we will show how to calculate measurement outcomes for each tile,
+the result of which is recorded on the original curve:
+\begin{center}
+\includegraphics[width=0.3\columnwidth ]{pic-curve-uniq.pdf}
+\end{center}
+
+%
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+%
+
+The basic data structure involved in the
+simulation we term a \emph{combinatorial curve diagram.}
+Firstly, we will require each curve to intersect 
+the edges of tiles transversally,
+and in particular a curve will not touch a tile corner.
+
+For each tile in the lattice,
+we store a combinatorial
+description of the curve(s) intersected with that tile.
+Each component of such an intersection we call a \emph{piece-of-curve.}
+\begin{center}
+\includegraphics[]{pic-cells.pdf}
+\end{center}
+
+We follow essentially the same approach as taken in \cite{Abramsky2007} 
+to describe elements of a Temperley-Leib algebra, but
+with some extra decorations.
+The key idea is to store a \emph{word} for each tile, comprised of
+the letters $\bigl<$ and $\bigr>$.
+Reading in a clockwise direction around the edge of
+the tile from the top-left corner,
+we record our encounters with each piece-of-curve,
+writing~$\bigl<$ for the first encounter, and~$\bigr>$ for the
+second.
+We may also encounter a dangling piece-of-curve
+(the head or the tail), so we use another symbol $*$ for this.
+The words for the above two tiles will then be 
+$\bigl<\bigl<\bigr>\bigr>\bigl<\bigr>$ and $\bigl<\bigr>*\bigl<\bigl<\bigr>\bigr>.$
+When the brackets are balanced,
+each such word will correspond one-to-one with an intersection
+of a curve in a tile, up to a continuous deformation of the interior of the tile.
+Ie. the data structure 
+will be insensitive to any continuous deformation of the interior of the tile,
+but the simulation does not need to track any of these degrees of freedom.
+
+\begin{center}
+\includegraphics[]{pic-cells-0.pdf}
+\end{center}
+
+We will also need to record
+various other attributes of these curves,
+and to do this we make this notation more elaborate
+in the paragraphs {\bf (I)}, {\bf(II)} and {\bf(III)} below.
+Each symbol in the word describes an intersection of
+the curve with the tile boundary,
+and so as we decorate these symbols these decorations will
+apply to such intersection points.
+
+\begin{center}
+\includegraphics[]{pic-cells-1.pdf}
+\end{center}
+
+{\bf (I)} We will record the direction of each piece-of-curve,
+this will be either an {\tt in} or {\tt out} decoration for each symbol.
+Such decorations need to balance according to the brackets.
+The decorated symbols $*_{\mbox{\tt in}}$ and 
+$*_{\mbox{\tt out}}$ 
+will denote respectively either
+the head or the tail of a curve.
+The words for the diagrams above now read as
+$ \bigl<_{\mbox{\tt in}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}
+    \bigr>_{\mbox{\tt out}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}$
+and
+$ \bigl<_{\mbox{\tt in}}\bigl>_{\mbox{\tt out}}*_{\mbox{\tt in}}
+    \bigr<_{\mbox{\tt out}}
+    \bigr<_{\mbox{\tt in}}\bigl>_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}.
+$
+
+{\bf (II)} We will record,
+for each intersection with the tile edge, 
+a numeral indicating which of the four
+sides of the tile the
+intersection occurs on.
+Numbering these clockwise from the top as $1, 2, 3, 4$ we have for the above curves: 
+$\bigl<_1\bigl<_2\bigr>_2\bigr>_3\bigl<_3\bigr>_4$ 
+and $\bigl<_1\bigr>_1*_2\bigl<_3\bigl<_3\bigr>_4\bigr>_4.$
+
+{\bf (III)} Finally, we will also decorate these symbols with anyons.
+This will be an index to a leaf of a (sum of) fusion tree(s).
+This means that anyons only reside on the curve close
+to the tile boundary,
+and so we cannot have more than two anyons
+for each piece-of-curve. 
+The number of such pieces is arbitrary, and so this
+is no restriction on generality.
+
+\begin{center}
+\includegraphics[]{pic-cells-2.pdf}
+\end{center}
+
+In joining tiles together to make a tiling we will
+require adjacent tiles to agree on their shared boundary.
+This will entail sequentially pairing symbols in the
+words for adjacent tiles
+and requiring that 
+the {\tt in} and {\tt out} decorations are matched.
+Because the word for a tile proceeds conter-clockwise
+around the tile, this pairing will always reverse the
+sequential order of the symbols of adjacent tiles.
+For example, given the above two tiles we sequentially pair the 
+$\bigl<_{\mbox{\tt out},2}\bigr>_{\mbox{\tt in},2}$ 
+and $\bigr>_{\mbox{\tt out},4}\bigr>_{\mbox{\tt in},4}$
+symbols with opposite order so that
+$\bigl<_{\mbox{\tt out},2}\sim\bigr>_{\mbox{\tt in},4}$
+and $\bigr>_{\mbox{\tt in},2} \sim \bigr>_{\mbox{\tt out},4}.$
+
+Note that in general, this will allow us to store the multiple disjoint curve diagrams that cover the lattice.
+
+For each piece-of-curve, apart from a head or tail, there is an associated 
+number we call the \emph{turn number}. This counts the number
+of ``right-hand turns'' the piece-of-curve makes as it
+traverses the tile, with a ``left-hand turn'' counting as $-1.$
+This number will take one of the values $-2, -1, 0, 1, 2:$
+\begin{center}
+\includegraphics[]{pic-cells-3.pdf}
+\end{center}
+
+%
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+%
+
+\subsection{The paperclip algorithm}
+
+In order to calculate the total charge of each tile, we must transport all anyons within the tile until they are neighbours along their curve.
+In doing so, it will be convenient to consider transporting these anyons by moving them along tile edges.
+This is equivalent to a ``refactoring'' of the fusion space, as described in Ref.~\cite{Burton2016}.
+We can further break down transport along the tile edge into a sequence of transports between neighbouring pieces of curve at that edge.
+The origin and destination of such a path
+now splits the curve diagram
+into three disjoint pieces which we term
+\emph{head}, \emph{body} and \emph{tail}, where
+the head contains the endpoint of the curve, the tail
+contains the beginning of the curve and the body is the remainder.
+Here we consider transport forwards along the curve (from tail towards head), but the reverse case is analogous.
+\begin{center}
+\includegraphics[]{pic-move-anyon.pdf}
+\end{center}
+
+This arrangement is equivalent (isotopic) to one of four 
+``paperclips'', which we distinguish between by counting how
+many \emph{right-hand turns} are made along the body of the curve diagram.
+We also show an equivalent (isotopic) picture where the
+curve diagram has been straightened, and the resulting distortion
+in the anyon path:
+\begin{center}
+\includegraphics[]{pic-paperclip.pdf}
+\end{center}
+In order to perform the desired transport, we must braid the anyon under consideration around the other anyons along the curve diagram.
+Denoting the sequence of anyons along the head, body and tail, $H, B$ and $T,$
+respectively, and using
+$H^r, B^r$ and $T^r$ to denote the same anyons with the reversed order, the appropriate braiding transformation ($R$-move) can be read off for each
+of the four paperclips:
+\begin{align*}
+-2:&\ R[B] \\
+-4:&\ R[H^r]\ R[H]\ R[B] \\
++4:&\ R[B]\ R[T]\ R[T^r] \\
++6:&\ R[H^r]\ R[H]\ R[B]\ R[T]\ R[T^r] \\
+\end{align*}
+where notation such as $R[B]$ is understood as sequentially clockwise braiding around
+each anyon in $B$.
+
+Once all the anyons within a tile have been brought into a sequential piece of the curve, their total charge can easily be read off by an appropriate $F$-move.
+This allows us to perform syndrome extraction, by repeating this procedure for each tile of the lattice.
+
+%
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+%
+
+\subsection{Decoding and error-correction}
+
+After the noise process is applied to the system,
+the error correction routine attempts to annihilate all the anyons on the lattice in a way that does not affect the encoded information. It proceeds as a dialogue between the
+decoder and the system.
+The syndrome extraction procedure provides information to the decoder, which suggests a recovery procedure, the results of which are found by a subsequent syndrome extraction step, and so on.
+This iterative procedure continues until the extracted syndrome is empty (i.e.~i.e.
+there are no remaining anyons on the lattice), or the decoder declares failure.
+Here we show this in a process diagram, with time running up
+the page:
+\begin{center}
+\includegraphics[]{pic-process.pdf}
+\end{center}
+
+So far we have discussed the simulation of the (quantum) system
+and now we turn to the decoder algorithm.
+This is similar to other clustering-type decoders used in the literature~\cite{Bravyi2011}, in that it attempts to form and fuse together clusters of anyons on larger and larger length scales, declaring failure if anyons remain after fusion at the largest length scale.
+Our simulation also declares failure if at any point the curve diagrams describing the state of the system form a homologically non-trivial loop (span the lattice), this being a necessary condition for error-correction failure.
+
+The structure of the error-correction routine is as follows, and will be illustrated by an example below.
+
+\begin{verbatim}
+ 1:  def error_correct():
+ 2:      syndrome = get_syndrome()
+ 3:      
+ 4:      # build a cluster for each charge
+ 5:      clusters = [Cluster(charge) for charge in syndrome]
+ 6:  
+ 7:      # join any neighbouring clusters
+ 8:      join(clusters, 1)
+ 9:      
+10:      while clusters:
+11:      
+12:          # find total charge on each cluster
+13:          for cluster in clusters:
+14:              fuse_cluster(cluster)
+15:      
+16:          # discard vacuum clusters
+17:          clusters = [cluster for cluster in clusters if non_vacuum(cluster)]
+18:      
+19:          # grow each cluster by 1 unit
+20:          for cluster in clusters:
+21:              grow_cluster(cluster, 1)
+22:      
+23:          # join any intersecting clusters
+24:          join(clusters, 0)
+25:  
+26:      # success !
+27:      return True
+\end{verbatim}
+
+First, we show the result of the initial call to {\tt get\_syndrome()}, on line 2. This is computed using the syndrome extraction step as described above.
+The locations of anyon charges are highlighted in red.
+For each of these charges we build a {\tt Cluster}, on line 5.
+Each cluster is shown as a gray shaded area.
+\begin{center}
+\includegraphics[]{pic-decode-0.pdf}
+\end{center}
+The next step is the call to {\tt join(clusters, 1)}, on line 8,
+which joins clusters that are separated by at most one lattice
+spacing. We now have seven clusters:
+\begin{center}
+\includegraphics[]{pic-decode-1.pdf}
+\end{center}
+Each cluster is structured as a rooted tree, as indicated by
+the arrows which point in the direction from the leaves to
+the root of the tree. 
+This tree structure is used in the call to {\tt fuse\_cluster()},
+on line 14.
+This moves anyons in the tree along the arrows to the root, 
+fusing with the charge at the root.
+This movement of anyons is a physical recovery operation that is easily simulated by extending the curve diagram along the transport path, and moving the anyons along it.
+\begin{center}
+\includegraphics[]{pic-decode-2.pdf}
+\end{center}
+For each cluster, the charge is then measured using the syndrome extraction procedure, and the resulting charge at the root is taken as the charge of
+that cluster. Any cluster with vacuum total charge is then discarded (line 17).
+In our example, we find two clusters with vacuum charge and we discard these.
+The next step is to grow the remaining clusters by one lattice spacing (line 20-21),
+and join (merge) any overlapping clusters (line 24).
+\begin{center}
+\includegraphics[]{pic-decode-3.pdf}
+\end{center}
+Note that we can choose the root of each cluster arbitrarily
+since we are only interested in the total charge of each cluster, and also that for simplicity we have neglected the boundary of the lattice in
+this example.
+
+We repeat these steps of fusing, growing and then joining clusters (lines 10-24.)
+If at any point this causes a topologically 
+non-trivial operation, the simulation aborts and a failure
+to decode is recorded.
+Otherwise we eventually run out
+of non-vacuum clusters, and the decoder succeeds (line 27).
+
+By repeatedly performing this simulation of noise and error-correction on different sized lattices, and for different noise rates (or memory lifetimes), we are able to estimate the error-correction threshold for this type of system.
+
+%------------------------------------------------------------------------------------------------------------%
+
+\begin{acknowledgments}
 
@@
 
+\end{acknowledgments}
+
 \bibliography{refs2}

### 2016-12-06 reresubmit/Response.txt
Some polish on the reply.

@@
-We believe that, given the comments of the three referees, this manuscript may now be appropriate for publication in PR.
-We have previously addressed the substantive concerns of Referees A and B, and we believe that our current submission has addressed the main concerns of Referee C.
-Relevant comments from the referees:
+We would like to thank the three referees for their comments on our manuscript.
+We have previously addressed the substantive concerns of Referees A and B, and in our current submission we have addressed the main concerns of Referee C.
+We believe that we have now addressed all of the concerns of the three referees and that our manuscript is now appropriate for publication in the Physical Review.
+We highlight some relevant comments from the referees in support of our manuscript:
 
@@
 This is the principal strength of topological fault tolerance for anyonic computation.
-In our error-correction procedure, we fuse each code anyon with any charges that lie near it, and this reverses any effects of small braids around that code anyons.
+In our error-correction procedure, we fuse each code anyon with any charges that lie near it, and this reverses any effects of small braids around that code anyon.
 The fact that one need not enlarge the size of an anyon to increase the distance of the code (as would be the case with punctures) can actually be an advantage in some circumstances by reducing the overhead.
@@
 
-Response: We have attempted to address this concern by merging the supplementary material, where the main discussion of our algorithm takes place, with the main text.
+Response: We have addressed this concern by merging the supplementary material, where the main discussion of our algorithm takes place, with the main text, together with a few additional clarifying remarks.
+We hope that the pseudo code description of our algorithm is a sufficient aid to help non-experts grasp the principles involved.
+However, we recognize that a complete reimplementation of our work would require a thorough understanding of the prior literature on quantum decoders, and that it might not be completely detailed as a standalone document.
+Given that other referees (nb Ref A) have commented that the paper was well written, we had to choose between adding additional pedagogical material, or trusting that non-experts would get a coarser but hopefully satisfactory understanding from the current text.
+Because many of the ideas in our decoder are standard in the literature, we have opted to keep our current description, and we hope this is sufficient.
+
+In summary, we believe we have addressed all of the concerns and that the manuscript is now suitable for publication in Physical Review A.

### 2016-12-07 reresubmit/Response.txt
tweaks

@@
 Response: We have addressed this concern by merging the supplementary material, where the main discussion of our algorithm takes place, with the main text, together with a few additional clarifying remarks.
-We hope that the pseudo code description of our algorithm is a sufficient aid to help non-experts grasp the principles involved.
+We hope that the pseudo-code description of our algorithm, along with explicit description of the data structures used, is a sufficient aid to help non-experts grasp the principles involved.
 However, we recognize that a complete reimplementation of our work would require a thorough understanding of the prior literature on quantum decoders, and that it might not be completely detailed as a standalone document.
-Given that other referees (nb Ref A) have commented that the paper was well written, we had to choose between adding additional pedagogical material, or trusting that non-experts would get a coarser but hopefully satisfactory understanding from the current text.
-Because many of the ideas in our decoder are standard in the literature, we have opted to keep our current description, and we hope this is sufficient.
+We had to choose between adding additional pedagogical material, or trusting that non-experts would get a coarser but hopefully satisfactory understanding from the current text.
+Because many of the ideas in our error-correction protocol are standard in the literature, we have opted to keep our current description, and we hope this is sufficient.
 

### 2016-12-07 reresubmit/main text/fib2.tex
tweaks

@@
 Given the toroidal boundary 
-conditions, this space contains the two-fold degenerate codespace.
+conditions, this space is the two-fold degenerate codespace.
 
@@
 a non-trivial loop of our (toric) manifold can also be 
-treated in an analogous way, following e.g.~\cite{Pfeifer2012}.
+treated in an analogous way, following e.g.~Ref.~\cite{Pfeifer2012}.
 
@@
 This procedure is iterated until either the decoder terminates successfully, 
-or the simulation itself declares failure.
+or the simulation itself declares failure because the components become too large to analyze (roughly when they span the lattice).
 
@@
 These observables are the physically accessible charge observables that will be measured during syndrome extraction, before being passed to the decoder which will in turn determine physical recovery operations to be performed on the system.
-
 We call each $\gamma_{ij}$ a \emph{tile.}
@@
 Syndrome extraction in this model corresponds to simulating measurements of the observables $\gamma_{ij}$, which represent the total charge contained within the corresponding tile.
-
 In order to compute measurement outcomes for the $\gamma_{ij}$
@@
 each such word will correspond one-to-one with an intersection
-of a curve in a tile, up to a continuous deformation of the interior of the tile.
-Ie. the data structure 
+of a curve in a tile, up to a continuous deformation of the interior of the tile,
+i.e.~the data structure 
 will be insensitive to any continuous deformation of the interior of the tile,

### 2016-12-08 reresubmit/Response.txt
submitted version for pra

@@
 We had to choose between adding additional pedagogical material, or trusting that non-experts would get a coarser but hopefully satisfactory understanding from the current text.
-Because many of the ideas in our error-correction protocol are standard in the literature, we have opted to keep our current description, and we hope this is sufficient.
+Because many of the ideas in our error-correction protocol are standard in the literature, we have opted to integrate and clarify our current description, and we hope this is sufficient.
 

### 2016-12-08 reresubmit/main text/fib2.tex
submitted version for pra

--- 2016-10-25 resubmit/main text/fib2.tex
@@
 \usepackage{mathrsfs}
+\usepackage{enumitem}
+
+\usepackage{tikz}
+\usetikzlibrary{decorations.pathreplacing,calc}
 
@@
 
-%------------------------------------------------------------------------------------------------------------%
-\paragraph{Topological model.}
+We will first introduce our setting and notation by giving a brief review of the background of Fibonacci anyons and error-correction for such systems in Section \ref{s:background}, before sketching an argument for why we expect these dynamics to be classically simulable in the regime of interest and outlining our simulation algorithm in Section \ref{s:simulation}.
+We then present numerical results and a discussion in Section \ref{s:results}.
+A more detailed explanation of our model, simulation algorithm, and error-correction protocol follows in Section \ref{s:technical}.
+
+%------------------------------------------------------------------------------------------------------------%
+
+\section{Background}\label{s:background}
+
+\subsection{Topological model}
 
@@
 In contrast, outcomes for nonabelian charge measurements depend on the history of the particles as well as their type.
+That is, the fusion space of a set of abelian anyons is one-dimensional, while it is generally larger for nonabelian anyons.
 
@@
 \end{align*}
+For $n$ anyons of type $\tau$, the dimension of the fusion space grows asymptotically as $\varphi^n$, where $\varphi=\frac{1+\sqrt{5}}{2}$ is the golden ratio.
 
@@
 order the anyons, and track
-the history of braiding processes (see Ref.~\cite{Burton2016} for a more comprehensive discussion).
+the history of braiding processes (see Ref.~\cite{Burton2016} for a more comprehensive discussion). It also denotes the direction along with $F$-moves occur.
 A clockwise braiding process, or \emph{half-twist}, is effected by an $R$-move:
@@
 when it performs a homologically nontrivial operation, thereby performing a potential logical error.
+Note that, as was found in Ref.~\cite{Brell2013}, we expect that our qualitative results may be reproduced by most alternative families of decoders, although it may not be clear in all cases how to extend these decoders to the nonabelian setting.
+The advantage of using a clustering decoder is its simplicity and flexibility, and the fact that its clustering scheme is compatible with the structure of the noise processes that allows us to classically simulate them.
 
@@
 procedure for a simple noise process is shown in \Fref{f:syndrome}.
-This procedure is discussed in more detail in the supplementary material, and the theoretical framework underlying it is expanded in Ref.~\cite{Burton2016}.
+This procedure is discussed in more detail in Section \ref{s:technical}, and the theoretical framework underlying it is expanded in Ref.~\cite{Burton2016}.
 Braiding processes that encircle 
 a non-trivial loop of our (toric) manifold can also be 
-treated in an analogous way, following e.g.~\cite{Pfeifer2012}.
+treated in an analogous way, following e.g.~Ref.~\cite{Pfeifer2012}.
 
@@
 This procedure is iterated until either the decoder terminates successfully, 
-or the simulation itself declares failure.
-
-%------------------------------------------------------------------------------------------------------------%
-\paragraph{Numerical results.}
+or the simulation itself declares failure because the components become too large to analyze (roughly when they span the lattice).
+
+%------------------------------------------------------------------------------------------------------------%
+
+\section{Results}\label{s:results}
+
+\subsection{Numerical results}
 
@@
 %------------------------------------------------------------------------------------------------------------%
-\paragraph{Discussion.}
+\subsection{Discussion}
 
@@
 %------------------------------------------------------------------------------------------------------------%
+
+\section{Technical details}\label{s:technical}
+
+\newcommand{\ntikzmark}[2]{#2\thinspace\tikz[overlay,remember picture,baseline=(#1.base)]{\node[inner sep=0pt] (#1) {};}}
+
+\newcommand{\makebrace}[3]{%
+    \begin{tikzpicture}[overlay, remember picture]
+        \draw [decoration={brace,amplitude=0.5em},decorate]
+        let \p1=(#1), \p2=(#2) in
+        ({max(\x1,\x2)}, {\y1+0.8em}) -- node[right=0.6em] {#3} ({max(\x1,\x2)}, {\y2});
+    \end{tikzpicture}
+}
+
+In order to estimate the error-correction threshold of Fibonacci anyon codes, we perform monte-carlo simulations of noise and recovery operations on systems of various sizes.
+For a given sample, the simulation can be broken down into several stages:
+\begin{itemize}[noitemsep, topsep=0pt]
+\item \ntikzmark{N}{Noise}
+\item \ntikzmark{S}{Syndrome extraction}
+\item \ntikzmark{D}{Decoding}
+\item \ntikzmark{R}{Recovery}
+\end{itemize}
+\makebrace{S}{R}{Error-correction}
+After application of noise, the subsequent three steps (forming the error-correction routine) are iterated until success or failure, as will be described in more detail below.
+
+It should be noted that while the noise, syndrome extraction, and recovery steps of this procedure are intended to really be a simulation of the physics of an anyon system, the decoding step is better thought of as an implementation of the classical processing that a successful error-correction experiment will require.
+Furthermore, the simulation of the noise and recovery steps will be rendered straightforward by the way we model our system in the first place.
+As such, the main novelty of our simulations is in the model itself, and the syndrome extraction step.
+
+The key to simulating these processes effectively is the ability to describe topological operations by \emph{curve diagrams}.
+This is an alternative representation of topological operations that is particularly suited to these kinds of numerical simulations of sparsely populated 2-dimensional anyon systems.
+The theoretical framework underpinning this description and the relation to to other representations of topological operations is discussed in Ref.~\cite{Burton2016}.
+
+In this section, we first describe our physical model of an anyon system and the corresponding noise, before showing how to simulate joint charge measurements (the core of syndrome extraction) within this model.
+The use of curve-diagrams is presented in an intuitive but ad-hoc way.
+Finally we describe our decoder and detail holistically how the different parts of the simulation interact.
+
+\subsection{Physical model}
+
+We consider anyon systems defined on a torus.
+We endow this with a $L\times L$ square lattice of observables:
+$$
+    \Lambda := \bigl\{ \gamma_{ij} \bigr\}_{i,j=1,...,L}
+$$
+These observables are the physically accessible charge observables that will be measured during syndrome extraction, before being passed to the decoder which will in turn determine physical recovery operations to be performed on the system.
+We call each $\gamma_{ij}$ a \emph{tile.}
+In figures we show a small gap between the tiles but this is not meant
+to reflect an actual physical gap.
+
+As noted above, the key to our model is to represent anyons and topological operations with curve diagrams.
+A curve diagram is a directed path that connects several anyons, which are denoted by preferred points along these paths.
+A curve diagram specifies a linear ordering of the anyons that allows us to define a basis for the corresponding fusion space, as well as to keep track of topological operations on this ordering.
+See Ref.~\cite{Burton2016} for a more formal introduction to curve diagrams.
+
+The main noise processes we consider in our simulations are pair-creation events, though other topological processes such as hopping, exchange, etc.~can also be implemented straightforwardly.
+The pair-creation process acts to populate the manifold with
+a randomly distributed set of anyon pairs,
+whose separation is much smaller than the size of a tile.
+
+Each such pair will have vacuum total charge and so the observables
+$\gamma_{ij}$ will only be affected by pairs that cross a tile boundary, i.e.~we
+need only consider distributing these pairs along edges of the tiles:
+\begin{center}
+\includegraphics[width=0.3\columnwidth ]{pic-pair-create.pdf}
+\end{center}
+
+In simulating system undergoing noise for time $T$, we place a Poisson-distributed number of pair-creation events on the edges of tiles, with mean $2L^2T$.
+
+In order to allow us to later calculate fusion outcomes for sets of anyons, in addition to locations of created anyons we also assign each pair a (directed) piece of curve, denoted in green.
+This curve can be thought of as a choice of fusion basis for the anyons along it.
+Since the total charge of any newly-created particle-antiparticle pair is vacuum, each of their fusion spaces can be treated independently.
+This results in our being able to consider independent disconnected curves for each such pair.
+We only need consider the joint state in the fusion space of different sets of anyons if they have interacted, and so it is with curve diagrams.
+Using this picture, it is easy to track the effects of moving anyons, which essentially are represented by appropriate extensions or deformations of the curve along which the anyon lies.
+These kinds of straightforward processes are all that are required to describe the noise and recovery steps of our simulation.
+
+\subsection{Syndrome extraction}
+
+Syndrome extraction in this model corresponds to simulating measurements of the observables $\gamma_{ij}$, which represent the total charge contained within the corresponding tile.
+In order to compute measurement outcomes for the $\gamma_{ij}$
+we first need to concatenate any two curve diagrams that 
+participate in the same $\gamma_{ij}.$
+Because each curve has vacuum total charge this can be
+done in an arbitrary way:
+\begin{center}
+\includegraphics[width=0.3\columnwidth ]{pic-join-pairs.pdf}
+\end{center}
+
+Working in the basis picked out by the resulting curve
+diagrams, we will show how to calculate measurement outcomes for each tile,
+the result of which is recorded on the original curve:
+\begin{center}
+\includegraphics[width=0.3\columnwidth ]{pic-curve-uniq.pdf}
+\end{center}
+
+%
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+%
+
+The basic data structure involved in the
+simulation we term a \emph{combinatorial curve diagram.}
+Firstly, we will require each curve to intersect 
+the edges of tiles transversally,
+and in particular a curve will not touch a tile corner.
+
+For each tile in the lattice,
+we store a combinatorial
+description of the curve(s) intersected with that tile.
+Each component of such an intersection we call a \emph{piece-of-curve.}
+\begin{center}
+\includegraphics[]{pic-cells.pdf}
+\end{center}
+
+We follow essentially the same approach as taken in \cite{Abramsky2007} 
+to describe elements of a Temperley-Leib algebra, but
+with some extra decorations.
+The key idea is to store a \emph{word} for each tile, comprised of
+the letters $\bigl<$ and $\bigr>$.
+Reading in a clockwise direction around the edge of
+the tile from the top-left corner,
+we record our encounters with each piece-of-curve,
+writing~$\bigl<$ for the first encounter, and~$\bigr>$ for the
+second.
+We may also encounter a dangling piece-of-curve
+(the head or the tail), so we use another symbol $*$ for this.
+The words for the above two tiles will then be 
+$\bigl<\bigl<\bigr>\bigr>\bigl<\bigr>$ and $\bigl<\bigr>*\bigl<\bigl<\bigr>\bigr>.$
+When the brackets are balanced,
+each such word will correspond one-to-one with an intersection
+of a curve in a tile, up to a continuous deformation of the interior of the tile,
+i.e.~the data structure 
+will be insensitive to any continuous deformation of the interior of the tile,
+but the simulation does not need to track any of these degrees of freedom.
+
+\begin{center}
+\includegraphics[]{pic-cells-0.pdf}
+\end{center}
+
+We will also need to record
+various other attributes of these curves,
+and to do this we make this notation more elaborate
+in the paragraphs {\bf (I)}, {\bf(II)} and {\bf(III)} below.
+Each symbol in the word describes an intersection of
+the curve with the tile boundary,
+and so as we decorate these symbols these decorations will
+apply to such intersection points.
+
+\begin{center}
+\includegraphics[]{pic-cells-1.pdf}
+\end{center}
+
+{\bf (I)} We will record the direction of each piece-of-curve,
+this will be either an {\tt in} or {\tt out} decoration for each symbol.
+Such decorations need to balance according to the brackets.
+The decorated symbols $*_{\mbox{\tt in}}$ and 
+$*_{\mbox{\tt out}}$ 
+will denote respectively either
+the head or the tail of a curve.
+The words for the diagrams above now read as
+$ \bigl<_{\mbox{\tt in}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}
+    \bigr>_{\mbox{\tt out}}\bigl<_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}$
+and
+$ \bigl<_{\mbox{\tt in}}\bigl>_{\mbox{\tt out}}*_{\mbox{\tt in}}
+    \bigr<_{\mbox{\tt out}}
+    \bigr<_{\mbox{\tt in}}\bigl>_{\mbox{\tt out}}\bigr>_{\mbox{\tt in}}.
+$
+
+{\bf (II)} We will record,
+for each intersection with the tile edge, 
+a numeral indicating which of the four
+sides of the tile the
+intersection occurs on.
+Numbering these clockwise from the top as $1, 2, 3, 4$ we have for the above curves: 
+$\bigl<_1\bigl<_2\bigr>_2\bigr>_3\bigl<_3\bigr>_4$ 
+and $\bigl<_1\bigr>_1*_2\bigl<_3\bigl<_3\bigr>_4\bigr>_4.$
+
+{\bf (III)} Finally, we will also decorate these symbols with anyons.
+This will be an index to a leaf of a (sum of) fusion tree(s).
+This means that anyons only reside on the curve close
+to the tile boundary,
+and so we cannot have more than two anyons
+for each piece-of-curve. 
+The number of such pieces is arbitrary, and so this
+is no restriction on generality.
+
+\begin{center}
+\includegraphics[]{pic-cells-2.pdf}
+\end{center}
+
+In joining tiles together to make a tiling we will
+require adjacent tiles to agree on their shared boundary.
+This will entail sequentially pairing symbols in the
+words for adjacent tiles
+and requiring that 
+the {\tt in} and {\tt out} decorations are matched.
+Because the word for a tile proceeds conter-clockwise
+around the tile, this pairing will always reverse the
+sequential order of the symbols of adjacent tiles.
+For example, given the above two tiles we sequentially pair the 
+$\bigl<_{\mbox{\tt out},2}\bigr>_{\mbox{\tt in},2}$ 
+and $\bigr>_{\mbox{\tt out},4}\bigr>_{\mbox{\tt in},4}$
+symbols with opposite order so that
+$\bigl<_{\mbox{\tt out},2}\sim\bigr>_{\mbox{\tt in},4}$
+and $\bigr>_{\mbox{\tt in},2} \sim \bigr>_{\mbox{\tt out},4}.$
+
+Note that in general, this will allow us to store the multiple disjoint curve diagrams that cover the lattice.
+
+For each piece-of-curve, apart from a head or tail, there is an associated 
+number we call the \emph{turn number}. This counts the number
+of ``right-hand turns'' the piece-of-curve makes as it
+traverses the tile, with a ``left-hand turn'' counting as $-1.$
+This number will take one of the values $-2, -1, 0, 1, 2:$
+\begin{center}
+\includegraphics[]{pic-cells-3.pdf}
+\end{center}
+
+%
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+%
+
+\subsection{The paperclip algorithm}
+
+In order to calculate the total charge of each tile, we must transport all anyons within the tile until they are neighbours along their curve.
+In doing so, it will be convenient to consider transporting these anyons by moving them along tile edges.
+This is equivalent to a ``refactoring'' of the fusion space, as described in Ref.~\cite{Burton2016}.
+We can further break down transport along the tile edge into a sequence of transports between neighbouring pieces of curve at that edge.
+The origin and destination of such a path
+now splits the curve diagram
+into three disjoint pieces which we term
+\emph{head}, \emph{body} and \emph{tail}, where
+the head contains the endpoint of the curve, the tail
+contains the beginning of the curve and the body is the remainder.
+Here we consider transport forwards along the curve (from tail towards head), but the reverse case is analogous.
+\begin{center}
+\includegraphics[]{pic-move-anyon.pdf}
+\end{center}
+
+This arrangement is equivalent (isotopic) to one of four 
+``paperclips'', which we distinguish between by counting how
+many \emph{right-hand turns} are made along the body of the curve diagram.
+We also show an equivalent (isotopic) picture where the
+curve diagram has been straightened, and the resulting distortion
+in the anyon path:
+\begin{center}
+\includegraphics[]{pic-paperclip.pdf}
+\end{center}
+In order to perform the desired transport, we must braid the anyon under consideration around the other anyons along the curve diagram.
+Denoting the sequence of anyons along the head, body and tail, $H, B$ and $T,$
+respectively, and using
+$H^r, B^r$ and $T^r$ to denote the same anyons with the reversed order, the appropriate braiding transformation ($R$-move) can be read off for each
+of the four paperclips:
+\begin{align*}
+-2:&\ R[B] \\
+-4:&\ R[H^r]\ R[H]\ R[B] \\
++4:&\ R[B]\ R[T]\ R[T^r] \\
++6:&\ R[H^r]\ R[H]\ R[B]\ R[T]\ R[T^r] \\
+\end{align*}
+where notation such as $R[B]$ is understood as sequentially clockwise braiding around
+each anyon in $B$.
+
+Once all the anyons within a tile have been brought into a sequential piece of the curve, their total charge can easily be read off by an appropriate $F$-move.
+This allows us to perform syndrome extraction, by repeating this procedure for each tile of the lattice.
+
+%
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+%
+
+\subsection{Decoding and error-correction}
+
+After the noise process is applied to the system,
+the error correction routine attempts to annihilate all the anyons on the lattice in a way that does not affect the encoded information. It proceeds as a dialogue between the
+decoder and the system.
+The syndrome extraction procedure provides information to the decoder, which suggests a recovery procedure, the results of which are found by a subsequent syndrome extraction step, and so on.
+This iterative procedure continues until the extracted syndrome is empty (i.e.~i.e.
+there are no remaining anyons on the lattice), or the decoder declares failure.
+Here we show this in a process diagram, with time running up
+the page:
+\begin{center}
+\includegraphics[]{pic-process.pdf}
+\end{center}
+
+So far we have discussed the simulation of the (quantum) system
+and now we turn to the decoder algorithm.
+This is similar to other clustering-type decoders used in the literature~\cite{Bravyi2011}, in that it attempts to form and fuse together clusters of anyons on larger and larger length scales, declaring failure if anyons remain after fusion at the largest length scale.
+Our simulation also declares failure if at any point the curve diagrams describing the state of the system form a homologically non-trivial loop (span the lattice), this being a necessary condition for error-correction failure.
+
+The structure of the error-correction routine is as follows, and will be illustrated by an example below.
+
+\begin{verbatim}
+ 1:  def error_correct():
+ 2:      syndrome = get_syndrome()
+ 3:      
+ 4:      # build a cluster for each charge
+ 5:      clusters = [Cluster(charge) for charge in syndrome]
+ 6:  
+ 7:      # join any neighbouring clusters
+ 8:      join(clusters, 1)
+ 9:      
+10:      while clusters:
+11:      
+12:          # find total charge on each cluster
+13:          for cluster in clusters:
+14:              fuse_cluster(cluster)
+15:      
+16:          # discard vacuum clusters
+17:          clusters = [cluster for cluster in clusters if non_vacuum(cluster)]
+18:      
+19:          # grow each cluster by 1 unit
+20:          for cluster in clusters:
+21:              grow_cluster(cluster, 1)
+22:      
+23:          # join any intersecting clusters
+24:          join(clusters, 0)
+25:  
+26:      # success !
+27:      return True
+\end{verbatim}
+
+First, we show the result of the initial call to {\tt get\_syndrome()}, on line 2. This is computed using the syndrome extraction step as described above.
+The locations of anyon charges are highlighted in red.
+For each of these charges we build a {\tt Cluster}, on line 5.
+Each cluster is shown as a gray shaded area.
+\begin{center}
+\includegraphics[]{pic-decode-0.pdf}
+\end{center}
+The next step is the call to {\tt join(clusters, 1)}, on line 8,
+which joins clusters that are separated by at most one lattice
+spacing. We now have seven clusters:
+\begin{center}
+\includegraphics[]{pic-decode-1.pdf}
+\end{center}
+Each cluster is structured as a rooted tree, as indicated by
+the arrows which point in the direction from the leaves to
+the root of the tree. 
+This tree structure is used in the call to {\tt fuse\_cluster()},
+on line 14.
+This moves anyons in the tree along the arrows to the root, 
+fusing with the charge at the root.
+This movement of anyons is a physical recovery operation that is easily simulated by extending the curve diagram along the transport path, and moving the anyons along it.
+\begin{center}
+\includegraphics[]{pic-decode-2.pdf}
+\end{center}
+For each cluster, the charge is then measured using the syndrome extraction procedure, and the resulting charge at the root is taken as the charge of
+that cluster. Any cluster with vacuum total charge is then discarded (line 17).
+In our example, we find two clusters with vacuum charge and we discard these.
+The next step is to grow the remaining clusters by one lattice spacing (line 20-21),
+and join (merge) any overlapping clusters (line 24).
+\begin{center}
+\includegraphics[]{pic-decode-3.pdf}
+\end{center}
+Note that we can choose the root of each cluster arbitrarily
+since we are only interested in the total charge of each cluster, and also that for simplicity we have neglected the boundary of the lattice in
+this example.
+
+We repeat these steps of fusing, growing and then joining clusters (lines 10-24.)
+If at any point this causes a topologically 
+non-trivial operation, the simulation aborts and a failure
+to decode is recorded.
+Otherwise we eventually run out
+of non-vacuum clusters, and the decoder succeeds (line 27).
+
+By repeatedly performing this simulation of noise and error-correction on different sized lattices, and for different noise rates (or memory lifetimes), we are able to estimate the error-correction threshold for this type of system.
+
+%------------------------------------------------------------------------------------------------------------%
+
 \begin{acknowledgments}
@@
 \end{acknowledgments}
+
+%\bibliography{refs2}
+
+%------------------------------------------------------------------------------------------------------------%
 
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{42}%
+\begin{thebibliography}{43}%
 \makeatletter
@@
   {NoStop}%
+\bibitem [{\citenamefont {Abramsky}(2007)}]{Abramsky2007}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Abramsky}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Mathematics of
+  Quantum Computing and Technology}}},\ \bibinfo {editor} {edited by\ \bibinfo
+  {editor} {\bibfnamefont {L.~K.}\ \bibnamefont {G.~Chen}}\ and\ \bibinfo
+  {editor} {\bibfnamefont {S.}~\bibnamefont {Lomonaco}}}\ (\bibinfo
+  {publisher} {Taylor \& Francis},\ \bibinfo {year} {2007})\ pp.\ \bibinfo
+  {pages} {415--458}\BibitemShut {NoStop}%
 \end{thebibliography}%
 
+%------------------------------------------------------------------------------------------------------------%
+
 \end{document}

### 2017-01-24 guide.tex
update after comment from B. Bartlett. Update refs.

@@
 
+% CUT HERE
 \newcommand{\ket}[1]{|{#1}\rangle}
@@
 \newcommand{\proj}[1]{\ketbra{#1}{#1}}
+\newcommand{\C}{\mathbb{C}}
+\newcommand{\R}{\mathbb{R}}
+% CUT HERE
 
@@
 \newcommand{\F}{\mathscr{H}} % H or F ?
-\newcommand{\C}{\mathbb{C}}
-\newcommand{\R}{\mathbb{R}}
 \newcommand{\A}{\mathcal{A}}
@@
 as in the Schr\"{o}dinger picture,
-modular functors would
-correspond to the algebra of observables, as in
+the axioms for modular functors 
+incorporate the algebra of observables, as in
 a Heisenberg picture.
+%modular functors would
+%correspond to the algebra of observables, as in
+%a Heisenberg picture.
 
@@
 explicitly used in Refs.~\cite{Freedman2002, Freedman2002simulation}.
-Also, Refs.~\cite{Beverland2014} and \cite{Kitaev2006topo}
+Also, Refs.~\cite{Beverland2016} and \cite{Kitaev2006topo}
 use the language of modular functors but they call them TQFT's.
@@
 However, in this work we restrict anyons to have
-definite charge states, as in \cite{Walker1991,Freedman2002simulation,Beverland2014}. 
+definite charge states, as in \cite{Walker1991,Freedman2002simulation,Beverland2016}. 
 This seems to be motivated physically as such configurations
@@
 %\cite{Turaev1994}, \cite{Walker1991} or \cite{Bakalov2001}.
-%For a more pedestrian treatment, see \cite{Freedman2002simulation} or \cite{Beverland2014}.
+%For a more pedestrian treatment, see \cite{Freedman2002simulation} or \cite{Beverland2016}.
 
@@
 
+% CUT HERE
 \begin{acknowledgments}
@@
 The author wishes to thank 
-Andrew Doherty, Courtney Brell, Steven Flammia and Dominic Williamson
+Andrew Doherty, Courtney Brell, Steven Flammia, Dominic Williamson and
+Bruce Bartlett 
 for helpful discussions and inspiration.
